### 2018-08-15 Analyze_summaries.Rmd
Initial commit

---
title: "Parsing mPFC: Community analysis"
author: "Claudio Toro-Serey & Joseph T. McGuire"
#date: "7/2/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

``` {r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}
Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere

# In case I want to visualize stuff in the brain
labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[,2:6]
labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))

library(igraph)
library(pander)
library(ggnetwork)
library(ggplot2)
library(gridExtra)
library(data.table)
library(plyr)
library(mcclust)
library(lme4)
library(parallel)
library(corrplot)
library(DescTools)

## Cohen's D for 2 groups
# for a more flexible approach, make the data input to be a list with entries for n groups, 
# then do length(list) for the number of groups. 
cohenD <- function(group1 = 1, group2 = 2){

  # means
  mean1 <- mean(group1, na.rm = T)
  mean2 <- mean(group2, na.rm = T)

  # variance
  var1 <- var(group1, na.rm = T)
  var2 <- var(group2, na.rm = T)

  # equation
  out <- (mean1 - mean2) / sqrt((var1 + var2)/2)

  return(out)

}

## log-log degree distribution
logDegreeDist <- function(Graph = padjMat) {

  tempD <- degree(Graph)
  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
  d <- (0:(max(tempD)-1))
  ind <- (tempDD!=0)
  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
       xlab = "Log-Degree", ylab = "Log-Intensity",  
       main = "Log-Log Degree Distribution")

}

## Create correlation matrix between vertices of 2 ROIs
# Requires labeled time series matrix
vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){

  # extract the time series from the ROIs
  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
  nVerts_1 <- length(indexing_1)
  nVerts_2 <- length(indexing_2)
  ROI_1_tseries <- timeSeries[indexing_1, ]
  ROI_2_tseries <- timeSeries[indexing_2, ]

  # Create empty matrix
  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)

  # 
  for (vertex_1 in seq(nVerts_1)){

    # temp series 1
    tempOne <- ROI_1_tseries[vertex_1, ]

    for(vertex_2 in seq(nVerts_2)){

      # temp series 2
      tempTwo <- ROI_2_tseries[vertex_2, ]

      # store the Pearson correlation in the corr matrix
      corrMat[vertex_1, vertex_2] <- cor(tempOne, tempTwo, method = "pearson")

    }
  }

  # name the dimensions of the matrix according to the surface vertex index
  rownames(corrMat) <- indexing_1
  colnames(corrMat) <- indexing_2

  # plot (optional?)  
  # unclustered heatmap
  heatmap(corrMat,
          Rowv = NA,
          Colv = NA,
          scale = "row",
          col = pallette(1000))

  # clustered heatmap
  heatmap(corrMat,
          scale = "row",
          col = pallette(1000))

  # print min-max corr vals
  print(range(corrMat))

  return(corrMat)

}

## Correlation matrix between an ROI and the Glasser parcels
parcelCorrMat <- function(ROI = 'R_7m_ROI', lbels = lookup$V1){

  # extract the time series from the ROIs
  indexing <- which(rownames(timeSeries)==as.character(ROI))
  nVerts <- length(indexing)
  ROI_tseries <- timeSeries[indexing, ]

  # create empty matrix to store values
  corrMat <- matrix(data = 0, nrow = nVerts, ncol = 360)

  # Loop through every combination of label and 7m vertex
  for (Parcel in lbels){

    # Get an ROI index to retrieve timeseries and store correlation vals
    indxROI <- which(lbels==as.character(Parcel))

    for(vertex in seq(nVerts)){

      # temp series
      tempROI <- as.numeric(ptSeries[indxROI, ])
      tempVertex <- ROI_tseries[vertex, ]

      # store the Pearson correlation in the corr matrix
      corrMat[vertex, indxROI] <- cor(tempROI, tempVertex, method = "pearson")

    }
  }

  # name the columns according to labels
  colnames(corrMat) <- lbels
  rownames(corrMat) <- indexing

  # plot (optional?)  
  # unclustered heatmap
  heatmap(corrMat,
          Rowv = NA,
          Colv = NA,
          scale = "none",
          col = pallette(1000))

  # clustered heatmap
  heatmap(corrMat,
          scale = "none",
          col = pallette(1000))

  # print min-max corr vals
  print(range(corrMat))

  return(corrMat)

}

## Correlation matrix between an Parcel and every other grayordinate
# THIS CAN BE OPTIMIZED WITH A BETTER USE OF COR()
partoverCorrMat <- function(ROI = 'R_7m_ROI', lbels = verts[[1]]){

  # extract the time series from the ROI
  indexing <- which(rownames(ptSeries)==as.character(ROI))
  ROI_tseries <- as.numeric(ptSeries[indexing, ])

  # get the remaining number of vertices
  nVerts <- length(lbels)

  # Create data frame to store values
  parcelIndx <- which(labelCoords_parcel$Label==ROI)
  corrVec <- data.frame(Seed = rep(ROI, nVerts),
                        Labels = lbels,
                        xstart = rep(labelCoords_parcel$x[parcelIndx], nVerts), # 7.33324 for R_7m
                        ystart = rep(labelCoords_parcel$y[parcelIndx], nVerts), # -63.142
                        zstart = rep(labelCoords_parcel$z[parcelIndx], nVerts)) # 42.5578

  for(vertex in seq(nVerts)){

    # temp series
    tempVertex <- timeSeries[vertex, ]

    # store the Pearson correlation in the corr matrix
    #corrVec$Correlation[vertex] <- cor(ROI_tseries, tempVertex, method = "pearson")

    # Another option, so that FDR can be applied
    tempCor <- cor.test(ROI_tseries, tempVertex, method = "pearson")
    corrVec$Correlation[vertex] <- tempCor$estimate
    corrVec$pval[vertex] <- tempCor$p.value

  }

  # Turn ROI vertices into 0s
  indexing <- which(corrVec$Labels==as.character(ROI))
  corrVec$Correlation[indexing] <- 0

  # Create a column with p-vals corrected for multiple comparisons
  corrVec$adjPval <- p.adjust(corrVec$pval, "BY")

  # normalize correlation vals for analysis (see below)
  tempTanh <- fisherTanh(Data = corrVec$Correlation)
  corrVec$tanhZ <- tempTanh$tanhZ
  corrVec$tanhPvals <- tempTanh$pvals
  corrVec$tanhPAdjusted <- tempTanh$adjustPvals

  return(corrVec)

}

## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
# Normalization approach suggested in network textbook (equation 7.10)
fisherTanh <- function(Data = padjMatrix){

  transformed <- list()

  # tanh
  transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))

  # p-vals
  if (is.matrix(Data)) {
    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
    n <- dim(Data)[1]
  } else if (is.vector(Data)) {
    z.vec <- transformed$tanhZ
    n <- length(Data)
  }
  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)

  # adjust pvals
  transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")

  if (is.matrix(Data)) {
    # get pvals and their adjustment into a symetric matrix form
    # regular
    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
    tempMat[upper.tri(tempMat)] <- transformed$pvals
    tempMat[lower.tri(tempMat)] <- transformed$pvals
    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
    transformed$pvals <- tempMat

    # adjusted
    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
    tempMat[upper.tri(tempMat)] <- transformed$adjustPvals
    tempMat[lower.tri(tempMat)] <- transformed$adjustPvals
    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
    transformed$adjustPvals <- tempMat
  }

  return(transformed)

}

## Extract the centroid-most vertex from each parcel
parcelCentroid <- function(ROI = 'R_7m_ROI', all_coordinates = labelCoords_vertex){

  # The coordinate file must contain a Label column

  # Get the ROI-specific vertices
  indx <- grep(ROI, all_coordinates$Label)

  # Grab the coordinates
  tempCoords <- all_coordinates[indx, c("x","y","z")]
  rownames(tempCoords) <- indx

  # Compute the distance among all vertices, and turn into a matrix
  tempDist <- dist(tempCoords, diag = T)
  tempDist <- as.matrix(tempDist)

  # Compute the sum of distances for each vertex, and get the minimum
  sumDists <- colSums(tempDist)
  minDist <- which(sumDists == min(sumDists))
  minDist <- indx[minDist]

  return(minDist)

}

## This function takes the output from partoverCorrMat() and adds/removes the characteristics we decided on.
prepROItoVer <- function(Data = R_7m_allCorr, Coordinates = labelCoords_vertex){

  # Add vertex coordinates
  tempDframe <- cbind(Data, Coordinates[,1:3])

  # Remove rows with non-significant adjusted pvalues
  indx <- tempDframe$adjPval < 0.05
  tempDframe <- tempDframe[indx, ]

  # Characterize correlation direction and round up vals for plotting
  tempDframe$Relation <- ifelse(tempDframe$Correlation < 0, "Negative", "Positive")
  tempDframe$Correlation <- round(tempDframe$Correlation, digits = 2)

  # Add a column to differentiate between left/right hemispheres
  tempDframe$Hemisphere <- substring(tempDframe$Labels,1,1)

  return(tempDframe)

}

## Plot correlation from ROI to rest of vertices
plotROItoVertex <- function(Data = R_7m_allCorr, ROI = 'R_7m_ROI', ColRange = Cols, View = "Axial", Legends = TRUE){

  ROIindx <- grep(ROI, Data$Labels)
  ROIvertices <- Data[ROIindx,c("x","y","z")] # grab ROI-specific vertices to black out
  labelCoord <- ROIvertices[1,] # just to place the label

  if (View == "Axial") {
    ggplot() +
      geom_point(data = Data, aes(x=x, y=y, alpha=.5, color = Correlation), show.legend = Legends) +
      geom_point(data = labelCoords_vertex, aes(x=x, y=y), alpha=0.01) +
      geom_nodes(data = ROIvertices, aes(x=x, y=y)) +
      geom_nodelabel_repel(aes(x=labelCoord$x, y=labelCoord$y, label = sub("_ROI","",ROI))) +
      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
      theme_blank()
  } else if (View == "Sagittal") {
    ggplot() +
      geom_point(data = Data, aes(x=y, y=z, alpha=.5, color = Correlation), show.legend = Legends) +
      geom_point(data = labelCoords_vertex, aes(x=y, y=z), alpha=0.01) +
      geom_nodes(data = ROIvertices, aes(x=y, y=z)) +
      geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
      theme_blank()
  } else if (View == "Coronal") {
    ggplot() +
      geom_point(data = Data, aes(x=x, y=z, alpha=.5, color = Correlation), show.legend = Legends) +
      geom_point(data = labelCoords_vertex, aes(x=x, y=z),  alpha=0.01) +
      geom_nodes(data = ROIvertices, aes(x=x, y=z), alpha=.5) +
      geom_nodelabel_repel(aes(x=labelCoord$x, y=labelCoord$z, label = sub("_ROI","",ROI))) +
      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
      theme_blank()
  } else if (View == "Medial Right") {
    if (substring(ROI,1,1) == "R") {
      oneHemi <- Data[grep("R", Data$Hemisphere), ]
      oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
      medialHemi$y <- medialHemi$y * -1
      ROIvertices$y <- ROIvertices$y * -1
      labelCoord$y <- labelCoord$y * -1
      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
      medialHemi_all$y <- medialHemi_all$y * -1
      ggplot() +
        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
        geom_nodes(data = ROIvertices, aes(x=y, y=z), alpha=.5) +
        geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
        theme_blank()
    } else {
      oneHemi <- Data[grep("R", Data$Hemisphere), ]
      oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
      medialHemi$y <- medialHemi$y * -1
      ROIvertices$y <- ROIvertices$y * -1
      labelCoord$y <- labelCoord$y * -1
      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
      medialHemi_all$y <- medialHemi_all$y * -1
      ggplot() +
        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
        theme_blank()
    }
  } else if (View == "Medial Left") {
    if (substring(ROI,1,1) == "L") {
      oneHemi <- Data[grep("L", Data$Hemisphere), ]
      oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
      ggplot() +
        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
        geom_nodes(data = ROIvertices, aes(x=y, y=z), alpha=.5) +
        geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
        theme_blank()
    } else {
      oneHemi <- Data[grep("L", Data$Hemisphere), ]
      oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
      ggplot() +
        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
        theme_blank()
    }
  }

}

## Run a fastgreedy modularity community detection on ROIs
# This function relies on having the timeSeries data uploaded, and labelCoords_vertex 
# Extras dictates whether the community object + correlation matrix should also be extracted
communityDetection <- function(Data = parcelBins$First, ROIS = "None", Type = "vertex", thresh = F, extras = F) {

  print(paste('Computing modularity based on', Type))

  if (ROIS == "None"){

    # This will just do SP for now, for sliding window
    print("Previously concatenated data")

    corrMat <- cor(t(Data))
    corrMatrix <- corrMat
    transfMat <- fisherTanh(Data = corrMat)
    if (thresh == T) {
      transfMat$tanhZ[transfMat$adjustPvals > 0.05] <- 0
    }
    corrMat <- transfMat$tanhZ

    diag(transfMat$tanhZ) <- 0    
    diag(corrMat) <- 0

    corrMat <- exp(corrMat)
    corrMat[corrMat==1] <- 0
    transfMat$tanhZ <- corrMat

    tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
    tempLap <- laplacian_matrix(tempGraph, normalized=T)
    tempEigen <- eigen(tempLap)
    f.vec <- length(tempEigen$values) - 1
    tempEigen$binarized <-  as.factor(ifelse(tempEigen$vectors[,f.vec] > 0, 1, 0)) # binarized Fiedler Vector

    summary <- data.frame(Label = colnames(corrMat),
                          Hemisphere = substring(colnames(corrMat),1,1),
                          EigenVal = tempEigen$values,
                          FiedlerVec = tempEigen$vectors[, (length(tempEigen$values) - 1)],
                          FiedlerBinary = tempEigen$binarized)

    ## Get the final components
    if (extras == T) {
      modularityResults <- list(CorrMatrix = corrMatrix,
                                TransfMatrix = transfMat,
                                Summary = summary)
    } else {
      modularityResults <- list(Summary = summary)
    }

  } else {

    if (Type == "vertex") {
      # To store the vertex indices corresponding to the ROIs
      indx <- numeric()

      # had to place dashes on each side because grep grabbed strings containing the names (i.e. 47m, a24pr)
      #ROIS <- c("_7m_", vmPFC_labels) # c("_a24_", "_7m_")
      for (ROI in ROIS) {
        indx <- c(indx, grep(ROI, rownames(Data)))  
      }

      nVerts <- length(indx)
      ROI_tseries <- Data[indx, ]

      # This used to be done with the for loop, but it was too slow. cor() speeds up the process by a lot
      corrMat <- cor(t(ROI_tseries))

      # name the dimensions of the matrix according to the surface vertex index
      rownames(corrMat) <- indx

      # for storing later
      corrMatrix <- corrMat

      # transform to Fisher's (think of thresholding)
      transfMat <- fisherTanh(Data = corrMat)

      # Determine if edges should be thresholded or not
      if (thresh == T) {
        transfMat$tanhZ[transfMat$adjustPvals > 0.05] <- 0
      }

      # Store Fisher transformed vals for graphing
      corrMat <- transfMat$tanhZ

      # diagonals of 1 could be interpreted as self-loops
      diag(transfMat$tanhZ) <- 0    
      diag(corrMat) <- 0

      # Exponentiate to preserve distribution while ensuring positive weights
      # I'm keeping corrMat and transfMat$tanhZ separate in case I want to uncorrect transfMat in the future
      corrMat <- exp(corrMat)
      corrMat[corrMat==1] <- 0
      transfMat$tanhZ <- corrMat

      # community detection
      # I initially used the absolute value of the correlation, but the exp preserves the distribution 
      # Next, try using the fisher transform

      tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
      tempCommunity <- fastgreedy.community(tempGraph)

      # community object
      #modularityResults$community <- tempCommunity

      # correlation matrix with transformed values
      #modularityResults$corrMat <- corrMatrix

      # get coordinate info from selected regions (useful for ggplot)
      summary <- data.frame(Vertex = indx,
                            Label = tempCommunity$names,
                            Membership = tempCommunity$membership,
                            Modularity = tempCommunity$modularity,
                            x = labelCoords_vertex[indx, "x"],
                            y = labelCoords_vertex[indx, "y"],
                            z = labelCoords_vertex[indx, "z"],
                            Hemisphere = substring(tempCommunity$names,1,1))

    } else if (Type == "parcels") {

      # This used to be done with the for loop, but it was too slow. cor() speeds up the process by a lot
      corrMat <- cor(t(Data))

      # for storing later
      corrMatrix <- corrMat

      # transform to Fisher's (think of thresholding)
      transfMat <- fisherTanh(Data = corrMat)

      # Determine if edges should be thresholded or not
      if (thresh == T) {
        transfMat$tanhZ[transfMat$adjustPvals > 0.05] <- 0
      }

      # Store Fisher transformed vals for graphing
      corrMat <- transfMat$tanhZ

      # diagonals of 1 could be interpreted as self-loops
      diag(transfMat$tanhZ) <- 0
      diag(corrMat) <- 0

      # Exponentiate to preserve distribution while ensuring positive weights
      # I'm keeping corrMat and transfMat$tanhZ separate in case I want to uncorrect transfMat in the future
      corrMat <- exp(corrMat)
      corrMat[corrMat==1] <- 0
      transfMat$tanhZ <- corrMat

      # community detection
      # I initially used the absolute value of the correlation, but the exp preserves the distribution 
      # Next, try thresholding it by the adjusted p-vals
      tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
      tempCommunity <- fastgreedy.community(tempGraph)

      # community object
      #modularityResults$community <- tempCommunity

      # correlation matrix with transformed values
      #modularityResults$corrMat <- corrMatrix

      # get coordinate info from selected regions (useful for ggplot)
      summary <- data.frame(Label = tempCommunity$names,
                            Membership = tempCommunity$membership,
                            Modularity = tempCommunity$modularity,
                            x = labelCoords_parcel[ ,"x"],
                            y = labelCoords_parcel[ ,"y"],
                            z = labelCoords_parcel[ ,"z"],
                            Hemisphere = substring(tempCommunity$names,1,1))

    }

    ## Get the final components
    modularityResults <- list(Community = tempCommunity,
                              CorrMatrix = corrMatrix,
                              TransfMatrix = transfMat,
                              Summary = summary)

  }

  return(modularityResults)

}

## plot the communities from communityDetection
plotCommunities <- function(Data = modularityResults, Hemi = "R", type = "Membership", Legends = T, bground=0.1, Cols = c("aquamarine4", "#D9541A")) {
  # This takes the output from the communityDetection function and plots them on the medial wall (since we're interested in medial now)
  # type is the name of the column to plot
  if (Hemi == "R") {
    # "Medial Right"
    oneHemi <- Data[grep("R", Data$Hemisphere), ] # from the ROIs
    oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
    medialHemi <- oneHemi[grep("Medial", oneHemi$Medial), ]
    medialHemi$y <- medialHemi$y * -1
    oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
    oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
    medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
    medialHemi_all$y <- medialHemi_all$y * -1
    ggplot() + 
      geom_point(data = medialHemi, aes_string(x="y", y="z", color = type), show.legend=Legends) +
      geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=bground) +
      scale_color_gradient(low = Cols[1], high = Cols[2]) +
      theme_blank() 
  } else if (Hemi == "L") {
    # "Medial Left"
    oneHemi <- Data[grep("L", Data$Hemisphere), ]
    oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
    medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
    oneHemi_all <- labelCoords_vertex[grep("L",labelCoords_vertex$Hemisphere), ] # whole surface
    oneHemi_all$Medial <- ifelse(oneHemi_all$x > -20, "Medial", "Other")
    medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
    ggplot() + 
      geom_point(data = medialHemi, aes_string(x="y", y="z", color = type), show.legend=Legends) +
      geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=bground) +
      scale_color_gradient(low = Cols[1], high = Cols[2]) +
      theme_blank() 
  }
}

## get ROI coords & index
# The point here is to reduce the summary dframes from community detection to show only ROIs
# Should work for extracting any label-indexed dframe though
# I wanted to also get the index in case I want to extract specific rows from parcel/vertex coord dframes
getCoords <- function(Labels = DMN_labels, Coords = labelCoords_parcel, TimeSeries = FALSE){

  indx <- numeric()

  # If you want to select time series from raw data
  if (TimeSeries == TRUE) {

    for (ROI in Labels) {
      indx <- c(indx, grep(ROI, rownames(Coords)))
    }

  } else { # for the summary output of the community detection output

    for (ROI in Labels) {
      indx <- c(indx, grep(ROI, Coords$Label))
    }

  }

  results <- list()
  results$Index <- indx
  results$Coords <- Coords[indx, ]

  return(results)

}

# eigen value community detection
eigenVals <- function(Data = binnedCommunities_p$First) {

  # This will produce a vector of values, ready to be plotted
  tempGraph <- graph_from_adjacency_matrix(Data$TransfMatrix$tanhZ, mode = "undirected", weighted = T)
  tempGraph <- laplacian_matrix(tempGraph, normalized=T)
  tempGraph <- eigen(tempGraph)
  f.vec <- length(tempGraph$values) - 1
  tempGraph$binarized <-  as.factor(ifelse(tempGraph$vectors[,f.vec] > 0, 1, 0)) # binarized Fiedler Vector

  return(tempGraph)

}

# Attempt at setting up data for confusion matrices and Jaccard index calculations
confusionMatrix <- function(partition1 = parcelCommunities[[1]]$Membership, partition2 = parcelCommunities[[1]]$FiedlerBinary) {

  # Divide partitions to evaluate
  # Usually 2 will be fiedler

  # Check if any partition has 0s (since I binarize the Fiedler vector)
  if (0 %in% partition1) {

    partition1[grep(0, partition1)] <- 1
    partition1[grep(1, partition1)] <- 2

  }

  if (0 %in% partition2) {

    partition2[grep(1, partition2)] <- 2   
    partition2[grep(0, partition2)] <- 1

  }

  # Community sizes
  commSizes1 <- table(partition1)
  commSizes2 <- table(partition2)

  # Number of communities per partition
  nComms1 <- length(commSizes1)
  nComms2 <- length(commSizes2)

  # Number of vertices
  n <- length(partition1)

  # Putting together elements of the confusion matrix
  confMatrix <- matrix(nrow = nComms1,
                       ncol = nComms2)

  for (i in as.numeric(case.names(commSizes1))) {

    # Vertices belonging to community qX of partition X
    tempComm1 <- partition1 == i

    for (j in as.numeric(case.names(commSizes2))) {

      # Vertices belonging to community qY of partition Y
      tempComm2 <- partition2 == j

      # Populate matrix
      confMatrix[i,j] <- sum(tempComm1 & tempComm2)

    }
  }

  if (sum(confMatrix) != n) {warning('Sum of the confusion matrix is not equal to number of vertices')}

  return(confMatrix)

}

# Permutation for 2 groups
permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){

  # prep data
  summaryPerm <- list()
  lOne <- length(group1)
  lTwo <- length(group2)
  bigSample <- c(group1,group2)

  if (paired == FALSE) {

    for (i in 1:nPerms){

      # relabel samples
      tempBig <- sample(bigSample)
      tempOne <- tempBig[1:lOne]
      tempTwo <- tempBig[(lOne+1):length(bigSample)]

      # stats
      tempDiffs <- statType(tempOne,na.rm=T) - statType(tempTwo,na.rm=T)
      summaryPerm$jointDist[i] <- tempDiffs # statType(tempDiffs, na.rm = T)

    }

  } else {

    for (i in 1:nPerms){

      # shift labels in a pairwise fashion
      tempDiffs <- statType((-1)^rbinom(lOne,1,0.5) * (group1 - group2))
      summaryPerm$jointDist[i] <- tempDiffs

    }

  }

  # get the observed difference
  diffs <- statType(group1,na.rm=T) - statType(group2,na.rm=T)
  observedAbs <- abs(diffs) # maybe leave it as means here
  observed <- diffs
  summaryPerm$Pval <- 2 * (1 - ecdf(summaryPerm$jointDist)(observedAbs))
  if (length(unique(abs(summaryPerm$jointDist))) == 1) {summaryPerm$Pval <- 1} # if the difference is always the same, then p = 1
  summaryPerm$Observed <- observed

  return(summaryPerm)

}

# Non-parametric Bootstrap for a single group
bootstrap <- function(group = 1, statType = mean, B = 5000){

  # prep param
  bootStats <- rep(0,B)

  # iterate
  for(b in 1:B){

    # wait group
    x <- sample(group,length(group),replace=T)  
    bootStats[b] <- statType(x,na.rm = T)

  }

  return(bootStats)

}

# number of times a node changes affiliation in a time series
flexibility <- function(Data = cbind(1:10, 6:15)) {
  # Calculation of flexibility based on Garcia et al., 2018  
  # This function takes in a data frame or matrix in which columns are the community affiliation 
  # It needs at least 2 colums, although it's pointless for that

  # How many jumps can there be?
  nJumps <- dim(Data)[2] - 1

  # Matrix to store jumps
  jumpCount <- matrix(nrow = dim(Data)[1], ncol = nJumps)

  # For each transition, get the which nodes changed affiliation
  for (jump in seq(nJumps)) {

    jumpCount[, jump] <- Data[, jump] != Data[, jump + 1]

  }

  # How many times did every node jump?
  totalJumps <- rowSums(jumpCount)

  # Calculate the flexibility per node
  flexibility <- totalJumps / nJumps

  return(flexibility)

}

# Sliding window
slidingWindow <- function(subjTS = ROI_timeSeries[[1]], mins = 15, jump = 1, Spectral = T, Modularity = F, ROIs = c("_7m_", vmPFC_labels)) {
  # This is a fairly specific function. It takes the time series from a participant and preps/runs community detection at each specified time window. 
  # Returns the summaries for each window (based on communityDetection function)
  # The selection of a window size is based on the fact that a TR = 0.720s and an hour is 5000 TRs (HCP-based)
  # Since each subject has a different amount of time points, and all are slightly under 1 hr, I chose to round down the number of window moves to avoid unevenness
  # 
  # Parameter definitions:
  #   
  #   subjTS: Subject time series. Note: if you want to look at more than vmpfc and 7m, add a parameter for the labels that can be passed to the community detection function
  # 
  #   mins: Size of the window that will slide through the data.
  #   
  #   jump: Steps (in mins) advanced per slide
  #   
  #   Spectral: Whether to compute spectral partitioning as well. Takes significantly longer, but might be more useful for bisections
  #
  # Right now this takes ~27 mins per subject to run. Think of ways to improve that.

  # Adapted so it works with the output from getCoords
  # One wouldn't really apply a full-brain analysis of this sort anyways, too computationally intensive
  indx <- subjTS$Index
  subjTS <- subjTS$Coords

  # Window sizing (length)
  # Think about incorporating custom TRs
  TS <- dim(subjTS)[2] # time series for the subject
  WS <- seq(834 * (mins/10)) # window from the first TR up to 834 (~10 mins) times the desired multiplier
  jump <- 84 * jump # 84 ~ 1 min, times the number of mins that the window moves
  nJumps <- floor((TS - length(WS)) / jump) # number of jumps to be performed, based on the selected parameters

  ##------- using lapply
  winData <- mclapply(seq(nJumps), function(x) subjTS[,WS+(jump*(x-1))])
  commTS <- mclapply(winData, communityDetection, ROIS = "None", Type = "vertex", thresh = T, extras = F)
  return(commTS)

}

# compare sliding window data to overall communities
slideCompare <- function(subjData = slideCommunities[[1]], template = vmpfc7mCommunities[[1]], func = "RI", comm = "Spectral") {
  # This function compares the community partition from each window slide to the one derived from the whole data set
  # 
  # Parameter definitions:
  #   
  #   subjData: A participant's output from slideCommunities
  #   
  #   template: The partition from the whole time series
  # 
  #   func: Which function to use for comparing ("RI" for adjusted RI, "VI" for variation of information)
  # 
  #   comm: The subject data might contain modularity and spectral partitions. Choose which to use.

  # For storing RIs or VIs
  tempComparison <- numeric()

  # How many jumps does the original data contain?
  nJumps <- length(subjData)

  # This loop is technically backwards. I should technically divide by function, then partition method, and then run the window comparisons
  # It's still really fast, so I won't worry.
  for (Win in seq(nJumps)) {
    if (comm == "Modularity") {
      if (func == "RI") {
        tempComparison[Win] <- arandi(subjData[[Win]]$Membership, template$Membership, adjust = T)
      } else if (func == "VI") {
        tempComparison[Win] <- vi.dist(subjData[[Win]]$Membership, template$Membership)
      }
    } else if (comm == "Spectral") {
      if (func == "RI") {
        tempComparison[Win] <- arandi(subjData[[Win]]$FiedlerBinary, template$FiedlerBinary, adjust = T)
      } else if (func == "VI") {
        tempComparison[Win] <- vi.dist(subjData[[Win]]$FiedlerBinary, template$FiedlerBinary)
      }
    }
  }

  return(tempComparison)

}

# Ensure that all spectral communities associated with 7m (i.e. DMN) have the same label value of 1 
evenSpectral <- function(Data = slideCommunities[[1]][[7]]) {

  # Get only the values for 7m
  shortData <- Data[grep("_7m_", Data$Label), ]

  # Get 7m's most probable affiliation
  affil <- mean(as.numeric(shortData$FiedlerBinary)-1)

  # If it is close to 1, then invert the labeling. 
  # Note: This has no effect on RI or VI, since they are insensitive to actual labeling
  # This is for visualization purposes only
  if (affil < 0.5) {

    UD <- as.numeric(Data$FiedlerBinary) - 1
    Data$FiedlerBinary <- as.factor((UD - 1)^2)
    Data$FiedlerVec <- Data$FiedlerVec * -1

  }

  return(Data)

}

# Create a vector ready to be used for HCP data (32k CIFTI surface)
# The input should be the summary from community partitioning
# Once this is created, go to the terminal and input something like this
# wb_command -cifti-convert -from-text dataforCifti.txt 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii testCifti.dscalar.nii
# Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307"){

  nVertices <- 59412
  tempVec <- rep(-1, nVertices)
  temp <- grep(MOI, colnames(Data))
  tempVec[Data$Vertex] <- Data[[temp]]
  write.table(file = paste(SubjID,"_",MOI,'_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")

}

# Perform pairwise comparisons of clustering outcomes on all subjects
comparePartitions <- function(Data = dmnval7mCommunities, MOI = "FiedlerBinary", Index = "VI", nSubjects = nSubj, subjNames = subjList) {
  # This function will compare the community partitions from all subjects and create a 'comparison matrix' for every pairwise combination of subjects
  # Alternatively, if a second MOI is added 
  # Inputs
  # 
  # Data: the list of summaries produced by the script
  # 
  # MOI: measure of interest (usually the binarized Fiedler vector). If a vector, compares across algorithms per subject
  # 
  # Index: VI for variation of information, RI for the adjusted rand index, Cor for a Pearson correlation

  # Get the column position of the MOI(s)
  Columns <- colnames(Data[[1]])
  indx <- as.numeric(Columns %in% MOI)
  MOI_indx <- which(indx==1)

  if (length(MOI_indx) < 2) {
    # Combine the measures of interest
    allVecs <- do.call(cbind, lapply(Data, "[[", MOI))

    # Create empty matrix
    indexMatrix <- matrix(data = NA, nrow = nSubjects, ncol = nSubjects)
    dimnames(indexMatrix) <- list(subjNames, subjNames)

    # Run every pairwise comparison with the index of interest on the measure of interest
    if (Index == "VI") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- vi.dist(allVecs[, subj], allVecs[, subj2])
        }
      }
    } else if (Index == "RI") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- arandi(allVecs[, subj], allVecs[, subj2], adjust = T)
        }
      }
    } else if (Index == "Cor") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- cor(allVecs[, subj], allVecs[, subj2])
        }
      }
    }
  } else {
    indexMatrix <- data.frame(SubjID = as.character(subjList),
                              Index = rep(0, nSubjects))
    # Run every pairwise comparison with the index of interest on the measure of interest
    if (Index == "VI") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- vi.dist(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
      }
    } else if (Index == "RI") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- arandi(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]], adjust = T)
      }
    } else if (Index == "Cor") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- cor(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
      }
    }
  }

  return(indexMatrix)

}

# Generate a matrix with submatrices of 1s of a given size along the diagonal
# Useful to extract specific portions of data from a similarity matrix
diagBlocks <- function(dims = 20, sqSize = 4) {
  div <- dims %/% sqSize
  finalMatrix<-matrix(0,nrow=dims,ncol=dims)
  index <- 1
  for(k in seq(div)){
    finalMatrix[index:(index + (sqSize-1)),index:(index + (sqSize-1))] <- 1
    index<-index + sqSize
  }
  finalMatrix <- finalMatrix == 1
  finalMatrix
}

```

``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
setwd('./For_HCP')
temp <- list.files(pattern = '*Binary*')
FB <- lapply(temp, read.table)
Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
FB_Means <- rowMeans(Summed)

write.table(file = 'propDMN_all.txt', FB_Means, row.names = F, col.names = F, dec = ".")
```

## Notes:

  - The mixed effects GLM is not that well defined. Fix the dependent to include total possible and actuals.
  - If we stick to the linear model, maybe plot the day and subject coefficients for PCC and PFC too (all in onw plot).
  - The official manuscript will probably have to include things like community size, density of each subject's network (so far, ~0.65), and maybe clustering coefficient?

## Abstract

Valuation effects are consistently observed in medial prefrontal and posterior cingulate cortex (mPFC and PCC). The spatial extent of these effects is mostly indistinguishable from the default mode network (DMN) in existing meta-analyses. However, little is known about how valuation effects fit within the broader functional architecture of mPFC and PCC, or whether that architecture is consistent or idiosyncratic across individuals. Here we complement a meta-analysis with fMRI-based graph theoretic approaches to subdivide mPFC and PCC at the single-subject level. Our results suggest the functional topography of mPFC has substantial variability across individuals. This highlights the potential usefulness of estimating brain effects at the individual level in this region, and points to limitations of aggregative methods such as coordinate-based meta-analysis in determining whether valuation and DMN effects emerge from common or separable brain systems. Our approach shows promise in addressing this issue through future manipulations of valuation.

## Introduction
One of the main goals of human cognitive neuroscience is to be able to prescribe function to brain regions, either in isolation or in their communication with others. Among general regions of the brain, the medial prefrontal cortex (mPFC, located in the midline frontal portion of the brain) has been suggested to subserve the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016). Specifically, this region has been related to a variety of functions, including decision making (Bartra, McGuire, & Kable, 2013), memory encoding (Shacter, Addis, & Buckner, 2007), and default mode deactivation (DMN) (Yeo et al., 2011). While much has been discovered about this area in primates (Barbas & Garcia-Cabezas, 2016), the lack of direct measurements of neuronal activity makes this a tough area to record in humans, one that nowadays relies mostly on functional MRI (fMRI). Unfortunately, the mPFC is especially challenging to image, as the oxygen-related signal recorded by fMRI is contaminated by the oxygen in the sinuses (Logothetis, 2008). In addition, this area is subject to more idiosyncratic cortical folding than any other region (Zilles, Palomero- Gallagher, & Amunts, 2013), thus adding a level of complexity to the generalizable dissection of topographic functional roles within mPFC.

Studies of valuation have consistently shown functional overlap with DMN. Recent meta-analytic work has attempted to distinguish the brain areas belonging to each by examining the locus of peak activity across studies related to the behavioral features mentioned above (Bartra et al., 2013; Acikalin, Gorgolewski, & Poldrack, 2017). While this approach offers valuable information, it is subject to the quality of imaging in each study, as well as their corresponding differences in tasks used to examine choice. In addition, recent findings suggest that the functional topology of the brain is better understood by accounting for organizational idosyncrasies (Braga and Buckner, 2018; Yeo et al., 2018, Gordon et al., 2017, Gratton...).

Given the shortcomings of study-specific and cross-study analyses mentioned above, there is potential value in combining complementary strengths from both approaches. While my lab is primarily interested in the portion of mPFC dedicated to decision making, in order to bypass the heterogeneity in behavioral tasks, it might be best to disentangle the mPFC by focusing first on which of its sub-regions belong to resting-state DMN, and which do not. The advantage lies in that (1) all resting state scans are performed equally (the subject lies in the scanner with their eyes open), and (2) there is a high quality resource of resting state data provided by the Human Connectome Project. Focusing on resting state data has been successful in determining a number of neural phenomena, including disentangling auditory and visual attention areas (Tobyne, Osher, Michalka, & Somers, 2017).

This approach opens an opportunity to examine brain dynamics. For example, a region’s function might depend on its connectivity at any given time with one brain community or another. An ever-growing trend in human neuroimaging has been to apply network statistics to tackle these functional challenges. One great advantage of network science is the ability to characterize connectivity in a way that allows for comparisons among individuals in a meaningful way (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018), thus letting us address the folding idiosyncrasies mentioned above. Therefore, I propose to use some of the statistics that we have learned in class to estimate intrinsic functional subdivisions of the mPFC at the individual subject level. Particularly, I would like to distinguish communities related to DMN from non-DMN, so that we can generate more informed topographic targets for future studies of decision making.

In this study, I try to address my question at 3 levels of granularity: 1) across the literature (meta-analysis), selecting a number of regions of interest (ROI) that show significant overlap and specificity between DMN and decision making; 2) full-brain connectivity of actual fMRI data, using a pre-specified brain atlas; and 3) characterizing the connectivity of surface vertices (small units of function that contain oxygen-dependent neural information across time) for the regions selected in step one. I performed the last two steps at an individual subject level for 3 subjects, hoping to find some commonalities among them. In this way, I attempted to extract functional topographical information from topological network features.

## Methods
**Meta-analysis**
To perform the first step, I used data from a metanalysis that gathered peak brain coordinates of activity from studies of valuation (n = 27 studies) and DMN (n = 77). These are the surviving areas post-statistical thresholding from each study. I analyzed this data by mapping the peak cortical coordinates to an atlas of the human cortical surface (Glasser et al., 2016). This produced a list of standardized parcels that were reported on each study. The advantage of utilizing this atlas was threefold: first, it reduced the number of functional vertices from 60,000 (cortical surface vertices) to 360 (cortical parcels). Second, it standardizes the vertices from the first to the second stage of my study. Finally, it allowed me to project each area on a brain space without much clutter. Since each vertex is embedded with topographical information, and since functional topography is essential to my question, I mostly project my results onto brain space.

I thus generated two undirected, loop-less, weighted graphs in which each vertex was a brain parcel, and edges correspond to the number of times each pair of them co-occurred across studies. Since different decision tasks use different sensory modalities, and since sensory areas get sometimes reported as unrelated peak coordinates in DMN studies, I bootstrapped the co- occurrences across studies and removed edges whose co-occurrences lied below the 90th percentile. Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded. With these graphs set up, I computed the strength and betweenness centrality in order to capture each parcel’s centrality in the valuation and DMN literatures separately.

In order to select of regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, I first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution. Next, I took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus my main target for dissociation).

**Whole Brain Parcellated connectivity**
For the second step, in order to actually quantify the intrinsic connectivity of these ROIs in the brain, I used data from the Human Connectome Project. Specifically, I acquired resting-state fMRI activity from 3 subjects, all of whom have been preprocessed according to industry standards to allow for group-level comparisons (Tobyne et al., 2017). Each data set contained around 1 hour of signals represented as 4800 time points, and each subject contained 60,000 vertices. I parcellated each subject’s brain according to the atlas mentioned above, so that each parcel contained the mean time series from its vertices, and correlated the mean time series among all parcels (Pearson). This produced a weighted adjacency matrix for each subject, where each of the 360 parcels is a vertex, and edges the correlations among all of them. Next, I took the exponential of the correlations, Fisher transformed them (i.e. tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant (FDR < 0.05). Again, I quantified each parcel’s strength and betweenness, averaged them across subjects, and examined whether any of the ROIs showed uniquely high centralities. For this, I performed a permutation comparing the mean strength between the ROIs and the rest of the brain for each participant.

For the main goal of this section, I maximized the strength-based modularity metric as a community detection method (fast-greedy algorithm), so that I could check if all the DMN ROIs from the previous section were affiliated with the same community. While this measure has resolution problems at large and low scales (Fortunato & Hric, 2016), if it does extract a close match to standard DMN networks, it could act as a good method for the final stage of the project (but see Peel, Larremore, and Clauset 2017 for issues with ground-truth). Even though this analysis is mainly geared to confirm that these ROIs are jointly captured, this step also let me examine whether some of the ROIs could be subdivided into DMN and non-DMN regions at this level of granularity.

In order to evaluate the validity of the modularity-based communities, I also clustered the brain by means of spectral partitioning. Specifically, I took the Fiedler vector (eigenvector associated with the second lowest eigenvalue) from each participant’s normalized Laplacian matrix, and divided the brain by the sign of the eigenvector values. This analysis served the additional purpose of more strictly dividing the brain into DMN and non-DMN communities. Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016). Finally, to quantify the agreement of these community methods, I computed both the adjusted rand index and variation of information distance (normalized by the logarithm of the number of vertices, 360 in this case) between them per subject. The adjusted rand index denotes the proportion of vertices that coincide in affiliation across partitions, and compares this score to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions. On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions. While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case. Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016). Importantly, due to having just 3 subjects, I abstained from performing formal statistics on the descriptive measures that I show.

**Within-ROI Connectivity**
For the third stage, I “zoomed in” each subject’s brain by computing the correlation among all of the surface-vertices contained within each ROI across all the ROIs, and applied the same correction as in step two. That means that the vertices became smaller functional brain units that are connected by the same type of edge (i.e. adjusted correlations) as in step two. This time, I only focused on partitioning the brain through modularity and spectral partitioning to see if the ROIs can be subdivided at this finer level of resolution. It is worth noting that while communities across subjects should be similar, the idiosyncrasies explained previously (i.e. cortical folding) should produce noticeable differences as well.

This time I added two new areas to the ROIs: 7m, as this area had unique relevance in DMN when compared to valuation (evidenced by its connectivity strength in DMN and chi- squared permutation in the meta-analysis, see results), and V1, as this visual processing area should not be affiliated with DMN. These regions thus acted as dual reference points, such that the community affiliated with 7m should denote DMN, while V1 indicated non-DMN. As before, I tested the validity of the partitions using the adjusted rand index and normalized variation of information. However, this time I also used the rand index to quantify the community correspondence between subjects. Specifically, I divided each subject’s spectrally- partitioned brain into PCC and mPFC topographical zones (posterior and frontal brain, respectively), and computed the index of each region between subjects. The high cross-subject heterogeneity of cortical folding of mPFC should produce relatively low rand indices, while the more homogeneous PCC should display the opposite pattern. This analysis was meant to tackle the subject-specific limitations discussed above. The final patterns were inspected visually.

## Introduction

This report focuses on the community detection results, but it might be worth adding the meta-analytic steps here eventually as well. In general, the similarity matrices show a representative subsample of subjects (n = 10) to conserve space (unless noted), but the boxplots and formal tests include all subjects. The trends shown by the example subjects generalize to the larger sample anyways.

## Partition Comparison: Full Datasets

Just as reference, the following shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.

``` {r Partition comparison: all brain example, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE}
# Load data
setwd('./Summary/')
temp <- list.files()
subjList <- sapply(temp, substring, first=1, last=6)
Summaries <- lapply(temp, read.csv)
nSubj <- length(Summaries)

plotCommunities(Summaries[[1]], Hemi = "L", Legends = F, type = "FiedlerBinary")

```

This first step just gives an idea of the level of agreement within and between subjects. As a first measure, we use the adjusted rand index (RI) to estimate the level of agreement between partitions. RI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g. clustered together in partition 1, but separately in 2). It is worth noting that the adjusted rand index has well known limitations (Fortunato & Hric, 2016). To compensate for this, we also performed all the upcoming analyses with the variation of information index (VI). This distance measure denotes how much information is gained by adding the second partition (thus, lower values are better), and is known for its robustness. Both RI and VI analyses agreed in the results they yielded, but we only report RI due to its easier interpretability. This first plot shows the distribution of RI values between modularity and spectral partitioning for each subject.

``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
# Cross-method
# Don't worry about plotting, since that's mainly for a general visualization
RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary","Membership"), nSubjects = length(Summaries), subjNames = subjList)

RI_within_plot <- ggplot(data = RI_all_within, aes(Index)) + 
        geom_density(fill = Cols[3]) + 
        xlim(0,1) + 
        labs(x = "Adj. Rand Index") +
        theme_classic()
RI_within_plot
```

The total number of subjects is `r nSubj`. The distribution suggests that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`). The importance of this results lies in that while spectral partitioning forces a bipartition of the network, modularity does not. This adds evidence to the division of these areas into DMN and non-DMN during rest. Due to this high agreement, we focus on results using spectral partitioning, as it paints a clearer picture of the division of interest.

Next, we examine how similar the partitions for PCC and mPFC are across subjects. Qualitative inspection of the brain community topologies shows good alignment for PCC, with a topologically similar mPFC pattern that shifts topographically across subjects. The following similarity matrix shows RIs for every pairwise comparison among all subjects for PCC (lower matrix) and PFC (upper) separately. Each row/column element is a single subject.

\bigskip

``` {r Partition comparison: all 2, fig.align="center", echo=FALSE, message = FALSE}
# Across subjects
# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
posteriorIndx <- Summaries[[1]]$y < 0
tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
# par(mfrow = c(1,2))
# corrplot(RI_all_between,
#          is.corr = F, 
#          method = "color", 
#          tl.pos = "n", 
#          tl.col = "black", 
#          cl.lim = c(0,1),
#          cl.pos = "b",
#          cl.length = 3)
# mtext("Subjects", side = 2, line = -4.5, cex = 1.5)
# mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "b")
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black",
         cl.pos = "n", 
         add = T)

# Let's compare stuff
testPCC <- RI_PCC[lower.tri(RI_PCC)]
testPFC <- RI_PFC[lower.tri(RI_PFC)]
Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.

```

The results match the qualitative observations mentioned above, with overall higher agreement for PCC (paired permutation, p = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`). However, the heterogeneity of mPFC could arise from noise in the signal. As a way to test for subject specificity, we used each subject's session data to compare day 1 vs day 2 clusters, as well as a session-based analysis.

\bigskip
\bigskip

## Partition Comparison: Day 1 vs Day 2

HCP resting state data is separated into 4 runs (2 per day of scanning). This section explores how much agreement there is between partitions computed on each day. The similarity matrix on the left shows the pairwise level of agreement for the overall data among the example subjects, while the right one divides this data into PCC and mPFC.

``` {r Partition comparison: halves, fig.align="center", echo=FALSE, message = FALSE}
# Select 10 subjects from the sample to display
selectSubj <- seq(1,20)

# Load
setwd('./Summary_halves/')
temp <- list.files(pattern = "*_finalSummary.csv")
subjList_halves <- sapply(temp, substring, first=1, last=9)
Summaries_halves <- lapply(temp, read.csv)
Summaries_halves_plot <- Summaries_halves[selectSubj]
subjList_halves_plot <- subjList_halves[selectSubj]

temp <- list.files(pattern = "*_corHalves.csv")
Correlation_halves <- lapply(temp, read.csv, header = F)
Correlation_halves_plot <- Correlation_halves[selectSubj]

# Compare all halves with RI
RI_all_between_halves <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)

# Compare PCC and PFC among all subjects
tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)

# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves, 
         is.corr = F, 
         method = "color",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.8,
         cl.pos = "b",
         cl.length = 3)
corrplot(RI_PCC_halves, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.col = "black", 
         tl.cex = 0.8,
         cl.lim = c(-0.03,1),
         cl.length = 3)
corrplot(RI_PFC_halves, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.8,
         cl.pos = "n", 
         add = T)

```

So far both visualizations show considerable subject specificity, and the regional division agrees with the whole-data similarity matrix. Importantly, this indicates that both PCC and mPFC partitions were more similar within- than between-subjects (e.g. RI values higher for each 2x2 diagonal submatrix than the off-diagonals). Now, how do we check whether the within subject consistency is significantly higher than across subjects? One way is to divide each subject's RI-agreement between days by the RI values with the days from the other subjects. This gives an RI ratio per subject that denotes the relative specificity of their partition. That means, partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.

``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
# Now compare all possible pairs of subjects
# Compare all halves with RI
RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)

# Compare PCC and PFC among all subjects
tempComm_PCC_halves <- lapply(Summaries_halves, "[", i = posteriorIndx, j =)
tempComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)

## Ratio of mean within subject sessions over between subject ones (per-subject)
# Selection of submatrices
template <- diagBlocks(ncol(RI_all_between_halves), 2) 
lowTemplate <- template[lower.tri(template)]

# Overall
# Split the within-subject session RI values per subject
withinSubjVals <- RI_all_between_halves[lower.tri(RI_all_between_halves)][lowTemplate]

# Now grab the columns from the similarity matrix for a subject
betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_halves), by = 2), function(x) RI_all_between_halves[-(x:(x+1)), x:(x+1)])

# And get a vector of the meanWithin / meanBetween ratio per subject
Halves_RIRatios_overall <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})

# PCC
withinSubjVals <- RI_PCC_halves[lower.tri(RI_PCC_halves)][lowTemplate]

# Now grab the columns from the similarity matrix for a subject
betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_halves), by = 2), function(x) RI_PCC_halves[-(x:(x+1)), x:(x+1)])

# And get a vector of the meanWithin / meanBetween ratio per subject
Halves_RIRatios_PCC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})

# PFC
withinSubjVals <- RI_PFC_halves[lower.tri(RI_PFC_halves)][lowTemplate]

# Now grab the columns from the similarity matrix for a subject
betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_halves), by = 2), function(x) RI_PFC_halves[-(x:(x+1)), x:(x+1)])

# And get a vector of the meanWithin / meanBetween ratio per subject
Halves_RIRatios_PFC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})

# Summarize for plotting
Halves_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
                                      RI = c(Halves_RIRatios_PCC, Halves_RIRatios_PFC))

# Stats
Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)

# plot
ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
          geom_boxplot(show.legend = F) +
          scale_fill_manual(values = Cols[seq(2)]) + 
          ylim(0, max(Halves_RIRatios_summary$RI)) +
          geom_hline(yintercept = 1) +
          labs(y = "RI Ratio", x = "") + 
          theme_classic()
```

As expected, we see that while both regions had good specificity (ratios > 1, denoted by the horizontal line), the ratios for PCC were significantly smaller than mPFC for all subjects (permutation, p = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`). However, the denominator is given by a single RI. If these topological patterns are indeed subject-specific for mPFC, these results might generalize to session specific data. This would give us a better estimate of within-subject RI variance to place in the denominator.

\bigskip
\bigskip

## Partition Comparison: Session

Next, each session is evaluated independently. The similarity matrix on the left shows how each session's data corresponded within and between subjects for all ROIs combined, while the one on the right shows PCC and mPFC separately. It is worth noting that each session is ~14 mins long, which is below the stability threshold for fMRI based modularity (Gordon et al., 2017). However, we also perform a sliding window analysis below that encompasses 20 mins of data per window.

``` {r Partition comparison: session similarity matrices, fig.align="center", echo=FALSE, message = FALSE}
# Select 10 subjects from the sample to display
selectSubj <- seq(1,40)

setwd('./Summary_sess/')
temp <- list.files()
subjList_sess <- sapply(temp, substring, first=1, last=9)
Summaries_sess <- lapply(temp, read.csv)
subjList_sess_plot <- subjList_sess[selectSubj]
Summaries_sess_plot <- Summaries_sess[selectSubj]

# Across subjects (just for plotting)
RI_all_between_sess <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)

# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.pos = "b",
         cl.length = 3)
corrplot(RI_PCC_sess, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         cl.lim = c(-0.03,1),
         cl.length = 3)
corrplot(RI_PFC_sess, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         add = T)

# Now run comparisons among all subjects
RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)

## Let's compare stuff (not accounting for complex interdependencies in the observations)
## Overall differences in mean RI between PCC and mPFC
lowPCC_sess <- RI_PCC_sess[lower.tri(RI_PCC_sess)]
lowPFC_sess <- RI_PFC_sess[lower.tri(RI_PFC_sess)]
Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T)
Sess_PCCvPFC_ES <- cohenD(lowPCC_sess, lowPFC_sess) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.

## Differences in RI values for sessions within vs between subjects (all subjects pooled together)

# create a selection matrix containing all within-subject session comparisons
template <- diagBlocks(ncol(RI_all_between_sess), 4) 
lowTemplate <- template[lower.tri(template)]

# Overall
# First list element is the within subject values, second is the between subject values
lowRISess <- RI_all_between_sess[lower.tri(RI_all_between_sess)]
Sess_overallComparison <- list(lowRISess[lowTemplate],
                               lowRISess[!lowTemplate])
Sess_overallComparison[[3]] <- permute(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
Sess_overallComparison[[4]] <- cohenD(Sess_overallComparison[[1]], Sess_overallComparison[[2]])

# PCC 
Sess_PCCComparison <- list(lowPCC_sess[lowTemplate],
                           lowPCC_sess[!lowTemplate])
Sess_PCCComparison[[3]] <- permute(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
Sess_PCCComparison[[4]] <- cohenD(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])

# mPFC
Sess_PFCComparison <- list(lowPFC_sess[lowTemplate],
                           lowPFC_sess[!lowTemplate])
Sess_PFCComparison[[3]] <- permute(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
Sess_PFCComparison[[4]] <- cohenD(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])

```

As before, we see higher agreement levels within subjects (with some exceptions). Simple permutation comparisons confirmed this intuition for the all-ROI (p = `r Sess_overallComparison[[3]]$Pval`; Cohen's D `r round(Sess_overallComparison[[4]], digits = 2)`), PCC (p = `r Sess_PCCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PCCComparison[[4]], digits = 2)`), and mPFC (p = `r Sess_PFCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PFCComparison[[4]], digits = 2)`) divisions. In order to quantify the consistency and specificity of these partitions, we again applied the RI ratio index, but this time using the mean RI among all of a subject's sessions in the denominator. The following plot shows the results for PCC and mPFC separately.

``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
## Brain storming:
## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
## Perhaps a more interresting idea would be to generate an index of variance within/between subject
## These are just attempts at that are not perfect:

# 1) Ratio of mean within subject sessions over between subject ones (per-subject)
# Overall
# Split the within-subject session RI values per subject
temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
withinSubjVals <- split(Sess_overallComparison[[1]], temp)

# Now grab the columns from the similarity matrix for a subject
betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_sess), by = 4), function(x) RI_all_between_sess[-(x:(x+3)), x:(x+3)])

# And get a vector of the meanWithin / meanBetween ratio per subject
Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})

# PCC
temp <- ceiling(seq_along(Sess_PCCComparison[[1]])/6)
withinSubjVals <- split(Sess_PCCComparison[[1]], temp)

# Now grab the columns from the similarity matrix for a subject
betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_sess), by = 4), function(x) RI_PCC_sess[-(x:(x+3)), x:(x+3)])

# And get a vector of the meanWithin / meanBetween ratio per subject
Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})

# PFC
temp <- ceiling(seq_along(Sess_PFCComparison[[1]])/6)
withinSubjVals <- split(Sess_PFCComparison[[1]], temp)

# Now grab the columns from the similarity matrix for a subject
betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_sess), by = 4), function(x) RI_PFC_sess[-(x:(x+3)), x:(x+3)])

# And get a vector of the meanWithin / meanBetween ratio per subject
Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})

# Summarize for plotting
Sess_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
                                    RI = c(Sess_RIRatios_PCC, Sess_RIRatios_PFC))

# Stats
Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)

ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
          geom_boxplot(show.legend = F) +
          scale_fill_manual(values = Cols[seq(2)]) + 
          ylim(0, max(Sess_RIRatios_summary$RI)) +
          geom_hline(yintercept = 1) +
          labs(y = "RI Ratio", x = "") + 
          theme_classic()
```

We can see again that the ratios for mPFC were higher than those of PCC (permutation, p = `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were above 1. This suggests that the PCC is well aligned across subjects (as mentioned before), while mPFC is consistent within subject, but quite different from other subjects.

Another way to determine the heterogeneity of these results is based on Kragel et al. (2018), who quantified the dissimilarity of brain patterns for behavioral domain, subdomain, and study (or how generalizeable the patterns are at each hierarchical level). In our case, for `r nSubj` subjects `r nSubj*3` matrices are created (`r nSubj*2` for daily comparisons, `r nSubj` for within subject comparisons). Each matrix is binarized to compare a subject's level of similarity within their daily data vs across every other subject's sessions. The `r nSubj*3` matrices are vectorized and used as predictors in a GLM with a quasibinomial distribution, where the dependent data is the full vectorized RI similarity matrix. This is a simplified version of a fully-dimensional model that considers all possible comparisons at the session level, which would otherwise have S + (S x (S-1)/2) parameters (with S = session). For this model, a significantly negative subject predictor implies that the odds of the partitions being similar across subjects are much lower than those within each subject (across sessions). Thus, subject specificity would dictate that all subject-level coefficients should be significant and negative.

``` {r Partition comparison: session linear model, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
# 2) Based on Kragel et al, 2018
# First, create a disimilarity matrix
dissimMatrix_all <- RI_all_between_sess
dissimMatrix_lower <- dissimMatrix_all[lower.tri(dissimMatrix_all)]

# Create selection matrices for half- and subject-level comparisons
coeffList <- list()
i <- 1
for (j in c(2,4)) {
  for (x in seq(1, ncol(dissimMatrix_all), by = j)) {
    tempMatrix <- matrix(0, ncol(dissimMatrix_all), nrow(dissimMatrix_all))
    tempMatrix[-(x:(x+(j-1))), (x:(x+(j-1)))] <- 1
    tempMatrix[(x:(x+(j-1))), -(x:(x+(j-1)))] <- 1
    coeffList[[i]] <- tempMatrix
    i <- i + 1
  }
}

# Turn into a vector based on the lower triangle
coeffList_lower <- lapply(coeffList, function(data) {as.factor(data[lower.tri(data)])})
coeffList <- as.data.frame(do.call(cbind, coeffList_lower))
colnames(coeffList) <- c(subjList_halves, subjList)

# Do a linear model with each 
#testModel <- lm(dissimMatrix_lower ~ ., coeffList)

# Logistic maybe better, given the RI bounds
# That said, the adjusted RI can sometimes be negative by a small margin (< 0.01), so we take the absolute values
tempY <- abs(RI_all_between_sess)
tempY <- tempY[lower.tri(tempY)]
specificityModel <- glm(tempY ~ ., coeffList, family = "quasibinomial")
tempSummary <- summary(specificityModel)

# Diagnostics: rank (full rank = nSubj * 3) and VIF (< 10 = better)
specificityModel_diagnostics <- list(Rank = rankMatrix(coeffList),
                                     Vif = VIF(specificityModel),
                                     Rsquared = 1 - tempSummary$deviance/tempSummary$null.deviance)

# Create a summary dataframe 
specificityModel_summary <- data.frame(Type = c(rep("Day", nSubj*2), rep("Subject", nSubj)),
                                       Coefficient = coef(specificityModel)[2:(nSubj*3+1)],
                                       Pvals = tempSummary$coefficients[2:(nSubj*3+1), 4])

# adjust pvals and get a percentage of significant coefficients for day and subject
specificityModel_summary$Pvals <- p.adjust(specificityModel_summary$Pvals, method = "BY")
prcntDay <- sum(specificityModel_summary$Pvals[specificityModel_summary$Type == "Day"] < 0.05) / (nSubj*2)
prcntSubj <- sum(specificityModel_summary$Pvals[specificityModel_summary$Type == "Subject"] < 0.05) / (nSubj)

# plot
specificityModel_plot <- ggplot(data = specificityModel_summary, aes(Type, Coefficient, fill = Type)) + 
  geom_hline(yintercept = 0, alpha = 0.7) + 
  geom_boxplot(show.legend = F) +
  theme_classic()
specificityModel_plot

```

The plot above shows the estimated coefficients from the linear model for day and subjects (R-squared for the model = `r round(specificityModel_diagnostics$Rsquared, digits = 2)`). As we would expect given the subject specificity of these partitions, `r round(prcntSubj, digits = 2)` percent of the subject coefficients were significant (a one sample t-test confirmed this notion). Conversely, `r round(prcntDay, digits = 2)` of the coefficients for daily comparisons were significant (non-significant t-test). These results suggest that the partitions were better explained as being subject-specific. That said, the current version of the model is fit with the data from all ROIs, and running it separately for PCC and mPFC might be fruitful in the future.

In order to diagnose the model, we checked the independency of observations through the rank of the design matrix, which was `r specificityModel_diagnostics$Rank[1]` (full rank for `r nSubj` subjects should be `r ncol(coeffList)`) for the present analysis. Further diagnostics included a qqnorm check on the model residuals (result: mostly normal), and variance inflation factors (VIF, also used by Kragel et al., 2018). The VIF is a measure of colinearity of the regressors, and it "shows the degree to which variance in each parameter estimate is increased due to partial colinearity with linear combinations of other regressors". While low (<2) VIF values are preferable, shared variance is unavoidable given the hierarchical structure of the model. Regardless, Kragel et al. take it as a good sign that their VIF are finite (?), which is also the case here (mean = `r mean(specificityModel_diagnostics$Vif)`). That said, these are above 10, which is a standard upper threshold (potential downside). *We will have to reconsider this portion.*

\bigskip
\bigskip

## Stability per subject

It is also worth considering how stable these measures are, so we performed a sliding window analysis  per subject (20 min windows shifting at ~1 min throughout the whole ~ 1hr time series). The first two plots show how well each window's clustering agreed with the partition derived from the whole data (in RIs, left), as well as how variable (in standard deviations) this index was throughout each time series (right).

\bigskip

``` {r Stability per subject: Overall, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE}
# Load files
setwd('./Sliding_window/')
temp <- list.files(pattern = '*Comparisons.csv')
SC <- lapply(temp, read.csv2)
temp <- list.files(pattern = '*Values.csv')
SVals <- lapply(temp, read.csv2)

# Put together a data frame to plot Fiedler vec x proprtion DMN
allSummaries <- do.call(rbind, Summaries)
allSummaries$SubjID <- rep(subjList, each = nrow(Summaries[[1]]))

# Do a mixed effects GLM (binomial) to estimate the relationship between Fiedler vec and propDMN
SC_FVvPDMN_model <- glmer(slidePropDMN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
SC_FVvPDMN_modelSummary <- summary(SC_FVvPDMN_model)
allSummaries$FittedVals <- fitted(SC_FVvPDMN_model)

# Overall
SC_all <- do.call(rbind, SC)
SC_plot <- ggplot(data = SC_all)
SC_plot <- SC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = "slategray4",alpha = 0.3, show.legend = F) +
              geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
              ylim(0,1) + 
              theme(text = element_text(size=35)) +
              labs(y = "Adj. Rand Index") +
              theme_classic()

# Mean RI across windows per subject
SC_summary <- aggregate(SC_all$Index, by = list(SC_all$SubjID), FUN = mean)
SC_summary$SD <- aggregate(SC_all$Index, by = list(SC_all$SubjID), FUN = sd)$x
colnames(SC_summary) <- list("SubjID", "RI", "SD")
SC_sd_plot <- ggplot(data = SC_summary, aes(x=SD)) + 
  geom_density(color = "black", fill = Cols[2], bins=50) + 
  xlim(0,1) +
  labs(x = "SD") +
  theme(text = element_text(size=35)) +
  theme_classic()

# Fiedler Vector x proportion of times a vertex was affiliated with DMN
SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
  #geom_point(aes(FiedlerVec, slidePropDMN, fill = SubjID), show.legend = F, alpha = 0.05, pch = 21, color = "black") + 
  geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
  theme_classic()

grid.arrange(SC_plot, SC_sd_plot, ncol = 2)

```

\bigskip

While some subjects show considerable variability, the overall trend is of fair stability. An interesting feature of spectral partitioning is that the Fiedler vector, which provides signed values to divide a network into positive and negative communities, was tightly related to the proportion of times any given cortical vertex was affiliated with the DMN throughout the fMRI sessions. Meaning, the higher the absolute value in the Fiedler vector for a given vertex, the more persistent its relationship was with its corresponding community in time. The following plot shows this relationship for each subject (gray smoothed lines), as well as the fitted values from a logistic mixed effects model (black line; model: prop. DMN ~ Fiedler vector, subjects as random intercepts; beta = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, p < 0.001).

\bigskip

``` {r Stability per subject: Fiedler vector vs prop. DMN plot, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
SC_FVvPDMN_plot
```

\bigskip

With the exception of some noisy subjects, the sigmoidal functions show a tight relationship between the two. This brings attention to the possibility of using the Fiedler vector as a surrogate for stability, thus reducing the computational needs for future analyses.

While these results show promise, so far we have only looked at stability for all the ROIs. The next three plots show similar data, but for PCC and mPFC separately. The middle plot compares the subject-wise mean RI for PCC and mPFC. While mPFC shows an overall significantly lower level of agreement with the overall partition, the variance throughout the time series is small.

``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE}
## Check stability for PCC and mPFC separately
# Get the sliding values for PCC and PFC separately
tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)

SC_PCC <- data.frame()
SC_PFC <- data.frame()

for (subj in seq(nSubj)) {
  tempPCC <- numeric()
  tempPFC <- numeric()
  nWins <- ncol(tempSW_PCC[[subj]])
  for (Win in seq(nWins)) {
    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][,Win], adjust = T)
    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][,Win], adjust = T)
  }
  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
                      Window = seq(nWins),
                      Index = tempPCC)
  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
                      Window = seq(nWins),
                      Index = tempPFC)
  SC_PCC <- rbind(SC_PCC, dfPCC)
  SC_PFC <- rbind(SC_PFC, dfPFC)
}

SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
SC_PCC_summary$Region <- rep("PCC", nSubj)
SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
SC_PFC_summary$Region <- rep("mPFC", nSubj)
SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
rm(SC_PCC_summary, SC_PFC_summary)

# plots
SC_PCCPFC_plot <- ggplot(data = SC_PCC)
SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
  geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
  ylim(0,1) + 
  labs(y = "Adj. Rand Index") +
  theme(text = element_text(size=35)) +
  geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
  geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
  theme_classic()

SC_PCCPFC_mean_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=as.factor(Region), y=Index, fill = as.factor(Region))) + 
  geom_boxplot(show.legend = F) + 
  scale_fill_manual(values = Cols[seq(2)]) +
  ylim(0,1) +
  labs(x = "", y = "") +
  theme(text = element_text(size=35), axis.text.y = element_text(size=40)) +
  theme_classic()

SC_PCCPFC_sd_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=SD, fill = as.factor(Region))) + 
  scale_fill_manual(values = Cols[seq(2)]) +
  geom_density(color = "black", alpha = 0.7, show.legend = F) + 
  xlim(0,1) +
  labs(x = "SD") +
  theme(text = element_text(size=35)) +
  theme_classic()

SW_PCCvPFC_permuteTest <- permute(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"], paired = T)
SW_PCCvPFC_ES <- cohenD(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"])

grid.arrange(SC_PCCPFC_plot, SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 3)
```

\bigskip

This suggests that, while the agreement of each window with the overall time series was stable for both PCC and mPFC (low SD, right plot), the overall agreement of mPFC is lower (paired permutation, p = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`). This result could be due to signal degeneration in mPFC (that said, it is worth noting that the topological patterns remain mostly the same for both PCC and mPFC throughout the SW analysis). To account for this, we computed the coefficient of variation for each vertex in each subject's minimally preprocessed fMRI data (i.e. mean of each vertex's time points over their standard deviation). The next plot shows the pooled subject-wise mean SNR for PCC and mPFC vertices, and indicates that the SNR is lower for mPFC than PCC, which could negatively affect our results.

\bigskip

``` {r Stability per subject: SNR Comparison, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
# Flexibility vs SNR
# Are vertices with lower SNR switching communities more often?
SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))

# Compare SNR between PCC and mPFC per subject
SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval)
SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff))
prcntSig <- (sum(SNR_PCCvsPFC_perm < 0.05) / nSubj) * 100

# Get the mean SNR for each region and the effect size for the comparison 
SNR_meanPCC <- sapply(tempComm_PCC, function(data) mean(data$varCoeff))
SNR_meanPFC <- sapply(tempComm_PFC, function(data) mean(data$varCoeff))
SNR_meanComp <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
                           SNR = c(SNR_meanPCC, SNR_meanPFC))

# Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
snrmeanComp_plot <- ggplot(data = SNR_meanComp, aes(Region, SNR, fill = Region)) +
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) +
  labs(x = "", y = "SNR") +
  theme(text = element_text(size=35)) +
  theme_classic()
snrmeanComp_plot
```

\bigskip

To formally examine this, for each subject we compared the SNR values of all vertices between PCC and mPFC (`r nSubj` permutation tests). About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected; mean Cohen's D = `r mean(SNR_PCCvsPFC_ES)`). In addition, we found that the degree of signal to noise for each vertex showed significant negative correlations with flexibility, a graph-theoretic index that measures the proportion of times a node in a network changed affiliation across partitions (mean correlation across subjects = `r round(mean(SNR_vs_Flex), digits = 2)`). This suggests that, for any given subject, vertices with low SNR resulted in variable participation between the communities, and could explain why mPFC had lower stability levels.

To further quantify the potential effect of noise in our results, we computed the variance explained by the mean time series of the DMN community on each DMN vertex separately through a simple linear model. Interestingly, there is a strong linear relationship between the Fiedler vector (the divisive vector from spectral partitioning) and the R-squared values (these match perfectly on the brain when inspected qualitatively). The following plot shows this relationship, with each line denoting a subject.

\bigskip

``` {r Stability per subject 4, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE}
setwd('./Variance/')
temp <- list.files()
Variance <- lapply(temp, read.csv)

### temporary fix to add z coordinates (these will be computed during the initial analysis from now on)
for (i in seq(nSubj)) {
  tempIndex <- Summaries[[i]]$Vertex %in% Variance[[i]]$Vertex
  Variance[[i]]$SubjID <- rep(subjList[i], nrow(Variance[[i]]))
  Variance[[i]]$tempX <- Summaries[[i]]$x[tempIndex]
  Variance[[i]]$tempZ <- Summaries[[i]]$z[tempIndex]
  Variance[[i]]$FiedlerVec <- Summaries[[i]]$FiedlerVec[tempIndex]
  Variance[[i]]$Flexibility <- Summaries[[i]]$slideFlexibility[tempIndex]
  Variance[[i]]$propDMN <- Summaries[[i]]$slidePropDMN[tempIndex]
  Variance[[i]]$varCoeff <- Summaries[[i]]$varCoeff[tempIndex]
  Variance[[i]]$Region <- ifelse(Variance[[i]]$tempY < 0, "PCC", "mPFC")
}

# plot
# let's put everyone's data together first
allVariance <- do.call(rbind, Variance)

# get the mean and SE of the R-squared values per subject/region
allVariance_sumarized <- aggregate(allVariance$Rsquared ~ allVariance$SubjID + allVariance$Region, FUN = 'mean')
colnames(allVariance_sumarized) <- list("SubjID", "Region", "meanRsquared")
allVariance_sumarized$SEM <- aggregate(allVariance$Rsquared ~ allVariance$SubjID + allVariance$Region, FUN = function(data) {sd(data)/sqrt(length(data))})[ , 3]

# There is a strong linear relationship between the Fiedler vector and the R-squared values
# These match perfectly on the brain when inspected qualitatively
v1 <- qplot(data = allVariance, FiedlerVec, Rsquared, color = SubjID, fill = SubjID, geom = "smooth", show.legend = F) + labs(x = "Fiedler Vector Values", y = "R-Squared Values") + theme_classic()

# The lower the R-squared, the more likely it is for nodes to change affiliation throughout time
v2 <- qplot(data = allVariance, Rsquared, Flexibility, color = SubjID, fill = SubjID, geom = "smooth") + theme_classic()

# And of course (given the relationship with the Fiedler vector), there's a sigmoidal relationship between R-squared vals and proportion of DMN affiliation
# only showing the upper side of the sigmoid here, as these values are restricted to the DMN community
v3 <- qplot(data = allVariance, Rsquared, propDMN, color = SubjID, fill = SubjID, geom = "smooth") + theme_classic()

# Finally, it's worth comparing the R-squared values between PCC and mPFC
# The intuition is that the variance explained by the community might be lower for mPFC given its noise
# And the answer is: mPFC yields significantly lower R-squares per subject and overall, as expected.
# To formally compare this (and given the binomial distribution of R-squares in mPFC), I report the Cohen's D per subject for PCC vs mPFC
v4 <- ggplot(data = allVariance_sumarized, aes(x = SubjID, y = meanRsquared, group = Region, color = Region)) +
  geom_point(show.legend = F) +
  geom_line(show.legend = F) +
  geom_errorbar(aes(ymin = meanRsquared - SEM, ymax = meanRsquared + SEM)) +
  scale_color_manual(values = Cols[seq(2)]) +
  ylim(0,0.5) +
  labs(x = "Subject", y = "Mean R-squared") +
  theme_classic() +
  theme(axis.text.x = element_blank()) 
v5 <- qplot(data = allVariance, Region, Rsquared, fill = Region, geom = "boxplot") + theme_classic()
Rsq_PCCvsPFC_Wilcox <- sapply(Variance, function(data) {wilcox.test(data$Rsquared[data$Region == "PCC"], data$Rsquared[data$Region == "mPFC"])$p.value})
Rsq_PCCvsPFC_Wilcox <- p.adjust(Rsq_PCCvsPFC_Wilcox, method = "BY")
prcntSig <- (sum(Rsq_PCCvsPFC_Wilcox < 0.05) / nSubj) * 100
Rsq_PCCvsPFC_ES <- sapply(Variance, function(data) {cohenD(data$Rsquared[data$Region == "PCC"], data$Rsquared[data$Region == "mPFC"])})

# This begs the question of a "gradient of noise" along the z-axis on mPFC
# Not really, but the coefficient of variation derived from minimally preprocessed data does show a strong trend
# Namely, the more ventral, the lower the SNR
# v6 <- ggplot(data = allVariance, aes(Rsquared, tempZ, fill = Region)) +
#         geom_point(color = "black", pch = 21, alpha = 0.1) + 
#         scale_fill_manual(values = Cols[seq(2)]) +
#         theme_classic()
# v7 <- ggplot(data = allVariance, aes(varCoeff, tempZ, fill = Region)) +
#         geom_point(color = "black", pch = 21) + 
#         scale_fill_manual(values = Cols[seq(2)]) +
#         theme_classic()

v1

```

\bigskip

Next, we compared the R-squared values for PCC and mPFC separately per subject. The following plot shows that for each subject, R-squared values tend to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had p values < 0.001). This is also true for Fiedler vector values, but to a lesser extent. These differences had moderately high effect sizes (mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`). These results suggest that overall, vertices belonging to the mPFC DMN community are less in synchrony with the activity of the community as a whole than those in PCC.

\bigskip

``` {r Stability per subject 5, fig.align="center", fig.width=6, fig.height=4, echo=FALSE, message = FALSE}
v4
```

\bigskip

This begs the question of whether there is a "gradient of noise" along the z-axis on mPFC (vmPFC explaining less variance?). The plots below show the density of R-squared (left) and SNR (right) values for every mPFC vertices across all participants. The R-squared values have no clear relationship with the ventral-dorsal axis (with some low values grouped in vmPFC). However, the coefficient of variation derived from minimally preprocessed data does show a trend (namely, the more ventral, the lower the SNR). This is notable because the R-squared values are estimated from data with added noise reduction steps. These results contextualize the degree of synchrony of mPFC vertices in terms of potential noise. While still an important factor, it is unlikely that our stability results could be due mostly to highly structured mPFC noise.

\bigskip

``` {r Stability per subject 6, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE}
# grid.arrange(v6, v7, ncol = 2)
par(mfrow = c(1,2))
smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
              xlab = "R-squared Value",
              ylab = "Z-Coordinate")

smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
              xlab = "Coefficient of Variation (SNR)",
              ylab = "")
```

\bigskip

\bigskip

## Correlation vs community detection in mPFC

Next, it is worth examining what we gain from using graph theoretic approaches over a simple seed-based functional connectivity analysis from PCC. For this purpose, we computed the mean time series of all the vertices contained in the DMN PCC ROI from Yeo et al. (2011) parcellation, and correlated it with the activity of every mPFC vertex from our ROIs. The similarity matrix below shows Day 1 vs Day 2 comparisons for mPFC partitions generated with seed-based correlations (top-left quadrant) vs community detection (bottom-right) across all participants, as well as how much did these methods agree with each other (not much, but enough, which is good). The important features here are that both approaches are very consistent, but community detection seems slightly more stable across days (quantified in the next section). Also, the cross-method agreement is fair, meaning that both approaches are showing similar topological features, but that these are more stable using graph theoretic approaches.

``` {r Correlation vs community detection: plot, fig.align="center", echo=FALSE, message = FALSE}
## Between halves analysis for correlation and communities (mPFC only)
tempComm_PFC_halves_plot <- lapply(seq_along(tempComm_PFC_halves_plot), function(x) cbind(tempComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- tempComm_PFC_halves_plot
D2 <- lapply(tempComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1,D2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
corrplot(allHalfCombs, 
         title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
         method = "color", 
         tl.col = "black",
         tl.cex = 0.6,
         cl.pos = "b",
         mar = c(0,0,3,0))
segments(0.5,0.5,0.5,40.5, lwd = 2)
segments(0.5,0.5,40.5,0.5, lwd = 2)
segments(0.5,40.5,40.5,40.5, lwd = 2)
segments(40.5,0.5,40.5,40.5, lwd = 2)
segments(0.5,20.5,40.5,20.5, lwd = 2)
segments(20.5,0.5,20.5,40.5, lwd = 2)

```

``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE}
# Compare correlation with community approach on mPFC
# tempComm_PFC_halves <- lapply(seq_along(tempComm_PFC_halves), function(x) cbind(tempComm_PFC_halves[[x]], Correlation_halves[[x]]))
# tempComm <- sapply(seq(1, 20, by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
# tempCor <- sapply(seq(1, 20, by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
# prepostComp <- data.frame(Community = tempComm, Correlation = tempCor)
# prepostComp <- melt(prepostComp)
# colnames(prepostComp) <- c("Approach", "Correlation")
# prepostComp_test <- permute(tempComm, tempCor, paired = T)
# 
# 
# ## Between halves analysis for correlation and communities (mPFC only)
# D1 <- tempComm_PFC_halves
# D2 <- lapply(tempComm_PFC_halves, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
# Data <- c(D1,D2)
# allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = length(Data), Index = "Cor", subjNames = c(subjList_halves, subjList_halves))
#

# Compare correlation with community approach on mPFC
tempComm <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
tempCor <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
tempBoth <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Both = tempBoth)
prepostComp <- melt(prepostComp)
colnames(prepostComp) <- c("Approach", "Correlation")
prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
prepostComp_ES <- cohenD(tempComm, tempCor)
```

\bigskip

The previous plot shows the inter-methodological correspondence with an example subjects. The final plot shows the spatial correlation between days for each method across all participants. Community reflects the data from the lower right quadrant, correlation belongs to the upper left, and both is the cross-approach correspondence (top right). Community detection had a high and significantly higher RI across days than a simple correlation (permutation p-value < 0.001; Cohen's D = `r round(prepostComp_ES, digits = 2)`). This is important because it shows that we can derive very stable topological features using community detection, even though mPFC has relatively low signal to noise ratio. Low intra-subject and high inter-subject variability of DMN partitions is in agreement with previous work (Laumann 2015; Gordon et al., 2017; Braga & Buckner, 2017; Kong...Yeo, 2018). Graph-based community detection might thus be a better way to detect stable functional topologies, since high stability throughout days is a consistent feature of DMN topologies.

``` {r Correlation vs community detection: comparison plot, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
# Day 1 vs Day 2 Spatial Correlation Comparison
prepostComp_plot <- ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
  geom_boxplot(show.legend = F) +
  labs(x = "", y = "Correlation Coefficient") +
  ylim(0,1) +
  theme(text = element_text(size=35)) +
  theme_classic()
prepostComp_plot
```

``` {r 16.1.1., fig.align="center", fig.width=6, fig.height=4, echo=FALSE, message = FALSE}

```

## Structural correspondence

``` {r Structural correspondence, fig.align="center", echo=FALSE, message = FALSE}
# Mean of correlations
meanMyelin <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
meanCurv <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
meanThick <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))

# SD 
sdMyelin <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
sdCurv <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
sdThick <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
```

Finally, we examined whether these topological features were defined by the structure of the brain by correlating each subject's Fiedler vector with their structural MRI data. We found that the Fiedler vector is uncorrelated with myelin density (mean correlation = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean correlation = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean correlation = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`). While these results suggest that each subject's functional topology is mostly independent of brain structure, we will perform more detailed analyses of this in the future (i.e. are there any outstanding structural features in a subject that match their unique topology?).

### 2018-08-15 Analyze_summaries.R

@@ -1,0 +1,1327 @@
+###-------- Libraries and functions ---------------
+Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere
+
+# In case I want to visualize stuff in the brain
+labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[,2:6]
+labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))
+
+library(igraph)
+#library(tidyverse)
+library(ggnetwork)
+library(ggplot2)
+library(gridExtra)
+library(data.table)
+library(plyr)
+library(mcclust)
+library(lme4)
+library(parallel)
+library(corrplot)
+
+
+## Cohen's D for 2 groups
+# for a more flexible approach, make the data input to be a list with entries for n groups, 
+# then do length(list) for the number of groups. 
+cohenD <- function(group1 = 1, group2 = 2){
+  
+  # means
+  mean1 <- mean(group1, na.rm = T)
+  mean2 <- mean(group2, na.rm = T)
+  
+  # variance
+  var1 <- var(group1, na.rm = T)
+  var2 <- var(group2, na.rm = T)
+  
+  # equation
+  out <- (mean1 - mean2) / sqrt((var1 + var2)/2)
+  
+  return(out)
+  
+}
+
+## log-log degree distribution
+logDegreeDist <- function(Graph = padjMat) {
+  
+  tempD <- degree(Graph)
+  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
+  d <- (0:(max(tempD)-1))
+  ind <- (tempDD!=0)
+  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
+       xlab = "Log-Degree", ylab = "Log-Intensity",  
+       main = "Log-Log Degree Distribution")
+  
+}
+
+
+## Create correlation matrix between vertices of 2 ROIs
+# Requires labeled time series matrix
+vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
+  
+  # extract the time series from the ROIs
+  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
+  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
[…]

### 2018-08-15 HCP_labelConn.sh

@@ -1,0 +1,60 @@
+#!bin/bash/
+
+# This is based on Sean's suggestions (see his NeuroImage paper, 2017)
+# First, grab an MGSR dtseries.nii data file from an HCP subject (from SCC). This file contains the residuals from regressing the mean greyordinate value from the series.
+# Second, get the mean of the timeseries for a given parcel using 'Q1-Q6_RelatedParcellation210.CorticalAreas_dil_Colors.32k_fs_LR.dlabel.nii' from Glasser's paper
+# Note: using -cifti-convert -to-text on the resulting file will generate a csv with the mean time series (column) for each parcel (row, N=360).
+#       This can be used to sed-vertex correlations, once the vertex index for columns have been sorted out
+# Third, correlate the parcellated ptseries file. This will create a 360x360 pconn file.
+# Fourth, convert the pconn file to text (as in the note) to get the 360x360 correlation matrix as a csv
+# The advantage here is that the RS are well preprocessed, allowing us to bypass the merging of the 4 RS scans.
+
+dataName=$1
+
+# Parcellate
+for dataFile in *${dataName} ; do
+
+  filename=$(echo $dataFile | cut -f 1 -d '_')
+
+  echo "Working on ${filename}"
+
+  # wb_command -cifti-parcellate ${filename}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii \
+  #                               Q1-Q6_RelatedParcellation210.CorticalAreas_dil_Colors.32k_fs_LR.dlabel.nii \
+  #                               COLUMN ${filename}.ptseries.nii -method MEAN
+
+  echo "Parcellating time series"
+  wb_command -cifti-parcellate ${dataFile} \
+                                Q1-Q6_RelatedParcellation210.CorticalAreas_dil_Colors.32k_fs_LR.dlabel.nii \
+                                COLUMN ${filename}.ptseries.nii -method MEAN
+
+  # Get each parcel's mean timeseries
+  wb_command -cifti-convert -to-text ${filename}.ptseries.nii ${filename}_ptSeries.txt
+
+  # Get the overall time series
+  echo "Storing the whole time series"
+  wb_command -cifti-convert -to-text ${dataFile} ${filename}_timeSeries.csv
+
+done
+
+# series=$(expr $series + 1)
+
+# done
+
+
+# z-score
+
+# average across participants
+
+
+##------ Notes (before 2/19/18)
+
[…]

### 2018-08-15 batch_makeIM.sh

@@ -1,0 +1,396 @@
+#!/bin/bash -l
+
+# I know that using a Python sub-script for such an easy task was dumb, but it
+# was the fastest and most comfortable option at the time.
+# IMPORTANT: Make sure you run vertexLabel.m on the HCP annotation file (FreeSurfer only) before running this script. Step 5 depends on the output.
+
+# load modules within SCC
+module load afni/2017.01.29.1818_openmp
+module load fsl
+module load freesurfer/6.0
+module load connectomewb/1.2.3
+module list
+
+# job name
+#$ -N I_POS
+
+echo "TRANSFORMING METANALYSIS COORDINATES INTO CORTICAL PARCELS (Glasser et al., 2016)"
+
+# file name will become a directory
+# echo "Enter file name (without .txt): "
+# read filename
+filename="I_POS"
+export filename
+echo $filename
+
+
+# create dirs, including those to make FS commands compatible
+# important for step 7 and annot2label transformation
+mkdir -p $PWD/$filename/results
+mkdir -p $PWD/Glasser/surf
+mkdir -p $PWD/Glasser/label/lh
+mkdir -p $PWD/Glasser/label/rh
+
+if [ ! -f ./Glasser/label/lh.HCP_MMP1p0.annot ] ; then
+    cp *.HCP_MMP1p0.annot ./Glasser/label # make sure to do it for both hemis, I'm using Sean's HCP annotation file
+    cp $SUBJECTS_DIR/fsaverage/surf/*h.white ./Glasser/surf/
+fi
+if [ "$(ls -A ./Glasser/label/lh)" ] ; then
+    echo
+    echo "HCP labels exist..."
+    echo
+else
+    echo
+    echo "Creating HCP label files from HCP annot..."
+    echo
+     # --border <fname>.gii creates a single overlay of binary borders
+    mri_annotation2label --subject Glasser --hemi lh --sd $PWD --annotation HCP_MMP1p0 --outdir ./Glasser/label/lh
+    mri_annotation2label --subject Glasser --hemi rh --sd $PWD --annotation HCP_MMP1p0 --outdir ./Glasser/label/rh
+fi
+
+# create study-specific text files in python
+#python readTxt.py
+
+# copy MNI template to new dir and cd to it to create spheres
[…]

### 2018-08-15 chiPerVertex.sh

@@ -1,0 +1,57 @@
+#!/bin/bash
+
+# This script takes the summary of the permutation analysis, and assigns the corresponding (signed) chi squared value that came from the comparison between conditions.
+
+# loop through all summary files
+for comparison in *summary.csv ; do
+
+    fname=$(echo $comparison | cut -d '_' -f 1)
+    touch ${fname}_lh_overlay.csv
+    touch ${fname}_rh_overlay.csv
+
+    echo "Working on ${fname} lh..."
+
+    # Go through each label from Glasser and insert its chi2 value on the respective vertex
+    # Change the label system if needed (i.e. DMN-space analysis).
+    while IFS=$'\t' read -r -a label ; do
+
+        if [ -z "$label" ] ; then
+            #echo "Cell is empty"
+            echo 0 >> ${fname}_lh_overlay.csv
+            #echo 0 >> check.csv
+        elif [[ $(grep "$label" ${fname}_summary.csv) != "" ]] ; then
+            #echo "$label in summary"
+            temp=$(grep $label ${fname}_summary.csv)
+            count=(${temp//,/ })
+            echo ${count[1]} >> ${fname}_lh_overlay.csv
+        else
+            #echo "Label not in summary"
+            echo 0 >> ${fname}_lh_overlay.csv
+            #echo 0 >> check.csv
+        fi
+
+    done < Glasser_labels_lh.csv
+
+    echo "Working on ${fname} rh..."
+
+    while IFS=$'\t' read -r -a label ; do
+
+        if [ -z "$label" ] ; then
+            #echo "Cell is empty"
+            echo 0 >> ${dirName}_rh_overlay.csv
+            #echo 0 >> check.csv
+        elif [[ $(grep "$label" ${fname}_summary.csv) != "" ]] ; then
+            #echo "$label in summary"
+            temp=$(grep $label ${fname}_summary.csv)
+            count=(${temp//,/ })
+            echo ${count[1]} >> ${fname}_rh_overlay.csv
+            #echo ${count[0]} >> check.csv
+        else
+            #echo "Label not in summary"
+            echo 0 >> ${fname}_rh_overlay.csv
+            #echo 0 >> check.csv
+        fi
+
+    done < Glasser_labels_rh.csv
+
+  done

### 2018-08-15 ciftitoText.sh

@@ -1,0 +1,34 @@
+#!bin/bash/
+
+# This will produce text files for each subject's CIFTI within a directory
+# First input to the function should be the general filename to follow (e.g. .MyelinMap_BC.32k_fs_LR.dscalar.nii)
+# Second should be the suffix of the generated file (e.g. myelin)
+dataName=$1
+dataType=$2
+
+# echo *${dataName}
+# echo $dataType
+
+# Turn each file into a text file
+for dataFile in *${dataName} ; do
+
+  fname=$(echo $dataFile | cut -f 1 -d '.')
+
+  echo $fname >> ${dataType}_subjList.txt
+
+  wb_command -cifti-convert -to-text $dataFile ${fname}_${dataType}.txt
+
+done
+
+# And combine
+# Note: this creates a tab-separated file.
+
+# Increase the upper limit of open files if necessary (for paste)
+nFiles=$(ls -l | wc -l)
+Limit=2
+if [ "$nFiles" -gt 500 ] ; then
+  ulimit -Hn 500 # The hard limit
+  ulimit -Sn 500 # The soft limit
+fi
+
+paste *_${dataType}.txt >> ${dataType}All.txt

### 2018-08-15 createAtlas.sh

@@ -1,0 +1,28 @@
+#!/bin/bash -l
+
+# this function will take a set of labels (from Glasser, .csv) and create an atlas that contains only those ROIs
+# no statistics are computed, it's just a visualization mask
+
+dirName=BBC
+
+#function createAtlas () {
+echo "#!ascii label, from condition ${dirName}" >> ${dirName}_lh_atlas.label
+echo "#!ascii label, from ondition ${dirName}" >> ${dirName}_rh_atlas.label
+totalLeft=0
+totalRight=0
+while IFS=$'\t' read -r -a label ; do
+  	if [[ $label == L* ]] ; then
+			totalLines=$(expr 2 + $(awk 'NR == 2 {print $1}' $HOME/fMRI/Glasser/label/lh/lh.${label}.label))
+    			totalLeft=$(expr $totalLines + $totalLeft)
+    			sed -n 3,${totalLines}p $HOME/fMRI/Glasser/label/lh/lh.${label}.label >> ${dirName}_lh_atlas.label
+    	else
+    			totalLines=$(expr 2 + $(awk 'NR == 2 {print $1}' $HOME/fMRI/Glasser/label/rh/rh.${label}.label))
+    			totalRight=$(expr $totalLines + $totalRight)
+    			sed -n 3,${totalLines}p $HOME/fMRI/Glasser/label/rh/rh.${label}.label >> ${dirName}_rh_atlas.label
+    	fi
+done < ${dirName}_threshLabels.csv
+sed -i "2i "$totalLeft"" ${dirName}_lh_atlas.label
+sed -i "2i "$totalRight"" ${dirName}_rh_atlas.label
+#}
+
+view $dirName

### 2018-08-15 createCiftifromVector.sh

@@ -1,0 +1,9 @@
+#!bin/bash/
+
+for dataFile in *dataforCifti.txt ; do
+
+  fname=$(echo $dataFile | cut -f 1,2 -d '_')
+
+  wb_command -cifti-convert -from-text ${dataFile} 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii ${fname}.dscalar.nii
+
+done

### 2018-08-15 graphAnalysis_solo.R

@@ -1,0 +1,1841 @@
+#!/usr/bin/env Rscript
+SubjID <- commandArgs(trailingOnly=TRUE)
+write(paste("Analyzing data for subject", SubjID), stdout())
+
+### Run a meta-analysis and graph theoretic fMRI analysis
+
+###------- Libraries and functions ---------------
+write('Loading functions and libraries...', stdout())
+
+library(igraph)
+#library(tidyverse)
+library(ggnetwork)
+library(ggplot2)
+library(gridExtra)
+library(data.table)
+library(plyr)
+library(mcclust)
+library(lme4)
+library(parallel)
+#library(lmerTest)
+
+## log-log degree distribution
+logDegreeDist <- function(Graph = padjMat) {
+  
+  tempD <- degree(Graph)
+  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
+  d <- (0:(max(tempD)-1))
+  ind <- (tempDD!=0)
+  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
+       xlab = "Log-Degree", ylab = "Log-Intensity",  
+       main = "Log-Log Degree Distribution")
+  
+}
+
+
+## Create correlation matrix between vertices of 2 ROIs
+# Requires labeled time series matrix
+vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
+  
+  # extract the time series from the ROIs
+  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
+  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
+  nVerts_1 <- length(indexing_1)
+  nVerts_2 <- length(indexing_2)
+  ROI_1_tseries <- timeSeries[indexing_1, ]
+  ROI_2_tseries <- timeSeries[indexing_2, ]
+  
+  # Create empty matrix
+  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)
+  
+  # 
+  for (vertex_1 in seq(nVerts_1)){
+    
+    # temp series 1
+    tempOne <- ROI_1_tseries[vertex_1, ]
+    
+    for(vertex_2 in seq(nVerts_2)){
+      
+      # temp series 2
+      tempTwo <- ROI_2_tseries[vertex_2, ]
+      
+      # store the Pearson correlation in the corr matrix
[…]

### 2018-08-15 graphAnalysis_solo_nonVS.R

@@ -1,0 +1,1839 @@
+#!/usr/bin/env Rscript
+SubjID <- commandArgs(trailingOnly=TRUE)
+write(paste("Analyzing data for subject", SubjID), stdout())
+
+### Run a meta-analysis and graph theoretic fMRI analysis
+
+###------- Libraries and functions ---------------
+write('Loading functions and libraries...', stdout())
+
+library(igraph)
+#library(tidyverse)
+library(ggnetwork)
+library(ggplot2)
+library(gridExtra)
+library(data.table)
+library(plyr)
+library(mcclust)
+library(lme4)
+library(parallel)
+#library(lmerTest)
+
+## log-log degree distribution
+logDegreeDist <- function(Graph = padjMat) {
+  
+  tempD <- degree(Graph)
+  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
+  d <- (0:(max(tempD)-1))
+  ind <- (tempDD!=0)
+  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
+       xlab = "Log-Degree", ylab = "Log-Intensity",  
+       main = "Log-Log Degree Distribution")
+  
+}
+
+
+## Create correlation matrix between vertices of 2 ROIs
+# Requires labeled time series matrix
+vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
+  
+  # extract the time series from the ROIs
+  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
+  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
+  nVerts_1 <- length(indexing_1)
+  nVerts_2 <- length(indexing_2)
+  ROI_1_tseries <- timeSeries[indexing_1, ]
+  ROI_2_tseries <- timeSeries[indexing_2, ]
+  
+  # Create empty matrix
+  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)
+  
+  # 
+  for (vertex_1 in seq(nVerts_1)){
+    
+    # temp series 1
+    tempOne <- ROI_1_tseries[vertex_1, ]
+    
+    for(vertex_2 in seq(nVerts_2)){
+      
+      # temp series 2
+      tempTwo <- ROI_2_tseries[vertex_2, ]
+      
+      # store the Pearson correlation in the corr matrix
[…]

### 2018-08-15 labelResample.sh

@@ -1,0 +1,36 @@
+#!/bin/bash
+
+# 1. To transform the label data from Glasser et al. (2016) into fsaverage space:
+# a. download the following dataset: http://brainvis.wustl.edu/workbench/standard_mesh_atlases.zip
+#    steps from: https://wiki.humanconnectome.org/download/attachments/63078513/Resampling-FreeSurfer-HCP.pdf?version=1&modificationDate=1471988055831&api=v2
+#    you also need to grab the Glasser label files
+
+# b. separate the .dlabel.nii file into .gii for both hemispheres:
+wb_command -cifti-separate Q1-Q6_RelatedParcellation210.CorticalAreas_dil_Final_Final_Areas_Group_Colors.32k_fs_LR.dlabel.nii COLUMN  \
+                           -label CORTEX_LEFT Glasser_pre_labels_lh.label.gii  \
+                           -label CORTEX_RIGHT Glasser_pre_labels_rh.label.gii  \
+
+# c. resample the labels into fsaverage space (twice, one for each hemisphere):
+wb_command -label-resample Glasser_pre_labels_lh.label.gii  \
+                           $HOME/Documents/HBM/Glasser_et_al_2016_HCP_MMP1.0_RVVG/standard_mesh_atlases/resample_fsaverage/fs_LR-deformed_to-fsaverage.L.sphere.32k_fs_LR.surf.gii  \
+                           $HOME/Documents/HBM/Glasser_et_al_2016_HCP_MMP1.0_RVVG/standard_mesh_atlases/resample_fsaverage/fsaverage6_std_sphere.L.41k_fsavg_L.surf.gii \
+                           ADAP_BARY_AREA \
+                           Glasser_post_labels_lh.label.gii  \
+                           -area-metrics  \
+                           $HOME/Documents/HBM/Glasser_et_al_2016_HCP_MMP1.0_RVVG/standard_mesh_atlases/resample_fsaverage/fs_LR.L.midthickness_va_avg.32k_fs_LR.shape.gii  \
+                           $HOME/Documents/HBM/Glasser_et_al_2016_HCP_MMP1.0_RVVG/standard_mesh_atlases/resample_fsaverage/fsaverage6.L.midthickness_va_avg.41k_fsavg_L.shape.gii
[…]

### 2018-08-15 prepSubj.sh

@@ -1,0 +1,37 @@
+#!bin/bash/
+
+subj=$1
+
+echo "Preparing data for subject ${subj}"
+
+# Copy data
+cp /projectnb/connectomedb/Q6/${subj}/MNINonLinear/fsaverage_LR32k/${subj}.corrThickness.32k_fs_LR.dscalar.nii /restricted/projectnb/cd-lab/Claudio/Community/
+cp /projectnb/connectomedb/Q6/${subj}/MNINonLinear/fsaverage_LR32k/${subj}.curvature.32k_fs_LR.dscalar.nii /restricted/projectnb/cd-lab/Claudio/Community/
+cp /projectnb/connectomedb/Q6/${subj}/MNINonLinear/fsaverage_LR32k/${subj}.MyelinMap_BC.32k_fs_LR.dscalar.nii /restricted/projectnb/cd-lab/Claudio/Community/
+
+cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/concatenated_rfMRI/rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii
+cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/rfMRI_REST1_LR/rfMRI_REST1_LR_Atlas_hp2000_clean.int.bpf.residMGSR.censor.demean.dtseries.nii /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST1_LR.dtseries.nii
+cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/rfMRI_REST1_RL/rfMRI_REST1_RL_Atlas_hp2000_clean.int.bpf.residMGSR.censor.demean.dtseries.nii /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST1_RL.dtseries.nii
+cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/rfMRI_REST2_LR/rfMRI_REST2_LR_Atlas_hp2000_clean.int.bpf.residMGSR.censor.demean.dtseries.nii /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST2_LR.dtseries.nii
[…]

### 2018-08-15 readTxt.py

@@ -1,0 +1,49 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+
+import os
+import sys
+
+# get the file name from bash input
+if os.environ.get('filename') == None:
+    print "No outside input from bash"
+    filename = raw_input("Enter file name (without .txt): ")
+else:
+    print "Input from bash"
+    filename = os.environ['filename']
+fname = filename + ".txt"
+
+# make target directory
+if not os.path.exists(filename):
+    os.makedirs(filename)
+
+# open files to read & write
+textFile = open(fname,'rU')
+textArray = textFile.readlines()
+totalRows = len(textArray)
+
+# change dir to store output
+os.chdir(filename)
+
+studyNumber = 1
+
+for i in range(totalRows):
+    if ('//' in textArray[i]) or (textArray[i] == '\n'):
+        # if you want to include all of the coordinates into one file:
+        # just use continue and open (coordFile, 'w') outside of the loop
+        if ('Subjects=' not in textArray[i]) and ('Reference=' not in textArray[i]) and (textArray[i] != '\n'):
+            splitting = textArray[i].split(' ')[1]
+            fileName = 'coords_%s_%s.txt' % (studyNumber,splitting[:-1])
+            studyNumber += 1
+            coordFile = open(fileName,'w')
+        else:
+            continue
+    else:
+
+        print textArray[i]
+        num = round(textArray[i])
+        print num
+        coordFile.write(textArray[i])
+
+coordFile.close
+textFile.close

### 2018-08-15 runGraph.sh

@@ -1,0 +1,33 @@
+#!/bin/bash -l
+
+# load modules within SCC
+module load R/3.4.3
+module list
+
+SubjID=$1
+
+# Setups
+#$ -l mem_total=48G
+#$ -pe omp 16
+#$ -j y
+
+# Prep subject
+sh prepSubj.sh $SubjID
+
+# Run the R script that calculates community detection for a set of participants
+Rscript graphAnalysis_solo.R $SubjID
+
+# Clean up
+rm -f ${SubjID}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii
+rm -f ${SubjID}_rfMRI_REST1_LR.dtseries.nii
+rm -f ${SubjID}_rfMRI_REST1_RL.dtseries.nii
+rm -f ${SubjID}_rfMRI_REST2_LR.dtseries.nii
+rm -f ${SubjID}_rfMRI_REST2_RL.dtseries.nii
+rm -f ${SubjID}.ptseries.nii
+rm -f ${SubjID}.corrThickness.32k_fs_LR.dscalar.nii
+rm -f ${SubjID}.curvature.32k_fs_LR.dscalar.nii
+rm -f ${SubjID}.MyelinMap_BC.32k_fs_LR.dscalar.nii
+
+mv ${SubjID}_myelin.txt ./MyelinMaps
+mv ${SubjID}_curvature.txt ./Curvature
+mv ${SubjID}_thickness.txt ./Thickness

### 2018-08-15 Analyze_summaries.Rmd
Added random ideas for intro

@@
 
+### scrabbling
+Previous meta analytic studies have provided important insights on the psychological phenomena attributed to mPFC subregions.
+For example, ADV et al find subdivisions of mPFC and MCC that are significantly tied to decision making in the literature.
+In particular, they show that more ventral regions are more tightly associated with reward and fear.
+However, this pattern overlaps with their finding that vmPFC also coactivates with DMN regions, and find no topographical distinction between these phenomena.
+Similarly, the results from Bartra et al and Laird et al show that this region can't be subdivided into DMN vs subjective value (acikalin, chris, russ).
+However, meta analysis rely on peaks often derived from group-averaged data.
+Recent work has prescribed relevance to the analysis of single subjects in fMRI.
+Yeo et al (2018) propose the use of individualized topologies when identifying functional networks.
+Gordon et al identify important idiosincrasies in oversampled subjects.
+Similarly, Braga and Buckner show that finer subdivisions of the DMN are possible when looking at each subject independently.
+This opens up the possibility that distinctions between DMN and subjective value are possible at this finer level of resolution, but would otherwise be masked in meta analytic work.
+Braga & Buckner's work is particularly informative when it comes to subdividing DMN.
+However, the seed-based functional connectivity analysis is sensitive to the selection of the seed.
+A natural next step would be to recruit all possible patterns of covariation within this network.
+A popular alternative is to rely on graph theoretic methods, which provide a characterization of networks that organically fits brain dynamics (provides an organic avenue to understand brain dynamics?), and thus permits the consideration of the full covariance structure of brain networks.
+(ADV & Tal somewhere here).
+
+add tors work too
+
+It is true that subregions of mPFC can be multifaceted, and ADV et al do suggest that given that no single psych construct belonged to each area.
+That said, the possibility remains that this is a feature of group averaging.
+
 ## Methods

### 2018-08-15 Manuscript/Manuscript.Rmd
Playing around with a manuscript template in R

---
title: 'Parsing medial prefrontal cortex: A joint meta-analytic and graph-theoretic approach.'

# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
author:
  - name: Claudio A. Toro-Serey
    affiliation: a,1,2
  - name: Joseph T. McGuire
    affiliation: a,1
address:
  - code: a
    address: Boston University, Department of Psychological and Brain Sciences, 64 Commonwealth Ave., Boston, 02250

corresponding_author:
  - code: 2
    text: "To whom correspondence should be addressed. E-mail: ctoro@bu.edu"

# For footer text
lead_author_surname: Toro-Serey

## Remove this if not required    
equal_authors:
  - code: 1
    text: "A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable)."

author_contributions: |
  Please provide details of author contributions here.

## Remove this if not required
conflict_of_interest: |
  Please declare any conflict of interest here.

abstract: |
  (Current count: 153) Valuation effects are consistently observed in medial prefrontal and posterior cingulate cortex (mPFC and PCC). The spatial extent of these effects is mostly indistinguishable from the default mode network (DMN) in existing meta-analyses. However, little is known about how valuation effects fit within the broader functional architecture of mPFC and PCC, or whether that architecture is consistent or idiosyncratic across individuals. Here we complement a meta-analysis with fMRI-based graph theoretic approaches to subdivide mPFC and PCC at the single-subject level. Our results suggest the functional topography of mPFC has substantial variability across individuals. This highlights the potential usefulness of estimating brain effects at the individual level in this region, and points to limitations of aggregative methods such as coordinate-based meta-analysis in determining whether valuation and DMN effects emerge from common or separable brain systems. Our approach shows promise in addressing this issue through future manipulations of valuation.

significance: |
  Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.

acknowledgements: |
  Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.

keywords:
  - Networks
  - DMN
  - Valuation

## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
pnas_type: pnasresearcharticle

bibliography: pnas-sample.bib
csl: pnas.csl

## change to true to add optional line numbering
lineno: false

output: rticles::pnas_article
---

(current, 676 words. Aim for 650)

The medial prefrontal cortex (mPFC) has been suggested to subserve many of the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016). Specifically, this region has been related to decision making (Bartra, McGuire, & Kable, 2013), memory encoding (Shacter, Addis, & Buckner, 2007), and default mode deactivation (DMN) (Yeo et al., 2011), among ohters. While much has been discovered about this area in primates (Barbas & Garcia-Cabezas, 2016), the lack of direct measurements of neuronal activity makes this a tough area to record in humans, one that nowadays relies mostly on functional MRI (fMRI). Unfortunately, the mPFC is especially challenging to image, as the oxygen-related signal recorded by fMRI is contaminated by the oxygen in the sinuses (Logothetis, 2008). In addition, this area is subject to more idiosyncratic cortical folding than any other region (Zilles, Palomero- Gallagher, & Amunts, 2013), thus adding a level of complexity to the generalizable dissection of topographic functional roles within mPFC.

Previous meta analytic studies have provided important insights on the psychological phenomena attributed to mPFC subregions. For example, de la Vega et al. (2016) found subdivisions of mPFC and MCC that are significantly tied to decision making in the literature. In particular, they show that more ventral regions are more tightly associated with reward and fear. However, this pattern overlaps with their finding that vmPFC also coactivates with DMN regions, and find no topographical distinction between these phenomena. Similarly, the results from Bartra et al and Laird et al show that this region can't be subdivided into DMN vs subjective value (acikalin, chris, russ). However, meta analyses rely on peaks often derived from group-averaged data. Recent work has prescribed relevance to the analysis of single subjects in fMRI. Yeo et al (2018) propose the use of individualized topologies when identifying functional networks. Gordon et al identify important idiosincrasies in oversampled subjects. Similarly, Braga and Buckner show that finer subdivisions of the DMN are possible when looking at each subject independently. This opens up the possibility that distinctions between DMN and subjective value are possible at this finer level of resolution, but would otherwise be masked in meta analytic work.

Braga & Buckner's work is particularly informative when it comes to subdividing DMN. However, the seed-based functional connectivity analysis is sensitive to the selection of the seed. A natural next step would be to recruit all possible patterns of covariation within this network. A popular alternative is to rely on graph theoretic methods, which provide a characterization of networks that organically fits brain dynamics (provides an organic avenue to understand brain dynamics?), and thus permits the consideration of the full covariance structure of brain networks. (ADV & Tal somewhere here).

Given the shortcomings of study-specific and cross-study analyses mentioned above, there is potential value in combining complementary strengths from both approaches. Focusing on resting state data has been successful in determining a number of neural phenomena, including disentangling auditory and visual attention areas (Tobyne, Osher, Michalka, & Somers, 2017).

One great advantage of network science is the ability to characterize connectivity in a way that allows for comparisons among individuals in a meaningful way (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018), thus letting us address the idiosyncrasies mentioned above. In this study, we aim to subdivide mPFC into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making. We address this aim at 3 levels of granularity: 1) across the literature (meta-analysis), selecting a number of regions of interest (ROI) that show significant overlap and specificity between DMN and decision making; 2) full-brain connectivity of actual fMRI data, using a pre-specified brain atlas; and 3) characterizing the connectivity of surface vertices (small units of function that contain oxygen-dependent neural information across time) for the regions selected in step one. I performed the last two steps at an individual subject level for 3 subjects, hoping to find some commonalities among them. In this way, I attempted to extract functional topographical information from topological network features.

Results {.unnumbered}
========================================

Discussion {.unnumbered}
========================================

(1500 words max)

Methods {.unnumbered}
========================================

See http://www.jneurosci.org/content/preparing-manuscript

References {.unnumbered}
========================================

Figures and Tables should be labelled and referenced in the standard way
using the `\label{}` and `\ref{}` commands.

Figure \[fig:frog\] shows an example of how to insert a column-wide
figure. To insert a figure wider than one column, please use the
`\begin{figure*}...\end{figure*}` environment. Figures wider than one
column should be sized to 11.4 cm or 17.8 cm wide.

Single column equations {#single-column-equations .unnumbered}
-----------------------

Authors may use 1- or 2-column equations in their article, according to
their preference.

To allow an equation to span both columns, options are to use the
`\begin{figure*}...\end{figure*}` environment mentioned above for
figures, or to use the `\begin{widetext}...\end{widetext}` environment
as shown in equation \[eqn:example\] below.

Please note that this option may run into problems with floats and
footnotes, as mentioned in the [cuted package
documentation](http://texdoc.net/pkg/cuted). In the case of problems
with footnotes, it may be possible to correct the situation using
commands `\footnotemark` and `\footnotetext`.

$$\begin{aligned}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \label{eqn:example} \\
       &=x^3+3x^2y+3xy^3+x^3. 
\end{aligned}$$

<!-- pandoc writes all tables using longtable, which fails in 2-column mode

  Species                    CBS     CV     G3
  ----------------------- ------ ------ ------
  1\. Acetaldehyde           0.0    0.0    0.0
  2\. Vinyl alcohol          9.1    9.6   13.5
  3\. Hydroxyethylidene     50.8   51.2   54.0

  : Comparison of the fitted potential energy surfaces and ab initio
  benchmark electronic energy calculations

-->

Supporting Information (SI) {#supporting-information-si .unnumbered}
---------------------------

The main text of the paper must stand on its own without the SI. Refer
to SI in the manuscript at an appropriate point in the text. Number
supporting figures and tables starting with S1, S2, etc. Authors are
limited to no more than 10 SI files, not including movie files. Authors
who place detailed materials and methods in SI must provide sufficient
detail in the main text methods to enable a reader to follow the logic
of the procedures and results and also must reference the online
methods. If a paper is fundamentally a study of a new method or
technique, then the methods must be described completely in the main
text. Because PNAS edits SI and composes it into a single PDF, authors
must provide the following file formats only.

### SI Text {#si-text .unnumbered}

Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a
PDF with the same file name for visual reference).

### SI Figures {#si-figures .unnumbered}

Provide a brief legend for each supporting figure after the supporting
text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or
GIF format; figures may not be embedded in manuscript text. When saving
TIFF files, use only LZW compression; do not use JPEG compression. Do
not save figure numbers, legends, or author names as part of the image.
Composite figures must be pre-assembled.

### 3D Figures {#d-figures .unnumbered}

Supply a composable U3D or PRC file so that it may be edited and
composed. Authors may submit a PDF file but please note it will be
published in raw format and will not be edited or composed.

### SI Tables {#si-tables .unnumbered}

Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a
PDF with the same file name for visual reference); include only one
table per file. Do not use tabs or spaces to separate columns in Word
tables.

### SI Datasets {#si-datasets .unnumbered}

Supply Excel (.xls), RTF, or PDF files. This file type will be published
in raw format and will not be edited or composed.

### SI Movies {#si-movies .unnumbered}

Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media
(wmv), animated GIF (gif), or MPEG files and submit a brief legend for
each movie in a Word or RTF file. All movies should be submitted at the
desired reproduction size and length. Movies should be no more than 10
MB in size.

### Still images {#still-images .unnumbered}

Authors must provide a still image from each video file. Supply TIFF,
EPS, high-resolution PDF, JPEG, or GIF files.

### Appendices {#appendices .unnumbered}

PNAS prefers that authors submit individual source files to ensure
readability. If this is not possible, supply a single PDF file that
contains all of the SI associated with the paper. This file type will be
published in raw format and will not be edited or composed.

<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
\showmatmethods
\showacknow
\pnasbreak

### 2018-08-15 Manuscript/Manuscript.tex
Playing around with a manuscript template in R

\documentclass[9pt,twocolumn,twoside,]{pnas-new}

%% Some pieces required from the pandoc template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Use the lineno option to display guide line numbers if required.
% Note that the use of elements such as single-column equations
% may affect the guide line number alignment.

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\templatetype{pnasresearcharticle}  % Choose template

\title{Parsing medial prefrontal cortex: A joint meta-analytic and
graph-theoretic approach.}

\author[a,1,2]{Claudio A. Toro-Serey}
\author[a,1]{Joseph T. McGuire}

  \affil[a]{Boston University, Department of Psychological and Brain Sciences, 64
Commonwealth Ave., Boston, 02250}

% Please give the surname of the lead author for the running footer
\leadauthor{Toro-Serey}

% Please add here a significance statement to explain the relevance of your work
\significancestatement{Authors must submit a 120-word maximum statement about the significance
of their research paper written at a level understandable to an
undergraduate educated scientist outside their field of speciality. The
primary goal of the Significance Statement is to explain the relevance
of the work in broad context to a broad readership. The Significance
Statement appears in the paper itself and is required for all research
papers.}

\authorcontributions{Please provide details of author contributions here.}

\authordeclaration{Please declare any conflict of interest here.}

\equalauthors{\textsuperscript{} }

\correspondingauthor{\textsuperscript{} }

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
 \keywords{  Networks |  DMN |  Valuation   }

\begin{abstract}
Valuation effects are consistently observed in medial prefrontal and
posterior cingulate cortex (mPFC and PCC). The spatial extent of these
effects is mostly indistinguishable from the default mode network (DMN)
in existing meta-analyses. However, little is known about how valuation
effects fit within the broader functional architecture of mPFC and PCC,
or whether that architecture is consistent or idiosyncratic across
individuals. Here we complement a meta-analysis with fMRI-based graph
theoretic approaches to subdivide mPFC and PCC at the single-subject
level. Our results suggest the functional topography of mPFC has
substantial variability across individuals. This highlights the
potential usefulness of estimating brain effects at the individual level
in this region, and points to limitations of aggregative methods such as
coordinate-based meta-analysis in determining whether valuation and DMN
effects emerge from common or separable brain systems. Our approach
shows promise in addressing this issue through future manipulations of
valuation.
\end{abstract}

\dates{This manuscript was compiled on \today}
\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}

\begin{document}

% Optional adjustment to line up main text (after abstract) of first page with line numbers, when using both lineno and twocolumn options.
% You should only change this length when you've finalised the article contents.
\verticaladjustment{-2pt}

\maketitle
\thispagestyle{firststyle}
\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.

\acknow{Please include your acknowledgments here, set in a single paragraph.
Please do not include any acknowledgments in the Supporting Information,
or anywhere else in the manuscript.}

One of the main goals of human cognitive neuroscience is to be able to
prescribe function to brain regions, either in isolation or in their
communication with others. Among general regions of the brain, the
medial prefrontal cortex (mPFC, located in the midline frontal portion
of the brain) has been suggested to subserve the cognitive abilities
that differentiate humans from other animals (Barbas \& Garcia-Cabezas,
2016). Specifically, this region has been related to a variety of
functions, including decision making (Bartra, McGuire, \& Kable, 2013),
memory encoding (Shacter, Addis, \& Buckner, 2007), and default mode
deactivation (DMN) (Yeo et al., 2011). While much has been discovered
about this area in primates (Barbas \& Garcia-Cabezas, 2016), the lack
of direct measurements of neuronal activity makes this a tough area to
record in humans, one that nowadays relies mostly on functional MRI
(fMRI). Unfortunately, the mPFC is especially challenging to image, as
the oxygen-related signal recorded by fMRI is contaminated by the oxygen
in the sinuses (Logothetis, 2008). In addition, this area is subject to
more idiosyncratic cortical folding than any other region (Zilles,
Palomero- Gallagher, \& Amunts, 2013), thus adding a level of complexity
to the generalizable dissection of topographic functional roles within
mPFC.

Studies of valuation have consistently shown functional overlap with
DMN. Recent meta-analytic work has attempted to distinguish the brain
areas belonging to each by examining the locus of peak activity across
studies related to the behavioral features mentioned above (Bartra et
al., 2013; Acikalin, Gorgolewski, \& Poldrack, 2017). While this
approach offers valuable information, it is subject to the quality of
imaging in each study, as well as their corresponding differences in
tasks used to examine choice. In addition, recent findings suggest that
the functional topology of the brain is better understood by accounting
for organizational idosyncrasies (Braga and Buckner, 2018; Yeo et al.,
2018, Gordon et al., 2017, Gratton\ldots{}).

Given the shortcomings of study-specific and cross-study analyses
mentioned above, there is potential value in combining complementary
strengths from both approaches. While my lab is primarily interested in
the portion of mPFC dedicated to decision making, in order to bypass the
heterogeneity in behavioral tasks, it might be best to disentangle the
mPFC by focusing first on which of its sub-regions belong to
resting-state DMN, and which do not. The advantage lies in that (1) all
resting state scans are performed equally (the subject lies in the
scanner with their eyes open), and (2) there is a high quality resource
of resting state data provided by the Human Connectome Project. Focusing
on resting state data has been successful in determining a number of
neural phenomena, including disentangling auditory and visual attention
areas (Tobyne, Osher, Michalka, \& Somers, 2017).

This approach opens an opportunity to examine brain dynamics. For
example, a region's function might depend on its connectivity at any
given time with one brain community or another. An ever-growing trend in
human neuroimaging has been to apply network statistics to tackle these
functional challenges. One great advantage of network science is the
ability to characterize connectivity in a way that allows for
comparisons among individuals in a meaningful way (Garcia, Ashourvan,
Muldoon, Vettel, \& Bassett, 2018), thus letting us address the folding
idiosyncrasies mentioned above. Therefore, I propose to use some of the
statistics that we have learned in class to estimate intrinsic
functional subdivisions of the mPFC at the individual subject level.
Particularly, I would like to distinguish communities related to DMN
from non-DMN, so that we can generate more informed topographic targets
for future studies of decision making.

In this study, I try to address my question at 3 levels of granularity:
1) across the literature (meta-analysis), selecting a number of regions
of interest (ROI) that show significant overlap and specificity between
DMN and decision making; 2) full-brain connectivity of actual fMRI data,
using a pre-specified brain atlas; and 3) characterizing the
connectivity of surface vertices (small units of function that contain
oxygen-dependent neural information across time) for the regions
selected in step one. I performed the last two steps at an individual
subject level for 3 subjects, hoping to find some commonalities among
them. In this way, I attempted to extract functional topographical
information from topological network features.

\section*{Results}\label{results}
\addcontentsline{toc}{section}{Results}

\section*{Discussion}\label{discussion}
\addcontentsline{toc}{section}{Discussion}

\section*{Methods}\label{methods}
\addcontentsline{toc}{section}{Methods}

\section*{Results}\label{results-1}
\addcontentsline{toc}{section}{Results}

Please note that whilst this template provides a preview of the typeset
manuscript for submission, to help in this preparation, it will not
necessarily be the final publication layout. For more detailed
information please see the
\href{http://www.pnas.org/site/authors/format.xhtml}{PNAS Information
for Authors}.

\subsection*{Author Affiliations}\label{author-affiliations}
\addcontentsline{toc}{subsection}{Author Affiliations}

Include department, institution, and complete address, with the
ZIP/postal code, for each author. Use lower case letters to match
authors with institutions, as shown in the example. Authors with an
ORCID ID may supply this information at submission.

\subsection*{Submitting Manuscripts}\label{submitting-manuscripts}
\addcontentsline{toc}{subsection}{Submitting Manuscripts}

All authors must submit their articles at
\href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you
are using Overleaf to write your article, you can use the ``Submit to
PNAS'' option in the top bar of the editor window.

\subsection*{Format}\label{format}
\addcontentsline{toc}{subsection}{Format}

Many authors find it useful to organize their manuscripts with the
following order of sections; Title, Author Affiliation, Keywords,
Abstract, Significance Statement, Results, Discussion, Materials and
methods, Acknowledgments, and References. Other orders and headings are
permitted.

\subsection*{Manuscript Length}\label{manuscript-length}
\addcontentsline{toc}{subsection}{Manuscript Length}

PNAS generally uses a two-column format averaging 67 characters,
including spaces, per line. The maximum length of a Direct Submission
research article is six pages and a PNAS PLUS research article is ten
pages including all text, spaces, and the number of characters displaced
by figures, tables, and equations. When submitting tables, figures,
and/or equations in addition to text, keep the text for your manuscript
under 39,000 characters (including spaces) for Direct Submissions and
72,000 characters (including spaces) for PNAS PLUS.

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

References should be cited in numerical order as they appear in text;
this will be done automatically via bibtex, e.g. (1) and (2, 3). All
references, including for the SI, should be included in the main
manuscript file. References appearing in both sections should not be
duplicated. SI references included in tables should be included with the
main reference section.

\subsection*{Data Archival}\label{data-archival}
\addcontentsline{toc}{subsection}{Data Archival}

PNAS must be able to archive the data essential to a published article.
Where such archiving is not possible, deposition of data in public
databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata,
and others outlined in the Information for Authors, is acceptable.

\subsection*{Language-Editing Services}\label{language-editing-services}
\addcontentsline{toc}{subsection}{Language-Editing Services}

Prior to submission, authors who believe their manuscripts would benefit
from professional editing are encouraged to use a language-editing
service (see list at www.pnas.org/site/authors/language-editing.xhtml).
PNAS does not take responsibility for or endorse these services, and
their use has no bearing on acceptance of a manuscript for publication.

\begin{figure}
\centering
\includegraphics{frog.png}
\caption{Placeholder image of a frog with a long example caption to show
justification setting.{}}
\end{figure}

\subsection*{Digital Figures}\label{sec:figures}
\addcontentsline{toc}{subsection}{Digital Figures}

Only TIFF, EPS, and high-resolution PDF for Mac or PC are allowed for
figures that will appear in the main text, and images must be final
size. Authors may submit U3D or PRC files for 3D images; these must be
accompanied by 2D representations in TIFF, EPS, or high-resolution PDF
format. Color images must be in RGB (red, green, blue) mode. Include the
font files for any text.

Figures and Tables should be labelled and referenced in the standard way
using the \texttt{\textbackslash{}label\{\}} and
\texttt{\textbackslash{}ref\{\}} commands.

Figure \[fig:frog\] shows an example of how to insert a column-wide
figure. To insert a figure wider than one column, please use the
\texttt{\textbackslash{}begin\{figure*\}...\textbackslash{}end\{figure*\}}
environment. Figures wider than one column should be sized to 11.4 cm or
17.8 cm wide.

\subsection*{Single column equations}\label{single-column-equations}
\addcontentsline{toc}{subsection}{Single column equations}

Authors may use 1- or 2-column equations in their article, according to
their preference.

To allow an equation to span both columns, options are to use the
\texttt{\textbackslash{}begin\{figure*\}...\textbackslash{}end\{figure*\}}
environment mentioned above for figures, or to use the
\texttt{\textbackslash{}begin\{widetext\}...\textbackslash{}end\{widetext\}}
environment as shown in equation \[eqn:example\] below.

Please note that this option may run into problems with floats and
footnotes, as mentioned in the \href{http://texdoc.net/pkg/cuted}{cuted
package documentation}. In the case of problems with footnotes, it may
be possible to correct the situation using commands
\texttt{\textbackslash{}footnotemark} and
\texttt{\textbackslash{}footnotetext}.

\[\begin{aligned}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \label{eqn:example} \\
       &=x^3+3x^2y+3xy^3+x^3. 
\end{aligned}\]

\subsection*{Supporting Information
(SI)}\label{supporting-information-si}
\addcontentsline{toc}{subsection}{Supporting Information (SI)}

The main text of the paper must stand on its own without the SI. Refer
to SI in the manuscript at an appropriate point in the text. Number
supporting figures and tables starting with S1, S2, etc. Authors are
limited to no more than 10 SI files, not including movie files. Authors
who place detailed materials and methods in SI must provide sufficient
detail in the main text methods to enable a reader to follow the logic
of the procedures and results and also must reference the online
methods. If a paper is fundamentally a study of a new method or
technique, then the methods must be described completely in the main
text. Because PNAS edits SI and composes it into a single PDF, authors
must provide the following file formats only.

\subsubsection*{SI Text}\label{si-text}
\addcontentsline{toc}{subsubsection}{SI Text}

Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a
PDF with the same file name for visual reference).

\subsubsection*{SI Figures}\label{si-figures}
\addcontentsline{toc}{subsubsection}{SI Figures}

Provide a brief legend for each supporting figure after the supporting
text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or
GIF format; figures may not be embedded in manuscript text. When saving
TIFF files, use only LZW compression; do not use JPEG compression. Do
not save figure numbers, legends, or author names as part of the image.
Composite figures must be pre-assembled.

\subsubsection*{3D Figures}\label{d-figures}
\addcontentsline{toc}{subsubsection}{3D Figures}

Supply a composable U3D or PRC file so that it may be edited and
composed. Authors may submit a PDF file but please note it will be
published in raw format and will not be edited or composed.

\subsubsection*{SI Tables}\label{si-tables}
\addcontentsline{toc}{subsubsection}{SI Tables}

Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a
PDF with the same file name for visual reference); include only one
table per file. Do not use tabs or spaces to separate columns in Word
tables.

\subsubsection*{SI Datasets}\label{si-datasets}
\addcontentsline{toc}{subsubsection}{SI Datasets}

Supply Excel (.xls), RTF, or PDF files. This file type will be published
in raw format and will not be edited or composed.

\subsubsection*{SI Movies}\label{si-movies}
\addcontentsline{toc}{subsubsection}{SI Movies}

Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media
(wmv), animated GIF (gif), or MPEG files and submit a brief legend for
each movie in a Word or RTF file. All movies should be submitted at the
desired reproduction size and length. Movies should be no more than 10
MB in size.

\subsubsection*{Still images}\label{still-images}
\addcontentsline{toc}{subsubsection}{Still images}

Authors must provide a still image from each video file. Supply TIFF,
EPS, high-resolution PDF, JPEG, or GIF files.

\subsubsection*{Appendices}\label{appendices}
\addcontentsline{toc}{subsubsection}{Appendices}

PNAS prefers that authors submit individual source files to ensure
readability. If this is not possible, supply a single PDF file that
contains all of the SI associated with the paper. This file type will be
published in raw format and will not be edited or composed.

\showmatmethods
\showacknow
\pnasbreak

\hypertarget{refs}{}
\hypertarget{ref-belkin2002using}{}
1. Belkin M, Niyogi P (2002) Using manifold stucture for partially
labeled classification. \emph{Advances in Neural Information Processing
Systems}, pp 929--936.

\hypertarget{ref-berard1994embedding}{}
2. Bérard P, Besson G, Gallot S (1994) Embedding riemannian manifolds by
their heat kernel. \emph{Geometric \& Functional Analysis GAFA}
4(4):373--398.

\hypertarget{ref-coifman2005geometric}{}
3. Coifman RR, et al. (2005) Geometric diffusions as a tool for harmonic
analysis and structure definition of data: Diffusion maps.
\emph{Proceedings of the National Academy of Sciences of the United
States of America} 102(21):7426--7431.

% Bibliography
% \bibliography{pnas-sample}

\end{document}

### 2018-08-16 Manuscript/Manuscript.Rmd
Small edits

@@
 
+Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007)
+
 The medial prefrontal cortex (mPFC) has been suggested to subserve many of the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016).
@@
 
+``` {r Libraries and functions, include = FALSE, echo = FALSE}
+setwd('../')
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
+
+Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere
+
+# In case I want to visualize stuff in the brain
+labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[,2:6]
+labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))
+
+library(igraph)
+library(pander)
+library(ggnetwork)
+library(ggplot2)
+library(gridExtra)
+library(data.table)
+library(plyr)
+library(mcclust)
+library(lme4)
+library(parallel)
+library(corrplot)
+library(DescTools)
+
+## Cohen's D for 2 groups
+# for a more flexible approach, make the data input to be a list with entries for n groups, 
+# then do length(list) for the number of groups. 
+cohenD <- function(group1 = 1, group2 = 2){
+
+  # means
+  mean1 <- mean(group1, na.rm = T)
+  mean2 <- mean(group2, na.rm = T)
+
+  # variance
+  var1 <- var(group1, na.rm = T)
+  var2 <- var(group2, na.rm = T)
+
+  # equation
+  out <- (mean1 - mean2) / sqrt((var1 + var2)/2)
+
+  return(out)
+
+}
+
+## log-log degree distribution
+logDegreeDist <- function(Graph = padjMat) {
+
+  tempD <- degree(Graph)
+  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
+  d <- (0:(max(tempD)-1))
+  ind <- (tempDD!=0)
+  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
+       xlab = "Log-Degree", ylab = "Log-Intensity",  
+       main = "Log-Log Degree Distribution")
+
+}
+
+## Create correlation matrix between vertices of 2 ROIs
+# Requires labeled time series matrix
+vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
+
+  # extract the time series from the ROIs
+  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
+  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
+  nVerts_1 <- length(indexing_1)
+  nVerts_2 <- length(indexing_2)
+  ROI_1_tseries <- timeSeries[indexing_1, ]
+  ROI_2_tseries <- timeSeries[indexing_2, ]
+
+  # Create empty matrix
+  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)
+
+  # 
+  for (vertex_1 in seq(nVerts_1)){
+
+    # temp series 1
+    tempOne <- ROI_1_tseries[vertex_1, ]
+
+    for(vertex_2 in seq(nVerts_2)){
+
+      # temp series 2
+      tempTwo <- ROI_2_tseries[vertex_2, ]
+
+      # store the Pearson correlation in the corr matrix
+      corrMat[vertex_1, vertex_2] <- cor(tempOne, tempTwo, method = "pearson")
+
+    }
+  }
+
+  # name the dimensions of the matrix according to the surface vertex index
+  rownames(corrMat) <- indexing_1
+  colnames(corrMat) <- indexing_2
+
+  # plot (optional?)  
+  # unclustered heatmap
+  heatmap(corrMat,
+          Rowv = NA,
+          Colv = NA,
+          scale = "row",
+          col = pallette(1000))
+
+  # clustered heatmap
+  heatmap(corrMat,
+          scale = "row",
+          col = pallette(1000))
+
+  # print min-max corr vals
+  print(range(corrMat))
+
+  return(corrMat)
+
+}
+
+## Correlation matrix between an ROI and the Glasser parcels
+parcelCorrMat <- function(ROI = 'R_7m_ROI', lbels = lookup$V1){
+
+  # extract the time series from the ROIs
+  indexing <- which(rownames(timeSeries)==as.character(ROI))
+  nVerts <- length(indexing)
+  ROI_tseries <- timeSeries[indexing, ]
+
+  # create empty matrix to store values
+  corrMat <- matrix(data = 0, nrow = nVerts, ncol = 360)
+
+  # Loop through every combination of label and 7m vertex
+  for (Parcel in lbels){
+
+    # Get an ROI index to retrieve timeseries and store correlation vals
+    indxROI <- which(lbels==as.character(Parcel))
+
+    for(vertex in seq(nVerts)){
+
+      # temp series
+      tempROI <- as.numeric(ptSeries[indxROI, ])
+      tempVertex <- ROI_tseries[vertex, ]
+
+      # store the Pearson correlation in the corr matrix
+      corrMat[vertex, indxROI] <- cor(tempROI, tempVertex, method = "pearson")
+
+    }
+  }
+
+  # name the columns according to labels
+  colnames(corrMat) <- lbels
+  rownames(corrMat) <- indexing
+
+  # plot (optional?)  
+  # unclustered heatmap
+  heatmap(corrMat,
+          Rowv = NA,
+          Colv = NA,
+          scale = "none",
+          col = pallette(1000))
+
+  # clustered heatmap
+  heatmap(corrMat,
+          scale = "none",
+          col = pallette(1000))
+
+  # print min-max corr vals
+  print(range(corrMat))
+
+  return(corrMat)
+
+}
+
+## Correlation matrix between an Parcel and every other grayordinate
+# THIS CAN BE OPTIMIZED WITH A BETTER USE OF COR()
+partoverCorrMat <- function(ROI = 'R_7m_ROI', lbels = verts[[1]]){
+
+  # extract the time series from the ROI
+  indexing <- which(rownames(ptSeries)==as.character(ROI))
+  ROI_tseries <- as.numeric(ptSeries[indexing, ])
+
+  # get the remaining number of vertices
+  nVerts <- length(lbels)
+
+  # Create data frame to store values
+  parcelIndx <- which(labelCoords_parcel$Label==ROI)
+  corrVec <- data.frame(Seed = rep(ROI, nVerts),
+                        Labels = lbels,
+                        xstart = rep(labelCoords_parcel$x[parcelIndx], nVerts), # 7.33324 for R_7m
+                        ystart = rep(labelCoords_parcel$y[parcelIndx], nVerts), # -63.142
+                        zstart = rep(labelCoords_parcel$z[parcelIndx], nVerts)) # 42.5578
+
+  for(vertex in seq(nVerts)){
+
+    # temp series
+    tempVertex <- timeSeries[vertex, ]
+
+    # store the Pearson correlation in the corr matrix
+    #corrVec$Correlation[vertex] <- cor(ROI_tseries, tempVertex, method = "pearson")
+
+    # Another option, so that FDR can be applied
+    tempCor <- cor.test(ROI_tseries, tempVertex, method = "pearson")
+    corrVec$Correlation[vertex] <- tempCor$estimate
+    corrVec$pval[vertex] <- tempCor$p.value
+
+  }
+
+  # Turn ROI vertices into 0s
+  indexing <- which(corrVec$Labels==as.character(ROI))
+  corrVec$Correlation[indexing] <- 0
+
+  # Create a column with p-vals corrected for multiple comparisons
+  corrVec$adjPval <- p.adjust(corrVec$pval, "BY")
+
+  # normalize correlation vals for analysis (see below)
+  tempTanh <- fisherTanh(Data = corrVec$Correlation)
+  corrVec$tanhZ <- tempTanh$tanhZ
+  corrVec$tanhPvals <- tempTanh$pvals
+  corrVec$tanhPAdjusted <- tempTanh$adjustPvals
+
+  return(corrVec)
+
+}
+
+## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
+# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
+# Normalization approach suggested in network textbook (equation 7.10)
+fisherTanh <- function(Data = padjMatrix){
+
+  transformed <- list()
+
+  # tanh
+  transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
+
+  # p-vals
+  if (is.matrix(Data)) {
+    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
+    n <- dim(Data)[1]
+  } else if (is.vector(Data)) {
+    z.vec <- transformed$tanhZ
+    n <- length(Data)
+  }
+  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)
+
+  # adjust pvals
+  transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")
+
+  if (is.matrix(Data)) {
+    # get pvals and their adjustment into a symetric matrix form
+    # regular
+    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
+    tempMat[upper.tri(tempMat)] <- transformed$pvals
+    tempMat[lower.tri(tempMat)] <- transformed$pvals
+    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
+    transformed$pvals <- tempMat
+
+    # adjusted
+    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
+    tempMat[upper.tri(tempMat)] <- transformed$adjustPvals
+    tempMat[lower.tri(tempMat)] <- transformed$adjustPvals
+    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
+    transformed$adjustPvals <- tempMat
+  }
+
+  return(transformed)
+
+}
+
+## Extract the centroid-most vertex from each parcel
+parcelCentroid <- function(ROI = 'R_7m_ROI', all_coordinates = labelCoords_vertex){
+
+  # The coordinate file must contain a Label column
+
+  # Get the ROI-specific vertices
+  indx <- grep(ROI, all_coordinates$Label)
+
+  # Grab the coordinates
+  tempCoords <- all_coordinates[indx, c("x","y","z")]
+  rownames(tempCoords) <- indx
+
+  # Compute the distance among all vertices, and turn into a matrix
+  tempDist <- dist(tempCoords, diag = T)
+  tempDist <- as.matrix(tempDist)
+
+  # Compute the sum of distances for each vertex, and get the minimum
+  sumDists <- colSums(tempDist)
+  minDist <- which(sumDists == min(sumDists))
+  minDist <- indx[minDist]
+
+  return(minDist)
+
+}
+
+## This function takes the output from partoverCorrMat() and adds/removes the characteristics we decided on.
+prepROItoVer <- function(Data = R_7m_allCorr, Coordinates = labelCoords_vertex){
+
+  # Add vertex coordinates
+  tempDframe <- cbind(Data, Coordinates[,1:3])
+
+  # Remove rows with non-significant adjusted pvalues
+  indx <- tempDframe$adjPval < 0.05
+  tempDframe <- tempDframe[indx, ]
+
+  # Characterize correlation direction and round up vals for plotting
+  tempDframe$Relation <- ifelse(tempDframe$Correlation < 0, "Negative", "Positive")
+  tempDframe$Correlation <- round(tempDframe$Correlation, digits = 2)
+
+  # Add a column to differentiate between left/right hemispheres
+  tempDframe$Hemisphere <- substring(tempDframe$Labels,1,1)
+
+  return(tempDframe)
+
+}
+
+## Plot correlation from ROI to rest of vertices
+plotROItoVertex <- function(Data = R_7m_allCorr, ROI = 'R_7m_ROI', ColRange = Cols, View = "Axial", Legends = TRUE){
+
+  ROIindx <- grep(ROI, Data$Labels)
+  ROIvertices <- Data[ROIindx,c("x","y","z")] # grab ROI-specific vertices to black out
+  labelCoord <- ROIvertices[1,] # just to place the label
+
+  if (View == "Axial") {
+    ggplot() +
+      geom_point(data = Data, aes(x=x, y=y, alpha=.5, color = Correlation), show.legend = Legends) +
+      geom_point(data = labelCoords_vertex, aes(x=x, y=y), alpha=0.01) +
+      geom_nodes(data = ROIvertices, aes(x=x, y=y)) +
+      geom_nodelabel_repel(aes(x=labelCoord$x, y=labelCoord$y, label = sub("_ROI","",ROI))) +
+      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
+      theme_blank()
+  } else if (View == "Sagittal") {
+    ggplot() +
+      geom_point(data = Data, aes(x=y, y=z, alpha=.5, color = Correlation), show.legend = Legends) +
+      geom_point(data = labelCoords_vertex, aes(x=y, y=z), alpha=0.01) +
+      geom_nodes(data = ROIvertices, aes(x=y, y=z)) +
+      geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
+      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
+      theme_blank()
+  } else if (View == "Coronal") {
+    ggplot() +
+      geom_point(data = Data, aes(x=x, y=z, alpha=.5, color = Correlation), show.legend = Legends) +
+      geom_point(data = labelCoords_vertex, aes(x=x, y=z),  alpha=0.01) +
+      geom_nodes(data = ROIvertices, aes(x=x, y=z), alpha=.5) +
+      geom_nodelabel_repel(aes(x=labelCoord$x, y=labelCoord$z, label = sub("_ROI","",ROI))) +
+      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
+      theme_blank()
+  } else if (View == "Medial Right") {
+    if (substring(ROI,1,1) == "R") {
+      oneHemi <- Data[grep("R", Data$Hemisphere), ]
+      oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
+      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
+      medialHemi$y <- medialHemi$y * -1
+      ROIvertices$y <- ROIvertices$y * -1
+      labelCoord$y <- labelCoord$y * -1
+      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
+      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
+      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
+      medialHemi_all$y <- medialHemi_all$y * -1
+      ggplot() +
+        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
+        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
+        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
+        geom_nodes(data = ROIvertices, aes(x=y, y=z), alpha=.5) +
+        geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
+        theme_blank()
+    } else {
+      oneHemi <- Data[grep("R", Data$Hemisphere), ]
+      oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
+      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
+      medialHemi$y <- medialHemi$y * -1
+      ROIvertices$y <- ROIvertices$y * -1
+      labelCoord$y <- labelCoord$y * -1
+      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
+      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
+      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
+      medialHemi_all$y <- medialHemi_all$y * -1
+      ggplot() +
+        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
+        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
+        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
+        theme_blank()
+    }
+  } else if (View == "Medial Left") {
+    if (substring(ROI,1,1) == "L") {
+      oneHemi <- Data[grep("L", Data$Hemisphere), ]
+      oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
+      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
+      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
+      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
+      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
+      ggplot() +
+        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
+        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
+        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
+        geom_nodes(data = ROIvertices, aes(x=y, y=z), alpha=.5) +
+        geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
+        theme_blank()
+    } else {
+      oneHemi <- Data[grep("L", Data$Hemisphere), ]
+      oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
+      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
+      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
+      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
+      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
+      ggplot() +
+        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
+        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
+        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
+        theme_blank()
+    }
+  }
+
+}
+
+## Run a fastgreedy modularity community detection on ROIs
+# This function relies on having the timeSeries data uploaded, and labelCoords_vertex 
+# Extras dictates whether the community object + correlation matrix should also be extracted
+communityDetection <- function(Data = parcelBins$First, ROIS = "None", Type = "vertex", thresh = F, extras = F) {
+
+  print(paste('Computing modularity based on', Type))
+
+  if (ROIS == "None"){
+
+    # This will just do SP for now, for sliding window
+    print("Previously concatenated data")
+
+    corrMat <- cor(t(Data))
+    corrMatrix <- corrMat
+    transfMat <- fisherTanh(Data = corrMat)
+    if (thresh == T) {
+      transfMat$tanhZ[transfMat$adjustPvals > 0.05] <- 0
+    }
+    corrMat <- transfMat$tanhZ
+
+    diag(transfMat$tanhZ) <- 0    
+    diag(corrMat) <- 0
+
+    corrMat <- exp(corrMat)
+    corrMat[corrMat==1] <- 0
+    transfMat$tanhZ <- corrMat
+
+    tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
+    tempLap <- laplacian_matrix(tempGraph, normalized=T)
+    tempEigen <- eigen(tempLap)
+    f.vec <- length(tempEigen$values) - 1
+    tempEigen$binarized <-  as.factor(ifelse(tempEigen$vectors[,f.vec] > 0, 1, 0)) # binarized Fiedler Vector
+
+    summary <- data.frame(Label = colnames(corrMat),
+                          Hemisphere = substring(colnames(corrMat),1,1),
+                          EigenVal = tempEigen$values,
+                          FiedlerVec = tempEigen$vectors[, (length(tempEigen$values) - 1)],
+                          FiedlerBinary = tempEigen$binarized)
+
+    ## Get the final components
+    if (extras == T) {
+      modularityResults <- list(CorrMatrix = corrMatrix,
+                                TransfMatrix = transfMat,
+                                Summary = summary)
+    } else {
+      modularityResults <- list(Summary = summary)
+    }
+
+  } else {
+
+    if (Type == "vertex") {
+      # To store the vertex indices corresponding to the ROIs
+      indx <- numeric()
+
+      # had to place dashes on each side because grep grabbed strings containing the names (i.e. 47m, a24pr)
+      #ROIS <- c("_7m_", vmPFC_labels) # c("_a24_", "_7m_")
+      for (ROI in ROIS) {
+        indx <- c(indx, grep(ROI, rownames(Data)))  
+      }
+
+      nVerts <- length(indx)
+      ROI_tseries <- Data[indx, ]
+
+      # This used to be done with the for loop, but it was too slow. cor() speeds up the process by a lot
+      corrMat <- cor(t(ROI_tseries))
+
+      # name the dimensions of the matrix according to the surface vertex index
+      rownames(corrMat) <- indx
+
+      # for storing later
+      corrMatrix <- corrMat
+
+      # transform to Fisher's (think of thresholding)
+      transfMat <- fisherTanh(Data = corrMat)
+
+      # Determine if edges should be thresholded or not
+      if (thresh == T) {
+        transfMat$tanhZ[transfMat$adjustPvals > 0.05] <- 0
+      }
+
+      # Store Fisher transformed vals for graphing
+      corrMat <- transfMat$tanhZ
+
+      # diagonals of 1 could be interpreted as self-loops
+      diag(transfMat$tanhZ) <- 0    
+      diag(corrMat) <- 0
+
+      # Exponentiate to preserve distribution while ensuring positive weights
+      # I'm keeping corrMat and transfMat$tanhZ separate in case I want to uncorrect transfMat in the future
+      corrMat <- exp(corrMat)
+      corrMat[corrMat==1] <- 0
+      transfMat$tanhZ <- corrMat
+
+      # community detection
+      # I initially used the absolute value of the correlation, but the exp preserves the distribution 
+      # Next, try using the fisher transform
+
+      tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
+      tempCommunity <- fastgreedy.community(tempGraph)
+
+      # community object
+      #modularityResults$community <- tempCommunity
+
+      # correlation matrix with transformed values
+      #modularityResults$corrMat <- corrMatrix
+
+      # get coordinate info from selected regions (useful for ggplot)
+      summary <- data.frame(Vertex = indx,
+                            Label = tempCommunity$names,
+                            Membership = tempCommunity$membership,
+                            Modularity = tempCommunity$modularity,
+                            x = labelCoords_vertex[indx, "x"],
+                            y = labelCoords_vertex[indx, "y"],
+                            z = labelCoords_vertex[indx, "z"],
+                            Hemisphere = substring(tempCommunity$names,1,1))
+
+    } else if (Type == "parcels") {
+
+      # This used to be done with the for loop, but it was too slow. cor() speeds up the process by a lot
+      corrMat <- cor(t(Data))
+
+      # for storing later
+      corrMatrix <- corrMat
+
+      # transform to Fisher's (think of thresholding)
+      transfMat <- fisherTanh(Data = corrMat)
+
+      # Determine if edges should be thresholded or not
+      if (thresh == T) {
+        transfMat$tanhZ[transfMat$adjustPvals > 0.05] <- 0
+      }
+
+      # Store Fisher transformed vals for graphing
+      corrMat <- transfMat$tanhZ
+
+      # diagonals of 1 could be interpreted as self-loops
+      diag(transfMat$tanhZ) <- 0
+      diag(corrMat) <- 0
+
+      # Exponentiate to preserve distribution while ensuring positive weights
+      # I'm keeping corrMat and transfMat$tanhZ separate in case I want to uncorrect transfMat in the future
+      corrMat <- exp(corrMat)
+      corrMat[corrMat==1] <- 0
+      transfMat$tanhZ <- corrMat
+
+      # community detection
+      # I initially used the absolute value of the correlation, but the exp preserves the distribution 
+      # Next, try thresholding it by the adjusted p-vals
+      tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
+      tempCommunity <- fastgreedy.community(tempGraph)
+
+      # community object
+      #modularityResults$community <- tempCommunity
+
+      # correlation matrix with transformed values
+      #modularityResults$corrMat <- corrMatrix
+
+      # get coordinate info from selected regions (useful for ggplot)
+      summary <- data.frame(Label = tempCommunity$names,
+                            Membership = tempCommunity$membership,
+                            Modularity = tempCommunity$modularity,
+                            x = labelCoords_parcel[ ,"x"],
+                            y = labelCoords_parcel[ ,"y"],
+                            z = labelCoords_parcel[ ,"z"],
+                            Hemisphere = substring(tempCommunity$names,1,1))
+
+    }
+
+    ## Get the final components
+    modularityResults <- list(Community = tempCommunity,
+                              CorrMatrix = corrMatrix,
+                              TransfMatrix = transfMat,
+                              Summary = summary)
+
+  }
+
+  return(modularityResults)
+
+}
+
+## plot the communities from communityDetection
+plotCommunities <- function(Data = modularityResults, Hemi = "R", type = "Membership", Legends = T, bground=0.1, Cols = c("aquamarine4", "#D9541A")) {
+  # This takes the output from the communityDetection function and plots them on the medial wall (since we're interested in medial now)
+  # type is the name of the column to plot
+  if (Hemi == "R") {
+    # "Medial Right"
+    oneHemi <- Data[grep("R", Data$Hemisphere), ] # from the ROIs
+    oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
+    medialHemi <- oneHemi[grep("Medial", oneHemi$Medial), ]
+    medialHemi$y <- medialHemi$y * -1
+    oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
+    oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
+    medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
+    medialHemi_all$y <- medialHemi_all$y * -1
+    ggplot() + 
+      geom_point(data = medialHemi, aes_string(x="y", y="z", color = type), show.legend=Legends) +
+      geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=bground) +
+      scale_color_gradient(low = Cols[1], high = Cols[2]) +
+      theme_blank() 
+  } else if (Hemi == "L") {
+    # "Medial Left"
+    oneHemi <- Data[grep("L", Data$Hemisphere), ]
+    oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
+    medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
+    oneHemi_all <- labelCoords_vertex[grep("L",labelCoords_vertex$Hemisphere), ] # whole surface
+    oneHemi_all$Medial <- ifelse(oneHemi_all$x > -20, "Medial", "Other")
+    medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
+    ggplot() + 
+      geom_point(data = medialHemi, aes_string(x="y", y="z", color = type), show.legend=Legends) +
+      geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=bground) +
+      scale_color_gradient(low = Cols[1], high = Cols[2]) +
+      theme_blank() 
+  }
+}
+
+## get ROI coords & index
+# The point here is to reduce the summary dframes from community detection to show only ROIs
+# Should work for extracting any label-indexed dframe though
+# I wanted to also get the index in case I want to extract specific rows from parcel/vertex coord dframes
+getCoords <- function(Labels = DMN_labels, Coords = labelCoords_parcel, TimeSeries = FALSE){
+
+  indx <- numeric()
+
+  # If you want to select time series from raw data
+  if (TimeSeries == TRUE) {
+
+    for (ROI in Labels) {
+      indx <- c(indx, grep(ROI, rownames(Coords)))
+    }
+
+  } else { # for the summary output of the community detection output
+
+    for (ROI in Labels) {
+      indx <- c(indx, grep(ROI, Coords$Label))
+    }
+
+  }
+
+  results <- list()
+  results$Index <- indx
+  results$Coords <- Coords[indx, ]
+
+  return(results)
+
+}
+
+# eigen value community detection
+eigenVals <- function(Data = binnedCommunities_p$First) {
+
+  # This will produce a vector of values, ready to be plotted
+  tempGraph <- graph_from_adjacency_matrix(Data$TransfMatrix$tanhZ, mode = "undirected", weighted = T)
+  tempGraph <- laplacian_matrix(tempGraph, normalized=T)
+  tempGraph <- eigen(tempGraph)
+  f.vec <- length(tempGraph$values) - 1
+  tempGraph$binarized <-  as.factor(ifelse(tempGraph$vectors[,f.vec] > 0, 1, 0)) # binarized Fiedler Vector
+
+  return(tempGraph)
+
+}
+
+# Attempt at setting up data for confusion matrices and Jaccard index calculations
+confusionMatrix <- function(partition1 = parcelCommunities[[1]]$Membership, partition2 = parcelCommunities[[1]]$FiedlerBinary) {
+
+  # Divide partitions to evaluate
+  # Usually 2 will be fiedler
+
+  # Check if any partition has 0s (since I binarize the Fiedler vector)
+  if (0 %in% partition1) {
+
+    partition1[grep(0, partition1)] <- 1
+    partition1[grep(1, partition1)] <- 2
+
+  }
+
+  if (0 %in% partition2) {
+
+    partition2[grep(1, partition2)] <- 2   
+    partition2[grep(0, partition2)] <- 1
+
+  }
+
+  # Community sizes
+  commSizes1 <- table(partition1)
+  commSizes2 <- table(partition2)
+
+  # Number of communities per partition
+  nComms1 <- length(commSizes1)
+  nComms2 <- length(commSizes2)
+
+  # Number of vertices
+  n <- length(partition1)
+
+  # Putting together elements of the confusion matrix
+  confMatrix <- matrix(nrow = nComms1,
+                       ncol = nComms2)
+
+  for (i in as.numeric(case.names(commSizes1))) {
+
+    # Vertices belonging to community qX of partition X
+    tempComm1 <- partition1 == i
+
+    for (j in as.numeric(case.names(commSizes2))) {
+
+      # Vertices belonging to community qY of partition Y
+      tempComm2 <- partition2 == j
+
+      # Populate matrix
+      confMatrix[i,j] <- sum(tempComm1 & tempComm2)
+
+    }
+  }
+
+  if (sum(confMatrix) != n) {warning('Sum of the confusion matrix is not equal to number of vertices')}
+
+  return(confMatrix)
+
+}
+
+# Permutation for 2 groups
+permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){
+
+  # prep data
+  summaryPerm <- list()
+  lOne <- length(group1)
+  lTwo <- length(group2)
+  bigSample <- c(group1,group2)
+
+  if (paired == FALSE) {
+
+    for (i in 1:nPerms){
+
+      # relabel samples
+      tempBig <- sample(bigSample)
+      tempOne <- tempBig[1:lOne]
+      tempTwo <- tempBig[(lOne+1):length(bigSample)]
+
+      # stats
+      tempDiffs <- statType(tempOne,na.rm=T) - statType(tempTwo,na.rm=T)
+      summaryPerm$jointDist[i] <- tempDiffs # statType(tempDiffs, na.rm = T)
+
+    }
+
+  } else {
+
+    for (i in 1:nPerms){
+
+      # shift labels in a pairwise fashion
+      tempDiffs <- statType((-1)^rbinom(lOne,1,0.5) * (group1 - group2))
+      summaryPerm$jointDist[i] <- tempDiffs
+
+    }
+
+  }
+
+  # get the observed difference
+  diffs <- statType(group1,na.rm=T) - statType(group2,na.rm=T)
+  observedAbs <- abs(diffs) # maybe leave it as means here
+  observed <- diffs
+  summaryPerm$Pval <- 2 * (1 - ecdf(summaryPerm$jointDist)(observedAbs))
+  if (length(unique(abs(summaryPerm$jointDist))) == 1) {summaryPerm$Pval <- 1} # if the difference is always the same, then p = 1
+  summaryPerm$Observed <- observed
+
+  return(summaryPerm)
+
+}
+
+# Non-parametric Bootstrap for a single group
+bootstrap <- function(group = 1, statType = mean, B = 5000){
+
+  # prep param
+  bootStats <- rep(0,B)
+
+  # iterate
+  for(b in 1:B){
+
+    # wait group
+    x <- sample(group,length(group),replace=T)  
+    bootStats[b] <- statType(x,na.rm = T)
+
+  }
+
+  return(bootStats)
+
+}
+
+# number of times a node changes affiliation in a time series
+flexibility <- function(Data = cbind(1:10, 6:15)) {
+  # Calculation of flexibility based on Garcia et al., 2018  
+  # This function takes in a data frame or matrix in which columns are the community affiliation 
+  # It needs at least 2 colums, although it's pointless for that
+
+  # How many jumps can there be?
+  nJumps <- dim(Data)[2] - 1
+
+  # Matrix to store jumps
+  jumpCount <- matrix(nrow = dim(Data)[1], ncol = nJumps)
+
+  # For each transition, get the which nodes changed affiliation
+  for (jump in seq(nJumps)) {
+
+    jumpCount[, jump] <- Data[, jump] != Data[, jump + 1]
+
+  }
+
+  # How many times did every node jump?
+  totalJumps <- rowSums(jumpCount)
+
+  # Calculate the flexibility per node
+  flexibility <- totalJumps / nJumps
+
+  return(flexibility)
+
+}
+
+# Sliding window
+slidingWindow <- function(subjTS = ROI_timeSeries[[1]], mins = 15, jump = 1, Spectral = T, Modularity = F, ROIs = c("_7m_", vmPFC_labels)) {
+  # This is a fairly specific function. It takes the time series from a participant and preps/runs community detection at each specified time window. 
+  # Returns the summaries for each window (based on communityDetection function)
+  # The selection of a window size is based on the fact that a TR = 0.720s and an hour is 5000 TRs (HCP-based)
+  # Since each subject has a different amount of time points, and all are slightly under 1 hr, I chose to round down the number of window moves to avoid unevenness
+  # 
+  # Parameter definitions:
+  #   
+  #   subjTS: Subject time series. Note: if you want to look at more than vmpfc and 7m, add a parameter for the labels that can be passed to the community detection function
+  # 
+  #   mins: Size of the window that will slide through the data.
+  #   
+  #   jump: Steps (in mins) advanced per slide
+  #   
+  #   Spectral: Whether to compute spectral partitioning as well. Takes significantly longer, but might be more useful for bisections
+  #
+  # Right now this takes ~27 mins per subject to run. Think of ways to improve that.
+
+  # Adapted so it works with the output from getCoords
+  # One wouldn't really apply a full-brain analysis of this sort anyways, too computationally intensive
+  indx <- subjTS$Index
+  subjTS <- subjTS$Coords
+
+  # Window sizing (length)
+  # Think about incorporating custom TRs
+  TS <- dim(subjTS)[2] # time series for the subject
+  WS <- seq(834 * (mins/10)) # window from the first TR up to 834 (~10 mins) times the desired multiplier
+  jump <- 84 * jump # 84 ~ 1 min, times the number of mins that the window moves
+  nJumps <- floor((TS - length(WS)) / jump) # number of jumps to be performed, based on the selected parameters
+
+  ##------- using lapply
+  winData <- mclapply(seq(nJumps), function(x) subjTS[,WS+(jump*(x-1))])
+  commTS <- mclapply(winData, communityDetection, ROIS = "None", Type = "vertex", thresh = T, extras = F)
+  return(commTS)
+
+}
+
+# compare sliding window data to overall communities
+slideCompare <- function(subjData = slideCommunities[[1]], template = vmpfc7mCommunities[[1]], func = "RI", comm = "Spectral") {
+  # This function compares the community partition from each window slide to the one derived from the whole data set
+  # 
+  # Parameter definitions:
+  #   
+  #   subjData: A participant's output from slideCommunities
+  #   
+  #   template: The partition from the whole time series
+  # 
+  #   func: Which function to use for comparing ("RI" for adjusted RI, "VI" for variation of information)
+  # 
+  #   comm: The subject data might contain modularity and spectral partitions. Choose which to use.
+
+  # For storing RIs or VIs
+  tempComparison <- numeric()
+
+  # How many jumps does the original data contain?
+  nJumps <- length(subjData)
+
+  # This loop is technically backwards. I should technically divide by function, then partition method, and then run the window comparisons
+  # It's still really fast, so I won't worry.
+  for (Win in seq(nJumps)) {
+    if (comm == "Modularity") {
+      if (func == "RI") {
+        tempComparison[Win] <- arandi(subjData[[Win]]$Membership, template$Membership, adjust = T)
+      } else if (func == "VI") {
+        tempComparison[Win] <- vi.dist(subjData[[Win]]$Membership, template$Membership)
+      }
+    } else if (comm == "Spectral") {
+      if (func == "RI") {
+        tempComparison[Win] <- arandi(subjData[[Win]]$FiedlerBinary, template$FiedlerBinary, adjust = T)
+      } else if (func == "VI") {
+        tempComparison[Win] <- vi.dist(subjData[[Win]]$FiedlerBinary, template$FiedlerBinary)
+      }
+    }
+  }
+
+  return(tempComparison)
+
+}
+
+# Ensure that all spectral communities associated with 7m (i.e. DMN) have the same label value of 1 
+evenSpectral <- function(Data = slideCommunities[[1]][[7]]) {
+
+  # Get only the values for 7m
+  shortData <- Data[grep("_7m_", Data$Label), ]
+
+  # Get 7m's most probable affiliation
+  affil <- mean(as.numeric(shortData$FiedlerBinary)-1)
+
+  # If it is close to 1, then invert the labeling. 
+  # Note: This has no effect on RI or VI, since they are insensitive to actual labeling
+  # This is for visualization purposes only
+  if (affil < 0.5) {
+
+    UD <- as.numeric(Data$FiedlerBinary) - 1
+    Data$FiedlerBinary <- as.factor((UD - 1)^2)
+    Data$FiedlerVec <- Data$FiedlerVec * -1
+
+  }
+
+  return(Data)
+
+}
+
+# Create a vector ready to be used for HCP data (32k CIFTI surface)
+# The input should be the summary from community partitioning
+# Once this is created, go to the terminal and input something like this
+# wb_command -cifti-convert -from-text dataforCifti.txt 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii testCifti.dscalar.nii
+# Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
+HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307"){
+
+  nVertices <- 59412
+  tempVec <- rep(-1, nVertices)
+  temp <- grep(MOI, colnames(Data))
+  tempVec[Data$Vertex] <- Data[[temp]]
+  write.table(file = paste(SubjID,"_",MOI,'_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")
+
+}
+
+# Perform pairwise comparisons of clustering outcomes on all subjects
+comparePartitions <- function(Data = dmnval7mCommunities, MOI = "FiedlerBinary", Index = "VI", nSubjects = nSubj, subjNames = subjList) {
+  # This function will compare the community partitions from all subjects and create a 'comparison matrix' for every pairwise combination of subjects
+  # Alternatively, if a second MOI is added 
+  # Inputs
+  # 
+  # Data: the list of summaries produced by the script
+  # 
+  # MOI: measure of interest (usually the binarized Fiedler vector). If a vector, compares across algorithms per subject
+  # 
+  # Index: VI for variation of information, RI for the adjusted rand index, Cor for a Pearson correlation
+
+  # Get the column position of the MOI(s)
+  Columns <- colnames(Data[[1]])
+  indx <- as.numeric(Columns %in% MOI)
+  MOI_indx <- which(indx==1)
+
+  if (length(MOI_indx) < 2) {
+    # Combine the measures of interest
+    allVecs <- do.call(cbind, lapply(Data, "[[", MOI))
+
+    # Create empty matrix
+    indexMatrix <- matrix(data = NA, nrow = nSubjects, ncol = nSubjects)
+    dimnames(indexMatrix) <- list(subjNames, subjNames)
+
+    # Run every pairwise comparison with the index of interest on the measure of interest
+    if (Index == "VI") {
+      for (subj in seq(nSubjects)) {
+        for (subj2 in seq(nSubjects)) {
+          indexMatrix[subj,subj2] <- vi.dist(allVecs[, subj], allVecs[, subj2])
+        }
+      }
+    } else if (Index == "RI") {
+      for (subj in seq(nSubjects)) {
+        for (subj2 in seq(nSubjects)) {
+          indexMatrix[subj,subj2] <- arandi(allVecs[, subj], allVecs[, subj2], adjust = T)
+        }
+      }
+    } else if (Index == "Cor") {
+      for (subj in seq(nSubjects)) {
+        for (subj2 in seq(nSubjects)) {
+          indexMatrix[subj,subj2] <- cor(allVecs[, subj], allVecs[, subj2])
+        }
+      }
+    }
+  } else {
+    indexMatrix <- data.frame(SubjID = as.character(subjList),
+                              Index = rep(0, nSubjects))
+    # Run every pairwise comparison with the index of interest on the measure of interest
+    if (Index == "VI") {
+      for (subj in seq(nSubjects)) {
+        indexMatrix$Index[subj] <- vi.dist(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
+      }
+    } else if (Index == "RI") {
+      for (subj in seq(nSubjects)) {
+        indexMatrix$Index[subj] <- arandi(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]], adjust = T)
+      }
+    } else if (Index == "Cor") {
+      for (subj in seq(nSubjects)) {
+        indexMatrix$Index[subj] <- cor(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
+      }
+    }
+  }
+
+  return(indexMatrix)
+
+}
+
+# Generate a matrix with submatrices of 1s of a given size along the diagonal
+# Useful to extract specific portions of data from a similarity matrix
+diagBlocks <- function(dims = 20, sqSize = 4) {
+  div <- dims %/% sqSize
+  finalMatrix<-matrix(0,nrow=dims,ncol=dims)
+  index <- 1
+  for(k in seq(div)){
+    finalMatrix[index:(index + (sqSize-1)),index:(index + (sqSize-1))] <- 1
+    index<-index + sqSize
+  }
+  finalMatrix <- finalMatrix == 1
+  finalMatrix
+}
+
+```
+
 Results {.unnumbered}
 ========================================
+``` {r Partition comparison: all brain example, fig.cap = "Template brain.", fig.width = 4, fig.height = 4, echo = FALSE}
+# Load data
+setwd('../Summary/')
+temp <- list.files()
+subjList <- sapply(temp, substring, first=1, last=6)
+Summaries <- lapply(temp, read.csv)
+nSubj <- length(Summaries)
+
+plotCommunities(Summaries[[1]], Hemi = "L", Legends = F, type = "FiedlerBinary")
+
+```
 
@@
 See http://www.jneurosci.org/content/preparing-manuscript
+
+**Meta-analysis**
+To perform the first step, I used data from a metanalysis that gathered peak brain coordinates of activity from studies of valuation (n = 27 studies) and DMN (n = 77).
+These are the surviving areas post-statistical thresholding from each study.
+I analyzed this data by mapping the peak cortical coordinates to an atlas of the human cortical surface (Glasser et al., 2016).
+This produced a list of standardized parcels that were reported on each study.
+The advantage of utilizing this atlas was threefold: first, it reduced the number of functional vertices from 60,000 (cortical surface vertices) to 360 (cortical parcels).
+Second, it standardizes the vertices from the first to the second stage of my study.
+Finally, it allowed me to project each area on a brain space without much clutter.
+Since each vertex is embedded with topographical information, and since functional topography is essential to my question, I mostly project my results onto brain space.
+
+I thus generated two undirected, loop-less, weighted graphs in which each vertex was a brain parcel, and edges correspond to the number of times each pair of them co-occurred across studies.
+Since different decision tasks use different sensory modalities, and since sensory areas get sometimes reported as unrelated peak coordinates in DMN studies, I bootstrapped the co- occurrences across studies and removed edges whose co-occurrences lied below the 90th percentile.
+Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded.
+With these graphs set up, I computed the strength and betweenness centrality in order to capture each parcel’s centrality in the valuation and DMN literatures separately.
+
+In order to select of regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, I first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution.
+Next, I took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus my main target for dissociation).
+
+**Whole Brain Parcellated connectivity**
+For the second step, in order to actually quantify the intrinsic connectivity of these ROIs in the brain, I used data from the Human Connectome Project.
+Specifically, I acquired resting-state fMRI activity from 3 subjects, all of whom have been preprocessed according to industry standards to allow for group-level comparisons (Tobyne et al., 2017).
+Each data set contained around 1 hour of signals represented as 4800 time points, and each subject contained 60,000 vertices.
+I parcellated each subject’s brain according to the atlas mentioned above, so that each parcel contained the mean time series from its vertices, and correlated the mean time series among all parcels (Pearson).
+This produced a weighted adjacency matrix for each subject, where each of the 360 parcels is a vertex, and edges the correlations among all of them.
+Next, I took the exponential of the correlations, Fisher transformed them (i.e.
+tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant (FDR < 0.05).
+Again, I quantified each parcel’s strength and betweenness, averaged them across subjects, and examined whether any of the ROIs showed uniquely high centralities.
+For this, I performed a permutation comparing the mean strength between the ROIs and the rest of the brain for each participant.
+
+For the main goal of this section, I maximized the strength-based modularity metric as a community detection method (fast-greedy algorithm), so that I could check if all the DMN ROIs from the previous section were affiliated with the same community.
+While this measure has resolution problems at large and low scales (Fortunato & Hric, 2016), if it does extract a close match to standard DMN networks, it could act as a good method for the final stage of the project (but see Peel, Larremore, and Clauset 2017 for issues with ground-truth).
+Even though this analysis is mainly geared to confirm that these ROIs are jointly captured, this step also let me examine whether some of the ROIs could be subdivided into DMN and non-DMN regions at this level of granularity.
+
+In order to evaluate the validity of the modularity-based communities, I also clustered the brain by means of spectral partitioning.
+Specifically, I took the Fiedler vector (eigenvector associated with the second lowest eigenvalue) from each participant’s normalized Laplacian matrix, and divided the brain by the sign of the eigenvector values.
+This analysis served the additional purpose of more strictly dividing the brain into DMN and non-DMN communities.
+Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).
+Finally, to quantify the agreement of these community methods, I computed both the adjusted rand index and variation of information distance (normalized by the logarithm of the number of vertices, 360 in this case) between them per subject.
+The adjusted rand index denotes the proportion of vertices that coincide in affiliation across partitions, and compares this score to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions.
+On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions.
+While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case.
+Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).
+Importantly, due to having just 3 subjects, I abstained from performing formal statistics on the descriptive measures that I show.
+
+**Within-ROI Connectivity**
+For the third stage, I “zoomed in” each subject’s brain by computing the correlation among all of the surface-vertices contained within each ROI across all the ROIs, and applied the same correction as in step two.
+That means that the vertices became smaller functional brain units that are connected by the same type of edge (i.e.
+adjusted correlations) as in step two.
+This time, I only focused on partitioning the brain through modularity and spectral partitioning to see if the ROIs can be subdivided at this finer level of resolution.
+It is worth noting that while communities across subjects should be similar, the idiosyncrasies explained previously (i.e.
+cortical folding) should produce noticeable differences as well.
+
+This time I added two new areas to the ROIs: 7m, as this area had unique relevance in DMN when compared to valuation (evidenced by its connectivity strength in DMN and chi- squared permutation in the meta-analysis, see results), and V1, as this visual processing area should not be affiliated with DMN.
+These regions thus acted as dual reference points, such that the community affiliated with 7m should denote DMN, while V1 indicated non-DMN.
+As before, I tested the validity of the partitions using the adjusted rand index and normalized variation of information.
+However, this time I also used the rand index to quantify the community correspondence between subjects.
+Specifically, I divided each subject’s spectrally- partitioned brain into PCC and mPFC topographical zones (posterior and frontal brain, respectively), and computed the index of each region between subjects.
+The high cross-subject heterogeneity of cortical folding of mPFC should produce relatively low rand indices, while the more homogeneous PCC should display the opposite pattern.
+This analysis was meant to tackle the subject-specific limitations discussed above.
+The final patterns were inspected visually.
 

### 2018-08-16 Manuscript/Manuscript.tex
Small edits

@@
 \begin{abstract}
-Valuation effects are consistently observed in medial prefrontal and
-posterior cingulate cortex (mPFC and PCC). The spatial extent of these
-effects is mostly indistinguishable from the default mode network (DMN)
-in existing meta-analyses. However, little is known about how valuation
-effects fit within the broader functional architecture of mPFC and PCC,
-or whether that architecture is consistent or idiosyncratic across
-individuals. Here we complement a meta-analysis with fMRI-based graph
-theoretic approaches to subdivide mPFC and PCC at the single-subject
-level. Our results suggest the functional topography of mPFC has
-substantial variability across individuals. This highlights the
-potential usefulness of estimating brain effects at the individual level
-in this region, and points to limitations of aggregative methods such as
-coordinate-based meta-analysis in determining whether valuation and DMN
-effects emerge from common or separable brain systems. Our approach
-shows promise in addressing this issue through future manipulations of
-valuation.
+(Current count: 153) Valuation effects are consistently observed in
+medial prefrontal and posterior cingulate cortex (mPFC and PCC). The
+spatial extent of these effects is mostly indistinguishable from the
+default mode network (DMN) in existing meta-analyses. However, little is
+known about how valuation effects fit within the broader functional
+architecture of mPFC and PCC, or whether that architecture is consistent
+or idiosyncratic across individuals. Here we complement a meta-analysis
+with fMRI-based graph theoretic approaches to subdivide mPFC and PCC at
+the single-subject level. Our results suggest the functional topography
+of mPFC has substantial variability across individuals. This highlights
+the potential usefulness of estimating brain effects at the individual
+level in this region, and points to limitations of aggregative methods
+such as coordinate-based meta-analysis in determining whether valuation
+and DMN effects emerge from common or separable brain systems. Our
+approach shows promise in addressing this issue through future
+manipulations of valuation.
 \end{abstract}
@@
 
-One of the main goals of human cognitive neuroscience is to be able to
-prescribe function to brain regions, either in isolation or in their
-communication with others. Among general regions of the brain, the
-medial prefrontal cortex (mPFC, located in the midline frontal portion
-of the brain) has been suggested to subserve the cognitive abilities
-that differentiate humans from other animals (Barbas \& Garcia-Cabezas,
-2016). Specifically, this region has been related to a variety of
-functions, including decision making (Bartra, McGuire, \& Kable, 2013),
-memory encoding (Shacter, Addis, \& Buckner, 2007), and default mode
-deactivation (DMN) (Yeo et al., 2011). While much has been discovered
-about this area in primates (Barbas \& Garcia-Cabezas, 2016), the lack
-of direct measurements of neuronal activity makes this a tough area to
-record in humans, one that nowadays relies mostly on functional MRI
-(fMRI). Unfortunately, the mPFC is especially challenging to image, as
-the oxygen-related signal recorded by fMRI is contaminated by the oxygen
-in the sinuses (Logothetis, 2008). In addition, this area is subject to
-more idiosyncratic cortical folding than any other region (Zilles,
-Palomero- Gallagher, \& Amunts, 2013), thus adding a level of complexity
-to the generalizable dissection of topographic functional roles within
-mPFC.
+(current, 676 words. Aim for 650)
 
-Studies of valuation have consistently shown functional overlap with
-DMN. Recent meta-analytic work has attempted to distinguish the brain
-areas belonging to each by examining the locus of peak activity across
-studies related to the behavioral features mentioned above (Bartra et
-al., 2013; Acikalin, Gorgolewski, \& Poldrack, 2017). While this
-approach offers valuable information, it is subject to the quality of
-imaging in each study, as well as their corresponding differences in
-tasks used to examine choice. In addition, recent findings suggest that
-the functional topology of the brain is better understood by accounting
-for organizational idosyncrasies (Braga and Buckner, 2018; Yeo et al.,
-2018, Gordon et al., 2017, Gratton\ldots{}).
+The medial prefrontal cortex (mPFC) has been suggested to subserve many
+of the cognitive abilities that differentiate humans from other animals
+(Barbas \& Garcia-Cabezas, 2016). Specifically, this region has been
+related to decision making (Bartra, McGuire, \& Kable, 2013), memory
+encoding (Shacter, Addis, \& Buckner, 2007), and default mode
+deactivation (DMN) (Yeo et al., 2011), among ohters. While much has been
+discovered about this area in primates (Barbas \& Garcia-Cabezas, 2016),
+the lack of direct measurements of neuronal activity makes this a tough
+area to record in humans, one that nowadays relies mostly on functional
+MRI (fMRI). Unfortunately, the mPFC is especially challenging to image,
+as the oxygen-related signal recorded by fMRI is contaminated by the
+oxygen in the sinuses (Logothetis, 2008). In addition, this area is
+subject to more idiosyncratic cortical folding than any other region
+(Zilles, Palomero- Gallagher, \& Amunts, 2013), thus adding a level of
+complexity to the generalizable dissection of topographic functional
+roles within mPFC.
+
+Previous meta analytic studies have provided important insights on the
+psychological phenomena attributed to mPFC subregions. For example, de
+la Vega et al. (2016) found subdivisions of mPFC and MCC that are
+significantly tied to decision making in the literature. In particular,
+they show that more ventral regions are more tightly associated with
+reward and fear. However, this pattern overlaps with their finding that
+vmPFC also coactivates with DMN regions, and find no topographical
+distinction between these phenomena. Similarly, the results from Bartra
+et al and Laird et al show that this region can't be subdivided into DMN
+vs subjective value (acikalin, chris, russ). However, meta analyses rely
+on peaks often derived from group-averaged data. Recent work has
+prescribed relevance to the analysis of single subjects in fMRI. Yeo et
+al (2018) propose the use of individualized topologies when identifying
+functional networks. Gordon et al identify important idiosincrasies in
+oversampled subjects. Similarly, Braga and Buckner show that finer
+subdivisions of the DMN are possible when looking at each subject
+independently. This opens up the possibility that distinctions between
+DMN and subjective value are possible at this finer level of resolution,
+but would otherwise be masked in meta analytic work.
+
+Braga \& Buckner's work is particularly informative when it comes to
+subdividing DMN. However, the seed-based functional connectivity
+analysis is sensitive to the selection of the seed. A natural next step
+would be to recruit all possible patterns of covariation within this
+network. A popular alternative is to rely on graph theoretic methods,
+which provide a characterization of networks that organically fits brain
+dynamics (provides an organic avenue to understand brain dynamics?), and
+thus permits the consideration of the full covariance structure of brain
+networks. (ADV \& Tal somewhere here).
 
@@
 mentioned above, there is potential value in combining complementary
-strengths from both approaches. While my lab is primarily interested in
-the portion of mPFC dedicated to decision making, in order to bypass the
-heterogeneity in behavioral tasks, it might be best to disentangle the
-mPFC by focusing first on which of its sub-regions belong to
-resting-state DMN, and which do not. The advantage lies in that (1) all
-resting state scans are performed equally (the subject lies in the
-scanner with their eyes open), and (2) there is a high quality resource
-of resting state data provided by the Human Connectome Project. Focusing
-on resting state data has been successful in determining a number of
-neural phenomena, including disentangling auditory and visual attention
-areas (Tobyne, Osher, Michalka, \& Somers, 2017).
+strengths from both approaches. Focusing on resting state data has been
+successful in determining a number of neural phenomena, including
+disentangling auditory and visual attention areas (Tobyne, Osher,
+Michalka, \& Somers, 2017).
 
-This approach opens an opportunity to examine brain dynamics. For
-example, a region's function might depend on its connectivity at any
-given time with one brain community or another. An ever-growing trend in
-human neuroimaging has been to apply network statistics to tackle these
-functional challenges. One great advantage of network science is the
-ability to characterize connectivity in a way that allows for
-comparisons among individuals in a meaningful way (Garcia, Ashourvan,
-Muldoon, Vettel, \& Bassett, 2018), thus letting us address the folding
-idiosyncrasies mentioned above. Therefore, I propose to use some of the
-statistics that we have learned in class to estimate intrinsic
-functional subdivisions of the mPFC at the individual subject level.
-Particularly, I would like to distinguish communities related to DMN
-from non-DMN, so that we can generate more informed topographic targets
-for future studies of decision making.
-
-In this study, I try to address my question at 3 levels of granularity:
-1) across the literature (meta-analysis), selecting a number of regions
-of interest (ROI) that show significant overlap and specificity between
-DMN and decision making; 2) full-brain connectivity of actual fMRI data,
-using a pre-specified brain atlas; and 3) characterizing the
-connectivity of surface vertices (small units of function that contain
-oxygen-dependent neural information across time) for the regions
-selected in step one. I performed the last two steps at an individual
-subject level for 3 subjects, hoping to find some commonalities among
-them. In this way, I attempted to extract functional topographical
-information from topological network features.
+One great advantage of network science is the ability to characterize
+connectivity in a way that allows for comparisons among individuals in a
+meaningful way (Garcia, Ashourvan, Muldoon, Vettel, \& Bassett, 2018),
+thus letting us address the idiosyncrasies mentioned above. In this
+study, we aim to subdivide mPFC into subject-specific DMN and non-DMN
+areas, so that we can generate more informed topographic targets for
+future studies of decision making. We address this aim at 3 levels of
+granularity: 1) across the literature (meta-analysis), selecting a
+number of regions of interest (ROI) that show significant overlap and
+specificity between DMN and decision making; 2) full-brain connectivity
+of actual fMRI data, using a pre-specified brain atlas; and 3)
+characterizing the connectivity of surface vertices (small units of
+function that contain oxygen-dependent neural information across time)
+for the regions selected in step one. I performed the last two steps at
+an individual subject level for 3 subjects, hoping to find some
+commonalities among them. In this way, I attempted to extract functional
+topographical information from topological network features.
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/Partition comparison: all brain example-1.pdf}
+\caption{Template brain.}
+\end{figure}
+
 \section*{Discussion}\label{discussion}
 \addcontentsline{toc}{section}{Discussion}
+
+(1500 words max)
 
@@
 
-\section*{Results}\label{results-1}
-\addcontentsline{toc}{section}{Results}
+See \url{http://www.jneurosci.org/content/preparing-manuscript}
 
-Please note that whilst this template provides a preview of the typeset
-manuscript for submission, to help in this preparation, it will not
-necessarily be the final publication layout. For more detailed
-information please see the
-\href{http://www.pnas.org/site/authors/format.xhtml}{PNAS Information
-for Authors}.
+\textbf{Meta-analysis} To perform the first step, I used data from a
+metanalysis that gathered peak brain coordinates of activity from
+studies of valuation (n = 27 studies) and DMN (n = 77). These are the
+surviving areas post-statistical thresholding from each study. I
+analyzed this data by mapping the peak cortical coordinates to an atlas
+of the human cortical surface (Glasser et al., 2016). This produced a
+list of standardized parcels that were reported on each study. The
+advantage of utilizing this atlas was threefold: first, it reduced the
+number of functional vertices from 60,000 (cortical surface vertices) to
+360 (cortical parcels). Second, it standardizes the vertices from the
+first to the second stage of my study. Finally, it allowed me to project
+each area on a brain space without much clutter. Since each vertex is
+embedded with topographical information, and since functional topography
+is essential to my question, I mostly project my results onto brain
+space.
 
-\subsection*{Author Affiliations}\label{author-affiliations}
-\addcontentsline{toc}{subsection}{Author Affiliations}
+I thus generated two undirected, loop-less, weighted graphs in which
+each vertex was a brain parcel, and edges correspond to the number of
+times each pair of them co-occurred across studies. Since different
+decision tasks use different sensory modalities, and since sensory areas
+get sometimes reported as unrelated peak coordinates in DMN studies, I
+bootstrapped the co- occurrences across studies and removed edges whose
+co-occurrences lied below the 90th percentile. Based on this, only edges
+with co-occurrences higher than 8 were preserved, and the remaining
+unconnected vertices (brain regions) were discarded. With these graphs
+set up, I computed the strength and betweenness centrality in order to
+capture each parcel's centrality in the valuation and DMN literatures
+separately.
 
-Include department, institution, and complete address, with the
-ZIP/postal code, for each author. Use lower case letters to match
-authors with institutions, as shown in the example. Authors with an
-ORCID ID may supply this information at submission.
+In order to select of regions of interest (ROI) from mPFC and other
+brain areas that are central to valuation and DMN literatures, I first
+bootstrapped the mean strength for each graph separately, and chose
+areas with strength above the 95th percentile of this distribution.
+Next, I took the intersection of these areas, such that the final ROIs
+were brain regions that overlapped between DMN and valuation in the
+literature (and thus my main target for dissociation).
 
-\subsection*{Submitting Manuscripts}\label{submitting-manuscripts}
-\addcontentsline{toc}{subsection}{Submitting Manuscripts}
+\textbf{Whole Brain Parcellated connectivity} For the second step, in
+order to actually quantify the intrinsic connectivity of these ROIs in
+the brain, I used data from the Human Connectome Project. Specifically,
+I acquired resting-state fMRI activity from 3 subjects, all of whom have
+been preprocessed according to industry standards to allow for
+group-level comparisons (Tobyne et al., 2017). Each data set contained
+around 1 hour of signals represented as 4800 time points, and each
+subject contained 60,000 vertices. I parcellated each subject's brain
+according to the atlas mentioned above, so that each parcel contained
+the mean time series from its vertices, and correlated the mean time
+series among all parcels (Pearson). This produced a weighted adjacency
+matrix for each subject, where each of the 360 parcels is a vertex, and
+edges the correlations among all of them. Next, I took the exponential
+of the correlations, Fisher transformed them (i.e.~tanh) so that all
+weights were positive while maintaining the shape of the original
+correlation distribution, and retained the edges whose adjusted p-values
+remained significant (FDR \textless{} 0.05). Again, I quantified each
+parcel's strength and betweenness, averaged them across subjects, and
+examined whether any of the ROIs showed uniquely high centralities. For
+this, I performed a permutation comparing the mean strength between the
+ROIs and the rest of the brain for each participant.
 
-All authors must submit their articles at
-\href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you
-are using Overleaf to write your article, you can use the ``Submit to
-PNAS'' option in the top bar of the editor window.
+For the main goal of this section, I maximized the strength-based
+modularity metric as a community detection method (fast-greedy
+algorithm), so that I could check if all the DMN ROIs from the previous
+section were affiliated with the same community. While this measure has
+resolution problems at large and low scales (Fortunato \& Hric, 2016),
+if it does extract a close match to standard DMN networks, it could act
+as a good method for the final stage of the project (but see Peel,
+Larremore, and Clauset 2017 for issues with ground-truth). Even though
+this analysis is mainly geared to confirm that these ROIs are jointly
+captured, this step also let me examine whether some of the ROIs could
+be subdivided into DMN and non-DMN regions at this level of granularity.
 
-\subsection*{Format}\label{format}
-\addcontentsline{toc}{subsection}{Format}
+In order to evaluate the validity of the modularity-based communities, I
+also clustered the brain by means of spectral partitioning.
+Specifically, I took the Fiedler vector (eigenvector associated with the
+second lowest eigenvalue) from each participant's normalized Laplacian
+matrix, and divided the brain by the sign of the eigenvector values.
+This analysis served the additional purpose of more strictly dividing
+the brain into DMN and non-DMN communities. Importantly, given the high
+density of these networks (see results), spectral partitioning was
+unlikely to face the issues associated with its use in sparse networks
+(Fortunato \& Hric, 2016). Finally, to quantify the agreement of these
+community methods, I computed both the adjusted rand index and variation
+of information distance (normalized by the logarithm of the number of
+vertices, 360 in this case) between them per subject. The adjusted rand
+index denotes the proportion of vertices that coincide in affiliation
+across partitions, and compares this score to a baseline given by the
+expectation based on a random vertex assignment for an equal number of
+clusters across partitions. On the other hand, variation of information
+gives a general sense of the amount of information to be gained by the
+complementary community partitioning (Meila, 2007), measured by the
+addition of the conditional entropies per combination of clusters across
+partitions. While the rand index is more easily interpreted, it suffers
+from the assumption that the baseline should have an equal number of
+vertices per cluster across partitions, which is not necessarily the
+case. Therefore, I used variation of information as a more robust
+similarity metric (Fortunato \& Hric, 2016). Importantly, due to having
+just 3 subjects, I abstained from performing formal statistics on the
+descriptive measures that I show.
 
-Many authors find it useful to organize their manuscripts with the
-following order of sections; Title, Author Affiliation, Keywords,
-Abstract, Significance Statement, Results, Discussion, Materials and
-methods, Acknowledgments, and References. Other orders and headings are
-permitted.
+\textbf{Within-ROI Connectivity} For the third stage, I ``zoomed in''
+each subject's brain by computing the correlation among all of the
+surface-vertices contained within each ROI across all the ROIs, and
+applied the same correction as in step two. That means that the vertices
+became smaller functional brain units that are connected by the same
+type of edge (i.e.~adjusted correlations) as in step two. This time, I
+only focused on partitioning the brain through modularity and spectral
+partitioning to see if the ROIs can be subdivided at this finer level of
+resolution. It is worth noting that while communities across subjects
+should be similar, the idiosyncrasies explained previously
+(i.e.~cortical folding) should produce noticeable differences as well.
 
-\subsection*{Manuscript Length}\label{manuscript-length}
-\addcontentsline{toc}{subsection}{Manuscript Length}
+This time I added two new areas to the ROIs: 7m, as this area had unique
+relevance in DMN when compared to valuation (evidenced by its
+connectivity strength in DMN and chi- squared permutation in the
+meta-analysis, see results), and V1, as this visual processing area
+should not be affiliated with DMN. These regions thus acted as dual
+reference points, such that the community affiliated with 7m should
+denote DMN, while V1 indicated non-DMN. As before, I tested the validity
+of the partitions using the adjusted rand index and normalized variation
+of information. However, this time I also used the rand index to
+quantify the community correspondence between subjects. Specifically, I
+divided each subject's spectrally- partitioned brain into PCC and mPFC
+topographical zones (posterior and frontal brain, respectively), and
+computed the index of each region between subjects. The high
+cross-subject heterogeneity of cortical folding of mPFC should produce
+relatively low rand indices, while the more homogeneous PCC should
+display the opposite pattern. This analysis was meant to tackle the
+subject-specific limitations discussed above. The final patterns were
+inspected visually.
 
-PNAS generally uses a two-column format averaging 67 characters,
-including spaces, per line. The maximum length of a Direct Submission
-research article is six pages and a PNAS PLUS research article is ten
-pages including all text, spaces, and the number of characters displaced
-by figures, tables, and equations. When submitting tables, figures,
-and/or equations in addition to text, keep the text for your manuscript
-under 39,000 characters (including spaces) for Direct Submissions and
-72,000 characters (including spaces) for PNAS PLUS.
-
-\subsection*{References}\label{references}
-\addcontentsline{toc}{subsection}{References}
-
-References should be cited in numerical order as they appear in text;
-this will be done automatically via bibtex, e.g. (1) and (2, 3). All
-references, including for the SI, should be included in the main
-manuscript file. References appearing in both sections should not be
-duplicated. SI references included in tables should be included with the
-main reference section.
-
-\subsection*{Data Archival}\label{data-archival}
-\addcontentsline{toc}{subsection}{Data Archival}
-
-PNAS must be able to archive the data essential to a published article.
-Where such archiving is not possible, deposition of data in public
-databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata,
-and others outlined in the Information for Authors, is acceptable.
-
-\subsection*{Language-Editing Services}\label{language-editing-services}
-\addcontentsline{toc}{subsection}{Language-Editing Services}
-
-Prior to submission, authors who believe their manuscripts would benefit
-from professional editing are encouraged to use a language-editing
-service (see list at www.pnas.org/site/authors/language-editing.xhtml).
-PNAS does not take responsibility for or endorse these services, and
-their use has no bearing on acceptance of a manuscript for publication.
-
-\begin{figure}
-\centering
-\includegraphics{frog.png}
-\caption{Placeholder image of a frog with a long example caption to show
-justification setting.{}}
-\end{figure}
-
-\subsection*{Digital Figures}\label{sec:figures}
-\addcontentsline{toc}{subsection}{Digital Figures}
-
-Only TIFF, EPS, and high-resolution PDF for Mac or PC are allowed for
-figures that will appear in the main text, and images must be final
-size. Authors may submit U3D or PRC files for 3D images; these must be
-accompanied by 2D representations in TIFF, EPS, or high-resolution PDF
-format. Color images must be in RGB (red, green, blue) mode. Include the
-font files for any text.
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
 
@@
 
-\hypertarget{refs}{}
-\hypertarget{ref-belkin2002using}{}
-1. Belkin M, Niyogi P (2002) Using manifold stucture for partially
-labeled classification. \emph{Advances in Neural Information Processing
-Systems}, pp 929--936.
-
-\hypertarget{ref-berard1994embedding}{}
-2. Bérard P, Besson G, Gallot S (1994) Embedding riemannian manifolds by
-their heat kernel. \emph{Geometric \& Functional Analysis GAFA}
-4(4):373--398.
-
-\hypertarget{ref-coifman2005geometric}{}
-3. Coifman RR, et al. (2005) Geometric diffusions as a tool for harmonic
-analysis and structure definition of data: Diffusion maps.
-\emph{Proceedings of the National Academy of Sciences of the United
-States of America} 102(21):7426--7431.
-
 % Bibliography

### 2018-08-17 Manuscript/Manuscript.Rmd
More work on manuscript

@@
 
-Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007)
+From what we talked:
+
+1. Disentangling mPFC (unsuccessful meta-analyses)
+2. Trouble imaging this area
+3. Network stats in the individual as a useful method
 
 The medial prefrontal cortex (mPFC) has been suggested to subserve many of the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016).
-Specifically, this region has been related to decision making (Bartra, McGuire, & Kable, 2013), memory encoding (Shacter, Addis, & Buckner, 2007), and default mode deactivation (DMN) (Yeo et al., 2011), among ohters.
-While much has been discovered about this area in primates (Barbas & Garcia-Cabezas, 2016), the lack of direct measurements of neuronal activity makes this a tough area to record in humans, one that nowadays relies mostly on functional MRI (fMRI).
-Unfortunately, the mPFC is especially challenging to image, as the oxygen-related signal recorded by fMRI is contaminated by the oxygen in the sinuses (Logothetis, 2008).
-In addition, this area is subject to more idiosyncratic cortical folding than any other region (Zilles, Palomero- Gallagher, & Amunts, 2013), thus adding a level of complexity to the generalizable dissection of topographic functional roles within mPFC.
-
-Previous meta analytic studies have provided important insights on the psychological phenomena attributed to mPFC subregions.
+Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007).
+However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
+This has prompted the question of whether these distinct phenomena are part of a common underlying brain system, or they can be dissociable.
+
+Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions.
 For example, de la Vega et al.
-(2016) found subdivisions of mPFC and MCC that are significantly tied to decision making in the literature.
-In particular, they show that more ventral regions are more tightly associated with reward and fear.
-However, this pattern overlaps with their finding that vmPFC also coactivates with DMN regions, and find no topographical distinction between these phenomena.
-Similarly, the results from Bartra et al and Laird et al show that this region can't be subdivided into DMN vs subjective value (acikalin, chris, russ).
-However, meta analyses rely on peaks often derived from group-averaged data.
-Recent work has prescribed relevance to the analysis of single subjects in fMRI.
-Yeo et al (2018) propose the use of individualized topologies when identifying functional networks.
-Gordon et al identify important idiosincrasies in oversampled subjects.
-Similarly, Braga and Buckner show that finer subdivisions of the DMN are possible when looking at each subject independently.
-This opens up the possibility that distinctions between DMN and subjective value are possible at this finer level of resolution, but would otherwise be masked in meta analytic work.
-
-Braga & Buckner's work is particularly informative when it comes to subdividing DMN.
-However, the seed-based functional connectivity analysis is sensitive to the selection of the seed.
+(2016) found subdivisions of mPFC and MCC that are significantly tied to decision making across the literature.
+In particular, they show that more ventral mPFC regions are increasingly associated with reward and fear.
+However, they also found that vmPFC coactivates with DMN regions, with no topographical distinction between this network and valuation.
+Focused work at disentangling DMN from subjective value also failed to separate these systems (Acikalin, Gorgolewski, & Poldrack, 2017).
+While informative, these meta-analyses relied on peak coordinates derived from group-averaged data.
+It has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
+Aiming to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
+Yeo et al (2018) have effectively incorporated individualized topologies for generating distributed functional networks.
+Gordon et al identify important idiosincrasies in oversampled subjects that are blurred in agglomerative analyses.
+The trend of individualized analyses has led to finer subdivisions of the DMN (Braga & Buckner, 2018).
+It is thus possible that the indisitinguishable extent of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
+
+Given the shortcomings of study-specific and cross-study analyses, there is potential value in combining complementary strengths from both approaches.
+Focusing on resting state data has been successful in determining a number of neural phenomena, including disentangling auditory and visual attention areas (Tobyne, Osher, Michalka, & Somers, 2017).
 A natural next step would be to recruit all possible patterns of covariation within this network.
 A popular alternative is to rely on graph theoretic methods, which provide a characterization of networks that organically fits brain dynamics (provides an organic avenue to understand brain dynamics?), and thus permits the consideration of the full covariance structure of brain networks.
-(ADV & Tal somewhere here).
-
-Given the shortcomings of study-specific and cross-study analyses mentioned above, there is potential value in combining complementary strengths from both approaches.
-Focusing on resting state data has been successful in determining a number of neural phenomena, including disentangling auditory and visual attention areas (Tobyne, Osher, Michalka, & Somers, 2017).
 
@@
 In this study, we aim to subdivide mPFC into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making.
-We address this aim at 3 levels of granularity: 1) across the literature (meta-analysis), selecting a number of regions of interest (ROI) that show significant overlap and specificity between DMN and decision making; 2) full-brain connectivity of actual fMRI data, using a pre-specified brain atlas; and 3) characterizing the connectivity of surface vertices (small units of function that contain oxygen-dependent neural information across time) for the regions selected in step one.
-I performed the last two steps at an individual subject level for 3 subjects, hoping to find some commonalities among them.
-In this way, I attempted to extract functional topographical information from topological network features.
+We address this aim at 3 levels of granularity: 1) across the literature (meta-analysis), selecting a number of regions of interest (ROI) that show significant overlap and specificity between DMN and decision making; and 2) characterizing the connectivity of all surface vertices for these ROIs.
+
+Do these things truly overlap, or are we not looking close enough?
+
+Add Tor's latest papers to the meta analysis
 

### 2018-08-17 Manuscript/Manuscript.Rmd
Backbone of intro more or less in shape?

@@
 
-(current, 676 words. Aim for 650)
-
-From what we talked:
-
-1. Disentangling mPFC (unsuccessful meta-analyses)
-2. Trouble imaging this area
-3. Network stats in the individual as a useful method
+(current, 708 words. Aim for 650)
 
@@
 Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007).
-However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
-This has prompted the question of whether these distinct phenomena are part of a common underlying brain system, or they can be dissociable.
+However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
+This has prompted the question of whether (and to what extent) these two systems can be dissociated.
 
   Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions.
-For example, de la Vega et al.
-(2016) found subdivisions of mPFC and MCC that are significantly tied to decision making across the literature.
-In particular, they show that more ventral mPFC regions are increasingly associated with reward and fear.
-However, they also found that vmPFC coactivates with DMN regions, with no topographical distinction between this network and valuation.
-Focused work at disentangling DMN from subjective value also failed to separate these systems (Acikalin, Gorgolewski, & Poldrack, 2017).
-While informative, these meta-analyses relied on peak coordinates derived from group-averaged data.
+Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009).
+Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, they strongly coactivate with DMN regions across the literature, with no clear topographical distinction (de la Vega et al., 2016).
+Focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
+These findings highlight multifaceted representations of psychological constructs within mPFC subregions.
+However, recent activation-based meta-analytic has demonstrated domain specificity in this area (Kragel et al., 2018).
+In addition, coordinate-based meta-analyses rely on peak coordinates derived from group-averaged data.
 It has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
 Aiming to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
-Yeo et al (2018) have effectively incorporated individualized topologies for generating distributed functional networks.
+For example, Yeo et al (2018) have effectively incorporated individualized topologies for generating distributed functional networks.
 Gordon et al identify important idiosincrasies in oversampled subjects that are blurred in agglomerative analyses.
-The trend of individualized analyses has led to finer subdivisions of the DMN (Braga & Buckner, 2018).
+Importantly, the trend of individualized analyses has led to finer subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018).
 It is thus possible that the indisitinguishable extent of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
-
-Given the shortcomings of study-specific and cross-study analyses, there is potential value in combining complementary strengths from both approaches.
-Focusing on resting state data has been successful in determining a number of neural phenomena, including disentangling auditory and visual attention areas (Tobyne, Osher, Michalka, & Somers, 2017).
-A natural next step would be to recruit all possible patterns of covariation within this network.
-A popular alternative is to rely on graph theoretic methods, which provide a characterization of networks that organically fits brain dynamics (provides an organic avenue to understand brain dynamics?), and thus permits the consideration of the full covariance structure of brain networks.
-
-One great advantage of network science is the ability to characterize connectivity in a way that allows for comparisons among individuals in a meaningful way (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018), thus letting us address the idiosyncrasies mentioned above.
-In this study, we aim to subdivide mPFC into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making.
-We address this aim at 3 levels of granularity: 1) across the literature (meta-analysis), selecting a number of regions of interest (ROI) that show significant overlap and specificity between DMN and decision making; and 2) characterizing the connectivity of all surface vertices for these ROIs.
-
-Do these things truly overlap, or are we not looking close enough?
-
-Add Tor's latest papers to the meta analysis
+With this in mind, a first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present in mPFC.
+
+  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008).
+As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time.
+A popular approach is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics.
+From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018).
+Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016).
+Among the algorithms used to estimate these communities, modularity has been widely effective in brain networks (Garcia et al., 2018).
+However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes bipartision through spectral partitioning a more viable option.
+In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix), and the resulting eigenvector corresponding to the second-to-last eigenvalue (i.e.
+the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975).
+This method could thus highlight the cluster of brain regions that more cohesively share activation patterns during rest.
+
+  In this study, we aim to subdivide regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making.
+We do this by capitalizing on therespective strengths of meta-analytic and subject-specific analyses of brain data.
 

### 2018-08-21 Manuscript/Manuscript.Rmd
Draft of intro ready (needs trimming though)

@@
 
-(current, 708 words. Aim for 650)
-
-  The medial prefrontal cortex (mPFC) has been suggested to subserve many of the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016).
+(Current: 880 words. Aim for 650)
+
   Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007).
 However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
-This has prompted the question of whether (and to what extent) these two systems can be dissociated.
+This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.
 
@@
 Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009).
-Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, they strongly coactivate with DMN regions across the literature, with no clear topographical distinction (de la Vega et al., 2016).
-Focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
-These findings highlight multifaceted representations of psychological constructs within mPFC subregions.
-However, recent activation-based meta-analytic has demonstrated domain specificity in this area (Kragel et al., 2018).
-In addition, coordinate-based meta-analyses rely on peak coordinates derived from group-averaged data.
-It has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
-Aiming to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
-For example, Yeo et al (2018) have effectively incorporated individualized topologies for generating distributed functional networks.
-Gordon et al identify important idiosincrasies in oversampled subjects that are blurred in agglomerative analyses.
-Importantly, the trend of individualized analyses has led to finer subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018).
-It is thus possible that the indisitinguishable extent of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
-With this in mind, a first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present in mPFC.
+Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, they strongly coactivate with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016).
+More specifically, focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
+These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system.
+However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area (Kragel et al., 2018).
+While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data.
+Averaging has traditionally been beneficial in identifying overall trends in brain function and organization when faced with short scanning sessions per subject.
+However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
+
+  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
+Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in agglomerative estimations (Laumann....; Gordon et al., 2018).
+Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018).
+In regards to DMN, the trend of individualized analyses has led to finer subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018).
+It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
+With this in mind, a first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.
 
@@
 As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time.
-A popular approach is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics.
+Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2018, Tobyne et al., 2018).
+A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018).
 From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018).
@@
 However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes bipartision through spectral partitioning a more viable option.
-In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix), and the resulting eigenvector corresponding to the second-to-last eigenvalue (i.e.
+In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix).
+The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e.
 the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975).
-This method could thus highlight the cluster of brain regions that more cohesively share activation patterns during rest.
+This method could thus highlight a refined cluster of brain regions that more cohesively share activation patterns during rest.
 
   In this study, we aim to subdivide regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making.
-We do this by capitalizing on therespective strengths of meta-analytic and subject-specific analyses of brain data.
+We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
+First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature according to an established brain atlas (Glasser et al., 2013).
+We then produce a network of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project, and estimate the extent of DMN coverage through community detection.
+We finalize by quantifying the generazibility and stability of the resulting functional topologies across subjects, and compare the approach to more traditional seed-based correlation methods.
 

### 2018-08-21 Manuscript/Manuscript.Rmd
Tweaks to intro

@@
   Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
-Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in agglomerative estimations (Laumann....; Gordon et al., 2018).
+Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations (Laumann et al., 2015; Gordon et al., 2018).
 Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018).
@@
 As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time.
-Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2018, Tobyne et al., 2018).
+Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2018; Laumann et al., 2015; Tobyne et al., 2018).
 A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018).
@@
 
-  In this study, we aim to subdivide regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN areas, so that we can generate more informed topographic targets for future studies of decision making.
+  In this study, we aim to subdivide regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN clusters, so that we can generate more informed topographic targets for future studies of decision making.
 We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
 First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature according to an established brain atlas (Glasser et al., 2013).
-We then produce a network of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project, and estimate the extent of DMN coverage through community detection.
-We finalize by quantifying the generazibility and stability of the resulting functional topologies across subjects, and compare the approach to more traditional seed-based correlation methods.
+We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project, and estimate the extent of DMN coverage through community detection.
+The resulting partitions were evaluated for consistency across methods, throughout each individual's time series, and across subjects.
 

### 2018-08-23 Manuscript/Manuscript.Rmd
Wording

@@
   Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007).
-However, the distributed valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
+However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
 This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.
@@
 Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018).
-In regards to DMN, the trend of individualized analyses has led to finer subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018).
+In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018).
 It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
@@
 the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975).
-This method could thus highlight a refined cluster of brain regions that more cohesively share activation patterns during rest.
-
-  In this study, we aim to subdivide regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN clusters, so that we can generate more informed topographic targets for future studies of decision making.
+This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.
+
+  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, so that we can generate more informed topographic targets for future studies of decision making.
 We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
-First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature according to an established brain atlas (Glasser et al., 2013).
+First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013).
 We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project, and estimate the extent of DMN coverage through community detection.
-The resulting partitions were evaluated for consistency across methods, throughout each individual's time series, and across subjects.
+The resulting partitions are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.
 

### 2018-08-23 Manuscript/Manuscript.Rmd
Confirming content from some citations

@@
 Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009).
-Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, they strongly coactivate with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016).
+Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, overall mPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016).
 More specifically, focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
@@
   Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
-Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations (Laumann et al., 2015; Gordon et al., 2018).
+Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations (Laumann et al., 2015; Gordon et al., 2017; Gratton et al., 2018).
 Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018).
@@
 As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time.
-Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2018; Laumann et al., 2015; Tobyne et al., 2018).
+Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2017; Laumann et al., 2015; Tobyne et al., 2018).
 A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018).
@@
 
-  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, so that we can generate more informed topographic targets for future studies of decision making.
+  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, so that we can more precisely describe the network's features (i.e.
+stability, expanse) and generate more informed topographic targets for future studies of decision making.
 We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
@@
 The resulting partitions are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.
+
+## Notes
+
+I'll probably have to fix this in the intro: ADV et al note that dmPFC and vmPFC are more coactivated with DMN's PCC than pregenual ACC.
+This forms the topological shape that we report here.
+On my second read, it sounds like my interpretation is still correct: sure, vmPFC coactivates with subcortical value-related areas more than other mPFC sections, but this area also strongly coactivates with DMN in a way that they don't dissect.
+That's why they talk about the multifaceted embedding of psychological constructs here, even if the subregions they define are part of distinct networks.
+
+It would be interesting to quantify the average percentage of the Yeo et al DMN netowrk that is utilized by each individual's DMN.
+That should be easy: mean(do.call(mean, apply(Summary, "[[", "FiedlerBinary"))).
+Also the average size: mean(do.call(sum, apply(Summary, "[[", "FiedlerBinary"))).
 

### 2018-08-24 Manuscript/Manuscript.Rmd
Phrasing and citations

@@
 
-  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Kable & Glimcher, 2007).
+  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011).
 However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
@@
 
-  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, so that we can more precisely describe the network's features (i.e.
-stability, expanse) and generate more informed topographic targets for future studies of decision making.
+  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals.
+This description will allow researchers to generate more precise topographic targets for future studies of decision making.
 We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
@@
 Also the average size: mean(do.call(sum, apply(Summary, "[[", "FiedlerBinary"))).
+
+Gratton et al.
+(2018) have figures similar to ours indicating within subject stability being higher than across-subject similarity (3A).
+Our twist would be that we are quantifying a finer resolution level restricted to the ROIs (they use a 333 region parcellation), and they estimated it for the MSC only.9 So: what they find persists when examined at a finer level of resolution for a widespread sample.
 

### 2018-08-24 Manuscript/Manuscript.Rmd
Working on methods

@@
 **Meta-analysis**
-To perform the first step, I used data from a metanalysis that gathered peak brain coordinates of activity from studies of valuation (n = 27 studies) and DMN (n = 77).
-These are the surviving areas post-statistical thresholding from each study.
-I analyzed this data by mapping the peak cortical coordinates to an atlas of the human cortical surface (Glasser et al., 2016).
+We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation (Bartra et al., 2010) (n = 27 studies) and DMN (Laird et al., 2009) (n = 77).
+These represent the surviving areas post-statistical thresholding from each study.
+For each peak volumetric coordinate, 10mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer.
+The sphere sections that overlapped with the cortex were mapped to an atlas of the human cortical surface (Glasser et al., 2016).
 This produced a list of standardized parcels that were reported on each study.
-The advantage of utilizing this atlas was threefold: first, it reduced the number of functional vertices from 60,000 (cortical surface vertices) to 360 (cortical parcels).
-Second, it standardizes the vertices from the first to the second stage of my study.
-Finally, it allowed me to project each area on a brain space without much clutter.
-Since each vertex is embedded with topographical information, and since functional topography is essential to my question, I mostly project my results onto brain space.
-
-I thus generated two undirected, loop-less, weighted graphs in which each vertex was a brain parcel, and edges correspond to the number of times each pair of them co-occurred across studies.
-Since different decision tasks use different sensory modalities, and since sensory areas get sometimes reported as unrelated peak coordinates in DMN studies, I bootstrapped the co- occurrences across studies and removed edges whose co-occurrences lied below the 90th percentile.
+
+With these lists, we computed the number of times every two parcels co-occurred across each literature.
+This allowed us to generate two weighted networks in which each vertex was a brain parcel, and edges correspond to the number of times each pair of them co-occurred across studies.
+In order to threshold the parcels that are most likely to belong to each lliterature, we bootstrapped the co-occurrences across studies and removed edges whose co-occurrences lied below the 90th percentile of this distribution.
 Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded.
-With these graphs set up, I computed the strength and betweenness centrality in order to capture each parcel’s centrality in the valuation and DMN literatures separately.
-
-In order to select of regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, I first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution.
-Next, I took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus my main target for dissociation).
+The connectivity strength of every pairwise parcels was then calculated as the sum of their co-occurrences.
+In order to select regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, we first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution.
+Next, we took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus our main target for dissociation).
 
 **Whole Brain Parcellated connectivity**
-For the second step, in order to actually quantify the intrinsic connectivity of these ROIs in the brain, I used data from the Human Connectome Project.
-Specifically, I acquired resting-state fMRI activity from 3 subjects, all of whom have been preprocessed according to industry standards to allow for group-level comparisons (Tobyne et al., 2017).
-Each data set contained around 1 hour of signals represented as 4800 time points, and each subject contained 60,000 vertices.
+In order to actually quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state data from the Human Connectome Project (n = 80).
+Beyond the standard minimally preprocessed pipeline from HCP (), the data went through a number of additional refinements that are explained in detail elsewhere (Tobyne et al., 2017).
+Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR).
+Each data set contained around 1 hour of signals represented as approximately 4800 time points, and each subject contained 60,000 vertices.
 I parcellated each subject’s brain according to the atlas mentioned above, so that each parcel contained the mean time series from its vertices, and correlated the mean time series among all parcels (Pearson).

### 2018-08-27 Manuscript/Manuscript.Rmd
Working on methods and discussion a bit

@@
 
-  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011).
+  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011).
 However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
@@
 
+For clinical implications, see Hiser & Koenigs 2018.
+In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC.
+It would be more interesting to identify the repercussions to damage in mPFC per individual.
+They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment.
+The refinement of the technique is thus coupled to being able to identify personalized functional topologies.
+They list a number of results related to mPFC functional connectivity too.
+In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse.
+(note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)
+
 Methods {.unnumbered}

### 2018-08-27 Manuscript/Manuscript.Rmd
More methods

@@
 Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009).
-Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, overall mPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016).
+Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016).
 More specifically, focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
@@
 While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data.
-Averaging has traditionally been beneficial in identifying overall trends in brain function and organization when faced with short scanning sessions per subject.
+Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject.
 However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
@@
 Among the algorithms used to estimate these communities, modularity has been widely effective in brain networks (Garcia et al., 2018).
-However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes bipartision through spectral partitioning a more viable option.
+However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning a more valuable option.
 In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix).
@@
 First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013).
-We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project, and estimate the extent of DMN coverage through community detection.
-The resulting partitions are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.
+We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning.
+The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.
 
@@
 
+Tentative outline:
+
+- Meta-analysis
+- fMRI data
+- Network definition
+- Community detection
+- Evaluation
+
 **Meta-analysis**
@@
 For each peak volumetric coordinate, 10mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer.
-The sphere sections that overlapped with the cortex were mapped to an atlas of the human cortical surface (Glasser et al., 2016).
+The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (Glasser et al., 2016).
 This produced a list of standardized parcels that were reported on each study.
@@
 With these lists, we computed the number of times every two parcels co-occurred across each literature.
-This allowed us to generate two weighted networks in which each vertex was a brain parcel, and edges correspond to the number of times each pair of them co-occurred across studies.
-In order to threshold the parcels that are most likely to belong to each lliterature, we bootstrapped the co-occurrences across studies and removed edges whose co-occurrences lied below the 90th percentile of this distribution.
+This allowed us to generate two weighted networks in which each vertex was a brain parcel, and edges corresponded to the number of times each pair of them co-occurred across studies.
 Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded.
 The connectivity strength of every pairwise parcels was then calculated as the sum of their co-occurrences.
+In order to threshold the parcels that are most likely to belong to each literature, we bootstrapped the connectivity strength and removed edges whose values lied below the 95th percentile of this distribution.
 In order to select regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, we first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution.
@@
 
-**Whole Brain Parcellated connectivity**
-In order to actually quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state data from the Human Connectome Project (n = 80).
-Beyond the standard minimally preprocessed pipeline from HCP (), the data went through a number of additional refinements that are explained in detail elsewhere (Tobyne et al., 2017).
+Next, we identified areas that were solely related to either literature.
+We limited the search space to the parcels from Glasser et al.
+(2013) that were contained within the DMN parcellation defined by Yeo et al.
+(2011).
+We permuted the label of every study (i.e.
+DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a ROI-wise chi-squared test of proportions on the number of prmuted studies that had reported each ROI.
+This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.
+
+**fMRI Data**
+In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state data from the Human Connectome Project (n = 80, randomly sampled from the total pool) Q6 release.
+Beyond the standard minimally preprocessed pipeline from HCP (), the data went through a number of additional refinements that are detailed elsewhere (Tobyne et al., 2017).
 Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR).
-Each data set contained around 1 hour of signals represented as approximately 4800 time points, and each subject contained 60,000 vertices.
-I parcellated each subject’s brain according to the atlas mentioned above, so that each parcel contained the mean time series from its vertices, and correlated the mean time series among all parcels (Pearson).
-This produced a weighted adjacency matrix for each subject, where each of the 360 parcels is a vertex, and edges the correlations among all of them.
-Next, I took the exponential of the correlations, Fisher transformed them (i.e.
-tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant (FDR < 0.05).
-Again, I quantified each parcel’s strength and betweenness, averaged them across subjects, and examined whether any of the ROIs showed uniquely high centralities.
-For this, I performed a permutation comparing the mean strength between the ROIs and the rest of the brain for each participant.
+Each subject's brain was comprised of 32k vertices per hemisphere.
+We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.
+Resting state data was acquired over four scanning sessions that occurred over the course of two days (two sessions per day).
+Each resting state scan was comprised of 1200 TRs (TR = 0.720s) for a total time of 14 min 33 s per session.
+We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).
+
+**Within-ROI Connectivity**
+To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,942 per subject) and computed the Pearson correlation of the time series of every pair of vertices.
+This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
+Next, we took the exponential of the correlations, Fisher transformed them (i.e.
+tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
 

### 2018-08-28 graphAnalysis_solo.R
Working on simpler ways to generate ROIs from meta-analysis
and deleted the VS version.

@@ -203,7 +203,7 @@ fisherTanh <- function(Data = padjMatrix){
   
   transformed <- list()
   
-  # tanh (ones reduced to 0.999 to avoid Inf)
+  # tanh
   Data[Data == 1] <- 1 * 0.999
   transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
   
@@ -472,6 +472,7 @@ communityDetection <- function(Data = parcelBins$First, ROIS = "None", Type = "v
       
       # for storing later
       corrMatrix <- corrMat
+      
       
       # transform to Fisher's (think of thresholding)
       transfMat <- fisherTanh(Data = corrMat)
@@ -1013,7 +1014,7 @@ Meta <- F # Run meta analysis?
 Parcellated <- F # Parcellated whole brain community detection
 Vertex <- T # ROI-based vertex analysis
 Plots <- F # If running on the SCC, plots might be unhelpful. Have a separate script for that instead
-Sliding <- F
+Sliding <- T
 
 # colors to differentiate other things
 #Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere
@@ -1023,9 +1024,6 @@ Cols <- c("DMN" = "aquamarine4","Valuation" = "#D9541A",rgb(190,190,190,100, max
 # These come from an arbitrary division based on where Mackey & Petrides (2014) draw their line
 # This is computed below, but if we want to save time it can be loaded instead.
 bothLbls <- as.character(read.table('bothLbls.csv', header = F)$V2)
-# add Accumbens (in the future replace 7m with Accumbens (i.e. gsub("_7m_", "Accumbens", bothLbls)))
-bothLbls <- c(bothLbls, "Accumbens")
-#
 
 vmPFC_labels <- c("_10pp_",
                   "_10r_",
@@ -1089,7 +1087,7 @@ mPFC_only <- c("_a24_",
 
 # Cortical surface for plotting
 labelPerVertex <- read.table('labelPerVertex.csv', header = F)
-labelCoords_vertex <- read.csv2('labelCoords_vertex.csv')[,2:6]
+labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[,2:6]
 labelCoords_parcel <- read.csv2('labelCoords_parcel.csv', sep = ",")
 
 # Ensure that coordinates are numeric once loaded
[…]

### 2018-08-28 graphAnalysis_solo_nonVS.R

@@ -1,1839 +1,0 @@
-#!/usr/bin/env Rscript
-SubjID <- commandArgs(trailingOnly=TRUE)
-write(paste("Analyzing data for subject", SubjID), stdout())
-
-### Run a meta-analysis and graph theoretic fMRI analysis
-
-###------- Libraries and functions ---------------
-write('Loading functions and libraries...', stdout())
-
-library(igraph)
-#library(tidyverse)
-library(ggnetwork)
-library(ggplot2)
-library(gridExtra)
-library(data.table)
-library(plyr)
-library(mcclust)
-library(lme4)
-library(parallel)
-#library(lmerTest)
-
-## log-log degree distribution
-logDegreeDist <- function(Graph = padjMat) {
-  
-  tempD <- degree(Graph)
-  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
-  d <- (0:(max(tempD)-1))
-  ind <- (tempDD!=0)
-  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
-       xlab = "Log-Degree", ylab = "Log-Intensity",  
-       main = "Log-Log Degree Distribution")
-  
-}
-
-
-## Create correlation matrix between vertices of 2 ROIs
-# Requires labeled time series matrix
-vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
-  
-  # extract the time series from the ROIs
-  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
-  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
-  nVerts_1 <- length(indexing_1)
-  nVerts_2 <- length(indexing_2)
-  ROI_1_tseries <- timeSeries[indexing_1, ]
-  ROI_2_tseries <- timeSeries[indexing_2, ]
-  
-  # Create empty matrix
-  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)
-  
-  # 
-  for (vertex_1 in seq(nVerts_1)){
-    
-    # temp series 1
-    tempOne <- ROI_1_tseries[vertex_1, ]
-    
-    for(vertex_2 in seq(nVerts_2)){
-      
-      # temp series 2
-      tempTwo <- ROI_2_tseries[vertex_2, ]
-      
-      # store the Pearson correlation in the corr matrix
[…]

### 2018-08-28 Manuscript/Manuscript.Rmd
More on intro and methods

@@
 
-(Current: 880 words. Aim for 650)
-
-  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011).
-However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
+(Current: 942 words. Aim for 650)
+
+  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011).
+However, the distributed cortical valuation system also includes posterior cingulate and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall (Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
 This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.
@@
 Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016).
-More specifically, focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
+More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
 These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system.
@@
 It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
-With this in mind, a first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.
+With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.
 
@@
 Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016).
-Among the algorithms used to estimate these communities, modularity has been widely effective in brain networks (Garcia et al., 2018).
+Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups (Garcia et al., 2018).
 However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning a more valuable option.
@@
 The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.
-
-## Notes
-
-I'll probably have to fix this in the intro: ADV et al note that dmPFC and vmPFC are more coactivated with DMN's PCC than pregenual ACC.
-This forms the topological shape that we report here.
-On my second read, it sounds like my interpretation is still correct: sure, vmPFC coactivates with subcortical value-related areas more than other mPFC sections, but this area also strongly coactivates with DMN in a way that they don't dissect.
-That's why they talk about the multifaceted embedding of psychological constructs here, even if the subregions they define are part of distinct networks.
-
-It would be interesting to quantify the average percentage of the Yeo et al DMN netowrk that is utilized by each individual's DMN.
-That should be easy: mean(do.call(mean, apply(Summary, "[[", "FiedlerBinary"))).
-Also the average size: mean(do.call(sum, apply(Summary, "[[", "FiedlerBinary"))).
-
-Gratton et al.
-(2018) have figures similar to ours indicating within subject stability being higher than across-subject similarity (3A).
-Our twist would be that we are quantifying a finer resolution level restricted to the ROIs (they use a 333 region parcellation), and they estimated it for the MSC only.9 So: what they find persists when examined at a finer level of resolution for a widespread sample.
+Finally, we show some interesting properties of SP related to the stability of brain networks.
 
@@
 
-With these lists, we computed the number of times every two parcels co-occurred across each literature.
-This allowed us to generate two weighted networks in which each vertex was a brain parcel, and edges corresponded to the number of times each pair of them co-occurred across studies.
-Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded.
-The connectivity strength of every pairwise parcels was then calculated as the sum of their co-occurrences.
-In order to threshold the parcels that are most likely to belong to each literature, we bootstrapped the connectivity strength and removed edges whose values lied below the 95th percentile of this distribution.
-In order to select regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, we first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution.
-Next, we took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus our main target for dissociation).
+With these lists, we identified the areas that were more consistently shared between DMN and valuation.
+For each literature, we summed the number of times each parcel was reported across studies, and performed a one-way chi-squared test of proportions on each parcel with a null probability equivalent to the bootstrapped (5000 iterations) mean of each literature's report counts.
+In other words, we checked which regions were significantly (p < 0.05) more reported in their respective literatures than their counterparts.
+Regions of interest were then determined based on which of the remaining regions were common across literatures.
 
 Next, we identified areas that were solely related to either literature.
-We limited the search space to the parcels from Glasser et al.
-(2013) that were contained within the DMN parcellation defined by Yeo et al.
+We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al.
 (2011).
@@
 **fMRI Data**
-In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state data from the Human Connectome Project (n = 80, randomly sampled from the total pool) Q6 release.
-Beyond the standard minimally preprocessed pipeline from HCP (), the data went through a number of additional refinements that are detailed elsewhere (Tobyne et al., 2017).
+In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP; Van Essen et al., 2013; www.humanconnectome.org) Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects).
+Each subject's data was acquired over two days at Washington University in St.
+Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany).
+A resting state session (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) was comprised of 1200 TRs for a total time of 14 min 33 s per session, with left-right and left-right phase encoding implemented on each day.
+We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).
+
+Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which include motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152 normalization, all scans went through a number of additional refinements (Tobyne et al., 2017).
+Only subjects with both left-right and right-left phase encoding were included.
+In addition, only datasets with either low motion levels (under 1.5mm) or 0.5mm mean framewise displacement (FD) were used.
+Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses.
 Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR).
@@
 Resting state data was acquired over four scanning sessions that occurred over the course of two days (two sessions per day).
-Each resting state scan was comprised of 1200 TRs (TR = 0.720s) for a total time of 14 min 33 s per session.
-We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).
 
@@
 ========================================
+
+## Notes
+
+It would be interesting to quantify the average percentage of the Yeo et al DMN netowrk that is utilized by each individual's DMN.
+That should be easy: mean(do.call(mean, apply(Summary, "[[", "FiedlerBinary"))).
+Also the average size: mean(do.call(sum, apply(Summary, "[[", "FiedlerBinary"))).
+
+Gratton et al.
+(2018) have figures similar to ours indicating within subject stability being higher than across-subject similarity (3A).
+Our twist would be that we are quantifying a finer resolution level restricted to the ROIs (they use a 333 region parcellation), and they estimated it for the MSC only.9 So: what they find persists when examined at a finer level of resolution for a widespread sample.
 

### 2018-08-28 Manuscript.Rmd
Change of plan. Going back to a regular markdown doc, not rticle

--- 2018-08-15 Analyze_summaries.Rmd
@@
 ## Introduction
-One of the main goals of human cognitive neuroscience is to be able to prescribe function to brain regions, either in isolation or in their communication with others.
-Among general regions of the brain, the medial prefrontal cortex (mPFC, located in the midline frontal portion of the brain) has been suggested to subserve the cognitive abilities that differentiate humans from other animals (Barbas & Garcia-Cabezas, 2016).
-Specifically, this region has been related to a variety of functions, including decision making (Bartra, McGuire, & Kable, 2013), memory encoding (Shacter, Addis, & Buckner, 2007), and default mode deactivation (DMN) (Yeo et al., 2011).
-While much has been discovered about this area in primates (Barbas & Garcia-Cabezas, 2016), the lack of direct measurements of neuronal activity makes this a tough area to record in humans, one that nowadays relies mostly on functional MRI (fMRI).
-Unfortunately, the mPFC is especially challenging to image, as the oxygen-related signal recorded by fMRI is contaminated by the oxygen in the sinuses (Logothetis, 2008).
-In addition, this area is subject to more idiosyncratic cortical folding than any other region (Zilles, Palomero- Gallagher, & Amunts, 2013), thus adding a level of complexity to the generalizable dissection of topographic functional roles within mPFC.
-
-Studies of valuation have consistently shown functional overlap with DMN.
-Recent meta-analytic work has attempted to distinguish the brain areas belonging to each by examining the locus of peak activity across studies related to the behavioral features mentioned above (Bartra et al., 2013; Acikalin, Gorgolewski, & Poldrack, 2017).
-While this approach offers valuable information, it is subject to the quality of imaging in each study, as well as their corresponding differences in tasks used to examine choice.
-In addition, recent findings suggest that the functional topology of the brain is better understood by accounting for organizational idosyncrasies (Braga and Buckner, 2018; Yeo et al., 2018, Gordon et al., 2017, Gratton...).
-
-Given the shortcomings of study-specific and cross-study analyses mentioned above, there is potential value in combining complementary strengths from both approaches.
-While my lab is primarily interested in the portion of mPFC dedicated to decision making, in order to bypass the heterogeneity in behavioral tasks, it might be best to disentangle the mPFC by focusing first on which of its sub-regions belong to resting-state DMN, and which do not.
-The advantage lies in that (1) all resting state scans are performed equally (the subject lies in the scanner with their eyes open), and (2) there is a high quality resource of resting state data provided by the Human Connectome Project.
-Focusing on resting state data has been successful in determining a number of neural phenomena, including disentangling auditory and visual attention areas (Tobyne, Osher, Michalka, & Somers, 2017).
-
-This approach opens an opportunity to examine brain dynamics.
-For example, a region’s function might depend on its connectivity at any given time with one brain community or another.
-An ever-growing trend in human neuroimaging has been to apply network statistics to tackle these functional challenges.
-One great advantage of network science is the ability to characterize connectivity in a way that allows for comparisons among individuals in a meaningful way (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018), thus letting us address the folding idiosyncrasies mentioned above.
-Therefore, I propose to use some of the statistics that we have learned in class to estimate intrinsic functional subdivisions of the mPFC at the individual subject level.
-Particularly, I would like to distinguish communities related to DMN from non-DMN, so that we can generate more informed topographic targets for future studies of decision making.
-
-In this study, I try to address my question at 3 levels of granularity: 1) across the literature (meta-analysis), selecting a number of regions of interest (ROI) that show significant overlap and specificity between DMN and decision making; 2) full-brain connectivity of actual fMRI data, using a pre-specified brain atlas; and 3) characterizing the connectivity of surface vertices (small units of function that contain oxygen-dependent neural information across time) for the regions selected in step one.
-I performed the last two steps at an individual subject level for 3 subjects, hoping to find some commonalities among them.
-In this way, I attempted to extract functional topographical information from topological network features.
+  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011).
+However, the distributed cortical valuation system also includes posterior cingulate and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall (Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
+This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.
+
+  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions.
+Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009).
+Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016).
+More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
+These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system.
+However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area (Kragel et al., 2018).
+While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data.
+Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject.
+However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
+
+  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
+Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations (Laumann et al., 2015; Gordon et al., 2017; Gratton et al., 2018).
+Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018).
+In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018).
+It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
+With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.
+
+  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008).
+As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time.
+Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2017; Laumann et al., 2015; Tobyne et al., 2018).
+A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018).
+From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018).
+Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016).
+Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups (Garcia et al., 2018).
+However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning a more valuable option.
+In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix).
+The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e.
+the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975).
+This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.
+
+  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals.
+This description will allow researchers to generate more precise topographic targets for future studies of decision making.
+We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
+First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013).
+We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning.
+The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.
+Finally, we show some interesting properties of SP related to the stability of brain networks.
 
 ## Methods
+Tentative outline:
+
+- Meta-analysis
+- fMRI data
+- Network definition
+- Community detection
+- Evaluation
+
 **Meta-analysis**
-To perform the first step, I used data from a metanalysis that gathered peak brain coordinates of activity from studies of valuation (n = 27 studies) and DMN (n = 77).
-These are the surviving areas post-statistical thresholding from each study.
-I analyzed this data by mapping the peak cortical coordinates to an atlas of the human cortical surface (Glasser et al., 2016).
+We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation (Bartra et al., 2010) (n = 27 studies) and DMN (Laird et al., 2009) (n = 77).
+These represent the surviving areas post-statistical thresholding from each study.
+For each peak volumetric coordinate, 10mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer.
+The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (Glasser et al., 2016).
 This produced a list of standardized parcels that were reported on each study.
-The advantage of utilizing this atlas was threefold: first, it reduced the number of functional vertices from 60,000 (cortical surface vertices) to 360 (cortical parcels).
-Second, it standardizes the vertices from the first to the second stage of my study.
-Finally, it allowed me to project each area on a brain space without much clutter.
-Since each vertex is embedded with topographical information, and since functional topography is essential to my question, I mostly project my results onto brain space.
-
-I thus generated two undirected, loop-less, weighted graphs in which each vertex was a brain parcel, and edges correspond to the number of times each pair of them co-occurred across studies.
-Since different decision tasks use different sensory modalities, and since sensory areas get sometimes reported as unrelated peak coordinates in DMN studies, I bootstrapped the co- occurrences across studies and removed edges whose co-occurrences lied below the 90th percentile.
-Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded.
-With these graphs set up, I computed the strength and betweenness centrality in order to capture each parcel’s centrality in the valuation and DMN literatures separately.
-
-In order to select of regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, I first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution.
-Next, I took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus my main target for dissociation).
-
-**Whole Brain Parcellated connectivity**
-For the second step, in order to actually quantify the intrinsic connectivity of these ROIs in the brain, I used data from the Human Connectome Project.
-Specifically, I acquired resting-state fMRI activity from 3 subjects, all of whom have been preprocessed according to industry standards to allow for group-level comparisons (Tobyne et al., 2017).
-Each data set contained around 1 hour of signals represented as 4800 time points, and each subject contained 60,000 vertices.
-I parcellated each subject’s brain according to the atlas mentioned above, so that each parcel contained the mean time series from its vertices, and correlated the mean time series among all parcels (Pearson).
-This produced a weighted adjacency matrix for each subject, where each of the 360 parcels is a vertex, and edges the correlations among all of them.
-Next, I took the exponential of the correlations, Fisher transformed them (i.e.
-tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant (FDR < 0.05).
-Again, I quantified each parcel’s strength and betweenness, averaged them across subjects, and examined whether any of the ROIs showed uniquely high centralities.
-For this, I performed a permutation comparing the mean strength between the ROIs and the rest of the brain for each participant.
+
+With these lists, we identified the areas that were more consistently shared between DMN and valuation.
+For each literature, we summed the number of times each parcel was reported across studies, and performed a one-way chi-squared test of proportions on each parcel with a null probability equivalent to the bootstrapped (5000 iterations) mean of each literature's report counts.
+In other words, we checked which regions were significantly (p < 0.05) more reported in their respective literatures than their counterparts.
+Regions of interest were then determined based on which of the remaining regions were common across literatures.
+
+Next, we identified areas that were solely related to either literature.
+We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al.
+(2011).
+We permuted the label of every study (i.e.
+DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a ROI-wise chi-squared test of proportions on the number of prmuted studies that had reported each ROI.
+This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.
+
+**fMRI Data**
+In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP; Van Essen et al., 2013; www.humanconnectome.org) Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects).
+Each subject's data was acquired over two days at Washington University in St.
+Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany).
+Four resting state sessions (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) were each comprised of 1200 TRs for a total scan time of 14 min 33 s, with left-right and left-right phase encoding implemented on each day.
+We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).
+
+Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which include considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152 normalization, all scans went through a number of additional refinements (Tobyne et al., 2017).
+Only subjects with both left-right and right-left phase encoding were included.
+In addition, only datasets with either low motion levels (under 1.5mm) or 0.5mm mean framewise displacement (FD) were used.
+Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses.
+Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR).
+Each subject's brain was comprised of 32k vertices per hemisphere.
+We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.
+Resting state data was acquired over four scanning sessions that occurred over the course of two days (two sessions per day).
+
+**Within-ROI Connectivity**
+To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,942 per subject) and computed the Pearson correlation of the time series of every pair of vertices.
+This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
+Next, we took the exponential of the correlations, Fisher transformed them (i.e.
+tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
 
@@
 
-## Introduction
-
-This report focuses on the community detection results, but it might be worth adding the meta-analytic steps here eventually as well.
-In general, the similarity matrices show a representative subsample of subjects (n = 10) to conserve space (unless noted), but the boxplots and formal tests include all subjects.
-The trends shown by the example subjects generalize to the larger sample anyways.
-
+## Results
 ## Partition Comparison: Full Datasets
@@
 are there any outstanding structural features in a subject that match their unique topology?).
+## Discussion
+For clinical implications, see Hiser & Koenigs 2018.
+In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC.
+It would be more interesting to identify the repercussions to damage in mPFC per individual.
+They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment.
+The refinement of the technique is thus coupled to being able to identify personalized functional topologies.
+They list a number of results related to mPFC functional connectivity too.
+In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse.
+(note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)
+
+## References

### 2018-08-28 Manuscript.Rmd
Cleaning up

@@
 ``` {r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}
+
 Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere
@@
 # In case I want to visualize stuff in the brain
-labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[,2:6]
+labelCoords_vertex <- read.csv2('labelCoords_vertex.csv')[,2:6]
 labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))
@@
 ``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
-setwd('./For_HCP')
-temp <- list.files(pattern = '*Binary*')
-FB <- lapply(temp, read.table)
-Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
-FB_Means <- rowMeans(Summed)
-
-write.table(file = 'propDMN_all.txt', FB_Means, row.names = F, col.names = F, dec = ".")
-```
-
-## Notes:
-
-  - The mixed effects GLM is not that well defined. Fix the dependent to include total possible and actuals.
-  - If we stick to the linear model, maybe plot the day and subject coefficients for PCC and PFC too (all in onw plot).
-  - The official manuscript will probably have to include things like community size, density of each subject's network (so far, ~0.65), and maybe clustering coefficient?
+# setwd('./For_HCP')
+# temp <- list.files(pattern = '*Binary*')
+# FB <- lapply(temp, read.table)
+# Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
+# FB_Means <- rowMeans(Summed)
+# 
+# write.table(file = 'propDMN_all.txt', FB_Means, row.names = F, col.names = F, dec = ".")
+```
 
@@
 ## Methods
-Tentative outline:
-
-- Meta-analysis
-- fMRI data
-- Network definition
-- Community detection
-- Evaluation
 
@@
 
-**Within-ROI Connectivity**
 For the third stage, I “zoomed in” each subject’s brain by computing the correlation among all of the surface-vertices contained within each ROI across all the ROIs, and applied the same correction as in step two.
@@
 The final patterns were inspected visually.
+
+**Community Detection**
+
+**Evaluation**
 

### 2018-08-29 Manuscript.Rmd
Adding images to results

@@
 ---
-title: "Parsing mPFC: Community analysis"
+title: "Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach"
 author: "Claudio Toro-Serey & Joseph T. McGuire"
@@
 output:
+  pdf_document: default
   html_document: default
-  pdf_document: default
 ---
@@
 ## Introduction
+
   Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011).
@@
 These represent the surviving areas post-statistical thresholding from each study.
-For each peak volumetric coordinate, 10mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer.
+For each peak volumetric coordinate, 10 mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer.
 The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (Glasser et al., 2016).
@@
 
-Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which include considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152 normalization, all scans went through a number of additional refinements (Tobyne et al., 2017).
-Only subjects with both left-right and right-left phase encoding were included.
-In addition, only datasets with either low motion levels (under 1.5mm) or 0.5mm mean framewise displacement (FD) were used.
+Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which includes considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152-based normalization, all scans went through a number of additional refinements (Tobyne et al., 2017).
+These included band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), as well as mean greyordinate signal regression (MGSR; Burgess et al., 2016).
+Only subjects with both left-right and right-left phase encoding were included (i.e.
+subjects with four rsfMRI sessions).
+In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used.
 Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses.
-Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR).
+Finally, data acquired on the same day (i.e.
+left-right and right-left phase encoding session) were temporally demeaned.
 Each subject's brain was comprised of 32k vertices per hemisphere.
 We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.
-Resting state data was acquired over four scanning sessions that occurred over the course of two days (two sessions per day).
-
-**Within-ROI Connectivity**
-To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,942 per subject) and computed the Pearson correlation of the time series of every pair of vertices.
+
+**Within-ROI Network Definition**
+To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,564 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
 This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
@@
 tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
-
-For the main goal of this section, I maximized the strength-based modularity metric as a community detection method (fast-greedy algorithm), so that I could check if all the DMN ROIs from the previous section were affiliated with the same community.
-While this measure has resolution problems at large and low scales (Fortunato & Hric, 2016), if it does extract a close match to standard DMN networks, it could act as a good method for the final stage of the project (but see Peel, Larremore, and Clauset 2017 for issues with ground-truth).
-Even though this analysis is mainly geared to confirm that these ROIs are jointly captured, this step also let me examine whether some of the ROIs could be subdivided into DMN and non-DMN regions at this level of granularity.
-
-In order to evaluate the validity of the modularity-based communities, I also clustered the brain by means of spectral partitioning.
-Specifically, I took the Fiedler vector (eigenvector associated with the second lowest eigenvalue) from each participant’s normalized Laplacian matrix, and divided the brain by the sign of the eigenvector values.
-This analysis served the additional purpose of more strictly dividing the brain into DMN and non-DMN communities.
-Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).
-Finally, to quantify the agreement of these community methods, I computed both the adjusted rand index and variation of information distance (normalized by the logarithm of the number of vertices, 360 in this case) between them per subject.
+As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately; 2) the concatenated timeseries from each pair of daily sessions; 3) each subject's dataset; and 4) on each step of a sliding window analysis (see Evaluation for more details).
+
+**Community Detection**
+
+Communities (i.e.
+clusters) were identified by means of spectral partitioning (SP; Fiedler, 1975).
+First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,564).
+This matrix was then transformed into its normalized Laplacian form
+
+$$\begin{aligned}
+L = I - D^{-\frac{1}{2}}AD^{-\frac{1}{2}}
+\end{aligned}$$
+
+Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
+the sum of its correlations with every other vertex), and $A$ is the correlation matrix.
+We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
+This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected (Fiedler, 1975).
+Given that this data-driven method is agnostic to the prevalent function of each community (i.e.
+DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis.
+Importantly, given the high density of these networks (**Add to results**), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).
+
+In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization (using the algorithm from Clauset et al., XXXX).
+This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
+The method heuristically iterates through many possible combination of vertices, and selects the clustering that maximizes the network's modularity.
+Thus, unlike SP, modularity can subdivide a network into many functional groups.
+If the partitions from the bounded and unbounded methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
+
+**Partition Evaluation**
+To quantify the agreement between partitions, we computed both the adjusted rand index and variation of information distance.
 The adjusted rand index denotes the proportion of vertices that coincide in affiliation across partitions, and compares this score to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions.
@@
 Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).
-Importantly, due to having just 3 subjects, I abstained from performing formal statistics on the descriptive measures that I show.
-
-For the third stage, I “zoomed in” each subject’s brain by computing the correlation among all of the surface-vertices contained within each ROI across all the ROIs, and applied the same correction as in step two.
-That means that the vertices became smaller functional brain units that are connected by the same type of edge (i.e.
-adjusted correlations) as in step two.
-This time, I only focused on partitioning the brain through modularity and spectral partitioning to see if the ROIs can be subdivided at this finer level of resolution.
-It is worth noting that while communities across subjects should be similar, the idiosyncrasies explained previously (i.e.
-cortical folding) should produce noticeable differences as well.
-
-This time I added two new areas to the ROIs: 7m, as this area had unique relevance in DMN when compared to valuation (evidenced by its connectivity strength in DMN and chi- squared permutation in the meta-analysis, see results), and V1, as this visual processing area should not be affiliated with DMN.
-These regions thus acted as dual reference points, such that the community affiliated with 7m should denote DMN, while V1 indicated non-DMN.
-As before, I tested the validity of the partitions using the adjusted rand index and normalized variation of information.
+
  However, this time I also used the rand index to quantify the community correspondence between subjects.
@@
 
-**Community Detection**
-
-**Evaluation**
-
 ## Results
+## Meta-analysis
+
+Figure 1 shows the resulting ROIs from the meta-analysis.
+Areas in blue denote the 17 overlapping ROIs, which landed mostly on the medial wall, as well as a region in IPL and TPJ.
+Area 7m (in red) was the only one to show unique affiliation, which was significant for DMN.
+
+```{r Meta-analysis ROIs, out.width="60%", out.height="40%", fig.align = "center"}
+include_graphics("ROIS.png")
+```
+
 ## Partition Comparison: Full Datasets
 
-Just as reference, the following shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
-
-``` {r Partition comparison: all brain example, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE}
-# Load data
-setwd('./Summary/')
-temp <- list.files()
-subjList <- sapply(temp, substring, first=1, last=6)
-Summaries <- lapply(temp, read.csv)
-nSubj <- length(Summaries)
-
-plotCommunities(Summaries[[1]], Hemi = "L", Legends = F, type = "FiedlerBinary")
-
+The following shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
+
+```{r Template partition, out.width="60%", out.height="40%", fig.align = "center"}
+include_graphics("template.png")
 ```
@@
 
-``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
+``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
 # Cross-method
@@
 
-``` {r Partition comparison: all 2, fig.align="center", echo=FALSE, message = FALSE}
+``` {r Partition comparison: all 2, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
 # Across subjects
@@
 
-``` {r Partition comparison: halves, fig.align="center", echo=FALSE, message = FALSE}
+``` {r Partition comparison: halves, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
 # Select 10 subjects from the sample to display
@@
 
-``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
+``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
 # Now compare all possible pairs of subjects
@@
 
-``` {r Partition comparison: session similarity matrices, fig.align="center", echo=FALSE, message = FALSE}
+``` {r Partition comparison: session similarity matrices, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
 # Select 10 subjects from the sample to display
@@
 
-``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
+``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
 ## Brain storming:
@@
 
-``` {r Partition comparison: session linear model, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE}
+``` {r Partition comparison: session linear model, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
 # 2) Based on Kragel et al, 2018
@@
 
-``` {r Stability per subject: Overall, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE}
+``` {r Stability per subject: Overall, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
 # Load files
@@
 
-``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE}
+``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
 ## Check stability for PCC and mPFC separately
@@
 
-``` {r Stability per subject: SNR Comparison, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
+``` {r Stability per subject: SNR Comparison, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
 ## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
@@
 
-``` {r Stability per subject 4, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE}
+``` {r Stability per subject 4, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
 setwd('./Variance/')
@@
 
-``` {r Stability per subject 6, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE}
+``` {r Stability per subject 6, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
 # grid.arrange(v6, v7, ncol = 2)
@@
 
-``` {r Correlation vs community detection: plot, fig.align="center", echo=FALSE, message = FALSE}
+``` {r Correlation vs community detection: plot, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
 ## Between halves analysis for correlation and communities (mPFC only)
@@
 
-``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE}
+``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
 # Compare correlation with community approach on mPFC
@@
 are there any outstanding structural features in a subject that match their unique topology?).
+
 ## Discussion
+
 For clinical implications, see Hiser & Koenigs 2018.

### 2018-08-29 Manuscript.Rmd
Problems with LaTex integrating the images. Keep on trying (works in HTML)

@@
 library(DescTools)
+library(knitr)
 
@@
 clusters) were identified by means of spectral partitioning (SP; Fiedler, 1975).
-First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,564).
+First, each adjusted network was represented as an n x n correlation matrix (where n = number of vertices within the ROIs, 5,564).
 This matrix was then transformed into its normalized Laplacian form
@@
 
-Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its correlations with every other vertex), and $A$ is the correlation matrix.
+Where I is the identity matrix, D is a diagonal matrix containing the strength of each vertex (i.e.
+the sum of its correlations with every other vertex), and A is the correlation matrix.
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
@@
 ```{r Meta-analysis ROIs, out.width="60%", out.height="40%", fig.align = "center"}
-include_graphics("ROIS.png")
+# include_graphics("./Images/ROIS.png")
 ```
@@
 
-```{r Template partition, out.width="60%", out.height="40%", fig.align = "center"}
-include_graphics("template.png")
+```{r Template partition, out.width="50%", out.height="30%", fig.align = "center"}
+# Load data
+setwd('./Summary/')
+temp <- list.files()
+subjList <- sapply(temp, substring, first=1, last=6)
+Summaries <- lapply(temp, read.csv)
+nSubj <- length(Summaries)
+
+#include_graphics("./Images/template.png")
 ```

### 2018-08-29 Manuscript.Rmd
PDF images problem fixed

@@
 
-**Meta-analysis**
+### *Meta-analysis*
+
 We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation (Bartra et al., 2010) (n = 27 studies) and DMN (Laird et al., 2009) (n = 77).
@@
 
-**fMRI Data**
+### *fMRI Data*
+
 In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP; Van Essen et al., 2013; www.humanconnectome.org) Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects).
@@
 
-**Within-ROI Network Definition**
+### *Within-ROI Network Definition*
+
 To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,564 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
@@
 
-**Community Detection**
+### *Community Detection*
 
@@
 
-**Partition Evaluation**
+### *Partition Evaluation*
+
 To quantify the agreement between partitions, we computed both the adjusted rand index and variation of information distance.
@@
 
+\newpage
+
 ## Results
-## Meta-analysis
+
+### *Meta-analysis*
 
@@
 
-```{r Meta-analysis ROIs, out.width="60%", out.height="40%", fig.align = "center"}
-# include_graphics("./Images/ROIS.png")
-```
-
-## Partition Comparison: Full Datasets
+```{r Meta-analysis ROIs, out.width="60%", fig.align = "center"}
+include_graphics("./Images/ROIS.png")
+```
+
+### *Partition Comparison: Full Datasets*
 
@@
 
-```{r Template partition, out.width="50%", out.height="30%", fig.align = "center"}
+```{r Template partition, out.width="50%", fig.align = "center"}
 # Load data
@@
 
-#include_graphics("./Images/template.png")
+include_graphics("./Images/template.png")
 ```
@@
 
-## Partition Comparison: Day 1 vs Day 2
+### *Partition Comparison: Day 1 vs Day 2*
 
@@
 
-## Partition Comparison: Session
+### *Partition Comparison: Session*
 
@@
 
-## Stability per subject
+### *Stability per subject*
 
@@
 
-## Correlation vs community detection in mPFC
+### *Correlation vs community detection in mPFC*
 
@@
 
-## Structural correspondence
+### *Structural correspondence*
 

### 2018-08-30 Manuscript.Rmd
Added info to intro and more methods

@@
 ---
-title: "Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach"
+title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
 author: "Claudio Toro-Serey & Joseph T. McGuire"
-#date: "7/2/2018"
 output:
+  word_document: default
   pdf_document: default
@@
 Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups (Garcia et al., 2018).
-However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning a more valuable option.
+However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option.
 In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix).
 The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e.
-the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975).
-This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.
+the Fiedler vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975).
+SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data (BLAH.) This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.
 
@@
 $$\begin{aligned}
-L = I - D^{-\frac{1}{2}}AD^{-\frac{1}{2}}
+L = I - D^{-\frac{1}{2}}WD^{-\frac{1}{2}}
 \end{aligned}$$
@@
 Where I is the identity matrix, D is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its correlations with every other vertex), and A is the correlation matrix.
+the sum of its correlations with every other vertex), and W is the correlation matrix.
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
@@
 Given that this data-driven method is agnostic to the prevalent function of each community (i.e.
-DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis.
+DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects).
 Importantly, given the high density of these networks (**Add to results**), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).
@@
 The method heuristically iterates through many possible combination of vertices, and selects the clustering that maximizes the network's modularity.
-Thus, unlike SP, modularity can subdivide a network into many functional groups.
+Thus, unlike SP, modularity can fractionate a network into many functional groups.
 If the partitions from the bounded and unbounded methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.

### 2018-08-31 graphAnalysis_solo.R
Fixing figures mainly

@@ -458,14 +458,14 @@ communityDetection <- function(Data = parcelBins$First, ROIS = "None", Type = "v
       
       # Check for outliers. 
       # If found, remove vertices from indx, coords, and data, and recompute
-      tempStr <- colSums(corrMat)
-      outliers <- boxplot.stats(tempStr)$out
-      if (length(outliers) > 0) {
-        outIndx <- which(tempStr %in% outliers)
-        indx <- indx[! outIndx]
-        ROI_tseries <- Data[indx, ]
-        corrMat <- cor(t(ROI_tseries))
-      }
+      # tempStr <- colSums(corrMat)
+      # outliers <- boxplot.stats(tempStr)$out
+      # if (length(outliers) > 0) {
+      #   outIndx <- which(tempStr %in% outliers)
+      #   indx <- indx[! outIndx]
+      #   ROI_tseries <- Data[indx, ]
+      #   corrMat <- cor(t(ROI_tseries))
+      # }
       
       # name the dimensions of the matrix according to the surface vertex index
       rownames(corrMat) <- indx
@@ -1095,7 +1095,10 @@ labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(
 labelCoords_vertex <- transform(labelCoords_vertex, y = as.numeric(as.character(y)))
 labelCoords_vertex <- transform(labelCoords_vertex, z = as.numeric(as.character(z)))
 
-
+# Data frame to store the graph densities of each network
+densities <- data.frame(SubjID = rep(SubjID, 7),
+                        Type = c("Overall", "Day 1", "Day 2", "Session 1", "Session 2", "Session 3", "Session 4"),
+                        Density = rep(NA, 7))
 
 
 
@@ -1528,6 +1531,9 @@ if (Vertex) {
                                                 mode = "undirected",
                                                 weighted = T)
   
+  # Store the graph density
+  densities$Density[grep("Overall", densities$Type)] <- graph.density(tempGraph)
+  
   # Descriptives (Betweenness takes a long time, disregard)
   dmnval7mCommunities$Summary$Strength <- strength(tempGraph)
   
@@ -1641,7 +1647,6 @@ if (Vertex) {
     dmnval7mCommunities_halves[[i]]$Summary$FiedlerBinary <- tempEigen_halves[[i]]$binarized
     
     # Descriptives
-    # For MA703 I won't worry about this, since I'm not using it. 
[…]

### 2018-08-31 Manuscript.Rmd
Fixing figures mainly
manuscrip edits

@@
 
-To quantify the agreement between partitions, we computed both the adjusted rand index and variation of information distance.
-The adjusted rand index denotes the proportion of vertices that coincide in affiliation across partitions, and compares this score to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions.
-On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions.
+In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (RI; Rand, 2012) as the reference metric of agreement between two clusterings.
+The adjusted rand index estimates the rate at which every pair of nodes in partition A were equally assigned to the same/different parcels on partition B, over all possible changes (e.g.
+clustered together on A, but separately on B).
+The resulting ratio is compared to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions.
+Because of this, the adjusted rand index is a simple metric that determines the percentage agreement of any two partitions that is agnostic to the labeling scheme.
+*(SHOULD WE INCLUDE THIS?) On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions.
 While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case.
-Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).
-
-However, this time I also used the rand index to quantify the community correspondence between subjects.
-Specifically, I divided each subject’s spectrally- partitioned brain into PCC and mPFC topographical zones (posterior and frontal brain, respectively), and computed the index of each region between subjects.
-The high cross-subject heterogeneity of cortical folding of mPFC should produce relatively low rand indices, while the more homogeneous PCC should display the opposite pattern.
-This analysis was meant to tackle the subject-specific limitations discussed above.
-The final patterns were inspected visually.
+Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).*
+
+The topographies were compared: 1) Across community detection methods; 2) Overall data across individuals (ADD); 3) Overall data across participants, PCC and mPFC separately; 4) Day 1 vs Day 2 overall; 5) Day 1 vs Day 2 PCC vs mPFC; 6) Across sessions overall; 7) Across sessions PCC vs mPFC; 8) Sliding windowper subject overall; 9) Sliding window PCC vs mPFC.
+We compared the agreement within subjects against across subjects by computing the ratio of the mean RI within and between subjects.
+Ratios close to one denote good alignment across subjects, while ratios over one mean that partitions per subject were more stable than what you would expect against every other subject.
 
@@
 This first step just gives an idea of the level of agreement within and between subjects.
-As a first measure, we use the adjusted rand index (RI) to estimate the level of agreement between partitions.
+As a first measure, we use the adjusted rand index (RI) to estimate the level of agreement between spectral partitioning and modularity.
 RI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g.
@@
 This adds evidence to the division of these areas into DMN and non-DMN during rest.
-Due to this high agreement, we focus on results using spectral partitioning, as it paints a clearer picture of the division of interest.
 

### 2018-08-31 Manuscript.Rmd
much work on the methods, plus adding references from Mendeley through a bib file

@@
   html_document: default
+bibliography: mPFC_paper.bib
 ---
@@
 This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
-Next, we took the exponential of the correlations, Fisher transformed them (i.e.
-tanh) so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
+Next, we applied Fisher's r to z transformation, and took the exponential of the correlations so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
 As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately; 2) the concatenated timeseries from each pair of daily sessions; 3) each subject's dataset; and 4) on each step of a sliding window analysis (see Evaluation for more details).
@@
 
-Where I is the identity matrix, D is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its correlations with every other vertex), and W is the correlation matrix.
+Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
+the sum of its correlations with every other vertex), and $W$ is the correlation matrix.
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
@@
 The resulting ratio is compared to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions.
-Because of this, the adjusted rand index is a simple metric that determines the percentage agreement of any two partitions that is agnostic to the labeling scheme.
+Because of this, the adjusted rand index is a simple metric that determines the percentage of agreement between any two partitions that is agnostic to the labeling scheme.
 *(SHOULD WE INCLUDE THIS?) On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions.

### 2018-08-31 Manuscript.Rmd
More work on methods and figures

@@
 output:
+  html_document: default
   word_document: default
   pdf_document: default
-  html_document: default
 bibliography: mPFC_paper.bib
@@
 
-``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
-# setwd('./For_HCP')
-# temp <- list.files(pattern = '*Binary*')
-# FB <- lapply(temp, read.table)
-# Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
-# FB_Means <- rowMeans(Summed)
-# 
-# write.table(file = 'propDMN_all.txt', FB_Means, row.names = F, col.names = F, dec = ".")
-```
-
 ## Abstract
@@
 Because of this, the adjusted rand index is a simple metric that determines the percentage of agreement between any two partitions that is agnostic to the labeling scheme.
-*(SHOULD WE INCLUDE THIS?) On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions.
+*(SHOULD WE INCLUDE THIS?
+The mutual information results would probably need to go in the supplemental materials) On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions.
 While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case.
@@
 
-The topographies were compared: 1) Across community detection methods; 2) Overall data across individuals (ADD); 3) Overall data across participants, PCC and mPFC separately; 4) Day 1 vs Day 2 overall; 5) Day 1 vs Day 2 PCC vs mPFC; 6) Across sessions overall; 7) Across sessions PCC vs mPFC; 8) Sliding windowper subject overall; 9) Sliding window PCC vs mPFC.
+We performed a number of comparisons among partitions.
+First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns.
+Modularity and SP show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018].
+Their alignment would thus give us confidence in the validity of the resulting topologies.
+Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group (ADD TO CODE).
+We then estimate the level of agreement between scans taken across days (i.e.
+pairs of daily left-right and right-left phase encoding sessions).
+If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement for the same subject across days than either day compared to every other subject.
+We then extend this idea by computing the overall agreement across all sessions.
+Similarly, we expect that sessions within subject will show higher agreement than between subjects.
+Finally, we perform a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37) 8) comparing each window's functional pattern against the clustering derived from the whole subject's data.
+This approach should give us a sense of the dynamics of the functional organization of mPFC during rest.
+We complement this analysis by calculating the proportion of times each surface vertex was affiliated with the DMN community across time, as well as computing the flexibility of each node (i.e.
+the number of times each vertex changed affiliation across time).
+Given that the functional heterogeneity of brain areas is unevenly distributed across the brain [@Mueller2013], we also performed these comparisons for PCC and mPFC separately.
+Given what we know about these general regions, we expected PCC to be well aligned across participants, and stable within subjects.
+On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject.
 We compared the agreement within subjects against across subjects by computing the ratio of the mean RI within and between subjects.
-Ratios close to one denote good alignment across subjects, while ratios over one mean that partitions per subject were more stable than what you would expect against every other subject.
+Ratios close to one denote good alignment across subjects, while ratios significantly higher than one suggest that partitions per subject were more stable than what you would expect against every other subject.
 
 \newpage
+
+### *Estimation of Noise Effects*
+### *Seed-based FC vs Community Detection*
+### *Structural Characteristics*
 
@@
 
-```{r Meta-analysis ROIs, out.width="60%", fig.align = "center"}
+```{r Meta-analysis ROIs, out.width="60%", fig.align = "center", fig.cap= "**Figure 1.** Template atlas from [-@Glasser2013] (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
+Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
 include_graphics("./Images/ROIS.png")
@@
 This result could be due to signal degeneration in mPFC (that said, it is worth noting that the topological patterns remain mostly the same for both PCC and mPFC throughout the SW analysis).
-To account for this, we computed the coefficient of variation for each vertex in each subject's minimally preprocessed fMRI data (i.e.
+To account for this, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
 mean of each vertex's time points over their standard deviation).
-The next plot shows the pooled subject-wise mean SNR for PCC and mPFC vertices, and indicates that the SNR is lower for mPFC than PCC, which could negatively affect our results.
+The next plot shows the pooled subject-wise mean tSNR for PCC and mPFC vertices, and indicates that the tSNR is lower for mPFC than PCC, which could negatively affect our results.
 
@@
 
-To formally examine this, for each subject we compared the SNR values of all vertices between PCC and mPFC (`r nSubj` permutation tests).
-About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected; mean Cohen's D = `r mean(SNR_PCCvsPFC_ES)`).
+To formally examine this, for each subject we compared the tSNR values of all vertices between PCC and mPFC (`r nSubj` permutation tests, 5000 iterations).
+About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected; mean Cohen's D = `r round(mean(SNR_PCCvsPFC_ES), digits = 2)`).
 In addition, we found that the degree of signal to noise for each vertex showed significant negative correlations with flexibility, a graph-theoretic index that measures the proportion of times a node in a network changed affiliation across partitions (mean correlation across subjects = `r round(mean(SNR_vs_Flex), digits = 2)`).
@@
 
+It will also be good to note that there is concurrent debate on the ground truth of community detection.
+In other fields, identifying a community structure is not necessarily associated with the true organization of the network.
+What happens is that you might find a tangential grouping that gives you information different from your original goal [@Clauset2004]
+
 ## References

### 2018-09-01 Manuscript.Rmd
Fixed some captions

@@
 output:
+  pdf_document: default
+  word_document: default
   html_document: default
-  word_document: default
-  pdf_document: default
 bibliography: mPFC_paper.bib
@@
 We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
-First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013).
+First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2016).
 We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning.
@@
 
-\newpage
-
 ### *Estimation of Noise Effects*
@@
 
+\newpage
+
 ## Results
@@
 
-```{r Meta-analysis ROIs, out.width="60%", fig.align = "center", fig.cap= "**Figure 1.** Template atlas from [-@Glasser2013] (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
+```{r Meta-analysis ROIs, out.width="60%", fig.align = "center", fig.cap= "Figure 1.
+Template atlas from Glasser et al.
+[-@Glasser2016] (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
 Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
-include_graphics("./Images/ROIS.png")
+include_graphics("./Images/ROIS2.png")
 ```
@@
 
-```{r Template partition, out.width="50%", fig.align = "center"}
+```{r Template partition, out.width="60%", fig.align = "center", fig.cap = "Figure 2.
+Brain partition for an example subject (100307).
+Fiedler vector values (top) are mapped onto the brain, dividing it into positive and negative communities.
+The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
 # Load data
@@
 
-include_graphics("./Images/template.png")
+# fig caption
+# "Figure 2.
+Brain partition for an example subject (100307).
+Fiedler vector values (top) are mapped onto the brain, dividing it into positive and negative communities.
+The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."
+
+#include_graphics(c("./Images/newPattern.png", "./Images/newPattern_binary.png"))
+include_graphics("./Images/newPattern_both.png")
 ```

### 2018-09-03 Manuscript.Rmd
Many changes to figures, methods, and ensuring that the new ROIs work

@@
 output:
+  html_document: default
+  word_document: default
   pdf_document: default
-  word_document: default
-  html_document: default
 bibliography: mPFC_paper.bib
@@
 
+``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
+setwd('./For_HCP')
+temp <- list.files(pattern = '*Binary*')
+FB <- lapply(temp, read.table)
+Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
+FB_Means <- rowMeans(Summed)
+
+```
+
 ## Abstract
@@
 
-To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,564 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
+To establish each subject's network, we selected all the vertices contained within the ROIs (n = **5,564 (UPDATE)** per subject) and computed the Pearson correlation of the time series for every pair of vertices.
 This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
@@
 DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects).
-Importantly, given the high density of these networks (**Add to results**), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).
+Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).
 
@@
 
-The following shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
+```{r Density calculation, out.width="60%", fig.align = "center"}
+# Load density data
+setwd('./Densities/')
+temp <- list.files()
+Densities <- do.call(rbind, lapply(temp, read.csv))
+
+# Get the mean density for all data, daily scans, and sessions
+# Check distributions, since median might be better
+mdAll <- mean(Densities$Density[grep("Overall", Densities$Type)])
+sddAll <- sd(Densities$Density[grep("Overall", Densities$Type)])
+mdDay <- mean(Densities$Density[grep("Day", Densities$Type)])
+mdSess <- mean(Densities$Density[grep("Session", Densities$Type)])
+```
+
+First, we estimated each individual's DMN coverage using the whole time series (4800 TRs).
+On average, networks had high densities (i.e.
+highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r sddAll`).
+Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
 
@@
 Brain partition for an example subject (100307).
-Fiedler vector values (top) are mapped onto the brain, dividing it into positive and negative communities.
+Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
 The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}

### 2018-09-03 graphAnalysis_solo.R

@@ -1082,8 +1082,7 @@ mPFC_only <- c("_a24_",
                "_10v_",
                "_OFC_",
                "_s32_",
-               "_p24_",
-               "_10d_")
+               "_p24_")
 
 # Cortical surface for plotting
 labelPerVertex <- read.table('labelPerVertex.csv', header = F)

### 2018-09-03 Manuscript.Rmd
Added a test to the graph analysis script, and wrote a draft on the noise methods section

@@
 output:
+  word_document: 
+    reference_docx: Style_reference.docx
+  pdf_document: default
   html_document: default
-  word_document: default
-  pdf_document: default
 bibliography: mPFC_paper.bib
@@
 
+Given the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we tested the association of their absolute magnitude with the proportion of times a vertex was part of the DMN community during the sliding window analysis.
+To do this, we performed a mixed effects logistic regression model in which each subject's eigenmap values were used as random predictors of the proportion of times they participated in the DMN community.
+
 ### *Estimation of Noise Effects*
+
+BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis2008].
+It was thus important to quantify the potential influence of noise in our findings.
+We examined this through two complementary steps.
+First, we computed the temporal signal-to-noise ratio (tSNR) of all the vertices in the ROIs from HCP minimally preprocessed data (i.e.
+prior to the complementary denoising described in the "fMRI Data" section).
+For each subject, we compared the mean tSNR between mPFC and PCC through a permutation analysis (5000 iterations), and report the percentage of subjects who had a significantly lower mean tSNR in mPFC.
+Next, we estimated which vertices within mPFC had a stronger relationship to the overall dynamics of DMN.
+To do this, we computed the mean time series of each subject's DMN map, which was then predicted by the time series each mPFC vertex in a mass univariate model.
+The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex.
+If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects.
+We then compare this dorsal-to-ventral gradient to one displaying tSNR values, as the latter should convey a linear relationship between noise and dorsal-to-ventral topographical placement.
+
 ### *Seed-based FC vs Community Detection*

### 2018-09-03 graphAnalysis_solo.R

@@ -1084,6 +1084,11 @@ mPFC_only <- c("_a24_",
                "_s32_",
                "_p24_")
 
+# Little test to ensure that the ROIs match before running the whole thing
+if (FALSE %in% (mPFC_only %in% c(mPFC_only, "Blah"))) {
+  stop("mPFC-only and Overlapping ROIs don't match")
+}
+
 # Cortical surface for plotting
 labelPerVertex <- read.table('labelPerVertex.csv', header = F)
 labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[,2:6]

### 2018-09-04 Manuscript.Rmd
Added a bit on Seed-FC methods

@@
 ### *Seed-based FC vs Community Detection*
+
+A potential downfall of the present approach is that it can be computationally demanding, while more direct seed-based functional connectivity methods could provide sufficient approximations of an individual's DMN orgnization.
+We examined this issue by estimating mPFC functional maps from its vertex-wise functional coupling with the mean PCC activation.
+For each subject, we computed the mean time series of all vertices contained within the PCC region of a standard DMN arrangement [@Yeo2011], and correlated it (Pearons) with the time series of every mPFC vertex from our ROIs.
+
 ### *Structural Characteristics*

### 2018-09-04 Manuscript.Rmd
Finished the methods backbone

@@
 output:
+  pdf_document: default
+  html_document: default
   word_document: 
     reference_docx: Style_reference.docx
-  pdf_document: default
-  html_document: default
 bibliography: mPFC_paper.bib
@@
 We examined this issue by estimating mPFC functional maps from its vertex-wise functional coupling with the mean PCC activation.
-For each subject, we computed the mean time series of all vertices contained within the PCC region of a standard DMN arrangement [@Yeo2011], and correlated it (Pearons) with the time series of every mPFC vertex from our ROIs.
-
-### *Structural Characteristics*
-
-\newpage
+For each subject's concatenated day 1 and day 2 scans, we computed the mean time series of all vertices contained within the PCC region of a standard DMN arrangement [@Yeo2011], and correlated it (Pearons) with the time series of every mPFC vertex from our ROIs.
+The resulting day 1 and day 2 mPFC maps were then correlated within and between subjects in three ways: 1) between correlation-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps.
+These spatial correlations are aimed to determine the day-to-day stability of each approach, as well as their level of agreement.
+These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [-@Kon2018] [-@Mueller2013]).
+We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
+
+### *Anatomical Correspondence*
+
+Finally, we examined whether each idiosyncrasies in functional topology corresponded to outstanding anatomical features.
+To do this, we correlated each subject's Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex).
+These simple correlations are aimed to provide a sense of this possible relationship, which can be studied in depth in the future.
+
+\bigskip
 

### 2018-09-04 Manuscript.Rmd
Starting the results

@@
 
-Figure 1 shows the resulting ROIs from the meta-analysis.
-Areas in blue denote the 17 overlapping ROIs, which landed mostly on the medial wall, as well as a region in IPL and TPJ.
-Area 7m (in red) was the only one to show unique affiliation, which was significant for DMN.
+We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions [@Glasser2016] across DMN and SV literatures.
+Using each literature's mean number of reports per area as the null probability, one-way chi-squared tests of proportions were used to identify regions that were significantly present in their respective literatures.
+The resulting lists were used to identify the set of overlapping brain areas.
+Unique areas were then determined by permuting the affiliation of each study (i.e.
+DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature.
+
+Figure 1 shows the resulting ROIs from these analyses.
+As expected, overlapping areas included 15 bilateral regions in PCC (**Probably need to add their respective stats here** 31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi).
+Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, p < 0.001).
 

### 2018-09-05 Manuscript.Rmd

@@
 
-We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions [@Glasser2016] across DMN and SV literatures.
-Using each literature's mean number of reports per area as the null probability, one-way chi-squared tests of proportions were used to identify regions that were significantly present in their respective literatures.
-The resulting lists were used to identify the set of overlapping brain areas.
+We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions [@Glasser2016] across DMN and SV literatures (see Methods).
+Using each literature's mean number of reports per area as the null probability (DMN = ; SV = ), one-way chi-squared tests of proportions were used to identify regions that were significantly present in their respective literatures.
+The resulting lists were used to identify the set of common brain areas.
 Unique areas were then determined by permuting the affiliation of each study (i.e.

### 2018-09-05 graphAnalysis_solo.R
Updated the computation of ROIs in graph_solo

@@ -1327,28 +1327,32 @@ if (Meta == T) {
   
   ## ALTERNATIVE AND MORE PARSIMONIOUS WAY TO GET MOST OF THE WAY THERE
   # First, load the raw count csv files
+  valCounts <- read.csv2('decCounts.csv', sep = ",")
+  dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
   
   # Then, get the means of the counts per domain
-  BV <- round(mean(boostrap(valCounts$Counts)))
+  BV <- round(mean(bootstrap(valCounts$Counts)))
   BD <- round(mean(bootstrap(dmnCounts$Counts)))
   
   # Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
   # than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
-  valTest <- numeric()
   for (i in seq(valCounts$Counts)) {
     indx <- valCounts$Counts[i]
-    valTest[i] <- prop.test(indx, 27, alternative = "greater", p = BV/27)$p.value
+    tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
+    valCounts$Chi[i] <- tempTest$statistic
+    valCounts$pVal[i] <- tempTest$p.value
   }
   
-  dmnTest <- numeric()
   for (i in seq(dmnCounts$Counts)) {
     indx <- dmnCounts$Counts[i]
-    dmnTest[i] <- prop.test(indx, 77, alternative = "greater", p = BD/77)$p.value
+    tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
+    dmnCounts$Chi[i] <- tempTest$statistic
+    dmnCounts$pVal[i] <- tempTest$p.value
   }
   
   # Retain only the significant parcels
-  t1 <- valCounts$Label[valTest < 0.05]
-  t2 <- dmnCounts$Label[dmnTest < 0.05]
+  t1 <- valCounts$Label[valCounts$pVal < 0.05]
+  t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
   
   # Remove hemispheric references 
   t1 <- unique(substring(t1,2))

### 2018-09-05 Manuscript.Rmd
Updated the references to a format that will read .bib files

@@
 output:
-  pdf_document: default
-  html_document: default
   word_document: 
     reference_docx: Style_reference.docx
+  html_document: default
+  pdf_document: default
 bibliography: mPFC_paper.bib
@@
 
-  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011).
-However, the distributed cortical valuation system also includes posterior cingulate and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall (Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011).
+  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value (SV) assigned to decision outcomes [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
+However, the distributed cortical valuation system also includes posterior cingulate (PCC) and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall [@Fox2005; @Laird2009; @Yeo2011].
 This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.
@@
   Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions.
-Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009).
-Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016).
-More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017).
+Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation [@Bartra2013] and DMN [@Laird2009].
+Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena [@DelaVega2016].
+More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017].
 These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system.
-However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area (Kragel et al., 2018).
+However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area [@Kragel2018].
 While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data.
 Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject.
-However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
+However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013] compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
 
   Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
-Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations (Laumann et al., 2015; Gordon et al., 2017; Gratton et al., 2018).
-Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018).
-In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018).
+Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018].
+Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2016].
+In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity [@Braga2017].
 It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
@@
 
-  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008).
+  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments [@Logothetis].
 As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time.
-Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2017; Laumann et al., 2015; Tobyne et al., 2018).
-A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018).
-From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018).
-Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016).
-Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups (Garcia et al., 2018).
+Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017].
+A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics [@Bassett2018a].
+From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017].
+Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016].
+Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017].
 However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option.
@@
 The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e.
-the Fiedler vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975).
-SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data (BLAH.) This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.
+the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003].
+SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018].
+This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.
 
@@
 We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
-First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2016).
+First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas [@Glasser2016].
 We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning.
@@
 
-We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation (Bartra et al., 2010) (n = 27 studies) and DMN (Laird et al., 2009) (n = 77).
+We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation [@Bartra2010] (n = 27 studies) and DMN [@Laird2009] (n = 77).
 These represent the surviving areas post-statistical thresholding from each study.
 For each peak volumetric coordinate, 10 mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer.
-The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (Glasser et al., 2016).
+The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (360 regions)[@Glasser2016].
 This produced a list of standardized parcels that were reported on each study.
@@
 We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al.
-(2011).
+[-@Yeo2011].
 We permuted the label of every study (i.e.
@@
 
-In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP; Van Essen et al., 2013; www.humanconnectome.org) Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects).
+In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP) [@VanEssen2012] Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects).
 Each subject's data was acquired over two days at Washington University in St.
@@
 
-Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which includes considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152-based normalization, all scans went through a number of additional refinements (Tobyne et al., 2017).
-These included band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), as well as mean greyordinate signal regression (MGSR; Burgess et al., 2016).
+Beyond the in-house minimally preprocessed pipeline from HCP [@Glasser2013], which includes considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152-based normalization, all scans went through a number of additional refinements [@Tobyne2017].
+These included band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), as well as mean greyordinate signal regression [@Burgess2016].
 Only subjects with both left-right and right-left phase encoding were included (i.e.
@@
 
-To establish each subject's network, we selected all the vertices contained within the ROIs (n = **5,564 (UPDATE)** per subject) and computed the Pearson correlation of the time series for every pair of vertices.
+To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,319 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
 This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
 Next, we applied Fisher's r to z transformation, and took the exponential of the correlations so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
-As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately; 2) the concatenated timeseries from each pair of daily sessions; 3) each subject's dataset; and 4) on each step of a sliding window analysis (see Evaluation for more details).
+As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Evaluation for more details).
 
@@
 Communities (i.e.
-clusters) were identified by means of spectral partitioning (SP; Fiedler, 1975).
-First, each adjusted network was represented as an n x n correlation matrix (where n = number of vertices within the ROIs, 5,564).
+clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2018].
+First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,319).
 This matrix was then transformed into its normalized Laplacian form
@@
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
-This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected (Fiedler, 1975).
+This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975].
 Given that this data-driven method is agnostic to the prevalent function of each community (i.e.
 DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects).
-Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks (Fortunato & Hric, 2016).
-
-In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization (using the algorithm from Clauset et al., XXXX).
+Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].
+
+In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization using the algorithm from Clauset et al.
+[-@Clauset2004].
 This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
@@
 
-In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (RI; Rand, 2012) as the reference metric of agreement between two clusterings.
+In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (ARI) [@Hubert1985] as the reference metric of agreement between two clusterings.
 The adjusted rand index estimates the rate at which every pair of nodes in partition A were equally assigned to the same/different parcels on partition B, over all possible changes (e.g.
@@
 Their alignment would thus give us confidence in the validity of the resulting topologies.
-Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group (ADD TO CODE).
+Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group (**ADD TO CODE**).
 We then estimate the level of agreement between scans taken across days (i.e.
@@
 These spatial correlations are aimed to determine the day-to-day stability of each approach, as well as their level of agreement.
-These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [-@Kon2018] [-@Mueller2013]).
+These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [-@Kon2018; -@Mueller2013]).
 We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
@@
 To do this, we correlated each subject's Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex).
-These simple correlations are aimed to provide a sense of this possible relationship, which can be studied in depth in the future.
+These simple correlations are aimed to provide a coarse sense of this possible relationship, which can be studied in depth in the future.
 
@@
 
-We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions [@Glasser2016] across DMN and SV literatures (see Methods).
-Using each literature's mean number of reports per area as the null probability (DMN = ; SV = ), one-way chi-squared tests of proportions were used to identify regions that were significantly present in their respective literatures.
+``` {r ROI computation, echo=FALSE, message = FALSE}
+  ## ROI definition
+  # First, load the raw count csv files
+  valCounts <- read.csv2('decCounts.csv', sep = ",")
+  dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
+
+  # Then, get the means of the counts per domain
+  tempBoot <- bootstrap(valCounts$Counts)
+  BV <- round(mean(tempBoot))
+  BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
+  tempBoot <- bootstrap(dmnCounts$Counts)
+  BD <- round(mean(tempBoot))
+  BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
+  rm(tempBoot)
+
+  # Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
+  # than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
+  for (i in seq(valCounts$Counts)) {
+    indx <- valCounts$Counts[i]
+    tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
+    valCounts$Chi[i] <- tempTest$statistic
+    valCounts$pVal[i] <- tempTest$p.value
+  }
+
+  for (i in seq(dmnCounts$Counts)) {
+    indx <- dmnCounts$Counts[i]
+    tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
+    dmnCounts$Chi[i] <- tempTest$statistic
+    dmnCounts$pVal[i] <- tempTest$p.value
+  }
+
+  # This part is just for reference, as the labels are loaded from a file
+  # # Retain only the significant parcels
+  # t1 <- valCounts$Label[valCounts$pVal < 0.05]
+  # t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
+  # 
+  # # Remove hemispheric references 
+  # t1 <- unique(substring(t1,2))
+  # t2 <- unique(substring(t2,2))
+  # 
+  # # And get the set of overlapping areas between literatures
+  # # This is missing some cingulate and PFC areas, and adds V2.
+  # # However, we can say that we are filling in the gap for completeness,
+  # # and removing V2 because it's demonstrably irrelevant.
+  # bothLbls_alt <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
+  # 
+  # # You could also try to permute the allocation of reports per literature,
+  # # and then perform a chi-squared per parcel. Get the max stat per iteration.
+  # # Now you have your null distribution.
+```
+
+We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions across DMN and SV literatures (see Methods).
+Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
+Using each literature's mean number of reports per area as the null probability (DMN = `r BD`, 95% CI [`r BDquant`]; SV = `r BV`, 95% CI [`r BVquant`]), one-way chi-squared tests of proportions were performed to identify regions that were significantly present in their respective literatures.
 The resulting lists were used to identify the set of common brain areas.
@@
 DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature.
+Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
 
 Figure 1 shows the resulting ROIs from these analyses.
-As expected, overlapping areas included 15 bilateral regions in PCC (**Probably need to add their respective stats here** 31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi).
+As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all p < 0.05).
+A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function.
 Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, p < 0.001).
@@
 
-First, we estimated each individual's DMN coverage using the whole time series (4800 TRs).
+With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 TRs).
+Each subject's network was constructed by performing pairwise correlations among the time series of all the vertices contained within the ROIs.
+After correcting for multiple tests, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
 On average, networks had high densities (i.e.
 highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r sddAll`).
+This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].
 Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
@@
 
+Mention the lack of interhemispheric distinction, citing Mackey and Petrides in regards to L-R diffs.
+
+## Acknowledgements
+Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
+
 ## References

### 2018-09-05 Manuscript.Rmd
Multiple updates to figure captions and formatting for pdf

@@
 output:
+  pdf_document: default
+  html_document: default
   word_document: 
     reference_docx: Style_reference.docx
-  html_document: default
-  pdf_document: default
 bibliography: mPFC_paper.bib
+header-includes:
+    - \usepackage{setspace}\doublespacing
 ---
@@
 Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018].
-Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2016].
+Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
 In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity [@Braga2017].
@@
 
-We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation [@Bartra2010] (n = 27 studies) and DMN [@Laird2009] (n = 77).
+We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation [@Bartra2013] (n = 27 studies) and DMN [@Laird2009] (n = 77).
 These represent the surviving areas post-statistical thresholding from each study.
@@
 Communities (i.e.
-clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2018].
+clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003].
 First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,319).
@@
 Their alignment would thus give us confidence in the validity of the resulting topologies.
-Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group (**ADD TO CODE**).
+Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group.
 We then estimate the level of agreement between scans taken across days (i.e.
@@
 
-BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis2008].
+BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis].
 It was thus important to quantify the potential influence of noise in our findings.
@@
 These spatial correlations are aimed to determine the day-to-day stability of each approach, as well as their level of agreement.
-These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [-@Kon2018; -@Mueller2013]).
+These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [@Kong2018; @Mueller2013]).
 We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
@@
 
+``` {r Load Summary Data}
+# Load data
+setwd('./Summary/')
+temp <- list.files()
+subjList <- sapply(temp, substring, first=1, last=6)
+Summaries <- lapply(temp, read.csv)
+nSubj <- length(Summaries)
+```
+
 ```{r Density calculation, out.width="60%", fig.align = "center"}
@@
 With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 TRs).
-Each subject's network was constructed by performing pairwise correlations among the time series of all the vertices contained within the ROIs.
+Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nrow(Summaries[[1]])` total vertices).
 After correcting for multiple tests, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
@@
 The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
-# Load data
-setwd('./Summary/')
-temp <- list.files()
-subjList <- sapply(temp, substring, first=1, last=6)
-Summaries <- lapply(temp, read.csv)
-nSubj <- length(Summaries)
-
-# fig caption
-# "Figure 2.
-Brain partition for an example subject (100307).
-Fiedler vector values (top) are mapped onto the brain, dividing it into positive and negative communities.
-The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."
 
@@
 This first step just gives an idea of the level of agreement within and between subjects.
-As a first measure, we use the adjusted rand index (RI) to estimate the level of agreement between spectral partitioning and modularity.
+As a first measure, we use the adjusted rand index (ARI) to estimate the level of agreement between spectral partitioning and modularity.
 RI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g.
@@
 
-``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE, fig.cap = "Figure 3.
+Distribution of ARI indices when comparing modularity and spectral partitioning.
+The distribution shows overall high agreement.
+(Will probably remove this figure)"}
 # Cross-method
@@
 
-The total number of subjects is `r nSubj`.
 The distribution suggests that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
@@
 
-``` {r Partition comparison: all 2, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: all 2, fig.align="center", fig.width = 5, fig.height = 5, fig.cap = "Figure 4.
+Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
+PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}
 # Across subjects
@@
 
-``` {r Partition comparison: halves, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: halves, fig.align="center", fig.width = 8, fig.height = 4, fig.cap = "Figure 5.
+Similarity matrices showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right).
+These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
 # Select 10 subjects from the sample to display
@@
 
-``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 6.
+mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI.
+PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE, cache = TRUE}
 # Now compare all possible pairs of subjects
@@
           geom_hline(yintercept = 1) +
-          labs(y = "RI Ratio", x = "") + 
+          labs(y = "ARI Ratio", x = "") + 
           theme_classic()
@@
 This is important because it shows that we can derive very stable topological features using community detection, even though mPFC has relatively low signal to noise ratio.
-Low intra-subject and high inter-subject variability of DMN partitions is in agreement with previous work (Laumann 2015; Gordon et al., 2017; Braga & Buckner, 2017; Kong...Yeo, 2018).
+Low intra-subject and high inter-subject variability of DMN partitions is in agreement with previous work [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018).
 Graph-based community detection might thus be a better way to detect stable functional topologies, since high stability throughout days is a consistent feature of DMN topologies.

### 2018-09-06 Manuscript.Rmd
Working on results and fixed some references

@@
 output:
+  word_document: 
+    reference_docx: Style_reference.docx
   pdf_document: default
   html_document: default
-  word_document: 
-    reference_docx: Style_reference.docx
 bibliography: mPFC_paper.bib
@@
 FB_Means <- rowMeans(Summed)
-
+nSubj <- length(temp)
+rm(temp)
 ```
@@
 
-In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP) [@VanEssen2012] Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects).
+In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP) [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
 Each subject's data was acquired over two days at Washington University in St.
@@
 
-To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,319 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
+To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,081 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
 This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
-Next, we applied Fisher's r to z transformation, and took the exponential of the correlations so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
+Next, we applied Fisher's r to z transformation, and took the exponential of these values so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
 As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Evaluation for more details).
@@
 Template atlas from Glasser et al.
-[-@Glasser2016] (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
+(2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
 Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
@@
 Summaries <- lapply(temp, read.csv)
-nSubj <- length(Summaries)
 ```
@@
 
-With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 TRs).
+With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 total TRs from four scanning sessions over two days).
 Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nrow(Summaries[[1]])` total vertices).
-After correcting for multiple tests, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
+After correcting for multiple testing, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
 On average, networks had high densities (i.e.
@@
 This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].
+
 Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
+This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the partition.
+Since this is a data-driven approach, there is no a priori labeling for these communities.
+We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects.
+In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment.
+mPFC, on the other hand, is mostly populated by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them.
+This non-DMN section extends posteriorly onto pregenual cinglate cortex.
+Note that vmPFC does not encompass area a25, which is often related to negative emotional valuation [@Joyce2018].
+Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than SV [@Hiser2018].
 
@@
 
-This first step just gives an idea of the level of agreement within and between subjects.
-As a first measure, we use the adjusted rand index (ARI) to estimate the level of agreement between spectral partitioning and modularity.
-RI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g.
-clustered together in partition 1, but separately in 2).
-It is worth noting that the adjusted rand index has well known limitations (Fortunato & Hric, 2016).
+Before determining the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004].
+Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model.
+Since modularity is agnostic to the desired number of clusters, it was capable of finding more than two communities in our datset.
+Thus, if both methods agreed in the number and topological organization of the current communities, it would add confidence to our results.
+We quantified the cross-method agreement with the adjusted rand index (ARI).
+ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g.
+clustered together in partition 1, but separately in 2), and has the benefit of being agnostic to labeling schemes [@Hubert1985].
+Figure 3 shows the distribution of ARI values across subjects.
+**It is worth noting that the adjusted rand index has well known limitations (Fortunato & Hric, 2016).
 To compensate for this, we also performed all the upcoming analyses with the variation of information index (VI).
@@
 Both RI and VI analyses agreed in the results they yielded, but we only report RI due to its easier interpretability.
-This first plot shows the distribution of RI values between modularity and spectral partitioning for each subject.
+This first plot shows the distribution of RI values between modularity and spectral partitioning for each subject.**
 
@@
 
-``` {r Partition comparison: all 2, fig.align="center", fig.width = 5, fig.height = 5, fig.cap = "Figure 4.
+``` {r Partition comparison: all 2, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 4.
 Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
@@
 
+It's also worth mentioning that PCC is largely covered by DMN.
+Then why does this area overlap with SV?
+I think the Mueller paper mentions that PCC is an important hub of the brain, and perhaps subserves many cognitive functions.
+
+And write a portion on the lack of subcortical reward-related regions (i.e.
+striatum).
+Say something like 'incorporating the ventral striatum did notrefine these partitions through either method.
+This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future.
+Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DMN and SV'.
+
+Talk about how there are other community detection algorithms, and that modularity and SP over and underfit, respectively.
+However, SP eigenmaps have been found to provide relevant functional information.
+In addition, both modularity and SP rely on connectivity strength, and thus is amenable to the correlative nature of functional connectivity.
+
+Add a portion showing that summing up the binarized maps produces a map similar to the one produced by Margulies et al. and others.
+
 ## Acknowledgements

### 2018-09-07 Manuscript.Rmd
Added supplemental materials area

@@
     reference_docx: Style_reference.docx
+  html_document: default
   pdf_document: default
-  html_document: default
 bibliography: mPFC_paper.bib
@@
 
+  # Retain only the significant parcels
+  t1 <- valCounts$Label[valCounts$pVal < 0.05]
+  t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
+
+  # Remove hemispheric references
+  t1 <- unique(substring(t1,2))
+  t2 <- unique(substring(t2,2))
+
+  # Labels to put in text
+  dmnLbls <- gsub("ROI","", t2) 
+  dmnLbls <- gsub("_","", dmnLbls)
+  valLbls <- gsub("ROI","", t1) 
+  valLbls <- gsub("_","", valLbls)
+
   # This part is just for reference, as the labels are loaded from a file
-  # # Retain only the significant parcels
-  # t1 <- valCounts$Label[valCounts$pVal < 0.05]
-  # t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
-  # 
-  # # Remove hemispheric references 
-  # t1 <- unique(substring(t1,2))
-  # t2 <- unique(substring(t2,2))
-  # 
   # # And get the set of overlapping areas between literatures
@@
   # # and removing V2 because it's demonstrably irrelevant.
-  # bothLbls_alt <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
+  # bothLbls <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
   # 
@@
   # # Now you have your null distribution.
+
 ```
@@
 Figure 1 shows the resulting ROIs from these analyses.
+DMN included `r length(t2)` significant regions, while SV was comprised of `r length(t1)` (see Supplemental Table 1).
 As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all p < 0.05).
@@
 
-\bigskip
-\bigskip
-
 ### *Stability per subject*
@@
 
+## Supplemental Materials
+
+### *Table 1. Significant brain regions per literature*
+| Literature                     | Significant Brain Regions      |
+| :----------------------------- | -----------------------------: |
+| Default Mode Network           | `r paste(dmnLbls)`             |
+| Subjective Value               | `r paste(valLbls)`             |
+
 ## References

### 2018-09-07 Manuscript.Rmd
More work on the results and figure captions

@@
     reference_docx: Style_reference.docx
+  pdf_document: default
   html_document: default
-  pdf_document: default
 bibliography: mPFC_paper.bib
@@
 # This takes either a matrix of correlation values (vectors too, but manually compute pvals)
-# Normalization approach suggested in network textbook (equation 7.10)
+# Normalization approach suggested in network textbook (equation 7.10)
 fisherTanh <- function(Data = padjMatrix){
@@
 
-The distribution suggests that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
-The importance of this results lies in that while spectral partitioning forces a bipartition of the network, modularity does not.
-This adds evidence to the division of these areas into DMN and non-DMN during rest.
-
-Next, we examine how similar the partitions for PCC and mPFC are across subjects.
-Qualitative inspection of the brain community topologies shows good alignment for PCC, with a topologically similar mPFC pattern that shifts topographically across subjects.
-The following similarity matrix shows RIs for every pairwise comparison among all subjects for PCC (lower matrix) and PFC (upper) separately.
-Each row/column element is a single subject.
-
-\bigskip
-
-``` {r Partition comparison: all 2, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 4.
-Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
-PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
 # Across subjects
@@
 RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+RI_all_between_lowtri <- RI_all_between[lower.tri(RI_all_between)]
+
 posteriorIndx <- Summaries[[1]]$y < 0
@@
 RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+
+# Let's compare stuff
+testPCC <- RI_PCC[lower.tri(RI_PCC)]
+testPFC <- RI_PFC[lower.tri(RI_PFC)]
+Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
+Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+```
+
+The distribution suggests that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
+The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not.
+This adds evidence to the division of these areas into DMN and non-DMN during rest.
+
+Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was considerable agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+However, qualitative inspection of the brain community topologies shows good alignment for PCC, with a topologically similar mPFC pattern that shifts topographically across subjects.
+To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 4).
+Indeed, this analysis showed that the functional topology of PCC is well maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), while mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) showed significantly lower levels of agreement (paired permutation, p = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+
+``` {r Partition comparison: all 2 plot, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 4.
+Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
+PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}
+
 # par(mfrow = c(1,2))
@@
 
-# Let's compare stuff
-testPCC <- RI_PCC[lower.tri(RI_PCC)]
-testPFC <- RI_PFC[lower.tri(RI_PFC)]
-Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
-Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-```
-
-The results match the qualitative observations mentioned above, with overall higher agreement for PCC (paired permutation, p = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
-However, the heterogeneity of mPFC could arise from noise in the signal.
-As a way to test for subject specificity, we used each subject's session data to compare day 1 vs day 2 clusters, as well as a session-based analysis.
-
-\bigskip
+```
+
 \bigskip
@@
 
-``` {r Partition comparison: halves, fig.align="center", fig.width = 8, fig.height = 4, fig.cap = "Figure 5.
-Similarity matrices showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right).
-These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
 # Select 10 subjects from the sample to display
@@
 RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-
+```
+
+``` {r Partition comparison: halves plot, fig.align="center", fig.width = 6, fig.height = 4, fig.cap = "Figure 5.
+Similarity matrices showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right).
+These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
 # plots
@@
 \bigskip
-\bigskip
 
@@
 
-``` {r Partition comparison: session similarity matrices, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: session similarity matrices, echo=FALSE, message = FALSE, cache = TRUE}
 # Select 10 subjects from the sample to display
@@
 RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-
+```
+
+``` {r Partition comparison: session similarity matrices plot, fig.align="center", fig.width = 6, fig.height = 4, fig.cap = "Figure 7.
+Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right).
+The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
 # plot
@@
 
-``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 8.
+Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions.
+Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE, cache = TRUE}
 ## Brain storming:
@@
 
-\bigskip
-
-``` {r Stability per subject: Overall, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Stability per subject: Overall, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 9.
+ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE, cache = TRUE}
 # Load files
@@
 
+grid.arrange(SC_plot, SC_sd_plot, ncol = 2)
+
+```
+
+While some subjects show considerable variability, the overall trend is of fair stability.
+An interesting feature of spectral partitioning is that the Fiedler vector was tightly related to the proportion of times any given cortical vertex was affiliated with the DMN throughout the sliding windows.
+Meaning, the higher the absolute value in the Fiedler vector for a given vertex, the more persistent its relationship was with its corresponding community in time.
+The following plot shows this relationship for each subject (gray smoothed lines), as well as the fitted values from a logistic mixed effects model (black line; model: prop.
+DMN ~ Fiedler vector, subjects as random intercepts; beta = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, p < 0.001).
+
+``` {r Stability per subject: Fiedler vector vs prop.
+DMN plot, fig.align="center", fig.width=3.5, fig.height=3.5, fig.cap = "Figure 10.
+Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
+Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
 # Fiedler Vector x proportion of times a vertex was affiliated with DMN
@@
 
-grid.arrange(SC_plot, SC_sd_plot, ncol = 2)
-
-```
-
-\bigskip
-
-While some subjects show considerable variability, the overall trend is of fair stability.
-An interesting feature of spectral partitioning is that the Fiedler vector, which provides signed values to divide a network into positive and negative communities, was tightly related to the proportion of times any given cortical vertex was affiliated with the DMN throughout the fMRI sessions.
-Meaning, the higher the absolute value in the Fiedler vector for a given vertex, the more persistent its relationship was with its corresponding community in time.
-The following plot shows this relationship for each subject (gray smoothed lines), as well as the fitted values from a logistic mixed effects model (black line; model: prop.
-DMN ~ Fiedler vector, subjects as random intercepts; beta = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, p < 0.001).
-
-\bigskip
-
-``` {r Stability per subject: Fiedler vector vs prop. DMN plot, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
 SC_FVvPDMN_plot
 ```
-
-\bigskip
 
@@
 
-``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, fig.cap = "Figure 11.
+ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle).
+Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE, cache = TRUE}
 ## Check stability for PCC and mPFC separately
@@
 
+This suggests that, while the agreement of each window with the overall time series was stable for both PCC and mPFC (low SD, right plot), the overall agreement of mPFC is lower (paired permutation, p = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+
 \bigskip
 
-This suggests that, while the agreement of each window with the overall time series was stable for both PCC and mPFC (low SD, right plot), the overall agreement of mPFC is lower (paired permutation, p = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+### *Potential Noise Effects*
+
 This result could be due to signal degeneration in mPFC (that said, it is worth noting that the topological patterns remain mostly the same for both PCC and mPFC throughout the SW analysis).
@@
 
-\bigskip
-
-``` {r Stability per subject: SNR Comparison, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Noise Effects: tSNR Comparison, fig.align="center", fig.width=3.5, fig.height=3.5, fig.cap = "Figure 12.
+Mean tSNR for mPFC and PCC across participants.
+This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE, cache = TRUE}
 ## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
@@
   scale_fill_manual(values = Cols[seq(2)]) +
-  labs(x = "", y = "SNR") +
+  labs(x = "", y = "tSNR") +
   theme(text = element_text(size=35)) +
@@
 ```
-
-\bigskip
 
@@
 
-``` {r Stability per subject 4, fig.align="center", fig.width=5, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Noise Effects: Per-subject Fiedler by R-sqd, fig.align="center", fig.width=4, fig.height=4, fig.cap = "Figure 13.
+Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
 setwd('./Variance/')
@@
 # These match perfectly on the brain when inspected qualitatively
-v1 <- qplot(data = allVariance, FiedlerVec, Rsquared, color = SubjID, fill = SubjID, geom = "smooth", show.legend = F) + labs(x = "Fiedler Vector Values", y = "R-Squared Values") + theme_classic()
+v1 <- ggplot(data = allVariance) + 
+  geom_smooth(aes(FiedlerVec, Rsquared, group = SubjID), fill = "gray70", color = "gray30", show.legend = F) + 
+  labs(x = "Fiedler Vector Values", y = "R-Squared Values") + 
+  theme_classic()
 
@@
 
-\bigskip
-
 Next, we compared the R-squared values for PCC and mPFC separately per subject.
@@
 
-\bigskip
-
-``` {r Stability per subject 5, fig.align="center", fig.width=6, fig.height=4, echo=FALSE, message = FALSE}
+``` {r Noise Effects: Mean R-sqd mPFC and PCC, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 14.
+Differences in mean R-squared values for each region per participant.
+The figure shows that PCC vertices tend to be more coupled with the overall dynamics of DMN across subjects.", echo=FALSE, message = FALSE}
 v4
 ```
-
-\bigskip
 
@@
 
-``` {r Stability per subject 6, fig.align="center", fig.width=8, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Noise Effects: R-sqd vs tSNR, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 15.
+Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the least tSNR (left).
+However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE, cache = TRUE}
 # grid.arrange(v6, v7, ncol = 2)
-par(mfrow = c(1,2))
-smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
-              xlab = "R-squared Value",
-              ylab = "Z-Coordinate")
-
-smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
-              xlab = "Coefficient of Variation (SNR)",
-              ylab = "")
-```
-
-\bigskip
+# par(mfrow = c(1,2))
+# smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
+#               xlab = "R-squared Value",
+#               ylab = "Z-Coordinate")
+# 
+# smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
+#               xlab = "Coefficient of Variation (SNR)",
+#               ylab = "")
+
+tempVariance <- allVariance[allVariance$Region == "mPFC", ]
+s1 <- ggplot(data = allVariance, aes(Rsquared, tempZ)) +
+  geom_bin2d(bins = 250) +
+  scale_fill_continuous(low = "grey30", high = "grey70") +
+  geom_density2d(color = Cols[2]) +
+  labs(x = "R-squared value", y = "Z-Coordinate") +
+  theme_classic()
+
+s2 <- ggplot(data = allVariance, aes(varCoeff, tempZ)) +
+  geom_bin2d(bins = 250) +
+  scale_fill_continuous(low = "grey30", high = "grey70") +
+  geom_density2d(color = Cols[2]) +
+  labs(x = "tSNR", y = "Z-Coordinate") +
+  theme_classic()
+
+grid.arrange(s2, s1, ncol = 2)
+```
 
@@
 
-``` {r Correlation vs community detection: plot, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
 ## Between halves analysis for correlation and communities (mPFC only)
@@
 allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
+```
+
+``` {r Correlation vs community detection: plot, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 16.
+Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (7m-based) and the Fiedler vector.
+The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.", echo=FALSE, message = FALSE, cache = TRUE}
 corrplot(allHalfCombs, 
-         title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
+         #title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
          method = "color", 
@@
 
-\bigskip
-
 The previous plot shows the inter-methodological correspondence with an example subjects.
@@
 
-``` {r Correlation vs community detection: comparison plot, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE}
+``` {r Correlation vs community detection: comparison plot, fig.align="center", fig.width=4, fig.height=4, fig.cap = "Figure 17.
+Day 1 vs Day 2 oefficients of spatial correlations for every method, as well as between methods.
+Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo=FALSE, message = FALSE}
 # Day 1 vs Day 2 Spatial Correlation Comparison
@@
 
-``` {r 16.1.1., fig.align="center", fig.width=6, fig.height=4, echo=FALSE, message = FALSE}
-
-```
-
 ### *Structural correspondence*

### 2018-09-18 Manuscript.Rmd
update to manuscript

@@
 title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
-author: "Claudio Toro-Serey & Joseph T. McGuire"
+author: "Claudio Toro-Serey^1^ & Joseph T. McGuire^1^"
 output:
+  pdf_document: default
+  html_document: default
   word_document: 
     reference_docx: Style_reference.docx
-  pdf_document: default
-  html_document: default
 bibliography: mPFC_paper.bib
@@
 
-``` {r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}
+```{r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}
 
@@
 # This takes either a matrix of correlation values (vectors too, but manually compute pvals)
-# Normalization approach suggested in network textbook (equation 7.10)
+# Normalization approach suggested in network textbook (equation 7.10)
 fisherTanh <- function(Data = padjMatrix){
@@
 
+1. Department of Psychological and Brain Sciences, Boston University, Boston, USA
+
+Corresponding author:
+
+\newpage
+
 ## Abstract
@@
 Our approach shows promise in addressing this issue through future manipulations of valuation.
+
+**Keywords:** brain networks; DMN; individual differences
+
+\newpage
 
@@
 ``` {r ROI computation, echo=FALSE, message = FALSE}
+
   ## ROI definition
@@
 
-```{r Meta-analysis ROIs, out.width="60%", fig.align = "center", fig.cap= "Figure 1.
+```{r Meta-analysis ROIs, out.width = "60%", fig.align = "center", fig.cap= "Figure 1.
 Template atlas from Glasser et al.
@@
 Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
+
 include_graphics("./Images/ROIS2.png")
+
 ```
@@
 
-```{r Template partition, out.width="60%", fig.align = "center", fig.cap = "Figure 2.
+```{r Template partition (Fig.
+2), out.width="60%", fig.align = "center", fig.cap = "Figure 2.
 Brain partition for an example subject (100307).
@@
 
-``` {r Partition comparison: all cross-method agreement, fig.align="center", fig.width=4, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE, fig.cap = "Figure 3.
+``` {r Partition comparison: all cross-method agreement (Fig.
+3), fig.align="center", fig.width=3.5, fig.height=3.5, echo=FALSE, message = FALSE, cache = TRUE, fig.cap = "Figure 3.
 Distribution of ARI indices when comparing modularity and spectral partitioning.
@@
 
-``` {r Partition comparison: all 2 plot, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 4.
+``` {r Partition comparison: all 2 plot, fig.align="center", out.width = "40%", fig.cap = "Figure 4.
 Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
@@
 # mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
+par(xpd=T)
 corrplot(RI_PCC,
@@
          tl.pos = "n", 
-         tl.col = "black", 
+         tl.cex = 0.1, 
          cl.lim = c(0,1),
          cl.length = 3,
-         cl.pos = "b")
+         addgrid.col = "grey99",
+         cl.pos = "r",
+         mar = c(1,0,2,0))
 corrplot(RI_PFC, 
@@
          tl.pos = "n", 
-         tl.col = "black",
+         tl.cex = 0.1,
          cl.pos = "n",
+         addgrid.col = "grey90",
+         mar = c(1,0,2,0), 
          add = T)
+mtext(expression(bold("Subject Partitions")), line = 0.8)
+mtext(expression(bold("Subject Partitions")), side = 2, line = -2.5)
+mtext(expression(bold("PFC")), line = 0, at = par("usr")[1]+0.7*diff(par("usr")[1:2]), col = "steelblue4")
+mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.22*diff(par("usr")[1:2]), col = "steelblue4")
 
@@
 
-``` {r Partition comparison: halves plot, fig.align="center", fig.width = 6, fig.height = 4, fig.cap = "Figure 5.
-Similarity matrices showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right).
+``` {r Partition comparison: halves plot, fig.align="center", out.width = "60%", fig.cap = "Figure 5.
+Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right).
 These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
@@
          method = "color",
+         addgrid.col = "grey90",
          tl.pos = "n", 
          tl.col = "black",
-         tl.cex = 0.8,
-         cl.pos = "b",
-         cl.length = 3)
+         tl.cex = 0.1,
+         cl.pos = "n",
+         cl.lim = c(0,1),
+         cl.length = 3,
+         mar = c(1,1,1,1))
+mtext("Subjects (Day 1 and Day 2)", line = 0)
+mtext("Subjects (Day 1 and Day 2)", side = 2, line = 3)
 corrplot(RI_PCC_halves, 
@@
          tl.col = "black", 
-         tl.cex = 0.8,
-         cl.lim = c(-0.03,1),
+         tl.cex = 0.1,
+         cl.lim = c(0,1),
+         cl.pos = "r",
+         addgrid.col = "grey90",
          cl.length = 3)
+mtext("Subjects (Day 1 and Day 2)", line = 0)
 corrplot(RI_PFC_halves, 
@@
          tl.col = "black",
-         tl.cex = 0.8,
+         tl.cex = 0.1,
          cl.pos = "n", 
+         addgrid.col = "grey90",
          add = T)
@@
 
-``` {r Partition comparison: halves ratios, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 6.
+``` {r Partition comparison: halves ratios (Fig.
+6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 6.
 mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI.
@@
 
-``` {r Partition comparison: session similarity matrices plot, fig.align="center", fig.width = 6, fig.height = 4, fig.cap = "Figure 7.
-Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right).
+``` {r Partition comparison: session similarity matrices plot, fig.align="center", out.width = "60%", fig.cap = "Figure 7.
+Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects).
 The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
@@
          add = T)
-
+```
+
+``` {r Partition comparison: session compare all, echo=FALSE, message = FALSE, cache = TRUE}
 # Now run comparisons among all subjects
@@
 
-``` {r Partition comparison: session ratios, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 8.
+``` {r Partition comparison: session ratios (Fig.
+8), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 8.
 Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions.
@@
 
-``` {r Stability per subject: Overall, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 9.
+``` {r Stability per subject: Overall (Fig.
+9), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 9.
 ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE, cache = TRUE}
@@
 ``` {r Stability per subject: Fiedler vector vs prop.
-DMN plot, fig.align="center", fig.width=3.5, fig.height=3.5, fig.cap = "Figure 10.
+DMN plot, fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 10.
 Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
@@
 
-``` {r Noise Effects: tSNR Comparison, fig.align="center", fig.width=3.5, fig.height=3.5, fig.cap = "Figure 12.
+``` {r Noise Effects: tSNR Comparison (Fig.
+12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 12.
 Mean tSNR for mPFC and PCC across participants.
@@
 
-``` {r Noise Effects: Per-subject Fiedler by R-sqd, fig.align="center", fig.width=4, fig.height=4, fig.cap = "Figure 13.
+``` {r Noise Effects: Per-subject Fiedler by R-sqd (Fig.
+13), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 13.
 Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
@@
 
-``` {r Noise Effects: R-sqd vs tSNR, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 15.
+``` {r Noise Effects: R-sqd vs tSNR (Fig.
+15), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 15.
 Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the least tSNR (left).
@@
 
-``` {r Correlation vs community detection: comparison plot, fig.align="center", fig.width=4, fig.height=4, fig.cap = "Figure 17.
+``` {r Correlation vs community detection: comparison plot (Fig.
+17), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 17.
 Day 1 vs Day 2 oefficients of spatial correlations for every method, as well as between methods.
@@
 ## Acknowledgements
+
 Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.

### 2018-09-18 Manuscript.Rmd
Change in figures and added AR/sliding window accessory analyses

@@
   pdf_document: default
-  html_document: default
   word_document: 
     reference_docx: Style_reference.docx
+  html_document: default
 bibliography: mPFC_paper.bib
@@
 We permuted the label of every study (i.e.
-DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a ROI-wise chi-squared test of proportions on the number of prmuted studies that had reported each ROI.
+DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a area-wise chi-squared test of proportions on the number of permuted studies that had reported each area.
 This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.
@@
 Because of this, the adjusted rand index is a simple metric that determines the percentage of agreement between any two partitions that is agnostic to the labeling scheme.
-*(SHOULD WE INCLUDE THIS?
-The mutual information results would probably need to go in the supplemental materials) On the other hand, variation of information gives a general sense of the amount of information to be gained by the complementary community partitioning (Meila, 2007), measured by the addition of the conditional entropies per combination of clusters across partitions.
-While the rand index is more easily interpreted, it suffers from the assumption that the baseline should have an equal number of vertices per cluster across partitions, which is not necessarily the case.
-Therefore, I used variation of information as a more robust similarity metric (Fortunato & Hric, 2016).*
+Note that this metric is adjusted for chance cluster labelings, and thus heavily penalizes deviations.
 
@@
 Figure 3 shows the distribution of ARI values across subjects.
-**It is worth noting that the adjusted rand index has well known limitations (Fortunato & Hric, 2016).
-To compensate for this, we also performed all the upcoming analyses with the variation of information index (VI).
-This distance measure denotes how much information is gained by adding the second partition (thus, lower values are better), and is known for its robustness.
-Both RI and VI analyses agreed in the results they yielded, but we only report RI due to its easier interpretability.
-This first plot shows the distribution of RI values between modularity and spectral partitioning for each subject.**
 
@@
 
-``` {r Partition comparison: all 2 plot, fig.align="center", out.width = "40%", fig.cap = "Figure 4.
+``` {r Partition comparison: all 2 (Fig.
+4), fig.align="center", out.width = "40%", fig.cap = "Figure 4.
 Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
@@
          cl.pos = "r",
-         mar = c(1,0,2,0))
+         mar = c(1,1,2,0))
 corrplot(RI_PFC, 
@@
          addgrid.col = "grey90",
-         mar = c(1,0,2,0), 
+         mar = c(1,1,2,0), 
          add = T)
-mtext(expression(bold("Subject Partitions")), line = 0.8)
-mtext(expression(bold("Subject Partitions")), side = 2, line = -2.5)
-mtext(expression(bold("PFC")), line = 0, at = par("usr")[1]+0.7*diff(par("usr")[1:2]), col = "steelblue4")
-mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.22*diff(par("usr")[1:2]), col = "steelblue4")
+segments(0.5,0.5,0.5,100.5, lwd = 2)
+segments(0.5,0.5,100.5,0.5, lwd = 2)
+segments(0.5,100.5,100.5,100.5, lwd = 2)
+segments(100.5,0.5,100.5,100.5, lwd = 2)
+mtext(expression(bold("Subject Partitions")), line = 3)
+mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
+mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
+mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")
 
@@
 
-``` {r Partition comparison: halves plot, fig.align="center", out.width = "60%", fig.cap = "Figure 5.
+``` {r Partition comparison: halves (Fig.
+5), fig.align="center", out.width = "60%", fig.cap = "Figure 5.
 Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right).
@@
          cl.length = 3,
-         mar = c(1,1,1,1))
-mtext("Subjects (Day 1 and Day 2)", line = 0)
-mtext("Subjects (Day 1 and Day 2)", side = 2, line = 3)
+         mar = c(1.1,1.1,1.1,1.1))
+# segments(0.5,0.5,0.5,20.5, lwd = 2)
+# segments(0.5,0.5,20.5,0.5, lwd = 2)
+# segments(0.5,20.5,20.5,20.5, lwd = 2)
+# segments(20.5,0.5,20.5,20.5, lwd = 2)
+mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
+mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
 corrplot(RI_PCC_halves, 
@@
          tl.pos = "n", 
-         tl.col = "black", 
-         tl.cex = 0.1,
          cl.lim = c(0,1),
@@
          cl.length = 3)
-mtext("Subjects (Day 1 and Day 2)", line = 0)
 corrplot(RI_PFC_halves, 
@@
          tl.pos = "n", 
-         tl.col = "black",
-         tl.cex = 0.1,
          cl.pos = "n", 
@@
          add = T)
-
+mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
+mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
+mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
 ```
@@
 ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
-          geom_boxplot(show.legend = F) +
+  geom_violin(show.legend = F, draw_quantiles = 0.5, trim = F, lwd = 0.7) +
   scale_fill_manual(values = Cols[seq(2)]) + 
-          ylim(0, max(Halves_RIRatios_summary$RI)) +
+  ylim(0, NA) +
   geom_hline(yintercept = 1) +
   labs(y = "ARI Ratio", x = "") + 
-          theme_classic()
+  theme_classic(base_size = 14)
 ```
@@
 
-``` {r Partition comparison: session similarity matrices plot, fig.align="center", out.width = "60%", fig.cap = "Figure 7.
+``` {r Partition comparison: session similarity matrices (Fig.
+7), fig.align="center", out.width = "60%", fig.cap = "Figure 7.
 Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects).
@@
          cl.lim = c(-0.03,1),
-         cl.pos = "b",
-         cl.length = 3)
+         cl.pos = "n",
+         cl.length = 3,
+         mar = c(1.1,1.1,1.1,1.1), 
+         addgrid.col = "grey90")
+# segments(0.5,0.5,0.5,40.5, lwd = 2)
+# segments(0.5,0.5,40.5,0.5, lwd = 2)
+# segments(0.5,40.5,40.5,40.5, lwd = 2)
+# segments(40.5,0.5,40.5,40.5, lwd = 2)
+mtext(expression(bold("Subjects (Session)")), line = 1)
+mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
 corrplot(RI_PCC_sess, 
@@
          tl.col = "black", 
-         cl.lim = c(-0.03,1),
-         cl.length = 3)
+         cl.lim = c(0,1),
+         cl.length = 3,
+         cl.pos = "r", 
+         addgrid.col = "grey90")
+# segments(0.5,0.5,0.5,20.5, lwd = 2)
+# segments(0.5,0.5,20.5,0.5, lwd = 2)
+# segments(0.5,20.5,20.5,20.5, lwd = 2)
+# segments(20.5,0.5,20.5,20.5, lwd = 2)
 corrplot(RI_PFC_sess, 
@@
          cl.pos = "n", 
+         addgrid.col = "grey90",
          add = T)
+mtext(expression(bold("Subjects (Session)")), line = 1)
+mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
+mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
 ```
@@
 As before, we see higher agreement levels within subjects (with some exceptions).
+Note that the overall ARI has markedly diminished for mPFC, which is expected as the 15 minute sessions are too short to determine stable community patterns [@Gordon2017].
+Nevertheless, we can still coarsely capture a subject's unique organizational pattern.
 Simple permutation comparisons confirmed this intuition for the all-ROI (p = `r Sess_overallComparison[[3]]$Pval`; Cohen's D `r round(Sess_overallComparison[[4]], digits = 2)`), PCC (p = `r Sess_PCCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PCCComparison[[4]], digits = 2)`), and mPFC (p = `r Sess_PFCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PFCComparison[[4]], digits = 2)`) divisions.
@@
 ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
-          geom_boxplot(show.legend = F) +
+  geom_violin(show.legend = F, draw_quantiles = 0.5, trim = F, lwd = 0.7) +
   scale_fill_manual(values = Cols[seq(2)]) + 
-          ylim(0, max(Sess_RIRatios_summary$RI)) +
+  ylim(0, NA) +
   geom_hline(yintercept = 1) +
   labs(y = "ARI Ratio", x = "") + 
-          theme_classic()
+  theme_classic(base_size = 14)
 ```
@@
 
-### *Stability per subject*
+### *Stability per subject (sliding window)*
 
@@
 
+## PLAYING WITH AR AND MA PROCESSES
+# tempSC <- do.call(rbind, SC)
+# tempSC <- SC_PFC
+# tempSC$SubjID <- as.factor(tempSC$SubjID)
+# test <- numeric()
+# intercepts <- numeric()
+# coefficients <- numeric()
+# 
+# for (i in seq(100)) {
+#   temp <- arima(SC[[i]]$Index, c(1,0,0), method = "ML")
+#   test <- c(test, temp$residuals)
+#   intercepts[i] <- temp$coef[2]
+#   coefficients[i] <- temp$coef[1] 
+# }
+# 
+# tempSC$Res <- test
+# 
+# ggplot(data = tempSC, aes(Window, Res, group = SubjID, color = SubjID)) +
+#   geom_line(show.legend = F, alpha = 0.5) +
+#   theme_classic()
+# 
+# ggplot(data = tempSC, aes(Res, group = SubjID, color = SubjID)) +
+#   geom_density(alpha = 0.5, show.legend = F) +
+#   theme_classic()
+# 
+# 
+# test <- aggregate(SC_PCC$Index, by = list(SC_PFC$SubjID), arima, order = c(10,0,0), method = "ML")
+# intercepts <- numeric()
+# coefficients <- numeric()
+# for(i in seq(100)) {
+#   intercepts[i] <- test$x[[i]]['intercept']
+#   coefficients[i] <- test$x[[i]]['ar1']
+# }
+# 
+# plot(intercepts)
+
+# AND WITH MORE SIMILARITY MATRICES
+# THE POINT HERE IS THAT I TOOK THE ARI SIMILARITY MATRIX OF ALL THE SLIDING WINDOWS PER SUBJECT AND AVERAGED ACROSS SUBJECTS
+# THIS PRODUCES A MATRIX WHERE YOU CAN TELL THE AUTOCORRELATED NATURE OF THE DATA IF UNCLUSTERED, BUT OTHERWISE THERE ARE MARKED DAY CLUSTERS
+# simMatrices <- list()
+# nrun <- 1
+# for (subj in SVals) {
+#   nWins <- ncol(subj)
+#   if (nWins != 37) {
+#     print("Fewer than 37 windows...")
+#   } else {
+#     tempMat <- matrix(NA, nWins, nWins)
+#     for (i in seq(nWins)) {
+#       for(j in seq(nWins)) {
+#         tempMat[i,j] <- arandi(subj[,i], subj[,j], adjust = T)
+#       }
+#     }
+#     simMatrices[[nrun]] <- tempMat
+#     nrun <- nrun + 1
+#   }
+# }
+# 
+# meanMatrices <- Reduce("+", simMatrices) / length(simMatrices)
+# corrplot(meanMatrices, method = "color", is.corr = F, cl.lim = c(0,1))
 ```
@@
 
-### temporary fix to add z coordinates (these will be computed during the initial analysis from now on)
+### Grab some of the other measures from the overall summary
 for (i in seq(nSubj)) {
@@
   Variance[[i]]$SubjID <- rep(subjList[i], nrow(Variance[[i]]))
-  Variance[[i]]$tempX <- Summaries[[i]]$x[tempIndex]
-  Variance[[i]]$tempZ <- Summaries[[i]]$z[tempIndex]
   Variance[[i]]$FiedlerVec <- Summaries[[i]]$FiedlerVec[tempIndex]
@@
 
-``` {r Correlation vs community detection: plot, fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 16.
+``` {r Correlation vs community detection (Fig.
+16), fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 16.
 Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (7m-based) and the Fiedler vector.
@@
          method = "color", 
-         tl.col = "black",
-         tl.cex = 0.6,
-         cl.pos = "b",
-         mar = c(0,0,3,0))
+         #tl.col = "black",
+         #tl.cex = 0.6,
+         addgrid.col = "grey90",
+         tl.pos = "n",
+         cl.pos = "r",
+         cl.length = 3,
+         mar = c(1,2,2,0))
 segments(0.5,0.5,0.5,40.5, lwd = 2)
@@
 segments(20.5,0.5,20.5,40.5, lwd = 2)
+mtext(expression(bold("Subject Partitions (Day 1 and Day 2)")), line = 3, at = par("usr")[1]+0.45*diff(par("usr")[1:2]))
+mtext(expression(bold("Subject Partitions (Day 1 and Day 2)")), side = 2, line = 3)
+mtext(expression(bold("Fiedler")), line = 1.5, at = par("usr")[1]+0.68*diff(par("usr")[1:2]))
+mtext(expression(bold("Correlation")), line = 1.5, at = par("usr")[1]+0.23*diff(par("usr")[1:2]))
+mtext(expression(bold("Fiedler")), side = 2, line = 2, at = par("usr")[1]+0.25*diff(par("usr")[1:2]))
+mtext(expression(bold("Correlation")), side = 2, line = 2, at = par("usr")[1]+0.68*diff(par("usr")[1:2]))
 
@@
 
+It might also be worth mentioning that previous work has established the shift in network types during rest through hidden Markov models (Vidaurre et al., 2016?).
+While this suggests that we should see fluctuations in affiliation, and not stability, Vidaurre's work establishes the dynamics of prevalent function among networks, and not their topologies.
+Our work focuses on the topographical arrangement of the DMN network, which can be active or not while maintaining its form.
+So, the two works are compatible.
+Note, I played a bit with AR and MA processes per subject to try to understand the autocorrelation in the sliding window.
+First, both acf/pacf and arima (order = n,0,n) R functions suggested that the data was better fit by AR.
+Moreover, ARs from 1 to 10 had neglegible differences, so I stuck with 1 results for simplicity.
+As expected the data is significantly autocorrelated, and when I checked plotted the residuals they were mostly within the 0.15 bound (normally distributed).
+Coefficients ranged from 0.6 to 1.
+So, there is clear rythmicity in the agreement between each window and the overall pattern.
+However, the intercepts from the ARn processes gave more or less the same estimates as the mean rand index over all the windows.
+This is mostly expected, as we saw that the standard deviation of the rand index was low across participants.
+I am currently interpreting this as a signal that there is clear periodicity that is otherwise harmless for our results: in the end, the agreement remains stable throughout the 4800 TRs.
+
 ## Acknowledgements

### 2018-09-21 Manuscript.Rmd
Mostly advancing on results (day and session analyses)
But some changes to the script so the code from these sections matches better.

@@
 
-In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (ARI) [@Hubert1985] as the reference metric of agreement between two clusterings.
-The adjusted rand index estimates the rate at which every pair of nodes in partition A were equally assigned to the same/different parcels on partition B, over all possible changes (e.g.
+In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (ARI) as the reference metric of agreement between two clusterings [@Hubert1985].
+ARI estimates the rate at which every pair of nodes in partition A were jointly assigned to the same/different parcels on partition B, over all possible changes (e.g.
 clustered together on A, but separately on B).
-The resulting ratio is compared to a baseline given by the expectation based on a random vertex assignment for an equal number of clusters across partitions.
-Because of this, the adjusted rand index is a simple metric that determines the percentage of agreement between any two partitions that is agnostic to the labeling scheme.
-Note that this metric is adjusted for chance cluster labelings, and thus heavily penalizes deviations.
+Because of this, the adjusted rand index determines the percentage of agreement between any two partitions while being agnostic to the labeling scheme.
+The resulting ratio is compared to a baseline given by the expectation of a random node assignment across partitions.
+This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index falls below chance).
 
@@
 On average, networks had high densities (i.e.
-highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r sddAll`).
+highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`).
 This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].
@@
 Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
-This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the partition.
-Since this is a data-driven approach, there is no a priori labeling for these communities.
+This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs Since this is a data-driven approach, there is no a priori labeling for these communities.
 We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects.
 In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment.
-mPFC, on the other hand, is mostly populated by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them.
+mPFC, on the other hand, is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them.
 This non-DMN section extends posteriorly onto pregenual cinglate cortex.
@@
 ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g.
-clustered together in partition 1, but separately in 2), and has the benefit of being agnostic to labeling schemes [@Hubert1985].
-Figure 3 shows the distribution of ARI values across subjects.
+clustered together in partition 1, but separately in 2).
+This measure has the benefit of being agnostic to labeling schemes, as well as controlling for the expectation that the clusters were randomly produced [@Hubert1985].
+This means that positive ARI values compare favorably against chance clustering.
+Figure 3 shows the distribution of ARI values comparing topologies produced by modularity and spectral partitioning across subjects.
 
@@
 
-HCP resting state data is separated into 4 runs (2 per day of scanning).
-This section explores how much agreement there is between partitions computed on each day.
-The similarity matrix on the left shows the pairwise level of agreement for the overall data among the example subjects, while the right one divides this data into PCC and mPFC.
+In order to determine whether the low agreement shown in mPFC across subjects was a function of intrinsic variability or a subject-specific pattern, we compared the agreement among communities estimated with data from each separate day.
+If the latter were true, within-subject ARI values should be consistently higher than across subjects.
+Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.
+Communities were estimated on concatenated pairs of daily left-right and right-left phase encoded sessions (see Methods for details), and once again compared using ARI.
+Figure 5 shows pairwise comparisons among ten example subjects for PCC and mPFC separately.
 
@@
 
-So far both visualizations show considerable subject specificity, and the regional division agrees with the whole-data similarity matrix.
-Importantly, this indicates that both PCC and mPFC partitions were more similar within- than between-subjects (e.g.
-RI values higher for each 2x2 diagonal submatrix than the off-diagonals).
-Now, how do we check whether the within subject consistency is significantly higher than across subjects?
-One way is to divide each subject's RI-agreement between days by the RI values with the days from the other subjects.
-This gives an RI ratio per subject that denotes the relative specificity of their partition.
-That means, partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
-
 ``` {r Partition comparison: halves ratios (Fig.
@@
 PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE, cache = TRUE}
-# Now compare all possible pairs of subjects
+## Now compare all possible pairs of subjects
 # Compare all halves with RI
@@
 
-## Ratio of mean within subject sessions over between subject ones (per-subject)
-# Selection of submatrices
+## Let's compare stuff (not accounting for complex interdependencies in the observations)
+## Overall differences in mean RI between PCC and mPFC
+lowPCC_halves <- RI_PCC_halves[lower.tri(RI_PCC_halves)]
+lowPFC_halves <- RI_PFC_halves[lower.tri(RI_PFC_halves)]
+Halves_PCCvPFC_perm <- permute(lowPCC_halves, lowPFC_halves, statType = mean, paired = T)
+Halves_PCCvPFC_ES <- cohenD(lowPCC_halves, lowPFC_halves) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
+# create a selection matrix containing all within-subject session comparisons
 template <- diagBlocks(ncol(RI_all_between_halves), 2) 
@@
 
+# Overall
+# First list element is the within subject values, second is the between subject values
+lowRIHalves <- RI_all_between_halves[lower.tri(RI_all_between_halves)]
+Halves_overallComparison <- list(lowRIHalves[lowTemplate],
+                                lowRIHalves[!lowTemplate])
+Halves_overallComparison[[3]] <- permute(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
+Halves_overallComparison[[4]] <- cohenD(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
+
+# PCC 
+Halves_PCCComparison <- list(lowPCC_halves[lowTemplate],
+                           lowPCC_halves[!lowTemplate])
+Halves_PCCComparison[[3]] <- permute(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
+Halves_PCCComparison[[4]] <- cohenD(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
+
+# mPFC
+Halves_PFCComparison <- list(lowPFC_halves[lowTemplate],
+                           lowPFC_halves[!lowTemplate])
+Halves_PFCComparison[[3]] <- permute(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
+Halves_PFCComparison[[4]] <- cohenD(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
+
+## Ratio of mean within subject sessions over between subject ones (per-subject)
 # Overall
@@
 # PCC
+# Split the within-subject session RI values per subject
 withinSubjVals <- RI_PCC_halves[lower.tri(RI_PCC_halves)][lowTemplate]
@@
 # PFC
+# Split the within-subject session RI values per subject
 withinSubjVals <- RI_PFC_halves[lower.tri(RI_PFC_halves)][lowTemplate]
@@
 # Stats
-Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
+Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T)
 Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
@@
   scale_fill_manual(values = Cols[seq(2)]) + 
-  ylim(0, NA) +
+  ylim(0, 10) +
   geom_hline(yintercept = 1) +
@@
   theme_classic(base_size = 14)
-```
-
-As expected, we see that while both regions had good specificity (ratios > 1, denoted by the horizontal line), the ratios for PCC were significantly smaller than mPFC for all subjects (permutation, p = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
-However, the denominator is given by a single RI.
-If these topological patterns are indeed subject-specific for mPFC, these results might generalize to session specific data.
-This would give us a better estimate of within-subject RI variance to place in the denominator.
+
+```
+
+Once again we found greater alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) than mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed higher levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
+However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic.
+Therefore, we divided each subject's ARI between days by the ARI values with the days from the other subjects.
+This ratio denotes the relative specificity of their partition.
+That means, partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
+Figure 6 shows the ratios for PCC and mPFC for all subjects.
+As expected, we found that while both regions had good specificity (i.e.
+ratios > 1), the ratios for PCC were significantly lower than mPFC (paired permutation, p = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
+These test/retest results suggest that the topographic varability seen in mPFC is rooted in subject-specific organization, and not an inability to capture its topology.
 
@@
 
-Next, each session is evaluated independently.
-The similarity matrix on the left shows how each session's data corresponded within and between subjects for all ROIs combined, while the one on the right shows PCC and mPFC separately.
-It is worth noting that each session is ~14 mins long, which is below the stability threshold for fMRI based modularity (Gordon et al., 2017).
-However, we also perform a sliding window analysis below that encompasses 20 mins of data per window.
+We extended the analysis of daily data by examining whether the organization of the DMN could be extracted using session data only.
+It is worth noting that the length of each session (approx.
+14 mins long) falls below the stability threshold for fMRI-based modularity estimations [@Gordon2017].
+Nonetheless, high ARI ratios with reduced data could signify the ability to localize a subject's DMN organization with fMRI sessions that are easier to fit along with other study sessions of interest.
 
@@
 
-As before, we see higher agreement levels within subjects (with some exceptions).
-Note that the overall ARI has markedly diminished for mPFC, which is expected as the 15 minute sessions are too short to determine stable community patterns [@Gordon2017].
-Nevertheless, we can still coarsely capture a subject's unique organizational pattern.
-Simple permutation comparisons confirmed this intuition for the all-ROI (p = `r Sess_overallComparison[[3]]$Pval`; Cohen's D `r round(Sess_overallComparison[[4]], digits = 2)`), PCC (p = `r Sess_PCCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PCCComparison[[4]], digits = 2)`), and mPFC (p = `r Sess_PFCComparison[[3]]$Pval`; Cohen's D = `r round(Sess_PFCComparison[[4]], digits = 2)`) divisions.
-In order to quantify the consistency and specificity of these partitions, we again applied the RI ratio index, but this time using the mean RI among all of a subject's sessions in the denominator.
-The following plot shows the results for PCC and mPFC separately.
+Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 7), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 8).
 
@@
 # Stats
-Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
+Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T)
 Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
@@
 
-We can see again that the ratios for mPFC were higher than those of PCC (permutation, p = `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were above 1.
-This suggests that the PCC is well aligned across subjects (as mentioned before), while mPFC is consistent within subject, but quite different from other subjects.
-
-Another way to determine the heterogeneity of these results is based on Kragel et al.
+We can see again that the ratios for mPFC were higher than those of PCC (permutation, p = `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
+This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with relatively small amounts of data in spite of a reduction in the estimates.
+
+**Another way to determine the heterogeneity of these results is based on Kragel et al.
 (2018), who quantified the dissimilarity of brain patterns for behavioral domain, subdomain, and study (or how generalizeable the patterns are at each hierarchical level).
@@
 Thus, subject specificity would dictate that all subject-level coefficients should be significant and negative.
+**
 
@@
 
-It is also worth considering how stable these measures are, so we performed a sliding window analysis  per subject (20 min windows shifting at ~1 min throughout the whole ~ 1hr time series).
+While the distinction of DMN and non-DMN is consistent across session and days, it is possible that the decrease in global ARI values going from full to session-specific data could be due to a dynamic shift in organization.
+In order to address this possibility, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived on each window with the original pattern estimated using the whole time series.
 The first two plots show how well each window's clustering agreed with the partition derived from the whole data (in RIs, left), as well as how variable (in standard deviations) this index was throughout each time series (right).
@@
 SC_sd_plot <- ggplot(data = SC_summary, aes(x=SD)) + 
-  geom_density(color = "black", fill = Cols[2], bins=50) + 
+  geom_density(color = "black", fill = Cols[2]) + 
   xlim(0,1) +

### 2018-09-27 Manuscript.Rmd
Advances in results section (up until noise effects)

@@
 output:
-  pdf_document: default
+  html_document: default
   word_document: 
     reference_docx: Style_reference.docx
-  html_document: default
+  pdf_document: default
 bibliography: mPFC_paper.bib
@@
 prior to the complementary denoising described in the "fMRI Data" section).
-For each subject, we compared the mean tSNR between mPFC and PCC through a permutation analysis (5000 iterations), and report the percentage of subjects who had a significantly lower mean tSNR in mPFC.
+We compared the mean tSNR for each region across subjects through a permutation analysis (all permutation analyses involved 5000 iterations).
+In addition, we compared the mean tSNR between mPFC and PCC through a permutation analysis for each separate subject, and report the percentage of subjects who had a significantly lower mean tSNR in mPFC after FDR correction for multiple testing [@Benjamini2001].
 Next, we estimated which vertices within mPFC had a stronger relationship to the overall dynamics of DMN.
-To do this, we computed the mean time series of each subject's DMN map, which was then predicted by the time series each mPFC vertex in a mass univariate model.
+To do this, we computed the mean time series of each subject's estimated DMN map, which was then predicted by the time series each mPFC vertex in a mass univariate analysis.
 The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex.
 If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects.
-We then compare this dorsal-to-ventral gradient to one displaying tSNR values, as the latter should convey a linear relationship between noise and dorsal-to-ventral topographical placement.
+We then spatially correlated (Pearson) the $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices.
+*(PERONSAL NOTE: THIS IS NOW DONE BY CONCATENATING ALL SUBJECTS.
+IT WOULD PERHAPS BE BETTER TO DO A MIXED EFFECTS MODEL WITH SUBJECTS AS RANDOM EFFECTS, AND TSNR AS A FIXED ONE)*
 
@@
 DMN included `r length(t2)` significant regions, while SV was comprised of `r length(t1)` (see Supplemental Table 1).
-As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all p < 0.05).
+As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all*p*< 0.05).
 A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function.
-Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, p < 0.001).
+Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, *p* < 0.001).
 
@@
 To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 4).
-Indeed, this analysis showed that the functional topology of PCC is well maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), while mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) showed significantly lower levels of agreement (paired permutation, p = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+Indeed, this analysis showed that the functional topology of PCC is well maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), while mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) showed significantly lower levels of agreement (paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
 
@@
 As expected, we found that while both regions had good specificity (i.e.
-ratios > 1), the ratios for PCC were significantly lower than mPFC (paired permutation, p = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
-These test/retest results suggest that the topographic varability seen in mPFC is rooted in subject-specific organization, and not an inability to capture its topology.
+ratios > 1), the ratios for PCC were significantly lower than mPFC (paired permutation,*p*= `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
+These test/retest results suggest that the topographic varability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
 
@@
 
-We can see again that the ratios for mPFC were higher than those of PCC (permutation, p = `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
+We can see again that the ratios for mPFC were higher than those of PCC (permutation,*p*= `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
 This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with relatively small amounts of data in spite of a reduction in the estimates.
 
-**Another way to determine the heterogeneity of these results is based on Kragel et al.
-(2018), who quantified the dissimilarity of brain patterns for behavioral domain, subdomain, and study (or how generalizeable the patterns are at each hierarchical level).
-In our case, for `r nSubj` subjects `r nSubj*3` matrices are created (`r nSubj*2` for daily comparisons, `r nSubj` for within subject comparisons).
-Each matrix is binarized to compare a subject's level of similarity within their daily data vs across every other subject's sessions.
-The `r nSubj*3` matrices are vectorized and used as predictors in a GLM with a quasibinomial distribution, where the dependent data is the full vectorized RI similarity matrix.
-This is a simplified version of a fully-dimensional model that considers all possible comparisons at the session level, which would otherwise have S + (S x (S-1)/2) parameters (with S = session).
-For this model, a significantly negative subject predictor implies that the odds of the partitions being similar across subjects are much lower than those within each subject (across sessions).
-Thus, subject specificity would dictate that all subject-level coefficients should be significant and negative.
-**
-
-``` {r Partition comparison: session linear model, fig.align="center", fig.width = 4, fig.height = 4, echo=FALSE, message = FALSE, cache = TRUE}
-# 2) Based on Kragel et al, 2018
-# First, create a disimilarity matrix
-dissimMatrix_all <- RI_all_between_sess
-dissimMatrix_lower <- dissimMatrix_all[lower.tri(dissimMatrix_all)]
-
-# Create selection matrices for half- and subject-level comparisons
-coeffList <- list()
-i <- 1
-for (j in c(2,4)) {
-  for (x in seq(1, ncol(dissimMatrix_all), by = j)) {
-    tempMatrix <- matrix(0, ncol(dissimMatrix_all), nrow(dissimMatrix_all))
-    tempMatrix[-(x:(x+(j-1))), (x:(x+(j-1)))] <- 1
-    tempMatrix[(x:(x+(j-1))), -(x:(x+(j-1)))] <- 1
-    coeffList[[i]] <- tempMatrix
-    i <- i + 1
-  }
-}
-
-# Turn into a vector based on the lower triangle
-coeffList_lower <- lapply(coeffList, function(data) {as.factor(data[lower.tri(data)])})
-coeffList <- as.data.frame(do.call(cbind, coeffList_lower))
-colnames(coeffList) <- c(subjList_halves, subjList)
-
-# Do a linear model with each 
-#testModel <- lm(dissimMatrix_lower ~ ., coeffList)
-
-# Logistic maybe better, given the RI bounds
-# That said, the adjusted RI can sometimes be negative by a small margin (< 0.01), so we take the absolute values
-tempY <- abs(RI_all_between_sess)
-tempY <- tempY[lower.tri(tempY)]
-specificityModel <- glm(tempY ~ ., coeffList, family = "quasibinomial")
-tempSummary <- summary(specificityModel)
-
-# Diagnostics: rank (full rank = nSubj * 3) and VIF (< 10 = better)
-specificityModel_diagnostics <- list(Rank = rankMatrix(coeffList),
-                                     Vif = VIF(specificityModel),
-                                     Rsquared = 1 - tempSummary$deviance/tempSummary$null.deviance)
-
-# Create a summary dataframe 
-specificityModel_summary <- data.frame(Type = c(rep("Day", nSubj*2), rep("Subject", nSubj)),
-                                       Coefficient = coef(specificityModel)[2:(nSubj*3+1)],
-                                       Pvals = tempSummary$coefficients[2:(nSubj*3+1), 4])
-
-# adjust pvals and get a percentage of significant coefficients for day and subject
-specificityModel_summary$Pvals <- p.adjust(specificityModel_summary$Pvals, method = "BY")
-prcntDay <- sum(specificityModel_summary$Pvals[specificityModel_summary$Type == "Day"] < 0.05) / (nSubj*2)
-prcntSubj <- sum(specificityModel_summary$Pvals[specificityModel_summary$Type == "Subject"] < 0.05) / (nSubj)
-
-# plot
-specificityModel_plot <- ggplot(data = specificityModel_summary, aes(Type, Coefficient, fill = Type)) + 
-  geom_hline(yintercept = 0, alpha = 0.7) + 
-  geom_boxplot(show.legend = F) +
-  theme_classic()
-specificityModel_plot
-
-```
-
-The plot above shows the estimated coefficients from the linear model for day and subjects (R-squared for the model = `r round(specificityModel_diagnostics$Rsquared, digits = 2)`).
-As we would expect given the subject specificity of these partitions, `r round(prcntSubj, digits = 2)` percent of the subject coefficients were significant (a one sample t-test confirmed this notion).
-Conversely, `r round(prcntDay, digits = 2)` of the coefficients for daily comparisons were significant (non-significant t-test).
-These results suggest that the partitions were better explained as being subject-specific.
-That said, the current version of the model is fit with the data from all ROIs, and running it separately for PCC and mPFC might be fruitful in the future.
-
-In order to diagnose the model, we checked the independency of observations through the rank of the design matrix, which was `r specificityModel_diagnostics$Rank[1]` (full rank for `r nSubj` subjects should be `r ncol(coeffList)`) for the present analysis.
-Further diagnostics included a qqnorm check on the model residuals (result: mostly normal), and variance inflation factors (VIF, also used by Kragel et al., 2018).
-The VIF is a measure of colinearity of the regressors, and it "shows the degree to which variance in each parameter estimate is increased due to partial colinearity with linear combinations of other regressors".
-While low (<2) VIF values are preferable, shared variance is unavoidable given the hierarchical structure of the model.
-Regardless, Kragel et al.
-take it as a good sign that their VIF are finite (?), which is also the case here (mean = `r mean(specificityModel_diagnostics$Vif)`).
-That said, these are above 10, which is a standard upper threshold (potential downside).
-*We will have to reconsider this portion.*
-
-### *Stability per subject (sliding window)*
-
-While the distinction of DMN and non-DMN is consistent across session and days, it is possible that the decrease in global ARI values going from full to session-specific data could be due to a dynamic shift in organization.
-In order to address this possibility, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived on each window with the original pattern estimated using the whole time series.
-The first two plots show how well each window's clustering agreed with the partition derived from the whole data (in RIs, left), as well as how variable (in standard deviations) this index was throughout each time series (right).
+### *Pattern stability over time*
 
@@
               theme(text = element_text(size=35)) +
-              labs(y = "Adj. Rand Index") +
+              labs(y = "ARI") +
               theme_classic()
@@
 
-While some subjects show considerable variability, the overall trend is of fair stability.
-An interesting feature of spectral partitioning is that the Fiedler vector was tightly related to the proportion of times any given cortical vertex was affiliated with the DMN throughout the sliding windows.
-Meaning, the higher the absolute value in the Fiedler vector for a given vertex, the more persistent its relationship was with its corresponding community in time.
-The following plot shows this relationship for each subject (gray smoothed lines), as well as the fitted values from a logistic mixed effects model (black line; model: prop.
-DMN ~ Fiedler vector, subjects as random intercepts; beta = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, p < 0.001).
+While the distinction of DMN and non-DMN is consistent across session and days, it is possible that the decrease in global ARI values going from full to session-specific data could be due to a dynamic shift in DMN organization.
+In order to address this possibility, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the original pattern estimated using the whole time series (Figure 9).
+Note that the length of the windows is well equipped to find stable community features in brain networks [@Gordon2017].
+This analysis revealed persistently high levels of agreement for most subjects, with overall low variability (overall mean of each subject's average ARI = `r round(mean(SC_summary$RI), digits = 2)`; SD = `r round(mean(SC_summary$SD), digits = 2)`).
+
+``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+## Check stability for PCC and mPFC separately
+# Get the sliding values for PCC and PFC separately
+tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
+tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)
+
+SC_PCC <- data.frame()
+SC_PFC <- data.frame()
+
+for (subj in seq(nSubj)) {
+  tempPCC <- numeric()
+  tempPFC <- numeric()
+  nWins <- ncol(tempSW_PCC[[subj]])
+  for (Win in seq(nWins)) {
+    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][,Win], adjust = T)
+    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][,Win], adjust = T)
+  }
+  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
+                      Window = seq(nWins),
+                      Index = tempPCC)
+  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
+                      Window = seq(nWins),
+                      Index = tempPFC)
+  SC_PCC <- rbind(SC_PCC, dfPCC)
+  SC_PFC <- rbind(SC_PFC, dfPFC)
+}
+
+SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
+SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
+SC_PCC_summary$Region <- rep("PCC", nSubj)
+SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
+SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
+SC_PFC_summary$Region <- rep("mPFC", nSubj)
+SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
+colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
+rm(SC_PCC_summary, SC_PFC_summary)
+
+# Compare mean ARI of sliding windows between regions
+SW_PCCvPFC_permuteTest <- permute(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"], paired = T)
+SW_PCCvPFC_ES <- cohenD(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"])
+
+```
+
+We additionally performed this analysis on mPFC and PCC separately to determine whether these results were region-specific (Figure 10).
+Even though the within-subject variance remained low for both regions, we found that the average agreement per subject was significantly higher for PCC (paired permutation,*p*= `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+Nonetheless, the mean ARI across each subject's time series was still relatively high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), thus suggesting that the each individual's DMN distribution is cosiderably stable in time.
+
+``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=10, fig.height=4, fig.cap = "Figure 10.
+ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle).
+Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE, cache = TRUE}
+
+# plots
+SC_PCCPFC_plot <- ggplot(data = SC_PCC)
+SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
+  geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
+  ylim(0,1) + 
+  labs(y = "ARI") +
+  theme(text = element_text(size=35)) +
+  geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
+  geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
+  theme_classic()
+
+SC_PCCPFC_mean_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=as.factor(Region), y=Index, fill = as.factor(Region))) + 
+  geom_boxplot(show.legend = F) + 
+  scale_fill_manual(values = Cols[seq(2)]) +
+  ylim(0,1) +
+  labs(x = "", y = "") +
+  theme(text = element_text(size=35), axis.text.y = element_text(size=40)) +
+  theme_classic()
+
+SC_PCCPFC_sd_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=SD, fill = as.factor(Region))) + 
+  scale_fill_manual(values = Cols[seq(2)]) +
+  geom_density(color = "black", alpha = 0.7, show.legend = F) + 
+  xlim(0,1) +
+  labs(x = "SD") +
+  theme(text = element_text(size=35)) +
+  theme_classic()
+
+grid.arrange(SC_PCCPFC_plot, SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 3)
+```
+
+We complemented these analyses by asking whether the magnitude of values in the Fiedler vector was associated with the stability of nodes throughout a subject's time series (*PERSONAL NOTE: It might be better to justify this from the use of this vector in statistical mechanics rather than mere curiosity, i.e.
+extreme FV values are given to elements at the peaks of the wave.
+Find a simple citation for this.*).
+Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model, with subject acting as a random effect (Figure 11).
+The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`,*p*< 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time.
+These analysis show that the original pattern identified with the full dataset is temporally stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN vertices in relatively short fMRI sessions (i.e.
+less than 20 mins).
 
 ``` {r Stability per subject: Fiedler vector vs prop.
-DMN plot, fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 10.
+DMN plot (Fig 11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 11.
 Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
@@
 
-With the exception of some noisy subjects, the sigmoidal functions show a tight relationship between the two.
-This brings attention to the possibility of using the Fiedler vector as a surrogate for stability, thus reducing the computational needs for future analyses.
-
-While these results show promise, so far we have only looked at stability for all the ROIs.
-The next three plots show similar data, but for PCC and mPFC separately.
-The middle plot compares the subject-wise mean RI for PCC and mPFC.
-While mPFC shows an overall significantly lower level of agreement with the overall partition, the variance throughout the time series is small.
-
-``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, fig.cap = "Figure 11.
-ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle).
-Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE, cache = TRUE}
-## Check stability for PCC and mPFC separately
-# Get the sliding values for PCC and PFC separately
-tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
-tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)
-
-SC_PCC <- data.frame()
-SC_PFC <- data.frame()
-
-for (subj in seq(nSubj)) {
-  tempPCC <- numeric()
-  tempPFC <- numeric()
-  nWins <- ncol(tempSW_PCC[[subj]])
-  for (Win in seq(nWins)) {
-    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][,Win], adjust = T)
-    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][,Win], adjust = T)
-  }
-  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
-                      Window = seq(nWins),
-                      Index = tempPCC)
-  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
-                      Window = seq(nWins),
-                      Index = tempPFC)
-  SC_PCC <- rbind(SC_PCC, dfPCC)
-  SC_PFC <- rbind(SC_PFC, dfPFC)
-}
-
-SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
-SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
-SC_PCC_summary$Region <- rep("PCC", nSubj)
-SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
-SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
-SC_PFC_summary$Region <- rep("mPFC", nSubj)
-SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
-colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
-rm(SC_PCC_summary, SC_PFC_summary)
-
-# plots
-SC_PCCPFC_plot <- ggplot(data = SC_PCC)
-SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
-  geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
-  ylim(0,1) + 
-  labs(y = "Adj. Rand Index") +
-  theme(text = element_text(size=35)) +
-  geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
-  geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
-  theme_classic()
-
-SC_PCCPFC_mean_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=as.factor(Region), y=Index, fill = as.factor(Region))) + 
-  geom_boxplot(show.legend = F) + 
-  scale_fill_manual(values = Cols[seq(2)]) +
-  ylim(0,1) +
-  labs(x = "", y = "") +
-  theme(text = element_text(size=35), axis.text.y = element_text(size=40)) +
-  theme_classic()
-
-SC_PCCPFC_sd_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=SD, fill = as.factor(Region))) + 
-  scale_fill_manual(values = Cols[seq(2)]) +
-  geom_density(color = "black", alpha = 0.7, show.legend = F) + 
-  xlim(0,1) +
-  labs(x = "SD") +
-  theme(text = element_text(size=35)) +
-  theme_classic()
-
-SW_PCCvPFC_permuteTest <- permute(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"], paired = T)
-SW_PCCvPFC_ES <- cohenD(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"])
-
-grid.arrange(SC_PCCPFC_plot, SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 3)
-```
-
-This suggests that, while the agreement of each window with the overall time series was stable for both PCC and mPFC (low SD, right plot), the overall agreement of mPFC is lower (paired permutation, p = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
-
 \bigskip
@@
 ### *Potential Noise Effects*
-
-This result could be due to signal degeneration in mPFC (that said, it is worth noting that the topological patterns remain mostly the same for both PCC and mPFC throughout the SW analysis).
-To account for this, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
-mean of each vertex's time points over their standard deviation).
-The next plot shows the pooled subject-wise mean tSNR for PCC and mPFC vertices, and indicates that the tSNR is lower for mPFC than PCC, which could negatively affect our results.
 
@@
 
-# Get the mean SNR for each region and the effect size for the comparison 
+# Get the mean SNR for each region and compare overall levels 
 SNR_meanPCC <- sapply(tempComm_PCC, function(data) mean(data$varCoeff))
 SNR_meanPFC <- sapply(tempComm_PFC, function(data) mean(data$varCoeff))
-SNR_meanComp <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
-                           SNR = c(SNR_meanPCC, SNR_meanPFC))
+SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
+                     Comparison = permute(SNR_meanPCC, SNR_meanPFC)$Pval,
+                     ES = cohenD(SNR_meanPCC, SNR_meanPFC))
+rm(SNR_meanPCC, SNR_meanPFC)
 
 # Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
-snrmeanComp_plot <- ggplot(data = SNR_meanComp, aes(Region, SNR, fill = Region)) +
+snrmeanComp_plot <- ggplot(data = SNR_meanComp$Values, aes(Region, SNR, fill = Region)) +
   geom_boxplot(show.legend = F) +
@@
 
-To formally examine this, for each subject we compared the tSNR values of all vertices between PCC and mPFC (`r nSubj` permutation tests, 5000 iterations).
+Even though our findings point to a stable representation of each subject's unique DMN organization, it is still possible that our results were affected by considerable levels of signal noise often found in mPFC (its ventral segment in particular).
+As a first step to account for this, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
+mean of each vertex's time points over their standard deviation).
+The tSNR of all vertices were averaged per region and subject (Figure 12), which showed that indeed mPFC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`) was overall noisier than PCC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`) across subjects (permutation, *p* = `r SNR_meanComp$Comparison`, Cohen's D = `r round(SNR_meanComp$ES, digits = 2)`).
+To more precisely examine this difference, we performed subject-wise comparisons of the tSNR values of all vertices between PCC and mPFC (total `r nSubj` permutation tests, 5000 iterations each).
 About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected; mean Cohen's D = `r round(mean(SNR_PCCvsPFC_ES), digits = 2)`).
-In addition, we found that the degree of signal to noise for each vertex showed significant negative correlations with flexibility, a graph-theoretic index that measures the proportion of times a node in a network changed affiliation across partitions (mean correlation across subjects = `r round(mean(SNR_vs_Flex), digits = 2)`).
-This suggests that, for any given subject, vertices with low SNR resulted in variable participation between the communities, and could explain why mPFC had lower stability levels.
-
-To further quantify the potential effect of noise in our results, we computed the variance explained by the mean time series of the DMN community on each DMN vertex separately through a simple linear model.
-Interestingly, there is a strong linear relationship between the Fiedler vector (the divisive vector from spectral partitioning) and the R-squared values (these match perfectly on the brain when inspected qualitatively).
-The following plot shows this relationship, with each line denoting a subject.
-
-\bigskip
+In addition, we found that the levels of tSNR for each vertex showed significant negative correlations with flexibility, a graph-theoretic index that measures the proportion of times a node in a network changed affiliation across partitions (mean *r* = `r round(mean(SNR_vs_Flex), digits = 2)`).
+These findings indicate that, for any given subject, vertices with low SNR resulted in more variable participation between the communities, and these vertices were more common in mPFC.
+This could explain why mPFC previously showed lower stability levels.
 
@@
 
-v1
-
-```
-
-Next, we compared the R-squared values for PCC and mPFC separately per subject.
-The following plot shows that for each subject, R-squared values tend to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had p values < 0.001).
-This is also true for Fiedler vector values, but to a lesser extent.
+#v1
+
+```
+
+To further interrogate the potential effect of noise in our results, we computed the variance explained by activity from each DMN vertex on the mean time series of the DMN community.
+If the signal quality issues persisted after preprocessing the data, we expected that noisy vertices would have the least explicative power on the activity of the DMN community as a whole.
+This also implied lower $R^2$ values for mPFC.
+Indeed, we found that for each subject, $R^2$ values tended to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had *p* values < 0.001) (Figure 14).
 These differences had moderately high effect sizes (mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`).
-These results suggest that overall, vertices belonging to the mPFC DMN community are less in synchrony with the activity of the community as a whole than those in PCC.
+These results suggest that, overall, vertices in mPFC tended to be less in synchrony with the activity of the DMN community as a whole.
 
@@
 
-This begs the question of whether there is a "gradient of noise" along the z-axis on mPFC (vmPFC explaining less variance?).
-The plots below show the density of R-squared (left) and SNR (right) values for every mPFC vertices across all participants.
-The R-squared values have no clear relationship with the ventral-dorsal axis (with some low values grouped in vmPFC).
+Given this trend, we asked whether there is a "gradient of noise" along the z-axis of mPFC, such that more ventral vertices would both be noisier and explain the least amount of DMN variance.
+Here we found that while the highest $R^2$ values are indeed placed dorsally, there is no clear relationship with the ventral-dorsal axis.
 However, the coefficient of variation derived from minimally preprocessed data does show a trend (namely, the more ventral, the lower the SNR).

### 2018-09-27 Manuscript.Rmd
noise effects draft ready

@@
 
-### *Potential Noise Effects*
+### *Potential Noise Effects (this part is challenging)*
 
@@
 
-# plot
 # let's put everyone's data together first
@@
 
+# Create a new data frame with values restricted to mPFC (for plotting and further stats)
+mPFCVariance <- allVariance[allVariance$Region == "mPFC", ]
+
+# Get the correlations between Z-axis, R2, and tSNR for every subject (to take mean and SD in text)
+# I just came up with this, so the code should be made more parsimonious in the future (like, why bind and then split...?)
+tempSubj <- split(mPFCVariance, f = mPFCVariance$SubjID)
+noiseCors <- data.frame(R2vtSNR = sapply(tempSubj, function(data) {cor(data$Rsquared, data$varCoeff)}),
+                        ZvtSNR = sapply(tempSubj, function(data) {cor(data$tempZ, data$varCoeff)}),
+                        ZvR2 = sapply(tempSubj, function(data) {cor(data$tempZ, data$Rsquared)}))
+rm(tempSubj)
+
+# plot
 # There is a strong linear relationship between the Fiedler vector and the R-squared values
@@
 
+``` {r Noise Effects: Mean R-sqd mPFC and PCC, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 14.
+Differences in mean R-squared values for each region per participant.
+The figure shows that PCC vertices tend to be more coupled with the overall dynamics of DMN across subjects.", echo=FALSE, message = FALSE}
+v4
+```
+
 To further interrogate the potential effect of noise in our results, we computed the variance explained by activity from each DMN vertex on the mean time series of the DMN community.
@@
 These results suggest that, overall, vertices in mPFC tended to be less in synchrony with the activity of the DMN community as a whole.
-
-``` {r Noise Effects: Mean R-sqd mPFC and PCC, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 14.
-Differences in mean R-squared values for each region per participant.
-The figure shows that PCC vertices tend to be more coupled with the overall dynamics of DMN across subjects.", echo=FALSE, message = FALSE}
-v4
-```
+Furthermore, the degree tSNR showed a moderate correlation with $R^2$ values across participants (mean *r* = `r round(mean(noiseCors$R2vtSNR), digits = 2)`; SD = `r round(sd(noiseCors$R2vtSNR), digits = 2)`), meaning that noisier vertices were less in synchrony with the general activity of the DMN.
 
 Given this trend, we asked whether there is a "gradient of noise" along the z-axis of mPFC, such that more ventral vertices would both be noisier and explain the least amount of DMN variance.
-Here we found that while the highest $R^2$ values are indeed placed dorsally, there is no clear relationship with the ventral-dorsal axis.
-However, the coefficient of variation derived from minimally preprocessed data does show a trend (namely, the more ventral, the lower the SNR).
-This is notable because the R-squared values are estimated from data with added noise reduction steps.
+Here we found that while $R^2$ are somewhat correlated with dorsal-ventral placement across subjects (mean *r* = `r round(mean(noiseCors$ZvR2), digits = 2)`; SD = `r round(sd(noiseCors$ZvR2), digits = 2)`), there is no clear relationship with the z-axis across subjects (Figure 15).
+Specifically, low $R^2$ are distributed evenly along this axis, denoting a degree of orthogonality between these features.
+Conversely, tSNR showed a strong linear relationship with the position of the vertex along this axis (mean *r* = `r round(mean(noiseCors$ZvtSNR), digits = 2)`; SD = `r round(sd(noiseCors$ZvtSNR), digits = 2)`).
 These results contextualize the degree of synchrony of mPFC vertices in terms of potential noise.
-While still an important factor, it is unlikely that our stability results could be due mostly to highly structured mPFC noise.
-
-\bigskip
+While still an important factor, it is unlikely that the degree of within-subject pattern stability observed here could be due mostly to highly structured mPFC noise.
 
@@
 15), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 15.
-Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the least tSNR (left).
+Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the lowest tSNR (left).
 However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE, cache = TRUE}
@@
 
-tempVariance <- allVariance[allVariance$Region == "mPFC", ]
-s1 <- ggplot(data = allVariance, aes(Rsquared, tempZ)) +
+# ALTERNATIVE IDEA FOR A FIGURE: BRAIN MAPS WITH THESE VALUES. THAT SAID, R2 MAPS LOOK THE SAME AS FV ONES, SO...
+s1 <- ggplot(data = mPFCVariance, aes(Rsquared, tempZ)) +
   geom_bin2d(bins = 250) +
@@
 
-s2 <- ggplot(data = allVariance, aes(varCoeff, tempZ)) +
+s2 <- ggplot(data = mPFCVariance, aes(varCoeff, tempZ)) +
   geom_bin2d(bins = 250) +
@@
 Then why does this area overlap with SV?
-I think the Mueller paper mentions that PCC is an important hub of the brain, and perhaps subserves many cognitive functions.
+I think the Mueller paper mentions that PCC is an important hub of the brain, and perhaps subserves many cognitive functions (recent Wash U paper on this too).
 
@@
 
+In terms of noise, there are a handful of things to keep in mind.
+First is that yes, mPFC is noisier overall, but that did not preclude the relatively high levels of agreement across days and sessions per subject, even though ARI heavily penalizes discrepancies (less than linearly).
+Second, low $R^2$ values were found all throughout the z-axis, meaning that variance explained is not strictly determined by the cardinal position of the vertex (and while the correlation was significant due to the sheer number of items, the coefficient was relatively low).
+Right now this might be ok as a way to bypass noise comments, but it would also be interesting to take advantage of the Fiedler vector here.
+Since it's linearly related to $R^2$ per subject, perhaps finding a way to threshold these values would provide cleaner and even more consistent maps.
+
 ## Acknowledgements

### 2018-09-28 Manuscript.Rmd
Done with corr vs comm results draft

@@
 ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
-  geom_violin(show.legend = F, draw_quantiles = 0.5, trim = F, lwd = 0.7) +
+  geom_boxplot(show.legend = F) +
   scale_fill_manual(values = Cols[seq(2)]) + 
@@
 ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
-  geom_violin(show.legend = F, draw_quantiles = 0.5, trim = F, lwd = 0.7) +
+  geom_boxplot(show.legend = F) +
   scale_fill_manual(values = Cols[seq(2)]) + 
@@
 
-Even though our findings point to a stable representation of each subject's unique DMN organization, it is still possible that our results were affected by considerable levels of signal noise often found in mPFC (its ventral segment in particular).
+Even though our findings point to a stable representation of each subject's unique DMN organization, it is still possible that they were affected by considerable levels of signal noise often found in mPFC (its ventral segment in particular).
 As a first step to account for this, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
@@
 tempSubj <- split(mPFCVariance, f = mPFCVariance$SubjID)
+# Get the correlation coefficients
 noiseCors <- data.frame(R2vtSNR = sapply(tempSubj, function(data) {cor(data$Rsquared, data$varCoeff)}),
@@
 This also implied lower $R^2$ values for mPFC.
-Indeed, we found that for each subject, $R^2$ values tended to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had *p* values < 0.001) (Figure 14).
-These differences had moderately high effect sizes (mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`).
+Indeed, we found that for each subject, $R^2$ values tended to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had *p* values < 0.001; mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`) (Figure 14).
 These results suggest that, overall, vertices in mPFC tended to be less in synchrony with the activity of the DMN community as a whole.
@@
 Here we found that while $R^2$ are somewhat correlated with dorsal-ventral placement across subjects (mean *r* = `r round(mean(noiseCors$ZvR2), digits = 2)`; SD = `r round(sd(noiseCors$ZvR2), digits = 2)`), there is no clear relationship with the z-axis across subjects (Figure 15).
-Specifically, low $R^2$ are distributed evenly along this axis, denoting a degree of orthogonality between these features.
+Specifically, low $R^2$ are evenly distributed along this axis, denoting a degree of orthogonality between these features.
 Conversely, tSNR showed a strong linear relationship with the position of the vertex along this axis (mean *r* = `r round(mean(noiseCors$ZvtSNR), digits = 2)`; SD = `r round(sd(noiseCors$ZvtSNR), digits = 2)`).
@@
 # ALTERNATIVE IDEA FOR A FIGURE: BRAIN MAPS WITH THESE VALUES. THAT SAID, R2 MAPS LOOK THE SAME AS FV ONES, SO...
-s1 <- ggplot(data = mPFCVariance, aes(Rsquared, tempZ)) +
-  geom_bin2d(bins = 250) +
-  scale_fill_continuous(low = "grey30", high = "grey70") +
-  geom_density2d(color = Cols[2]) +
-  labs(x = "R-squared value", y = "Z-Coordinate") +
-  theme_classic()
-
-s2 <- ggplot(data = mPFCVariance, aes(varCoeff, tempZ)) +
-  geom_bin2d(bins = 250) +
+s1 <- ggplot(data = mPFCVariance, aes(varCoeff, tempZ)) +
+  geom_bin2d(bins = 250, show.legend = F) +
   scale_fill_continuous(low = "grey30", high = "grey70") +
@@
 
-grid.arrange(s2, s1, ncol = 2)
+s2 <- ggplot(data = mPFCVariance, aes(Rsquared, tempZ)) +
+  geom_bin2d(bins = 250, show.legend = F) +
+  scale_fill_continuous(low = "grey30", high = "grey70") +
+  geom_density2d(color = Cols[2]) +
+  labs(x = "R-squared value", y = "Z-Coordinate") +
+  xlim(c(0,1)) +
+  theme_classic()
+
+grid.arrange(s1, s2, ncol = 2)
 ```
@@
 ### *Correlation vs community detection in mPFC*
-
-Next, it is worth examining what we gain from using graph theoretic approaches over a simple seed-based functional connectivity analysis from PCC.
-For this purpose, we computed the mean time series of all the vertices contained in the DMN PCC ROI from Yeo et al.
-(2011) parcellation, and correlated it with the activity of every mPFC vertex from our ROIs.
-The similarity matrix below shows Day 1 vs Day 2 comparisons for mPFC partitions generated with seed-based correlations (top-left quadrant) vs community detection (bottom-right) across all participants, as well as how much did these methods agree with each other (not much, but enough, which is good).
-The important features here are that both approaches are very consistent, but community detection seems slightly more stable across days (quantified in the next section).
-Also, the cross-method agreement is fair, meaning that both approaches are showing similar topological features, but that these are more stable using graph theoretic approaches.
 
@@
 
+``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+# Compare correlation with community approach on mPFC
+# tempComm_PFC_halves <- lapply(seq_along(tempComm_PFC_halves), function(x) cbind(tempComm_PFC_halves[[x]], Correlation_halves[[x]]))
+# tempComm <- sapply(seq(1, 20, by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
+# tempCor <- sapply(seq(1, 20, by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
+# prepostComp <- data.frame(Community = tempComm, Correlation = tempCor)
+# prepostComp <- melt(prepostComp)
+# colnames(prepostComp) <- c("Approach", "Correlation")
+# prepostComp_test <- permute(tempComm, tempCor, paired = T)
+# 
+# 
+# ## Between halves analysis for correlation and communities (mPFC only)
+# D1 <- tempComm_PFC_halves
+# D2 <- lapply(tempComm_PFC_halves, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
+# Data <- c(D1,D2)
+# allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = length(Data), Index = "Cor", subjNames = c(subjList_halves, subjList_halves))
+#
+
+# Compare correlation with community approach on mPFC
+tempComm <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
+tempCor <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
+tempBoth <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
+prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
+prepostComp <- melt(prepostComp)
+colnames(prepostComp) <- c("Approach", "Correlation")
+prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
+prepostComp_ES <- cohenD(tempComm, tempCor)
+```
+
+The computational demands of our approach escalate quickly as the number of vertices increases.
+We thus explored the possible advantage to using graph-theoretic approaches on all possible network connections over a simple seed-based functional connectivity analysis from PCC.
+Given that the spatial distribution of the DMN is considerably stable within individuals [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018], we examined whether maps generated with spectral partitioning were more similar per subject across days than those computed from seed-based correlations.
+First, we computed the mean time series of all the vertices contained in the DMN PCC ROI from Yeo et al.
+(2011) parcellation, and correlated it with the activity of every mPFC vertex from our ROIs.
+We then performed pairwise spatial Pearson correlations among maps computed for each day and method from all subjects (Figure 16).
+
+Figure 17 shows the overall degree of similarity across days for patterns dervied using community detection, seed-based correlation, and across methods (i.e.
+day one community detection versus day two seed-based correlation).
+While both approaches are very consistent, community detection displayed a significantly higher ARI across days than a simple correlation (paired permutation *p* < 0.001; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
+It is worth noting that the cross-method agreement is fair, meaning that both approaches show similar topological features.
+These findings suggest that graph-theoretic community detection algorithms provide a better way to detect stable functional topologies, an important factor when faced with the levels of noise present in mPFC.
+
 ``` {r Correlation vs community detection (Fig.
 16), fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 16.
-Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (7m-based) and the Fiedler vector.
+Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector (10 example subjects).
 The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.", echo=FALSE, message = FALSE, cache = TRUE}
@@
 
-``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
-# Compare correlation with community approach on mPFC
-# tempComm_PFC_halves <- lapply(seq_along(tempComm_PFC_halves), function(x) cbind(tempComm_PFC_halves[[x]], Correlation_halves[[x]]))
-# tempComm <- sapply(seq(1, 20, by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
-# tempCor <- sapply(seq(1, 20, by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
-# prepostComp <- data.frame(Community = tempComm, Correlation = tempCor)
-# prepostComp <- melt(prepostComp)
-# colnames(prepostComp) <- c("Approach", "Correlation")
-# prepostComp_test <- permute(tempComm, tempCor, paired = T)
-# 
-# 
-# ## Between halves analysis for correlation and communities (mPFC only)
-# D1 <- tempComm_PFC_halves
-# D2 <- lapply(tempComm_PFC_halves, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
-# Data <- c(D1,D2)
-# allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = length(Data), Index = "Cor", subjNames = c(subjList_halves, subjList_halves))
-#
-
-# Compare correlation with community approach on mPFC
-tempComm <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
-tempCor <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
-tempBoth <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
-prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Both = tempBoth)
-prepostComp <- melt(prepostComp)
-colnames(prepostComp) <- c("Approach", "Correlation")
-prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
-prepostComp_ES <- cohenD(tempComm, tempCor)
-```
-
-The previous plot shows the inter-methodological correspondence with an example subjects.
-The final plot shows the spatial correlation between days for each method across all participants.
-Community reflects the data from the lower right quadrant, correlation belongs to the upper left, and both is the cross-approach correspondence (top right).
-Community detection had a high and significantly higher RI across days than a simple correlation (permutation p-value < 0.001; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
-This is important because it shows that we can derive very stable topological features using community detection, even though mPFC has relatively low signal to noise ratio.
-Low intra-subject and high inter-subject variability of DMN partitions is in agreement with previous work [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018).
-Graph-based community detection might thus be a better way to detect stable functional topologies, since high stability throughout days is a consistent feature of DMN topologies.
-
 ``` {r Correlation vs community detection: comparison plot (Fig.

### 2018-09-28 Manuscript.Rmd
Draft up to discussion ready, plus position of figures at the end

@@
 output:
+  pdf_document: default
   html_document: default
@@
     reference_docx: Style_reference.docx
-  pdf_document: default
 bibliography: mPFC_paper.bib
@@
 Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject.
-However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013] compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
+However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013a] compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
 
   Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
-Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018].
+Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018a].
 Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
@@
 the number of times each vertex changed affiliation across time).
-Given that the functional heterogeneity of brain areas is unevenly distributed across the brain [@Mueller2013], we also performed these comparisons for PCC and mPFC separately.
+Given that the functional heterogeneity of brain areas is unevenly distributed across the brain [@Mueller2013a], we also performed these comparisons for PCC and mPFC separately.
 Given what we know about these general regions, we expected PCC to be well aligned across participants, and stable within subjects.
@@
 These spatial correlations are aimed to determine the day-to-day stability of each approach, as well as their level of agreement.
-These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [@Kong2018; @Mueller2013]).
+These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [@Kong2018; @Mueller2013a]).
 We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
@@
 
-```{r Meta-analysis ROIs, out.width = "60%", fig.align = "center", fig.cap= "Figure 1.
-Template atlas from Glasser et al.
-(2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
-Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
-
-include_graphics("./Images/ROIS2.png")
-
-```
-
 ### *Partition Comparison: Full Datasets*
@@
 Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than SV [@Hiser2018].
-
-```{r Template partition (Fig.
-2), out.width="60%", fig.align = "center", fig.cap = "Figure 2.
-Brain partition for an example subject (100307).
-Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
-The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
-
-#include_graphics(c("./Images/newPattern.png", "./Images/newPattern_binary.png"))
-include_graphics("./Images/newPattern_both.png")
-```
 
@@
 
+``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
+# Cross-method
+# Don't worry about plotting, since that's mainly for a general visualization
+RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary","Membership"), nSubjects = length(Summaries), subjNames = subjList)
+
+# Across subjects
+# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
+RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+RI_all_between_lowtri <- RI_all_between[lower.tri(RI_all_between)]
+
+posteriorIndx <- Summaries[[1]]$y < 0
+tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
+tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
+RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+
+# Let's compare stuff
+testPCC <- RI_PCC[lower.tri(RI_PCC)]
+testPFC <- RI_PFC[lower.tri(RI_PFC)]
+Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
+Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+```
+
+The distribution suggests that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
+The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not.
+This adds evidence to the division of these areas into DMN and non-DMN during rest.
+
+Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was considerable agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+However, qualitative inspection of the brain community topologies shows good alignment for PCC, with a topologically similar mPFC pattern that shifts topographically across subjects.
+To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 4).
+Indeed, this analysis showed that the functional topology of PCC is well maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), while mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) showed significantly lower levels of agreement (paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+
+### *Partition Comparison: Day 1 vs Day 2*
+
+In order to determine whether the low agreement shown in mPFC across subjects was a function of intrinsic variability or a subject-specific pattern, we compared the agreement among communities estimated with data from each separate day.
+If the latter were true, within-subject ARI values should be consistently higher than across subjects.
+Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.
+Communities were estimated on concatenated pairs of daily left-right and right-left phase encoded sessions (see Methods for details), and once again compared using ARI.
+Figure 5 shows pairwise comparisons among ten example subjects for PCC and mPFC separately.
+
+``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
+# Select 10 subjects from the sample to display
+selectSubj <- seq(1,20)
+
+# Load
+setwd('./Summary_halves/')
+temp <- list.files(pattern = "*_finalSummary.csv")
+subjList_halves <- sapply(temp, substring, first=1, last=9)
+Summaries_halves <- lapply(temp, read.csv)
+Summaries_halves_plot <- Summaries_halves[selectSubj]
+subjList_halves_plot <- subjList_halves[selectSubj]
+
+temp <- list.files(pattern = "*_corHalves.csv")
+Correlation_halves <- lapply(temp, read.csv, header = F)
+Correlation_halves_plot <- Correlation_halves[selectSubj]
+
+# Compare all halves with RI
+RI_all_between_halves <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+
+# Compare PCC and PFC among all subjects
+tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
+tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
+RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+```
+
+``` {r Partition comparison: halves ratios, echo=FALSE, message = FALSE, cache = TRUE}
+## Now compare all possible pairs of subjects
+# Compare all halves with RI
+RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+
+# Compare PCC and PFC among all subjects
+tempComm_PCC_halves <- lapply(Summaries_halves, "[", i = posteriorIndx, j =)
+tempComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
+RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+
+## Let's compare stuff (not accounting for complex interdependencies in the observations)
+## Overall differences in mean RI between PCC and mPFC
+lowPCC_halves <- RI_PCC_halves[lower.tri(RI_PCC_halves)]
+lowPFC_halves <- RI_PFC_halves[lower.tri(RI_PFC_halves)]
+Halves_PCCvPFC_perm <- permute(lowPCC_halves, lowPFC_halves, statType = mean, paired = T)
+Halves_PCCvPFC_ES <- cohenD(lowPCC_halves, lowPFC_halves) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
+# create a selection matrix containing all within-subject session comparisons
+template <- diagBlocks(ncol(RI_all_between_halves), 2) 
+lowTemplate <- template[lower.tri(template)]
+
+# Overall
+# First list element is the within subject values, second is the between subject values
+lowRIHalves <- RI_all_between_halves[lower.tri(RI_all_between_halves)]
+Halves_overallComparison <- list(lowRIHalves[lowTemplate],
+                                lowRIHalves[!lowTemplate])
+Halves_overallComparison[[3]] <- permute(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
+Halves_overallComparison[[4]] <- cohenD(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
+
+# PCC 
+Halves_PCCComparison <- list(lowPCC_halves[lowTemplate],
+                           lowPCC_halves[!lowTemplate])
+Halves_PCCComparison[[3]] <- permute(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
+Halves_PCCComparison[[4]] <- cohenD(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
+
+# mPFC
+Halves_PFCComparison <- list(lowPFC_halves[lowTemplate],
+                           lowPFC_halves[!lowTemplate])
+Halves_PFCComparison[[3]] <- permute(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
+Halves_PFCComparison[[4]] <- cohenD(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
+
+## Ratio of mean within subject sessions over between subject ones (per-subject)
+# Overall
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_all_between_halves[lower.tri(RI_all_between_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_halves), by = 2), function(x) RI_all_between_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_overall <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# PCC
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_PCC_halves[lower.tri(RI_PCC_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_halves), by = 2), function(x) RI_PCC_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_PCC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# PFC
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_PFC_halves[lower.tri(RI_PFC_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_halves), by = 2), function(x) RI_PFC_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_PFC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# Summarize for plotting
+Halves_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
+                                      RI = c(Halves_RIRatios_PCC, Halves_RIRatios_PFC))
+
+# Stats
+Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T)
+Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
+
+```
+
+Once again we found greater alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) than mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed higher levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
+However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic.
+Therefore, we divided each subject's ARI between days by the ARI values with the days from the other subjects.
+This ratio denotes the relative specificity of their partition.
+That means, partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
+Figure 6 shows the ratios for PCC and mPFC for all subjects.
+As expected, we found that while both regions had good specificity (i.e.
+ratios > 1), the ratios for PCC were significantly lower than mPFC (paired permutation,*p*= `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
+These test/retest results suggest that the topographic varability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
+
+### *Partition Comparison: Session*
+
+We extended the analysis of daily data by examining whether the organization of the DMN could be extracted using session data only.
+It is worth noting that the length of each session (approx.
+14 mins long) falls below the stability threshold for fMRI-based modularity estimations [@Gordon2017].
+Nonetheless, high ARI ratios with reduced data could signify the ability to localize a subject's DMN organization with fMRI sessions that are easier to fit along with other study sessions of interest.
+
+``` {r Partition comparison: session similarity matrices, echo=FALSE, message = FALSE, cache = TRUE}
+# Select 10 subjects from the sample to display
+selectSubj <- seq(1,40)
+
+setwd('./Summary_sess/')
+temp <- list.files()
+subjList_sess <- sapply(temp, substring, first=1, last=9)
+Summaries_sess <- lapply(temp, read.csv)
+subjList_sess_plot <- subjList_sess[selectSubj]
+Summaries_sess_plot <- Summaries_sess[selectSubj]
+
+# Across subjects (just for plotting)
+RI_all_between_sess <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
+tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
+RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+```
+
+``` {r Partition comparison: session compare all, echo=FALSE, message = FALSE, cache = TRUE}
+# Now run comparisons among all subjects
+RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
+tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
+RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+
+## Let's compare stuff (not accounting for complex interdependencies in the observations)
+## Overall differences in mean RI between PCC and mPFC
+lowPCC_sess <- RI_PCC_sess[lower.tri(RI_PCC_sess)]
+lowPFC_sess <- RI_PFC_sess[lower.tri(RI_PFC_sess)]
+Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T)
+Sess_PCCvPFC_ES <- cohenD(lowPCC_sess, lowPFC_sess) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
+
+# create a selection matrix containing all within-subject session comparisons
+template <- diagBlocks(ncol(RI_all_between_sess), 4) 
+lowTemplate <- template[lower.tri(template)]
+
+# Overall
+# First list element is the within subject values, second is the between subject values
+lowRISess <- RI_all_between_sess[lower.tri(RI_all_between_sess)]
+Sess_overallComparison <- list(lowRISess[lowTemplate],
+                               lowRISess[!lowTemplate])
+Sess_overallComparison[[3]] <- permute(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
+Sess_overallComparison[[4]] <- cohenD(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
+
+# PCC 
+Sess_PCCComparison <- list(lowPCC_sess[lowTemplate],
+                           lowPCC_sess[!lowTemplate])
+Sess_PCCComparison[[3]] <- permute(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
+Sess_PCCComparison[[4]] <- cohenD(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
+
+# mPFC
+Sess_PFCComparison <- list(lowPFC_sess[lowTemplate],
+                           lowPFC_sess[!lowTemplate])
+Sess_PFCComparison[[3]] <- permute(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
+Sess_PFCComparison[[4]] <- cohenD(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
+
+```
+
+Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 7), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 8).
+
+``` {r Partition comparison: session ratios, echo=FALSE, message = FALSE, cache = TRUE}
+## Brain storming:
+## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
+## Perhaps a more interresting idea would be to generate an index of variance within/between subject
+## These are just attempts at that are not perfect:
+
+# 1) Ratio of mean within subject sessions over between subject ones (per-subject)
+# Overall
+# Split the within-subject session RI values per subject
+temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
+withinSubjVals <- split(Sess_overallComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_sess), by = 4), function(x) RI_all_between_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# PCC
+temp <- ceiling(seq_along(Sess_PCCComparison[[1]])/6)
+withinSubjVals <- split(Sess_PCCComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_sess), by = 4), function(x) RI_PCC_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# PFC
+temp <- ceiling(seq_along(Sess_PFCComparison[[1]])/6)
+withinSubjVals <- split(Sess_PFCComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_sess), by = 4), function(x) RI_PFC_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# Summarize for plotting
+Sess_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
+                                    RI = c(Sess_RIRatios_PCC, Sess_RIRatios_PFC))
+
+# Stats
+Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T)
+Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
+```
+
+We can see again that the ratios for mPFC were higher than those of PCC (permutation,*p*= `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
+This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with relatively small amounts of data in spite of a reduction in the estimates.
+
+### *Pattern stability over time*
+
+``` {r Stability per subject: Overall, echo=FALSE, message = FALSE, cache = TRUE}
+# Load files
+setwd('./Sliding_window/')
+temp <- list.files(pattern = '*Comparisons.csv')
+SC <- lapply(temp, read.csv2)
+temp <- list.files(pattern = '*Values.csv')
+SVals <- lapply(temp, read.csv2)
+
+# Put together a data frame to plot Fiedler vec x proprtion DMN
+allSummaries <- do.call(rbind, Summaries)
+allSummaries$SubjID <- rep(subjList, each = nrow(Summaries[[1]]))
+
+# Do a mixed effects GLM (binomial) to estimate the relationship between Fiedler vec and propDMN
+SC_FVvPDMN_model <- glmer(slidePropDMN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
+SC_FVvPDMN_modelSummary <- summary(SC_FVvPDMN_model)
+allSummaries$FittedVals <- fitted(SC_FVvPDMN_model)
+
+# Overall
+SC_all <- do.call(rbind, SC)
+SC_plot <- ggplot(data = SC_all)
+SC_plot <- SC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = "slategray4",alpha = 0.3, show.legend = F) +
+              geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
+              ylim(0,1) + 
+              theme(text = element_text(size=35)) +
+              labs(y = "ARI") +
+              theme_classic()
+
+# Mean RI across windows per subject
+SC_summary <- aggregate(SC_all$Index, by = list(SC_all$SubjID), FUN = mean)
+SC_summary$SD <- aggregate(SC_all$Index, by = list(SC_all$SubjID), FUN = sd)$x
+colnames(SC_summary) <- list("SubjID", "RI", "SD")
+SC_sd_plot <- ggplot(data = SC_summary, aes(x=SD)) + 
+  geom_density(color = "black", fill = Cols[2]) + 
+  xlim(0,1) +
+  labs(x = "SD") +
+  theme(text = element_text(size=35)) +
+  theme_classic()
+
+## PLAYING WITH AR AND MA PROCESSES
+# tempSC <- do.call(rbind, SC)
+# tempSC <- SC_PFC
+# tempSC$SubjID <- as.factor(tempSC$SubjID)
+# test <- numeric()
+# intercepts <- numeric()
+# coefficients <- numeric()
+# 
+# for (i in seq(100)) {
+#   temp <- arima(SC[[i]]$Index, c(1,0,0), method = "ML")
+#   test <- c(test, temp$residuals)
+#   intercepts[i] <- temp$coef[2]
+#   coefficients[i] <- temp$coef[1] 
+# }
+# 
+# tempSC$Res <- test
+# 
+# ggplot(data = tempSC, aes(Window, Res, group = SubjID, color = SubjID)) +
+#   geom_line(show.legend = F, alpha = 0.5) +
+#   theme_classic()
+# 
+# ggplot(data = tempSC, aes(Res, group = SubjID, color = SubjID)) +
+#   geom_density(alpha = 0.5, show.legend = F) +
+#   theme_classic()
+# 
+# 
+# test <- aggregate(SC_PCC$Index, by = list(SC_PFC$SubjID), arima, order = c(10,0,0), method = "ML")
+# intercepts <- numeric()
+# coefficients <- numeric()
+# for(i in seq(100)) {
+#   intercepts[i] <- test$x[[i]]['intercept']
+#   coefficients[i] <- test$x[[i]]['ar1']
+# }
+# 
+# plot(intercepts)
+
+# AND WITH MORE SIMILARITY MATRICES
+# THE POINT HERE IS THAT I TOOK THE ARI SIMILARITY MATRIX OF ALL THE SLIDING WINDOWS PER SUBJECT AND AVERAGED ACROSS SUBJECTS
+# THIS PRODUCES A MATRIX WHERE YOU CAN TELL THE AUTOCORRELATED NATURE OF THE DATA IF UNCLUSTERED, BUT OTHERWISE THERE ARE MARKED DAY CLUSTERS
+# simMatrices <- list()
+# nrun <- 1
+# for (subj in SVals) {
+#   nWins <- ncol(subj)
+#   if (nWins != 37) {
+#     print("Fewer than 37 windows...")
+#   } else {
+#     tempMat <- matrix(NA, nWins, nWins)
+#     for (i in seq(nWins)) {
+#       for(j in seq(nWins)) {
+#         tempMat[i,j] <- arandi(subj[,i], subj[,j], adjust = T)
+#       }
+#     }
+#     simMatrices[[nrun]] <- tempMat
+#     nrun <- nrun + 1
+#   }
+# }
+# 
+# meanMatrices <- Reduce("+", simMatrices) / length(simMatrices)
+# corrplot(meanMatrices, method = "color", is.corr = F, cl.lim = c(0,1))
+```
+
+While the distinction of DMN and non-DMN is consistent across session and days, it is possible that the decrease in global ARI values going from full to session-specific data could be due to a dynamic shift in DMN organization.
+In order to address this possibility, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the original pattern estimated using the whole time series (Figure 9).
+Note that the length of the windows is well equipped to find stable community features in brain networks [@Gordon2017].
+This analysis revealed persistently high levels of agreement for most subjects, with overall low variability (overall mean of each subject's average ARI = `r round(mean(SC_summary$RI), digits = 2)`; SD = `r round(mean(SC_summary$SD), digits = 2)`).
+
+``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+## Check stability for PCC and mPFC separately
+# Get the sliding values for PCC and PFC separately
+tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
+tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)
+
+SC_PCC <- data.frame()
+SC_PFC <- data.frame()
+
+for (subj in seq(nSubj)) {
+  tempPCC <- numeric()
+  tempPFC <- numeric()
+  nWins <- ncol(tempSW_PCC[[subj]])
+  for (Win in seq(nWins)) {
+    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][,Win], adjust = T)
+    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][,Win], adjust = T)
+  }
+  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
+                      Window = seq(nWins),
+                      Index = tempPCC)
+  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
+                      Window = seq(nWins),
+                      Index = tempPFC)
+  SC_PCC <- rbind(SC_PCC, dfPCC)
+  SC_PFC <- rbind(SC_PFC, dfPFC)
+}
+
+SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
+SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
+SC_PCC_summary$Region <- rep("PCC", nSubj)
+SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
+SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
+SC_PFC_summary$Region <- rep("mPFC", nSubj)
+SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
+colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
+rm(SC_PCC_summary, SC_PFC_summary)
+
+# Compare mean ARI of sliding windows between regions
+SW_PCCvPFC_permuteTest <- permute(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"], paired = T)
+SW_PCCvPFC_ES <- cohenD(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"])
+
+```
+
+We additionally performed this analysis on mPFC and PCC separately to determine whether these results were region-specific (Figure 10).
+Even though the within-subject variance remained low for both regions, we found that the average agreement per subject was significantly higher for PCC (paired permutation,*p*= `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+Nonetheless, the mean ARI across each subject's time series was still relatively high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), thus suggesting that the each individual's DMN distribution is cosiderably stable in time.
+
+We complemented these analyses by asking whether the magnitude of values in the Fiedler vector was associated with the stability of nodes throughout a subject's time series (*PERSONAL NOTE: It might be better to justify this from the use of this vector in statistical mechanics rather than mere curiosity, i.e.
+extreme FV values are given to elements at the peaks of the wave.
+Find a simple citation for this.*).
+Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model, with subject acting as a random effect (Figure 11).
+The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`,*p*< 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time.
+These analysis show that the original pattern identified with the full dataset is temporally stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN vertices in relatively short fMRI sessions (i.e.
+less than 20 mins).
+
+\bigskip
+
+### *Potential Noise Effects (this part is challenging)*
+
+``` {r Noise Effects: tSNR Comparison, echo=FALSE, message = FALSE, cache = TRUE}
+## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
+# Flexibility vs SNR
+# Are vertices with lower SNR switching communities more often?
+SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))
+
+# Compare SNR between PCC and mPFC per subject
+SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval)
+SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
+SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff))
+prcntSig <- (sum(SNR_PCCvsPFC_perm < 0.05) / nSubj) * 100
+
+# Get the mean SNR for each region and compare overall levels 
+SNR_meanPCC <- sapply(tempComm_PCC, function(data) mean(data$varCoeff))
+SNR_meanPFC <- sapply(tempComm_PFC, function(data) mean(data$varCoeff))
+SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
+                     Comparison = permute(SNR_meanPCC, SNR_meanPFC)$Pval,
+                     ES = cohenD(SNR_meanPCC, SNR_meanPFC))
+rm(SNR_meanPCC, SNR_meanPFC)
+```
+
+Even though our findings point to a stable representation of each subject's unique DMN organization, it is still possible that they were affected by considerable levels of signal noise often found in mPFC (its ventral segment in particular).
+As a first step to account for this, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
+mean of each vertex's time points over their standard deviation).
+The tSNR of all vertices were averaged per region and subject (Figure 12), which showed that indeed mPFC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`) was overall noisier than PCC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`) across subjects (permutation, *p* = `r SNR_meanComp$Comparison`, Cohen's D = `r round(SNR_meanComp$ES, digits = 2)`).
+To more precisely examine this difference, we performed subject-wise comparisons of the tSNR values of all vertices between PCC and mPFC (total `r nSubj` permutation tests, 5000 iterations each).
+About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected; mean Cohen's D = `r round(mean(SNR_PCCvsPFC_ES), digits = 2)`).
+In addition, we found that the levels of tSNR for each vertex showed significant negative correlations with flexibility, a graph-theoretic index that measures the proportion of times a node in a network changed affiliation across partitions (mean *r* = `r round(mean(SNR_vs_Flex), digits = 2)`).
+These findings indicate that, for any given subject, vertices with low SNR resulted in more variable participation between the communities, and these vertices were more common in mPFC.
+This could explain why mPFC previously showed lower stability levels.
+
+``` {r Noise Effects: Per-subject Fiedler by R-sqd, fig.align="center", fig.width=3, fig.height=3, fig.cap = "FORMER Figure 13.
+Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
+setwd('./Variance/')
+temp <- list.files()
+Variance <- lapply(temp, read.csv)
+
+### Grab some of the other measures from the overall summary
+for (i in seq(nSubj)) {
+  tempIndex <- Summaries[[i]]$Vertex %in% Variance[[i]]$Vertex
+  Variance[[i]]$SubjID <- rep(subjList[i], nrow(Variance[[i]]))
+  Variance[[i]]$FiedlerVec <- Summaries[[i]]$FiedlerVec[tempIndex]
+  Variance[[i]]$Flexibility <- Summaries[[i]]$slideFlexibility[tempIndex]
+  Variance[[i]]$propDMN <- Summaries[[i]]$slidePropDMN[tempIndex]
+  Variance[[i]]$varCoeff <- Summaries[[i]]$varCoeff[tempIndex]
+  Variance[[i]]$Region <- ifelse(Variance[[i]]$tempY < 0, "PCC", "mPFC")
+}
+
+# let's put everyone's data together first
+allVariance <- do.call(rbind, Variance)
+
+# get the mean and SE of the R-squared values per subject/region
+allVariance_sumarized <- aggregate(allVariance$Rsquared ~ allVariance$SubjID + allVariance$Region, FUN = 'mean')
+colnames(allVariance_sumarized) <- list("SubjID", "Region", "meanRsquared")
+allVariance_sumarized$SEM <- aggregate(allVariance$Rsquared ~ allVariance$SubjID + allVariance$Region, FUN = function(data) {sd(data)/sqrt(length(data))})[ , 3]
+
+# Create a new data frame with values restricted to mPFC (for plotting and further stats)
+mPFCVariance <- allVariance[allVariance$Region == "mPFC", ]
+
+# Get the correlations between Z-axis, R2, and tSNR for every subject (to take mean and SD in text)
+# I just came up with this, so the code should be made more parsimonious in the future (like, why bind and then split...?)
+tempSubj <- split(mPFCVariance, f = mPFCVariance$SubjID)
+# Get the correlation coefficients
+noiseCors <- data.frame(R2vtSNR = sapply(tempSubj, function(data) {cor(data$Rsquared, data$varCoeff)}),
+                        ZvtSNR = sapply(tempSubj, function(data) {cor(data$tempZ, data$varCoeff)}),
+                        ZvR2 = sapply(tempSubj, function(data) {cor(data$tempZ, data$Rsquared)}))
+rm(tempSubj)
+
+# plot
+# There is a strong linear relationship between the Fiedler vector and the R-squared values
+# These match perfectly on the brain when inspected qualitatively
+v1 <- ggplot(data = allVariance) + 
+  geom_smooth(aes(FiedlerVec, Rsquared, group = SubjID), fill = "gray70", color = "gray30", show.legend = F) + 
+  labs(x = "Fiedler Vector Values", y = "R-Squared Values") + 
+  theme_classic()
+
+# The lower the R-squared, the more likely it is for nodes to change affiliation throughout time
+v2 <- qplot(data = allVariance, Rsquared, Flexibility, color = SubjID, fill = SubjID, geom = "smooth") + theme_classic()
+
+# And of course (given the relationship with the Fiedler vector), there's a sigmoidal relationship between R-squared vals and proportion of DMN affiliation
+# only showing the upper side of the sigmoid here, as these values are restricted to the DMN community
+v3 <- qplot(data = allVariance, Rsquared, propDMN, color = SubjID, fill = SubjID, geom = "smooth") + theme_classic()
+
+# Finally, it's worth comparing the R-squared values between PCC and mPFC
+# The intuition is that the variance explained by the community might be lower for mPFC given its noise
+# And the answer is: mPFC yields significantly lower R-squares per subject and overall, as expected.
+# To formally compare this (and given the binomial distribution of R-squares in mPFC), I report the Cohen's D per subject for PCC vs mPFC
+v4 <- ggplot(data = allVariance_sumarized, aes(x = SubjID, y = meanRsquared, group = Region, color = Region)) +
+  geom_point(show.legend = F) +
+  geom_line(show.legend = F) +
+  geom_errorbar(aes(ymin = meanRsquared - SEM, ymax = meanRsquared + SEM)) +
+  scale_color_manual(values = Cols[seq(2)]) +
+  ylim(0,0.5) +
+  labs(x = "Subject", y = "Mean R-squared") +
+  theme_classic() +
+  theme(axis.text.x = element_blank()) 
+v5 <- qplot(data = allVariance, Region, Rsquared, fill = Region, geom = "boxplot") + theme_classic()
+Rsq_PCCvsPFC_Wilcox <- sapply(Variance, function(data) {wilcox.test(data$Rsquared[data$Region == "PCC"], data$Rsquared[data$Region == "mPFC"])$p.value})
+Rsq_PCCvsPFC_Wilcox <- p.adjust(Rsq_PCCvsPFC_Wilcox, method = "BY")
+prcntSig <- (sum(Rsq_PCCvsPFC_Wilcox < 0.05) / nSubj) * 100
+Rsq_PCCvsPFC_ES <- sapply(Variance, function(data) {cohenD(data$Rsquared[data$Region == "PCC"], data$Rsquared[data$Region == "mPFC"])})
+
+# This begs the question of a "gradient of noise" along the z-axis on mPFC
+# Not really, but the coefficient of variation derived from minimally preprocessed data does show a strong trend
+# Namely, the more ventral, the lower the SNR
+# v6 <- ggplot(data = allVariance, aes(Rsquared, tempZ, fill = Region)) +
+#         geom_point(color = "black", pch = 21, alpha = 0.1) + 
+#         scale_fill_manual(values = Cols[seq(2)]) +
+#         theme_classic()
+# v7 <- ggplot(data = allVariance, aes(varCoeff, tempZ, fill = Region)) +
+#         geom_point(color = "black", pch = 21) + 
+#         scale_fill_manual(values = Cols[seq(2)]) +
+#         theme_classic()
+
+#v1
+
+```
+
+To further interrogate the potential effect of noise in our results, we computed the variance explained by activity from each DMN vertex on the mean time series of the DMN community.
+If the signal quality issues persisted after preprocessing the data, we expected that noisy vertices would have the least explicative power on the activity of the DMN community as a whole.
+This also implied lower $R^2$ values for mPFC.
+Indeed, we found that for each subject, $R^2$ values tended to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had *p* values < 0.001; mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`) (Figure 13).
+These results suggest that, overall, vertices in mPFC tended to be less in synchrony with the activity of the DMN community as a whole.
+Furthermore, the degree tSNR showed a moderate correlation with $R^2$ values across participants (mean *r* = `r round(mean(noiseCors$R2vtSNR), digits = 2)`; SD = `r round(sd(noiseCors$R2vtSNR), digits = 2)`), meaning that noisier vertices were less in synchrony with the general activity of the DMN.
+
+Given this trend, we asked whether there is a "gradient of noise" along the z-axis of mPFC, such that more ventral vertices would both be noisier and explain the least amount of DMN variance.
+Here we found that while $R^2$ are somewhat correlated with dorsal-ventral placement across subjects (mean *r* = `r round(mean(noiseCors$ZvR2), digits = 2)`; SD = `r round(sd(noiseCors$ZvR2), digits = 2)`), there is no clear relationship with the z-axis across subjects (Figure 14).
+Specifically, low $R^2$ are evenly distributed along this axis, denoting a degree of orthogonality between these features.
+Conversely, tSNR showed a strong linear relationship with the position of the vertex along this axis (mean *r* = `r round(mean(noiseCors$ZvtSNR), digits = 2)`; SD = `r round(sd(noiseCors$ZvtSNR), digits = 2)`).
+These results contextualize the degree of synchrony of mPFC vertices in terms of potential noise.
+While still an important factor, it is unlikely that the degree of within-subject pattern stability observed here could be due mostly to highly structured mPFC noise.
+
+### *Correlation vs community detection in mPFC*
+
+``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+## Between halves analysis for correlation and communities (mPFC only)
+tempComm_PFC_halves_plot <- lapply(seq_along(tempComm_PFC_halves_plot), function(x) cbind(tempComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
+D1 <- tempComm_PFC_halves_plot
+D2 <- lapply(tempComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
+Data <- c(D1,D2)
+allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
+```
+
+``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+# Compare correlation with community approach on mPFC
+# tempComm_PFC_halves <- lapply(seq_along(tempComm_PFC_halves), function(x) cbind(tempComm_PFC_halves[[x]], Correlation_halves[[x]]))
+# tempComm <- sapply(seq(1, 20, by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
+# tempCor <- sapply(seq(1, 20, by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
+# prepostComp <- data.frame(Community = tempComm, Correlation = tempCor)
+# prepostComp <- melt(prepostComp)
+# colnames(prepostComp) <- c("Approach", "Correlation")
+# prepostComp_test <- permute(tempComm, tempCor, paired = T)
+# 
+# 
+# ## Between halves analysis for correlation and communities (mPFC only)
+# D1 <- tempComm_PFC_halves
+# D2 <- lapply(tempComm_PFC_halves, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
+# Data <- c(D1,D2)
+# allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = length(Data), Index = "Cor", subjNames = c(subjList_halves, subjList_halves))
+#
+
+# Compare correlation with community approach on mPFC
+tempComm <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
+tempCor <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
+tempBoth <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
+prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
+prepostComp <- melt(prepostComp)
+colnames(prepostComp) <- c("Approach", "Correlation")
+prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
+prepostComp_ES <- cohenD(tempComm, tempCor)
+```
+
+The computational demands of our approach escalate quickly as the number of vertices increases.
+We thus explored the possible advantage to using graph-theoretic approaches on all possible network connections over a simple seed-based functional connectivity analysis from PCC.
+Given that the spatial distribution of the DMN is considerably stable within individuals [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018], we examined whether maps generated with spectral partitioning were more similar per subject across days than those computed from seed-based correlations.
+First, we computed the mean time series of all the vertices contained in the DMN PCC ROI from Yeo et al.
+(2011) parcellation, and correlated it with the activity of every mPFC vertex from our ROIs.
+We then performed pairwise spatial Pearson correlations among maps computed for each day and method from all subjects (Figure 15).
+
+Figure 16 shows the overall degree of similarity across days for patterns dervied using community detection, seed-based correlation, and across methods (i.e.
+day one community detection versus day two seed-based correlation).
+While both approaches are very consistent, community detection displayed a significantly higher ARI across days than a simple correlation (paired permutation *p* < 0.001; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
+It is worth noting that the cross-method agreement is fair, meaning that both approaches show similar topological features.
+These findings suggest that graph-theoretic community detection algorithms provide a better way to detect stable functional topologies, an important factor when faced with the levels of noise present in mPFC.
+
+### *Structural correspondence*
+
+``` {r Structural correspondence, fig.align="center", echo=FALSE, message = FALSE}
+# Mean of correlations
+meanMyelin <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
+meanCurv <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
+meanThick <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
+
+# SD 
+sdMyelin <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
+sdCurv <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
+sdThick <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
+```
+
+Finally, we coarsely examined whether these idiosyncratic topographical arrangements were defined by anatomical brain features.
+To do so, we correlated each subject's Fiedler vector with their respective structural MRI data.
+On average, we found that the Fiedler vector is uncorrelated with myelin density (mean *r* = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean *r* = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean *r* = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`).
+While these findings point at an orthogonality between structure and functional organization, they resonate with previous work that found no strong matches between intersubject functional variability and cortical thickness, and low variability in sulcal depth within DMN [@Mueller2013a].
+
+## Discussion
+
+For clinical implications, see Hiser & Koenigs 2018.
+In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC.
+It would be more interesting to identify the repercussions to damage in mPFC per individual.
+They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment.
+The refinement of the technique is thus coupled to being able to identify personalized functional topologies.
+They list a number of results related to mPFC functional connectivity too.
+In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse.
+(note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)
+
+It will also be good to note that there is concurrent debate on the ground truth of community detection.
+In other fields, identifying a community structure is not necessarily associated with the true organization of the network.
+What happens is that you might find a tangential grouping that gives you information different from your original goal [@Clauset2004]
+
+Mention the lack of interhemispheric distinction, citing Mackey and Petrides in regards to L-R diffs.
+
+It's also worth mentioning that PCC is largely covered by DMN.
+Then why does this area overlap with SV?
+I think the Mueller paper mentions that PCC is an important hub of the brain, and perhaps subserves many cognitive functions (recent Wash U paper on this too).
+
+And write a portion on the lack of subcortical reward-related regions (i.e.
+striatum).
+Say something like 'incorporating the ventral striatum did notrefine these partitions through either method.
+This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future.
+Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DMN and SV'.
+
+Talk about how there are other community detection algorithms, and that modularity and SP over and underfit, respectively.
+However, SP eigenmaps have been found to provide relevant functional information.
+In addition, both modularity and SP rely on connectivity strength, and thus is amenable to the correlative nature of functional connectivity.
+
+Add a portion showing that summing up the binarized maps produces a map similar to the one produced by Margulies et al. and others.
+
+It might also be worth mentioning that previous work has established the shift in network types during rest through hidden Markov models (Vidaurre et al., 2016?).
+While this suggests that we should see fluctuations in affiliation, and not stability, Vidaurre's work establishes the dynamics of prevalent function among networks, and not their topologies.
+Our work focuses on the topographical arrangement of the DMN network, which can be active or not while maintaining its form.
+So, the two works are compatible.
+Note, I played a bit with AR and MA processes per subject to try to understand the autocorrelation in the sliding window.
+First, both acf/pacf and arima (order = n,0,n) R functions suggested that the data was better fit by AR.
+Moreover, ARs from 1 to 10 had neglegible differences, so I stuck with 1 results for simplicity.
+As expected the data is significantly autocorrelated, and when I checked plotted the residuals they were mostly within the 0.15 bound (normally distributed).
+Coefficients ranged from 0.6 to 1.
+So, there is clear rythmicity in the agreement between each window and the overall pattern.
+However, the intercepts from the ARn processes gave more or less the same estimates as the mean rand index over all the windows.
+This is mostly expected, as we saw that the standard deviation of the rand index was low across participants.
+I am currently interpreting this as a signal that there is clear periodicity that is otherwise harmless for our results: in the end, the agreement remains stable throughout the 4800 TRs.
+
+In terms of noise, there are a handful of things to keep in mind.
+First is that yes, mPFC is noisier overall, but that did not preclude the relatively high levels of agreement across days and sessions per subject, even though ARI heavily penalizes discrepancies (less than linearly).
+Second, low $R^2$ values were found all throughout the z-axis, meaning that variance explained is not strictly determined by the cardinal position of the vertex (and while the correlation was significant due to the sheer number of items, the coefficient was relatively low).
+Right now this might be ok as a way to bypass noise comments, but it would also be interesting to take advantage of the Fiedler vector here.
+Since it's linearly related to $R^2$ per subject, perhaps finding a way to threshold these values would provide cleaner and even more consistent maps.
+
+\newpage
+## Acknowledgements
+
+We would like to thank Dan Sussman for initial guidance on community detection and evaluation methods.
+Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
+
+## Supplemental Materials
+
+### *Table 1. Significant brain regions per literature*
+| Literature                  | Significant Brain Regions   |
+| :-------------------------- | --------------------------: |
+| Default Mode Network        | `r paste(dmnLbls)`          |
+| Subjective Value            | `r paste(valLbls)`          |
+
+## Figures
+
+```{r Meta-analysis ROIs (Fig.
+1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1.
+Template atlas from Glasser et al.
+(2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
+Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
+# Change to inflated eventually
+include_graphics("./Images/ROIS2.png")
+```
+
+```{r Template partition (Fig.
+2), out.width="50%", fig.align = "center", fig.cap = "Figure 2.
+Brain partition for an example subject (100307).
+Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
+The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
+include_graphics("./Images/newPattern_both.png")
+```
+
 ``` {r Partition comparison: all cross-method agreement (Fig.
@@
 (Will probably remove this figure)"}
-# Cross-method
-# Don't worry about plotting, since that's mainly for a general visualization
-RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary","Membership"), nSubjects = length(Summaries), subjNames = subjList)
-
 RI_within_plot <- ggplot(data = RI_all_within, aes(Index)) + 
@@
 
-``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
-# Across subjects
-# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
-RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
-RI_all_between_lowtri <- RI_all_between[lower.tri(RI_all_between)]
-
-posteriorIndx <- Summaries[[1]]$y < 0
-tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
-tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
-RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
-RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
-
-# Let's compare stuff
-testPCC <- RI_PCC[lower.tri(RI_PCC)]
-testPFC <- RI_PFC[lower.tri(RI_PFC)]
-Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
-Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-```
-
-The distribution suggests that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
-The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not.
-This adds evidence to the division of these areas into DMN and non-DMN during rest.
-
-Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was considerable agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
-However, qualitative inspection of the brain community topologies shows good alignment for PCC, with a topologically similar mPFC pattern that shifts topographically across subjects.
-To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 4).
-Indeed, this analysis showed that the functional topology of PCC is well maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), while mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) showed significantly lower levels of agreement (paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
-
 ``` {r Partition comparison: all 2 (Fig.
@@
 PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}
-
-# par(mfrow = c(1,2))
-# corrplot(RI_all_between,
-#          is.corr = F, 
-#          method = "color", 
-#          tl.pos = "n", 
-#          tl.col = "black", 
-#          cl.lim = c(0,1),
-#          cl.pos = "b",
-#          cl.length = 3)
-# mtext("Subjects", side = 2, line = -4.5, cex = 1.5)
-# mtext("Subjects", side = 3, line = 4.5, cex = 1.5)
 par(xpd=T)
@@
 
-```
-
-\bigskip
-
-### *Partition Comparison: Day 1 vs Day 2*
-
-In order to determine whether the low agreement shown in mPFC across subjects was a function of intrinsic variability or a subject-specific pattern, we compared the agreement among communities estimated with data from each separate day.
-If the latter were true, within-subject ARI values should be consistently higher than across subjects.
-Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.
-Communities were estimated on concatenated pairs of daily left-right and right-left phase encoded sessions (see Methods for details), and once again compared using ARI.
-Figure 5 shows pairwise comparisons among ten example subjects for PCC and mPFC separately.
-
-``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
-# Select 10 subjects from the sample to display
-selectSubj <- seq(1,20)
-
-# Load
-setwd('./Summary_halves/')
-temp <- list.files(pattern = "*_finalSummary.csv")
-subjList_halves <- sapply(temp, substring, first=1, last=9)
-Summaries_halves <- lapply(temp, read.csv)
-Summaries_halves_plot <- Summaries_halves[selectSubj]
-subjList_halves_plot <- subjList_halves[selectSubj]
-
-temp <- list.files(pattern = "*_corHalves.csv")
-Correlation_halves <- lapply(temp, read.csv, header = F)
-Correlation_halves_plot <- Correlation_halves[selectSubj]
-
-# Compare all halves with RI
-RI_all_between_halves <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-
-# Compare PCC and PFC among all subjects
-tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
-tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
-RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
 ```
@@
 PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE, cache = TRUE}
-## Now compare all possible pairs of subjects
-# Compare all halves with RI
-RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-
-# Compare PCC and PFC among all subjects
-tempComm_PCC_halves <- lapply(Summaries_halves, "[", i = posteriorIndx, j =)
-tempComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
-RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-
-## Let's compare stuff (not accounting for complex interdependencies in the observations)
-## Overall differences in mean RI between PCC and mPFC
-lowPCC_halves <- RI_PCC_halves[lower.tri(RI_PCC_halves)]
-lowPFC_halves <- RI_PFC_halves[lower.tri(RI_PFC_halves)]
-Halves_PCCvPFC_perm <- permute(lowPCC_halves, lowPFC_halves, statType = mean, paired = T)
-Halves_PCCvPFC_ES <- cohenD(lowPCC_halves, lowPFC_halves) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
-# create a selection matrix containing all within-subject session comparisons
-template <- diagBlocks(ncol(RI_all_between_halves), 2) 
-lowTemplate <- template[lower.tri(template)]
-
-# Overall
-# First list element is the within subject values, second is the between subject values
-lowRIHalves <- RI_all_between_halves[lower.tri(RI_all_between_halves)]
-Halves_overallComparison <- list(lowRIHalves[lowTemplate],
-                                lowRIHalves[!lowTemplate])
-Halves_overallComparison[[3]] <- permute(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
-Halves_overallComparison[[4]] <- cohenD(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
-
-# PCC 
-Halves_PCCComparison <- list(lowPCC_halves[lowTemplate],
-                           lowPCC_halves[!lowTemplate])
-Halves_PCCComparison[[3]] <- permute(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
-Halves_PCCComparison[[4]] <- cohenD(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
-
-# mPFC
-Halves_PFCComparison <- list(lowPFC_halves[lowTemplate],
-                           lowPFC_halves[!lowTemplate])
-Halves_PFCComparison[[3]] <- permute(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
-Halves_PFCComparison[[4]] <- cohenD(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
-
-## Ratio of mean within subject sessions over between subject ones (per-subject)
-# Overall
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_all_between_halves[lower.tri(RI_all_between_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_halves), by = 2), function(x) RI_all_between_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_overall <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# PCC
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_PCC_halves[lower.tri(RI_PCC_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_halves), by = 2), function(x) RI_PCC_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_PCC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# PFC
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_PFC_halves[lower.tri(RI_PFC_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_halves), by = 2), function(x) RI_PFC_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_PFC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# Summarize for plotting
-Halves_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
-                                      RI = c(Halves_RIRatios_PCC, Halves_RIRatios_PFC))
-
-# Stats
-Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T)
-Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
-
 # plot
@@
   theme_classic(base_size = 14)
-
-```
-
-Once again we found greater alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) than mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed higher levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
-However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic.
-Therefore, we divided each subject's ARI between days by the ARI values with the days from the other subjects.
-This ratio denotes the relative specificity of their partition.
-That means, partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
-Figure 6 shows the ratios for PCC and mPFC for all subjects.
-As expected, we found that while both regions had good specificity (i.e.
-ratios > 1), the ratios for PCC were significantly lower than mPFC (paired permutation,*p*= `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
-These test/retest results suggest that the topographic varability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
-
-\bigskip
-
-### *Partition Comparison: Session*
-
-We extended the analysis of daily data by examining whether the organization of the DMN could be extracted using session data only.
-It is worth noting that the length of each session (approx.
-14 mins long) falls below the stability threshold for fMRI-based modularity estimations [@Gordon2017].
-Nonetheless, high ARI ratios with reduced data could signify the ability to localize a subject's DMN organization with fMRI sessions that are easier to fit along with other study sessions of interest.
-
-``` {r Partition comparison: session similarity matrices, echo=FALSE, message = FALSE, cache = TRUE}
-# Select 10 subjects from the sample to display
-selectSubj <- seq(1,40)
-
-setwd('./Summary_sess/')
-temp <- list.files()
-subjList_sess <- sapply(temp, substring, first=1, last=9)
-Summaries_sess <- lapply(temp, read.csv)
-subjList_sess_plot <- subjList_sess[selectSubj]
-Summaries_sess_plot <- Summaries_sess[selectSubj]
-
-# Across subjects (just for plotting)
-RI_all_between_sess <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
-tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
-RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
 ```
@@
 
-``` {r Partition comparison: session compare all, echo=FALSE, message = FALSE, cache = TRUE}
-# Now run comparisons among all subjects
-RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
-tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
-RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-
-## Let's compare stuff (not accounting for complex interdependencies in the observations)
-## Overall differences in mean RI between PCC and mPFC
-lowPCC_sess <- RI_PCC_sess[lower.tri(RI_PCC_sess)]
-lowPFC_sess <- RI_PFC_sess[lower.tri(RI_PFC_sess)]
-Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T)
-Sess_PCCvPFC_ES <- cohenD(lowPCC_sess, lowPFC_sess) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
-
-# create a selection matrix containing all within-subject session comparisons
-template <- diagBlocks(ncol(RI_all_between_sess), 4) 
-lowTemplate <- template[lower.tri(template)]
-
-# Overall
-# First list element is the within subject values, second is the between subject values
-lowRISess <- RI_all_between_sess[lower.tri(RI_all_between_sess)]
-Sess_overallComparison <- list(lowRISess[lowTemplate],
-                               lowRISess[!lowTemplate])
-Sess_overallComparison[[3]] <- permute(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
-Sess_overallComparison[[4]] <- cohenD(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
-
-# PCC 
-Sess_PCCComparison <- list(lowPCC_sess[lowTemplate],
-                           lowPCC_sess[!lowTemplate])
-Sess_PCCComparison[[3]] <- permute(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
-Sess_PCCComparison[[4]] <- cohenD(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
-
-# mPFC
-Sess_PFCComparison <- list(lowPFC_sess[lowTemplate],
-                           lowPFC_sess[!lowTemplate])
-Sess_PFCComparison[[3]] <- permute(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
-Sess_PFCComparison[[4]] <- cohenD(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
-
-```
-
-Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 7), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 8).
-
 ``` {r Partition comparison: session ratios (Fig.
@@
 Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE, cache = TRUE}
-## Brain storming:
-## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
-## Perhaps a more interresting idea would be to generate an index of variance within/between subject
-## These are just attempts at that are not perfect:
-
-# 1) Ratio of mean within subject sessions over between subject ones (per-subject)
-# Overall
-# Split the within-subject session RI values per subject
-temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
-withinSubjVals <- split(Sess_overallComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_sess), by = 4), function(x) RI_all_between_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# PCC
-temp <- ceiling(seq_along(Sess_PCCComparison[[1]])/6)
-withinSubjVals <- split(Sess_PCCComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_sess), by = 4), function(x) RI_PCC_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# PFC
-temp <- ceiling(seq_along(Sess_PFCComparison[[1]])/6)
-withinSubjVals <- split(Sess_PFCComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_sess), by = 4), function(x) RI_PFC_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# Summarize for plotting
-Sess_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
-                                    RI = c(Sess_RIRatios_PCC, Sess_RIRatios_PFC))
-
-# Stats
-Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T)
-Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
-
 ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
@@
 
-We can see again that the ratios for mPFC were higher than those of PCC (permutation,*p*= `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
-This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with relatively small amounts of data in spite of a reduction in the estimates.
-
-### *Pattern stability over time*
-
 ``` {r Stability per subject: Overall (Fig.
@@
 ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE, cache = TRUE}
-# Load files
-setwd('./Sliding_window/')
-temp <- list.files(pattern = '*Comparisons.csv')
-SC <- lapply(temp, read.csv2)
-temp <- list.files(pattern = '*Values.csv')
-SVals <- lapply(temp, read.csv2)
-
-# Put together a data frame to plot Fiedler vec x proprtion DMN
-allSummaries <- do.call(rbind, Summaries)
-allSummaries$SubjID <- rep(subjList, each = nrow(Summaries[[1]]))
-
-# Do a mixed effects GLM (binomial) to estimate the relationship between Fiedler vec and propDMN
-SC_FVvPDMN_model <- glmer(slidePropDMN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
-SC_FVvPDMN_modelSummary <- summary(SC_FVvPDMN_model)
-allSummaries$FittedVals <- fitted(SC_FVvPDMN_model)
-
-# Overall
-SC_all <- do.call(rbind, SC)
-SC_plot <- ggplot(data = SC_all)
-SC_plot <- SC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = "slategray4",alpha = 0.3, show.legend = F) +
-              geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
-              ylim(0,1) + 
-              theme(text = element_text(size=35)) +
-              labs(y = "ARI") +
-              theme_classic()
-
-# Mean RI across windows per subject
-SC_summary <- aggregate(SC_all$Index, by = list(SC_all$SubjID), FUN = mean)
-SC_summary$SD <- aggregate(SC_all$Index, by = list(SC_all$SubjID), FUN = sd)$x
-colnames(SC_summary) <- list("SubjID", "RI", "SD")
-SC_sd_plot <- ggplot(data = SC_summary, aes(x=SD)) + 
-  geom_density(color = "black", fill = Cols[2]) + 
-  xlim(0,1) +
-  labs(x = "SD") +
-  theme(text = element_text(size=35)) +
-  theme_classic()
-
+# TAKE THE TIME TO BRING THE GGPLOT DEFINITION DOWN HERE EVENTUALLY
 grid.arrange(SC_plot, SC_sd_plot, ncol = 2)
-
-## PLAYING WITH AR AND MA PROCESSES
-# tempSC <- do.call(rbind, SC)
-# tempSC <- SC_PFC
-# tempSC$SubjID <- as.factor(tempSC$SubjID)
-# test <- numeric()
-# intercepts <- numeric()
-# coefficients <- numeric()
-# 
-# for (i in seq(100)) {
-#   temp <- arima(SC[[i]]$Index, c(1,0,0), method = "ML")
-#   test <- c(test, temp$residuals)
-#   intercepts[i] <- temp$coef[2]
-#   coefficients[i] <- temp$coef[1] 
-# }
-# 
-# tempSC$Res <- test
-# 
-# ggplot(data = tempSC, aes(Window, Res, group = SubjID, color = SubjID)) +
-#   geom_line(show.legend = F, alpha = 0.5) +
-#   theme_classic()
-# 
-# ggplot(data = tempSC, aes(Res, group = SubjID, color = SubjID)) +
-#   geom_density(alpha = 0.5, show.legend = F) +
-#   theme_classic()
-# 
-# 
-# test <- aggregate(SC_PCC$Index, by = list(SC_PFC$SubjID), arima, order = c(10,0,0), method = "ML")
-# intercepts <- numeric()
-# coefficients <- numeric()
-# for(i in seq(100)) {
-#   intercepts[i] <- test$x[[i]]['intercept']
-#   coefficients[i] <- test$x[[i]]['ar1']
-# }
-# 
-# plot(intercepts)
-
-# AND WITH MORE SIMILARITY MATRICES
-# THE POINT HERE IS THAT I TOOK THE ARI SIMILARITY MATRIX OF ALL THE SLIDING WINDOWS PER SUBJECT AND AVERAGED ACROSS SUBJECTS
-# THIS PRODUCES A MATRIX WHERE YOU CAN TELL THE AUTOCORRELATED NATURE OF THE DATA IF UNCLUSTERED, BUT OTHERWISE THERE ARE MARKED DAY CLUSTERS
-# simMatrices <- list()
-# nrun <- 1
-# for (subj in SVals) {
-#   nWins <- ncol(subj)
-#   if (nWins != 37) {
-#     print("Fewer than 37 windows...")
-#   } else {
-#     tempMat <- matrix(NA, nWins, nWins)
-#     for (i in seq(nWins)) {
-#       for(j in seq(nWins)) {
-#         tempMat[i,j] <- arandi(subj[,i], subj[,j], adjust = T)
-#       }
-#     }
-#     simMatrices[[nrun]] <- tempMat
-#     nrun <- nrun + 1
-#   }
-# }
-# 
-# meanMatrices <- Reduce("+", simMatrices) / length(simMatrices)
-# corrplot(meanMatrices, method = "color", is.corr = F, cl.lim = c(0,1))
-```
-
-While the distinction of DMN and non-DMN is consistent across session and days, it is possible that the decrease in global ARI values going from full to session-specific data could be due to a dynamic shift in DMN organization.
-In order to address this possibility, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the original pattern estimated using the whole time series (Figure 9).
-Note that the length of the windows is well equipped to find stable community features in brain networks [@Gordon2017].
-This analysis revealed persistently high levels of agreement for most subjects, with overall low variability (overall mean of each subject's average ARI = `r round(mean(SC_summary$RI), digits = 2)`; SD = `r round(mean(SC_summary$SD), digits = 2)`).
-
-``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
-## Check stability for PCC and mPFC separately
-# Get the sliding values for PCC and PFC separately
-tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
-tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)
-
-SC_PCC <- data.frame()
-SC_PFC <- data.frame()
-
-for (subj in seq(nSubj)) {
-  tempPCC <- numeric()
-  tempPFC <- numeric()
-  nWins <- ncol(tempSW_PCC[[subj]])
-  for (Win in seq(nWins)) {
-    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][,Win], adjust = T)
-    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][,Win], adjust = T)
-  }
-  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
-                      Window = seq(nWins),
-                      Index = tempPCC)
-  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
-                      Window = seq(nWins),
-                      Index = tempPFC)
-  SC_PCC <- rbind(SC_PCC, dfPCC)
-  SC_PFC <- rbind(SC_PFC, dfPFC)
-}
-
-SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
-SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
-SC_PCC_summary$Region <- rep("PCC", nSubj)
-SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
-SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
-SC_PFC_summary$Region <- rep("mPFC", nSubj)
-SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
-colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
-rm(SC_PCC_summary, SC_PFC_summary)
-
-# Compare mean ARI of sliding windows between regions
-SW_PCCvPFC_permuteTest <- permute(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"], paired = T)
-SW_PCCvPFC_ES <- cohenD(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"])
-
-```
-
-We additionally performed this analysis on mPFC and PCC separately to determine whether these results were region-specific (Figure 10).
-Even though the within-subject variance remained low for both regions, we found that the average agreement per subject was significantly higher for PCC (paired permutation,*p*= `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
-Nonetheless, the mean ARI across each subject's time series was still relatively high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), thus suggesting that the each individual's DMN distribution is cosiderably stable in time.
+```
 
@@
 ```
-
-We complemented these analyses by asking whether the magnitude of values in the Fiedler vector was associated with the stability of nodes throughout a subject's time series (*PERSONAL NOTE: It might be better to justify this from the use of this vector in statistical mechanics rather than mere curiosity, i.e.
-extreme FV values are given to elements at the peaks of the wave.
-Find a simple citation for this.*).
-Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model, with subject acting as a random effect (Figure 11).
-The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`,*p*< 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time.
-These analysis show that the original pattern identified with the full dataset is temporally stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN vertices in relatively short fMRI sessions (i.e.
-less than 20 mins).
 
@@
 
-\bigskip
-
-### *Potential Noise Effects (this part is challenging)*
-
 ``` {r Noise Effects: tSNR Comparison (Fig.
@@
 This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE, cache = TRUE}
-## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
-# Flexibility vs SNR
-# Are vertices with lower SNR switching communities more often?
-SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))
-
-# Compare SNR between PCC and mPFC per subject
-SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval)
-SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
-SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff))
-prcntSig <- (sum(SNR_PCCvsPFC_perm < 0.05) / nSubj) * 100
-
-# Get the mean SNR for each region and compare overall levels 
-SNR_meanPCC <- sapply(tempComm_PCC, function(data) mean(data$varCoeff))
-SNR_meanPFC <- sapply(tempComm_PFC, function(data) mean(data$varCoeff))
-SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
-                     Comparison = permute(SNR_meanPCC, SNR_meanPFC)$Pval,
-                     ES = cohenD(SNR_meanPCC, SNR_meanPFC))
-rm(SNR_meanPCC, SNR_meanPFC)
-
 # Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
@@
 
-Even though our findings point to a stable representation of each subject's unique DMN organization, it is still possible that they were affected by considerable levels of signal noise often found in mPFC (its ventral segment in particular).
-As a first step to account for this, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
-mean of each vertex's time points over their standard deviation).
-The tSNR of all vertices were averaged per region and subject (Figure 12), which showed that indeed mPFC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`) was overall noisier than PCC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`) across subjects (permutation, *p* = `r SNR_meanComp$Comparison`, Cohen's D = `r round(SNR_meanComp$ES, digits = 2)`).
-To more precisely examine this difference, we performed subject-wise comparisons of the tSNR values of all vertices between PCC and mPFC (total `r nSubj` permutation tests, 5000 iterations each).
-About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected; mean Cohen's D = `r round(mean(SNR_PCCvsPFC_ES), digits = 2)`).
-In addition, we found that the levels of tSNR for each vertex showed significant negative correlations with flexibility, a graph-theoretic index that measures the proportion of times a node in a network changed affiliation across partitions (mean *r* = `r round(mean(SNR_vs_Flex), digits = 2)`).
-These findings indicate that, for any given subject, vertices with low SNR resulted in more variable participation between the communities, and these vertices were more common in mPFC.
-This could explain why mPFC previously showed lower stability levels.
-
-``` {r Noise Effects: Per-subject Fiedler by R-sqd (Fig.
-13), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 13.
-Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
-setwd('./Variance/')
-temp <- list.files()
-Variance <- lapply(temp, read.csv)
-
-### Grab some of the other measures from the overall summary
-for (i in seq(nSubj)) {
-  tempIndex <- Summaries[[i]]$Vertex %in% Variance[[i]]$Vertex
-  Variance[[i]]$SubjID <- rep(subjList[i], nrow(Variance[[i]]))
-  Variance[[i]]$FiedlerVec <- Summaries[[i]]$FiedlerVec[tempIndex]
-  Variance[[i]]$Flexibility <- Summaries[[i]]$slideFlexibility[tempIndex]
-  Variance[[i]]$propDMN <- Summaries[[i]]$slidePropDMN[tempIndex]
-  Variance[[i]]$varCoeff <- Summaries[[i]]$varCoeff[tempIndex]
-  Variance[[i]]$Region <- ifelse(Variance[[i]]$tempY < 0, "PCC", "mPFC")
-}
-
-# let's put everyone's data together first
-allVariance <- do.call(rbind, Variance)
-
-# get the mean and SE of the R-squared values per subject/region
-allVariance_sumarized <- aggregate(allVariance$Rsquared ~ allVariance$SubjID + allVariance$Region, FUN = 'mean')
-colnames(allVariance_sumarized) <- list("SubjID", "Region", "meanRsquared")
-allVariance_sumarized$SEM <- aggregate(allVariance$Rsquared ~ allVariance$SubjID + allVariance$Region, FUN = function(data) {sd(data)/sqrt(length(data))})[ , 3]
-
-# Create a new data frame with values restricted to mPFC (for plotting and further stats)
-mPFCVariance <- allVariance[allVariance$Region == "mPFC", ]
-
-# Get the correlations between Z-axis, R2, and tSNR for every subject (to take mean and SD in text)
-# I just came up with this, so the code should be made more parsimonious in the future (like, why bind and then split...?)
-tempSubj <- split(mPFCVariance, f = mPFCVariance$SubjID)
-# Get the correlation coefficients
-noiseCors <- data.frame(R2vtSNR = sapply(tempSubj, function(data) {cor(data$Rsquared, data$varCoeff)}),
-                        ZvtSNR = sapply(tempSubj, function(data) {cor(data$tempZ, data$varCoeff)}),
-                        ZvR2 = sapply(tempSubj, function(data) {cor(data$tempZ, data$Rsquared)}))
-rm(tempSubj)
-
-# plot
-# There is a strong linear relationship between the Fiedler vector and the R-squared values
-# These match perfectly on the brain when inspected qualitatively
-v1 <- ggplot(data = allVariance) + 
-  geom_smooth(aes(FiedlerVec, Rsquared, group = SubjID), fill = "gray70", color = "gray30", show.legend = F) + 
-  labs(x = "Fiedler Vector Values", y = "R-Squared Values") + 
-  theme_classic()
-
-# The lower the R-squared, the more likely it is for nodes to change affiliation throughout time
-v2 <- qplot(data = allVariance, Rsquared, Flexibility, color = SubjID, fill = SubjID, geom = "smooth") + theme_classic()
-
-# And of course (given the relationship with the Fiedler vector), there's a sigmoidal relationship between R-squared vals and proportion of DMN affiliation
-# only showing the upper side of the sigmoid here, as these values are restricted to the DMN community
-v3 <- qplot(data = allVariance, Rsquared, propDMN, color = SubjID, fill = SubjID, geom = "smooth") + theme_classic()
-
-# Finally, it's worth comparing the R-squared values between PCC and mPFC
-# The intuition is that the variance explained by the community might be lower for mPFC given its noise
-# And the answer is: mPFC yields significantly lower R-squares per subject and overall, as expected.
-# To formally compare this (and given the binomial distribution of R-squares in mPFC), I report the Cohen's D per subject for PCC vs mPFC
-v4 <- ggplot(data = allVariance_sumarized, aes(x = SubjID, y = meanRsquared, group = Region, color = Region)) +
-  geom_point(show.legend = F) +
-  geom_line(show.legend = F) +
-  geom_errorbar(aes(ymin = meanRsquared - SEM, ymax = meanRsquared + SEM)) +
-  scale_color_manual(values = Cols[seq(2)]) +
-  ylim(0,0.5) +
-  labs(x = "Subject", y = "Mean R-squared") +
-  theme_classic() +
-  theme(axis.text.x = element_blank()) 
-v5 <- qplot(data = allVariance, Region, Rsquared, fill = Region, geom = "boxplot") + theme_classic()
-Rsq_PCCvsPFC_Wilcox <- sapply(Variance, function(data) {wilcox.test(data$Rsquared[data$Region == "PCC"], data$Rsquared[data$Region == "mPFC"])$p.value})
-Rsq_PCCvsPFC_Wilcox <- p.adjust(Rsq_PCCvsPFC_Wilcox, method = "BY")
-prcntSig <- (sum(Rsq_PCCvsPFC_Wilcox < 0.05) / nSubj) * 100
-Rsq_PCCvsPFC_ES <- sapply(Variance, function(data) {cohenD(data$Rsquared[data$Region == "PCC"], data$Rsquared[data$Region == "mPFC"])})
-
-# This begs the question of a "gradient of noise" along the z-axis on mPFC
-# Not really, but the coefficient of variation derived from minimally preprocessed data does show a strong trend
-# Namely, the more ventral, the lower the SNR
-# v6 <- ggplot(data = allVariance, aes(Rsquared, tempZ, fill = Region)) +
-#         geom_point(color = "black", pch = 21, alpha = 0.1) + 
-#         scale_fill_manual(values = Cols[seq(2)]) +
-#         theme_classic()
-# v7 <- ggplot(data = allVariance, aes(varCoeff, tempZ, fill = Region)) +
-#         geom_point(color = "black", pch = 21) + 
-#         scale_fill_manual(values = Cols[seq(2)]) +
-#         theme_classic()
-
-#v1
-
-```
-
-``` {r Noise Effects: Mean R-sqd mPFC and PCC, fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 14.
+``` {r Noise Effects: Mean R-sqd mPFC and PCC (Fig.
+13 UPDATE IN TEXT FROM THIS FIG ON), fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 13.
 Differences in mean R-squared values for each region per participant.
@@
 
-To further interrogate the potential effect of noise in our results, we computed the variance explained by activity from each DMN vertex on the mean time series of the DMN community.
-If the signal quality issues persisted after preprocessing the data, we expected that noisy vertices would have the least explicative power on the activity of the DMN community as a whole.
-This also implied lower $R^2$ values for mPFC.
-Indeed, we found that for each subject, $R^2$ values tended to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had *p* values < 0.001; mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`) (Figure 14).
-These results suggest that, overall, vertices in mPFC tended to be less in synchrony with the activity of the DMN community as a whole.
-Furthermore, the degree tSNR showed a moderate correlation with $R^2$ values across participants (mean *r* = `r round(mean(noiseCors$R2vtSNR), digits = 2)`; SD = `r round(sd(noiseCors$R2vtSNR), digits = 2)`), meaning that noisier vertices were less in synchrony with the general activity of the DMN.
-
-Given this trend, we asked whether there is a "gradient of noise" along the z-axis of mPFC, such that more ventral vertices would both be noisier and explain the least amount of DMN variance.
-Here we found that while $R^2$ are somewhat correlated with dorsal-ventral placement across subjects (mean *r* = `r round(mean(noiseCors$ZvR2), digits = 2)`; SD = `r round(sd(noiseCors$ZvR2), digits = 2)`), there is no clear relationship with the z-axis across subjects (Figure 15).
-Specifically, low $R^2$ are evenly distributed along this axis, denoting a degree of orthogonality between these features.
-Conversely, tSNR showed a strong linear relationship with the position of the vertex along this axis (mean *r* = `r round(mean(noiseCors$ZvtSNR), digits = 2)`; SD = `r round(sd(noiseCors$ZvtSNR), digits = 2)`).
-These results contextualize the degree of synchrony of mPFC vertices in terms of potential noise.
-While still an important factor, it is unlikely that the degree of within-subject pattern stability observed here could be due mostly to highly structured mPFC noise.
-
 ``` {r Noise Effects: R-sqd vs tSNR (Fig.
-15), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 15.
+14), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 14.
 Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the lowest tSNR (left).
@@
 
-\bigskip
-
-### *Correlation vs community detection in mPFC*
-
-``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
-## Between halves analysis for correlation and communities (mPFC only)
-tempComm_PFC_halves_plot <- lapply(seq_along(tempComm_PFC_halves_plot), function(x) cbind(tempComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
-D1 <- tempComm_PFC_halves_plot
-D2 <- lapply(tempComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
-Data <- c(D1,D2)
-allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
-```
-
-``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
-# Compare correlation with community approach on mPFC
-# tempComm_PFC_halves <- lapply(seq_along(tempComm_PFC_halves), function(x) cbind(tempComm_PFC_halves[[x]], Correlation_halves[[x]]))
-# tempComm <- sapply(seq(1, 20, by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
-# tempCor <- sapply(seq(1, 20, by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
-# prepostComp <- data.frame(Community = tempComm, Correlation = tempCor)
-# prepostComp <- melt(prepostComp)
-# colnames(prepostComp) <- c("Approach", "Correlation")
-# prepostComp_test <- permute(tempComm, tempCor, paired = T)
-# 
-# 
-# ## Between halves analysis for correlation and communities (mPFC only)
-# D1 <- tempComm_PFC_halves
-# D2 <- lapply(tempComm_PFC_halves, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
-# Data <- c(D1,D2)
-# allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = length(Data), Index = "Cor", subjNames = c(subjList_halves, subjList_halves))
-#
-
-# Compare correlation with community approach on mPFC
-tempComm <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
-tempCor <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
-tempBoth <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
-prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
-prepostComp <- melt(prepostComp)
-colnames(prepostComp) <- c("Approach", "Correlation")
-prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
-prepostComp_ES <- cohenD(tempComm, tempCor)
-```
-
-The computational demands of our approach escalate quickly as the number of vertices increases.
-We thus explored the possible advantage to using graph-theoretic approaches on all possible network connections over a simple seed-based functional connectivity analysis from PCC.
-Given that the spatial distribution of the DMN is considerably stable within individuals [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018], we examined whether maps generated with spectral partitioning were more similar per subject across days than those computed from seed-based correlations.
-First, we computed the mean time series of all the vertices contained in the DMN PCC ROI from Yeo et al.
-(2011) parcellation, and correlated it with the activity of every mPFC vertex from our ROIs.
-We then performed pairwise spatial Pearson correlations among maps computed for each day and method from all subjects (Figure 16).
-
-Figure 17 shows the overall degree of similarity across days for patterns dervied using community detection, seed-based correlation, and across methods (i.e.
-day one community detection versus day two seed-based correlation).
-While both approaches are very consistent, community detection displayed a significantly higher ARI across days than a simple correlation (paired permutation *p* < 0.001; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
-It is worth noting that the cross-method agreement is fair, meaning that both approaches show similar topological features.
-These findings suggest that graph-theoretic community detection algorithms provide a better way to detect stable functional topologies, an important factor when faced with the levels of noise present in mPFC.
-
 ``` {r Correlation vs community detection (Fig.
-16), fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 16.
+15), fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 15.
 Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector (10 example subjects).
@@
 ``` {r Correlation vs community detection: comparison plot (Fig.
-17), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 17.
+16), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 16.
 Day 1 vs Day 2 oefficients of spatial correlations for every method, as well as between methods.
@@
 prepostComp_plot
-```
-
-### *Structural correspondence*
-
-``` {r Structural correspondence, fig.align="center", echo=FALSE, message = FALSE}
-# Mean of correlations
-meanMyelin <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
-meanCurv <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
-meanThick <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
-
-# SD 
-sdMyelin <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
-sdCurv <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
-sdThick <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
-```
-
-Finally, we examined whether these topological features were defined by the structure of the brain by correlating each subject's Fiedler vector with their structural MRI data.
-We found that the Fiedler vector is uncorrelated with myelin density (mean correlation = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean correlation = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean correlation = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`).
-While these results suggest that each subject's functional topology is mostly independent of brain structure, we will perform more detailed analyses of this in the future (i.e.
-are there any outstanding structural features in a subject that match their unique topology?).
-
-## Discussion
-
-For clinical implications, see Hiser & Koenigs 2018.
-In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC.
-It would be more interesting to identify the repercussions to damage in mPFC per individual.
-They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment.
-The refinement of the technique is thus coupled to being able to identify personalized functional topologies.
-They list a number of results related to mPFC functional connectivity too.
-In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse.
-(note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)
-
-It will also be good to note that there is concurrent debate on the ground truth of community detection.
-In other fields, identifying a community structure is not necessarily associated with the true organization of the network.
-What happens is that you might find a tangential grouping that gives you information different from your original goal [@Clauset2004]
-
-Mention the lack of interhemispheric distinction, citing Mackey and Petrides in regards to L-R diffs.
-
-It's also worth mentioning that PCC is largely covered by DMN.
-Then why does this area overlap with SV?
-I think the Mueller paper mentions that PCC is an important hub of the brain, and perhaps subserves many cognitive functions (recent Wash U paper on this too).
-
-And write a portion on the lack of subcortical reward-related regions (i.e.
-striatum).
-Say something like 'incorporating the ventral striatum did notrefine these partitions through either method.
-This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future.
-Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DMN and SV'.
-
-Talk about how there are other community detection algorithms, and that modularity and SP over and underfit, respectively.
-However, SP eigenmaps have been found to provide relevant functional information.
-In addition, both modularity and SP rely on connectivity strength, and thus is amenable to the correlative nature of functional connectivity.
-
-Add a portion showing that summing up the binarized maps produces a map similar to the one produced by Margulies et al. and others.
-
-It might also be worth mentioning that previous work has established the shift in network types during rest through hidden Markov models (Vidaurre et al., 2016?).
-While this suggests that we should see fluctuations in affiliation, and not stability, Vidaurre's work establishes the dynamics of prevalent function among networks, and not their topologies.
-Our work focuses on the topographical arrangement of the DMN network, which can be active or not while maintaining its form.
-So, the two works are compatible.
-Note, I played a bit with AR and MA processes per subject to try to understand the autocorrelation in the sliding window.
-First, both acf/pacf and arima (order = n,0,n) R functions suggested that the data was better fit by AR.
-Moreover, ARs from 1 to 10 had neglegible differences, so I stuck with 1 results for simplicity.
-As expected the data is significantly autocorrelated, and when I checked plotted the residuals they were mostly within the 0.15 bound (normally distributed).
-Coefficients ranged from 0.6 to 1.
-So, there is clear rythmicity in the agreement between each window and the overall pattern.
-However, the intercepts from the ARn processes gave more or less the same estimates as the mean rand index over all the windows.
-This is mostly expected, as we saw that the standard deviation of the rand index was low across participants.
-I am currently interpreting this as a signal that there is clear periodicity that is otherwise harmless for our results: in the end, the agreement remains stable throughout the 4800 TRs.
-
-In terms of noise, there are a handful of things to keep in mind.
-First is that yes, mPFC is noisier overall, but that did not preclude the relatively high levels of agreement across days and sessions per subject, even though ARI heavily penalizes discrepancies (less than linearly).
-Second, low $R^2$ values were found all throughout the z-axis, meaning that variance explained is not strictly determined by the cardinal position of the vertex (and while the correlation was significant due to the sheer number of items, the coefficient was relatively low).
-Right now this might be ok as a way to bypass noise comments, but it would also be interesting to take advantage of the Fiedler vector here.
-Since it's linearly related to $R^2$ per subject, perhaps finding a way to threshold these values would provide cleaner and even more consistent maps.
-
-## Acknowledgements
-
-Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
-
-## Supplemental Materials
-
-### *Table 1. Significant brain regions per literature*
-| Literature                     | Significant Brain Regions      |
-| :----------------------------- | -----------------------------: |
-| Default Mode Network           | `r paste(dmnLbls)`             |
-| Subjective Value               | `r paste(valLbls)`             |
-
+
+```
+
+\newpage
 ## References

### 2018-10-19 Manuscript.Rmd
Many updates, mainly to keep figures at the bottom

@@
 Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+# To get the rate of stability per vertex across subjects
+FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
+FBS <- rowMeans(FB)
+FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]
+
+# Now let's test something: 
+# Traditionally, a vertex-wise test would be carried across subjects.
+# If these traditional analyses miss out on these idiosyncrasies, you should get unsignificant results.
+# So we did a prop.test per vertex, and corrected with FDR to mimic this situation.
+All_proptests <- apply(FB, 1, function(x) {prop.test(sum(x), nSubj)})
+Pvals_corrected <- p.adjust(sapply(All_proptests, "[[", "p.value"), method = "BY")
+Chisquares <- sapply(All_proptests, "[[", "statistic")
 ```
@@
 ``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
-# Select 10 subjects from the sample to display
-selectSubj <- seq(1,20)
-
-# Load
+# Load data
 setwd('./Summary_halves/')
@@
 Summaries_halves <- lapply(temp, read.csv)
+
+# Select subsection of subjects for plotting the similarity matrices
+selectSubj <- seq(1,20)
 Summaries_halves_plot <- Summaries_halves[selectSubj]
@@
 
+# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
 temp <- list.files(pattern = "*_corHalves.csv")
@@
 
-# Compare all halves with RI
-RI_all_between_halves <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-
-# Compare PCC and PFC among all subjects
+# Compare all halves with RI (plot only)
+RI_all_between_halves_plot <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+
+# Compare PCC and PFC among all subjects (plot only)
 tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
 tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
-RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+RI_PFC_halves_plot <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+RI_PCC_halves_plot <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
 ```
@@
 ``` {r Partition comparison: halves ratios, echo=FALSE, message = FALSE, cache = TRUE}
-## Now compare all possible pairs of subjects
+## Now compare all possible pairs of subjects (for actual reporting)
 # Compare all halves with RI
@@
 ``` {r Partition comparison: session similarity matrices, echo=FALSE, message = FALSE, cache = TRUE}
-# Select 10 subjects from the sample to display
-selectSubj <- seq(1,40)
-
+# Load data
 setwd('./Summary_sess/')
@@
 Summaries_sess <- lapply(temp, read.csv)
+
+# Select 10 subjects from the sample to plot
+selectSubj <- seq(1,40)
 subjList_sess_plot <- subjList_sess[selectSubj]
@@
 # Across subjects (just for plotting)
-RI_all_between_sess <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
 tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
 tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
-RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
 ```
@@
 ``` {r Partition comparison: session compare all, echo=FALSE, message = FALSE, cache = TRUE}
-# Now run comparisons among all subjects
+# Now run comparisons among all subjects (for actual reporting)
 RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
@@
 In other fields, identifying a community structure is not necessarily associated with the true organization of the network.
-What happens is that you might find a tangential grouping that gives you information different from your original goal [@Clauset2004]
+What happens is that you might find a tangential grouping that gives you information different from your original goal [@Clauset2004].
+In our case, however, averaging everyone's partitions produces organizational maps that resemble those from previous work (e.g.
+Margulies).
 
@@
 In addition, both modularity and SP rely on connectivity strength, and thus is amenable to the correlative nature of functional connectivity.
-
-Add a portion showing that summing up the binarized maps produces a map similar to the one produced by Margulies et al. and others.
 
@@
 Since it's linearly related to $R^2$ per subject, perhaps finding a way to threshold these values would provide cleaner and even more consistent maps.
+
+So what's the advantage of this work over previous ones?
+Gratton, Gordon, and Kong have already found some degree of subject stability and intersubject variability.
+Ours complements these findings by looking at the vertex level, not just mean parcel activity (this made sense for them, as they were looking at the whole brain).
+Also, most of these analyses rely on a small set of oversampled subjects (i.e.
+MSC).
+Here we extend this to 100, giving credit to individualize examinations even without oversampling.
 
@@
 par(mfrow=c(1,2))
-corrplot(RI_all_between_halves, 
+corrplot(RI_all_between_halves_plot, 
          is.corr = F, 
@@
 mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
-corrplot(RI_PCC_halves, 
+corrplot(RI_PCC_halves_plot, 
          is.corr = F,     
@@
          cl.length = 3)
-corrplot(RI_PFC_halves, 
+corrplot(RI_PFC_halves_plot, 
          is.corr = F, 
@@
 par(mfrow=c(1,2))
-corrplot(RI_all_between_sess, 
+corrplot(RI_all_between_sess_plot, 
          is.corr = F, 
@@
 mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
-corrplot(RI_PCC_sess, 
+corrplot(RI_PCC_sess_plot, 
          is.corr = F, 
@@
 # segments(20.5,0.5,20.5,20.5, lwd = 2)
-corrplot(RI_PFC_sess, 
+corrplot(RI_PFC_sess_plot, 
          is.corr = F, 

### 2018-11-26 view.sh
Cleaning up files, and updating notes on coord -> parcellation transformation script

@@ -1,0 +1,4 @@
+#!/bin/bash
+
+freeview -f $SUBJECTS_DIR/fsaverage/surf/lh.inflated:annot=lh.HCP_MMP1p0.annot:overlay=DECvsDMN_lh_overlay.gii:overlay=DECvsNEG_lh_overlay.gii:overlay=DECvsPOS_lh_overlay.gii:overlay=DMNvsNEG_lh_overlay.gii:overlay=DMNvsPOS_lh_overlay.gii:overlay=NEGvsPOS_lh_overlay.gii \
+            $SUBJECTS_DIR/fsaverage/surf/rh.inflated:annot=rh.HCP_MMP1p0.annot:overlay=DECvsDMN_rh_overlay.gii:overlay=DECvsNEG_rh_overlay.gii:overlay=DECvsPOS_rh_overlay.gii:overlay=DMNvsNEG_rh_overlay.gii:overlay=DMNvsPOS_rh_overlay.gii:overlay=NEGvsPOS_rh_overlay.gii

### 2018-11-26 batch_makeIM.sh
Cleaning up files, and updating notes on coord -> parcellation transformation script

@@ -24,7 +24,7 @@ export filename
 echo $filename
 
 
-# create dirs, including those to make FS commands compatible
+# create dirs, including those to make FreeSurfer commands compatible
 # important for step 7 and annot2label transformation
 mkdir -p $PWD/$filename/results
 mkdir -p $PWD/Glasser/surf
@@ -60,8 +60,8 @@ else
 fi
 
 # parameters
-sphereSze=10 ;
-labelThresh=1; # too small at 10, maybe use SD of all sizes.
+sphereSze=10 ; # size of the sphere to be projected to the cortical surface
+labelThresh=1; # Minimum n of vertices needed to map single coordinate spheres to a Glasser parcel (previously 10, but decided to avoid this threshold)
 printf "%s," Study Vertices_count | awk '{print $0}' >> noMatch.csv
 
 # index so that the MNI atlas is only multiplied by 0 once
@@ -76,24 +76,24 @@ for coordFile in coords*.txt ; do
 
     ## 1. generate an MNI template with the coordinate points
     if [ ! -f ${fname}_Points.nii.gz ] ; then
-      	while IFS=$'\t' read -r -a coords ; do
-	    num1=$(printf "%.0f" "${coords[0]}")
-	    num2=$(printf "%.0f" "${coords[1]}")
-	    num3=$(printf "%.0f" "${coords[2]}")
-	    # sanity check
-	    echo $num1
+		# get the first set of coordinates, each num = (x,y,z)
+		while IFS=$'\t' read -r -a coords ; do
+			num1=$(printf "%.0f" "${coords[0]}")
+			num2=$(printf "%.0f" "${coords[1]}")
+			num3=$(printf "%.0f" "${coords[2]}")
+			# sanity check
+			echo $num1
       	    echo $num2
       	    echo $num3
-            # create points
+            # create points using AFNI
+			# MNI template is first multiplied by 0 to ensure that only the relevant coordinates are present 
       	    if [ $startIndex = 0 ] ; then
             	echo
             	echo "Setting coordinate foci..."
-       		echo
-            	3dcalc -LPI -a MNI152_T1_1mm_brain.nii.gz -prefix points.nii.gz \
-            		-expr "a*0 + (equals(x,$num1)*equals(y,$num2)*equals(z,$num3))"
+       			echo
[…]

### 2018-11-26 batch_makeIM.sh
Made the coord -> glasser process more clear in script

@@ -116,7 +116,7 @@ for coordFile in coords*.txt ; do
       	echo
     fi
 
-    ## 3. volumetric to cortical surface conversion
+    ## 3. volumetric to cortical surface conversion using white matter folding
     ## surface templates in $FREESURFER_HOME/subjects/fsaverage/surf/
     ## note: appending "--nvox ${fname}_nvox.csv --srchit ${fname}_vox.nii.gz" gives num of surviving converted voxels (not specific to mask though)
     if [ ! -f ${fname}_lh.gii ] ; then
@@ -131,8 +131,9 @@ for coordFile in coords*.txt ; do
       	echo
     fi
 
-    ## 4. extracting vector of binaries for all vertices
+    ## 4. extracting boolean vector (is vertex in sphere, yes/no?) for all vertices to match with Glasser parcels
     ## wb_command properly transforms data into ASCII, so don't use FS, AFNI, or FSL for this
+	## personal note: potentially no need to use xmllint if wb_command -gifti-convert is used instead
     if [ ! -f ${fname}_lh_binaries.csv ] ; then
       	echo
       	echo "Converting GIFTI into ASCII for binary extraction..."
@@ -141,7 +142,7 @@ for coordFile in coords*.txt ; do
       	wb_command -gifti-convert ASCII ${fname}_rh.gii ${fname}_rh_binaries
       	echo "cat //GIFTI/DataArray/Data" | xmllint --shell ${fname}_lh_binaries | sed '/^\/ >/d' | sed 's/<[^>]*.//g' >> ${fname}_lh_binaries.csv
       	echo "cat //GIFTI/DataArray/Data" | xmllint --shell ${fname}_rh_binaries | sed '/^\/ >/d' | sed 's/<[^>]*.//g' >> ${fname}_rh_binaries.csv
-	sed -i 1d ${fname}_lh_binaries.csv
+		sed -i 1d ${fname}_lh_binaries.csv
       	sed -i 1d ${fname}_rh_binaries.csv
     else
       	echo
@@ -149,7 +150,7 @@ for coordFile in coords*.txt ; do
       	echo
     fi
 
-    ## 5. match binaries to labels and create parcel list
+    ## 5. match boolean vector to labels and create parcel list
     if [ ! -f ${fname}_matchLabels.csv ] ; then
       	echo
       	echo "Matching mask vertices to labels..."
[…]

### 2018-12-03 Manuscript.Rmd
Added note on the usefulness of the sliding window analysis
Temp visualizations comparing FValues across communities per subject

@@
 
+  # NOTES:
+  # you can apply pairwise comparisons with outer: outer(tempList,tempList,FUN = Vectorize(arandi, SIMPLIFY = FALSE, USE.NAMES = FALSE))
+
   # Get the column position of the MOI(s)
@@
 FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
+FV <- do.call(cbind, lapply(Summaries, "[[", "FiedlerVec"))
 FBS <- rowMeans(FB)
@@
 All_proptests <- apply(FB, 1, function(x) {prop.test(sum(x), nSubj)})
-Pvals_corrected <- p.adjust(sapply(All_proptests, "[[", "p.value"), method = "BY")
+Prop_pvals_corrected <- p.adjust(sapply(All_proptests, "[[", "p.value"), method = "BY")
+Prop_pvals_corrected <- ifelse(Prop_pvals_corrected < 0.05, 1, 0)
 Chisquares <- sapply(All_proptests, "[[", "statistic")
+
+# And a t-test on the FV vals
+All_ttests <- apply(FV, 1, t.test)
+Ttest_pvals_corrected <- p.adjust(sapply(All_ttests, "[[", "p.value"), method = "BY")
+Ttest_pvals_corrected <- ifelse(Ttest_pvals_corrected < 0.05, 1, 0)
+Tstats <- sapply(All_ttests, "[[", "statistic")
+
+### Testing grounds
+# this part compares the distribution of Fiedler values for DMN and nonDMN
+# note: remove filter(y > 0) for 'full brain'
+# First plot compares the median FV between communities across subjects
+test <- do.call(rbind, Summaries)
+test %>%
+  mutate(SubjID = rep(subjList, each = 5081),
+         FV_abs = abs(FiedlerVec),
+         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
+  filter(y > 0) %>%
+  group_by(SubjID, Community) %>%
+  summarize(FV_mean = median(FV_abs)) %>%
+  ggplot(aes(Community, FV_mean)) +
+  geom_boxplot() + 
+  theme_classic()
+# Second one plots the ecdf
+# Line indicates the 75th quantile of the combined Fiedler vectors across participants (i.e. potential threshold)
+test %>%
+  mutate(SubjID = rep(subjList, each = nrow(Summaries[[1]])),
+         FV_abs = abs(FiedlerVec),
+         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
+  filter(y > 0) %>%
+  ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
+  stat_ecdf() +
+  geom_vline(xintercept = 0.009, lty = 2) +
+  theme_classic()
 ```
@@
 Here we extend this to 100, giving credit to individualize examinations even without oversampling.
+
+Make sure to emphasize that the high overlap between sliding windows makes it more likely that differences are due to noise in the signal, and not strong variability.
+Like, you wouldn't expect the actual network distribution to shift that much after shifting the time series by 1 minute.g
 

### 2018-12-05 Manuscript.Rmd
Working on a contrast permutation

@@
       tempBig <- sample(bigSample)
-      tempOne <- tempBig[1:lOne]
-      tempTwo <- tempBig[(lOne+1):length(bigSample)]
+      tempOne <- tempBig[seq(lOne)]
+      tempTwo <- tempBig[-seq(lOne)]
 
@@
 
+``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
+# Based on Yeo et al. 17 network parcellation
+# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
+Yeo_labels <- c("_25_",
+                "_OFC_",
+                "_10v_",
+                "_s32_",
+                "_TE1a_",
+                "_STSva_",
+                "_8ad_",
+                "_9p_",
+                "_23d_",
+                "_d23ab_",
+                "_31a_",
+                "_31pv_",
+                "_31pd_",
+                "_7m_",
+                "_v23ab_",
+                "_p24_",
+                "_d32_",
+                "_9m_",
+                "_p32_",
+                "_a24_",
+                "_s32_",
+                "_10r_",
+                "_10d_",
+                "_9a_",
+                "_p10p_",
+                "_PCV_",
+                "_POS1_",
+                "_RSC_")
+
+Yeo_PCC_labels <- c("_7m_",
+                    "_23d_",
+                    "_31a_",
+                    "_31pd_",
+                    "_31pv_",
+                    "_PCV_",
+                    "_POS1_",
+                    "_RSC_",
+                    "_d23ab_",
+                    "_v23ab_")
+
+mPFC_only <- c("_a24_",
+               "_d32_",
+               "_p32_",
+               "_10r_",
+               "_9m_",
+               "_10v_",
+               "_OFC_",
+               "_s32_",
+               "_p24_")
+
+# Permutation analysis
+# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
+# Load the coordinates as studies in a list, because for the contrast the studies are permuted
+# Use table(unlist(list)) to get the counts in that case
+setwd('./DEC')
+templist <- dir()
+studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
+
+setwd('../DMN/')
+templist <- dir()
+studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
+
+# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
+allStudies <- c(studyList_sv, studyList_dmn)
+nPerms <- 10
+nullDist <- numeric()
+
+for (i in seq(nPerms)) {
+
+  # Sample all the studies and divide into 2 groups
+  randPerm <- sample(allStudies)
+  tmpSV <- randPerm[seq(length(studyList_sv))]
+  tmpDMN <- randPerm[-seq(length(studyList_sv))]
+
+  # Count the number of times each region was reported in the literature
+  # Bilateral activations still count as 1, so we might want to reconsider that
+  tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+                      SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
+                      DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
+
+  # Perform the prop test for each pair and get the max chi-squared stat
+  nullDist[i] <- max(
+                  apply(tmpDF[,2:3], 1, function(data) {
+                    prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
+                    }
+                  ), na.rm = T)
+
+}
+```
+
 ``` {r ROI computation, echo=FALSE, message = FALSE}
+# Based on Yeo et al. 17 network parcellation
+# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
+Yeo_labels <- c("_25_",
+                "_OFC_",
+                "_10v_",
+                "_s32_",
+                "_TE1a_",
+                "_STSva_",
+                "_8ad_",
+                "_9p_",
+                "_23d_",
+                "_d23ab_",
+                "_31a_",
+                "_31pv_",
+                "_31pd_",
+                "_7m_",
+                "_v23ab_",
+                "_p24_",
+                "_d32_",
+                "_9m_",
+                "_p32_",
+                "_a24_",
+                "_s32_",
+                "_10r_",
+                "_10d_",
+                "_9a_",
+                "_p10p_",
+                "_PCV_",
+                "_POS1_",
+                "_RSC_")
+
+Yeo_PCC_labels <- c("_7m_",
+                    "_23d_",
+                    "_31a_",
+                    "_31pd_",
+                    "_31pv_",
+                    "_PCV_",
+                    "_POS1_",
+                    "_RSC_",
+                    "_d23ab_",
+                    "_v23ab_")
+
+mPFC_only <- c("_a24_",
+               "_d32_",
+               "_p32_",
+               "_10r_",
+               "_9m_",
+               "_10v_",
+               "_OFC_",
+               "_s32_",
+               "_p24_")
 
@@
 dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
+
+# Now select only the ROIs from Yeo et al (TEMP)
+valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
+dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
 

### 2018-12-05 Manuscript.Rmd
Replicated the permutation analysis from Matlab in R, with one caveat (see comments under 'Meta-analysis')

@@
 # These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
-Yeo_labels <- c("_25_",
-                "_OFC_",
-                "_10v_",
-                "_s32_",
-                "_TE1a_",
-                "_STSva_",
-                "_8ad_",
-                "_9p_",
-                "_23d_",
-                "_d23ab_",
-                "_31a_",
-                "_31pv_",
-                "_31pd_",
-                "_7m_",
-                "_v23ab_",
-                "_p24_",
-                "_d32_",
-                "_9m_",
-                "_p32_",
-                "_a24_",
-                "_s32_",
-                "_10r_",
-                "_10d_",
-                "_9a_",
-                "_p10p_",
-                "_PCV_",
-                "_POS1_",
-                "_RSC_")
+Yeo_labels <- c("L_25_",
+                "L_OFC_",
+                "L_10v_",
+                "L_s32_",
+                "L_TE1a_",
+                "L_STSva_",
+                "L_8ad_",
+                "L_9p_",
+                "L_23d_",
+                "L_d23ab_",
+                "L_31a_",
+                "L_31pv_",
+                "L_31pd_",
+                "L_7m_",
+                "L_v23ab_",
+                "L_p24_",
+                "L_d32_",
+                "L_9m_",
+                "L_p32_",
+                "L_a24_",
+                "L_10r_",
+                "L_10d_",
+                "L_9a_",
+                "L_p10p_",
+                "L_PCV_",
+                "L_POS1_",
+                "L_RSC_",
+                "L_25_",
+                "R_OFC_",
+                "R_10v_",
+                "R_s32_",
+                "R_TE1a_",
+                "R_STSva_",
+                "R_8ad_",
+                "R_9p_",
+                "R_23d_",
+                "R_d23ab_",
+                "R_31a_",
+                "R_31pv_",
+                "R_31pd_",
+                "R_7m_",
+                "R_v23ab_",
+                "R_p24_",
+                "R_d32_",
+                "R_9m_",
+                "R_p32_",
+                "R_a24_",
+                "R_10r_",
+                "R_10d_",
+                "R_9a_",
+                "R_p10p_",
+                "R_PCV_",
+                "R_POS1_",
+                "R_RSC_")
 
@@
 
+# This version is literally what I had selected originally, plus 25, OFC, 10v. This replicates the 7m finding. 
+# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
+Yeo_labels <- c("L_25_",
+                "L_OFC_",
+                "L_10v_",
+                "R_PGi_ROI",
+                "R_PGs_ROI",
+                "R_8Ad_ROI",
+                "R_9p_ROI",
+                "R_23d_ROI",
+                "R_d23ab_RO",
+                "R_31a_ROI",
+                "R_31pv_ROI",
+                "R_31pd_ROI",
+                "R_7m_ROI",
+                "R_v23ab_RO",
+                "R_p24_ROI",
+                "R_d32_ROI",
+                "R_9m_ROI",
+                "R_p32_ROI",
+                "R_a24_ROI",
+                "R_10r_ROI",
+                "R_10d_ROI",
+                "L_PGi_ROI",
+                "L_PGs_ROI",
+                "L_8Ad_ROI",
+                "L_9p_ROI",
+                "L_23d_ROI",
+                "L_d23ab_RO",
+                "L_31a_ROI",
+                "L_31pv_ROI",
+                "L_31pd_ROI",
+                "L_7m_ROI",
+                "L_v23ab_RO",
+                "L_p24_ROI",
+                "L_d32_ROI",
+                "L_9m_ROI",
+                "L_p32_ROI",
+                "L_a24_ROI",
+                "L_10r_ROI",
+                "L_10d_ROI",
+                "R_TE1a_ROI",
+                "R_STSva_RO",
+                "R_s32_ROI",
+                "R_9a_ROI",
+                "L_p10p_ROI",
+                "L_PCV_ROI")
+
 # Permutation analysis
@@
 allStudies <- c(studyList_sv, studyList_dmn)
-nPerms <- 10
+nPerms <- 100
 nullDist <- numeric()
@@
 for (i in seq(nPerms)) {
+
+  if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
 
@@
 }
+
+# Now do the same for the actual data, to see how it compares to the null dist
+tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+                    SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
+                    DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
+                    propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
+                    propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
+
+# Perform the prop test for each pair and get the max chi-squared stat
+tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)})
+
+plot(density(nullDist))
+
+quantile(nullDist, 0.95)
+
+tmpDF %>% filter(Chi_squared > quantile(nullDist,0.95))
 ```

### 2018-12-06 Manuscript.Rmd
Saving the new search space criteria and updated the labels within the manuscript for the meta-analysis

@@
 
-# This version is literally what I had selected originally, plus 25, OFC, 10v. This replicates the 7m finding. 
+# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
+# Minus PGi and PGs. This replicates the 7m finding. 
 # But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
-Yeo_labels <- c("L_25_",
-                "L_OFC_",
-                "L_10v_",
-                "R_PGi_ROI",
-                "R_PGs_ROI",
+Yeo_labels <- c("L_25_ROI",
+                "L_OFC_ROI",
+                "L_10v_ROI",
+                "R_25_ROI",
+                "R_OFC_ROI",
+                "R_10v_ROI",
+                "L_s32_ROI",
+                "L_RSC_ROI",
+                "R_RSC_ROI",
                 "R_8Ad_ROI",
@@
                 "R_23d_ROI",
-                "R_d23ab_RO",
+                "R_d23ab_ROI",
                 "R_31a_ROI",
@@
                 "R_7m_ROI",
-                "R_v23ab_RO",
+                "R_v23ab_ROI",
                 "R_p24_ROI",
@@
                 "R_10d_ROI",
-                "L_PGi_ROI",
-                "L_PGs_ROI",
                 "L_8Ad_ROI",
@@
                 "L_7m_ROI",
-                "L_v23ab_RO",
+                "L_v23ab_ROI",
                 "L_p24_ROI",
@@
                 "L_10d_ROI",
-                "R_TE1a_ROI",
-                "R_STSva_RO",
                 "R_s32_ROI",
@@
 allStudies <- c(studyList_sv, studyList_dmn)
-nPerms <- 100
+nPerms <- 5000
 nullDist <- numeric()

### 2018-12-06 graphAnalysis_solo.R
community detection is now based on the Yeo parcels, after replication of meta-analysis results

@@ -1023,7 +1023,7 @@ Cols <- c("DMN" = "aquamarine4","Valuation" = "#D9541A",rgb(190,190,190,100, max
 # Label groups for specific analyses (DMN and DEC)
 # These come from an arbitrary division based on where Mackey & Petrides (2014) draw their line
 # This is computed below, but if we want to save time it can be loaded instead.
-bothLbls <- as.character(read.table('bothLbls.csv', header = F)$V2)
+#bothLbls <- as.character(read.table('bothLbls.csv', header = F)$V2)
 
 vmPFC_labels <- c("_10pp_",
                   "_10r_",
@@ -1036,32 +1036,51 @@ vmPFC_labels <- c("_10pp_",
                   "_s32_")
 
 # Based on Yeo et al.
-Yeo_labels <- c("_PG1_",
-                "_PGs_",
-                "_TE1a_",
-                "_STSva_",
-                "_8ad_",
-                "_9p_",
-                "_23d_",
-                "_d23ab_",
-                "_31a_",
-                "_31pv_",
-                "_31pd_",
-                "_7m_",
-                "_v23ab_",
-                "_p24_",
-                "_d32_",
-                "_9m_",
-                "_p32_",
-                "_a24_",
-                "_s32_",
-                "_10r_",
-                "_10d_",
-                "_9a_",
-                "_p10p_",
-                "_PCV_",
-                "_POS1_",
-                "_RSC_")
+bothLbls <- c("L_25_ROI",
+              "L_OFC_ROI",
+              "L_10v_ROI",
+              "R_25_ROI",
+              "R_OFC_ROI",
+              "R_10v_ROI",
+              "L_s32_ROI",
+              "L_RSC_ROI",
+              "R_RSC_ROI",
+              "R_8Ad_ROI",
+              "R_9p_ROI",
+              "R_23d_ROI",
+              "R_d23ab_ROI",
+              "R_31a_ROI",
+              "R_31pv_ROI",
+              "R_31pd_ROI",
+              "R_7m_ROI",
+              "R_v23ab_ROI",
+              "R_p24_ROI",
+              "R_d32_ROI",
+              "R_9m_ROI",
+              "R_p32_ROI",
+              "R_a24_ROI",
+              "R_10r_ROI",
+              "R_10d_ROI",
+              "L_8Ad_ROI",
[…]

### 2018-12-06 Manuscript.Rmd
Stored the permutation results, now with pvalues relative to null dist in manuscript

@@
 ``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
-# Based on Yeo et al. 17 network parcellation
-# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
-Yeo_labels <- c("L_25_",
-                "L_OFC_",
-                "L_10v_",
-                "L_s32_",
-                "L_TE1a_",
-                "L_STSva_",
-                "L_8ad_",
-                "L_9p_",
-                "L_23d_",
-                "L_d23ab_",
-                "L_31a_",
-                "L_31pv_",
-                "L_31pd_",
-                "L_7m_",
-                "L_v23ab_",
-                "L_p24_",
-                "L_d32_",
-                "L_9m_",
-                "L_p32_",
-                "L_a24_",
-                "L_10r_",
-                "L_10d_",
-                "L_9a_",
-                "L_p10p_",
-                "L_PCV_",
-                "L_POS1_",
-                "L_RSC_",
-                "L_25_",
-                "R_OFC_",
-                "R_10v_",
-                "R_s32_",
-                "R_TE1a_",
-                "R_STSva_",
-                "R_8ad_",
-                "R_9p_",
-                "R_23d_",
-                "R_d23ab_",
-                "R_31a_",
-                "R_31pv_",
-                "R_31pd_",
-                "R_7m_",
-                "R_v23ab_",
-                "R_p24_",
-                "R_d32_",
-                "R_9m_",
-                "R_p32_",
-                "R_a24_",
-                "R_10r_",
-                "R_10d_",
-                "R_9a_",
-                "R_p10p_",
-                "R_PCV_",
-                "R_POS1_",
-                "R_RSC_")
-
-Yeo_PCC_labels <- c("_7m_",
-                    "_23d_",
-                    "_31a_",
-                    "_31pd_",
-                    "_31pv_",
-                    "_PCV_",
-                    "_POS1_",
-                    "_RSC_",
-                    "_d23ab_",
-                    "_v23ab_")
-
-mPFC_only <- c("_a24_",
-               "_d32_",
-               "_p32_",
-               "_10r_",
-               "_9m_",
-               "_10v_",
-               "_OFC_",
-               "_s32_",
-               "_p24_")
-
 # This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
@@
 
-# Permutation analysis
-# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
-# Load the coordinates as studies in a list, because for the contrast the studies are permuted
-# Use table(unlist(list)) to get the counts in that case
-setwd('./DEC')
-templist <- dir()
-studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
-
-setwd('../DMN/')
-templist <- dir()
-studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
-
-# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
-allStudies <- c(studyList_sv, studyList_dmn)
-nPerms <- 5000
-nullDist <- numeric()
-
-for (i in seq(nPerms)) {
-
-  if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
-
-  # Sample all the studies and divide into 2 groups
-  randPerm <- sample(allStudies)
-  tmpSV <- randPerm[seq(length(studyList_sv))]
-  tmpDMN <- randPerm[-seq(length(studyList_sv))]
-
-  # Count the number of times each region was reported in the literature
-  # Bilateral activations still count as 1, so we might want to reconsider that
-  tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-                      SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
-                      DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
-
-  # Perform the prop test for each pair and get the max chi-squared stat
-  nullDist[i] <- max(
-                  apply(tmpDF[,2:3], 1, function(data) {
-                    prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
-                    }
-                  ), na.rm = T)
-
-}
-
-# Now do the same for the actual data, to see how it compares to the null dist
-tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-                    SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
-                    DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
-                    propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
-                    propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
-
-# Perform the prop test for each pair and get the max chi-squared stat
-tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)})
-
-plot(density(nullDist))
-
-quantile(nullDist, 0.95)
-
-tmpDF %>% filter(Chi_squared > quantile(nullDist,0.95))
-```
-
-``` {r ROI computation, echo=FALSE, message = FALSE}
-# Based on Yeo et al. 17 network parcellation
-# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
-Yeo_labels <- c("_25_",
-                "_OFC_",
-                "_10v_",
-                "_s32_",
-                "_TE1a_",
-                "_STSva_",
-                "_8ad_",
-                "_9p_",
-                "_23d_",
-                "_d23ab_",
-                "_31a_",
-                "_31pv_",
-                "_31pd_",
-                "_7m_",
-                "_v23ab_",
-                "_p24_",
-                "_d32_",
-                "_9m_",
-                "_p32_",
-                "_a24_",
-                "_s32_",
-                "_10r_",
-                "_10d_",
-                "_9a_",
-                "_p10p_",
-                "_PCV_",
-                "_POS1_",
-                "_RSC_")
-
 Yeo_PCC_labels <- c("_7m_",
@@
 
+# Permutation analysis
+# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
+# Load the coordinates as studies in a list, because for the contrast the studies are permuted
+# Use table(unlist(list)) to get the counts in that case
+setwd('./DEC')
+templist <- dir()
+studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
+
+setwd('../DMN/')
+templist <- dir()
+studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
+
+# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
+allStudies <- c(studyList_sv, studyList_dmn)
+nPerms <- 5000
+nullDist <- numeric()
+
+for (i in seq(nPerms)) {
+
+  if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
+
+  # Sample all the studies and divide into 2 groups
+  randPerm <- sample(allStudies)
+  tmpSV <- randPerm[seq(length(studyList_sv))]
+  tmpDMN <- randPerm[-seq(length(studyList_sv))]
+
+  # Count the number of times each region was reported in the literature
+  # Bilateral activations still count as 1, so we might want to reconsider that
+  tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+                      SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
+                      DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
+
+  # Perform the prop test for each pair and get the max chi-squared stat
+  nullDist[i] <- max(
+                  apply(tmpDF[,2:3], 1, function(data) {
+                    prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
+                    }
+                  ), na.rm = T)
+
+}
+
+# Now do the same for the actual data, to see how it compares to the null dist
+tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+                    SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
+                    DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
+                    propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
+                    propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
+
+# Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
+tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
+  round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
+  })
+tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
+
+# ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
+significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))
+
+```
+
+``` {r ROI computation, echo=FALSE, message = FALSE}
+#TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
 ## ROI definition
@@
 
-# Now select only the ROIs from Yeo et al (TEMP)
-valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
-dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
-
-# Then, get the means of the counts per domain
+# Then, get the means of the counts per domain, both within/outside the search space
+# This is to get a broad estimate of the average report amounts in the literature
 tempBoot <- bootstrap(valCounts$Counts)
@@
 
+# Now select only the ROIs from Yeo et al (TEMP)
+valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
+dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
+
 # Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
@@
 valLbls <- gsub("_","", valLbls)
+
+# final overlap
+bothLbls <- dmnLbls[dmnLbls %in% valLbls]
 

### 2018-12-06 graphAnalysis_solo.R
community detection now only relies on bothLbls, as 7m was already contained within the Yeo space

@@ -829,7 +829,7 @@ flexibility <- function(Data = cbind(1:10, 6:15)) {
 
 
 # Sliding window
-slidingWindow <- function(subjTS = ROI_timeSeries[[1]], mins = 15, jump = 1, Spectral = T, Modularity = F, ROIs = c("_7m_", vmPFC_labels)) {
+slidingWindow <- function(subjTS = ROI_timeSeries[[1]], mins = 15, jump = 1, Spectral = T, Modularity = F, ROIs = c(vmPFC_labels)) {
   # This is a fairly specific function. It takes the time series from a participant and preps/runs community detection at each specified time window. 
   # Returns the summaries for each window (based on communityDetection function)
   # The selection of a window size is based on the fact that a TR = 0.720s and an hour is 5000 TRs (HCP-based)
@@ -1154,13 +1154,13 @@ thicknessData <- read.csv(paste(SubjID,'_thickness.txt', sep=""), header = F)
 thicknessData$Label <- labelCoords_vertex$Label
 
 # Get myelin density for ROIs
-myelinROI <- getCoords(Labels = c("_7m_", bothLbls), Coords = myelinData, TimeSeries = F)$Coords
+myelinROI <- getCoords(Labels = c(bothLbls), Coords = myelinData, TimeSeries = F)$Coords
 
 # Get curvature for ROIs
-curvatureROI <- getCoords(Labels = c("_7m_", bothLbls), Coords = curvatureData, TimeSeries = F)$Coords
+curvatureROI <- getCoords(Labels = c(bothLbls), Coords = curvatureData, TimeSeries = F)$Coords
 
 # Get thickness for ROIs
-thicknessROI <- getCoords(Labels = c("_7m_", bothLbls), Coords = thicknessData, TimeSeries = F)$Coords
+thicknessROI <- getCoords(Labels = c(bothLbls), Coords = thicknessData, TimeSeries = F)$Coords
 
 ###------- Meta-analysis: Load ---------------
 if (Meta == T) {
@@ -1516,7 +1516,7 @@ if (Parcellated == T) {
   write("Computing community detection for the parcellated brain...", stdout())
   
   # Modularity
-  parcelCommunities <- mclapply(ptSeries, communityDetection, ROIS = c("_7m_", bothLbls), Type = "parcels", thresh = T)
[…]

### 2018-12-06 graphAnalysis_solo.R
little hiccup: c(bothLbls) -> bothLbls

@@ -1154,13 +1154,13 @@ thicknessData <- read.csv(paste(SubjID,'_thickness.txt', sep=""), header = F)
 thicknessData$Label <- labelCoords_vertex$Label
 
 # Get myelin density for ROIs
-myelinROI <- getCoords(Labels = c(bothLbls), Coords = myelinData, TimeSeries = F)$Coords
+myelinROI <- getCoords(Labels = bothLbls, Coords = myelinData, TimeSeries = F)$Coords
 
 # Get curvature for ROIs
-curvatureROI <- getCoords(Labels = c(bothLbls), Coords = curvatureData, TimeSeries = F)$Coords
+curvatureROI <- getCoords(Labels = bothLbls, Coords = curvatureData, TimeSeries = F)$Coords
 
 # Get thickness for ROIs
-thicknessROI <- getCoords(Labels = c(bothLbls), Coords = thicknessData, TimeSeries = F)$Coords
+thicknessROI <- getCoords(Labels = bothLbls, Coords = thicknessData, TimeSeries = F)$Coords
 
 ###------- Meta-analysis: Load ---------------
 if (Meta == T) {
@@ -1516,7 +1516,7 @@ if (Parcellated == T) {
   write("Computing community detection for the parcellated brain...", stdout())
   
   # Modularity
-  parcelCommunities <- mclapply(ptSeries, communityDetection, ROIS = c(bothLbls), Type = "parcels", thresh = T)
+  parcelCommunities <- mclapply(ptSeries, communityDetection, ROIS = bothLbls, Type = "parcels", thresh = T)
   
   # Spectral
   tempEigen <- mclapply(parcelCommunities, eigenVals)
@@ -1550,7 +1550,7 @@ if (Vertex) {
   write("Computing community detection for the ROI vertices...", stdout())
   
   # Modularity
-  dmnval7mCommunities <- communityDetection(Data = timeSeries, ROIS = c(bothLbls), Type = "vertex", thresh = T)
+  dmnval7mCommunities <- communityDetection(Data = timeSeries, ROIS = bothLbls, Type = "vertex", thresh = T)
   
   # Spectral
   tempEigen <- eigenVals(dmnval7mCommunities)
@@ -1609,7 +1609,7 @@ if (Vertex) {
   
   ## Raw mPFC and PCC SNR
   # Reduce the 4 SNR-dedicated tseries to the ROIs
[…]

### 2018-12-06 Manuscript.Rmd
Added a notes section to aid the restructuring of the paper, and removed the meta-analysis from the community detection script (unneeded)

@@
 
+## Ideas to do
+
+- The new manuscript organization could go like this: 
+1) Meta-analysis and ROIs
+2) Summary all
+  a) Make sure to report mean density and algebraic connectivity
+  b) Cross-method agreement
+  c) Spatially averaged community maps reproduce group-level analysis
+3) Sliding window
+  a) Fiedler vector magnitude as a proxy for affiliation strength
+  b) Proportion DMN for mPFC and PCC separately to denote overall stability
+  b) Proportion DMN across time-series ~ fiedler vector value (consider renaming propDMN to stability)
+4) Threshold the maps and rerun summary all
+5) Day 1 vs day 2
+6) Session
+7) Potential noise
+8) Structural correspondence
+9) Community > correlation
+
 ## Abstract
@@
 Make sure to emphasize that the high overlap between sliding windows makes it more likely that differences are due to noise in the signal, and not strong variability.
-Like, you wouldn't expect the actual network distribution to shift that much after shifting the time series by 1 minute.g
+Like, you wouldn't expect the actual network distribution to shift that much after shifting the time series by 1 minute.
 

### 2018-12-06 graphAnalysis_solo.R
Added a notes section to aid the restructuring of the paper, and removed the meta-analysis from the community detection script (unneeded)

@@ -2,7 +2,7 @@
 SubjID <- commandArgs(trailingOnly=TRUE)
 write(paste("Analyzing data for subject", SubjID), stdout())
 
-### Run a meta-analysis and graph theoretic fMRI analysis
+### Run a graph theoretic fMRI analysis
 
 ###------- Libraries and functions ---------------
 write('Loading functions and libraries...', stdout())
@@ -654,7 +654,7 @@ getCoords <- function(Labels = DMN_labels, Coords = labelCoords_parcel, TimeSeri
 
 
 # eigen value community detection
-eigenVals <- function(Data = binnedCommunities_p$First) {
+eigenVals <- function(Data) {
   
   # This will produce a vector of values, ready to be plotted
   tempGraph <- graph_from_adjacency_matrix(Data$TransfMatrix$tanhZ, mode = "undirected", weighted = T)
@@ -1010,7 +1010,6 @@ comparePartitions <- function(Data = dmnval7mCommunities, MOI = "FiedlerBinary",
 write('Setting up variables for future computations...', stdout())
 
 ## Choose what to analyze
-Meta <- F # Run meta analysis?
 Parcellated <- F # Parcellated whole brain community detection
 Vertex <- T # ROI-based vertex analysis
 Plots <- F # If running on the SCC, plots might be unhelpful. Have a separate script for that instead
@@ -1161,297 +1160,6 @@ curvatureROI <- getCoords(Labels = bothLbls, Coords = curvatureData, TimeSeries 
 
 # Get thickness for ROIs
 thicknessROI <- getCoords(Labels = bothLbls, Coords = thicknessData, TimeSeries = F)$Coords
-
-###------- Meta-analysis: Load ---------------
-if (Meta == T) {
-  
-  write("Setting up meta-analysis matrices...", stdout())
-  
-  # set directory for subjective value
-  setwd('./DEC/')
-  
-  # number of studies and vector of study names
-  nStudies <- length(dir()) - 1
-  stuDir <- dir()[1:nStudies]
-  
-  # create empty matrix
-  valMatrix <- matrix(data = 0, nrow = nrow(labelCoords_parcel), ncol = nrow(labelCoords_parcel))
-  dimnames(valMatrix) <- list(labelCoords_parcel$Label, labelCoords_parcel$Label)
-  
[…]

### 2018-12-06 Manuscript.Rmd
Made a quick structuring change: sliding post overall

@@
 
-### *Partition Comparison: Day 1 vs Day 2*
-
-In order to determine whether the low agreement shown in mPFC across subjects was a function of intrinsic variability or a subject-specific pattern, we compared the agreement among communities estimated with data from each separate day.
-If the latter were true, within-subject ARI values should be consistently higher than across subjects.
-Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.
-Communities were estimated on concatenated pairs of daily left-right and right-left phase encoded sessions (see Methods for details), and once again compared using ARI.
-Figure 5 shows pairwise comparisons among ten example subjects for PCC and mPFC separately.
-
-``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
-# Load data
-setwd('./Summary_halves/')
-temp <- list.files(pattern = "*_finalSummary.csv")
-subjList_halves <- sapply(temp, substring, first=1, last=9)
-Summaries_halves <- lapply(temp, read.csv)
-
-# Select subsection of subjects for plotting the similarity matrices
-selectSubj <- seq(1,20)
-Summaries_halves_plot <- Summaries_halves[selectSubj]
-subjList_halves_plot <- subjList_halves[selectSubj]
-
-# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
-temp <- list.files(pattern = "*_corHalves.csv")
-Correlation_halves <- lapply(temp, read.csv, header = F)
-Correlation_halves_plot <- Correlation_halves[selectSubj]
-
-# Compare all halves with RI (plot only)
-RI_all_between_halves_plot <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-
-# Compare PCC and PFC among all subjects (plot only)
-tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
-tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
-RI_PFC_halves_plot <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-RI_PCC_halves_plot <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-```
-
-``` {r Partition comparison: halves ratios, echo=FALSE, message = FALSE, cache = TRUE}
-## Now compare all possible pairs of subjects (for actual reporting)
-# Compare all halves with RI
-RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-
-# Compare PCC and PFC among all subjects
-tempComm_PCC_halves <- lapply(Summaries_halves, "[", i = posteriorIndx, j =)
-tempComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
-RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-
-## Let's compare stuff (not accounting for complex interdependencies in the observations)
-## Overall differences in mean RI between PCC and mPFC
-lowPCC_halves <- RI_PCC_halves[lower.tri(RI_PCC_halves)]
-lowPFC_halves <- RI_PFC_halves[lower.tri(RI_PFC_halves)]
-Halves_PCCvPFC_perm <- permute(lowPCC_halves, lowPFC_halves, statType = mean, paired = T)
-Halves_PCCvPFC_ES <- cohenD(lowPCC_halves, lowPFC_halves) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
-# create a selection matrix containing all within-subject session comparisons
-template <- diagBlocks(ncol(RI_all_between_halves), 2) 
-lowTemplate <- template[lower.tri(template)]
-
-# Overall
-# First list element is the within subject values, second is the between subject values
-lowRIHalves <- RI_all_between_halves[lower.tri(RI_all_between_halves)]
-Halves_overallComparison <- list(lowRIHalves[lowTemplate],
-                                lowRIHalves[!lowTemplate])
-Halves_overallComparison[[3]] <- permute(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
-Halves_overallComparison[[4]] <- cohenD(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
-
-# PCC 
-Halves_PCCComparison <- list(lowPCC_halves[lowTemplate],
-                           lowPCC_halves[!lowTemplate])
-Halves_PCCComparison[[3]] <- permute(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
-Halves_PCCComparison[[4]] <- cohenD(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
-
-# mPFC
-Halves_PFCComparison <- list(lowPFC_halves[lowTemplate],
-                           lowPFC_halves[!lowTemplate])
-Halves_PFCComparison[[3]] <- permute(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
-Halves_PFCComparison[[4]] <- cohenD(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
-
-## Ratio of mean within subject sessions over between subject ones (per-subject)
-# Overall
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_all_between_halves[lower.tri(RI_all_between_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_halves), by = 2), function(x) RI_all_between_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_overall <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# PCC
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_PCC_halves[lower.tri(RI_PCC_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_halves), by = 2), function(x) RI_PCC_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_PCC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# PFC
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_PFC_halves[lower.tri(RI_PFC_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_halves), by = 2), function(x) RI_PFC_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_PFC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# Summarize for plotting
-Halves_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
-                                      RI = c(Halves_RIRatios_PCC, Halves_RIRatios_PFC))
-
-# Stats
-Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T)
-Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
-
-```
-
-Once again we found greater alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) than mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed higher levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
-However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic.
-Therefore, we divided each subject's ARI between days by the ARI values with the days from the other subjects.
-This ratio denotes the relative specificity of their partition.
-That means, partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
-Figure 6 shows the ratios for PCC and mPFC for all subjects.
-As expected, we found that while both regions had good specificity (i.e.
-ratios > 1), the ratios for PCC were significantly lower than mPFC (paired permutation,*p*= `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
-These test/retest results suggest that the topographic varability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
-
-### *Partition Comparison: Session*
-
-We extended the analysis of daily data by examining whether the organization of the DMN could be extracted using session data only.
-It is worth noting that the length of each session (approx.
-14 mins long) falls below the stability threshold for fMRI-based modularity estimations [@Gordon2017].
-Nonetheless, high ARI ratios with reduced data could signify the ability to localize a subject's DMN organization with fMRI sessions that are easier to fit along with other study sessions of interest.
-
-``` {r Partition comparison: session similarity matrices, echo=FALSE, message = FALSE, cache = TRUE}
-# Load data
-setwd('./Summary_sess/')
-temp <- list.files()
-subjList_sess <- sapply(temp, substring, first=1, last=9)
-Summaries_sess <- lapply(temp, read.csv)
-
-# Select 10 subjects from the sample to plot
-selectSubj <- seq(1,40)
-subjList_sess_plot <- subjList_sess[selectSubj]
-Summaries_sess_plot <- Summaries_sess[selectSubj]
-
-# Across subjects (just for plotting)
-RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
-tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
-RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-```
-
-``` {r Partition comparison: session compare all, echo=FALSE, message = FALSE, cache = TRUE}
-# Now run comparisons among all subjects (for actual reporting)
-RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
-tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
-RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-
-## Let's compare stuff (not accounting for complex interdependencies in the observations)
-## Overall differences in mean RI between PCC and mPFC
-lowPCC_sess <- RI_PCC_sess[lower.tri(RI_PCC_sess)]
-lowPFC_sess <- RI_PFC_sess[lower.tri(RI_PFC_sess)]
-Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T)
-Sess_PCCvPFC_ES <- cohenD(lowPCC_sess, lowPFC_sess) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
-
-# create a selection matrix containing all within-subject session comparisons
-template <- diagBlocks(ncol(RI_all_between_sess), 4) 
-lowTemplate <- template[lower.tri(template)]
-
-# Overall
-# First list element is the within subject values, second is the between subject values
-lowRISess <- RI_all_between_sess[lower.tri(RI_all_between_sess)]
-Sess_overallComparison <- list(lowRISess[lowTemplate],
-                               lowRISess[!lowTemplate])
-Sess_overallComparison[[3]] <- permute(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
-Sess_overallComparison[[4]] <- cohenD(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
-
-# PCC 
-Sess_PCCComparison <- list(lowPCC_sess[lowTemplate],
-                           lowPCC_sess[!lowTemplate])
-Sess_PCCComparison[[3]] <- permute(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
-Sess_PCCComparison[[4]] <- cohenD(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
-
-# mPFC
-Sess_PFCComparison <- list(lowPFC_sess[lowTemplate],
-                           lowPFC_sess[!lowTemplate])
-Sess_PFCComparison[[3]] <- permute(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
-Sess_PFCComparison[[4]] <- cohenD(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
-
-```
-
-Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 7), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 8).
-
-``` {r Partition comparison: session ratios, echo=FALSE, message = FALSE, cache = TRUE}
-## Brain storming:
-## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
-## Perhaps a more interresting idea would be to generate an index of variance within/between subject
-## These are just attempts at that are not perfect:
-
-# 1) Ratio of mean within subject sessions over between subject ones (per-subject)
-# Overall
-# Split the within-subject session RI values per subject
-temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
-withinSubjVals <- split(Sess_overallComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_sess), by = 4), function(x) RI_all_between_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# PCC
-temp <- ceiling(seq_along(Sess_PCCComparison[[1]])/6)
-withinSubjVals <- split(Sess_PCCComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_sess), by = 4), function(x) RI_PCC_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# PFC
-temp <- ceiling(seq_along(Sess_PFCComparison[[1]])/6)
-withinSubjVals <- split(Sess_PFCComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_sess), by = 4), function(x) RI_PFC_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# Summarize for plotting
-Sess_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
-                                    RI = c(Sess_RIRatios_PCC, Sess_RIRatios_PFC))
-
-# Stats
-Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T)
-Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
-```
-
-We can see again that the ratios for mPFC were higher than those of PCC (permutation,*p*= `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
-This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with relatively small amounts of data in spite of a reduction in the estimates.
-
 ### *Pattern stability over time*
@@
 
-# Do a mixed effects GLM (binomial) to estimate the relationship between Fiedler vec and propDMN
+# Do a mixed effects GLM (binomial, quasi unavailable on glmer) to estimate the relationship between Fiedler vec and propDMN
 SC_FVvPDMN_model <- glmer(slidePropDMN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
@@
 Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model, with subject acting as a random effect (Figure 11).
-The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`,*p*< 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time.
+The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time.
 These analysis show that the original pattern identified with the full dataset is temporally stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN vertices in relatively short fMRI sessions (i.e.
@@
 \bigskip
+
+### *Partition Comparison: Day 1 vs Day 2*
+
+In order to determine whether the low agreement shown in mPFC across subjects was a function of intrinsic variability or a subject-specific pattern, we compared the agreement among communities estimated with data from each separate day.
+If the latter were true, within-subject ARI values should be consistently higher than across subjects.
+Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.
+Communities were estimated on concatenated pairs of daily left-right and right-left phase encoded sessions (see Methods for details), and once again compared using ARI.
+Figure 5 shows pairwise comparisons among ten example subjects for PCC and mPFC separately.
+
+``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
+# Load data
+setwd('./Summary_halves/')
+temp <- list.files(pattern = "*_finalSummary.csv")
+subjList_halves <- sapply(temp, substring, first=1, last=9)
+Summaries_halves <- lapply(temp, read.csv)
+
+# Select subsection of subjects for plotting the similarity matrices
+selectSubj <- seq(1,20)
+Summaries_halves_plot <- Summaries_halves[selectSubj]
+subjList_halves_plot <- subjList_halves[selectSubj]
+
+# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
+temp <- list.files(pattern = "*_corHalves.csv")
+Correlation_halves <- lapply(temp, read.csv, header = F)
+Correlation_halves_plot <- Correlation_halves[selectSubj]
+
+# Compare all halves with RI (plot only)
+RI_all_between_halves_plot <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+
+# Compare PCC and PFC among all subjects (plot only)
+tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
+tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
+RI_PFC_halves_plot <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+RI_PCC_halves_plot <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+```
+
+``` {r Partition comparison: halves ratios, echo=FALSE, message = FALSE, cache = TRUE}
+## Now compare all possible pairs of subjects (for actual reporting)
+# Compare all halves with RI
+RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+
+# Compare PCC and PFC among all subjects
+tempComm_PCC_halves <- lapply(Summaries_halves, "[", i = posteriorIndx, j =)
+tempComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
+RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+
+## Let's compare stuff (not accounting for complex interdependencies in the observations)
+## Overall differences in mean RI between PCC and mPFC
+lowPCC_halves <- RI_PCC_halves[lower.tri(RI_PCC_halves)]
+lowPFC_halves <- RI_PFC_halves[lower.tri(RI_PFC_halves)]
+Halves_PCCvPFC_perm <- permute(lowPCC_halves, lowPFC_halves, statType = mean, paired = T)
+Halves_PCCvPFC_ES <- cohenD(lowPCC_halves, lowPFC_halves) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
+# create a selection matrix containing all within-subject session comparisons
+template <- diagBlocks(ncol(RI_all_between_halves), 2) 
+lowTemplate <- template[lower.tri(template)]
+
+# Overall
+# First list element is the within subject values, second is the between subject values
+lowRIHalves <- RI_all_between_halves[lower.tri(RI_all_between_halves)]
+Halves_overallComparison <- list(lowRIHalves[lowTemplate],
+                                lowRIHalves[!lowTemplate])
+Halves_overallComparison[[3]] <- permute(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
+Halves_overallComparison[[4]] <- cohenD(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
+
+# PCC 
+Halves_PCCComparison <- list(lowPCC_halves[lowTemplate],
+                           lowPCC_halves[!lowTemplate])
+Halves_PCCComparison[[3]] <- permute(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
+Halves_PCCComparison[[4]] <- cohenD(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
+
+# mPFC
+Halves_PFCComparison <- list(lowPFC_halves[lowTemplate],
+                           lowPFC_halves[!lowTemplate])
+Halves_PFCComparison[[3]] <- permute(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
+Halves_PFCComparison[[4]] <- cohenD(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
+
+## Ratio of mean within subject sessions over between subject ones (per-subject)
+# Overall
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_all_between_halves[lower.tri(RI_all_between_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_halves), by = 2), function(x) RI_all_between_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_overall <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# PCC
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_PCC_halves[lower.tri(RI_PCC_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_halves), by = 2), function(x) RI_PCC_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_PCC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# PFC
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_PFC_halves[lower.tri(RI_PFC_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_halves), by = 2), function(x) RI_PFC_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_PFC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# Summarize for plotting
+Halves_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
+                                      RI = c(Halves_RIRatios_PCC, Halves_RIRatios_PFC))
+
+# Stats
+Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T)
+Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
+
+```
+
+Once again we found greater alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) than mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed higher levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
+However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic.
+Therefore, we divided each subject's ARI between days by the ARI values with the days from the other subjects.
+This ratio denotes the relative specificity of their partition.
+That means, partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
+Figure 6 shows the ratios for PCC and mPFC for all subjects.
+As expected, we found that while both regions had good specificity (i.e.
+ratios > 1), the ratios for PCC were significantly lower than mPFC (paired permutation,*p*= `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
+These test/retest results suggest that the topographic varability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
+
+### *Partition Comparison: Session*
+
+We extended the analysis of daily data by examining whether the organization of the DMN could be extracted using session data only.
+It is worth noting that the length of each session (approx.
+14 mins long) falls below the stability threshold for fMRI-based modularity estimations [@Gordon2017].
+Nonetheless, high ARI ratios with reduced data could signify the ability to localize a subject's DMN organization with fMRI sessions that are easier to fit along with other study sessions of interest.
+
+``` {r Partition comparison: session similarity matrices, echo=FALSE, message = FALSE, cache = TRUE}
+# Load data
+setwd('./Summary_sess/')
+temp <- list.files()
+subjList_sess <- sapply(temp, substring, first=1, last=9)
+Summaries_sess <- lapply(temp, read.csv)
+
+# Select 10 subjects from the sample to plot
+selectSubj <- seq(1,40)
+subjList_sess_plot <- subjList_sess[selectSubj]
+Summaries_sess_plot <- Summaries_sess[selectSubj]
+
+# Across subjects (just for plotting)
+RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
+tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
+RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+```
+
+``` {r Partition comparison: session compare all, echo=FALSE, message = FALSE, cache = TRUE}
+# Now run comparisons among all subjects (for actual reporting)
+RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
+tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
+RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+
+## Let's compare stuff (not accounting for complex interdependencies in the observations)
+## Overall differences in mean RI between PCC and mPFC
+lowPCC_sess <- RI_PCC_sess[lower.tri(RI_PCC_sess)]
+lowPFC_sess <- RI_PFC_sess[lower.tri(RI_PFC_sess)]
+Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T)
+Sess_PCCvPFC_ES <- cohenD(lowPCC_sess, lowPFC_sess) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
+
+# create a selection matrix containing all within-subject session comparisons
+template <- diagBlocks(ncol(RI_all_between_sess), 4) 
+lowTemplate <- template[lower.tri(template)]
+
+# Overall
+# First list element is the within subject values, second is the between subject values
+lowRISess <- RI_all_between_sess[lower.tri(RI_all_between_sess)]
+Sess_overallComparison <- list(lowRISess[lowTemplate],
+                               lowRISess[!lowTemplate])
+Sess_overallComparison[[3]] <- permute(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
+Sess_overallComparison[[4]] <- cohenD(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
+
+# PCC 
+Sess_PCCComparison <- list(lowPCC_sess[lowTemplate],
+                           lowPCC_sess[!lowTemplate])
+Sess_PCCComparison[[3]] <- permute(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
+Sess_PCCComparison[[4]] <- cohenD(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
+
+# mPFC
+Sess_PFCComparison <- list(lowPFC_sess[lowTemplate],
+                           lowPFC_sess[!lowTemplate])
+Sess_PFCComparison[[3]] <- permute(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
+Sess_PFCComparison[[4]] <- cohenD(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
+
+```
+
+Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 7), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 8).
+
+``` {r Partition comparison: session ratios, echo=FALSE, message = FALSE, cache = TRUE}
+## Brain storming:
+## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
+## Perhaps a more interresting idea would be to generate an index of variance within/between subject
+## These are just attempts at that are not perfect:
+
+# 1) Ratio of mean within subject sessions over between subject ones (per-subject)
+# Overall
+# Split the within-subject session RI values per subject
+temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
+withinSubjVals <- split(Sess_overallComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_sess), by = 4), function(x) RI_all_between_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# PCC
+temp <- ceiling(seq_along(Sess_PCCComparison[[1]])/6)
+withinSubjVals <- split(Sess_PCCComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_sess), by = 4), function(x) RI_PCC_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# PFC
+temp <- ceiling(seq_along(Sess_PFCComparison[[1]])/6)
+withinSubjVals <- split(Sess_PFCComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_sess), by = 4), function(x) RI_PFC_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# Summarize for plotting
+Sess_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
+                                    RI = c(Sess_RIRatios_PCC, Sess_RIRatios_PFC))
+
+# Stats
+Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T)
+Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
+```
+
+We can see again that the ratios for mPFC were higher than those of PCC (permutation,*p*= `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
+This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with relatively small amounts of data in spite of a reduction in the estimates.
 

### 2018-12-07 Manuscript.Rmd
Change to exploratory ECDF of absolute FV magnitudes so that all plots are plotted along the same column for comparison

@@
 
+# Libraries used for the whole process
+library(tidyverse)
 library(igraph)
@@
 
-# Permutation analysis
-# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
-# Load the coordinates as studies in a list, because for the contrast the studies are permuted
-# Use table(unlist(list)) to get the counts in that case
-setwd('./DEC')
-templist <- dir()
-studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
-
-setwd('../DMN/')
-templist <- dir()
-studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
-
-# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
-allStudies <- c(studyList_sv, studyList_dmn)
-nPerms <- 5000
-nullDist <- numeric()
-
-for (i in seq(nPerms)) {
-
-  if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
-
-  # Sample all the studies and divide into 2 groups
-  randPerm <- sample(allStudies)
-  tmpSV <- randPerm[seq(length(studyList_sv))]
-  tmpDMN <- randPerm[-seq(length(studyList_sv))]
-
-  # Count the number of times each region was reported in the literature
-  # Bilateral activations still count as 1, so we might want to reconsider that
-  tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-                      SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
-                      DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
-
-  # Perform the prop test for each pair and get the max chi-squared stat
-  nullDist[i] <- max(
-                  apply(tmpDF[,2:3], 1, function(data) {
-                    prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
-                    }
-                  ), na.rm = T)
-
-}
-
-# Now do the same for the actual data, to see how it compares to the null dist
-tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-                    SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
-                    DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
-                    propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
-                    propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
-
-# Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
-tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
-  round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
-  })
-tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
-
-# ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
-significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))
+# # Permutation analysis
+# # Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
+# # Load the coordinates as studies in a list, because for the contrast the studies are permuted
+# # Use table(unlist(list)) to get the counts in that case
+# setwd('./DEC')
+# templist <- dir()
+# studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
+# 
+# setwd('../DMN/')
+# templist <- dir()
+# studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
+# 
+# # For each permutation, reassign the study labels, maintaining the original number of studies per condition 
+# allStudies <- c(studyList_sv, studyList_dmn)
+# nPerms <- 5000
+# nullDist <- numeric()
+# 
+# for (i in seq(nPerms)) {
+#   
+#   if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
+#     
+#   # Sample all the studies and divide into 2 groups
+#   randPerm <- sample(allStudies)
+#   tmpSV <- randPerm[seq(length(studyList_sv))]
+#   tmpDMN <- randPerm[-seq(length(studyList_sv))]
+#   
+#   # Count the number of times each region was reported in the literature
+#   # Bilateral activations still count as 1, so we might want to reconsider that
+#   tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+#                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
+#                       DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
+#   
+#   # Perform the prop test for each pair and get the max chi-squared stat
+#   nullDist[i] <- max(
+#                   apply(tmpDF[,2:3], 1, function(data) {
+#                     prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
+#                     }
+#                   ), na.rm = T)
+#   
+# }
+# 
+# # Now do the same for the actual data, to see how it compares to the null dist
+# tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+#                     SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
+#                     DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
+#                     propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
+#                     propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
+# 
+# # Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
+# tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
+#   round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
+#   })
+# tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
+# 
+# # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
+# significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))
 
@@
 ``` {r ROI computation, echo=FALSE, message = FALSE}
-#TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
-## ROI definition
-# First, load the raw count csv files
-valCounts <- read.csv2('decCounts.csv', sep = ",")
-dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
-
-# Then, get the means of the counts per domain, both within/outside the search space
-# This is to get a broad estimate of the average report amounts in the literature
-tempBoot <- bootstrap(valCounts$Counts)
-BV <- round(mean(tempBoot))
-BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
-tempBoot <- bootstrap(dmnCounts$Counts)
-BD <- round(mean(tempBoot))
-BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
-rm(tempBoot)
-
-# Now select only the ROIs from Yeo et al (TEMP)
-valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
-dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
-
-# Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
-# than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
-for (i in seq(valCounts$Counts)) {
-  indx <- valCounts$Counts[i]
-  tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
-  valCounts$Chi[i] <- tempTest$statistic
-  valCounts$pVal[i] <- tempTest$p.value
-}
-
-for (i in seq(dmnCounts$Counts)) {
-  indx <- dmnCounts$Counts[i]
-  tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
-  dmnCounts$Chi[i] <- tempTest$statistic
-  dmnCounts$pVal[i] <- tempTest$p.value
-}
-
-# Retain only the significant parcels
-t1 <- valCounts$Label[valCounts$pVal < 0.05]
-t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
-
-# Remove hemispheric references
-t1 <- unique(substring(t1,2))
-t2 <- unique(substring(t2,2))
-
-# Labels to put in text
-dmnLbls <- gsub("ROI","", t2) 
-dmnLbls <- gsub("_","", dmnLbls)
-valLbls <- gsub("ROI","", t1) 
-valLbls <- gsub("_","", valLbls)
-
-# final overlap
-bothLbls <- dmnLbls[dmnLbls %in% valLbls]
+# #TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
+# ## ROI definition
+# # First, load the raw count csv files
+# valCounts <- read.csv2('decCounts.csv', sep = ",")
+# dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
+# 
+# # Then, get the means of the counts per domain, both within/outside the search space
+# # This is to get a broad estimate of the average report amounts in the literature
+# tempBoot <- bootstrap(valCounts$Counts)
+# BV <- round(mean(tempBoot))
+# BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
+# tempBoot <- bootstrap(dmnCounts$Counts)
+# BD <- round(mean(tempBoot))
+# BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
+# rm(tempBoot)
+# 
+# # Now select only the ROIs from Yeo et al (TEMP)
+# valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
+# dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
+# 
+# # Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
+# # than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
+# for (i in seq(valCounts$Counts)) {
+#   indx <- valCounts$Counts[i]
+#   tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
+#   valCounts$Chi[i] <- tempTest$statistic
+#   valCounts$pVal[i] <- tempTest$p.value
+# }
+# 
+# for (i in seq(dmnCounts$Counts)) {
+#   indx <- dmnCounts$Counts[i]
+#   tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
+#   dmnCounts$Chi[i] <- tempTest$statistic
+#   dmnCounts$pVal[i] <- tempTest$p.value
+# }
+# 
+# # Retain only the significant parcels
+# t1 <- valCounts$Label[valCounts$pVal < 0.05]
+# t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
+# 
+# # Remove hemispheric references
+# t1 <- unique(substring(t1,2))
+# t2 <- unique(substring(t2,2))
+# 
+# # Labels to put in text
+# dmnLbls <- gsub("ROI","", t2) 
+# dmnLbls <- gsub("_","", dmnLbls)
+# valLbls <- gsub("ROI","", t1) 
+# valLbls <- gsub("_","", valLbls)
+# 
+# # final overlap
+# bothLbls <- dmnLbls[dmnLbls %in% valLbls]
 
@@
 Summaries <- lapply(temp, read.csv)
+nVertices <- nrow(Summaries[[1]]) # in case I need the number of vertices included per brain
 ```
@@
 test <- do.call(rbind, Summaries)
-test %>%
-  mutate(SubjID = rep(subjList, each = 5081),
+ecdfPCC <- test %>%
+          mutate(SubjID = rep(subjList, each = nVertices),
                  FV_abs = abs(FiedlerVec),
                  Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
-  filter(y > 0) %>%
-  group_by(SubjID, Community) %>%
-  summarize(FV_mean = median(FV_abs)) %>%
-  ggplot(aes(Community, FV_mean)) +
-  geom_boxplot() + 
+          filter(y < 0) %>%
+          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
+          stat_ecdf(alpha = 0.3) +
+          #scale_color_manual(values = c("Yellow", "Red")) +
+          xlim(0,0.05) +
+          geom_vline(xintercept = 0.009, lty = 2) +
+          labs(title = "Per-subject ECDF of Fiedler values: PCC") +
           theme_classic()
-# Second one plots the ecdf
-# Line indicates the 75th quantile of the combined Fiedler vectors across participants (i.e. potential threshold)
-test %>%
-  mutate(SubjID = rep(subjList, each = nrow(Summaries[[1]])),
+
+ecdfPFC <- test %>%
+          mutate(SubjID = rep(subjList, each = nVertices),
                  FV_abs = abs(FiedlerVec),
@@
           ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
-  stat_ecdf() +
+          #scale_color_manual(values = c("Yellow", "Red")) +
+          stat_ecdf(alpha = 0.3) +
+          xlim(0,0.05) +
+          labs(title = "Per-subject ECDF of Fiedler values: PFC") +
           geom_vline(xintercept = 0.009, lty = 2) +
           theme_classic()
+
+ecdfALL <- test %>%
+  mutate(SubjID = rep(subjList, each = nVertices),
+         FV_abs = abs(FiedlerVec),
+         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
+  ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
+  #scale_color_manual(values = c("Yellow", "Red")) +
+  stat_ecdf(alpha = 0.5) +
+  xlim(0,0.05) +
+  labs(title = "Per-subject ECDF of Fiedler values") +
+  geom_vline(xintercept = 0.009, lty = 2) +
+  theme_classic()
+
+#grid.arrange(pcc1,pfc1, ncol = 2)
+#grid.arrange(All,pcc2,pfc2, ncol = 1)
+
 ```

### 2018-12-07 Manuscript.Rmd
Trying to not be stupid and creating a thresholding function for FV. But it's not working

@@
   nVertices <- 59412
-  tempVec <- rep(-1, nVertices)
+  tempVec <- rep(0, nVertices)
   temp <- grep(MOI, colnames(Data))
@@
 
+### *Thresholding*
+``` {r Threshold this stupid stuff}
+# This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
+# The threshold will be based on proportion DMN given by thresholdRange
+threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {
+
+  ## Check if the proportions even go that low, otherwise replace by next most stable low/high value
+  # get the 2 values with highest reports (this should be stable upper/lower proportions)
+  stableExtremes <- sort(table(Data$slidePropDMN), decreasing = T)[seq(2)]
+  stableExtremes <- sort(as.numeric(names(stableExtremes)))
+
+  # if the values are not extreme enough, replace the original threshold with the new stable ones
+  if (thresholdRange[1] < stableExtremes[1]) {
+
+    thresholdRange[1] <- stableExtremes[1]
+
+  }
+
+  if (thresholdRange[2] > stableExtremes[2]) {
+
+    thresholdRange[2] <- stableExtremes[2]
+
+  }
+
+  ## Run the actual process
+  # placeholder to be returned
+  thresholds <- c(NA,NA)
+
+  # start the counter at chance
+  meanProp <- 0.5
+
+  # select a range of FV values
+  thresh <- seq(0, min(Data$FiedlerVec), length.out = nthresh)
+
+  # Iterate over the possible FV until DMN affiliations go below 1%
+  count <- 1
+  while (meanProp > thresholdRange[1]) {
+
+    # get the mean proportion of DMN from remaining vertices based on putative threshold
+    meanProp <- Data %>% filter(FiedlerVec <= thresh[count]) %>% summarize(mean(slidePropDMN))
+
+    # if a threshold meets requirement, store its value
+    if (meanProp <= thresholdRange[1]) {
+      thresholds[1] <- thresh[count]
+    }
+    print(count)
+    print(meanProp)
+    print(thresh[count])
+    count <- count + 1
+
+  }
+
+  # repeat for the upper threshold
+  # restart parameters
+  meanProp <- 0.5
+  thresh <- seq(0, max(abs(Data$FiedlerVec)), length.out = nthresh)
+
+  # Iterate over the possible FV until DMN affiliations go over 99%
+  count <- 1
+  while (meanProp < thresholdRange[2]) {
+
+    # get the mean proportion of DMN from remaining vertices based on putative threshold
+    meanProp <- Data %>% filter(FiedlerVec > thresh[count]) %>% summarize(mean(slidePropDMN))
+
+    # if a threshold meets requirement, store its value
+    if (meanProp >= thresholdRange[2]) {
+      thresholds[2] <- thresh[count]
+    }
+
+    count <- count + 1
+
+  }
+
+  return(round(thresholds, digits = 5))
+
+}
+```
 ### *Pattern stability over time*
@@
          tl.cex = 0.1, 
-         cl.lim = c(0,1),
+         #cl.lim = c(0,1),
          cl.length = 3,
@@
          cl.pos = "n",
-         cl.lim = c(0,1),
+         #cl.lim = c(0,1),
          cl.length = 3,
@@
          tl.pos = "n", 
-         cl.lim = c(0,1),
+         #cl.lim = c(0,1),
          cl.pos = "r",
@@
          tl.col = "black", 
-         cl.lim = c(0,1),
+         #cl.lim = c(0,1),
          cl.length = 3,

### 2018-12-08 Manuscript.Rmd
Ok improvements to thresholding

@@
 
+# This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
+# The threshold will be based on proportion DMN given by thresholdRange
+threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {
+
+  ## Check if the proportions even go that low, otherwise replace by next most stable low/high value
+  # get the 2 values with highest reports (this should be stable upper/lower proportions)
+  stableExtremes <- sort(table(Data$slidePropDMN), decreasing = T)[seq(2)]
+  stableExtremes <- sort(as.numeric(names(stableExtremes)))
+
+  # if the values are not extreme enough, replace the original threshold with the new stable ones
+  if (thresholdRange[1] < stableExtremes[1]) {
+
+    thresholdRange[1] <- stableExtremes[1]
+
+  }
+
+  if (thresholdRange[2] > stableExtremes[2]) {
+
+    thresholdRange[2] <- stableExtremes[2]
+
+  }
+
+  ## Run the actual process
+  # placeholder to be returned
+  thresholds <- c(NA,NA)
+
+  # start the counter at chance
+  meanProp <- 0.5
+
+  # select a range of FV values
+  thresh <- seq(0, min(Data$FiedlerVec), length.out = nthresh)
+
+  # Iterate over the possible FV until DMN affiliations go below 1%
+  count <- 1
+  while (meanProp >= thresholdRange[1]) {
+
+    # get the mean proportion of DMN from remaining vertices based on putative threshold
+    meanProp <- Data %>% filter(FiedlerVec <= thresh[count]) %>% summarize(mean(slidePropDMN))
+
+    # if a threshold meets requirement, store its value
+    if (meanProp <= thresholdRange[1]) {
+      thresholds[1] <- thresh[count]
+    }
+
+    count <- count + 1
+
+  }
+
+  # repeat for the upper threshold
+  # restart parameters
+  meanProp <- 0.5
+  thresh <- seq(0, max(abs(Data$FiedlerVec)), length.out = nthresh)
+
+  # Iterate over the possible FV until DMN affiliations go over 99%
+  count <- 1
+  while (meanProp <= thresholdRange[2]) {
+
+    # get the mean proportion of DMN from remaining vertices based on putative threshold
+    meanProp <- Data %>% filter(FiedlerVec > thresh[count]) %>% summarize(mean(slidePropDMN))
+
+    # if a threshold meets requirement, store its value
+    if (meanProp >= thresholdRange[2]) {
+      thresholds[2] <- thresh[count]
+    }
+
+    count <- count + 1
+
+  }
+
+  return(round(thresholds, digits = 5))
+
+}
 ```
@@
 ``` {r Threshold this stupid stuff}
-# This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
-# The threshold will be based on proportion DMN given by thresholdRange
-threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {
-
-  ## Check if the proportions even go that low, otherwise replace by next most stable low/high value
-  # get the 2 values with highest reports (this should be stable upper/lower proportions)
-  stableExtremes <- sort(table(Data$slidePropDMN), decreasing = T)[seq(2)]
-  stableExtremes <- sort(as.numeric(names(stableExtremes)))
-
-  # if the values are not extreme enough, replace the original threshold with the new stable ones
-  if (thresholdRange[1] < stableExtremes[1]) {
-
-    thresholdRange[1] <- stableExtremes[1]
-
-  }
-
-  if (thresholdRange[2] > stableExtremes[2]) {
-
-    thresholdRange[2] <- stableExtremes[2]
-
-  }
-
-  ## Run the actual process
-  # placeholder to be returned
-  thresholds <- c(NA,NA)
-
-  # start the counter at chance
-  meanProp <- 0.5
-
-  # select a range of FV values
-  thresh <- seq(0, min(Data$FiedlerVec), length.out = nthresh)
-
-  # Iterate over the possible FV until DMN affiliations go below 1%
-  count <- 1
-  while (meanProp > thresholdRange[1]) {
-
-    # get the mean proportion of DMN from remaining vertices based on putative threshold
-    meanProp <- Data %>% filter(FiedlerVec <= thresh[count]) %>% summarize(mean(slidePropDMN))
-
-    # if a threshold meets requirement, store its value
-    if (meanProp <= thresholdRange[1]) {
-      thresholds[1] <- thresh[count]
-    }
-    print(count)
-    print(meanProp)
-    print(thresh[count])
-    count <- count + 1
-
-  }
-
-  # repeat for the upper threshold
-  # restart parameters
-  meanProp <- 0.5
-  thresh <- seq(0, max(abs(Data$FiedlerVec)), length.out = nthresh)
-
-  # Iterate over the possible FV until DMN affiliations go over 99%
-  count <- 1
-  while (meanProp < thresholdRange[2]) {
-
-    # get the mean proportion of DMN from remaining vertices based on putative threshold
-    meanProp <- Data %>% filter(FiedlerVec > thresh[count]) %>% summarize(mean(slidePropDMN))
-
-    # if a threshold meets requirement, store its value
-    if (meanProp >= thresholdRange[2]) {
-      thresholds[2] <- thresh[count]
-    }
-
-    count <- count + 1
-
-  }
-
-  return(round(thresholds, digits = 5))
-
+# Get a FV threshold for each subject based on mean vertex stability
+# Run the function safely, because some noisy subjects have no relationship between stability and FV
+# Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
+TFV <- safely(threshFV)
+tempList <- lapply(Summaries, TFV)
+
+# Store thre FV thresholds for all subject 
+threshDF <- data_frame(SubjID = substring(subjList,1,6),
+                       Lower = NA,
+                       Upper = NA)
+for (i in seq_along(tempList)) {
+  if (is.null(tempList[[i]]$result)) {
+    threshDF[i,2:3] <- c(0,0)
+  } else {
+    threshDF[i,2] <- tempList[[i]]$result[1]
+    threshDF[i,3] <- tempList[[i]]$result[2]
+  }
 }

### 2018-12-08 Manuscript.Rmd
The thresholding works, but doesn't really change the matrix-visualizations

@@
 labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))
+
+# Whether to apply subject-wise thresholds on maps or not
+threshMaps <- TRUE
 
@@
 
+*NOTE: It might be better to just avoid cluster comparisons at this pre-threshold level*
 With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 total TRs from four scanning sessions over two days).
@@
 
-### *Thresholding*
-``` {r Threshold this stupid stuff}
-# Get a FV threshold for each subject based on mean vertex stability
-# Run the function safely, because some noisy subjects have no relationship between stability and FV
-# Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
-TFV <- safely(threshFV)
-tempList <- lapply(Summaries, TFV)
-
-# Store thre FV thresholds for all subject 
-threshDF <- data_frame(SubjID = substring(subjList,1,6),
-                       Lower = NA,
-                       Upper = NA)
-for (i in seq_along(tempList)) {
-  if (is.null(tempList[[i]]$result)) {
-    threshDF[i,2:3] <- c(0,0)
-  } else {
-    threshDF[i,2] <- tempList[[i]]$result[1]
-    threshDF[i,3] <- tempList[[i]]$result[2]
-  }
-}
-```
 ### *Pattern stability over time*
@@
 
+### *Thresholding*
+``` {r Threshold this stupid stuff}
+# Get a FV threshold for each subject based on mean vertex stability
+# Run the function safely, because some noisy subjects have no relationship between stability and FV
+# Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
+TFV <- safely(threshFV)
+tempList <- lapply(Summaries, TFV)
+
+# Store thre FV thresholds for all subject 
+threshDF <- data_frame(SubjID = substring(subjList,1,6),
+                       Lower = NA,
+                       Upper = NA)
+for (i in seq_along(tempList)) {
+  if (is.null(tempList[[i]]$result)) {
+    threshDF[i,2:3] <- c(0,0)
+  } else {
+    threshDF[i,2] <- as.numeric(tempList[[i]]$result[1])
+    threshDF[i,3] <- as.numeric(tempList[[i]]$result[2])
+  }
+}
+
+```
+
+### *Partition Comparison:Thresholded Full Datasets*
+``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
+# Apply threshold to Summaries
+if (threshMaps) {
+  for (i in seq(nSubj)) {
+  Summaries[[i]] <- Summaries[[i]] %>%
+    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
+    mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
+  }
+}
+
+# Across subjects
+# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
+RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+RI_all_between_lowtri <- RI_all_between[lower.tri(RI_all_between)]
+
+posteriorIndx <- Summaries[[1]]$y < 0
+tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
+tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
+RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+
+# Let's compare stuff
+testPCC <- RI_PCC[lower.tri(RI_PCC)]
+testPFC <- RI_PFC[lower.tri(RI_PFC)]
+Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
+Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+# To get the rate of stability per vertex across subjects
+FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
+FV <- do.call(cbind, lapply(Summaries, "[[", "FiedlerVec"))
+FBS <- rowMeans(FB)
+FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]
+
+# Now let's test something: 
+# Traditionally, a vertex-wise test would be carried across subjects.
+# If these traditional analyses miss out on these idiosyncrasies, you should get unsignificant results.
+# So we did a prop.test per vertex, and corrected with FDR to mimic this situation.
+All_proptests <- apply(FB, 1, function(x) {prop.test(sum(x), nSubj)})
+Prop_pvals_corrected <- p.adjust(sapply(All_proptests, "[[", "p.value"), method = "BY")
+Prop_pvals_corrected <- ifelse(Prop_pvals_corrected < 0.05, 1, 0)
+Chisquares <- sapply(All_proptests, "[[", "statistic")
+
+# And a t-test on the FV vals
+All_ttests <- apply(FV, 1, t.test)
+Ttest_pvals_corrected <- p.adjust(sapply(All_ttests, "[[", "p.value"), method = "BY")
+Ttest_pvals_corrected <- ifelse(Ttest_pvals_corrected < 0.05, 1, 0)
+Tstats <- sapply(All_ttests, "[[", "statistic")
+
+```
 ### *Partition Comparison: Day 1 vs Day 2*
@@
 Summaries_halves <- lapply(temp, read.csv)
+
+# Apply threshold to Summaries
+if (threshMaps) {
+  # create a vector of repeated indices, so each threshold is applied to each subject twice
+  threshindex <- rep(seq(nSubj), each = 2)
+  count <- 1
+  for (i in threshindex) {
+    Summaries_halves[[count]] <- Summaries_halves[[count]] %>%
+            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
+            mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
+    count <- count + 1
+  }
+}
 
@@
 Summaries_sess <- lapply(temp, read.csv)
+
+# Apply threshold to Summaries
+if (threshMaps) {
+  # create a vector of repeated indices, so each threshold is applied to each subject twice
+  threshindex <- rep(seq(nSubj), each = 4)
+  count <- 1
+  for (i in threshindex) {
+    Summaries_sess[[count]] <- Summaries_sess[[count]] %>%
+            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
+            mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
+    count <- count + 1
+  }
+}
 
@@
          tl.col = "black", 
-         cl.lim = c(-0.03,1),
+         #cl.lim = c(-0.03,1),
          cl.pos = "n",

### 2018-12-08 graphAnalysis_solo.R
The thresholding works, but doesn't really change the matrix-visualizations

@@ -1092,6 +1092,7 @@ Yeo_PCC_labels <- c("_7m_",
                     "_d23ab_",
                     "_v23ab_")
 
+
 # mPFC_only <- c("_a24_",
 #                "_d32_",
 #                "_p32_",
@@ -1100,22 +1101,41 @@ Yeo_PCC_labels <- c("_7m_",
 #                "_10v_",
 #                "_OFC_",
 #                "_s32_",
-#                "_p24_")
+#                "_p24_",
+#                "_10d_",
+#                "_25_")
 
-mPFC_only <- c("_a24_",
-               "_d32_",
-               "_p32_",
-               "_10r_",
-               "_9m_",
-               "_10v_",
-               "_OFC_",
-               "_s32_",
-               "_p24_",
-               "_10d_",
-               "_25_")
+mPFC_only <- c("L_25_ROI",
+              "L_OFC_ROI",
+              "L_10v_ROI",
+              "R_25_ROI",
+              "R_OFC_ROI",
+              "R_10v_ROI",
+              "L_s32_ROI",
+              "R_8Ad_ROI",
+              "R_9p_ROI",
+              "R_p24_ROI",
+              "R_d32_ROI",
+              "R_9m_ROI",
+              "R_p32_ROI",
+              "R_a24_ROI",
+              "R_10r_ROI",
+              "R_10d_ROI",
+              "L_8Ad_ROI",
+              "L_9p_ROI",
+              "L_p24_ROI",
+              "L_d32_ROI",
+              "L_9m_ROI",
+              "L_p32_ROI",
+              "L_a24_ROI",
+              "L_10r_ROI",
+              "L_10d_ROI",
+              "R_s32_ROI",
+              "R_9a_ROI",
+              "L_p10p_ROI")
 
 # Little test to ensure that the ROIs match before running the whole thing
-if (FALSE %in% (mPFC_only %in% c(mPFC_only, "Blah"))) {
+if (FALSE %in% (mPFC_only %in% bothLbls)) {
   stop("mPFC-only and Overlapping ROIs don't match")
 }
 

### 2018-12-08 Manuscript.Rmd
Thresholding fully checked. Small improvement to HCPOut

@@
 # Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
-HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307"){
+HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){
 
   nVertices <- 59412
-  tempVec <- rep(0, nVertices)
+  tempVec <- rep(padding, nVertices)
   temp <- grep(MOI, colnames(Data))

### 2018-12-11 Manuscript.Rmd
This works, but the pdf isn't opening well

@@
 output:
+  pdf_document: default
   word_document: 
     reference_docx: Style_reference.docx
-  pdf_document: default
   html_document: default
@@
 
-``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
+``` {r ROI computation from Matlab, echo=FALSE, message = FALSE, cache = TRUE}
 # This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
@@
 
-# # Permutation analysis
-# # Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
-# # Load the coordinates as studies in a list, because for the contrast the studies are permuted
-# # Use table(unlist(list)) to get the counts in that case
+# Permutation analysis
+# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
+# Load the coordinates as studies in a list, because for the contrast the studies are permuted
+# Use table(unlist(list)) to get the counts in that case
 # setwd('./DEC')
@@
 # allStudies <- c(studyList_sv, studyList_dmn)
-# nPerms <- 5000
+# nPerms <- 1000 # stored statistics are computed @ 5k, but it's computationally demanding to do that.
 # nullDist <- numeric()
@@
 ``` {r ROI computation, echo=FALSE, message = FALSE}
-# #TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
-# ## ROI definition
-# # First, load the raw count csv files
-# valCounts <- read.csv2('decCounts.csv', sep = ",")
-# dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
-# 
-# # Then, get the means of the counts per domain, both within/outside the search space
-# # This is to get a broad estimate of the average report amounts in the literature
-# tempBoot <- bootstrap(valCounts$Counts)
-# BV <- round(mean(tempBoot))
-# BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
-# tempBoot <- bootstrap(dmnCounts$Counts)
-# BD <- round(mean(tempBoot))
-# BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
-# rm(tempBoot)
-# 
-# # Now select only the ROIs from Yeo et al (TEMP)
-# valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
-# dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
-# 
-# # Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
-# # than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
-# for (i in seq(valCounts$Counts)) {
-#   indx <- valCounts$Counts[i]
-#   tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
-#   valCounts$Chi[i] <- tempTest$statistic
-#   valCounts$pVal[i] <- tempTest$p.value
-# }
-# 
-# for (i in seq(dmnCounts$Counts)) {
-#   indx <- dmnCounts$Counts[i]
-#   tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
-#   dmnCounts$Chi[i] <- tempTest$statistic
-#   dmnCounts$pVal[i] <- tempTest$p.value
-# }
-# 
-# # Retain only the significant parcels
-# t1 <- valCounts$Label[valCounts$pVal < 0.05]
-# t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
-# 
-# # Remove hemispheric references
-# t1 <- unique(substring(t1,2))
-# t2 <- unique(substring(t2,2))
-# 
-# # Labels to put in text
-# dmnLbls <- gsub("ROI","", t2) 
-# dmnLbls <- gsub("_","", dmnLbls)
-# valLbls <- gsub("ROI","", t1) 
-# valLbls <- gsub("_","", valLbls)
-# 
-# # final overlap
-# bothLbls <- dmnLbls[dmnLbls %in% valLbls]
-
-# This part is just for reference, as the labels are loaded from a file
-# # And get the set of overlapping areas between literatures
-# # This is missing some cingulate and PFC areas, and adds V2.
-# # However, we can say that we are filling in the gap for completeness,
-# # and removing V2 because it's demonstrably irrelevant.
-# bothLbls <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
-# 
-# # You could also try to permute the allocation of reports per literature,
-# # and then perform a chi-squared per parcel. Get the max stat per iteration.
-# # Now you have your null distribution.
+#TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
+## ROI definition
+# First, load the raw count csv files
+valCounts <- read.csv2('decCounts.csv', sep = ",")
+dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
+
+# Then, get the means of the counts per domain, both within/outside the search space
+# This is to get a broad estimate of the average report amounts in the literature
+tempBoot <- bootstrap(valCounts$Counts)
+BV <- round(mean(tempBoot))
+BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
+tempBoot <- bootstrap(dmnCounts$Counts)
+BD <- round(mean(tempBoot))
+BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
+rm(tempBoot)
+
+# Now select only the ROIs from Yeo et al (TEMP)
+valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
+dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
+
+# Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
+# than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
+for (i in seq(valCounts$Counts)) {
+  indx <- valCounts$Counts[i]
+  tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
+  valCounts$Chi[i] <- tempTest$statistic
+  valCounts$pVal[i] <- tempTest$p.value
+}
+for (i in seq(dmnCounts$Counts)) {
+ indx <- dmnCounts$Counts[i]
+ tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
+ dmnCounts$Chi[i] <- tempTest$statistic
+ dmnCounts$pVal[i] <- tempTest$p.value
+}
+# Retain only the significant parcels
+t1 <- valCounts$Label[valCounts$pVal < 0.05]
+t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
+# Remove hemispheric references
+t1 <- unique(substring(t1,2))
+t2 <- unique(substring(t2,2))
+# Labels to put in text
+dmnLbls <- gsub("ROI","", t2)
+dmnLbls <- gsub("_","", dmnLbls)
+valLbls <- gsub("ROI","", t1)
+valLbls <- gsub("_","", valLbls)
+
+#bothLbls <- dmnLbls[dmnLbls %in% valLbls] # This part is just for reference, as the labels are loaded from a file
+# final overlap
+# And get the set of overlapping areas between literatures
+# This is missing some cingulate and PFC areas, and adds V2.
+# However, we can say that we are filling in the gap for completeness,
+# and removing V2 because it's demonstrably irrelevant.
+#bothLbls <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
+# You could also try to permute the allocation of reports per literature,
+# and then perform a chi-squared per parcel. Get the max stat per iteration.
+# Now you have your null distribution.
 
@@
 #grid.arrange(pcc1,pfc1, ncol = 2)
-#grid.arrange(All,pcc2,pfc2, ncol = 1)
+#grid.arrange(ecdfALL,ecdfPCC,ecdfPFC, ncol = 1)
 
@@
 ### *Partition Comparison:Thresholded Full Datasets*
-``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: all thresholded, echo=FALSE, message = FALSE, cache = TRUE}
 # Apply threshold to Summaries
@@
 Summaries_halves <- lapply(temp, read.csv)
+selectSubj <- seq(20)
+
+# Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
+# Select a subsection of participants for plotting
+Summaries_halves_plot <- Summaries_halves[selectSubj]
+unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
+unthreshComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
 
@@
 
-# Select subsection of subjects for plotting the similarity matrices
-selectSubj <- seq(1,20)
-Summaries_halves_plot <- Summaries_halves[selectSubj]
-subjList_halves_plot <- subjList_halves[selectSubj]
-
-# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
-temp <- list.files(pattern = "*_corHalves.csv")
-Correlation_halves <- lapply(temp, read.csv, header = F)
-Correlation_halves_plot <- Correlation_halves[selectSubj]
-
-# Compare all halves with RI (plot only)
-RI_all_between_halves_plot <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-
-# Compare PCC and PFC among all subjects (plot only)
-tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
-tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
-RI_PFC_halves_plot <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-RI_PCC_halves_plot <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+# # Now recompute so that all network analyses are performed on thresholded data
+# # Select subsection of subjects for plotting the similarity matrices
+# Summaries_halves_plot <- Summaries_halves[selectSubj]
+# subjList_halves_plot <- subjList_halves[selectSubj]
+
+# # Compare all halves with RI (plot only)
+# RI_all_between_halves_plot <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+# 
+# # Compare PCC and PFC among all subjects (plot only)
+# tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
+# tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
+# RI_PFC_halves_plot <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
+# RI_PCC_halves_plot <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
 ```
@@
 
+# Select a submatrix with the best-performing subjects to show on the matrix figures
+# These will be also displayed on the session matrix
+# This way I don't have to recompute stuff
+tmp <- data_frame(SubjID = subjList,
+                  DailyARI = Halves_PFCComparison[[1]])
+best <- tmp %>% top_n(10, wt = DailyARI) %>% arrange(DailyARI)
+bestindx <- substr(subjList_halves,1,6) %in% best$SubjID
+
+RI_all_between_halves_plot <- RI_all_between_halves[bestindx, bestindx]
+RI_PFC_halves_plot <- RI_PFC_halves[bestindx, bestindx]
+RI_PCC_halves_plot <- RI_PCC_halves[bestindx, bestindx]
+
+# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
+temp <- list.files(pattern = "*_corHalves.csv")
+Correlation_halves <- lapply(temp, read.csv, header = F)
+Correlation_halves_plot <- Correlation_halves[bestindx] # CHANGE TO THE ACTUAL SUBJECTS
 ```
@@
 
-# Select 10 subjects from the sample to plot
-selectSubj <- seq(1,40)
-subjList_sess_plot <- subjList_sess[selectSubj]
-Summaries_sess_plot <- Summaries_sess[selectSubj]
-
-# Across subjects (just for plotting)
-RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
-tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
-RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+# # Select 10 subjects from the sample to plot
+# selectSubj <- seq(40)
+# subjList_sess_plot <- subjList_sess[selectSubj]
+# Summaries_sess_plot <- Summaries_sess[selectSubj]
+# 
+# 
+# # Across subjects (just for plotting)
+# RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+# tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
+# tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
+# RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
+# RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
 ```
@@
 
+# Select the best performing for plotting, from daily performance
+bestindx <- substr(subjList_sess,1,6) %in% best$SubjID
+RI_all_between_sess_plot <- RI_all_between_sess[bestindx, bestindx]
+RI_PFC_sess_plot <- RI_PFC_sess[bestindx, bestindx]
+RI_PCC_sess_plot <- RI_PCC_sess[bestindx, bestindx]
 ```
@@
 ## Between halves analysis for correlation and communities (mPFC only)
-tempComm_PFC_halves_plot <- lapply(seq_along(tempComm_PFC_halves_plot), function(x) cbind(tempComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
-D1 <- tempComm_PFC_halves_plot
-D2 <- lapply(tempComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
+unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
+D1 <- unthreshComm_PFC_halves_plot
+D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
 Data <- c(D1,D2)
+subjList_halves_plot <- rep(best$SubjID, each = 2)
 allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
@@
 # Compare correlation with community approach on mPFC
-tempComm <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
-tempCor <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
-tempBoth <- sapply(seq(1, length(tempComm_PFC_halves), by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
+tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
+tempCor <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
+tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
 prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
@@
 
-### *Table 1. Significant brain regions per literature*
+### *Table 1. (UPDATE) Significant brain regions per literature*
 | Literature                  | Significant Brain Regions   |
@@
 
-``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=10, fig.height=4, fig.cap = "Figure 10.
+``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=4, fig.cap = "Figure 10.
 ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle).
@@
 
-# plots
-SC_PCCPFC_plot <- ggplot(data = SC_PCC)
-SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
-  geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
-  ylim(0,1) + 
-  labs(y = "ARI") +
-  theme(text = element_text(size=35)) +
-  geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
-  geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
-  theme_classic()
+# # plots
+# SC_PCCPFC_plot <- ggplot(data = SC_PCC)
+# SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
+#   geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
+#   ylim(0,1) + 
+#   labs(y = "ARI") +
+#   theme(text = element_text(size=35)) +
+#   geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
+#   geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
+#   theme_classic()
 
@@
 
-grid.arrange(SC_PCCPFC_plot, SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 3)
+grid.arrange(SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 2)
+
 ```

### 2018-12-11 Manuscript.Rmd
The final dataset was run, and this script will produce the pdf fine (was running into issues plotting the mixed effects before, corrupting the pdf)

@@
 # First plot compares the median FV between communities across subjects
-test <- do.call(rbind, Summaries)
-ecdfPCC <- test %>%
-          mutate(SubjID = rep(subjList, each = nVertices),
-                 FV_abs = abs(FiedlerVec),
+allSummaries <- do.call(rbind, Summaries)
+allSummaries$SubjID <- rep(subjList, each = nVertices) 
+ecdfPCC <- allSummaries %>%
+          mutate(FV_abs = abs(FiedlerVec),
                  Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
@@
 
-ecdfPFC <- test %>%
-          mutate(SubjID = rep(subjList, each = nVertices),
-                 FV_abs = abs(FiedlerVec),
+ecdfPFC <- allSummaries %>%
+          mutate(FV_abs = abs(FiedlerVec),
                  Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
@@
 
-ecdfALL <- test %>%
-  mutate(SubjID = rep(subjList, each = nVertices),
-         FV_abs = abs(FiedlerVec),
+ecdfALL <- allSummaries %>%
+  mutate(FV_abs = abs(FiedlerVec),
          Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
@@
 
-# Put together a data frame to plot Fiedler vec x proprtion DMN
-allSummaries <- do.call(rbind, Summaries)
-allSummaries$SubjID <- rep(subjList, each = nrow(Summaries[[1]]))
-
 # Do a mixed effects GLM (binomial, quasi unavailable on glmer) to estimate the relationship between Fiedler vec and propDMN
@@
 allSummaries$FittedVals <- fitted(SC_FVvPDMN_model)
+
+# Create a smaller dataframe just to plot the fit
+# Otherwise, plotting the thousands fitted can place an unnecessary burden on the document
+# (at some point, knitting to pdf wouldn't show the logistic plot because of this)
+FiedlerVector <- seq(min(allSummaries$FiedlerVec), max(allSummaries$FiedlerVec), length.out = nVertices)
+formula <- SC_FVvPDMN_modelSummary$coefficients[1,1] + (SC_FVvPDMN_modelSummary$coefficients[2,1] * FiedlerVector)
+Fitted_Proportion <- exp(formula) / (1 + exp(formula))
+SC_FVvPDMN_fits <- data.frame(FiedlerVector, Fitted_Proportion)
+rm(FiedlerVector, formula, Fitted_Proportion)
 
@@
 Summaries_halves <- lapply(temp, read.csv)
-selectSubj <- seq(20)
 
 # Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
-# Select a subsection of participants for plotting
-Summaries_halves_plot <- Summaries_halves[selectSubj]
-unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
-unthreshComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
+Summaries_halves_unthresh <- Summaries_halves
+
+# Load the correlation-based maps from each day for analysis in a subsequent section
+temp <- list.files(pattern = "*_corHalves.csv")
+Correlation_halves <- lapply(temp, read.csv, header = F)
 
@@
                   DailyARI = Halves_PFCComparison[[1]])
-best <- tmp %>% top_n(10, wt = DailyARI) %>% arrange(DailyARI)
+best <- tmp %>% top_n(10, wt = DailyARI) 
 bestindx <- substr(subjList_halves,1,6) %in% best$SubjID
@@
 
-# Load the correlation-based maps (this might be ok to move to the cor vs comm chunk)
-temp <- list.files(pattern = "*_corHalves.csv")
-Correlation_halves <- lapply(temp, read.csv, header = F)
-Correlation_halves_plot <- Correlation_halves[bestindx] # CHANGE TO THE ACTUAL SUBJECTS
+# Get the same subsection of participants for the correlation plots
+Correlation_halves_plot <- Correlation_halves[bestindx]
+
+# Save unthresholded subjects for comparing and plotting against correlation maps
+unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_unthresh[bestindx], "[", i = !posteriorIndx, j =)
+unthreshComm_PFC_halves <- lapply(Summaries_halves_unthresh, "[", i = !posteriorIndx, j =)
 ```
@@
 # Change to inflated eventually
-include_graphics("./Images/ROIS2.png")
+include_graphics("./Images/ROIS3.png")
 ```
@@
 ``` {r Partition comparison: all cross-method agreement (Fig.
-3), fig.align="center", fig.width=3.5, fig.height=3.5, echo=FALSE, message = FALSE, cache = TRUE, fig.cap = "Figure 3.
+3), fig.align="center", fig.width=3.5, fig.height=3.5, echo=FALSE, message = FALSE, fig.cap = "Figure 3.
 Distribution of ARI indices when comparing modularity and spectral partitioning.
@@
 Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
-PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE, cache = TRUE}
+PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE}
 par(xpd=T)
@@
 Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right).
-These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE, cache = TRUE}
+These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE}
 # plots
@@
 mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI.
-PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE, cache = TRUE}
+PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE}
 # plot
@@
 Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects).
-The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE, cache = TRUE}
+The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE}
 # plot
@@
 Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions.
-Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE, cache = TRUE}
+Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE}
 ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
@@
 9), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 9.
-ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE, cache = TRUE}
+ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE}
 # TAKE THE TIME TO BRING THE GGPLOT DEFINITION DOWN HERE EVENTUALLY
@@
 
-``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=4, fig.cap = "Figure 10.
+``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 10.
 ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle).
-Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE, cache = TRUE}
+Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE}
 
@@
   geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
-  #geom_point(aes(FiedlerVec, slidePropDMN, fill = SubjID), show.legend = F, alpha = 0.05, pch = 21, color = "black") + 
-  geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
+  #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
+  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
   labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
+  scale_y_continuous(limits = c(0,1)) +
   theme_classic()
@@
 Mean tSNR for mPFC and PCC across participants.
-This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE, cache = TRUE}
+This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE}
 # Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
@@
 Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the lowest tSNR (left).
-However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE, cache = TRUE}
+However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE}
 # grid.arrange(v6, v7, ncol = 2)
@@
 Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector (10 example subjects).
-The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.", echo=FALSE, message = FALSE, cache = TRUE}
+The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.", echo=FALSE, message = FALSE}
 corrplot(allHalfCombs, 

### 2018-12-11 Manuscript.Rmd
Updated meta-analysis and roi plots, now onto correlation vs FV, which shows negative corrs for some reason

@@
 The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
-include_graphics("./Images/newPattern_both.png")
-```
-
-``` {r Partition comparison: all cross-method agreement (Fig.
-3), fig.align="center", fig.width=3.5, fig.height=3.5, echo=FALSE, message = FALSE, fig.cap = "Figure 3.
-Distribution of ARI indices when comparing modularity and spectral partitioning.
-The distribution shows overall high agreement.
-(Will probably remove this figure)"}
-RI_within_plot <- ggplot(data = RI_all_within, aes(Index)) + 
-        geom_density(fill = Cols[3]) + 
-        xlim(0,1) + 
-        labs(x = "Adj. Rand Index") +
-        theme_classic()
-RI_within_plot
+include_graphics("./Images/FB_FV_example.png")
 ```
@@
 
+```
+
+``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 10.
+ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle).
+Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE}
+
+# # plots
+# SC_PCCPFC_plot <- ggplot(data = SC_PCC)
+# SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
+#   geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
+#   ylim(0,1) + 
+#   labs(y = "ARI") +
+#   theme(text = element_text(size=35)) +
+#   geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
+#   geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
+#   theme_classic()
+
+SC_PCCPFC_mean_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=as.factor(Region), y=Index, fill = as.factor(Region))) + 
+  geom_boxplot(show.legend = F) + 
+  scale_fill_manual(values = Cols[seq(2)]) +
+  ylim(0,1) +
+  labs(x = "", y = "") +
+  theme(text = element_text(size=35), axis.text.y = element_text(size=40)) +
+  theme_classic()
+
+SC_PCCPFC_sd_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=SD, fill = as.factor(Region))) + 
+  scale_fill_manual(values = Cols[seq(2)]) +
+  geom_density(color = "black", alpha = 0.7, show.legend = F) + 
+  xlim(0,1) +
+  labs(x = "SD") +
+  theme(text = element_text(size=35)) +
+  theme_classic()
+
+grid.arrange(SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 2)
+
+```
+
+``` {r Stability per subject: Fiedler vector vs prop.
+DMN plot (Fig 11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 11.
+Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
+Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
+# Fiedler Vector x proportion of times a vertex was affiliated with DMN
+SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
+  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
+  #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
+  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
+  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
+  scale_y_continuous(limits = c(0,1)) +
+  theme_classic()
+
+SC_FVvPDMN_plot
 ```
@@
 
-``` {r Stability per subject: Overall (Fig.
-9), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 9.
-ARI between communities computed at each sliding epoch and the original partition for all subjects (left), as well as the distribution of ARI standard deviations per subject (right).", echo=FALSE, message = FALSE}
-# TAKE THE TIME TO BRING THE GGPLOT DEFINITION DOWN HERE EVENTUALLY
-grid.arrange(SC_plot, SC_sd_plot, ncol = 2)
-```
-
-``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 10.
-ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle).
-Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE}
-
-# # plots
-# SC_PCCPFC_plot <- ggplot(data = SC_PCC)
-# SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
-#   geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
-#   ylim(0,1) + 
-#   labs(y = "ARI") +
-#   theme(text = element_text(size=35)) +
-#   geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
-#   geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
-#   theme_classic()
-
-SC_PCCPFC_mean_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=as.factor(Region), y=Index, fill = as.factor(Region))) + 
-  geom_boxplot(show.legend = F) + 
-  scale_fill_manual(values = Cols[seq(2)]) +
-  ylim(0,1) +
-  labs(x = "", y = "") +
-  theme(text = element_text(size=35), axis.text.y = element_text(size=40)) +
-  theme_classic()
-
-SC_PCCPFC_sd_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=SD, fill = as.factor(Region))) + 
-  scale_fill_manual(values = Cols[seq(2)]) +
-  geom_density(color = "black", alpha = 0.7, show.legend = F) + 
-  xlim(0,1) +
-  labs(x = "SD") +
-  theme(text = element_text(size=35)) +
-  theme_classic()
-
-grid.arrange(SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 2)
-
-```
-
-``` {r Stability per subject: Fiedler vector vs prop.
-DMN plot (Fig 11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 11.
-Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
-Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
-# Fiedler Vector x proportion of times a vertex was affiliated with DMN
-SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
-  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
-  #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
-  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
-  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
-  scale_y_continuous(limits = c(0,1)) +
-  theme_classic()
-
-SC_FVvPDMN_plot
-```
-
 ``` {r Noise Effects: tSNR Comparison (Fig.

### 2018-12-13 Manuscript.Rmd
Some daily correlations are negative due to the simplicity of the DMN-pairing heuristic. This affects Corr vs FV even if the maps look great across days. I added code to identify individuals with negative cross-day correlations to examine later.

@@
 
+# Some participants have strongly uncorrelated maps because 7m isn't fully covered on one of the days
+# ARI doesn't mind this, so the results are fine
+# But the Corr vs FV analysis below is badly affected
+# For now I'm just selecting the individuals that have negatively correlated FVectors
+# It might be worth visually inspecting each to see if a simple heuristic works (i.e. if corr < -0.5, then FV * -1 & 1 - FB)
+# Although this doesn't adress which half is the culprit
+unCorrParticipants <- data.frame(SubjID = subjList,
+                                 Corrs = sapply(seq(1, nSubj *2, by = 2), function(x) {cor(Summaries_halves_unthresh[[x]]$FiedlerVec, Summaries_halves_unthresh[[x+1]]$FiedlerVec)})) %>%
+  filter(Corrs < 0)
+
 # Load the correlation-based maps from each day for analysis in a subsequent section

### 2018-12-14 Manuscript.Rmd
Corr vs FV in manuscript fixed
The problem with reversed labeling is fixed, so the correlation vs FV analysis chunk now looks fine

@@
 # Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
+# Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we're manually reverting it after visual inspection
+revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "120515_H2", "108525_H2", "156637_H1", "156637_H1")
+for (subj in revertSubjs) {
+  indx <- grep(subj, subjList_halves)
+  Summaries_halves[[indx]] <- transform(Summaries_halves[[indx]], FiedlerVec = FiedlerVec * -1)
+}
 Summaries_halves_unthresh <- Summaries_halves
@@
 # Save unthresholded subjects for comparing and plotting against correlation maps
+# this comment is temporary, just to force the cache to update
+Foo <- "Fighters"
 unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_unthresh[bestindx], "[", i = !posteriorIndx, j =)
@@
 ## Between halves analysis for correlation and communities (mPFC only)
+Foo <- "Fighters"
 unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
@@
 # Compare correlation with community approach on mPFC
+Foo <- "Fighters"
 tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
@@
 We then performed pairwise spatial Pearson correlations among maps computed for each day and method from all subjects (Figure 15).
+For `r nrow(unCorrParticipants %>% filter(Corrs < 0))` subjects, the maps produced with one of the days' datasets insufficiently covered area 7m, and so the community labeling was reversed (for one additional subject, both daily maps were reverted).
+ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topology was highly similar.
+We thus visually inspected these subjects and reverted the labeling when it was clear that the topologies aligned across days (n = 8).
 
@@
 The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.", echo=FALSE, message = FALSE}
+Foo <- "Fighters"
 corrplot(allHalfCombs, 

### 2018-12-15 Manuscript.Rmd
removed the v4 plot, and updated ARI ratio stats to medians

@@
 Summaries <- lapply(temp, read.csv)
+nSubj <- length(Summaries)
 nVertices <- nrow(Summaries[[1]]) # in case I need the number of vertices included per brain
@@
 # Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we're manually reverting it after visual inspection
-revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "120515_H2", "108525_H2", "156637_H1", "156637_H1")
+revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1", "156637_H1")
 for (subj in revertSubjs) {
@@
 # Stats
-Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T)
+Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T, statType = median)
 Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
@@
 Therefore, we divided each subject's ARI between days by the ARI values with the days from the other subjects.
-This ratio denotes the relative specificity of their partition.
-That means, partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
+This ratio denotes the relative specificity of their partition, such that partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
 Figure 6 shows the ratios for PCC and mPFC for all subjects.
 As expected, we found that while both regions had good specificity (i.e.
-ratios > 1), the ratios for PCC were significantly lower than mPFC (paired permutation,*p*= `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r Halves_mPFCvPCC_ES`).
+ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PFC), digits = 2)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PCC), digits = 2)`) *CONSIDER IQR INSTEAD OF MEANS/SD* when compared with a paired permutation test (*p* = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
 These test/retest results suggest that the topographic varability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
@@
 # Stats
-Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T)
+Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T, statType = median)
 Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
@@
 ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topology was highly similar.
-We thus visually inspected these subjects and reverted the labeling when it was clear that the topologies aligned across days (n = 8).
+We thus visually inspected these subjects and reverted the labeling when it was clear that the topologies aligned across days (n = 7).
 
@@
 The figure shows that PCC vertices tend to be more coupled with the overall dynamics of DMN across subjects.", echo=FALSE, message = FALSE}
-v4
+#v4
 ```

### 2019-01-12 Manuscript.Rmd
More detailed abstract

@@
 However, little is known about how valuation effects fit within the broader functional architecture of mPFC and PCC, or whether that architecture is consistent or idiosyncratic across individuals.
-Here we complement a meta-analysis with fMRI-based graph theoretic approaches to subdivide mPFC and PCC at the single-subject level.
-Our results suggest the functional topography of mPFC has substantial variability across individuals.
-This highlights the potential usefulness of estimating brain effects at the individual level in this region, and points to limitations of aggregative methods such as coordinate-based meta-analysis in determining whether valuation and DMN effects emerge from common or separable brain systems.
-Our approach shows promise in addressing this issue through future manipulations of valuation.
+Here we complement a meta-analysis with fMRI-based graph-theoretic approaches on functional connectivity to subdivide mPFC and PCC at the single-subject level.
+Our results show that valuation and DMN effects had substantial meta-analytic overlap in mPFC and PCC.
+However, the regions of group-level overlap could be reliably segregated into two communities in every individual (n = 100).
+This subdivision had low inter-individual alignment despite sharing qualitative topological features similar to those found by Braga and Buckner (2017).
+Using measures that correct for chance clustering, we found that (1) different graph-theoretic clustering algorithms strongly agree in this partition; (2) each individual’s network arrangement was more similar across their own fMRI sessions than across subjects; (3) this idiosyncrasy was higher for mPFC; and (4) the idiosyncratic functional topography was not merely the result of measurement noise.
+We also show the advantages of graph-theoretic approaches over traditional seed-based functional connectivity for single-subject analysis.
+This work highlights the potential usefulness of estimating brain effects at the individual level in these regions, and points to limitations of aggregative methods in determining the degree of neural overlap between DMN and valuation.
+Future behavioral manipulations will examine whether the two sub-networks are better understood as subdivisions of the DMN or as segregating DMN from non-DMN regions.
 

### 2019-01-25 Manuscript.Rmd
Reshaping the manuscript so that thresholded maps play a big role

--- 2018-12-15 Manuscript.Rmd
@@
 ---
-title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
-author: "Claudio Toro-Serey^1^ & Joseph T. McGuire^1^"
+title: 'Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex '
+author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
 output:
@@
 More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017].
-These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system.
+These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same neural system.
 However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area [@Kragel2018].
@@
 Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject.
-However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013a] compared to the rest of the brain, thus making group-averaging studies difficult to interpret.
+However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013a], thus making group-averaging studies difficult to interpret.
 
@@
 In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix).
-The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e.
+The resulting eigenvector corresponding to the second-lowest eigenvalue (i.e.
 the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003].
@@
 
-  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals.
-This description will allow researchers to generate more precise topographic targets for future studies of decision making.
+  In this study, we aimed to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals.
 We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
 First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas [@Glasser2016].
-We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning.
-The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.
-Finally, we show some interesting properties of SP related to the stability of brain networks.
+We then produce a rsFC networks of all the surface vertices within these ROIs for each of 100 individual resting state dataset from the Human Connectome Project (HCP)[@VanEssen2012], and estimate the extent of DMN coverage through spectral partitioning.
+Our results suggest the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects.
+These sub-networks resembled an organizational scheme recently observed in a handful of subjects (Braga & Buckner, 2017).
+We also show that graph theoretic tools are capable of identifying these sub-networks in isolated individuals.
+Our work highlights the usefulness of estimating brain effects at the individual level in these regions, and points to limitations of aggregative methods in determining the degree of neural overlap between DMN and valuation.
 
@@
 These represent the surviving areas post-statistical thresholding from each study.
-For each peak volumetric coordinate, 10 mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer.
-The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (360 regions)[@Glasser2016].
+For each study, each peak volumetric coordinate was mapped onto a 1mm standard space (MNI152) using AFNI's 3dcalc (CITATION).
+We then generated 10mm speheres at these points with FSL's fslmaths (CITATION), and then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf (CITATION).
+The sphere sections that overlapped with the cortex were mapped to an atlas of the human cortical surface (360 regions)[@Glasser2016].
 This produced a list of standardized parcels that were reported on each study.
 
+<!-- 
 With these lists, we identified the areas that were more consistently shared between DMN and valuation.
@@
 Regions of interest were then determined based on which of the remaining regions were common across literatures.
-
-Next, we identified areas that were solely related to either literature.
-We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al.
-[-@Yeo2011].
+-->
+
+With these lists, we identified areas that were significantly more associated to either literature.
+We limited the search space to the parcels that were contained within the medial portion of the DMN parcellation defined by Yeo et al.
+[-@Yeo2011], as it broadly encompassed our a priori domain of interest.
 We permuted the label of every study (i.e.
-DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a area-wise chi-squared test of proportions on the number of permuted studies that had reported each area.
-This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.
+DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic from chi-squared tests of proportions that compared the number of studies that contained each area.
+This gave us a null distribution of 5000 chi-squared values.
+We then used the 95th percentile of this distribution as a significance threshold to evaluate the chi-squared values produced by comparing the actual rates of reporting of each area between literatures.
+The resulting ROIs contained two spatially discontiguous regions (Figure 1), which we label PCC and mPFC for further analyses.
 
@@
 
-In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP) [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
+In order to quantify the resting connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
 Each subject's data was acquired over two days at Washington University in St.
@@
 Next, we applied Fisher's r to z transformation, and took the exponential of these values so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
-As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Evaluation for more details).
+As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).
 
@@
 clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003].
-First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,319).
+First, each network was represented as an $n$ x $n$ matrix of previously adjusted correlation values (where $n$ = number of vertices within the ROIs, 5,319).
 This matrix was then transformed into its normalized Laplacian form
@@
 Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its correlations with every other vertex), and $W$ is the correlation matrix.
+the sum of its correlations with every other vertex), and $W$ is the adjusted correlation matrix.
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
-This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975].
+This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975].
 Given that this data-driven method is agnostic to the prevalent function of each community (i.e.
-DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects).
+DMN or not DMN), we defined the DMN community as the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects).
 Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].
 
-In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization using the algorithm from Clauset et al.
+In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al.
 [-@Clauset2004].
 This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
-The method heuristically iterates through many possible combination of vertices, and selects the clustering that maximizes the network's modularity.
+The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.
 Thus, unlike SP, modularity can fractionate a network into many functional groups.
-If the partitions from the bounded and unbounded methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
+If the partitions from the bounded and unbounded community detection methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
 
@@
 Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group.
-We then estimate the level of agreement between scans taken across days (i.e.
+We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise RI comparisons across subjects.
+Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we perform the following analyses on PCC and mPFC separately.
+
+To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting organization against the clustering derived from the whole subject's data.
+Given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise.
+In that regard, and consdiering the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we also examined the relationship between the magnitude of Fiedler vector values with the proportion of times a vertex was part of the DMN community across windows.
+To do this, we performed a mixed effects logistic regression model, with subject as a mixed effect and vertex-wise eigenmap values (derived from their full dataset) as fixed predictors on the proportion of times each vertex participated in the DMN community.
+Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time.
+These thresholds allowed us to produce individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.
+
+We then estimated the level of agreement between scans taken across days (i.e.
 pairs of daily left-right and right-left phase encoding sessions).
 If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement for the same subject across days than either day compared to every other subject.
+We tested this idea by computing the ratio of the mean RI within and between subjects.
+Ratios close to one denoted good alignment across subjects, while ratios significantly higher than one suggested that partitions per subject were more stable than what you would expect against every other subject.
 We then extend this idea by computing the overall agreement across all sessions.
-Similarly, we expect that sessions within subject will show higher agreement than between subjects.
-Finally, we perform a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37) 8) comparing each window's functional pattern against the clustering derived from the whole subject's data.
-This approach should give us a sense of the dynamics of the functional organization of mPFC during rest.
-We complement this analysis by calculating the proportion of times each surface vertex was affiliated with the DMN community across time, as well as computing the flexibility of each node (i.e.
-the number of times each vertex changed affiliation across time).
-Given that the functional heterogeneity of brain areas is unevenly distributed across the brain [@Mueller2013a], we also performed these comparisons for PCC and mPFC separately.
+Similar to the day-to-day analysis, we expect that sessions within subjects will show higher agreement than between subjects.
 Given what we know about these general regions, we expected PCC to be well aligned across participants, and stable within subjects.
 On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject.
-We compared the agreement within subjects against across subjects by computing the ratio of the mean RI within and between subjects.
-Ratios close to one denote good alignment across subjects, while ratios significantly higher than one suggest that partitions per subject were more stable than what you would expect against every other subject.
-
-Given the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we tested the association of their absolute magnitude with the proportion of times a vertex was part of the DMN community during the sliding window analysis.
-To do this, we performed a mixed effects logistic regression model in which each subject's eigenmap values were used as random predictors of the proportion of times they participated in the DMN community.
 
@@
 We then spatially correlated (Pearson) the $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices.
-*(PERONSAL NOTE: THIS IS NOW DONE BY CONCATENATING ALL SUBJECTS.
-IT WOULD PERHAPS BE BETTER TO DO A MIXED EFFECTS MODEL WITH SUBJECTS AS RANDOM EFFECTS, AND TSNR AS A FIXED ONE)*
 
@@
 
-We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions across DMN and SV literatures (see Methods).
+We performed a coordinate-based meta-analysis to identify unique standard regions across DMN and SV literatures (see Methods).
 Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
+The areas considered were limited to the medial portion of the DMN, as defined by Yeo et al.[-@Yeo2011].
+Unique areas were identified by permuting the affiliation of each study (i.e.
+DMN or SV) to create a null distribution of chi-squared statistics, which was used to identify regions more often reported in either literature.
+Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
+Figure 1 shows the resulting ROIs from these analyses. Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, *p* < 0.001).
+
+<!--
 Using each literature's mean number of reports per area as the null probability (DMN = `r BD`, 95% CI [`r BDquant`]; SV = `r BV`, 95% CI [`r BVquant`]), one-way chi-squared tests of proportions were performed to identify regions that were significantly present in their respective literatures.
@@
 Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
-
-Figure 1 shows the resulting ROIs from these analyses.
 DMN included `r length(t2)` significant regions, while SV was comprised of `r length(t1)` (see Supplemental Table 1).
@@
 A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function.
-Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, *p* < 0.001).
+-->
 
@@
 Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
-This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs Since this is a data-driven approach, there is no a priori labeling for these communities.
+This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs.
+Since this is a data-driven approach, there is no a priori labeling for these communities.
 We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects.
@@
 
-The distribution suggests that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
+This comparison showed that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
 The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not.

### 2019-01-30 Manuscript.Rmd
Reshaping the paper with current data

@@
 We limited the search space to the parcels that were contained within the medial portion of the DMN parcellation defined by Yeo et al.
-[-@Yeo2011], as it broadly encompassed our a priori domain of interest.
+[-@Yeo2011], as it broadly encompassed our a priori domain of interest (25 parcels across hemispheres).
 We permuted the label of every study (i.e.
@@
 
-To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,081 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
+To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
 This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
@@
 clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003].
-First, each network was represented as an $n$ x $n$ matrix of previously adjusted correlation values (where $n$ = number of vertices within the ROIs, 5,319).
+First, each network was represented as an $n$ x $n$ matrix of previously adjusted correlation values (where $n$ = number of vertices within the ROIs, 4,801).
 This matrix was then transformed into its normalized Laplacian form
@@
 BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis].
-It was thus important to quantify the potential influence of noise in our findings.
+Even though we made attempts to remove clear sources of noise through data preprocessing and stability analyses, it was still important to quantify the remaining potential influence of noise in our findings.
 We examined this through two complementary steps.
@@
 
-# Permutation analysis
-# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
-# Load the coordinates as studies in a list, because for the contrast the studies are permuted
-# Use table(unlist(list)) to get the counts in that case
+# # Permutation analysis
+# # Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
+# # Load the coordinates as studies in a list, because for the contrast the studies are permuted
+# # Use table(unlist(list)) to get the counts in that case
 # setwd('./DEC')
@@
 # significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))
+
+# results!
+# s32 (prportion sv = 0.6; proportion DMN = 0.2, Chi = 11.95, p < 0.01)
+# 7m (prportion sv = 0.07; proportion DMN = 0.4, Chi = 8.45, p < 0.05)
+# null chi <- 8.4
 
@@
 Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
-The areas considered were limited to the medial portion of the DMN, as defined by Yeo et al.[-@Yeo2011].
+The 25 areas considered were limited to the medial portion of the DMN, as defined by Yeo et al.[-@Yeo2011].
 Unique areas were identified by permuting the affiliation of each study (i.e.
@@
 Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
-Figure 1 shows the resulting ROIs from these analyses. Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, *p* < 0.001).
+
+Figure 1 shows the resulting ROIs from these analyses.
+The 95th percentile of the permuted Chi-squared distribution was 8.4.
+Based on this threshold, area 7m was the only one to show unique affiliation to DMN (observed $\chi^2$ = 8.45, *p* < 0.05), while SV was uniquely represented by area s32 (observed $\chi^2$ = 11.95, *p* < 0.01).
 
@@
 *NOTE: It might be better to just avoid cluster comparisons at this pre-threshold level*
-With these 16 ROIs (15 overlapping, 1 DMN-specific), we estimated each individual's DMN coverage using the whole time series (4800 total TRs from four scanning sessions over two days).
-Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nrow(Summaries[[1]])` total vertices).
+With these 25 ROIs (23 overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using the whole time series (4800 total TRs from four scanning sessions over two days).
+Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices).
 After correcting for multiple testing, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
@@
 This non-DMN section extends posteriorly onto pregenual cinglate cortex.
-Note that vmPFC does not encompass area a25, which is often related to negative emotional valuation [@Joyce2018].
 Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than SV [@Hiser2018].

### 2019-02-05 Manuscript.Rmd
Done with methods draft

@@
 Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its correlations with every other vertex), and $W$ is the adjusted correlation matrix.
+the sum of its correlation values with every other vertex), and $W$ is the adjusted correlation matrix.
+This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal.
+This transormation ensures that every row adds up to zeo.
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
@@
 Given that this data-driven method is agnostic to the prevalent function of each community (i.e.
-DMN or not DMN), we defined the DMN community as the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects).
+DMN or not DMN), we defined the DMN community to be the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects).
 Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].
@@
 Thus, unlike SP, modularity can fractionate a network into many functional groups.
-If the partitions from the bounded and unbounded community detection methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
+We assumed that if the partitions from the bounded and unbounded community detection methods show high level of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
 
@@
 clustered together on A, but separately on B).
-Because of this, the adjusted rand index determines the percentage of agreement between any two partitions while being agnostic to the labeling scheme.
+Therefore, the adjusted rand index determines the percentage of agreement between any two partitions while being agnostic to the labeling scheme.
 The resulting ratio is compared to a baseline given by the expectation of a random node assignment across partitions.
@@
 Their alignment would thus give us confidence in the validity of the resulting topologies.
-Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group.
+Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean ARI for the group.
 We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise RI comparisons across subjects.
-Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we perform the following analyses on PCC and mPFC separately.
-
-To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting organization against the clustering derived from the whole subject's data.
+Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all the subsequent analyses on PCC and mPFC separately.
+
+To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the clustering derived from the whole subject's data.
 Given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise.
@@
 Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time.
-These thresholds allowed us to produce individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.
+These thresholds yielded individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.
 
@@
 We tested this idea by computing the ratio of the mean RI within and between subjects.
-Ratios close to one denoted good alignment across subjects, while ratios significantly higher than one suggested that partitions per subject were more stable than what you would expect against every other subject.
+Ratios close to one denoted good alignment across subjects, while ratios significantly higher than one suggested that partitions within a subject were more stable than what you would expect against every other subject.
 We then extend this idea by computing the overall agreement across all sessions.
-Similar to the day-to-day analysis, we expect that sessions within subjects will show higher agreement than between subjects.
-Given what we know about these general regions, we expected PCC to be well aligned across participants, and stable within subjects.
+Similar to the day-to-day analysis, we expect that sessions within subjects would show higher agreement than between subjects.
+Given what we know about these general regions, we expected PCC to be fairly well aligned across participants, and stable within subjects.
 On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject.
@@
 BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis].
-Even though we made attempts to remove clear sources of noise through data preprocessing and stability analyses, it was still important to quantify the remaining potential influence of noise in our findings.
+Even though we made attempts to remove clear sources of noise through data preprocessing and stability analyses, it was still important to quantify the remaining potential influence of structured noise in our findings.
 We examined this through two complementary steps.
-First, we computed the temporal signal-to-noise ratio (tSNR) of all the vertices in the ROIs from HCP minimally preprocessed data (i.e.
+First, we computed the temporal signal-to-noise ratio (tSNR) of all the vertices in the ROIs from the HCP minimally preprocessed data (i.e.
 prior to the complementary denoising described in the "fMRI Data" section).
 We compared the mean tSNR for each region across subjects through a permutation analysis (all permutation analyses involved 5000 iterations).
-In addition, we compared the mean tSNR between mPFC and PCC through a permutation analysis for each separate subject, and report the percentage of subjects who had a significantly lower mean tSNR in mPFC after FDR correction for multiple testing [@Benjamini2001].
-Next, we estimated which vertices within mPFC had a stronger relationship to the overall dynamics of DMN.
-To do this, we computed the mean time series of each subject's estimated DMN map, which was then predicted by the time series each mPFC vertex in a mass univariate analysis.
+In addition, we compared the mean tSNR between mPFC and PCC through a permutation analysis for each separate subject, and report the percentage of subjects who had a significantly lower mean tSNR in mPFC (post FDR correction for multiple testing [@Benjamini2001]).
+
+Next, we examined whether a vertex's affiliation to the DMN community was driven by its tSNR.
+First, we computed the mean time series of each subject's DMN community.
+We then performed a mass univariate analysis to predict the average time series from each individual vertice's time series.
 The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex.
 If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects.
-We then spatially correlated (Pearson) the $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices.
+We then spatially correlated (Pearson) each subject's $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices, and report the mean correlation across subjects.
 
@@
 
-A potential downfall of the present approach is that it can be computationally demanding, while more direct seed-based functional connectivity methods could provide sufficient approximations of an individual's DMN orgnization.
-We examined this issue by estimating mPFC functional maps from its vertex-wise functional coupling with the mean PCC activation.
-For each subject's concatenated day 1 and day 2 scans, we computed the mean time series of all vertices contained within the PCC region of a standard DMN arrangement [@Yeo2011], and correlated it (Pearons) with the time series of every mPFC vertex from our ROIs.
-The resulting day 1 and day 2 mPFC maps were then correlated within and between subjects in three ways: 1) between correlation-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps.
-These spatial correlations are aimed to determine the day-to-day stability of each approach, as well as their level of agreement.
-These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for example, see [@Kong2018; @Mueller2013a]).
+A potential downfall of our approach lies in whether the considerable computational demands are indeed required to identify these individualized partitions.
+It is possible that careful seed-based functional connectivity could provide sufficiently stable approximations of an individual's DMN arrangement.
+Given the high variability and idiosyncrasy of mPFC (see Results), we examined if SP could capture more reliable maps than seed-based functional connectivity in this area.
+First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average PCC activity for each day separately.
+We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps.
+These spatial correlations were aimed to determine the day-to-day stability of each approach, as well as the overall level of agreement between them.
+These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]).
 We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
 
+The thresholded partitions in our work qualitatively resembled the topographical arrangement of networks A and B defined by Braga and Buckner [-@Braga2017].
+We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
+In their work, Braga and Buckner selected individual vertices along the dorsolateral prefrontal cortex (DLPFC) that produced these two anticorrelated networks.
+Therefore, we hypothesized that if the communities we identified on the medial wall match their proposed networks, we should be able to find seed vertices in DLPFC that can reproduce them.
+The whole-brain seed-based functional connectivity maps for these subjects were qualitatively compared to those produced by spectral partitioning.
+
 ### *Anatomical Correspondence*
@@
 Finally, we examined whether each idiosyncrasies in functional topology corresponded to outstanding anatomical features.
-To do this, we correlated each subject's Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex).
+To do this, we correlated each subject's thresholded Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex).
 These simple correlations are aimed to provide a coarse sense of this possible relationship, which can be studied in depth in the future.

### 2019-02-05 Manuscript.Rmd
up to results section 2

@@
 A potential downfall of our approach lies in whether the considerable computational demands are indeed required to identify these individualized partitions.
-It is possible that careful seed-based functional connectivity could provide sufficiently stable approximations of an individual's DMN arrangement.
+It is possible that regional seed-based functional connectivity could provide sufficiently stable approximations of an individual's DMN arrangement.
 Given the high variability and idiosyncrasy of mPFC (see Results), we examined if SP could capture more reliable maps than seed-based functional connectivity in this area.
@@
 
-We performed a coordinate-based meta-analysis to identify unique standard regions across DMN and SV literatures (see Methods).
+We performed a coordinate-based meta-analysis to identify unique standard regions across DMN and SV literatures.
 Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
 The 25 areas considered were limited to the medial portion of the DMN, as defined by Yeo et al.[-@Yeo2011].
-Unique areas were identified by permuting the affiliation of each study (i.e.
-DMN or SV) to create a null distribution of chi-squared statistics, which was used to identify regions more often reported in either literature.
+Unique areas were identified by first permuting the affiliation of each study (i.e.
+DMN or SV) to create a distribution of Chi-squared statistics based on the comparison of the number of reports per area between literatures (see Methods for details).
+This putative null distribution was used to identify regions more often reported in either literature.
 Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.

### 2019-02-08 Manuscript.Rmd
Almost done with results draft. Need to add B&B comparison

@@
 
+All network analyses were performed using the igraph package (CITE) in R 3.4.1.
 To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
@@
 This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal.
-This transormation ensures that every row adds up to zeo.
+This transormation ensures that every row adds up to zero.
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
@@
 To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the clustering derived from the whole subject's data.
-Given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise.
+The length of the windows is well equipped to find stable community features in brain networks [@Gordon2017].
+In addition, given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise.
 In that regard, and consdiering the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we also examined the relationship between the magnitude of Fiedler vector values with the proportion of times a vertex was part of the DMN community across windows.
 To do this, we performed a mixed effects logistic regression model, with subject as a mixed effect and vertex-wise eigenmap values (derived from their full dataset) as fixed predictors on the proportion of times each vertex participated in the DMN community.
-Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time.
+Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time (all other values were turned into zeros).
+Individuals without such stable nodes were not thresholded, but their maps were not discarded.
+Values in the eigenvector maps that did not meet threshold were set to zero, and set to 0.5 during binarization so that they would not bias the mean estimates across subjects.
 These thresholds yielded individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.
@@
 
+### *Anatomical Correspondence*
+
+Finally, we examined whether each idiosyncrasies in functional topology corresponded to outstanding anatomical features.
+To do this, we correlated each subject's thresholded Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex).
+These simple correlations are aimed to provide a coarse sense of this possible relationship, which can be studied in depth in the future.
+
+\bigskip
+
 ### *Seed-based FC vs Community Detection*
@@
 The whole-brain seed-based functional connectivity maps for these subjects were qualitatively compared to those produced by spectral partitioning.
-
-### *Anatomical Correspondence*
-
-Finally, we examined whether each idiosyncrasies in functional topology corresponded to outstanding anatomical features.
-To do this, we correlated each subject's thresholded Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex).
-These simple correlations are aimed to provide a coarse sense of this possible relationship, which can be studied in depth in the future.
 
@@
 
-*NOTE: It might be better to just avoid cluster comparisons at this pre-threshold level*
-With these 25 ROIs (23 overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using the whole time series (4800 total TRs from four scanning sessions over two days).
+With these 25 ROIs (23 overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using their full time series (4800 total TRs from four scanning sessions over two days).
 Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices).
-After correcting for multiple testing, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
+After correcting for multiple comparisons, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
 On average, networks had high densities (i.e.
@@
 In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment.
-mPFC, on the other hand, is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them.
-This non-DMN section extends posteriorly onto pregenual cinglate cortex.
-Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than SV [@Hiser2018].
+On the other hand, mPFC is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them.
+This non-DMN section extends posteriorly onto pregenual cinglate cortex (area a24).
+Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than subjective value [@Hiser2018].
 
@@
 Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model.
-Since modularity is agnostic to the desired number of clusters, it was capable of finding more than two communities in our datset.
-Thus, if both methods agreed in the number and topological organization of the current communities, it would add confidence to our results.
+Since modularity is not bound to a desired number of partitions, it was capable of finding more than two communities in our datset.
 We quantified the cross-method agreement with the adjusted rand index (ARI).
-ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g.
-clustered together in partition 1, but separately in 2).
+ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes.
 This measure has the benefit of being agnostic to labeling schemes, as well as controlling for the expectation that the clusters were randomly produced [@Hubert1985].
 This means that positive ARI values compare favorably against chance clustering.
-Figure 3 shows the distribution of ARI values comparing topologies produced by modularity and spectral partitioning across subjects.
 
@@
 The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not.
-This adds evidence to the division of these areas into DMN and non-DMN during rest.
-
-Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was considerable agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
-However, qualitative inspection of the brain community topologies shows good alignment for PCC, with a topologically similar mPFC pattern that shifts topographically across subjects.
-To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 4).
-Indeed, this analysis showed that the functional topology of PCC is well maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), while mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) showed significantly lower levels of agreement (paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+This adds support to the division of these areas into DMN and non-DMN during rest.
+Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.
+
+Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was fairly low agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+However, qualitative inspection of the brain community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects.
+To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3).
+Indeed, this analysis showed that the functional topology of PCC is better maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`)(paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
 
@@
 
-While the distinction of DMN and non-DMN is consistent across session and days, it is possible that the decrease in global ARI values going from full to session-specific data could be due to a dynamic shift in DMN organization.
-In order to address this possibility, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the original pattern estimated using the whole time series (Figure 9).
-Note that the length of the windows is well equipped to find stable community features in brain networks [@Gordon2017].
-This analysis revealed persistently high levels of agreement for most subjects, with overall low variability (overall mean of each subject's average ARI = `r round(mean(SC_summary$RI), digits = 2)`; SD = `r round(mean(SC_summary$SD), digits = 2)`).
+In order to address this the degree of stability of these partitions in time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the original pattern estimated using the whole time series (Figure 4).
 
@@
 
-We additionally performed this analysis on mPFC and PCC separately to determine whether these results were region-specific (Figure 10).
-Even though the within-subject variance remained low for both regions, we found that the average agreement per subject was significantly higher for PCC (paired permutation,*p*= `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
-Nonetheless, the mean ARI across each subject's time series was still relatively high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), thus suggesting that the each individual's DMN distribution is cosiderably stable in time.
-
-We complemented these analyses by asking whether the magnitude of values in the Fiedler vector was associated with the stability of nodes throughout a subject's time series (*PERSONAL NOTE: It might be better to justify this from the use of this vector in statistical mechanics rather than mere curiosity, i.e.
-extreme FV values are given to elements at the peaks of the wave.
-Find a simple citation for this.*).
-Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model, with subject acting as a random effect (Figure 11).
+This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation,*p* = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+These results suggest that the each individual's DMN distribution is cosiderably stable in time.
+
+There is precedence in thhe literature that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Tian2018](**add another citation, like the global map paper**).
+Therefore, we asked whether the magnitude of these eigenvector values was associated with the stability of nodes in time.
+Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model (Figure 5).
 The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time.
-These analysis show that the original pattern identified with the full dataset is temporally stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN vertices in relatively short fMRI sessions (i.e.
-less than 20 mins).
-
-\bigskip
-
-### *Thresholding*
+We refer to this proportion of affiliations over time as the stability of a given node.
+
 ``` {r Threshold this stupid stuff}
@@
   if (is.null(tempList[[i]]$result)) {
+    # if there wass no clear threshold (i.e. noisy participants), then leave it as 0
     threshDF[i,2:3] <- c(0,0)
@@
 
-```
+# get descriptives
+threshDescriptives <- threshDF %>% 
+                        filter(Lower < 0, Upper > 0) %>% 
+                        summarize(mL = mean(Lower), 
+                                  sdL = sd(Lower), 
+                                  mU = mean(Upper), 
+                                  sdU = sd(Upper)) %>% 
+                        round(., digits = 4)
+
+rm(tempList)
+
+```
+
+These analyses show that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN and non-DMN vertices, even in relatively short resting fMRI sessions (i.e.
+less than 20 mins).
+We therefore thresholded each subject's Fiedler vector to produce these refined maps.
+We estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 95%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
+Vertices that under these thresholds were set to zero (instead of removed) so that the dimensionality of the data was unaffected, and 0.5 in the binarized maps so that they wouldn't bias the calculation of averages.
+Figure 6 (left) shows the updated partition for the one showed in figure 2.
+The maps used in all subsequent analyses were thresholded by this individualized criterion.
 
@@
 # Apply threshold to Summaries
+# IMPORTANT: THIS PROCESS OVERWRITES THE VARIABLES FROM THE FIRST COMPARISON SECTION
+# THIS IS DONE FOR STORAGE-SAKE, BUT IT MIGHT BE WORTH GIVING THESE TEIR OWN NAME
 if (threshMaps) {
@@
 ```
+
+With these thresholded maps, we recomputed the overall similarity of their functional organization across participants.
+Compared to before, there was even less overall agreement of the full maps among individuals (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+Figure 6 (right) shows the spatial average of the thresholded binarized partitions across all participants, denoting the proportion of times a vertex was affiliated with the DMN community.
+This summary conveys a common organizational principle for both communities, but also highlights the considerable variability across individuals in mPFC compared to PCC.
+
 ### *Partition Comparison: Day 1 vs Day 2*
 
-In order to determine whether the low agreement shown in mPFC across subjects was a function of intrinsic variability or a subject-specific pattern, we compared the agreement among communities estimated with data from each separate day.
-If the latter were true, within-subject ARI values should be consistently higher than across subjects.
-Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.
-Communities were estimated on concatenated pairs of daily left-right and right-left phase encoded sessions (see Methods for details), and once again compared using ARI.
-Figure 5 shows pairwise comparisons among ten example subjects for PCC and mPFC separately.
+The relative high variability seen in the aggregate map could be due to residual noise that was not captured by the sliding window analysis, or variations in the functional organization of mPFC across days.
+While the sliding window analysis suggested that these partitions are stable, many of the windows contained data from both days.
+A stricter evaluation of subject-specificity would be to compare every subject's subdivisions produced by data from each day separately.
+If the variability that we observed was truly due to having captured an individual's unique organization, day to day ARI values should be consistently higher within- than between-subjects.
+Figure 7 shows pairwise comparisons among ten example subjects for whole brain (left), as well as PCC/mPFC separately (right).
 
@@
 
-Once again we found greater alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) than mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed higher levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
+Once again we found low alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) and mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed relatively high levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
 However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic.
-Therefore, we divided each subject's ARI between days by the ARI values with the days from the other subjects.
-This ratio denotes the relative specificity of their partition, such that partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios.
-Figure 6 shows the ratios for PCC and mPFC for all subjects.
+Therefore, we divided everyone's within-subject ARI by the mean ARI of their between-subject comparison.
+This ratio denotes the relative specificity of their partition, such that partitions that align well across subjects should yield ratios close to 1, while unique and stable partitions would produce high ratios.
+Figure 8 shows these ARI ratios for PCC and mPFC for all subjects.
 As expected, we found that while both regions had good specificity (i.e.
-ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PFC), digits = 2)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PCC), digits = 2)`) *CONSIDER IQR INSTEAD OF MEANS/SD* when compared with a paired permutation test (*p* = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
-These test/retest results suggest that the topographic varability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
-
-### *Partition Comparison: Session*
+ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PFC), digits = 2)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PCC), digits = 2)`) when compared with a paired permutation test (*p* = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
+These test/retest results suggest that the topographic variability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
+
+### *Partition Comparison: Session based*
 
@@
 
-Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 7), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 8).
+Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 8), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 9).
 
@@
 
-### *Potential Noise Effects (this part is challenging)*
+### *Potential Noise Effects*
+
+*NOTE: this part seems less relevant now that we are thresholding the partitions. Might be better to add to sliding window section*
 
@@
 # Are vertices with lower SNR switching communities more often?
+# This is pointless if thresholded maps are used, since flexibility is bound to be super low 
 SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))
 
-# Compare SNR between PCC and mPFC per subject
-SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval)
+# Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
+tempComm_PCC <- lapply(tempComm_PCC, function(data) {data %>% filter(FiedlerVec != 0)})
+tempComm_PFC <- lapply(tempComm_PFC, function(data) {data %>% filter(FiedlerVec != 0)}) 
+SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) {permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval})
 SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
-SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff))
-prcntSig <- (sum(SNR_PCCvsPFC_perm < 0.05) / nSubj) * 100
+SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) {cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)})
+prcntSig <- mean(SNR_PCCvsPFC_perm < 0.05) * 100
 
 # Get the mean SNR for each region and compare overall levels 
-SNR_meanPCC <- sapply(tempComm_PCC, function(data) mean(data$varCoeff))
-SNR_meanPFC <- sapply(tempComm_PFC, function(data) mean(data$varCoeff))
+SNR_meanPCC <- sapply(tempComm_PCC, function(data) {mean(data$varCoeff)})
+SNR_meanPFC <- sapply(tempComm_PFC, function(data) {mean(data$varCoeff)})
 SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
@@
 
-Even though our findings point to a stable representation of each subject's unique DMN organization, it is still possible that they were affected by considerable levels of signal noise often found in mPFC (its ventral segment in particular).
-As a first step to account for this, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
-mean of each vertex's time points over their standard deviation).
-The tSNR of all vertices were averaged per region and subject (Figure 12), which showed that indeed mPFC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`) was overall noisier than PCC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`) across subjects (permutation, *p* = `r SNR_meanComp$Comparison`, Cohen's D = `r round(SNR_meanComp$ES, digits = 2)`).
-To more precisely examine this difference, we performed subject-wise comparisons of the tSNR values of all vertices between PCC and mPFC (total `r nSubj` permutation tests, 5000 iterations each).
-About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected; mean Cohen's D = `r round(mean(SNR_PCCvsPFC_ES), digits = 2)`).
-In addition, we found that the levels of tSNR for each vertex showed significant negative correlations with flexibility, a graph-theoretic index that measures the proportion of times a node in a network changed affiliation across partitions (mean *r* = `r round(mean(SNR_vs_Flex), digits = 2)`).
-These findings indicate that, for any given subject, vertices with low SNR resulted in more variable participation between the communities, and these vertices were more common in mPFC.
-This could explain why mPFC previously showed lower stability levels.
+Even though our findings point to a stable representation of each subject's unique DMN organization, it is still possible that they were driven by considerable levels of signal noise often found in mPFC (its ventral segment in particular).
+To account for any residual noise, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
+mean of each vertex's time series over its standard deviation).
+Note that we did this for the vertices that survived the threshold.
+The tSNR of all vertices were averaged per region and subject (Figure 11), which showed that mPFC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`) and PCC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`) had similar tSNR (permutation, *p* = `r SNR_meanComp$Comparison`, Cohen's D = `r round(SNR_meanComp$ES, digits = 2)`).
+To more precisely examine this difference, we performed subject-wise comparisons of the tSNR values of all vertices between PCC and mPFC (5000 iterations each).
+About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected), but these differences had low effect sizes (mean Cohen's D = `r round(mean(SNR_PCCvsPFC_ES), digits = 2)`).
+These findings further confirm that the idiosyncrasies observed in these areas (and in mPFC in particular) are not a function of measurement noise.
 
@@
 
-# let's put everyone's data together first
-allVariance <- do.call(rbind, Variance)
+# let's put everyone's data together and filter out according to the threshold
+allVariance <- do.call(rbind, Variance) %>%
+                  filter(FiedlerVec != 0)
 
@@
   theme(axis.text.x = element_blank())
+
 v5 <- qplot(data = allVariance, Region, Rsquared, fill = Region, geom = "boxplot") + theme_classic()
@@
 These results suggest that, overall, vertices in mPFC tended to be less in synchrony with the activity of the DMN community as a whole.
-Furthermore, the degree tSNR showed a moderate correlation with $R^2$ values across participants (mean *r* = `r round(mean(noiseCors$R2vtSNR), digits = 2)`; SD = `r round(sd(noiseCors$R2vtSNR), digits = 2)`), meaning that noisier vertices were less in synchrony with the general activity of the DMN.
+Furthermore, the level of tSNR showed a moderate correlation with $R^2$ values across participants (mean *r* = `r round(mean(noiseCors$R2vtSNR), digits = 2)`; SD = `r round(sd(noiseCors$R2vtSNR), digits = 2)`), meaning that noisier vertices were less in synchrony with the general activity of the DMN.
 
@@
 The computational demands of our approach escalate quickly as the number of vertices increases.
-We thus explored the possible advantage to using graph-theoretic approaches on all possible network connections over a simple seed-based functional connectivity analysis from PCC.
-Given that the spatial distribution of the DMN is considerably stable within individuals [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018], we examined whether maps generated with spectral partitioning were more similar per subject across days than those computed from seed-based correlations.
-First, we computed the mean time series of all the vertices contained in the DMN PCC ROI from Yeo et al.
-(2011) parcellation, and correlated it with the activity of every mPFC vertex from our ROIs.
-We then performed pairwise spatial Pearson correlations among maps computed for each day and method from all subjects (Figure 15).
+We thus explored the possible advantage to using graph-theoretic approaches over a simple seed-based functional connectivity analysis from PCC.
+Given that other groups have found the spatial distribution of the DMN to be considerably stable within individuals [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018], we examined whether maps generated with spectral partitioning were more similar per subject across days than those computed from seed-based correlations.
+First, we computed each individual's mean time series of all the vertices contained within PCC, and correlated it with the activity of every mPFC.
+Since correlation values are continuous, we compared them to their respective unbinarized Fiedler vector maps.
+We performed pairwise spatial Pearson correlations among maps computed for each day and method from all subjects.
 For `r nrow(unCorrParticipants %>% filter(Corrs < 0))` subjects, the maps produced with one of the days' datasets insufficiently covered area 7m, and so the community labeling was reversed (for one additional subject, both daily maps were reverted).
-ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topology was highly similar.
-We thus visually inspected these subjects and reverted the labeling when it was clear that the topologies aligned across days (n = 7).
-
-Figure 16 shows the overall degree of similarity across days for patterns dervied using community detection, seed-based correlation, and across methods (i.e.
+ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topography was highly similar.
+We thus visually inspected these subjects (n = 7) and reverted the labeling when it was clear that the topologies aligned across days.
+Figure 13 shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alingment between methods, but particularly high agreement within subject and method.
+
+Figure 14 shows the overall degree of similarity across days for patterns dervied using community detection, seed-based correlation, and across methods (i.e.
 day one community detection versus day two seed-based correlation).
@@
          cl.length = 3,
-         addgrid.col = "grey99",
+         #addgrid.col = "grey99",
          cl.pos = "r",
@@
          cl.pos = "n",
-         addgrid.col = "grey90",
+         #addgrid.col = "grey90",
          mar = c(1,1,2,0), 
@@
 SC_FVvPDMN_plot
+```
+
+```{r Thresholded maps (Fig 6), out.width = "80%", fig.align = "center", fig.cap= "Figure 6.
+A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
+Values that did not meet the threshold were set to zero on the Fiedler vector, and 0.5 on the binarized maps (giving rise to a third community of high-variability vertices).
+B: Spatial mean of the binarized maps across all participants, indicating the proportion of DMN affiliations per vertex in our sample.
+This aggregate map shows the common organizational principle of the DMN and non-DMN communities, while also pinpointing the relatively high level of variability in mPFC."}
+# Change to inflated eventually
+include_graphics("./Images/thresholded.png")
 ```

### 2019-02-08 Manuscript.Rmd
first draft text ready, now working on figures

@@
 output:
-  pdf_document: default
   word_document: 
     reference_docx: Style_reference.docx
+  pdf_document: default
   html_document: default
@@
 This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975].
+Every individual map is therefore binarized by sign in order to evaluate the topography of each sub-network (see next section for details).
+Figure 1 provides a schematic of the process.
 Given that this data-driven method is agnostic to the prevalent function of each community (i.e.
@@
 We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
-
-The thresholded partitions in our work qualitatively resembled the topographical arrangement of networks A and B defined by Braga and Buckner [-@Braga2017].
-We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
-In their work, Braga and Buckner selected individual vertices along the dorsolateral prefrontal cortex (DLPFC) that produced these two anticorrelated networks.
-Therefore, we hypothesized that if the communities we identified on the medial wall match their proposed networks, we should be able to find seed vertices in DLPFC that can reproduce them.
-The whole-brain seed-based functional connectivity maps for these subjects were qualitatively compared to those produced by spectral partitioning.
 
@@
 
+### *Structural correspondence*
+
+``` {r Structural correspondence, fig.align="center", echo=FALSE, message = FALSE}
+# Mean of correlations
+meanMyelin <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
+meanCurv <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
+meanThick <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
+
+# SD 
+sdMyelin <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
+sdCurv <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
+sdThick <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
+```
+
+We coarsely examined whether these idiosyncratic topographical arrangements were defined by anatomical brain features.
+To do so, we correlated each subject's Fiedler vector with their respective structural MRI data.
+On average, we found that the Fiedler vector is uncorrelated with myelin density (mean *r* = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean *r* = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean *r* = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`).
+While these findings point at an orthogonality between structure and functional organization, they resonate with previous work that found no strong matches between intersubject functional variability and cortical thickness, and low variability in sulcal depth within DMN [@Mueller2013a].
 ### *Correlation vs community detection in mPFC*
@@
 
-### *Structural correspondence*
-
-``` {r Structural correspondence, fig.align="center", echo=FALSE, message = FALSE}
-# Mean of correlations
-meanMyelin <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
-meanCurv <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
-meanThick <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
-
-# SD 
-sdMyelin <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
-sdCurv <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
-sdThick <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
-```
-
-Finally, we coarsely examined whether these idiosyncratic topographical arrangements were defined by anatomical brain features.
-To do so, we correlated each subject's Fiedler vector with their respective structural MRI data.
-On average, we found that the Fiedler vector is uncorrelated with myelin density (mean *r* = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean *r* = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean *r* = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`).
-While these findings point at an orthogonality between structure and functional organization, they resonate with previous work that found no strong matches between intersubject functional variability and cortical thickness, and low variability in sulcal depth within DMN [@Mueller2013a].
+### *Similarities with other work*
+
+The thresholded partitions in our work qualitatively resembled the topographical arrangement of networks A and B proposed by Braga and Buckner [-@Braga2017].
+We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
+In their work, Braga and Buckner selected individual vertices along the dorsolateral prefrontal cortex (DLPFC) that produced these two anticorrelated networks.
+Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to find seed vertices in DLPFC that can reproduce them.
+The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 15.
+
+Visual inspection of these networks shows a remarkable similarity between our DMN and non-DMN communities and their networks A and B.
+These qualitative results are important, as here we reinforce the idea that canonical DMN can be reliably subdivide at the individual level.
+Further, it shows the potential of community detection methods to automatically extract these partitions without the need to rely on group data.
+One way in which our results are at odds with those from Braga and Buckner is the functional labeling of these sub-networks.
+Based on our criteria, network B would more closely identify with DMN (per 7m affiliation), while we currently do not have enough evidence to label network A.
+These discrepancies should be addressed with explicit behavioral manipulations in the future.
 
@@
 ## Figures
+
+```{r Method (Figure 1), out.width = "100%", fig.align = "center", fig.cap= "Summary of the partitioning scheme and its evaluation.
+Each connectome if transformed into a normalized Laplacian matrix, whose eigenvector associated with the second-to-lowest eigenvalue assigns negative or positive values to each vertex.
+These continuous maps are binarized by sign, and compared within and between subjects using the chance-correcting Adjusted Rand Index (ARI)."}
+# Change to inflated eventually
+include_graphics("./Images/method_figure.png")
+```
 
@@
 
-```{r Thresholded maps (Fig 6), out.width = "80%", fig.align = "center", fig.cap= "Figure 6.
+```{r Thresholded maps (Fig 6), out.width = "100%", fig.align = "center", fig.cap= "Figure 6.
 A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
@@
 
+```{r B&B comparison (Figure 15), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga & Buckner's (2017) criterion, and those produced by spectral partitioning.
+Networks A and B were produced by carefully selecting a DLPFC seed (pointed by the green arrows).
+In each case, our DMN and non-DMN networks map remarkably well to their proposed functional organization."}
+# Change to inflated eventually
+include_graphics("./Images/braga_comparison.png")
+```
+
 \newpage

### 2019-02-08 Manuscript.Rmd
first draft ready!

@@
 
-## Ideas to do
-
-- The new manuscript organization could go like this: 
-1) Meta-analysis and ROIs
-2) Summary all
-  a) Make sure to report mean density and algebraic connectivity
-  b) Cross-method agreement
-  c) Spatially averaged community maps reproduce group-level analysis
-3) Sliding window
-  a) Fiedler vector magnitude as a proxy for affiliation strength
-  b) Proportion DMN for mPFC and PCC separately to denote overall stability
-  b) Proportion DMN across time-series ~ fiedler vector value (consider renaming propDMN to stability)
-4) Threshold the maps and rerun summary all
-5) Day 1 vs day 2
-6) Session
-7) Potential noise
-8) Structural correspondence
-9) Community > correlation
-
 ## Abstract
@@
 Every individual map is therefore binarized by sign in order to evaluate the topography of each sub-network (see next section for details).
-Figure 1 provides a schematic of the process.
 Given that this data-driven method is agnostic to the prevalent function of each community (i.e.
@@
 In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC.
-It would be more interesting to identify the repercussions to damage in mPFC per individual.
+It would be more interesting to identify the repercussions of damage in mPFC per individual.
 They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment.
@@
 In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse.
-(note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)
+(note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas' latest)
 
@@
 
-Mention the lack of interhemispheric distinction, citing Mackey and Petrides in regards to L-R diffs.
-
-It's also worth mentioning that PCC is largely covered by DMN.
-Then why does this area overlap with SV?
-I think the Mueller paper mentions that PCC is an important hub of the brain, and perhaps subserves many cognitive functions (recent Wash U paper on this too).
-
-And write a portion on the lack of subcortical reward-related regions (i.e.
-striatum).
-Say something like 'incorporating the ventral striatum did notrefine these partitions through either method.
-This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future.
-Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DMN and SV'.
-
 Talk about how there are other community detection algorithms, and that modularity and SP over and underfit, respectively.
@@
 In addition, both modularity and SP rely on connectivity strength, and thus is amenable to the correlative nature of functional connectivity.
+
+Interhemispheric differences? citing Mackey and Petrides
+
+And write a portion on the lack of subcortical reward-related regions (i.e.
+striatum).
+Say something like 'incorporating the ventral striatum did not refine these partitions through either method.
+This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future.
+Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DMN and SV'.
+It is worth noting that the SV-only area from the meta-analysis tends to land in non-DMN, although it ends up in no-ones land when thresholding the maps.
 
@@
 
+<!--
 ### *Table 1. (UPDATE) Significant brain regions per literature*
@@
 | Subjective Value            | `r paste(valLbls)`          |
+-->
 
@@
 
+<!---
 ```{r Method (Figure 1), out.width = "100%", fig.align = "center", fig.cap= "Summary of the partitioning scheme and its evaluation.
@@
 ```
+-->
 
 ```{r Meta-analysis ROIs (Fig.
-1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1.
-Template atlas from Glasser et al.
+1), out.width = "50%", fig.align = "center", fig.cap= "Template atlas from Glasser et al.
 (2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
-Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
+DMN regions defined by Yeo et al.
+(2011) in blue, which encompass areas of considerable overlap between DMN and SV.
+Literature-specific regions (7m in yellow and s32 in red) were identified from a permutation analysis comparing these literatures."}
 # Change to inflated eventually
@@
 ```{r Template partition (Fig.
-2), out.width="50%", fig.align = "center", fig.cap = "Figure 2.
-Brain partition for an example subject (100307).
+2), out.width="50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307).
 Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
@@
 ``` {r Partition comparison: all 2 (Fig.
-4), fig.align="center", out.width = "40%", fig.cap = "Figure 4.
-Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
-PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE}
+4), fig.align="center", out.width = "40%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
+PCC is better aligned across individuals than mPFC.", echo=FALSE, message = FALSE}
 par(xpd=T)
@@
 
-``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 10.
-ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle).
-Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE}
+``` {r Stability per subject: PCC vs mPFC (Fig 5), fig.align="center", fig.width=5, fig.height=3, fig.cap = "MEan agreement between partitions from each sliding window and the map produced with the whole data per subject, for mPFC and PCC separately (left), and the distribution of standard deviations along the time series per subject (right).
+There was strong (at least 50% after adjusting for chance) and stable agreement in both regions, but higher for PCC.", echo=FALSE, message = FALSE}
 
@@
 ``` {r Stability per subject: Fiedler vector vs prop.
-DMN plot (Fig 11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 11.
-Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
-Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
+DMN plot (Fig 6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
+Grey lines display each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
 # Fiedler Vector x proportion of times a vertex was affiliated with DMN
@@
 
-```{r Thresholded maps (Fig 6), out.width = "100%", fig.align = "center", fig.cap= "Figure 6.
-A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
+```{r Thresholded maps (Fig 7), out.width = "100%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
 Values that did not meet the threshold were set to zero on the Fiedler vector, and 0.5 on the binarized maps (giving rise to a third community of high-variability vertices).
@@
 ``` {r Partition comparison: halves (Fig.
-5), fig.align="center", out.width = "60%", fig.cap = "Figure 5.
-Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right).
-These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE}
+8), fig.align="center", out.width = "60%", fig.cap = "Similarity matrices for 10 example participants showing pattern agreement across days for the whole brain (left), and for PCC and mPFC separately (right).
+These figures show high agreement within (but not between) subjects, with mPFC again showing higher heterogeneity in the group.", echo=FALSE, message = FALSE}
 # plots
@@
 ``` {r Partition comparison: halves ratios (Fig.
-6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 6.
-mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI.
+9), fig.align="center", fig.width=3, fig.height=3, fig.cap = "mPFC yields higher within-subject agreement than between subjects, as evidenced by a high within/between subject mean ARI.
 PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE}
@@
 ``` {r Partition comparison: session similarity matrices (Fig.
-7), fig.align="center", out.width = "60%", fig.cap = "Figure 7.
-Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects).
-The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE}
+10), fig.align="center", out.width = "60%", fig.cap = "Similarity matrices showing pattern agreement across sessions for the whole brain (left), and for PCC and mPFC separately (right), for the same 10 example subjects.
+The general pattern from the daily analysis is preserved, with marked individuality for mPFC and PCC, but higher for the former.", echo=FALSE, message = FALSE}
 # plot
@@
 ``` {r Partition comparison: session ratios (Fig.
-8), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 8.
-Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions.
+11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions.
 Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE}
@@
 ``` {r Noise Effects: tSNR Comparison (Fig.
-12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 12.
-Mean tSNR for mPFC and PCC across participants.
+12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "WEIRD: Mean tSNR for mPFC and PCC across participants.
 This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE}
@@
 
+<!--
 ``` {r Noise Effects: Mean R-sqd mPFC and PCC (Fig.
-13 UPDATE IN TEXT FROM THIS FIG ON), fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 13.
-Differences in mean R-squared values for each region per participant.
+13), fig.align="center", fig.width=6, fig.height=4, fig.cap = "Differences in mean R-squared values for each region per participant.
 The figure shows that PCC vertices tend to be more coupled with the overall dynamics of DMN across subjects.", echo=FALSE, message = FALSE}
@@
 ```
+-->
 
 ``` {r Noise Effects: R-sqd vs tSNR (Fig.
-14), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 14.
-Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the lowest tSNR (left).
+13), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Vertex tSNR values across all subjects are correlated with their position along the z-axis, with vmPFC showing the lowest tSNR (left).
 However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE}
@@
 ``` {r Correlation vs community detection (Fig.
-15), fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Figure 15.
-Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector (10 example subjects).
-The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.", echo=FALSE, message = FALSE}
+14), fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector for 10 example subjects.
+The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.
+There is high agreement within method (diagonal quadrants), but both methods suggest similar partitions (off diagonal quadrants).", echo=FALSE, message = FALSE}
 Foo <- "Fighters"
@@
 ``` {r Correlation vs community detection: comparison plot (Fig.
-16), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 16.
-Day 1 vs Day 2 oefficients of spatial correlations for every method, as well as between methods.
+15), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Day 1 vs Day 2 correlation coefficients for every method, as well as between methods.
 Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo=FALSE, message = FALSE}
@@
 
-```{r B&B comparison (Figure 15), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga & Buckner's (2017) criterion, and those produced by spectral partitioning.
+```{r BandB comparison (Figure 16), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga and Buckner's (2017) criterion, and those produced by spectral partitioning.
 Networks A and B were produced by carefully selecting a DLPFC seed (pointed by the green arrows).
 In each case, our DMN and non-DMN networks map remarkably well to their proposed functional organization."}
+
 # Change to inflated eventually
 include_graphics("./Images/braga_comparison.png")
+
 ```

### 2019-02-08 Manuscript.Rmd
Tweaks to first draft, so everything aligns well

@@
 output:
-  pdf_document: default
+  pdf_document: 
+    keep_tex: true
   word_document: 
@@
 
-## Abstract
+## Abstract (**will be expanded once we decide what to keep**)
 
@@
 If the variability that we observed was truly due to having captured an individual's unique organization, day to day ARI values should be consistently higher within- than between-subjects.
-Figure 7 shows pairwise comparisons among ten example subjects for whole brain (left), as well as PCC/mPFC separately (right).
+Figure 7 shows pairwise comparisons among ten example subjects for whole brain (left), as well as for PCC and mPFC separately (right).
 
@@
 
-Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 8), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 9).
+Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 9), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 10).
 
@@
 This also implied lower $R^2$ values for mPFC.
-Indeed, we found that for each subject, $R^2$ values tended to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had *p* values < 0.001; mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`) (Figure 13).
+Indeed, we found that for each subject, $R^2$ values tended to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had *p* values < 0.001; mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`).
 These results suggest that, overall, vertices in mPFC tended to be less in synchrony with the activity of the DMN community as a whole.
@@
 Given this trend, we asked whether there is a "gradient of noise" along the z-axis of mPFC, such that more ventral vertices would both be noisier and explain the least amount of DMN variance.
-Here we found that while $R^2$ are somewhat correlated with dorsal-ventral placement across subjects (mean *r* = `r round(mean(noiseCors$ZvR2), digits = 2)`; SD = `r round(sd(noiseCors$ZvR2), digits = 2)`), there is no clear relationship with the z-axis across subjects (Figure 14).
+Here we found that while $R^2$ are somewhat correlated with dorsal-ventral placement across subjects (mean *r* = `r round(mean(noiseCors$ZvR2), digits = 2)`; SD = `r round(sd(noiseCors$ZvR2), digits = 2)`), there is no clear relationship with the z-axis across subjects (Figure 12).
 Specifically, low $R^2$ are evenly distributed along this axis, denoting a degree of orthogonality between these features.
@@
 While these findings point at an orthogonality between structure and functional organization, they resonate with previous work that found no strong matches between intersubject functional variability and cortical thickness, and low variability in sulcal depth within DMN [@Mueller2013a].
+
+\bigskip
+
 ### *Correlation vs community detection in mPFC*
@@
 
-## Figures
-
 <!---
@@
 -->
+
+\bigskip
+
+## Figures
 
@@
 
-``` {r Stability per subject: PCC vs mPFC (Fig 5), fig.align="center", fig.width=5, fig.height=3, fig.cap = "MEan agreement between partitions from each sliding window and the map produced with the whole data per subject, for mPFC and PCC separately (left), and the distribution of standard deviations along the time series per subject (right).
-There was strong (at least 50% after adjusting for chance) and stable agreement in both regions, but higher for PCC.", echo=FALSE, message = FALSE}
+``` {r Stability per subject: PCC vs mPFC (Fig 5), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Mean agreement between partitions from each sliding window and the map produced with the whole data per subject, for mPFC and PCC separately (left), and the distribution of standard deviations along the time series per subject (right).
+There was strong (at least 50 percent after adjusting for chance) and stable agreement in both regions, but higher for PCC.", echo=FALSE, message = FALSE}
 

### 2019-03-05 cross_correlate.R
write a csv with ccf values (+ update aesthetics)

@@ -50,11 +50,10 @@ timeSeries_sess <- lapply(temp, fread, header=F)
 timeSeries_sess <- lapply(timeSeries_sess, data.matrix)
 
 # load the resulting mapping and produce indices for both nets (thresholded at the group mean of |0.01|)
-# mComm2 is our DMN
 map <- read_csv(paste("../For_HCP/", SubjID, "_FiedlerVec_dataforCifti.txt", sep=""), col_names = F, col_types = cols())[[1]]
 map[map == -1] <- 0
-comm1 <- which(map < -0.01)
-comm2 <- which(map > 0.01)
+comm1 <- which(map < -0.01) # non DMN
+comm2 <- which(map > 0.01) # DMN
 
 # get the mean of the communities per session
 mComm1 <- lapply(timeSeries_sess, mean.activity, mask = comm1)
@@ -74,10 +73,12 @@ ccfData <- tibble(Session = rep(factor(sessLbls, levels = sessLbls), each = nrow
 # plot all dists
 ccfCI <- quantile(bootstrap(ccfData$CCF), 0.975)
 p <- ggplot(aes(Lag, CCF, group = Session, color = Session), data = ccfData) +
-  geom_line(size = 1.5) +
-  geom_hline(yintercept = 0, size = 1, color = "#D9541A") +
+  geom_line(size = 1) +
+  geom_point(size = 1.3) +
+  geom_hline(yintercept = 0, color = "#D9541A") +
   geom_hline(yintercept = abs(ccfCI), linetype = "dashed", color = "#D9541A") +
   geom_hline(yintercept = abs(ccfCI) * -1, linetype = "dashed", color = "#D9541A") +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "#D9541A") +
   scale_color_manual(values = Cols) +
   theme_classic()
 
@@ -88,7 +89,11 @@ ggsave(paste("../CCF_", SubjID, ".png", sep = ""),
        p,
        device = "png")
 
-print("Cross-correlation plots for each session produced.")
+# write a csv file with the ccf per session
+rownames(t1) <- t2[, 1]
+write.table(t1, paste("../CCF_", SubjID, "_vals.csv", sep = ""), col.names = F, sep = ",")
+
+print("Cross-correlation plots and files produced for each session")
 
 
 

### 2019-03-05 Analyze_summaries.R
remove unnecessary files

@@ -1,1327 +1,0 @@
-###-------- Libraries and functions ---------------
-Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere
-
-# In case I want to visualize stuff in the brain
-labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[,2:6]
-labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))
-
-library(igraph)
-#library(tidyverse)
-library(ggnetwork)
-library(ggplot2)
-library(gridExtra)
-library(data.table)
-library(plyr)
-library(mcclust)
-library(lme4)
-library(parallel)
-library(corrplot)
-
-
-## Cohen's D for 2 groups
-# for a more flexible approach, make the data input to be a list with entries for n groups, 
-# then do length(list) for the number of groups. 
-cohenD <- function(group1 = 1, group2 = 2){
-  
-  # means
-  mean1 <- mean(group1, na.rm = T)
-  mean2 <- mean(group2, na.rm = T)
-  
-  # variance
-  var1 <- var(group1, na.rm = T)
-  var2 <- var(group2, na.rm = T)
-  
-  # equation
-  out <- (mean1 - mean2) / sqrt((var1 + var2)/2)
-  
-  return(out)
-  
-}
-
-## log-log degree distribution
-logDegreeDist <- function(Graph = padjMat) {
-  
-  tempD <- degree(Graph)
-  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
-  d <- (0:(max(tempD)-1))
-  ind <- (tempDD!=0)
-  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
-       xlab = "Log-Degree", ylab = "Log-Intensity",  
-       main = "Log-Log Degree Distribution")
-  
-}
-
-
-## Create correlation matrix between vertices of 2 ROIs
-# Requires labeled time series matrix
-vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
-  
-  # extract the time series from the ROIs
-  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
-  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
[…]

### 2019-03-07 ccf_eval.R
plots to evaluate ccf outputs across subjects

@@ -1,0 +1,69 @@
+# produce histograms for the peaks of each ccf across subjects
+
+# libraries & functions
+suppressMessages(library(tidyverse))
+
+# load data
+setwd('./cross_correlate/')
+temp <- list.files(pattern = ".csv")
+timeSeries_sess <- lapply(temp, read.csv, header = F)
+nSubj <- length(timeSeries_sess)
+
+# save the lag positions and trim mDFs
+lag <- timeSeries_sess[[1]]$V1
+timeSeries_sess <- lapply(timeSeries_sess, "[", i = , j = 2:ncol(timeSeries_sess[[1]]))
+
+
+## mean correlation per peak
+## this is a very rough estimate, because it disregards the variance within subject
+# average within subject and then between subjects + SE
+mCorr_subj <- do.call(rbind, lapply(timeSeries_sess, rowMeans))
+mCorr_all <- tibble(Lag = lag,
+                    meanCorrelation = colMeans(mCorr_subj),
+                    SE = apply(mCorr_subj, 2, sd) / sqrt(nSubj)) %>%
+             mutate(lower = meanCorrelation - SE,
+                    upper = meanCorrelation + SE)
+
+# plot
+(p <- ggplot(aes(Lag, meanCorrelation), data = mCorr_all) +
+        geom_line(color = "grey50") +
+        geom_point(size = 1.5, color = "grey50") +
+        geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
+        geom_hline(yintercept = 0, linetype = "dashed", color = "#D9541A") +
+        geom_vline(xintercept = 0, linetype = "dashed", color = "#D9541A") +
+        theme_classic())
+
+
+## peak counts
+# get the absolute peak per subject
+peaksAbs <- lapply(timeSeries_sess, function(data) {
+    as.numeric(apply(data, 2, function(x) {which(abs(x) == max(abs(x)))}))
+  }) %>% 
+  lapply(function(x) {lag[x]}) %>%
+  do.call(cbind, .) 
+  
+
+# get the positive peak per subject
+peaksPos <- lapply(timeSeries_sess, function(data) {
+    as.numeric(apply(data, 2, function(x) {which(x == max(x))}))
+  }) %>% 
+  lapply(function(x) {lag[x]}) %>%
+  do.call(cbind, .) 
+
[…]

### 2019-03-07 Manuscript.Rmd
working on the draft comments from Joe

@@
 ---
-title: 'Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex '
+title: 'Individual heterogeneity in the functional topography of the medial prefrontal cortex'
 author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
@@
   word_document: 
-    reference_docx: Style_reference.docx
+    reference_docx: Style_reference_draft.docx
   html_document: default
@@
   # Index: VI for variation of information, RI for the adjusted rand index, Cor for a Pearson correlation
+  # ARI can yield many decimals, thus inflating the ratios. I thus round at 4 decimals.
 
@@
     }
+
+    indexMatrix <- round(indexMatrix, digits = 4)
+
   } else {
@@
     }
+
+    indexMatrix$Index <- round(indexMatrix$Index, digits = 4)
+
   }
@@
 
-## Abstract (**will be expanded once we decide what to keep**)
-
-  Valuation effects are consistently observed in medial prefrontal and posterior cingulate cortex (mPFC and PCC).
-The spatial extent of these effects is mostly indistinguishable from the default mode network (DMN) in existing meta-analyses.
-However, little is known about how valuation effects fit within the broader functional architecture of mPFC and PCC, or whether that architecture is consistent or idiosyncratic across individuals.
-Here we complement a meta-analysis with fMRI-based graph theoretic approaches to subdivide mPFC and PCC at the single-subject level.
-Our results suggest the functional topography of mPFC has substantial variability across individuals.
-This highlights the potential usefulness of estimating brain effects at the individual level in this region, and points to limitations of aggregative methods such as coordinate-based meta-analysis in determining whether valuation and DMN effects emerge from common or separable brain systems.
-Our approach shows promise in addressing this issue through future manipulations of valuation.
+## Abstract
+
+  There is extensive topographic overlap between cortical regions associated with the default-mode network (DMN) and regions that exhibit effects of subjective value during decision making.
+The two sets of functional effects involve common regions of medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC).
+At the same time, differences between the two sets of activation patterns are apparent at the aggregated meta-analytic level, and further individual-level functional subdivisions might be obscured by group averaging.
+Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DMN effects.
+We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to divide mPFC/PCC into distinct cortical communities in individual participants (n=100 from the Human Connectome Project).
+We labeled the communities "DMN" and "non-DMN" on the basis of their overlap with the meta-analytically identified PCC region.
+The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable over time and across test-retest days using moderate amounts of fMRI data (30 min per day).
+The topography of the identified subdivisions differed across individuals, and the degree of inter-individual variability was greater in mPFC than in PCC.
+Our results will aid future task-based fMRI studies in identifying functionally specific cortical subdivisions, and suggest it would be premature to infer that different task manipulations call upon shared cognitive processes solely because they evoke overlapping activation in mPFC at the group or meta-analytic level.
 
@@
 
-  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value (SV) assigned to decision outcomes [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
-However, the distributed cortical valuation system also includes posterior cingulate (PCC) and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall [@Fox2005; @Laird2009; @Yeo2011].
-This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.
-
-  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions.
-Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation [@Bartra2013] and DMN [@Laird2009].
-Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena [@DelaVega2016].
-More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017].
+  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018], including the subjective value (SV) assigned to decision outcomes [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
+Choice-related activity in these areas has shown significant spatial overlap with the default mode network (DMN) along the medial wall [@Fox2005; @Laird2009; @Yeo2011], prompting the question of whether (and to what extent) these two systems can be dissociated.
+
+  Previous coordinate-based meta-analyses have identified topographically similar activation patterns in mPFC for valuation [@Bartra2013; @Clithero2014] and default-mode task deactivation [@Laird2009].
+More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017], even though there is clear divergence in other areas (ventral striatum in favor of SV, with DMN exclusively on sections of PCC and the temporoparietal junction).
 These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same neural system.
-However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area [@Kragel2018].
-While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data.
+
+  A key limitation of group-averaging and meta-analysis is that individual-specific functionl subdivisions can be overlooked.
 Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject.
-However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013a], thus making group-averaging studies difficult to interpret.
+However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a], thus making group-averaging studies difficult to interpret.
 
   Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
-Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018a].
+Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018a; @Tobyne2018].
 Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
 In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity [@Braga2017].
-It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
+It is thus possible that the indistinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
 With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.
 
-  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments [@Logothetis].
-As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time.
+  [i'm here] As such, there is value in examining all possible sources of covariation that compose DMN.
 Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017].
@@
 We then spatially correlated (Pearson) each subject's $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices, and report the mean correlation across subjects.
-
-### *Anatomical Correspondence*
-
-Finally, we examined whether each idiosyncrasies in functional topology corresponded to outstanding anatomical features.
-To do this, we correlated each subject's thresholded Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex).
-These simple correlations are aimed to provide a coarse sense of this possible relationship, which can be studied in depth in the future.
-
-\bigskip
 
@@
 
-# # Permutation analysis
-# # Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
-# # Load the coordinates as studies in a list, because for the contrast the studies are permuted
-# # Use table(unlist(list)) to get the counts in that case
-# setwd('./DEC')
-# templist <- dir()
-# studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
-# 
-# setwd('../DMN/')
-# templist <- dir()
-# studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
-# 
-# # For each permutation, reassign the study labels, maintaining the original number of studies per condition
-# allStudies <- c(studyList_sv, studyList_dmn)
-# nPerms <- 1000 # stored statistics are computed @ 5k, but it's computationally demanding to do that.
-# nullDist <- numeric()
+# Permutation analysis
+# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
+# Load the coordinates as studies in a list, because for the contrast the studies are permuted
+# Use table(unlist(list)) to get the counts in that case
+setwd('./POS')
+templist <- dir()
+studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
+
+setwd('../DMN/')
+templist <- dir()
+studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
+
+# For each permutation, reassign the study labels, maintaining the original number of studies per condition
+allStudies <- c(studyList_sv, studyList_dmn)
+nPerms <- 1000 # stored statistics are computed @ 5k, but it's computationally demanding to do that.
+nullDist <- numeric()
 # 
@@
 # Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
-tempComm_PCC <- lapply(tempComm_PCC, function(data) {data %>% filter(FiedlerVec != 0)})
-tempComm_PFC <- lapply(tempComm_PFC, function(data) {data %>% filter(FiedlerVec != 0)}) 
+tempComm_PCC <- lapply(tempComm_PCC, filter, FiedlerVec != 0)
+tempComm_PFC <- lapply(tempComm_PFC, filter, FiedlerVec != 0) 
 SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) {permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval})
@@
 
-### *Structural correspondence*
-
-``` {r Structural correspondence, fig.align="center", echo=FALSE, message = FALSE}
-# Mean of correlations
-meanMyelin <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
-meanCurv <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
-meanThick <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
-
-# SD 
-sdMyelin <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
-sdCurv <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
-sdThick <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
-```
-
-We coarsely examined whether these idiosyncratic topographical arrangements were defined by anatomical brain features.
-To do so, we correlated each subject's Fiedler vector with their respective structural MRI data.
-On average, we found that the Fiedler vector is uncorrelated with myelin density (mean *r* = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean *r* = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean *r* = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`).
-While these findings point at an orthogonality between structure and functional organization, they resonate with previous work that found no strong matches between intersubject functional variability and cortical thickness, and low variability in sulcal depth within DMN [@Mueller2013a].
-
-\bigskip
-
 ### *Correlation vs community detection in mPFC*
@@
 ## Between halves analysis for correlation and communities (mPFC only)
-Foo <- "Fighters"
 unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
@@
 # Compare correlation with community approach on mPFC
-Foo <- "Fighters"
 tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))

### 2019-03-13 Manuscript.Rmd
most of Joe's first pass of comments addressed

@@
 
-# Whether to apply subject-wise thresholds on maps or not
-threshMaps <- TRUE
+# general options
+threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
+feedback <- FALSE # show permutation progress?
 
@@
 # This takes either a matrix of correlation values (vectors too, but manually compute pvals)
-# Normalization approach suggested in network textbook (equation 7.10)
+# Normalization approach suggested in network textbook (equation 7.20)
+# This transformation is approximately normal with mean 0 and sd = sqrt(1 / (n - 3))
 fisherTanh <- function(Data = padjMatrix){
@@
   }
-  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)
+  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n - 3)), lower.tail = F) # no lower tail, but absolute Zs = two tailed
 
@@
       # had to place dashes on each side because grep grabbed strings containing the names (i.e. 47m, a24pr)
-      #ROIS <- c("_7m_", vmPFC_labels) # c("_a24_", "_7m_")
       for (ROI in ROIS) {
@@
       corrMat <- exp(corrMat)
-      corrMat[corrMat==1] <- 0
+      corrMat[corrMat == 1] <- 0
       transfMat$tanhZ <- corrMat
@@
 The two sets of functional effects involve common regions of medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC).
-At the same time, differences between the two sets of activation patterns are apparent at the aggregated meta-analytic level, and further individual-level functional subdivisions might be obscured by group averaging.
+At the same time, differences between the two sets of activation patterns are not apparent at the aggregated meta-analytic level, and further individual-level functional subdivisions might be obscured by group averaging.
 Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DMN effects.
@@
 
-  [i'm here] As such, there is value in examining all possible sources of covariation that compose DMN.
+  Interrogating all sources of covariation through functional connectivity provides an avenue for capturing subject-specific brain organization.
 Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017].
-A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics [@Bassett2018a].
+A popular approach to analyze these connectomes is to rely on graph theoretic methods, which are properly equiped to understand brain network dynamics [@Bassett2018a].
 From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017].
@@
 Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017].
-However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option.
-In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix).
-The resulting eigenvector corresponding to the second-lowest eigenvalue (i.e.
-the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003].
+However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes a forced dissection through spectral partitioning (SP) a more valuable option [@Fiedler1975; @Belkin2003].
 SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018].
@@
   In this study, we aimed to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals.
-We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data.
-First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas [@Glasser2016].
-We then produce a rsFC networks of all the surface vertices within these ROIs for each of 100 individual resting state dataset from the Human Connectome Project (HCP)[@VanEssen2012], and estimate the extent of DMN coverage through spectral partitioning.
-Our results suggest the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects.
-These sub-networks resembled an organizational scheme recently observed in a handful of subjects (Braga & Buckner, 2017).
-We also show that graph theoretic tools are capable of identifying these sub-networks in isolated individuals.
+We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks.
+First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that considerably overlapped with previously-defined DMN and limbic networks along the medial wall [@Yeo2011].
+A meta-analysis of DMN and SV literatures revealed areas in PCC and mPFC that were uniquely related to DMN and SV, respectively (these areas were used as markers to identify the affiliation of each individual's communities).
+We then produced rsFC networks of all the surface vertices within these regions of interest (ROI) for each of 100 individual resting state dataset from the Human Connectome Project (HCP)[@VanEssen2012], and estimated the extent of DMN coverage through spectral partitioning.
+We found that these areas of overlap can be partitioned into two communities that topographically vary across subjects, but that follow a comon organizational principle.
+This partition was in substantial agreement with results from a different community detection algorithm (moularity).
+A sliding window analysis revealed that spectral partitioning allows for a more immediate identification of noisy viertices with unreliable affiliation.
+Refining the partitions by filtering out these nodes resulted in idiosyncratic partitions that were highly stable across scanning runs per individual, and this pattern was higher for mPFC.
+We show that partitions produced by spectral partitioning had higher test-retest reliability per subject than common seed-based functional connectivity, without the need of group-drived priors [@Kong2018].
+Lastly, we provide evidence that these communities resembled an organizational scheme recently observed in a handful of subjects [@Braga2017].
 Our work highlights the usefulness of estimating brain effects at the individual level in these regions, and points to limitations of aggregative methods in determining the degree of neural overlap between DMN and valuation.
@@
 
+### *Search space*
+
+For all our analyses, we defined our search space based on the 17 network parcellation proposed by Yeo et al.
+[-@Yeo2011].
+First, Ww selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial wall.
+Next, we overlayed these networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained parcels that shared at least 15% of vertices with them.
+This resulted in 45 regions of interest (ROI) across hemispheres (Table 1).
+These ROIs were naturally divided into two spatially discontiguous clusters that covered PCC and mPFC, thus facilitating the study of each general region separately.
+
+\bigskip
+
 ### *Meta-analysis*
 
-We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation [@Bartra2013] (n = 27 studies) and DMN [@Laird2009] (n = 77).
+We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels were differentially associated with valuation or DMN effects.
+For subjective value, we gathered peak brain coordinates of activity from 198 studies that were associated with positive effects for current or prospective rewards [@Bartra2013].
+For DMN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009].
 These represent the surviving areas post-statistical thresholding from each study.
-For each study, each peak volumetric coordinate was mapped onto a 1mm standard space (MNI152) using AFNI's 3dcalc (CITATION).
-We then generated 10mm speheres at these points with FSL's fslmaths (CITATION), and then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf (CITATION).
-The sphere sections that overlapped with the cortex were mapped to an atlas of the human cortical surface (360 regions)[@Glasser2016].
-This produced a list of standardized parcels that were reported on each study.
-
-<!-- 
-With these lists, we identified the areas that were more consistently shared between DMN and valuation.
-For each literature, we summed the number of times each parcel was reported across studies, and performed a one-way chi-squared test of proportions on each parcel with a null probability equivalent to the bootstrapped (5000 iterations) mean of each literature's report counts.
-In other words, we checked which regions were significantly (p < 0.05) more reported in their respective literatures than their counterparts.
-Regions of interest were then determined based on which of the remaining regions were common across literatures.
--->
+For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere[@Wager2009].
+The indicator map for each study was then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl2012] (http://surfer.nmr.mgh.harvard.edu/).
+Any sphere sections that overlapped with the cortex were mapped to our ROIs, and we tallied how many studies had positive indicator values in each parcel.
 
 With these lists, we identified areas that were significantly more associated to either literature.
-We limited the search space to the parcels that were contained within the medial portion of the DMN parcellation defined by Yeo et al.
-[-@Yeo2011], as it broadly encompassed our a priori domain of interest (25 parcels across hemispheres).
 We permuted the label of every study (i.e.
-DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic from chi-squared tests of proportions that compared the number of studies that contained each area.
+DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from chi-squared tests of proportions that compared the number of studies that contained each area.
 This gave us a null distribution of 5000 chi-squared values.
-We then used the 95th percentile of this distribution as a significance threshold to evaluate the chi-squared values produced by comparing the actual rates of reporting of each area between literatures.
-The resulting ROIs contained two spatially discontiguous regions (Figure 1), which we label PCC and mPFC for further analyses.
+The 95th percentile of this distribution served as an FWE-corrected significance threshold to evaluate unpermuted chi-squared values.
 
@@
 
-In order to quantify the resting connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
+Oue fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
 Each subject's data was acquired over two days at Washington University in St.
 Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany).
-Four resting state sessions (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) were each comprised of 1200 TRs for a total scan time of 14 min 33 s, with left-right and left-right phase encoding implemented on each day.
-We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).
-
-Beyond the in-house minimally preprocessed pipeline from HCP [@Glasser2013], which includes considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152-based normalization, all scans went through a number of additional refinements [@Tobyne2017].
-These included band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), as well as mean greyordinate signal regression [@Burgess2016].
+Four resting state runs (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised 1200 time points(14 min 33 s) for a totalof 4800 time points.
+Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other.
 Only subjects with both left-right and right-left phase encoding were included (i.e.
@@
 In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used.
+
+Data initially underwent the HCP minimally preprocessing pipeline [@Glasser2013], which included considerable gradient nonlinearity correction, motion correction, EPI distortion correction, temporal denoising based on independent components (FIX, [@Griffanti2014; @Salimi-Khorshidi2014]), high-pass filtering (0.0005 Hz threshold), and MNI152-based normalization.
+Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017].
+Steps included linear interpolation across timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising and high-motion censoring by deletion, as well as mean greyordinate signal regression [@Burgess2016].
 Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses.
@@
 left-right and right-left phase encoding session) were temporally demeaned.
-Each subject's brain was comprised of 32k vertices per hemisphere.
+Each subject's brain was comprised of 32k standard HCP greyordinates per hemisphere (combined in a CIFTI file).
 We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.
@@
 
-All network analyses were performed using the igraph package (CITE) in R 3.4.1.
+All network analyses were performed using the igraph package [@Csardi2006] in R 3.4.1 [@R Development Core Team].
 To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
 This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
-Next, we applied Fisher's r to z transformation, and took the exponential of these values so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05).
-As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).
+Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify strong correlations.
+The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values).
+Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
+Values of 1 of this transformed distribution were returned to 0 in order to avoid the inclusion of these edges in the network analyses.
+We report the proportion of retained edges (i.e.
+network density) in the Results section.
+As part of the evaluation step, we produced these network weight matrices (and the community detection outlined below) at four levels: 1) for each run separately (1200 TRs each); 2) for the concatenated time series for the two runs on the same day (2400 TRs total); 3) for each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).
 
@@
 clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003].
-First, each network was represented as an $n$ x $n$ matrix of previously adjusted correlation values (where $n$ = number of vertices within the ROIs, 4,801).
+First, each network was represented as an $n$ x $n$ network weight matrix (where $n$ = number of vertices within the ROIs, 4,801).
 This matrix was then transformed into its normalized Laplacian form
@@
 Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its correlation values with every other vertex), and $W$ is the adjusted correlation matrix.
+the sum of its correlation values with every other vertex), and $W$ is the network weight matrix.
 This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal.
-This transormation ensures that every row adds up to zero.
+This transformation ensures that every row adds up to zero.
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
-This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975].
-Every individual map is therefore binarized by sign in order to evaluate the topography of each sub-network (see next section for details).
-Given that this data-driven method is agnostic to the prevalent function of each community (i.e.
-DMN or not DMN), we defined the DMN community to be the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects).
-Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].
-
-In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al.
+This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with [@Fiedler1975].
+This method enforces the partition of a network into similarly-sized communities, and guarantees that they share at least one edge [@Chung1999].
+In this way, spectral partitioning avoids producing communities that are too small to be physiologically meaningful (for example, isolated vertices that are considerably affected by measurement noise).
+Every individual partition is therefore binarized by sign in order to evaluate the topography of each community (see next section for details).
+Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community to be the one containing the DMN-specific PCC parcel identified in our meta-analysis.
+Given the high density of these networks (see Results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].
+
+In order to evaluate the convergent validity of the resulting partitions across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al.
 [-@Clauset2004].
@@
 The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.
-Thus, unlike SP, modularity can fractionate a network into many functional groups.
-We assumed that if the partitions from the bounded and unbounded community detection methods show high level of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
+Unlike SP, modularity can fractionate a network into more than two functional groups.
+We assumed that if the partitions from the bounded and unbounded community detection methods showed high level of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
+We also diagnose our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by spectral partitioning to be non-zero.
+This eigenvalue serves as an estimator of the optimal number of communities in a network [@Chung1999], such that a rank of two in our partitions justifies limiting the number of communities to two.
 
@@
 
-In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (ARI) as the reference metric of agreement between two clusterings [@Hubert1985].
-ARI estimates the rate at which every pair of nodes in partition A were jointly assigned to the same/different parcels on partition B, over all possible changes (e.g.
-clustered together on A, but separately on B).
-Therefore, the adjusted rand index determines the percentage of agreement between any two partitions while being agnostic to the labeling scheme.
-The resulting ratio is compared to a baseline given by the expectation of a random node assignment across partitions.
-This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index falls below chance).
+In order to evaluate the stability and topographical heterogeneity of the communities within and across subjects, we chose the adjusted rand index (ARI) as the reference metric of agreement between two clusterings [@Hubert1985].
+The base of the ARI is computed by the formula
+
+$$\frac{a + b}{a + b + c + d}$$
+
+Where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number grouped together (separately) in one partition, but separately (together) in the other.
+Therefore, ARI estimates the ratio at which every pair of nodes in partition A were jointly assigned to the same/different parcels on partition B, over all possible relational changes.
+The resulting ratio is adjusted by comparing it to a baseline given by the expectation of a random node assignment across partitions.
+This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below 50%).
+In short, the ARI determines the chance-corrected percentage of agreement between any two partitions while being agnostic to the labeling scheme.
 
@@
 First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns.
-Modularity and SP show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018].
+Modularity and SP have been previously found to show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018].
 Their alignment would thus give us confidence in the validity of the resulting topologies.
-Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean ARI for the group.
-We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise RI comparisons across subjects.
+Next, we compared the functional organization derived from the whole time series across subjects, and report the mean pairwise ARI for the group.
+We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects.
 Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all the subsequent analyses on PCC and mPFC separately.
 
-To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the clustering derived from the whole subject's data.
-The length of the windows is well equipped to find stable community features in brain networks [@Gordon2017].
-In addition, given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise.
-In that regard, and consdiering the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we also examined the relationship between the magnitude of Fiedler vector values with the proportion of times a vertex was part of the DMN community across windows.
-To do this, we performed a mixed effects logistic regression model, with subject as a mixed effect and vertex-wise eigenmap values (derived from their full dataset) as fixed predictors on the proportion of times each vertex participated in the DMN community.
-Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time (all other values were turned into zeros).
-Individuals without such stable nodes were not thresholded, but their maps were not discarded.
+To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the partition derived from the whole subject's data.
+A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017].
+We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows.
+To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full dataset).
+Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time.
+*Individuals without such stable nodes were not thresholded, but their maps were not discarded.
 Values in the eigenvector maps that did not meet threshold were set to zero, and set to 0.5 during binarization so that they would not bias the mean estimates across subjects.
 These thresholds yielded individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.
-
-We then estimated the level of agreement between scans taken across days (i.e.
-pairs of daily left-right and right-left phase encoding sessions).
-If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement for the same subject across days than either day compared to every other subject.
-We tested this idea by computing the ratio of the mean RI within and between subjects.
-Ratios close to one denoted good alignment across subjects, while ratios significantly higher than one suggested that partitions within a subject were more stable than what you would expect against every other subject.
-We then extend this idea by computing the overall agreement across all sessions.
-Similar to the day-to-day analysis, we expect that sessions within subjects would show higher agreement than between subjects.
-Given what we know about these general regions, we expected PCC to be fairly well aligned across participants, and stable within subjects.
-On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject.
-
+(MANY NOTES: this can go into the results, and will need to add 1) % of subjects without stable nodes, and 2) the mean and range for the % of nodes that were stable.*
+
+We then estimated the level of agreement between network partitions estimated using data from individual days (with 2 days per participant).
+If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement within subject (test/re-test across days) than across subjects.
+We tested this idea by computing the ratio of the mean ARI within and between subjects.
+Ratios close to one denoted similar within-subject and across-subject alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-subject than across subjects.
+We then extended this idea by computing the overall agreement across all runs (4 per subject) Similar to the day-based analysis, we assessed whether session-level data showed higher agreement within-subject than between subjects.
+
+<!--
 ### *Estimation of Noise Effects*
@@
 We then spatially correlated (Pearson) each subject's $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices, and report the mean correlation across subjects.
+-->
 
@@
 
-A potential downfall of our approach lies in whether the considerable computational demands are indeed required to identify these individualized partitions.
-It is possible that regional seed-based functional connectivity could provide sufficiently stable approximations of an individual's DMN arrangement.
-Given the high variability and idiosyncrasy of mPFC (see Results), we examined if SP could capture more reliable maps than seed-based functional connectivity in this area.
+We evaluated the performance of the spectral partitioning algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity.
 First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average PCC activity for each day separately.
-We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps.
-These spatial correlations were aimed to determine the day-to-day stability of each approach, as well as the overall level of agreement between them.
-These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]).
+We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps.
+These spatial correlations were aimed to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
+The two methods are expected to produce somewhat similar arrangements, but the one displaying the higher within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]).
 We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
@@
 
-``` {r ROI computation from Matlab, echo=FALSE, message = FALSE, cache = TRUE}
-# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
-# Minus PGi and PGs. This replicates the 7m finding. 
-# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
+``` {r Meta-analysis permutation, echo=FALSE, message = FALSE, cache = TRUE}
+# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC
 Yeo_labels <- c("L_25_ROI",
@@
 
-Yeo_PCC_labels <- c("_7m_",
-                    "_23d_",
-                    "_31a_",
-                    "_31pd_",
-                    "_31pv_",
-                    "_PCV_",
-                    "_POS1_",
-                    "_RSC_",
-                    "_d23ab_",
-                    "_v23ab_")
-
-mPFC_only <- c("_a24_",
-               "_d32_",
-               "_p32_",
-               "_10r_",
-               "_9m_",
-               "_10v_",
-               "_OFC_",
-               "_s32_",
-               "_p24_")
-
 # Permutation analysis
@@
 templist <- dir()
-studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
+studyList_sv <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())
 
@@
 templist <- dir()
-studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
+studyList_dmn <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())
+
+# raw counts for each area per literature
+nRegions_sv <- do.call(rbind, studyList_sv) %>% count
+nRegions_dmn <- do.call(rbind, studyList_dmn) %>% count
+nRegions_all <- left_join(nRegions_sv, nRegions_dmn, by = "X1")
 
@@
 allStudies <- c(studyList_sv, studyList_dmn)
-nPerms <- 1000 # stored statistics are computed @ 5k, but it's computationally demanding to do that.
+nPerms <- 100 # reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
 nullDist <- numeric()
-# 
-# for (i in seq(nPerms)) {
-# 
-#   if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
-# 
-#   # Sample all the studies and divide into 2 groups
-#   randPerm <- sample(allStudies)
-#   tmpSV <- randPerm[seq(length(studyList_sv))]
-#   tmpDMN <- randPerm[-seq(length(studyList_sv))]
-# 
-#   # Count the number of times each region was reported in the literature
-#   # Bilateral activations still count as 1, so we might want to reconsider that
-#   tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-#                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
-#                       DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
-# 
-#   # Perform the prop test for each pair and get the max chi-squared stat
-#   nullDist[i] <- max(
-#                   apply(tmpDF[,2:3], 1, function(data) {
-#                     prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
-#                     }
-#                   ), na.rm = T)
-# 
-# }
-# 
-# # Now do the same for the actual data, to see how it compares to the null dist
-# tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-#                     SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
-#                     DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
-#                     propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
-#                     propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
-# 
-# # Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
-# tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
-#   round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
-#   })
-# tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
-# 
-# # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
-# significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))
+
+for (i in seq(nPerms)) {
+
+  # provide feedback only if requested (if TRUE, it will show up in the doc or pdf file)
+  if (feedback) {
+    if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
+  }
+
+  # Sample all the studies and divide into 2 groups
+  randPerm <- sample(allStudies)
+  tmpSV <- randPerm[seq(length(studyList_sv))]
+  tmpDMN <- randPerm[-seq(length(studyList_sv))]
+
+  # Count the number of times each region was reported in the literature
+  tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+                      SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
+                      DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
+
+  # Perform the prop test for each pair and get the max chi-squared stat
+  nullDist[i] <- max(
+                  apply(tmpDF[,2:3], 1, function(data) {
+                    prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
+                    }
+                  ), na.rm = T)
+
+}
+
+# Now do the same for the actual data, to see how it compares to the null dist
+tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+                    SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
+                    DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
+                    propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
+                    propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
+
+# Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
+tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
+  round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
+  })
+tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
+
+# ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
+significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist, 0.95))
 
 # results!
-# s32 (prportion sv = 0.6; proportion DMN = 0.2, Chi = 11.95, p < 0.01)
-# 7m (prportion sv = 0.07; proportion DMN = 0.4, Chi = 8.45, p < 0.05)
-# null chi <- 8.4
+# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DMN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.01)
+# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DMN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p < 0.05, R: p < 0.0001)
+# v23 right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
+# null 95th-q chi <- 10.04 (varies; this was done ith 100 but resembles the 5k one)
 
@@
 Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
-The 25 areas considered were limited to the medial portion of the DMN, as defined by Yeo et al.[-@Yeo2011].
+The 45 areas considered were limited to the medial portion of the default mode and limbic networks, as defined by the Yeo et al.[-@Yeo2011] 17 network parcellation.
 Unique areas were identified by first permuting the affiliation of each study (i.e.
@@
 This putative null distribution was used to identify regions more often reported in either literature.
-Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
 
 Figure 1 shows the resulting ROIs from these analyses.
-The 95th percentile of the permuted Chi-squared distribution was 8.4.
-Based on this threshold, area 7m was the only one to show unique affiliation to DMN (observed $\chi^2$ = 8.45, *p* < 0.05), while SV was uniquely represented by area s32 (observed $\chi^2$ = 11.95, *p* < 0.01).
+The 95th percentile of the permuted Chi-squared distribution was `r quantile(nullDist, 0.95)`.
+Based on this threshold, area 7m was the only one to show unique affiliation to DMN (observed $\chi^2$ = 8.45, *p* < 0.05), while SV was uniquely represented by area 25 (observed $\chi^2$ = 11.95, *p* < 0.01).
+The purpose of these supra-threshold areas was to identify the most-likely affiliation of the two communities in our partitions by their coverage of these regions.
+However, area 25 sits in close proximity to the ventral striatum, which is reliably active in SV studies [@Bartra2013].
+Considering that our projection from volumetric spheres to the cortex might have attributed striatal reports to this region, we decided not to use it as a marker of SV.
+We also chose not to use area v23 due to its unilateral significance.
+Instead, we only rely on area 7m to demarcate the DMN community.
 
@@
 
-With these 25 ROIs (23 overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using their full time series (4800 total TRs from four scanning sessions over two days).
+With these `r length(unique(str_remove(Yeo_labels, "_ROI")))` ROIs (`r (length(unique(str_remove(Yeo_labels, "_ROI"))) - 2)` overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using their full time series (4800 total TRs from four scanning sessions over two days).
 Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices).
@@
 highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`).
-This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].
+This high degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].
 
@@
 
-### *Partition Comparison:Thresholded Full Datasets*
+### *Partition Comparison: Thresholded Full Datasets*
 ``` {r Partition comparison: all thresholded, echo=FALSE, message = FALSE, cache = TRUE}
@@
 This ratio denotes the relative specificity of their partition, such that partitions that align well across subjects should yield ratios close to 1, while unique and stable partitions would produce high ratios.
+Given what we know about these general regions, we expected PCC to be well aligned both within and between subjects.
+On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject.
+
 Figure 8 shows these ARI ratios for PCC and mPFC for all subjects.
@@
 
-<!--
-### *Table 1. (UPDATE) Significant brain regions per literature*
+### *Table 1. Regions of interest from Glasser et al. (2016). Prefixes indicate hemispheric location (e.g. R = right).*
 | Literature           | Significant Brain Regions                 |
-| :-------------------------- | --------------------------: |
-| Default Mode Network        | `r paste(dmnLbls)`          |
-| Subjective Value            | `r paste(valLbls)`          |
--->
+| :------------------- | ----------------------------------------: |
+| ROIs                 | `r print(str_remove(Yeo_labels, "_ROI"))` |
 
@@
 ```{r Meta-analysis ROIs (Fig.
-1), out.width = "50%", fig.align = "center", fig.cap= "Template atlas from Glasser et al.
-(2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
+1), out.width="50%", fig.align = "center", fig.cap= "Proportion of times each ROI was reported in each literature (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
 DMN regions defined by Yeo et al.
 (2011) in blue, which encompass areas of considerable overlap between DMN and SV.
-Literature-specific regions (7m in yellow and s32 in red) were identified from a permutation analysis comparing these literatures."}
+Literature-specific regions (7m in yellow and 25 in red) were identified from a permutation analysis of chi-squared tests comparing these literatures."}
 # Change to inflated eventually
-include_graphics("./Images/ROIS3.png")
+include_graphics("./Images/ROIS4.png")
 ```

### 2019-03-13 Manuscript.Rmd
Done with abstract, intro, and methods revision + updated bibliogrphy

@@
 output:
+  word_document: 
+    reference_docx: Style_reference_draft.docx
   pdf_document: 
     keep_tex: true
-  word_document: 
-    reference_docx: Style_reference_draft.docx
   html_document: default
@@
 Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DMN effects.
-We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to divide mPFC/PCC into distinct cortical communities in individual participants (n=100 from the Human Connectome Project).
+We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to divide mPFC/PCC into distinct cortical communities in individual participants (n = 100 from the Human Connectome Project).
 We labeled the communities "DMN" and "non-DMN" on the basis of their overlap with the meta-analytically identified PCC region.
@@
 We found that these areas of overlap can be partitioned into two communities that topographically vary across subjects, but that follow a comon organizational principle.
-This partition was in substantial agreement with results from a different community detection algorithm (moularity).
-A sliding window analysis revealed that spectral partitioning allows for a more immediate identification of noisy viertices with unreliable affiliation.
+This partition was in substantial agreement with results from a different community detection algorithm (modularity).
+A sliding window analysis showed that spectral partitioning allows for a more immediate identification of noisy viertices with unreliable affiliation.
 Refining the partitions by filtering out these nodes resulted in idiosyncratic partitions that were highly stable across scanning runs per individual, and this pattern was higher for mPFC.
@@
 Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time.
-*Individuals without such stable nodes were not thresholded, but their maps were not discarded.
-Values in the eigenvector maps that did not meet threshold were set to zero, and set to 0.5 during binarization so that they would not bias the mean estimates across subjects.
-These thresholds yielded individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.
-(MANY NOTES: this can go into the results, and will need to add 1) % of subjects without stable nodes, and 2) the mean and range for the % of nodes that were stable.*
 
@@
 
-With these `r length(unique(str_remove(Yeo_labels, "_ROI")))` ROIs (`r (length(unique(str_remove(Yeo_labels, "_ROI"))) - 2)` overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using their full time series (4800 total TRs from four scanning sessions over two days).
+With these `r length(unique(str_remove(Yeo_labels, "_ROI")))` ROIs (`r (length(unique(str_remove(Yeo_labels, "_ROI"))) - 2)` overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using their full time series (approximately 4800 total TRs from four scanning sessions over two days).
 Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices).
@@
 ``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
-# Cross-method
-# Don't worry about plotting, since that's mainly for a general visualization
-RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary","Membership"), nSubjects = length(Summaries), subjNames = subjList)
-
-# Across subjects
+## Community number evaluation (across and within methods)
+# ARI between methods
+RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary", "Membership"), nSubjects = nSubj, subjNames = subjList)
+
+# Number of communities per subject for modularity
+nModularity <- sapply(Summaries, function(data) {max(data$Membership)}) # n of estimated communities by modularity
+
+# Median size of the extra (>2) communities estimated by modularity
+modularityCounts <- lapply(Summaries, function(data) {sort(count(data$Membership)$freq, decreasing = T)})
+modularityCounts_two <- sapply(modularityCounts, function(x) {mean(x[seq(2)], na.rm = T)})
+modularityCounts_extra <- sapply(modularityCounts, function(x) {mean(x[3:4], na.rm = T)})
+
+# eigenvalue-based diagnosis of optimal n of communities
+prcntDissection <- lapply(Summaries, function(data) {which(data$EigenVal < 0.00001)}) # how many consecutive 0s?
+prcntDissection <- mean((sapply(prcntDissection, length) + 1) == 2) * nSubj # % of subjects who only had 1 zero (thus optimal cuts = 2)
+
+## Across subjects
 # Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
@@
 
-#grid.arrange(pcc1,pfc1, ncol = 2)
-#grid.arrange(ecdfALL,ecdfPCC,ecdfPFC, ncol = 1)
-
 ```
@@
 This comparison showed that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
-The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not.
-This adds support to the division of these areas into DMN and non-DMN during rest.
-Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.
+Modularity showed a tendency to produce additional communities (median = `r median(nModularity)`, max = `r max(nModularity)`).
+However, these communities encompassed a small number of vertices (median = `r median(modularityCounts_extra, na.rm = T)`, IQR = `r IQR(modularityCounts_extra, na.rm = T)`) compared to the principal two (median = `r median(modularityCounts_two, na.rm = T)`, IQR = `r IQR(modularityCounts_two, na.rm = T)`), suggesting that the overall network is composed of two main communities.
+In addition, the estimation of the optimal number of cuts based on the rank of the first non-zero eigenvalue (see "Partition evaluation" for details) showed that `r prcntDissection` percent of the individual networks are best partitioned into two communities.
 
@@
 
-In order to address this the degree of stability of these partitions in time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the original pattern estimated using the whole time series (Figure 4).
+In order to estimate the degree of stability of these partitions in time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the partition computed using the whole time series (Figure 4).
 
@@
 
-There is precedence in thhe literature that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Tian2018](**add another citation, like the global map paper**).
+There is precedence in thhe literature that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
 Therefore, we asked whether the magnitude of these eigenvector values was associated with the stability of nodes in time.
@@
 
-``` {r Threshold this stupid stuff}
+``` {r Threshold values}
 # Get a FV threshold for each subject based on mean vertex stability
@@
 
+# number of subjects without stable vertices
+nUnstable <- threshDF %>% 
+                filter(Lower == 0, Upper == 0) %>% 
+                nrow
+
 rm(tempList)
@@
 We estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 95%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
-Vertices that under these thresholds were set to zero (instead of removed) so that the dimensionality of the data was unaffected, and 0.5 in the binarized maps so that they wouldn't bias the calculation of averages.
+Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, but their partitions were not discarded.
+Vertices under these thresholds were set to zero (instead of removed) so that the dimensionality of the data was unaffected, and 0.5 in the binarized maps so that they wouldn't bias the calculation of averages.
 Figure 6 (left) shows the updated partition for the one showed in figure 2.
@@
 
+# percent of stable nodes per subject
+prcntStable <- sapply(Summaries, function(data) {mean(data$FiedlerBinary != 0.5)})
+
 # Across subjects
@@
 
-With these thresholded maps, we recomputed the overall similarity of their functional organization across participants.
+The average percentage of stable vertices per subject was `r round(mean(prcntStable[prcntStable < 1]), digits = 2)` (SD = `r round(sd(prcntStable[prcntStable < 1]), digits = 2)`).
+With these thresholded partitions, we recomputed the overall similarity of their functional organization across participants.
 Compared to before, there was even less overall agreement of the full maps among individuals (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
@@
 PCC is better aligned across individuals than mPFC.", echo=FALSE, message = FALSE}
-par(xpd=T)
+par(xpd = T)
 corrplot(RI_PCC,

### 2019-03-14 Manuscript.Rmd
starting tsnr stuff

@@
 
-All network analyses were performed using the igraph package [@Csardi2006] in R 3.4.1 [@R Development Core Team].
+All network analyses were performed using the igraph package [@G.2006] in R 3.4.1 [@RTeam2018].
 To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
@@
 # For each permutation, reassign the study labels, maintaining the original number of studies per condition
-allStudies <- c(studyList_sv, studyList_dmn)
-nPerms <- 100 # reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
-nullDist <- numeric()
-
-for (i in seq(nPerms)) {
-
-  # provide feedback only if requested (if TRUE, it will show up in the doc or pdf file)
-  if (feedback) {
-    if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
-  }
-
-  # Sample all the studies and divide into 2 groups
-  randPerm <- sample(allStudies)
-  tmpSV <- randPerm[seq(length(studyList_sv))]
-  tmpDMN <- randPerm[-seq(length(studyList_sv))]
-
-  # Count the number of times each region was reported in the literature
-  tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-                      SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
-                      DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
-
-  # Perform the prop test for each pair and get the max chi-squared stat
-  nullDist[i] <- max(
-                  apply(tmpDF[,2:3], 1, function(data) {
-                    prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
-                    }
-                  ), na.rm = T)
-
-}
-
-# Now do the same for the actual data, to see how it compares to the null dist
-tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-                    SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
-                    DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
-                    propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
-                    propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
-
-# Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
-tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
-  round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
-  })
-tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
-
-# ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
-significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist, 0.95))
+# allStudies <- c(studyList_sv, studyList_dmn)
+# nPerms <- 100 # reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
+# nullDist <- numeric()
+# 
+# for (i in seq(nPerms)) {
+# 
+#   # provide feedback only if requested (if TRUE, it will show up in the doc or pdf file)
+#   if (feedback) {
+#     if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
+#   }
+#   
+#   # Sample all the studies and divide into 2 groups
+#   randPerm <- sample(allStudies)
+#   tmpSV <- randPerm[seq(length(studyList_sv))]
+#   tmpDMN <- randPerm[-seq(length(studyList_sv))]
+# 
+#   # Count the number of times each region was reported in the literature
+#   tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+#                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
+#                       DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
+# 
+#   # Perform the prop test for each pair and get the max chi-squared stat
+#   nullDist[i] <- max(
+#                   apply(tmpDF[,2:3], 1, function(data) {
+#                     prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
+#                     }
+#                   ), na.rm = T)
+# 
+# }
+# 
+# # Now do the same for the actual data, to see how it compares to the null dist
+# tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
+#                     SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
+#                     DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
+#                     propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
+#                     propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
+# 
+# # Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
+# tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
+#   round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
+#   })
+# tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
+# 
+# # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
+# significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist, 0.95))
 
@@
 # v23 right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
-# null 95th-q chi <- 10.04 (varies; this was done ith 100 but resembles the 5k one)
-
-```
-
-``` {r ROI computation, echo=FALSE, message = FALSE}
+# null 95th-q chi <- 9.11 (varies; this was done ith 100 but resembles the 5k one)
+
+```
+
+``` {r ROI computation (overlapping: old), echo=FALSE, message = FALSE}
 #TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
@@
 
-Figure 1 shows the resulting ROIs from these analyses.
-The 95th percentile of the permuted Chi-squared distribution was `r quantile(nullDist, 0.95)`.
-Based on this threshold, area 7m was the only one to show unique affiliation to DMN (observed $\chi^2$ = 8.45, *p* < 0.05), while SV was uniquely represented by area 25 (observed $\chi^2$ = 11.95, *p* < 0.01).
+Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the resulting significant ROIs from the permutation.
+The 95th percentile of the permuted Chi-squared distribution was 9.11.
+Based on this threshold, area 7m was the only one to show unique bilateral affiliation to DMN (Left: observed $\chi^2$ = 10.07, *p* = 0.034; Right: observed $\chi^2$ = 18.89, *p* < 0.0001), while SV was uniquely represented bilaterally by area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.014; Right: observed $\chi^2$ = 12.83, *p* = 0.014).
 The purpose of these supra-threshold areas was to identify the most-likely affiliation of the two communities in our partitions by their coverage of these regions.
@@
 Considering that our projection from volumetric spheres to the cortex might have attributed striatal reports to this region, we decided not to use it as a marker of SV.
-We also chose not to use area v23 due to its unilateral significance.
+We also chose not to use area v23 due to its unilateral significance (Right: observed $\chi^2$ = 11.51, *p* = 0.018).
 Instead, we only rely on area 7m to demarcate the DMN community.
@@
 
-This comparison showed that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`).
+This comparison showed that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)`, SD = `r round(sd(RI_all_within$Index), digits = 2)`).
 Modularity showed a tendency to produce additional communities (median = `r median(nModularity)`, max = `r max(nModularity)`).
@@
 ``` {r Noise Effects: tSNR Comparison, echo=FALSE, message = FALSE, cache = TRUE}
-## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
-# Flexibility vs SNR
-# Are vertices with lower SNR switching communities more often?
-# This is pointless if thresholded maps are used, since flexibility is bound to be super low 
-SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))
-
 # Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
@@
 Variance <- lapply(temp, read.csv)
+
+### new stuff
+# append the Rsquared values onto the current summaries
+# unfortunately this only counts on the DMN community
+appendVar <- lapply(seq(nSubj), function(subj) {left_join(Summaries[[subj]], Variance[[subj]], by = "Vertex")})
+
+# correlate tSNR with Rsquared before and after thresholds
+snrR2_cors <- list()
+
+snrR2_cors$pre_thresh <- sapply(appendVar, function(data) {
+  data %>% 
+    filter(!is.na(Rsquared)) %>%
+    select(varCoeff, Rsquared) %>%
+    cor(.$varCoeff)
+})[2, ]
+
+snrR2_cors$post_thresh <- sapply(appendVar, function(data) {
+  data %>% 
+    filter(!is.na(Rsquared), FiedlerBinary != 0.5) %>%
+    select(varCoeff, Rsquared) %>%
+    cor(.$varCoeff)
+})[2, ]
+
+# next get the mean tSNR of PCC and mPFC before/after
+snrR2_means <- list()
+snrR2_means <- sapply(appendVar, function(data) {
+  data %>% 
+    filter(!is.na(Rsquared)) %>%
+    mutate(region = ifelse(z > 0, "mPFC", "PCC")) %>%
+    group_by(region) %>% 
+    summarize(mean_tsnr = mean(varCoeff)) %>%
+    ungroup()
+})
+
+### end new stuff
 

### 2019-03-15 Manuscript.Rmd
complete restructuring of the tSNR section

@@
 
+``` {r Noise Effects: Per-subject Fiedler by R-sqd, fig.align="center", fig.width=3, fig.height=3, fig.cap = "FORMER Figure 13.
+Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
+setwd('./Variance/')
+temp <- list.files()
+Variance <- lapply(temp, read.csv)
+
+## append the Rsquared values onto the current summaries
+# unfortunately this only counts on the DMN community
+appendVar <- lapply(seq(nSubj), function(subj) {left_join(Summaries[[subj]], Variance[[subj]], by = "Vertex")})
+
+## correlate tSNR with Rsquared before and after thresholds
+snrR2_cors <- list()
+
+snrR2_cors$pre_thresh <- lapply(appendVar, function(data) {
+  data %>% 
+    filter(!is.na(Rsquared)) %>%
+    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
+    group_by(region) %>%
+    dplyr::summarise(correlation = cor(varCoeff, Rsquared)) %>%
+    ungroup()
+}) %>% reduce(left_join, by = "region")
+
+snrR2_cors$post_thresh <- lapply(appendVar, function(data) {
+  data %>% 
+    filter(!is.na(Rsquared), FiedlerBinary != 0.5) %>%
+    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
+    group_by(region) %>%
+    dplyr::summarise(correlation = cor(varCoeff, Rsquared)) %>%
+    ungroup()
+}) %>% reduce(left_join, by = "region")
+
+## next get the mean tSNR of PCC and mPFC before/after thresholding
+# the first piece of code gets each subject's mean tSNR per region, and reduces to a single matrix
+# the second one is similar, but filtering out vertices that didn't meet the threshold
+# the third one applies summary stats to each list to create a summary table
+snrR2_means <- list()
+
+snrR2_means$pre_thresh <- lapply(appendVar, function(data) {
+  data %>% 
+    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
+    group_by(region) %>% 
+    dplyr::summarise(mean_tsnr = mean(varCoeff)) %>%
+    ungroup()
+}) %>% reduce(left_join, by = "region")
+
+snrR2_means$post_thresh <- lapply(appendVar, function(data) {
+  data %>% 
+    filter(FiedlerBinary != 0.5) %>%
+    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
+    group_by(region) %>% 
+    dplyr::summarise(mean_tsnr = mean(varCoeff)) %>%
+    ungroup()
+}) %>% reduce(left_join, by = "region")
+
+# and compute summary stats on each 
+snrR2_means$overall <- sapply(snrR2_means, function(x) {
+  c(rowMeans(x[, -1]), apply(x[, -1], 1, sd))
+})
+rownames(snrR2_means$overall) <- c("mPFC_mean", "PCC_mean", "mPFC_SD", "PCC_SD")
+
+# permutation pre vs post
+tsnrPermute_mPFC <- permute(as.numeric(snrR2_means$pre_thresh[1, -1]), as.numeric(snrR2_means$post_thresh[1, -1]), paired = T)
+tsnrPermute_PCC <- permute(as.numeric(snrR2_means$pre_thresh[2, -1]), as.numeric(snrR2_means$post_thresh[2, -1]), paired = T)
+
+# effect size pre vs post
+tsnrCohen_mPFC <- CohenD(as.numeric(snrR2_means$post_thresh[1, -1]), as.numeric(snrR2_means$pre_thresh[1, -1]))
+tsnrCohen_PCC <- CohenD(as.numeric(snrR2_means$post_thresh[2, -1]), as.numeric(snrR2_means$pre_thresh[2, -1]))
+
+# ##### old
+# 
+# # Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
+# tempComm_PCC <- lapply(tempComm_PCC, filter, FiedlerVec != 0)
+# tempComm_PFC <- lapply(tempComm_PFC, filter, FiedlerVec != 0) 
+# SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) {permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval})
+# SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
+# SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) {cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)})
+# prcntSig <- mean(SNR_PCCvsPFC_perm < 0.05) * 100
+# 
+# # Get the mean SNR for each region and compare overall levels 
+# SNR_meanPCC <- sapply(tempComm_PCC, function(data) {mean(data$varCoeff)})
+# SNR_meanPFC <- sapply(tempComm_PFC, function(data) {mean(data$varCoeff)})
+# SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
+#                      Comparison = permute(SNR_meanPCC, SNR_meanPFC)$Pval,
+#                      ES = cohenD(SNR_meanPCC, SNR_meanPFC))
+# rm(SNR_meanPCC, SNR_meanPFC)
+
+```
+
+To discard the possibility that the higher inter-subject variability in mPFC was driven by retaining vertices with lower signal quality, we compared the mean temporal signal to noise ratio (tSNR) for each region pre and post thresholding.
+We used subject time series that were not demeaned, but were otherwise equivalent to the data originally used.
+Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC actually significantly increased post-thresholding across subjects (Pre: mean = `r snrR2_means$overall[1, 1]`, SD = `r snrR2_means$overall[3, 1]`; Post: mean = `r snrR2_means$overall[1, 2]`, SD = `r snrR2_means$overall[3, 2]`; paired permutation p-value = `r tsnrPermute_mPFC$Pval`, Cohen's D = `r tsnrCohen_mPFC[1]`), whereas the signal quality in PCC was preserved (Pre: mean = `r snrR2_means$overall[2, 1]`, SD = `r snrR2_means$overall[4, 1]`; Post: mean = `r snrR2_means$overall[2, 2]`, SD = `r snrR2_means$overall[4, 2]`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r tsnrCohen_PCC[1]`).
+
 ### *Partition Comparison: Day 1 vs Day 2*
@@
 This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with relatively small amounts of data in spite of a reduction in the estimates.
-
-### *Potential Noise Effects*
-
-*NOTE: this part seems less relevant now that we are thresholding the partitions. Might be better to add to sliding window section*
-
-``` {r Noise Effects: tSNR Comparison, echo=FALSE, message = FALSE, cache = TRUE}
-# Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
-tempComm_PCC <- lapply(tempComm_PCC, filter, FiedlerVec != 0)
-tempComm_PFC <- lapply(tempComm_PFC, filter, FiedlerVec != 0) 
-SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) {permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval})
-SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
-SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) {cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)})
-prcntSig <- mean(SNR_PCCvsPFC_perm < 0.05) * 100
-
-# Get the mean SNR for each region and compare overall levels 
-SNR_meanPCC <- sapply(tempComm_PCC, function(data) {mean(data$varCoeff)})
-SNR_meanPFC <- sapply(tempComm_PFC, function(data) {mean(data$varCoeff)})
-SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
-                     Comparison = permute(SNR_meanPCC, SNR_meanPFC)$Pval,
-                     ES = cohenD(SNR_meanPCC, SNR_meanPFC))
-rm(SNR_meanPCC, SNR_meanPFC)
-```
-
-Even though our findings point to a stable representation of each subject's unique DMN organization, it is still possible that they were driven by considerable levels of signal noise often found in mPFC (its ventral segment in particular).
-To account for any residual noise, we computed the temporal signal to noise ratio (tSNR) for each vertex in each subject's minimally preprocessed fMRI data (i.e.
-mean of each vertex's time series over its standard deviation).
-Note that we did this for the vertices that survived the threshold.
-The tSNR of all vertices were averaged per region and subject (Figure 11), which showed that mPFC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="mPFC"]), digits = 2)`) and PCC (mean = `r round(mean(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SNR_meanComp$Values$SNR[SNR_meanComp$Values$Region=="PCC"]), digits = 2)`) had similar tSNR (permutation, *p* = `r SNR_meanComp$Comparison`, Cohen's D = `r round(SNR_meanComp$ES, digits = 2)`).
-To more precisely examine this difference, we performed subject-wise comparisons of the tSNR values of all vertices between PCC and mPFC (5000 iterations each).
-About `r round(prcntSig, digits = 2)` percent of the comparisons proved significant at alpha = 0.05 (FDR corrected), but these differences had low effect sizes (mean Cohen's D = `r round(mean(SNR_PCCvsPFC_ES), digits = 2)`).
-These findings further confirm that the idiosyncrasies observed in these areas (and in mPFC in particular) are not a function of measurement noise.
-
-``` {r Noise Effects: Per-subject Fiedler by R-sqd, fig.align="center", fig.width=3, fig.height=3, fig.cap = "FORMER Figure 13.
-Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
-setwd('./Variance/')
-temp <- list.files()
-Variance <- lapply(temp, read.csv)
-
-### new stuff
-# append the Rsquared values onto the current summaries
-# unfortunately this only counts on the DMN community
-appendVar <- lapply(seq(nSubj), function(subj) {left_join(Summaries[[subj]], Variance[[subj]], by = "Vertex")})
-
-# correlate tSNR with Rsquared before and after thresholds
-snrR2_cors <- list()
-
-snrR2_cors$pre_thresh <- sapply(appendVar, function(data) {
-  data %>% 
-    filter(!is.na(Rsquared)) %>%
-    select(varCoeff, Rsquared) %>%
-    cor(.$varCoeff)
-})[2, ]
-
-snrR2_cors$post_thresh <- sapply(appendVar, function(data) {
-  data %>% 
-    filter(!is.na(Rsquared), FiedlerBinary != 0.5) %>%
-    select(varCoeff, Rsquared) %>%
-    cor(.$varCoeff)
-})[2, ]
-
-# next get the mean tSNR of PCC and mPFC before/after
-snrR2_means <- list()
-snrR2_means <- sapply(appendVar, function(data) {
-  data %>% 
-    filter(!is.na(Rsquared)) %>%
-    mutate(region = ifelse(z > 0, "mPFC", "PCC")) %>%
-    group_by(region) %>% 
-    summarize(mean_tsnr = mean(varCoeff)) %>%
-    ungroup()
-})
-
-### end new stuff
-
-### Grab some of the other measures from the overall summary
-for (i in seq(nSubj)) {
-  tempIndex <- Summaries[[i]]$Vertex %in% Variance[[i]]$Vertex
-  Variance[[i]]$SubjID <- rep(subjList[i], nrow(Variance[[i]]))
-  Variance[[i]]$FiedlerVec <- Summaries[[i]]$FiedlerVec[tempIndex]
-  Variance[[i]]$Flexibility <- Summaries[[i]]$slideFlexibility[tempIndex]
-  Variance[[i]]$propDMN <- Summaries[[i]]$slidePropDMN[tempIndex]
-  Variance[[i]]$varCoeff <- Summaries[[i]]$varCoeff[tempIndex]
-  Variance[[i]]$Region <- ifelse(Variance[[i]]$tempY < 0, "PCC", "mPFC")
-}
-
-# let's put everyone's data together and filter out according to the threshold
-allVariance <- do.call(rbind, Variance) %>%
-                  filter(FiedlerVec != 0)
-
-# get the mean and SE of the R-squared values per subject/region
-allVariance_sumarized <- aggregate(allVariance$Rsquared ~ allVariance$SubjID + allVariance$Region, FUN = 'mean')
-colnames(allVariance_sumarized) <- list("SubjID", "Region", "meanRsquared")
-allVariance_sumarized$SEM <- aggregate(allVariance$Rsquared ~ allVariance$SubjID + allVariance$Region, FUN = function(data) {sd(data)/sqrt(length(data))})[ , 3]
-
-# Create a new data frame with values restricted to mPFC (for plotting and further stats)
-mPFCVariance <- allVariance[allVariance$Region == "mPFC", ]
-
-# Get the correlations between Z-axis, R2, and tSNR for every subject (to take mean and SD in text)
-# I just came up with this, so the code should be made more parsimonious in the future (like, why bind and then split...?)
-tempSubj <- split(mPFCVariance, f = mPFCVariance$SubjID)
-# Get the correlation coefficients
-noiseCors <- data.frame(R2vtSNR = sapply(tempSubj, function(data) {cor(data$Rsquared, data$varCoeff)}),
-                        ZvtSNR = sapply(tempSubj, function(data) {cor(data$tempZ, data$varCoeff)}),
-                        ZvR2 = sapply(tempSubj, function(data) {cor(data$tempZ, data$Rsquared)}))
-rm(tempSubj)
-
-# plot
-# There is a strong linear relationship between the Fiedler vector and the R-squared values
-# These match perfectly on the brain when inspected qualitatively
-v1 <- ggplot(data = allVariance) + 
-  geom_smooth(aes(FiedlerVec, Rsquared, group = SubjID), fill = "gray70", color = "gray30", show.legend = F) + 
-  labs(x = "Fiedler Vector Values", y = "R-Squared Values") + 
-  theme_classic()
-
-# The lower the R-squared, the more likely it is for nodes to change affiliation throughout time
-v2 <- qplot(data = allVariance, Rsquared, Flexibility, color = SubjID, fill = SubjID, geom = "smooth") + theme_classic()
-
-# And of course (given the relationship with the Fiedler vector), there's a sigmoidal relationship between R-squared vals and proportion of DMN affiliation
-# only showing the upper side of the sigmoid here, as these values are restricted to the DMN community
-v3 <- qplot(data = allVariance, Rsquared, propDMN, color = SubjID, fill = SubjID, geom = "smooth") + theme_classic()
-
-# Finally, it's worth comparing the R-squared values between PCC and mPFC
-# The intuition is that the variance explained by the community might be lower for mPFC given its noise
-# And the answer is: mPFC yields significantly lower R-squares per subject and overall, as expected.
-# To formally compare this (and given the binomial distribution of R-squares in mPFC), I report the Cohen's D per subject for PCC vs mPFC
-v4 <- ggplot(data = allVariance_sumarized, aes(x = SubjID, y = meanRsquared, group = Region, color = Region)) +
-  geom_point(show.legend = F) +
-  geom_line(show.legend = F) +
-  geom_errorbar(aes(ymin = meanRsquared - SEM, ymax = meanRsquared + SEM)) +
-  scale_color_manual(values = Cols[seq(2)]) +
-  ylim(0,0.5) +
-  labs(x = "Subject", y = "Mean R-squared") +
-  theme_classic() +
-  theme(axis.text.x = element_blank())
-
-v5 <- qplot(data = allVariance, Region, Rsquared, fill = Region, geom = "boxplot") + theme_classic()
-Rsq_PCCvsPFC_Wilcox <- sapply(Variance, function(data) {wilcox.test(data$Rsquared[data$Region == "PCC"], data$Rsquared[data$Region == "mPFC"])$p.value})
-Rsq_PCCvsPFC_Wilcox <- p.adjust(Rsq_PCCvsPFC_Wilcox, method = "BY")
-prcntSig <- (sum(Rsq_PCCvsPFC_Wilcox < 0.05) / nSubj) * 100
-Rsq_PCCvsPFC_ES <- sapply(Variance, function(data) {cohenD(data$Rsquared[data$Region == "PCC"], data$Rsquared[data$Region == "mPFC"])})
-
-# This begs the question of a "gradient of noise" along the z-axis on mPFC
-# Not really, but the coefficient of variation derived from minimally preprocessed data does show a strong trend
-# Namely, the more ventral, the lower the SNR
-# v6 <- ggplot(data = allVariance, aes(Rsquared, tempZ, fill = Region)) +
-#         geom_point(color = "black", pch = 21, alpha = 0.1) + 
-#         scale_fill_manual(values = Cols[seq(2)]) +
-#         theme_classic()
-# v7 <- ggplot(data = allVariance, aes(varCoeff, tempZ, fill = Region)) +
-#         geom_point(color = "black", pch = 21) + 
-#         scale_fill_manual(values = Cols[seq(2)]) +
-#         theme_classic()
-
-#v1
-
-```
-
-To further interrogate the potential effect of noise in our results, we computed the variance explained by activity from each DMN vertex on the mean time series of the DMN community.
-If the signal quality issues persisted after preprocessing the data, we expected that noisy vertices would have the least explicative power on the activity of the DMN community as a whole.
-This also implied lower $R^2$ values for mPFC.
-Indeed, we found that for each subject, $R^2$ values tended to be higher for PCC (`r prcntSig` percent of Wilcoxon ranksum tests across subjects had *p* values < 0.001; mean Cohen's D = `r round(mean(Rsq_PCCvsPFC_ES), digits = 2)`).
-These results suggest that, overall, vertices in mPFC tended to be less in synchrony with the activity of the DMN community as a whole.
-Furthermore, the level of tSNR showed a moderate correlation with $R^2$ values across participants (mean *r* = `r round(mean(noiseCors$R2vtSNR), digits = 2)`; SD = `r round(sd(noiseCors$R2vtSNR), digits = 2)`), meaning that noisier vertices were less in synchrony with the general activity of the DMN.
-
-Given this trend, we asked whether there is a "gradient of noise" along the z-axis of mPFC, such that more ventral vertices would both be noisier and explain the least amount of DMN variance.
-Here we found that while $R^2$ are somewhat correlated with dorsal-ventral placement across subjects (mean *r* = `r round(mean(noiseCors$ZvR2), digits = 2)`; SD = `r round(sd(noiseCors$ZvR2), digits = 2)`), there is no clear relationship with the z-axis across subjects (Figure 12).
-Specifically, low $R^2$ are evenly distributed along this axis, denoting a degree of orthogonality between these features.
-Conversely, tSNR showed a strong linear relationship with the position of the vertex along this axis (mean *r* = `r round(mean(noiseCors$ZvtSNR), digits = 2)`; SD = `r round(sd(noiseCors$ZvtSNR), digits = 2)`).
-These results contextualize the degree of synchrony of mPFC vertices in terms of potential noise.
-While still an important factor, it is unlikely that the degree of within-subject pattern stability observed here could be due mostly to highly structured mPFC noise.
 
@@
 
-``` {r Noise Effects: tSNR Comparison (Fig.
-12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "WEIRD: Mean tSNR for mPFC and PCC across participants.
-This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE}
-# Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
-snrmeanComp_plot <- ggplot(data = SNR_meanComp$Values, aes(Region, SNR, fill = Region)) +
-  geom_boxplot(show.legend = F) +
-  scale_fill_manual(values = Cols[seq(2)]) +
-  labs(x = "", y = "tSNR") +
-  theme(text = element_text(size=35)) +
-  theme_classic()
-snrmeanComp_plot
-```
-
-<!--
-``` {r Noise Effects: Mean R-sqd mPFC and PCC (Fig.
-13), fig.align="center", fig.width=6, fig.height=4, fig.cap = "Differences in mean R-squared values for each region per participant.
-The figure shows that PCC vertices tend to be more coupled with the overall dynamics of DMN across subjects.", echo=FALSE, message = FALSE}
-#v4
-```
--->
-
-``` {r Noise Effects: R-sqd vs tSNR (Fig.
-13), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Vertex tSNR values across all subjects are correlated with their position along the z-axis, with vmPFC showing the lowest tSNR (left).
-However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE}
-# grid.arrange(v6, v7, ncol = 2)
-# par(mfrow = c(1,2))
-# smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
-#               xlab = "R-squared Value",
-#               ylab = "Z-Coordinate")
-# 
-# smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
-#               xlab = "Coefficient of Variation (SNR)",
-#               ylab = "")
-
-# ALTERNATIVE IDEA FOR A FIGURE: BRAIN MAPS WITH THESE VALUES. THAT SAID, R2 MAPS LOOK THE SAME AS FV ONES, SO...
-s1 <- ggplot(data = mPFCVariance, aes(varCoeff, tempZ)) +
-  geom_bin2d(bins = 250, show.legend = F) +
-  scale_fill_continuous(low = "grey30", high = "grey70") +
-  geom_density2d(color = Cols[2]) +
-  labs(x = "tSNR", y = "Z-Coordinate") +
-  theme_classic()
-
-s2 <- ggplot(data = mPFCVariance, aes(Rsquared, tempZ)) +
-  geom_bin2d(bins = 250, show.legend = F) +
-  scale_fill_continuous(low = "grey30", high = "grey70") +
-  geom_density2d(color = Cols[2]) +
-  labs(x = "R-squared value", y = "Z-Coordinate") +
-  xlim(c(0,1)) +
-  theme_classic()
-
-grid.arrange(s1, s2, ncol = 2)
-```
-
 ``` {r Correlation vs community detection (Fig.

### 2019-03-15 Manuscript.Rmd
second draft ready

@@
 ---
-title: 'Individual heterogeneity in the functional topography of the medial prefrontal cortex'
+title: 'Individual heterogeneity in the functional topography of the default-mode network in medial prefrontal cortex'
 author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
@@
 We then produced rsFC networks of all the surface vertices within these regions of interest (ROI) for each of 100 individual resting state dataset from the Human Connectome Project (HCP)[@VanEssen2012], and estimated the extent of DMN coverage through spectral partitioning.
+Focusing on individual vertices in this search space rather than the parcels (as is usual in brain network analyses) allowed us to finely delineate the topographical extent of each community.
 We found that these areas of overlap can be partitioned into two communities that topographically vary across subjects, but that follow a comon organizational principle.
@@
 [-@Yeo2011].
-First, Ww selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial wall.
-Next, we overlayed these networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained parcels that shared at least 15% of vertices with them.
+First, We selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial wall.
+Next, we overlayed these networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained parcels that shared a considerable amount of vertices with them (visually inspected).
 This resulted in 45 regions of interest (ROI) across hemispheres (Table 1).
@@
 For DMN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009].
-These represent the surviving areas post-statistical thresholding from each study.
-For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere[@Wager2009].
+These coordinates represent the surviving areas post-statistical thresholding from each study.
+For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009].
 The indicator map for each study was then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl2012] (http://surfer.nmr.mgh.harvard.edu/).
@@
 
-Oue fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
+Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
 Each subject's data was acquired over two days at Washington University in St.
 Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany).
-Four resting state runs (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised 1200 time points(14 min 33 s) for a totalof 4800 time points.
+Four resting state runs (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised 1200 time points(14 min 33 s) for a total of 4800 time points.
 Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other.
@@
 This method enforces the partition of a network into similarly-sized communities, and guarantees that they share at least one edge [@Chung1999].
-In this way, spectral partitioning avoids producing communities that are too small to be physiologically meaningful (for example, isolated vertices that are considerably affected by measurement noise).
+In this way, spectral partitioning avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
 Every individual partition is therefore binarized by sign in order to evaluate the topography of each community (see next section for details).
 Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community to be the one containing the DMN-specific PCC parcel identified in our meta-analysis.
-Given the high density of these networks (see Results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].
+The high density of these networks (see Results) ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].
 
@@
 [-@Clauset2004].
-This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
-The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.
-Unlike SP, modularity can fractionate a network into more than two functional groups.
-We assumed that if the partitions from the bounded and unbounded community detection methods showed high level of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
-We also diagnose our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by spectral partitioning to be non-zero.
+*(TBD) This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
+The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.* Unlike SP, modularity can fractionate a network into more than two functional groups.
+We assumed that if the partitions from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
+We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by spectral partitioning to be non-zero.
 This eigenvalue serves as an estimator of the optimal number of communities in a network [@Chung1999], such that a rank of two in our partitions justifies limiting the number of communities to two.
@@
 We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows.
-To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full dataset).
+To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series).
 Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time.
@@
 These spatial correlations were aimed to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-The two methods are expected to produce somewhat similar arrangements, but the one displaying the higher within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]).
+The two methods were expected to produce somewhat similar arrangements, but the one displaying the higher within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]).
 We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
@@
 Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
-The 45 areas considered were limited to the medial portion of the default mode and limbic networks, as defined by the Yeo et al.[-@Yeo2011] 17 network parcellation.
+The 45 areas considered were limited to the medial portion of the default mode and limbic networks, as defined by the Yeo et al.'s [-@Yeo2011] 17 network parcellation.
 Unique areas were identified by first permuting the affiliation of each study (i.e.
-DMN or SV) to create a distribution of Chi-squared statistics based on the comparison of the number of reports per area between literatures (see Methods for details).
+DMN or SV) to create a distribution of chi-squared statistics based on the comparison of the number of reports per area between literatures (see Methods for details).
 This putative null distribution was used to identify regions more often reported in either literature.
@@
 Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the resulting significant ROIs from the permutation.
-The 95th percentile of the permuted Chi-squared distribution was 9.11.
+The 95th percentile of the permuted chi-squared distribution was 9.11.
 Based on this threshold, area 7m was the only one to show unique bilateral affiliation to DMN (Left: observed $\chi^2$ = 10.07, *p* = 0.034; Right: observed $\chi^2$ = 18.89, *p* < 0.0001), while SV was uniquely represented bilaterally by area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.014; Right: observed $\chi^2$ = 12.83, *p* = 0.014).
@@
 Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices).
-After correcting for multiple comparisons, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
+After correcting for multiple comparisons, we performed spectral partitioning on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
 On average, networks had high densities (i.e.
-highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`).
-This high degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].
+highly connected) regardless of whether they were produced with a single run all the full time series (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`).
+This high degree of density is important, as this method is known to face challenges when computed on sparse networks [@Fortunato2016].
 
@@
 This non-DMN section extends posteriorly onto pregenual cinglate cortex (area a24).
-Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than subjective value [@Hiser2018].
 
@@
 Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model.
-Since modularity is not bound to a desired number of partitions, it was capable of finding more than two communities in our datset.
+Since modularity is not bound to a desired number of communities, it was capable of finding more than two in our datset.
 We quantified the cross-method agreement with the adjusted rand index (ARI).
@@
 Modularity showed a tendency to produce additional communities (median = `r median(nModularity)`, max = `r max(nModularity)`).
-However, these communities encompassed a small number of vertices (median = `r median(modularityCounts_extra, na.rm = T)`, IQR = `r IQR(modularityCounts_extra, na.rm = T)`) compared to the principal two (median = `r median(modularityCounts_two, na.rm = T)`, IQR = `r IQR(modularityCounts_two, na.rm = T)`), suggesting that the overall network is composed of two main communities.
+However, these communities encompassed a small number of vertices (mean = `r mean(modularityCounts_extra, na.rm = T)`, IQR = `r IQR(modularityCounts_extra, na.rm = T)`) compared to the principal two (mean = `r mean(modularityCounts_two, na.rm = T)`, IQR = `r IQR(modularityCounts_two, na.rm = T)`), suggesting that the overall network is composed of two main communities.
 In addition, the estimation of the optimal number of cuts based on the rank of the first non-zero eigenvalue (see "Partition evaluation" for details) showed that `r prcntDissection` percent of the individual networks are best partitioned into two communities.
 
-Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was fairly low agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was moderate agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
 However, qualitative inspection of the brain community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects.
 To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3).
-Indeed, this analysis showed that the functional topology of PCC is better maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`)(paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+Indeed, this analysis showed that the functional topology of PCC is better maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`)(paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
 
@@
 
-This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation,*p* = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
 These results suggest that the each individual's DMN distribution is cosiderably stable in time.
@@
 We used subject time series that were not demeaned, but were otherwise equivalent to the data originally used.
-Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC actually significantly increased post-thresholding across subjects (Pre: mean = `r snrR2_means$overall[1, 1]`, SD = `r snrR2_means$overall[3, 1]`; Post: mean = `r snrR2_means$overall[1, 2]`, SD = `r snrR2_means$overall[3, 2]`; paired permutation p-value = `r tsnrPermute_mPFC$Pval`, Cohen's D = `r tsnrCohen_mPFC[1]`), whereas the signal quality in PCC was preserved (Pre: mean = `r snrR2_means$overall[2, 1]`, SD = `r snrR2_means$overall[4, 1]`; Post: mean = `r snrR2_means$overall[2, 2]`, SD = `r snrR2_means$overall[4, 2]`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r tsnrCohen_PCC[1]`).
+Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC actually significantly increased post-thresholding across subjects (Pre: mean = `r snrR2_means$overall[1, 1]`, SD = `r snrR2_means$overall[3, 1]`; Post: mean = `r snrR2_means$overall[1, 2]`, SD = `r snrR2_means$overall[3, 2]`; paired permutation p-value = `r tsnrPermute_mPFC$Pval`, Cohen's D = `r tsnrCohen_mPFC[1]`), whereas the mean signal quality in PCC was unaffected (Pre: mean = `r snrR2_means$overall[2, 1]`, SD = `r snrR2_means$overall[4, 1]`; Post: mean = `r snrR2_means$overall[2, 2]`, SD = `r snrR2_means$overall[4, 2]`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r tsnrCohen_PCC[1]`).
 
@@
 
-The relative high variability seen in the aggregate map could be due to residual noise that was not captured by the sliding window analysis, or variations in the functional organization of mPFC across days.
+The relative high variability seen in the aggregate map could be due to variations in the functional organization of mPFC across days.
 While the sliding window analysis suggested that these partitions are stable, many of the windows contained data from both days.
@@
 
-Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 9), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+Computing SP on networks from individual sessions showed that we can still coarsely capture a subject's unique organizational pattern (Figure 9), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
 We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 10).
@@
 We can see again that the ratios for mPFC were higher than those of PCC (permutation,*p*= `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
-This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with relatively small amounts of data in spite of a reduction in the estimates.
+This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with small amounts of data in spite of a reduction in the estimates.
 
@@
 The computational demands of our approach escalate quickly as the number of vertices increases.
-We thus explored the possible advantage to using graph-theoretic approaches over a simple seed-based functional connectivity analysis from PCC.
+We thus explored the possible advantage to using community detection over a simple seed-based functional connectivity analysis from PCC.
 Given that other groups have found the spatial distribution of the DMN to be considerably stable within individuals [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018], we examined whether maps generated with spectral partitioning were more similar per subject across days than those computed from seed-based correlations.
@@
 We thus visually inspected these subjects (n = 7) and reverted the labeling when it was clear that the topologies aligned across days.
-Figure 13 shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alingment between methods, but particularly high agreement within subject and method.
-
-Figure 14 shows the overall degree of similarity across days for patterns dervied using community detection, seed-based correlation, and across methods (i.e.
+Figure 11 shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alingment between methods, but particularly high agreement within subject and method.
+
+Figure 12 shows the overall degree of similarity across days for patterns dervied using community detection, seed-based correlation, and across methods (i.e.
 day one community detection versus day two seed-based correlation).
@@
 It is worth noting that the cross-method agreement is fair, meaning that both approaches show similar topological features.
-These findings suggest that graph-theoretic community detection algorithms provide a better way to detect stable functional topologies, an important factor when faced with the levels of noise present in mPFC.
+These findings suggest that graph-theoretic community detection algorithms provide a better way to detect stable functional topologies.
 
@@
 Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to find seed vertices in DLPFC that can reproduce them.
-The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 15.
+The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 13.
 
@@
 | :------------------- | ----------------------------------------: |
-| ROIs                 | `r print(str_remove(Yeo_labels, "_ROI"))` |
+| ROIs                 | `r str_remove(Yeo_labels, "_ROI")` |
 

### 2019-03-22 Manuscript.Rmd
updates to figures

@@
 output:
+  pdf_document: 
+    keep_tex: true
   word_document: 
     reference_docx: Style_reference_draft.docx
-  pdf_document: 
-    keep_tex: true
   html_document: default
@@
 
-Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere
+Cols <- c("aquamarine4", "#D9541A", rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere
 
@@
 ```{r Meta-analysis ROIs (Fig.
-1), out.width="50%", fig.align = "center", fig.cap= "Proportion of times each ROI was reported in each literature (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom).
+1), out.width="50%", fig.align = "center", fig.cap= "A: Proportion of times each ROI was reported in each literature.
+B: common and unique brain regions associated with DMN and subjective value.
 DMN regions defined by Yeo et al.
 (2011) in blue, which encompass areas of considerable overlap between DMN and SV.
-Literature-specific regions (7m in yellow and 25 in red) were identified from a permutation analysis of chi-squared tests comparing these literatures."}
+Literature-specific regions (bilateral 7m and right v23 in yellow, and bilateral 25 in red) were identified from a permutation analysis of chi-squared tests comparing these literatures."}
 # Change to inflated eventually
@@
 Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
-The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
+The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m, bordered)."}
 include_graphics("./Images/FB_FV_example.png")
@@
 ``` {r Partition comparison: all 2 (Fig.
-4), fig.align="center", out.width = "40%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
+3), fig.align="center", out.width = "50%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
 PCC is better aligned across individuals than mPFC.", echo=FALSE, message = FALSE}
-par(xpd = T)
-corrplot(RI_PCC,
-         is.corr = F, 
-         method = "color",
-         type = "lower", 
-         tl.pos = "n", 
-         tl.cex = 0.1, 
-         #cl.lim = c(0,1),
-         cl.length = 3,
-         #addgrid.col = "grey99",
-         cl.pos = "r",
-         mar = c(1,1,2,0))
-corrplot(RI_PFC, 
-         is.corr = F, 
-         method = "color", 
-         type = "upper", 
-         tl.pos = "n", 
-         tl.cex = 0.1,
-         cl.pos = "n",
-         #addgrid.col = "grey90",
-         mar = c(1,1,2,0), 
-         add = T)
-segments(0.5,0.5,0.5,100.5, lwd = 2)
-segments(0.5,0.5,100.5,0.5, lwd = 2)
-segments(0.5,100.5,100.5,100.5, lwd = 2)
-segments(100.5,0.5,100.5,100.5, lwd = 2)
-mtext(expression(bold("Subject Partitions")), line = 3)
-mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
-mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
-mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")
-
-```
-
-``` {r Stability per subject: PCC vs mPFC (Fig 5), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Mean agreement between partitions from each sliding window and the map produced with the whole data per subject, for mPFC and PCC separately (left), and the distribution of standard deviations along the time series per subject (right).
-There was strong (at least 50 percent after adjusting for chance) and stable agreement in both regions, but higher for PCC.", echo=FALSE, message = FALSE}
-
-# # plots
-# SC_PCCPFC_plot <- ggplot(data = SC_PCC)
-# SC_PCCPFC_plot <- SC_PCCPFC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[2], alpha = 0.3, show.legend = F) +
-#   geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
-#   ylim(0,1) + 
-#   labs(y = "ARI") +
-#   theme(text = element_text(size=35)) +
-#   geom_line(data = SC_PFC, aes(x = Window, y = Index, group = as.factor(SubjID)), color = Cols[1], alpha = 0.3, show.legend = F) +
-#   geom_smooth(data = SC_PFC, aes(x = Window, y = Index), color = Cols[1], fill = Cols[1]) +
+# code to produce the plot
+# par(xpd = T)
+# corrplot(abs(RI_PCC), # absolute for display purposes only, as it avoids the couple of negative ARIs and evens out the color bar
+#          is.corr = F, 
+#          method = "color",
+#          type = "lower", 
+#          tl.pos = "n", 
+#          tl.cex = 0.1, 
+#          cl.lim = c(0,1),
+#          cl.length = 3,
+#          #addgrid.col = "grey99",
+#          cl.pos = "r",
+#          mar = c(1,1,2,0))
+# corrplot(RI_PFC, 
+#          is.corr = F, 
+#          method = "color", 
+#          type = "upper", 
+#          tl.pos = "n", 
+#          tl.cex = 0.1,
+#          cl.pos = "n",
+#          #addgrid.col = "grey90",
+#          mar = c(1,1,2,0), 
+#          add = T)
+# segments(0.5,0.5,0.5,100.5, lwd = 2)
+# segments(0.5,0.5,100.5,0.5, lwd = 2)
+# segments(0.5,100.5,100.5,100.5, lwd = 2)
+# segments(100.5,0.5,100.5,100.5, lwd = 2)
+# mtext(expression(bold("Subject Partitions")), line = 3)
+# mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
+# mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
+# mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")
+
+include_graphics("./Images/similarity_all.png")
+
+```
+
+``` {r Stability per subject: Fiedler vector vs prop.
+DMN plot (Fig 5), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
+Grey lines display each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
+# code to generate plot
+# Fiedler Vector x proportion of times a vertex was affiliated with DMN
+# SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
+#   geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
+#   #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
+#   geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
+#   labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
+#   scale_y_continuous(limits = c(0,1)) +
 #   theme_classic()
 
-SC_PCCPFC_mean_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=as.factor(Region), y=Index, fill = as.factor(Region))) + 
-  geom_boxplot(show.legend = F) + 
-  scale_fill_manual(values = Cols[seq(2)]) +
-  ylim(0,1) +
-  labs(x = "", y = "") +
-  theme(text = element_text(size=35), axis.text.y = element_text(size=40)) +
-  theme_classic()
-
-SC_PCCPFC_sd_plot <- ggplot(data = SC_PCCPFC_summary, aes(x=SD, fill = as.factor(Region))) + 
-  scale_fill_manual(values = Cols[seq(2)]) +
-  geom_density(color = "black", alpha = 0.7, show.legend = F) + 
-  xlim(0,1) +
-  labs(x = "SD") +
-  theme(text = element_text(size=35)) +
-  theme_classic()
-
-grid.arrange(SC_PCCPFC_mean_plot, SC_PCCPFC_sd_plot, ncol = 2)
-
-```
-
-``` {r Stability per subject: Fiedler vector vs prop.
-DMN plot (Fig 6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
-Grey lines display each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
-# Fiedler Vector x proportion of times a vertex was affiliated with DMN
-SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
-  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
-  #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
-  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
-  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
-  scale_y_continuous(limits = c(0,1)) +
-  theme_classic()
-
-SC_FVvPDMN_plot
-```
-
-```{r Thresholded maps (Fig 7), out.width = "100%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
+include_graphics("./Images/SW_props.png")
+
+```
+
+\bigskip
+
+```{r Thresholded maps (Fig 7), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
 Values that did not meet the threshold were set to zero on the Fiedler vector, and 0.5 on the binarized maps (giving rise to a third community of high-variability vertices).
@@
 This aggregate map shows the common organizational principle of the DMN and non-DMN communities, while also pinpointing the relatively high level of variability in mPFC."}
-# Change to inflated eventually
+
 include_graphics("./Images/thresholded.png")
-```
-
-``` {r Partition comparison: halves (Fig.
-8), fig.align="center", out.width = "60%", fig.cap = "Similarity matrices for 10 example participants showing pattern agreement across days for the whole brain (left), and for PCC and mPFC separately (right).
-These figures show high agreement within (but not between) subjects, with mPFC again showing higher heterogeneity in the group.", echo=FALSE, message = FALSE}
-# plots
-par(mfrow=c(1,2))
-corrplot(RI_all_between_halves_plot, 
-         is.corr = F, 
-         method = "color",
-         addgrid.col = "grey90",
-         tl.pos = "n", 
-         tl.col = "black",
-         tl.cex = 0.1,
-         cl.pos = "n",
-         #cl.lim = c(0,1),
-         cl.length = 3,
-         mar = c(1.1,1.1,1.1,1.1))
-# segments(0.5,0.5,0.5,20.5, lwd = 2)
-# segments(0.5,0.5,20.5,0.5, lwd = 2)
-# segments(0.5,20.5,20.5,20.5, lwd = 2)
-# segments(20.5,0.5,20.5,20.5, lwd = 2)
-mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
-mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
-corrplot(RI_PCC_halves_plot, 
-         is.corr = F,     
-         method = "color",
-         type = "lower", 
-         tl.pos = "n", 
-         #cl.lim = c(0,1),
-         cl.pos = "r",
-         addgrid.col = "grey90",
-         cl.length = 3)
-corrplot(RI_PFC_halves_plot, 
-         is.corr = F, 
-         method = "color",
-         type = "upper", 
-         tl.pos = "n", 
-         cl.pos = "n", 
-         addgrid.col = "grey90",
-         add = T)
-mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
-mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
-mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
-```
-
-``` {r Partition comparison: halves ratios (Fig.
-9), fig.align="center", fig.width=3, fig.height=3, fig.cap = "mPFC yields higher within-subject agreement than between subjects, as evidenced by a high within/between subject mean ARI.
-PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE}
-# plot
-ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
-  geom_boxplot(show.legend = F) +
-  scale_fill_manual(values = Cols[seq(2)]) + 
-  ylim(0, 10) +
-  geom_hline(yintercept = 1) +
-  labs(y = "ARI Ratio", x = "") + 
-  theme_classic(base_size = 14)
-```
-
-``` {r Partition comparison: session similarity matrices (Fig.
-10), fig.align="center", out.width = "60%", fig.cap = "Similarity matrices showing pattern agreement across sessions for the whole brain (left), and for PCC and mPFC separately (right), for the same 10 example subjects.
-The general pattern from the daily analysis is preserved, with marked individuality for mPFC and PCC, but higher for the former.", echo=FALSE, message = FALSE}
-# plot
-par(mfrow=c(1,2))
-corrplot(RI_all_between_sess_plot, 
-         is.corr = F, 
-         method = "color", 
-         tl.pos = "n", 
-         tl.cex = 0.5,
-         tl.col = "black", 
-         #cl.lim = c(-0.03,1),
-         cl.pos = "n",
-         cl.length = 3,
-         mar = c(1.1,1.1,1.1,1.1), 
-         addgrid.col = "grey90")
-# segments(0.5,0.5,0.5,40.5, lwd = 2)
-# segments(0.5,0.5,40.5,0.5, lwd = 2)
-# segments(0.5,40.5,40.5,40.5, lwd = 2)
-# segments(40.5,0.5,40.5,40.5, lwd = 2)
-mtext(expression(bold("Subjects (Session)")), line = 1)
-mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
-corrplot(RI_PCC_sess_plot, 
-         is.corr = F, 
-         method = "color", 
-         type = "lower", 
-         tl.pos = "n", 
-         tl.cex = 0.5,
-         tl.col = "black", 
-         #cl.lim = c(0,1),
-         cl.length = 3,
-         cl.pos = "r", 
-         addgrid.col = "grey90")
-# segments(0.5,0.5,0.5,20.5, lwd = 2)
-# segments(0.5,0.5,20.5,0.5, lwd = 2)
-# segments(0.5,20.5,20.5,20.5, lwd = 2)
-# segments(20.5,0.5,20.5,20.5, lwd = 2)
-corrplot(RI_PFC_sess_plot, 
-         is.corr = F, 
-         method = "color", 
-         type = "upper", 
-         tl.pos = "n", 
-         tl.col = "black", 
-         cl.pos = "n", 
-         addgrid.col = "grey90",
-         add = T)
-mtext(expression(bold("Subjects (Session)")), line = 1)
-mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
-mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
-```
-
-``` {r Partition comparison: session ratios (Fig.
-11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions.
-Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE}
-ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
-  geom_boxplot(show.legend = F) +
-  scale_fill_manual(values = Cols[seq(2)]) + 
-  ylim(0, NA) +
-  geom_hline(yintercept = 1) +
-  labs(y = "ARI Ratio", x = "") + 
-  theme_classic(base_size = 14)
+
+```
+
+``` {r Partition comparison: halves and runs (Fig.
+8), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 days of scans each), showing pattern agreement across days and subjects for PCC and mPFC separately.
+Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncrasies in community arrangement for both PCC and mPFC (ratios > 1, solid line), with higher subject-specificity in the latter.
+Right: within-to-between subject mean ARI ratios for each subject again show higher idiosyncratic organization for mPFC.", echo=FALSE, message = FALSE}
+### code for plots in this fig
+
+## similarity matrix
+# corrplot(abs(RI_PCC_halves_plot), # absolute to get rid of that annoying -0.02 that messes up the limits. This is just for example.
+#          is.corr = F,     
+#          method = "color",
+#          type = "lower", 
+#          tl.pos = "n", 
+#          cl.lim = c(0,1),
+#          cl.pos = "r",
+#          addgrid.col = "grey90",
+#          cl.length = 3)
+# corrplot(RI_PFC_halves_plot, 
+#          is.corr = F, 
+#          method = "color",
+#          type = "upper", 
+#          tl.pos = "n", 
+#          cl.pos = "n", 
+#          addgrid.col = "grey90",
+#          add = T)
+#mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
+#mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
+#mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
+
+## ARI for days
+# ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
+#   geom_boxplot(show.legend = F) +
+#   scale_fill_manual(values = Cols[seq(2)]) + 
+#   ylim(0, 20) +
+#   geom_hline(yintercept = 1) +
+#   labs(y = "ARI Ratio", x = "") + 
+#   theme_classic(base_size = 14)
+
+## ARI for session
+# ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
+#   geom_boxplot(show.legend = F) +
+#   scale_fill_manual(values = Cols[seq(2)]) + 
+#   ylim(0, 20) +
+#   geom_hline(yintercept = 1) +
+#   labs(y = "ARI Ratio", x = "") + 
+#   theme_classic(base_size = 14)
+
+include_graphics("./Images/ratios.png")
+
 ```
@@
 \newpage
+
 ## References

### 2019-03-25 graphAnalysis_solo.R
Most recent version of an individual's graph analysis

@@ -1044,8 +1044,6 @@ bothLbls <- c("L_25_ROI",
               "L_s32_ROI",
               "L_RSC_ROI",
               "R_RSC_ROI",
-              "R_8Ad_ROI",
-              "R_9p_ROI",
               "R_23d_ROI",
               "R_d23ab_ROI",
               "R_31a_ROI",
@@ -1060,8 +1058,6 @@ bothLbls <- c("L_25_ROI",
               "R_a24_ROI",
               "R_10r_ROI",
               "R_10d_ROI",
-              "L_8Ad_ROI",
-              "L_9p_ROI",
               "L_23d_ROI",
               "L_d23ab_RO",
               "L_31a_ROI",
@@ -1078,7 +1074,6 @@ bothLbls <- c("L_25_ROI",
               "L_10d_ROI",
               "R_s32_ROI",
               "R_9a_ROI",
-              "L_p10p_ROI",
               "L_PCV_ROI")            
 
 Yeo_PCC_labels <- c("_7m_",
@@ -1112,8 +1107,6 @@ mPFC_only <- c("L_25_ROI",
               "R_OFC_ROI",
               "R_10v_ROI",
               "L_s32_ROI",
-              "R_8Ad_ROI",
-              "R_9p_ROI",
               "R_p24_ROI",
               "R_d32_ROI",
               "R_9m_ROI",
@@ -1121,8 +1114,6 @@ mPFC_only <- c("L_25_ROI",
               "R_a24_ROI",
               "R_10r_ROI",
               "R_10d_ROI",
-              "L_8Ad_ROI",
-              "L_9p_ROI",
               "L_p24_ROI",
               "L_d32_ROI",
               "L_9m_ROI",
@@ -1131,8 +1122,7 @@ mPFC_only <- c("L_25_ROI",
               "L_10r_ROI",
               "L_10d_ROI",
               "R_s32_ROI",
-              "R_9a_ROI",
-              "L_p10p_ROI")
+              "R_9a_ROI")
 
 # Little test to ensure that the ROIs match before running the whole thing
 if (FALSE %in% (mPFC_only %in% bothLbls)) {

### 2019-03-25 Manuscript.Rmd
Many improvements (see list)
- Fixed ROI list
- Updated FV vs Prop plot
- Deleted unnecessary chunk
- Improved meta analysis permutation speed (mclapply + dedicated function)

@@
 
-Cols <- c("aquamarine4", "#D9541A", rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere
+Cols <- c("aquamarine4", "#D9541A", rgb(190,190,190,100, maxColorValue = 255))
 
@@
 library(knitr)
+
+# produce one permutation instance of the meta-analysis (so it can be fed to mclapply for quicker results)
+metaPerm <- function(list1 = studyList_sv, list2 = studyList_dmn, labels = Yeo_labels, perm = 1) {
+
+  # print every 100th permutation just to have a general sense of how far we are
+  if ((perm %% 100) == 0) {sprintf("Permutation %s", perm)}
+
+  # combine study lists
+  allStudies <- c(studyList_sv, studyList_dmn)
+
+  # Sample all the studies and divide into 2 groups
+  randPerm <- sample(allStudies)
+  tmpSV <- randPerm[seq(length(list1))]
+  tmpDMN <- randPerm[-seq(length(list1))]
+
+  # Count the number of times each region was reported in the literature
+  tmpDF <- data.frame(Parcel = gsub("_", "", labels),
+                      SV = sapply(labels, function(roi) {length(grep(roi, tmpSV))}),
+                      DMN = sapply(labels, function(roi) {length(grep(roi, tmpDMN))}))
+
+  # Perform the prop test for each pair and get the max chi-squared stat
+  maxStat <- max(
+    apply(tmpDF[, 2:3], 1, function(data) {
+      prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
+    }
+    ), na.rm = T)
+
+  return(maxStat)
+
+}
 
@@
               "R_RSC_ROI",
-                "R_8Ad_ROI",
-                "R_9p_ROI",
               "R_23d_ROI",
@@
               "R_10d_ROI",
-                "L_8Ad_ROI",
-                "L_9p_ROI",
               "L_23d_ROI",
@@
               "R_9a_ROI",
-                "L_p10p_ROI",
               "L_PCV_ROI")
@@
 
+# reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
+nPerms <- 1000
+
 # For each permutation, reassign the study labels, maintaining the original number of studies per condition
-# allStudies <- c(studyList_sv, studyList_dmn)
-# nPerms <- 100 # reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
-# nullDist <- numeric()
-# 
-# for (i in seq(nPerms)) {
-# 
-#   # provide feedback only if requested (if TRUE, it will show up in the doc or pdf file)
-#   if (feedback) {
-#     if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
-#   }
-#   
-#   # Sample all the studies and divide into 2 groups
-#   randPerm <- sample(allStudies)
-#   tmpSV <- randPerm[seq(length(studyList_sv))]
-#   tmpDMN <- randPerm[-seq(length(studyList_sv))]
-# 
-#   # Count the number of times each region was reported in the literature
-#   tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-#                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
-#                       DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
-# 
-#   # Perform the prop test for each pair and get the max chi-squared stat
-#   nullDist[i] <- max(
-#                   apply(tmpDF[,2:3], 1, function(data) {
-#                     prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
-#                     }
-#                   ), na.rm = T)
-# 
-# }
-# 
-# # Now do the same for the actual data, to see how it compares to the null dist
-# tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
-#                     SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
-#                     DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
-#                     propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
-#                     propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
-# 
-# # Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
-# tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
-#   round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
-#   })
-# tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
-# 
-# # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
-# significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist, 0.95))
+nullDist <- mclapply(seq(nPerms), function(data) {metaPerm()})
+
+# Now do the same for the actual data, to see how it compares to the null dist
+tmpDF <- data.frame(Parcel = gsub("_", "", Yeo_labels),
+                    SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
+                    DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
+                    propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
+                    propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
+
+# Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
+tmpDF$Chi_squared <- apply(tmpDF[, 2:3], 1, function(data) {
+  round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
+  })
+tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
+
+# ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
+significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist, 0.95))
 
@@
 
-``` {r ROI computation (overlapping: old), echo=FALSE, message = FALSE}
+``` {r ROI computation (overlapping: DELETE), echo=FALSE, message = FALSE}
 #TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
@@
 
-<!---
-```{r Method (Figure 1), out.width = "100%", fig.align = "center", fig.cap= "Summary of the partitioning scheme and its evaluation.
-Each connectome if transformed into a normalized Laplacian matrix, whose eigenvector associated with the second-to-lowest eigenvalue assigns negative or positive values to each vertex.
-These continuous maps are binarized by sign, and compared within and between subjects using the chance-correcting Adjusted Rand Index (ARI)."}
-# Change to inflated eventually
-include_graphics("./Images/method_figure.png")
-```
--->
-
-\bigskip
-
 ## Figures
@@
 
+\bigskip
+
 ```{r Template partition (Fig.
@@
 ```
+
+\bigskip
 
@@
 
+\bigskip
+
 ``` {r Stability per subject: Fiedler vector vs prop.
 DMN plot (Fig 5), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
-Grey lines display each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
+Grey lines display each subject's association, while the black line shows the fit from a mixed effects logistic regression.
+Dashed red lines indicate the mean FV value at which maps were thresholded.", echo=FALSE, message = FALSE}
 # code to generate plot
 # Fiedler Vector x proportion of times a vertex was affiliated with DMN
-# SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
-#   geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
-#   #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
-#   geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
-#   labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
-#   scale_y_continuous(limits = c(0,1)) +
-#   theme_classic()
-
-include_graphics("./Images/SW_props.png")
+SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
+  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
+  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 2) +
+  geom_vline(xintercept = c(-0.014, 0.013), linetype = "dashed", color = Cols[2]) +
+  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
+  scale_y_continuous(limits = c(0,1)) +
+  theme_classic()
+
+SC_FVvPDMN_plot
+
+#include_graphics("./Images/SW_props.png")
 
@@
 
+\bigskip
+
 ``` {r Correlation vs community detection: comparison plot (Fig.
@@
 
+\bigskip
+
 ```{r BandB comparison (Figure 16), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga and Buckner's (2017) criterion, and those produced by spectral partitioning.

### 2019-03-25 Manuscript.Rmd
update to sliding window figure

@@
 threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
-feedback <- FALSE # show permutation progress?
+permuting <- FALSE # show permutation progress?
 
@@
 
+# optional because it can take a long time to run
+if (permuting) {
+
   # reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
@@
   # For each permutation, reassign the study labels, maintaining the original number of studies per condition
-nullDist <- mclapply(seq(nPerms), function(data) {metaPerm()})
+  nullDist <- mclapply(seq(nPerms), function(permutation) {metaPerm(perm = permutation)})
+  nullDist <- do.call(rbind, nullDist)
 
@@
 
+}
 # results!
@@
 ``` {r Stability per subject: Fiedler vector vs prop.
-DMN plot (Fig 5), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows.
-Grey lines display each subject's association, while the black line shows the fit from a mixed effects logistic regression.
+DMN plot (Fig 5), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each subject, we produced partitions for each 20 minute sliding window (1 min shift, ~84 TRs) throughout their full time series (median number of windows = 37).
+B: Proportion of times each vertex was affiliated with the DMN community across windows (up), and the continuous Fiedler vector map for the current subject using their full time series (down).
+The maps share considerable qualitative similarities in their gradients along the cortical surface.
+C: Relationship between the magnitude of Fiedler vector values and the proportion of DMN affiliations.
+Grey lines display each subject's association, while the black line shows the fit from a mixed-effects logistic regression.
 Dashed red lines indicate the mean FV value at which maps were thresholded.", echo=FALSE, message = FALSE}
-# code to generate plot
-# Fiedler Vector x proportion of times a vertex was affiliated with DMN
-SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
-  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
-  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 2) +
-  geom_vline(xintercept = c(-0.014, 0.013), linetype = "dashed", color = Cols[2]) +
-  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
-  scale_y_continuous(limits = c(0,1)) +
-  theme_classic()
-
-SC_FVvPDMN_plot
-
-#include_graphics("./Images/SW_props.png")
+# code to generate plots
+
+# # time series
+# # this one uses the actual subject's loaded time series (not included due to space)
+# n <- 4 # n of vertices to include
+# tr <- 4800 
+# ts <- data.matrix(t1[sample(59000, n), 1:tr])
+# df <- tibble(vertex = rep(seq(n), each = tr),
+#              Time = floor(rep(seq(0, tr, length.out = tr), n)),
+#              Signal = matrix(ts, ncol = 1) + rep(seq(-1, 1, length.out = n), each = tr)) %>%
+#   ggplot(data = df, aes(Time, Signal, group = vertex, color = as.character(vertex))) +
+#     geom_line(show.legend = F, lwd = 0.2, alpha = 0.6) +
+#     theme_classic()
+# 
+# # Fiedler Vector x proportion of times a vertex was affiliated with DMN
+# SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
+#   geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
+#   geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 2) +
+#   geom_vline(xintercept = c(-0.014, 0.013), linetype = "dashed", color = Cols[2]) +
+#   labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
+#   scale_y_continuous(limits = c(0,1)) +
+#   theme_classic()
+# 
+# SC_FVvPDMN_plot
+
+include_graphics("./Images/SW_props.png")
 

### 2019-03-26 Manuscript.Rmd
new figure, 2 discussion paragraphs, and working on a discussion outline

@@
 
+A considerable amount of meta-analytic work has been dedicated to pinpointing the spatial embedding of behavioral constructs in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across psychological phenomena [@DelaVega2016; @Kragel2018; @Hiser2018].
+In particular, the effects elicited by the subjective value (SV) of an option and the default mode network (DMN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
+However, recent studies have shown considerable variability of the brain's functional topography across individuals, emphasizing the importance of capturing its organization at the individual subject level, and pointing to limitations in aggregative estimations [@Braga2017; @Gordon2017; @Gratton2018a; @Kong2018; @Laumann2015; @Tobyne2018].
+Therefore, determining the distinct functional mapping of psychological processes (and the potential extent of their overlap) first requires: 1) understanding and quantifying the degree of heterogeneity in the intrinsic functional organization of this area in a large group of individuals; and 2) a method to reliably and precisely capture it in isolated subjects.
+
+Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to subdivide areas of overlap into DMN and non-DMN in 100 individuals from the Human Connectome Project.
+Our results show that the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects.
+These sub-networks were stable over time and across test-retest days using moderate amounts of fMRI data (up to 30 min per day), and resembled an organizational scheme recently observed in a handful of subjects [@Braga2017].
+We also show that spectral partitioning is capable of identifying these sub-networks in isolated individuals better than more direct seed-based functional connectivity approaches.
+
+Outline:
+
+- Summarize the results
+- Ours are not the first to show variability, but previous studies have focused on a relatively small number of subjects and often rely on qualitative assessment of these differences.
+They also use parcellations for networks, whereas we focused on individual vertices to gain spatial finesse.
+Also, to the best of our knowledge we are the first to quantify the organizational heterogeneity of these areas in the human brain.
+- We are also not the first to show functional subdivision of DMN [@Kernbach2018] (but that's using group averages on parcellated data), or this particular individualized pattern of subdivision (braga).
+Our results are complementary in the sense that we show similar outcomes in 100 subjects.
+The major discrepancy is that we assign meaning to the communities based on their coverage of regions identified through a meta-analysis.
+- Talk about SP as a way to identify an individual's partition: deterministic, with simple diagnostics, and requires less data requirements.
+- The main gap is mapping behavior to functional organization, but we will do that with behavioral manipulations of subjective value in the future.
+Instead, we focus on understanding the importance of individualized mapping in these areas first, as a baseline.
+- Clinical implications: individualized targets, and more accurate estimation of impacts based on assessment of individual patients.
+Similarly, our approach focuses on individual estimations without group priors, so it's well fit to address the problem of low n in clinical research.
+Also, SP can produce these effects with moderate amounts of data.
+Previous results suggest impractical amounts.
+
+- Limitations
+  - community detection ground truth
+  - other algorithms (benefit of SP is that it's deterministic, allows for diagnostics, and discourages extremely large/small communities)
+  - bipartition: we focus on that since we tried to capture what belongs to DMN and non-DMN.
+This intuition can be generalized to other behaviors.
+SP can be expanded to extract additional communities in combination with k-means and the identification of the first non-zero eigenvalue in the low-high rank.
+  - Small search space: working at the vertex-level makes it computationally difficult to produce estimates at the whole-brain level.
+
 For clinical implications, see Hiser & Koenigs 2018.
@@
 In addition, both modularity and SP rely on connectivity strength, and thus is amenable to the correlative nature of functional connectivity.
-
-Interhemispheric differences? citing Mackey and Petrides
 
@@
 ``` {r Correlation vs community detection (Fig.
-14), fig.align="center", fig.width = 4, fig.height = 4, fig.cap = "Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector for 10 example subjects.
+14), fig.align="center", fig.cap = "A: Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector for 10 example subjects.
 The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.
-There is high agreement within method (diagonal quadrants), but both methods suggest similar partitions (off diagonal quadrants).", echo=FALSE, message = FALSE}
-Foo <- "Fighters"
-corrplot(allHalfCombs, 
-         #title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
-         method = "color", 
-         #tl.col = "black",
-         #tl.cex = 0.6,
-         addgrid.col = "grey90",
-         tl.pos = "n",
-         cl.pos = "r",
-         cl.length = 3,
-         mar = c(1,2,2,0))
-segments(0.5,0.5,0.5,40.5, lwd = 2)
-segments(0.5,0.5,40.5,0.5, lwd = 2)
-segments(0.5,40.5,40.5,40.5, lwd = 2)
-segments(40.5,0.5,40.5,40.5, lwd = 2)
-segments(0.5,20.5,40.5,20.5, lwd = 2)
-segments(20.5,0.5,20.5,40.5, lwd = 2)
-mtext(expression(bold("Subject Partitions (Day 1 and Day 2)")), line = 3, at = par("usr")[1]+0.45*diff(par("usr")[1:2]))
-mtext(expression(bold("Subject Partitions (Day 1 and Day 2)")), side = 2, line = 3)
-mtext(expression(bold("Fiedler")), line = 1.5, at = par("usr")[1]+0.68*diff(par("usr")[1:2]))
-mtext(expression(bold("Correlation")), line = 1.5, at = par("usr")[1]+0.23*diff(par("usr")[1:2]))
-mtext(expression(bold("Fiedler")), side = 2, line = 2, at = par("usr")[1]+0.25*diff(par("usr")[1:2]))
-mtext(expression(bold("Correlation")), side = 2, line = 2, at = par("usr")[1]+0.68*diff(par("usr")[1:2]))
-
-```
-
-\bigskip
-
-``` {r Correlation vs community detection: comparison plot (Fig.
-15), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Day 1 vs Day 2 correlation coefficients for every method, as well as between methods.
-Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo=FALSE, message = FALSE}
-# Day 1 vs Day 2 Spatial Correlation Comparison
-prepostComp_plot <- ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
-  geom_boxplot(show.legend = F) +
-  labs(x = "", y = "Correlation Coefficient") +
-  ylim(0,1) +
-  theme(text = element_text(size=35)) +
-  theme_classic()
-prepostComp_plot
+There is high agreement within method (diagonal quadrants), but both methods suggest similar partitions (off-diagonal quadrants).
+B: Day 1 vs Day 2 correlation coefficients for every method, as well as between methods.
+Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo = FALSE, message = FALSE}
+# code to produce the plots
+
+# correlation matrix
+# corrplot(allHalfCombs, 
+#          #title = "Comparing All Community and Correlation mPFC Partitions \n Across All Subjects",
+#          method = "color", 
+#          #tl.col = "black",
+#          #tl.cex = 0.6,
+#          addgrid.col = "grey90",
+#          tl.pos = "n",
+#          cl.pos = "r",
+#          cl.length = 3,
+#          mar = c(1,2,2,0))
+# segments(0.5,0.5,0.5,40.5, lwd = 2)
+# segments(0.5,0.5,40.5,0.5, lwd = 2)
+# segments(0.5,40.5,40.5,40.5, lwd = 2)
+# segments(40.5,0.5,40.5,40.5, lwd = 2)
+# segments(0.5,20.5,40.5,20.5, lwd = 2)
+# segments(20.5,0.5,20.5,40.5, lwd = 2)
+# mtext(expression(bold("Subject Partitions (Day 1 and Day 2)")), line = 3, at = par("usr")[1]+0.45*diff(par("usr")[1:2]))
+# mtext(expression(bold("Subject Partitions (Day 1 and Day 2)")), side = 2, line = 3)
+# mtext(expression(bold("Fiedler")), line = 1.5, at = par("usr")[1]+0.68*diff(par("usr")[1:2]))
+# mtext(expression(bold("Correlation")), line = 1.5, at = par("usr")[1]+0.23*diff(par("usr")[1:2]))
+# mtext(expression(bold("Fiedler")), side = 2, line = 2, at = par("usr")[1]+0.25*diff(par("usr")[1:2]))
+# mtext(expression(bold("Correlation")), side = 2, line = 2, at = par("usr")[1]+0.68*diff(par("usr")[1:2]))
+# 
+# # Day 1 vs Day 2 Spatial Correlation Comparison
+# prepostComp_plot <- ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
+#   geom_boxplot(show.legend = F) +
+#   labs(x = "", y = "Correlation Coefficient") +
+#   ylim(0,1) +
+#   theme(text = element_text(size=35)) +
+#   theme_classic()
+# prepostComp_plot
+
+include_graphics("./Images/commvscorr.png")
 

### 2019-03-27 Manuscript.Rmd
working on Joe's comments

@@
 ---
-title: 'Individual heterogeneity in the functional topography of the default-mode network in medial prefrontal cortex'
+title: 'Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex'
 author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
@@
 
-  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018], including the subjective value (SV) assigned to decision outcomes [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
-Choice-related activity in these areas has shown significant spatial overlap with the default mode network (DMN) along the medial wall [@Fox2005; @Laird2009; @Yeo2011], prompting the question of whether (and to what extent) these two systems can be dissociated.
-
-  Previous coordinate-based meta-analyses have identified topographically similar activation patterns in mPFC for valuation [@Bartra2013; @Clithero2014] and default-mode task deactivation [@Laird2009].
-More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017], even though there is clear divergence in other areas (ventral striatum in favor of SV, with DMN exclusively on sections of PCC and the temporoparietal junction).
-These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same neural system.
-
-  A key limitation of group-averaging and meta-analysis is that individual-specific functionl subdivisions can be overlooked.
-Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject.
-However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a], thus making group-averaging studies difficult to interpret.
-
-  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI.
-Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018a; @Tobyne2018].
-Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
-In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity [@Braga2017].
-It is thus possible that the indistinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level.
-With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.
-
-  Interrogating all sources of covariation through functional connectivity provides an avenue for capturing subject-specific brain organization.
-Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017].
-A popular approach to analyze these connectomes is to rely on graph theoretic methods, which are properly equiped to understand brain network dynamics [@Bassett2018a].
-From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017].
+  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018].
+One such function is subjective valuation during economic decision making [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
+Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued.
+These regions are also implicated in a set of functions associated with the default-mode network (DMN).
+DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@McKiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Fox2005; @Yeo2011].
+
+  Coordinate-based meta-analyses of the fMRI literature have demonstrated that valuation and DMN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017].
+The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DMN.
+Within PCC and adjacent precuneus, a more posterior subregion appears DMN-specific, whereas a more anterior subregion is implicated in both effects.
+One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DMN effects.
+The potential existence of common nodes has primpted theorizing about posible cognitive-level overlap between valuation and DMN-related processes.
+For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Northoff2012; @Clithero2014; @Acikalin2017; Reddan2018].
+
+  However, to draw firm conclusions about functional overlap will require a better understanding of individual-level heterogeneity in topographic patterns of brain activity.
+A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Michalka2015; @Fedorenko2012; Woo2014], potentially exaggerating the degree of overlap across domains.
+This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a].
+An alternative approach is to focus on analyses at the individual-participant level.
+Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Laumann2015; @Gordon2017; @Gratton2018a; @Tobyne2018].
+Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
+Recent work has uncovered fine-grained subdivisions within the DMN through tailored analyses of seed-based functional connectivity [@Braga2017].
+It is therefore possible that the diffuse overlap of DMN and valuation effects can be attributed to a lack of spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
+An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DMN effects within mPFC and PCC.
+
+  A useful way to characterize individual-specific brain organization is to examine patterns of resting-state functional connectivity (rsFC; i.e.
+time-series correlations between pairs of locations in the brain).
+Connectome-based analyses of rsFC have been fruitful in characterizing individualized functional topologies that correspond well to task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017; @Smith2009].
+A popular way to analyze these connectomes is to rely on graph theoretic methods, which are properly equiped to understand brain network dynamics [@Bassett2018a].
+In the context of network analysis, community detection algorithms have been successfully used to subdivide brain networks into multiple distinct communities [@Garcia2017].
 Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016].
-Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017].
-However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes a forced dissection through spectral partitioning (SP) a more valuable option [@Fiedler1975; @Belkin2003].
+Among these algorithms, spectral partitioning (SP) efficiently captures  [@Fiedler1975; @Belkin2003].
 SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018].
@@
 These spatial correlations were aimed to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-The two methods were expected to produce somewhat similar arrangements, but the one displaying the higher within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]).
+The two methods were expected to produce somewhat similar arrangements, but the one displaying the higher within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018a]).
 We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
@@
 - Summarize the results
-- Ours are not the first to show variability, but previous studies have focused on a relatively small number of subjects and often rely on qualitative assessment of these differences.
+- Ours are not the first to show variability across individuals, but previous studies have focused on a relatively small number of subjects and often rely on qualitative assessment of these differences.
 They also use parcellations for networks, whereas we focused on individual vertices to gain spatial finesse.
@@
 The major discrepancy is that we assign meaning to the communities based on their coverage of regions identified through a meta-analysis.
+- Stability within subject has also been showsn before (Gratton2018b). This work was done using parcellations and oversampling though.
 - Talk about SP as a way to identify an individual's partition: deterministic, with simple diagnostics, and requires less data requirements.

### 2019-03-27 Manuscript.Rmd
adding bibliographies to repo

@@
   html_document: default
-bibliography: mPFC_paper.bib
+bibliography: Bibliography/mPFC_paper.bib
 header-includes:

### 2019-03-27 Manuscript.Rmd
Added papers to bibliography, and finished revising the intro

--- 2019-03-27 Manuscript.Rmd
@@
 Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016].
-Among these algorithms, spectral partitioning (SP) efficiently captures  [@Fiedler1975; @Belkin2003].
-SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018].
-This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.
-
-  In this study, we aimed to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals.
+In attempting to refine the DMN topography at the individual level, we focus on dividing mPFC and PCC into communities encapsulating what belongs and does not belong to DMN.
+Spectral partitioning (SP) is an efficient community detection algorithm that deterministically forces such bisections [@Fiedler1975; @Belkin2003].
+For a network composed of pairwise correlations among its nodes, SP partitions the network by binarizing the eigenvector linked to the second-to-lowest eigenvalue of the adjusted (Laplacian) correlation matrix according to its sign (i.e.
+positive or negative number).
+SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018], and was recently shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
+This method can therefore capture a refined group of brain regions that more cohesively share activation patterns during rest.
+
+  In this study, we aimed to subdivide regions commonly attributed to both DMN and subjective valuation into individual-specific DMN and non-DMN communities, quantifying the degree of topographical heterogeneity present in this network within and across individuals.
 We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks.
-First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that considerably overlapped with previously-defined DMN and limbic networks along the medial wall [@Yeo2011].
-A meta-analysis of DMN and SV literatures revealed areas in PCC and mPFC that were uniquely related to DMN and SV, respectively (these areas were used as markers to identify the affiliation of each individual's communities).
-We then produced rsFC networks of all the surface vertices within these regions of interest (ROI) for each of 100 individual resting state dataset from the Human Connectome Project (HCP)[@VanEssen2012], and estimated the extent of DMN coverage through spectral partitioning.
-Focusing on individual vertices in this search space rather than the parcels (as is usual in brain network analyses) allowed us to finely delineate the topographical extent of each community.
-We found that these areas of overlap can be partitioned into two communities that topographically vary across subjects, but that follow a comon organizational principle.
-This partition was in substantial agreement with results from a different community detection algorithm (modularity).
-A sliding window analysis showed that spectral partitioning allows for a more immediate identification of noisy viertices with unreliable affiliation.
-Refining the partitions by filtering out these nodes resulted in idiosyncratic partitions that were highly stable across scanning runs per individual, and this pattern was higher for mPFC.
-We show that partitions produced by spectral partitioning had higher test-retest reliability per subject than common seed-based functional connectivity, without the need of group-drived priors [@Kong2018].
-Lastly, we provide evidence that these communities resembled an organizational scheme recently observed in a handful of subjects [@Braga2017].
-Our work highlights the usefulness of estimating brain effects at the individual level in these regions, and points to limitations of aggregative methods in determining the degree of neural overlap between DMN and valuation.
+First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DMN and limbic networks along the medial cortical wall [@Yeo2011].
+A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level.
+We then derived an rsFC network of all the surface vertices within the search space for each of 100 individual resting-state fMRI data sets from the Human Connectome Project (HCP)[@VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel).
+Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community.
+The resulting communities varied topographically across subjects, while also appearing to follow common organizational principles.
+A combination of sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC.
+Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
+Lastly, we provide evidence that the resulting communities resembled an organizational scheme recently observed in a handful of subjects [@Braga2017].
+Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
 
@@
 # Store thre FV thresholds for all subject 
-threshDF <- data_frame(SubjID = substring(subjList,1,6),
+threshDF <- data_frame(SubjID = substring(subjList, 1, 6),
                        Lower = NA,
@@
     # if there wass no clear threshold (i.e. noisy participants), then leave it as 0
-    threshDF[i,2:3] <- c(0,0)
+    threshDF[i, 2:3] <- c(0, 0)
   } else {
-    threshDF[i,2] <- as.numeric(tempList[[i]]$result[1])
-    threshDF[i,3] <- as.numeric(tempList[[i]]$result[2])
+    threshDF[i, 2] <- as.numeric(tempList[[i]]$result[1])
+    threshDF[i, 3] <- as.numeric(tempList[[i]]$result[2])
   }
@@
   Summaries[[i]] <- Summaries[[i]] %>%
-    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
+    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i, 2]) & FiedlerVec < as.numeric(threshDF[i, 3]), 0, FiedlerVec)) %>%
     mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))

### 2019-03-27 Manuscript.Rmd
advances on methods revision

@@
 
-For all our analyses, we defined our search space based on the 17 network parcellation proposed by Yeo et al.
+For all analyses, we defined our search space based on the 17-network parcellation proposed by Yeo et al.
 [-@Yeo2011].
-First, We selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial wall.
-Next, we overlayed these networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained parcels that shared a considerable amount of vertices with them (visually inspected).
-This resulted in 45 regions of interest (ROI) across hemispheres (Table 1).
-These ROIs were naturally divided into two spatially discontiguous clusters that covered PCC and mPFC, thus facilitating the study of each general region separately.
+First, we selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial wall.
+Next, we overlayed those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
+This resulted in a search space that consisted of 40 parcels across hemispheres (Table 1).
+The search space was naturally divided into two spatially discontiguous clusters that covered PCC and mPFC, facilitating the study of each general region separately.
 
@@
 
-We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels were differentially associated with valuation or DMN effects.
-For subjective value, we gathered peak brain coordinates of activity from 198 studies that were associated with positive effects for current or prospective rewards [@Bartra2013].
+We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DMN effects.
+For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects for current or prospective rewards [@Bartra2013].
 For DMN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009].
-These coordinates represent the surviving areas post-statistical thresholding from each study.
+These coordinates represent the areas that exceeded the statistical significance threshold in each original study.
 For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009].
 The indicator map for each study was then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl2012] (http://surfer.nmr.mgh.harvard.edu/).
-Any sphere sections that overlapped with the cortex were mapped to our ROIs, and we tallied how many studies had positive indicator values in each parcel.
-
-With these lists, we identified areas that were significantly more associated to either literature.
+Any sphere sections that overlapped with the cortex (no lower limit restrictions) were mapped to the corresponding parcel, and we tallied how many studies had positive indicator values in each parcel.
+Two studies from the subjective valuation corpus were removed because they did not contain cortical voxels, leaving a final number of 198 studies.
+
+With these lists, we tested for parcels that were significantly more strongly associated with one domain than the other.
 We permuted the label of every study (i.e.
-DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from chi-squared tests of proportions that compared the number of studies that contained each area.
-This gave us a null distribution of 5000 chi-squared values.
+DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains.
+This gave us a null distribution of 5000 maximum chi-squared values.
 The 95th percentile of this distribution served as an FWE-corrected significance threshold to evaluate unpermuted chi-squared values.
@@
 In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used.
-
-Data initially underwent the HCP minimally preprocessing pipeline [@Glasser2013], which included considerable gradient nonlinearity correction, motion correction, EPI distortion correction, temporal denoising based on independent components (FIX, [@Griffanti2014; @Salimi-Khorshidi2014]), high-pass filtering (0.0005 Hz threshold), and MNI152-based normalization.
+See [@VanEssen2012] for more details about the data acquisition protocol.
+
+Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, temporal denoising based on independent components (FIX, [@Griffanti2014; @Salimi-Khorshidi2014]), high-pass filtering (0.0005 Hz threshold), and MNI152-based normalization.
 Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017].
@@
 
-### *Within-ROI Network Definition*
+### *Network Definition*
 
 All network analyses were performed using the igraph package [@G.2006] in R 3.4.1 [@RTeam2018].
-To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices.
+To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices.
 This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
@@
 Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
-The 45 areas considered were limited to the medial portion of the default mode and limbic networks, as defined by the Yeo et al.'s [-@Yeo2011] 17 network parcellation.
+The 40 areas considered were limited to the medial portion of the default mode and limbic networks, as defined by the Yeo et al.'s [-@Yeo2011] 17 network parcellation.
 Unique areas were identified by first permuting the affiliation of each study (i.e.

### 2019-03-28 Manuscript.Rmd
Methods done. Onto Results

@@
 
+```{r Density calculation, out.width="60%", fig.align = "center"}
+# Load density data
+setwd('./Densities/')
+temp <- list.files()
+Densities <- do.call(rbind, lapply(temp, read.csv))
+
+# Get the mean density for all data, daily scans, and sessions
+mdAll <- mean(Densities$Density[grep("Overall", Densities$Type)])
+sddAll <- sd(Densities$Density[grep("Overall", Densities$Type)])
+mdDay <- mean(Densities$Density[grep("Day", Densities$Type)])
+mdSess <- mean(Densities$Density[grep("Session", Densities$Type)])
+```
+
 All network analyses were performed using the igraph package [@G.2006] in R 3.4.1 [@RTeam2018].
 To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices.
-This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them.
+This produced a weighted network for each subject, in which the nodes were surface vertices and the edges were the correlations among them.
 Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify strong correlations.
 The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values).
+*TODO: recompute corrCounts so it also stores the # of pos/neg correlations turned to 0, as well as the number of TRs per subject (add to fMRI deets)*.
 Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
 Values of 1 of this transformed distribution were returned to 0 in order to avoid the inclusion of these edges in the network analyses.
-We report the proportion of retained edges (i.e.
-network density) in the Results section.
-As part of the evaluation step, we produced these network weight matrices (and the community detection outlined below) at four levels: 1) for each run separately (1200 TRs each); 2) for the concatenated time series for the two runs on the same day (2400 TRs total); 3) for each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).
+The proportion of remaining edges (i.e.
+network density) was high for all individuals(mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`).
+We generated and analyzed network weight matrices at four levels: 1) for each run separately (1200 TRs each); 2) for the concatenated time series for the two runs on each day (2400 TRs total); 3) for each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).
 
@@
 Communities (i.e.
-clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003].
-First, each network was represented as an $n$ x $n$ network weight matrix (where $n$ = number of vertices within the ROIs, 4,801).
+clusters) were identified using the SP algorithm [@Belkin2003; @Chung1999; @Fiedler1975].
+First, each network was represented as an $n$ x $n$ network weight matrix $W$ as described above (where $n$ equals the number of vertices in the search space, 4,801).
 This matrix was then transformed into its normalized Laplacian form
@@
 Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its correlation values with every other vertex), and $W$ is the network weight matrix.
+the sum of its transformed correlation values with every other vertex), and $W$ is the network weight matrix.
 This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal.
-This transformation ensures that every row adds up to zero.
+The transformation ensures that every row sums to zero.
 We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
-This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with [@Fiedler1975].
-This method enforces the partition of a network into similarly-sized communities, and guarantees that they share at least one edge [@Chung1999].
-In this way, spectral partitioning avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
-Every individual partition is therefore binarized by sign in order to evaluate the topography of each community (see next section for details).
-Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community to be the one containing the DMN-specific PCC parcel identified in our meta-analysis.
-The high density of these networks (see Results) ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].
-
-In order to evaluate the convergent validity of the resulting partitions across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al.
+This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975].
+This method partitions the network into two similarly-sized communities, and guarantees that they share at least one edge [@Chung1999].
+In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
+Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community as that which contained the DMN-specific PCC parcel identified in our meta-analysis.
+The high density of these networks ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].
+
+In order to evaluate the convergent validity of the resulting partitionings across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al.
 [-@Clauset2004].
-*(TBD) This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
-The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.* Unlike SP, modularity can fractionate a network into more than two functional groups.
-We assumed that if the partitions from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.
-We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by spectral partitioning to be non-zero.
+*(TODO: rephrase) This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
+The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.* Unlike SP, modularity can fractionate a network into more than two communities.
+We assumed that if the partitionings from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we were indeed fractioning the search space into an adequate number of communities.
+We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by SP to be non-zero.
 This eigenvalue serves as an estimator of the optimal number of communities in a network [@Chung1999], such that a rank of two in our partitions justifies limiting the number of communities to two.
@@
 
-In order to evaluate the stability and topographical heterogeneity of the communities within and across subjects, we chose the adjusted rand index (ARI) as the reference metric of agreement between two clusterings [@Hubert1985].
+In order to evaluate the stability and topographical heterogeneity of the communities within and across individuals, we chose the adjusted rand index (ARI) as a reference metric of agreement between two partitionings [@Hubert1985].
 The base of the ARI is computed by the formula
@@
 Where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number grouped together (separately) in one partition, but separately (together) in the other.
-Therefore, ARI estimates the ratio at which every pair of nodes in partition A were jointly assigned to the same/different parcels on partition B, over all possible relational changes.
+Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $(n\times (n - 1))/2$).
 The resulting ratio is adjusted by comparing it to a baseline given by the expectation of a random node assignment across partitions.
+The index ranges from 0 to 1, where 0 denotes the value expected by chance.
 This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below 50%).
@@
 Modularity and SP have been previously found to show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018].
-Their alignment would thus give us confidence in the validity of the resulting topologies.
-Next, we compared the functional organization derived from the whole time series across subjects, and report the mean pairwise ARI for the group.
-We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects.
-Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all the subsequent analyses on PCC and mPFC separately.
-
-To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the partition derived from the whole subject's data.
+Alignment between the two algorithms would therefore give us confidence in the validity of the resulting partitionings.
+Next, we compared the partitionings derived from each individual's full time series across subjects, and report the mean pairwise ARI for the group.
+We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects.
+Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all subsequent analyses on PCC and mPFC separately.
+
+To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the partition derived from the whole subject's data.
 A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017].
@@
 To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series).
-Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time.
+Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DMN or non-DMN more than 95% of the time.
 
 We then estimated the level of agreement between network partitions estimated using data from individual days (with 2 days per participant).
-If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement within subject (test/re-test across days) than across subjects.
-We tested this idea by computing the ratio of the mean ARI within and between subjects.
-Ratios close to one denoted similar within-subject and across-subject alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-subject than across subjects.
-We then extended this idea by computing the overall agreement across all runs (4 per subject) Similar to the day-based analysis, we assessed whether session-level data showed higher agreement within-subject than between subjects.
-
-<!--
-### *Estimation of Noise Effects*
-
-BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis].
-Even though we made attempts to remove clear sources of noise through data preprocessing and stability analyses, it was still important to quantify the remaining potential influence of structured noise in our findings.
-We examined this through two complementary steps.
-First, we computed the temporal signal-to-noise ratio (tSNR) of all the vertices in the ROIs from the HCP minimally preprocessed data (i.e.
-prior to the complementary denoising described in the "fMRI Data" section).
-We compared the mean tSNR for each region across subjects through a permutation analysis (all permutation analyses involved 5000 iterations).
-In addition, we compared the mean tSNR between mPFC and PCC through a permutation analysis for each separate subject, and report the percentage of subjects who had a significantly lower mean tSNR in mPFC (post FDR correction for multiple testing [@Benjamini2001]).
-
-Next, we examined whether a vertex's affiliation to the DMN community was driven by its tSNR.
-First, we computed the mean time series of each subject's DMN community.
-We then performed a mass univariate analysis to predict the average time series from each individual vertice's time series.
-The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex.
-If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects.
-We then spatially correlated (Pearson) each subject's $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices, and report the mean correlation across subjects.
--->
-
-### *Seed-based FC vs Community Detection*
-
-We evaluated the performance of the spectral partitioning algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity.
-First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average PCC activity for each day separately.
-We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps.
-These spatial correlations were aimed to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-The two methods were expected to produce somewhat similar arrangements, but the one displaying the higher within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018a]).
-We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
+If the functional organization estimated by SP is indeed individual-specific, we should see higher agreement within individual (test/re-test across days) than across individuals.
+We tested this idea by computing the ratio of the mean ARI within and between individuals.
+Ratios close to one denoted similar within-participant and across-participant alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-participant than across participants.
+We then extended this idea by computing the overall agreement across individual runs (4 per subject).
+Similar to the day-based analysis, we assessed whether run-level data showed higher agreement within-subject than between subjects.
+
+### *Seed-based rsFC versus Community Detection*
+
+We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity.
+First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average activity across all vertices in PCC for each day separately.
+We compared these seed-based maps with the Fiedler vectors produced by SP by examining three sets of spatial correlations across vertices between days: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps.
+These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
+The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018a]).
+We therefore compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
 
@@
 
-We performed a coordinate-based meta-analysis to identify unique standard regions across DMN and SV literatures.
-Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
-The 40 areas considered were limited to the medial portion of the default mode and limbic networks, as defined by the Yeo et al.'s [-@Yeo2011] 17 network parcellation.
-Unique areas were identified by first permuting the affiliation of each study (i.e.
-DMN or SV) to create a distribution of chi-squared statistics based on the comparison of the number of reports per area between literatures (see Methods for details).
-This putative null distribution was used to identify regions more often reported in either literature.
-
-Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the resulting significant ROIs from the permutation.
+We performed a coordinate-based meta-analysis to identify subregions of mPFC and PCC that were preferentially associated with the DMN or SV literatures.
+Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to discrete parcels from a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
+The `r length(Yeo_labels)` parcels considered were limited to the medial portion of the default mode and limbic networks defined by the Yeo et al.'s [-@Yeo2011] 17-network parcellation.
+Unique areas were identified by first permuting the domain labels across studies (DMN or SV) to create a null distribution for the maximum chi-squared statistic in the search space (see Methods for details).
+The null distribution was used to identify regions that were reported significantly more often reported in one literature or the other.
+
+Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the significant differences between domains.
 The 95th percentile of the permuted chi-squared distribution was 9.11.
-Based on this threshold, area 7m was the only one to show unique bilateral affiliation to DMN (Left: observed $\chi^2$ = 10.07, *p* = 0.034; Right: observed $\chi^2$ = 18.89, *p* < 0.0001), while SV was uniquely represented bilaterally by area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.014; Right: observed $\chi^2$ = 12.83, *p* = 0.014).
-The purpose of these supra-threshold areas was to identify the most-likely affiliation of the two communities in our partitions by their coverage of these regions.
-However, area 25 sits in close proximity to the ventral striatum, which is reliably active in SV studies [@Bartra2013].
-Considering that our projection from volumetric spheres to the cortex might have attributed striatal reports to this region, we decided not to use it as a marker of SV.
-We also chose not to use area v23 due to its unilateral significance (Right: observed $\chi^2$ = 11.51, *p* = 0.018).
-Instead, we only rely on area 7m to demarcate the DMN community.
-
-<!--
-Using each literature's mean number of reports per area as the null probability (DMN = `r BD`, 95% CI [`r BDquant`]; SV = `r BV`, 95% CI [`r BVquant`]), one-way chi-squared tests of proportions were performed to identify regions that were significantly present in their respective literatures.
-The resulting lists were used to identify the set of common brain areas.
-Unique areas were then determined by permuting the affiliation of each study (i.e.
-DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature.
-Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
-DMN included `r length(t2)` significant regions, while SV was comprised of `r length(t1)` (see Supplemental Table 1).
-As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all*p*< 0.05).
-A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function.
--->
+Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DMN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.034; Right: observed $\chi^2$ = 18.89, *p* < 0.0001).
+The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.018; **TODO: ADD LEFT**).
+There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.014; Right: observed $\chi^2$ = 12.83, *p* = 0.014); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum.
+No toher parcels were preferentially implicated in valuation relative to DMN.
+We therefore selected area 7m as an interpretable, bilateral reference point for labeling DMN and non-DMN communities in the analyses that follow.
+We note that area 7m has been found to not partake in DMN in previous work [@AndrewsHanna2010].
+However, we adhere to the nomenclature established by [@Glasser2016], whose area 7m is positioned considerably more ventrally and is well contained within canonical DMN.
 
@@
 
-```{r Density calculation, out.width="60%", fig.align = "center"}
-# Load density data
-setwd('./Densities/')
-temp <- list.files()
-Densities <- do.call(rbind, lapply(temp, read.csv))
-
-# Get the mean density for all data, daily scans, and sessions
-# Check distributions, since median might be better
-mdAll <- mean(Densities$Density[grep("Overall", Densities$Type)])
-sddAll <- sd(Densities$Density[grep("Overall", Densities$Type)])
-mdDay <- mean(Densities$Density[grep("Day", Densities$Type)])
-mdSess <- mean(Densities$Density[grep("Session", Densities$Type)])
-```
-
-With these `r length(unique(str_remove(Yeo_labels, "_ROI")))` ROIs (`r (length(unique(str_remove(Yeo_labels, "_ROI"))) - 2)` overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using their full time series (approximately 4800 total TRs from four scanning sessions over two days).
-Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices).
-After correcting for multiple comparisons, we performed spectral partitioning on these networks to identify cohesive functional communities denoting DMN and non-DMN areas.
-On average, networks had high densities (i.e.
-highly connected) regardless of whether they were produced with a single run all the full time series (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`).
-This high degree of density is important, as this method is known to face challenges when computed on sparse networks [@Fortunato2016].
-
-Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning.
-This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs.
-Since this is a data-driven approach, there is no a priori labeling for these communities.
-We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects.
-In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment.
-On the other hand, mPFC is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them.
-This non-DMN section extends posteriorly onto pregenual cinglate cortex (area a24).
-
-Before determining the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004].
+With our mPFC/PCC search space, we estimated each individual's DMN coverage using their full time series (approximately 4800 total TRs from four scanning sessions over two days).
+Each subject's network (n = `r nSubj`) was constructed by calculating pairwise correlations among the time series for all the surface vertices in the search space (`r nVertices` total vertices).
+We applied the SP community detection algorithm to thresholded transformations of these networks to identify cohesive functional communities corresponding to DMN and non-DMN areas.
+
+Figure 2 shows a representative partitioning of the search space for a single participant (100307).
+The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods).
+Since this is a data-driven approach, there is no a priori labeling for the two communities.
+We thus defined the DMN community as the one containing the one DMN-specific PCC parcel from the meta-analysis (7m).
+In qualitative terms, the resulting patterns contained substantial DMN coverage in posterior PCC (as dictated by our labeling strategy), with non-DMN vertices in anterior PCC.
+The mPFC region tended to include DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them.
+This non-DMN section extended posteriorly into pregenual cinglate cortex (area a24).
+
+Before evaluating the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004].
 Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model.

### 2019-03-28 Manuscript.Rmd
halfway through the results section

@@
 The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values).
-*TODO: recompute corrCounts so it also stores the # of pos/neg correlations turned to 0, as well as the number of TRs per subject (add to fMRI deets)*.
+**TODO: recompute corrCounts so it also stores the # of pos/neg correlations turned to 0, as well as the number of TRs per subject (add to fMRI deets)**.
 Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
@@
 [-@Clauset2004].
-*(TODO: rephrase) This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
-The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.* Unlike SP, modularity can fractionate a network into more than two communities.
+**(TODO: rephrase) This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
+The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.** Unlike SP, modularity can fractionate a network into more than two communities.
 We assumed that if the partitionings from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we were indeed fractioning the search space into an adequate number of communities.
@@
 
-Before evaluating the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004].
-Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model.
-Since modularity is not bound to a desired number of communities, it was capable of finding more than two in our datset.
-We quantified the cross-method agreement with the adjusted rand index (ARI).
-ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes.
-This measure has the benefit of being agnostic to labeling schemes, as well as controlling for the expectation that the clusters were randomly produced [@Hubert1985].
-This means that positive ARI values compare favorably against chance clustering.
+Before evaluating the degree of generazibility of this topographic pattern across individuals, we examined the validity of these partitionings by comparing them to results from an alterntive community detection algorithm, modularity maximization [@Clauset2004].
+Modularity seeks to find the set of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model.
+Since modularity is not bound to a desired number of communities, it was capable of finding more than two in our data set.
+We quantified the cross-method agreement in terms of the Adjusted Rand Index (ARI; see methods), which measures the proportion of node pairs of nodes in a network that were either clustered together or separately in both partitionings, while being agnostic to labeling schemes and controlling for chance clustering.
 
@@
 
-This comparison showed that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)`, SD = `r round(sd(RI_all_within$Index), digits = 2)`).
+This comparison showed that both clustering methods were in high agreement across subjects (mean ARI = `r round(mean(RI_all_within$Index), digits = 2)`, SD = `r round(sd(RI_all_within$Index), digits = 2)`).
 Modularity showed a tendency to produce additional communities (median = `r median(nModularity)`, max = `r max(nModularity)`).
-However, these communities encompassed a small number of vertices (mean = `r mean(modularityCounts_extra, na.rm = T)`, IQR = `r IQR(modularityCounts_extra, na.rm = T)`) compared to the principal two (mean = `r mean(modularityCounts_two, na.rm = T)`, IQR = `r IQR(modularityCounts_two, na.rm = T)`), suggesting that the overall network is composed of two main communities.
-In addition, the estimation of the optimal number of cuts based on the rank of the first non-zero eigenvalue (see "Partition evaluation" for details) showed that `r prcntDissection` percent of the individual networks are best partitioned into two communities.
-
-Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was moderate agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
-However, qualitative inspection of the brain community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects.
+However, these communities encompassed a **(TBD: small number of vertices (mean = `r mean(modularityCounts_extra, na.rm = T)`, IQR = `r IQR(modularityCounts_extra, na.rm = T)`) compared to the principal two (mean = `r mean(modularityCounts_two, na.rm = T)`, IQR = `r IQR(modularityCounts_two, na.rm = T)`)**, suggesting that the overall network is composed of two main communities.
+In addition, the estimation of the optimal number of cuts based on the rank of the first non-zero eigenvalue (see "Partition evaluation" for details) showed that `r prcntDissection` percent of the individual networks were best partitioned into two communities.
+
+Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+Qualitative inspection of the brain community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects.
 To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3).
-Indeed, this analysis showed that the functional topology of PCC is better maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`)(paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+Indeed, this analysis showed that the functional topography of PCC was better maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`)(paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
 
@@
 
-In order to estimate the degree of stability of these partitions in time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the partition computed using the whole time series (Figure 4).
+In order to estimate the degree of stability of these partitions in time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min), comparing the partitioning derived from each window with the partitioning computed using the entire time series (Figure 4).
 
@@
 
-This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
-These results suggest that the each individual's DMN distribution is cosiderably stable in time.
-
-There is precedence in thhe literature that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
+**This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+These results suggest that some nodes were considerably variable in time, despite overall stability in the community arrangement.**
+
+There is precedent in thhe literature for the idea that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
 Therefore, we asked whether the magnitude of these eigenvector values was associated with the stability of nodes in time.
-Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model (Figure 5).
-The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time.
+Specifically, we estimated the proportion of DMN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
+The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with **higher absolute Fiedler vector values** were more persistent in their relationship with their corresponding community over time.
 We refer to this proportion of affiliations over time as the stability of a given node.
@@
 
-These analyses show that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN and non-DMN vertices, even in relatively short resting fMRI sessions (i.e.
-less than 20 mins).
+These analyses show that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DMN and non-DMN vertices.
 We therefore thresholded each subject's Fiedler vector to produce these refined maps.
 We estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 95%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
-Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, but their partitions were not discarded.
-Vertices under these thresholds were set to zero (instead of removed) so that the dimensionality of the data was unaffected, and 0.5 in the binarized maps so that they wouldn't bias the calculation of averages.
-Figure 6 (left) shows the updated partition for the one showed in figure 2.
+Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
+Sub-threshold vertices were set to zero in Fiedler vector maps and 0.5 in the binarized maps so that they would not bias the calculation of averages.
+Figure 5 shows the thresholded partitioning for the same individual shown in Figure 2.
 The maps used in all subsequent analyses were thresholded by this individualized criterion.

### 2019-03-29 Manuscript.Rmd
Done with revision, just need to address TBDs and table arrangement

@@
         for (subj2 in seq(nSubjects)) {
-          indexMatrix[subj,subj2] <- cor(allVecs[, subj], allVecs[, subj2])
+          indexMatrix[subj,subj2] <- cor(allVecs[, subj], allVecs[, subj2], method = "spearman")
         }
@@
       for (subj in seq(nSubjects)) {
-        indexMatrix$Index[subj] <- cor(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
+        indexMatrix$Index[subj] <- cor(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]], method = "spearman")
       }
@@
 network density) was high for all individuals(mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`).
-We generated and analyzed network weight matrices at four levels: 1) for each run separately (1200 TRs each); 2) for the concatenated time series for the two runs on each day (2400 TRs total); 3) for each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).
+We generated and analyzed network weight matrices at four levels: (1) for each run separately (1200 TRs each); (2) for the concatenated time series for the two runs on each day (2400 TRs total); (3) for each subject's full dataset (4800 TRs total); and (4) on each step of a sliding window analysis (see Partition Evaluation for more details).
 
@@
 
-In order to evaluate the stability and topographical heterogeneity of the communities within and across individuals, we chose the adjusted rand index (ARI) as a reference metric of agreement between two partitionings [@Hubert1985].
+In order to evaluate the stability and topographical heterogeneity of the communities within and across individuals, we chose the adjusted rand index (ARI) as a reference metric of agreement between two partitionings [@Hubert1985], which was calculated using the "mcclust" package in R [@Arno2012].
 The base of the ARI is computed by the formula
@@
 
-The average percentage of stable vertices per subject was `r round(mean(prcntStable[prcntStable < 1]), digits = 2)` (SD = `r round(sd(prcntStable[prcntStable < 1]), digits = 2)`).
+The average proportion of stable vertices per subject was `r round(mean(prcntStable[prcntStable < 1]), digits = 2)` (SD = `r round(sd(prcntStable[prcntStable < 1]), digits = 2)`).
 With these thresholded partitions, we recomputed the overall similarity of their functional organization across participants.
-Compared to before, there was even less overall agreement of the full maps among individuals (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
-The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
-Figure 6 (right) shows the spatial average of the thresholded binarized partitions across all participants, denoting the proportion of times a vertex was affiliated with the DMN community.
-This summary conveys a common organizational principle for both communities, but also highlights the considerable variability across individuals in mPFC compared to PCC.
+Compared to before, there was even **less overall agreement** of the full maps among individuals (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+Figure 5 (bottom) shows the spatial average of the thresholded binarized partitions across all participants, denoting the proportion of times a vertex was affiliated with the DMN community.
+This summary illustrates the common organizational layout of both communities, but also highlights the considerable variability across individuals, especially in mPFC.
 
@@
 Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
-setwd('./Variance/')
-temp <- list.files()
-Variance <- lapply(temp, read.csv)
-
-## append the Rsquared values onto the current summaries
-# unfortunately this only counts on the DMN community
-appendVar <- lapply(seq(nSubj), function(subj) {left_join(Summaries[[subj]], Variance[[subj]], by = "Vertex")})
-
-## correlate tSNR with Rsquared before and after thresholds
-snrR2_cors <- list()
-
-snrR2_cors$pre_thresh <- lapply(appendVar, function(data) {
-  data %>% 
-    filter(!is.na(Rsquared)) %>%
-    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
-    group_by(region) %>%
-    dplyr::summarise(correlation = cor(varCoeff, Rsquared)) %>%
-    ungroup()
-}) %>% reduce(left_join, by = "region")
-
-snrR2_cors$post_thresh <- lapply(appendVar, function(data) {
-  data %>% 
-    filter(!is.na(Rsquared), FiedlerBinary != 0.5) %>%
-    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
-    group_by(region) %>%
-    dplyr::summarise(correlation = cor(varCoeff, Rsquared)) %>%
-    ungroup()
-}) %>% reduce(left_join, by = "region")
-
 ## next get the mean tSNR of PCC and mPFC before/after thresholding
@@
 # the third one applies summary stats to each list to create a summary table
-snrR2_means <- list()
-
-snrR2_means$pre_thresh <- lapply(appendVar, function(data) {
+snr_means <- list()
+
+snr_means$pre_thresh <- lapply(Summaries, function(data) {
   data %>% 
@@
 
-snrR2_means$post_thresh <- lapply(appendVar, function(data) {
+snr_means$post_thresh <- lapply(Summaries, function(data) {
   data %>% 
@@
 # and compute summary stats on each 
-snrR2_means$overall <- sapply(snrR2_means, function(x) {
+snr_means$overall <- sapply(snr_means, function(x) {
   c(rowMeans(x[, -1]), apply(x[, -1], 1, sd))
 })
-rownames(snrR2_means$overall) <- c("mPFC_mean", "PCC_mean", "mPFC_SD", "PCC_SD")
+rownames(snr_means$overall) <- c("mPFC_mean", "PCC_mean", "mPFC_SD", "PCC_SD")
 
 # permutation pre vs post
-tsnrPermute_mPFC <- permute(as.numeric(snrR2_means$pre_thresh[1, -1]), as.numeric(snrR2_means$post_thresh[1, -1]), paired = T)
-tsnrPermute_PCC <- permute(as.numeric(snrR2_means$pre_thresh[2, -1]), as.numeric(snrR2_means$post_thresh[2, -1]), paired = T)
+tsnrPermute_mPFC <- permute(as.numeric(snr_means$pre_thresh[1, -1]), as.numeric(snr_means$post_thresh[1, -1]), paired = T)
+tsnrPermute_PCC <- permute(as.numeric(snr_means$pre_thresh[2, -1]), as.numeric(snr_means$post_thresh[2, -1]), paired = T)
+tsnrPermute_Post <- permute(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]))
 
 # effect size pre vs post
-tsnrCohen_mPFC <- CohenD(as.numeric(snrR2_means$post_thresh[1, -1]), as.numeric(snrR2_means$pre_thresh[1, -1]))
-tsnrCohen_PCC <- CohenD(as.numeric(snrR2_means$post_thresh[2, -1]), as.numeric(snrR2_means$pre_thresh[2, -1]))
-
-# ##### old
-# 
-# # Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
-# tempComm_PCC <- lapply(tempComm_PCC, filter, FiedlerVec != 0)
-# tempComm_PFC <- lapply(tempComm_PFC, filter, FiedlerVec != 0) 
-# SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) {permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval})
-# SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
-# SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) {cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)})
-# prcntSig <- mean(SNR_PCCvsPFC_perm < 0.05) * 100
-# 
-# # Get the mean SNR for each region and compare overall levels 
-# SNR_meanPCC <- sapply(tempComm_PCC, function(data) {mean(data$varCoeff)})
-# SNR_meanPFC <- sapply(tempComm_PFC, function(data) {mean(data$varCoeff)})
-# SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
-#                      Comparison = permute(SNR_meanPCC, SNR_meanPFC)$Pval,
-#                      ES = cohenD(SNR_meanPCC, SNR_meanPFC))
-# rm(SNR_meanPCC, SNR_meanPFC)
-
+tsnrCohen_mPFC <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$pre_thresh[1, -1]))
+tsnrCohen_PCC <- CohenD(as.numeric(snr_means$post_thresh[2, -1]), as.numeric(snr_means$pre_thresh[2, -1]))
+tsnrCohen_Post <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]))
 ```
 
-To discard the possibility that the higher inter-subject variability in mPFC was driven by retaining vertices with lower signal quality, we compared the mean temporal signal to noise ratio (tSNR) for each region pre and post thresholding.
-We used subject time series that were not demeaned, but were otherwise equivalent to the data originally used.
-Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC actually significantly increased post-thresholding across subjects (Pre: mean = `r snrR2_means$overall[1, 1]`, SD = `r snrR2_means$overall[3, 1]`; Post: mean = `r snrR2_means$overall[1, 2]`, SD = `r snrR2_means$overall[3, 2]`; paired permutation p-value = `r tsnrPermute_mPFC$Pval`, Cohen's D = `r tsnrCohen_mPFC[1]`), whereas the mean signal quality in PCC was unaffected (Pre: mean = `r snrR2_means$overall[2, 1]`, SD = `r snrR2_means$overall[4, 1]`; Post: mean = `r snrR2_means$overall[2, 2]`, SD = `r snrR2_means$overall[4, 2]`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r tsnrCohen_PCC[1]`).
+To test the possibility that the higher inter-subject variability in mPFC was driven merely by lower signal quality in the retained vertices, we quantified the mean temporal signal to noise ratio (tSNR) for each region, both before and after thresholding.
+We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
+Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding across subjects (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unaffected (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r tsnrCohen_PCC[1]`).
+In fact, tSNR after thresholding was significantly higher for mPFC (permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
+**(TBD: in terms of tSNR variability (sd) within region, it is true  that mPFC > PCC, both before and after the threshold (mPFC: pre mean sd = 33.96, post mean sd = 30.15; PCC: pre mean sd = 15.28, post mean sd = 14.59))**
 
@@
 
-The relative high variability seen in the aggregate map could be due to variations in the functional organization of mPFC across days.
-While the sliding window analysis suggested that these partitions are stable, many of the windows contained data from both days.
-A stricter evaluation of subject-specificity would be to compare every subject's subdivisions produced by data from each day separately.
-If the variability that we observed was truly due to having captured an individual's unique organization, day to day ARI values should be consistently higher within- than between-subjects.
-Figure 7 shows pairwise comparisons among ten example subjects for whole brain (left), as well as for PCC and mPFC separately (right).
+The relatively high variability seen in the aggregate map could reflect at least three factors: (1) measurement noise, (2) dynamic variation in mPFC network organization, and (3) stable patterns of functional organization that differ across individuals.
+To evaluate the third possibility, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
+If the variability we observed were truly due to having captured an individual's unique organization, day to day ARI values should be consistently higher within- than between-individuals.
+Figure 6 shows pairwise comparisons among ten example subjects for PCC and mPFC separately (left).
 
@@
 
-Once again we found low alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) and mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed relatively high levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
-However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic.
-Therefore, we divided everyone's within-subject ARI by the mean ARI of their between-subject comparison.
-This ratio denotes the relative specificity of their partition, such that partitions that align well across subjects should yield ratios close to 1, while unique and stable partitions would produce high ratios.
-Given what we know about these general regions, we expected PCC to be well aligned both within and between subjects.
-On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject.
-
-Figure 8 shows these ARI ratios for PCC and mPFC for all subjects.
-As expected, we found that while both regions had good specificity (i.e.
-ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PFC), digits = 2)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PCC), digits = 2)`) when compared with a paired permutation test (*p* = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
-These test/retest results suggest that the topographic variability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.
-
-### *Partition Comparison: Session based*
-
-We extended the analysis of daily data by examining whether the organization of the DMN could be extracted using session data only.
-It is worth noting that the length of each session (approx.
-14 mins long) falls below the stability threshold for fMRI-based modularity estimations [@Gordon2017].
-Nonetheless, high ARI ratios with reduced data could signify the ability to localize a subject's DMN organization with fMRI sessions that are easier to fit along with other study sessions of interest.
+Once again we found low alignment across individuals for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) and mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed comparatively high levels of within-individual agreement (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
+We calculated an index of relative specificity by computing the ratio of each individual’s across-day (within-participant) ARI to the mean of all between-participant ARI values involving that individual.
+**The index is expected to take on a value near 1 if partitionings are well aligned across individuals and/or are subject to a common level of measurement noise.
+It is expected to exceed 1 insofar as functional network organization is reliable and individual-specific.
+This index is intended to factor out the potential effects of measurement noise, as they are asumed to be constant for each region (TBD, not sure if needed).**
+
+Figure 6 shows these ARI ratios for PCC and mPFC for all individuals As expected, we found that while both regions showed evidence for specificity (i.e.
+ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PFC), digits = 2)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PCC), digits = 2)`) when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`) **(TBD: test against 1.
+I think it might be worth doing it for PCC's sake, as mPFC's numbers + figure already convey its idiosyncrasy very well.
+If we do it here, we'll do it for the run-specific analysis too)**.
+These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns.
+
+### *Partition Comparison: Run based*
+
+We extended the analysis of per-day data by examining whether the organization of the DMN could be extracted using per-run data only.
+The duration of each run (approximately 14 mins long) falls below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
+Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DMN organization from only a single run of data.
 
@@
 
-Computing SP on networks from individual sessions showed that we can still coarsely capture a subject's unique organizational pattern (Figure 9), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 10).
+Run-specific SP results could still capture a subject's unique organizational pattern to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, this time using the mean across-run (within-participant) ARI in the denominator of the ratio (Figure 6).
 
@@
 
-We can see again that the ratios for mPFC were higher than those of PCC (permutation,*p*= `r Sess_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1.
-This further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that such patterns can be identified with small amounts of data in spite of a reduction in the estimates.
+Ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, SD = `r round(sd(Sess_RIRatios_PFC), digits = 2)`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, SD = `r round(sd(Sess_RIRatios_PCC), digits = 2)`).
+This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
 
@@
 The computational demands of our approach escalate quickly as the number of vertices increases.
-We thus explored the possible advantage to using community detection over a simple seed-based functional connectivity analysis from PCC.
-Given that other groups have found the spatial distribution of the DMN to be considerably stable within individuals [@Laumann2015; @Gordon2017; @Braga2017; @Kong2018], we examined whether maps generated with spectral partitioning were more similar per subject across days than those computed from seed-based correlations.
-First, we computed each individual's mean time series of all the vertices contained within PCC, and correlated it with the activity of every mPFC.
-Since correlation values are continuous, we compared them to their respective unbinarized Fiedler vector maps.
-We performed pairwise spatial Pearson correlations among maps computed for each day and method from all subjects.
+We thus explored the possible advantage of community detection relative to a simple seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
+We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations.
+We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC **(TBD: limiting this to 7m as a seed.
+I think it makes sense, especially since we're saying that PCC (1) is also subdivided to some extent, and (2) also shifts across individuals to some extent.
+Alternatively, you wouldn't use 7m as a seed unless you just wanted to find DMN.
+Full PCC is what a traditional analysis might have done.)**.
+We compared the map of correlation values in mPFC to the map of unbinarized Fiedler vector values.
+We performed pairwise spatial Spearman correlations among maps computed for each day and method from all subjects.
 For `r nrow(unCorrParticipants %>% filter(Corrs < 0))` subjects, the maps produced with one of the days' datasets insufficiently covered area 7m, and so the community labeling was reversed (for one additional subject, both daily maps were reverted).
@@
 We thus visually inspected these subjects (n = 7) and reverted the labeling when it was clear that the topologies aligned across days.
-Figure 11 shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alingment between methods, but particularly high agreement within subject and method.
-
-Figure 12 shows the overall degree of similarity across days for patterns dervied using community detection, seed-based correlation, and across methods (i.e.
-day one community detection versus day two seed-based correlation).
-While both approaches are very consistent, community detection displayed a significantly higher ARI across days than a simple correlation (paired permutation *p* < 0.001; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
-It is worth noting that the cross-method agreement is fair, meaning that both approaches show similar topological features.
-These findings suggest that graph-theoretic community detection algorithms provide a better way to detect stable functional topologies.
+Figure 7 (left) shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.
+
+Figure 7 (right) shows the test/re-test reliability across days for patterns dervied using community detection, seed-based correlation, and across methods (e.g.
+Day 1 community detection versus Day 2 seed-based correlation).
+While both approaches were reliable, community detection displayed a significantly higher ARI across days than a simple correlation (paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", prepostComp_permTest$Pval))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
+Agreement across methods was fair, signifying that the two approaches identified similar topographic features but also systematic differences.
+These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies.
 
@@
 
-The thresholded partitions in our work qualitatively resembled the topographical arrangement of networks A and B proposed by Braga and Buckner [-@Braga2017].
+The thresholded partitions in our work qualitatively resembled the topographical arrangement of DMN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
 We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
-In their work, Braga and Buckner selected individual vertices along the dorsolateral prefrontal cortex (DLPFC) that produced these two anticorrelated networks.
+In their work, Braga and Buckner selected individual vertices along the dorsolateral prefrontal cortex (DLPFC) that produced two anticorrelated networks.
 Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to find seed vertices in DLPFC that can reproduce them.
-The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 13.
-
-Visual inspection of these networks shows a remarkable similarity between our DMN and non-DMN communities and their networks A and B.
-These qualitative results are important, as here we reinforce the idea that canonical DMN can be reliably subdivide at the individual level.
-Further, it shows the potential of community detection methods to automatically extract these partitions without the need to rely on group data.
-One way in which our results are at odds with those from Braga and Buckner is the functional labeling of these sub-networks.
-Based on our criteria, network B would more closely identify with DMN (per 7m affiliation), while we currently do not have enough evidence to label network A.
-These discrepancies should be addressed with explicit behavioral manipulations in the future.
+The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 9.
+
+Visual inspection of these networks shows a remarkable similarity between our DMN and non-DMN communities and the previously reported sub-networks A and B.
+Our search space does not comprise a number of diagnostic areas used in identifying netowrk A, such as the temporo-parietal junction and parahippocampal area [@Braga2019].
+Lack of signal from these areas could drive the small discrepancies in the topography between our work and theirs.
+Nevertheless, these qualitative similarities are important, as they collectively suggest there may exist a true functional partitioning of canonical DMN regions into two distinct communities.
+Results from the present investigation suggest that the topographic organization of the communities is variable across a large sample of participants, especially in mPFC, and that the SP algorithm is a useful and reliable tool for identifying the two communities in individuals.
 
@@
 The major discrepancy is that we assign meaning to the communities based on their coverage of regions identified through a meta-analysis.
-- Stability within subject has also been showsn before (Gratton2018b). This work was done using parcellations and oversampling though.
+- Stability within subject has also been shown before. This work was done using either parcellations and oversampling though. [@Laumann2015; @Gordon2017; @Braga2017; @Gratton2018b; @Kong2018]
 - Talk about SP as a way to identify an individual's partition: deterministic, with simple diagnostics, and requires less data requirements.
+- Similarity with B&B: One way in which our results are at odds with those from Braga and Buckner is the functional labeling of these sub-networks.
+Based on our criteria, network B would more closely identify with DMN (per 7m affiliation), while we currently do not have enough evidence to label network A.
+These discrepancies should be addressed with explicit behavioral manipulations in the future.
+Also our search space is limited compared to theirs, thus making the patterns only partially similar.
 - The main gap is mapping behavior to functional organization, but we will do that with behavioral manipulations of subjective value in the future.
@@
   - Small search space: working at the vertex-level makes it computationally difficult to produce estimates at the whole-brain level.
+
+<!--
 
@@
 Like, you wouldn't expect the actual network distribution to shift that much after shifting the time series by 1 minute.
+-->
 
@@
 We would like to thank Dan Sussman for initial guidance on community detection and evaluation methods.
+This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI awards N00014-16-1-2832 and N00014-17-1-2304).
 Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
-
-## Supplemental Materials
-
-### *Table 1. Regions of interest from Glasser et al. (2016). Prefixes indicate hemispheric location (e.g. R = right).*
-| Literature           | Significant Brain Regions                 |
-| :------------------- | ----------------------------------------: |
-| ROIs                 | `r str_remove(Yeo_labels, "_ROI")` |
 
@@
 
+## Supplemental Materials
+
+### *Table 1. Regions of interest from Glasser et al. (2016). Prefixes indicate hemispheric location (e.g. R = right).*
+| Literature           | Significant Brain Regions                 |
+| :------------------- | ----------------------------------------: |
+| ROIs                 | `r str_remove(Yeo_labels, "_ROI")` |
+
 \newpage

### 2019-03-29 Manuscript.Rmd
small tweaks

@@
 ``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
+# this is used to get the number of subjects and proportion maps for the group (for visualization only)
 setwd('./For_HCP')
@@
 A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level.
-We then derived an rsFC network of all the surface vertices within the search space for each of 100 individual resting-state fMRI data sets from the Human Connectome Project (HCP)[@VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel).
+We then derived an rsFC network of all the surface vertices within the search space for each of `r nSubj` individual resting-state fMRI data sets from the Human Connectome Project (HCP)[@VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel).
 Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community.

### 2019-03-29 Manuscript.Rmd
updated the table

@@
 
-### *Table 1. Regions of interest from Glasser et al. (2016). Prefixes indicate hemispheric location (e.g. R = right).*
-| Literature           | Significant Brain Regions                 |
-| :------------------- | ----------------------------------------: |
-| ROIs                 | `r str_remove(Yeo_labels, "_ROI")` |
+``` {r Subdivide search space into hemi-region for table, echo = FALSE, message = FALSE} 
+# based on a subject's data, create a region vector for PCC and mPFC
+# then split by region and hemisphere into a list (length = 4), and retain the unique (and stripped) labels for display
+searchSpace <- Summaries[[1]] %>%
+                  mutate(region = ifelse(y < 0, "PCC", "mPFC"),
+                         Label = str_remove(substr(Label, 3, 20), "_ROI")) %>%
+                  select(Hemisphere, region, Label) %>% # unneeded, but makes it easier to examine the df
+                  split(list(.$Hemisphere, .$region)) %>%
+                  lapply(., function(x) {unique(x$Label)})
+
+```
+
+### *Table 1. Parcels from Glasser et al. (2016) contained in the search space.*
+| Hemisphere  |            mPFC        |          PCC          |
+| :---------- | :--------------------: | --------------------: |
+| Left        | `r searchSpace$L.mPFC` | `r searchSpace$L.PCC` |
+| Right       | `r searchSpace$R.mPFC` | `r searchSpace$R.PCC` |
 

### 2019-03-29 Manuscript.Rmd
update to bibliography and tweaks to manuscript before knitting

@@
 These regions are also implicated in a set of functions associated with the default-mode network (DMN).
-DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@McKiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Fox2005; @Yeo2011].
+DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Fox2005; @Yeo2011].
 
@@
 The potential existence of common nodes has primpted theorizing about posible cognitive-level overlap between valuation and DMN-related processes.
-For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Northoff2012; @Clithero2014; @Acikalin2017; Reddan2018].
+For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Northoff2012; @Clithero2014; @Acikalin2017; @Reddan2018].
 
   However, to draw firm conclusions about functional overlap will require a better understanding of individual-level heterogeneity in topographic patterns of brain activity.
-A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Michalka2015; @Fedorenko2012; Woo2014], potentially exaggerating the degree of overlap across domains.
+A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Woo2014; @Michalka2015; @Wang2015], potentially exaggerating the degree of overlap across domains.
 This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a].
 An alternative approach is to focus on analyses at the individual-participant level.
-Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Laumann2015; @Gordon2017; @Gratton2018a; @Tobyne2018].
+Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Laumann2015; @Gordon2017; @Gratton2018b; @Tobyne2018].
 Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
-Recent work has uncovered fine-grained subdivisions within the DMN through tailored analyses of seed-based functional connectivity [@Braga2017].
+Recent work has uncovered fine-grained subdivisions within the DMN through tailored analyses of seed-based functional connectivity [@Braga2017; @Braga2019].
 It is therefore possible that the diffuse overlap of DMN and valuation effects can be attributed to a lack of spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
@@
 Next, we overlayed those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
-This resulted in a search space that consisted of 40 parcels across hemispheres (Table 1).
+This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1).
 The search space was naturally divided into two spatially discontiguous clusters that covered PCC and mPFC, facilitating the study of each general region separately.
@@
 For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009].
-The indicator map for each study was then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl2012] (http://surfer.nmr.mgh.harvard.edu/).
+The indicator map for each study was then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/).
 Any sphere sections that overlapped with the cortex (no lower limit restrictions) were mapped to the corresponding parcel, and we tallied how many studies had positive indicator values in each parcel.
@@
 The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values).
-**TODO: recompute corrCounts so it also stores the # of pos/neg correlations turned to 0, as well as the number of TRs per subject (add to fMRI deets)**.
+**TODO: recompute corrCounts so it also stores the # of pos/neg correlations turned to 0, as well as the number of TRs per subject (add to fMRI details)**.
 Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
@@
 These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018a]).
+The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018b]).
 We therefore compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
@@
 ## Between halves analysis for correlation and communities (mPFC only)
+# Spearman to avoid issues with the differences in value ranges
 unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
@@
 allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
+
+Foo <- "fighters"
 ```
@@
 In particular, the effects elicited by the subjective value (SV) of an option and the default mode network (DMN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
-However, recent studies have shown considerable variability of the brain's functional topography across individuals, emphasizing the importance of capturing its organization at the individual subject level, and pointing to limitations in aggregative estimations [@Braga2017; @Gordon2017; @Gratton2018a; @Kong2018; @Laumann2015; @Tobyne2018].
+However, recent studies have shown considerable variability of the brain's functional topography across individuals, emphasizing the importance of capturing its organization at the individual subject level, and pointing to limitations in aggregative estimations [@Braga2017; @Gordon2017; @Gratton2018b; @Kong2018; @Laumann2015; @Tobyne2018].
 Therefore, determining the distinct functional mapping of psychological processes (and the potential extent of their overlap) first requires: 1) understanding and quantifying the degree of heterogeneity in the intrinsic functional organization of this area in a large group of individuals; and 2) a method to reliably and precisely capture it in isolated subjects.
@@
 
+\newpage
+
 ## Supplemental Materials

### 2019-03-29 Manuscript.Rmd
had to fix an incorrect p = 0

@@
 
-**This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+**This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
 These results suggest that some nodes were considerably variable in time, despite overall stability in the community arrangement.**

### 2019-03-29 Manuscript.Rmd
added the extra permutation values (at 5k now)

@@
 ``` {r Meta-analysis permutation, echo=FALSE, message = FALSE, cache = TRUE}
-# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC
+# Glasser parcels contained in Yeo's 17-net DMN and limbic networks on the medial cortical wall
 Yeo_labels <- c("L_25_ROI",
@@
   # reported statistics are computed @ 5k, but it's computationally demanding to do that every time.
-  nPerms <- 1000
+  nPerms <- 5000
 
@@
 
-  # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
+  # ROIs that survived the threshold based on Chi-squared value 
   significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist, 0.95))
@@
 # results!
-# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DMN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.01)
-# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DMN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p < 0.05, R: p < 0.0001)
-# v23 right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
-# null 95th-q chi <- 9.11 (varies; this was done ith 100 but resembles the 5k one)
-
-```
-
-``` {r ROI computation (overlapping: DELETE), echo=FALSE, message = FALSE}
-#TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
-## ROI definition
-# First, load the raw count csv files
-valCounts <- read.csv2('decCounts.csv', sep = ",")
-dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")
-
-# Then, get the means of the counts per domain, both within/outside the search space
-# This is to get a broad estimate of the average report amounts in the literature
-tempBoot <- bootstrap(valCounts$Counts)
-BV <- round(mean(tempBoot))
-BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
-tempBoot <- bootstrap(dmnCounts$Counts)
-BD <- round(mean(tempBoot))
-BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
-rm(tempBoot)
-
-# Now select only the ROIs from Yeo et al (TEMP)
-valCounts <- getCoords(Labels = Yeo_labels, Coords = valCounts)$Coords
-dmnCounts <- getCoords(Labels = Yeo_labels, Coords = dmnCounts)$Coords
-
-# Now, for every ROI, do a prop test to check if the proportion of reports is significantly greater
-# than the mean report over the number of studies (i.e. sample-based null probability, which could be changed to perm)
-for (i in seq(valCounts$Counts)) {
-  indx <- valCounts$Counts[i]
-  tempTest <- prop.test(indx, 27, alternative = "greater", p = BV/27)
-  valCounts$Chi[i] <- tempTest$statistic
-  valCounts$pVal[i] <- tempTest$p.value
-}
-for (i in seq(dmnCounts$Counts)) {
- indx <- dmnCounts$Counts[i]
- tempTest <- prop.test(indx, 77, alternative = "greater", p = BD/77)
- dmnCounts$Chi[i] <- tempTest$statistic
- dmnCounts$pVal[i] <- tempTest$p.value
-}
-# Retain only the significant parcels
-t1 <- valCounts$Label[valCounts$pVal < 0.05]
-t2 <- dmnCounts$Label[dmnCounts$pVal < 0.05]
-# Remove hemispheric references
-t1 <- unique(substring(t1,2))
-t2 <- unique(substring(t2,2))
-# Labels to put in text
-dmnLbls <- gsub("ROI","", t2)
-dmnLbls <- gsub("_","", dmnLbls)
-valLbls <- gsub("ROI","", t1)
-valLbls <- gsub("_","", valLbls)
-
-#bothLbls <- dmnLbls[dmnLbls %in% valLbls] # This part is just for reference, as the labels are loaded from a file
-# final overlap
-# And get the set of overlapping areas between literatures
-# This is missing some cingulate and PFC areas, and adds V2.
-# However, we can say that we are filling in the gap for completeness,
-# and removing V2 because it's demonstrably irrelevant.
-#bothLbls <- unique(c(t1[t1 %in% t2], t2[t2 %in% t1]))
-# You could also try to permute the allocation of reports per literature,
-# and then perform a chi-squared per parcel. Get the max stat per iteration.
-# Now you have your null distribution.
+# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DMN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.005)
+# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DMN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p = 0.02, R: p < 0.0001)
+# v23ab right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
+# v23ab left (proportion sv = 0.16; proportion DMN = 0.32, chi = 8.25, p = 0.06)
+# null 95th-q chi <- 8.87 (varies; this was done ith 100 but resembles the 5k one)
 
@@
 Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the significant differences between domains.
-The 95th percentile of the permuted chi-squared distribution was 9.11.
-Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DMN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.034; Right: observed $\chi^2$ = 18.89, *p* < 0.0001).
-The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.018; **TODO: ADD LEFT**).
-There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.014; Right: observed $\chi^2$ = 12.83, *p* = 0.014); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum.
+The 95th percentile of the permuted chi-squared distribution was 8.87.
+Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DMN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.029; Right: observed $\chi^2$ = 18.89, *p* < 0.001).
+The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.011; Left: observed $\chi^2$ = 8.25, *p* = 0.067).
+There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.005; Right: observed $\chi^2$ = 12.83, *p* = 0.005); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum.
 No toher parcels were preferentially implicated in valuation relative to DMN.
@@
 
+\bigskip
+
+```{r Extra examples (supplemental fig 1), out.width = "50%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings, with their binarized forms.
+A common organizational principle is visible, even though it shifts topographically across individuals."}
+include_graphics("./Images/extra_examples.png")
+```
+
+\bigskip
+
+```{r ARI Comparison (supplemental fig 2), out.width = "50%", fig.align = "center", fig.cap = "Example of a day-to-day comparison using ARI for two subjects (100307 and 100408).
+This reflects how qualitatively similar, individual-specific partitionings can have relatively low values, and how partitionings across individuals are much closer to chance (i.e.
+0)"}
+include_graphics("./Images/ARI_comparison.png")
+```
+
 \newpage

### 2019-04-01 Manuscript.Rmd
Removed density files due to miscalculation (fixed in corrCounts), plus revisions to manuscript

@@
 
+``` {r fMRI data descriptives} 
+# load file with the n of TRs and density data
+corrCounts <- read.csv('corrCounts.csv')
+```
 Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
@@
 Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany).
-Four resting state runs (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised 1200 time points(14 min 33 s) for a total of 4800 time points.
+Four resting state runs (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised up to 1200 time points(14 min 33 s) for a total of up to 4800 time points (median = `r median(corrCounts$nTR)`, minimum = `r min(corrCounts$nTR)`).
 Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other.
@@
 subjects with four rsfMRI sessions).
-In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used.
+In addition, only datasets with either low motion levels (under 1.5 mm) or under 0.5 mm mean framewise displacement (FD) were used.
 See [@VanEssen2012] for more details about the data acquisition protocol.
@@
 
-```{r Density calculation, out.width="60%", fig.align = "center"}
+```{r Density calculation}
 # Load density data
-setwd('./Densities/')
-temp <- list.files()
-Densities <- do.call(rbind, lapply(temp, read.csv))
-
-# Get the mean density for all data, daily scans, and sessions
-mdAll <- mean(Densities$Density[grep("Overall", Densities$Type)])
-sddAll <- sd(Densities$Density[grep("Overall", Densities$Type)])
-mdDay <- mean(Densities$Density[grep("Day", Densities$Type)])
-mdSess <- mean(Densities$Density[grep("Session", Densities$Type)])
+corrCounts <- corrCounts %>%
+  mutate(prcntNS = NonSignificant / Total,
+         prcntPos = SignificantPos / (Total - NonSignificant),
+         prcntNeg = SignificantNeg / (Total - NonSignificant),
+         density = 1 - prcntNS)
+
+# density descriptives
+mdAll <- mean(corrCounts$density)
+sddAll <- sd(corrCounts$density)
+
+# prcnt pos/neg
+mPos <- round(mean(corrCounts$prcntPos), digits = 2)
+sdPos <-round(sd(corrCounts$prcntPos), digits = 2)
+mNeg <- round(mean(corrCounts$prcntNeg), digits = 2)
+sdNeg <-round(sd(corrCounts$prcntNeg), digits = 2)
 ```
@@
 The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values).
-**TODO: recompute corrCounts so it also stores the # of pos/neg correlations turned to 0, as well as the number of TRs per subject (add to fMRI details)**.
+The proportion of remaining edges (i.e.
+network density) was high for all individuals (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`), and was mostly composed of positive correlations (positive: mean = `r mPos`, sd = `r sdPos`; negative: mean = `r mNeg`, sd = `r sdNeg`).
 Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
 Values of 1 of this transformed distribution were returned to 0 in order to avoid the inclusion of these edges in the network analyses.
-The proportion of remaining edges (i.e.
-network density) was high for all individuals(mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`).
 We generated and analyzed network weight matrices at four levels: (1) for each run separately (1200 TRs each); (2) for the concatenated time series for the two runs on each day (2400 TRs total); (3) for each subject's full dataset (4800 TRs total); and (4) on each step of a sliding window analysis (see Partition Evaluation for more details).
@@
 [-@Clauset2004].
-**(TODO: rephrase) This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network.
-The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity.** Unlike SP, modularity can fractionate a network into more than two communities.
+This method compares the strength of the connection between any two vertices to their probability of being randomly connected to any other vertex in the network.
+The method heuristically iterates through many possible combinations of vertices, and selects the partitioning that maximizes the network's so-called modularity.
+Unlike SP, modularity can fractionate a network into more than two communities.
 We assumed that if the partitionings from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we were indeed fractioning the search space into an adequate number of communities.

### 2019-04-01 community_detection.R
single subject community detection script, density/TR calc, and manuscript typo

@@ -1,0 +1,182 @@
+#!/usr/bin/env Rscript
+SubjID <- commandArgs(trailingOnly=TRUE)
+write(paste("Analyzing data for subject", SubjID), stdout())
+
+library(igraph)
+library(data.table)
+library(parallel)
+library(tidyverse)
+
+# Normalization approach suggested in network textbook (equation 7.10)
+fisherTanh <- function(Data = padjMatrix){
+  
+  transformed <- list()
+  
+  # tanh
+  Data[Data == 1] <- 1 * 0.999
+  transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
+  
+  # p-vals
+  if (is.matrix(Data)) {
+    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
+    n <- dim(Data)[1]
+  } else if (is.vector(Data)) {
+    z.vec <- transformed$tanhZ
+    n <- length(Data)
+  }
+  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)
+  
+  # adjust pvals
+  transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")
+  
+  if (is.matrix(Data)) {
+    # get pvals and their adjustment into a symetric matrix form
+    # regular
+    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
+    tempMat[upper.tri(tempMat)] <- transformed$pvals
+    tempMat[lower.tri(tempMat)] <- transformed$pvals
+    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
+    transformed$pvals <- tempMat
+    
+    # adjusted
+    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
+    tempMat[upper.tri(tempMat)] <- transformed$adjustPvals
+    tempMat[lower.tri(tempMat)] <- transformed$adjustPvals
+    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
+    transformed$adjustPvals <- tempMat
+  }
+  
+  return(transformed)
+  
+}
+
+# ROIs
+yeoLbls <- c("L_25_ROI",
+             "L_OFC_ROI",
+             "L_10v_ROI",
+             "R_25_ROI",
+             "R_OFC_ROI",
+             "R_10v_ROI",
+             "L_s32_ROI",
+             "L_RSC_ROI",
+             "R_RSC_ROI",
+             "R_23d_ROI",
[…]

### 2019-04-01 countCors.R

@@ -1,0 +1,104 @@
+# simple script to count the number of pos/neg correlations that go into SP
+# this can be used to compute densities later on
+
+library(data.table)
+
+# fisher r to z transformation, plus p-value adjustment with FDR
+fisherTanh <- function(Data = padjMatrix){
+  
+  transformed <- list()
+  
+  # tanh
+  transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
+  
+  # p-vals
+  if (is.matrix(Data)) {
+    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
+    n <- dim(Data)[1]
+  } else if (is.vector(Data)) {
+    z.vec <- transformed$tanhZ
+    n <- length(Data)
+  }
+  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n - 3)), lower.tail = F) # no lower tail, but absolute Zs = two tailed
+  
+  # adjust pvals
+  transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")
+  
+  if (is.matrix(Data)) {
+    # get pvals and their adjustment into a symetric matrix form
+    # regular
+    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
+    tempMat[upper.tri(tempMat)] <- transformed$pvals
+    tempMat[lower.tri(tempMat)] <- transformed$pvals
+    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
+    transformed$pvals <- tempMat
+    
+    # adjusted
+    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
+    tempMat[upper.tri(tempMat)] <- transformed$adjustPvals
+    tempMat[lower.tri(tempMat)] <- transformed$adjustPvals
+    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
+    transformed$adjustPvals <- tempMat
+  }
+  
+  return(transformed)
+  
+}
+
+# get filenames
+files <- dir(pattern = "_timeSeries.csv")
+subjList <- sapply(files, substring, first = 1, last = 6)
+
+# get sample summary file to get vertex indices
+vertexIndex <- read.csv('./Analyzed/Summary/100307_finalSummary.csv')
+vertexIndex <- vertexIndex$Vertex
+
+# vectors to store correlations and other stuff Joe asked for later on
+nTR <- as.numeric()
+neg <- as.numeric()
[…]

### 2019-04-01 Manuscript.Rmd
single subject community detection script, density/TR calc, and manuscript typo

@@
 The proportion of remaining edges (i.e.
-network density) was high for all individuals (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`), and was mostly composed of positive correlations (positive: mean = `r mPos`, sd = `r sdPos`; negative: mean = `r mNeg`, sd = `r sdNeg`).
+network density) was high for all individuals (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`), which were mostly composed of positive correlations (positive: mean = `r mPos`, sd = `r sdPos`; negative: mean = `r mNeg`, sd = `r sdNeg`).
 Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.

### 2019-04-01 community_detection.R
gitignore for r history and fixed error (data matrix) on community detection script

@@ -5,7 +5,6 @@ write(paste("Analyzing data for subject", SubjID), stdout())
 library(igraph)
 library(data.table)
 library(parallel)
-library(tidyverse)
 
 # Normalization approach suggested in network textbook (equation 7.10)
 fisherTanh <- function(Data = padjMatrix){
@@ -133,12 +132,14 @@ labelCoords_vertex <- read.table('labelCoords_vertex.csv', sep = ",", header = T
 # load data
 write("Loading data", stdout())
 Data <- fread(paste("./tseries/", SubjID, "_timeSeries.csv", sep = ""), header = F)
+Data <- data.matrix(Data)
 
 # append the ROI label to each vertex
 dimnames(Data) <- list(labelCoords_vertex$Label, seq(ncol(Data)))
 
 # select ROIs
-indx <- sapply(yeoLbls, function(lbl) {grep(lbl, rownames(Data))}) %>% reduce(c)
+indx <- sapply(yeoLbls, function(lbl) {grep(lbl, rownames(Data))})
+indx <- do.call(c, indx)
 
 # reduce time series to onle search space
 nVerts <- length(indx)

### 2019-04-01 singleTS.sh
script to prep a subject's time series + run comm detection for a single subject

@@ -1,0 +1,31 @@
+#!/bin/bash -l
+
+# this script will copy a subject's dense time series, turn it into a csv, and run community detection on it
+# its output is just the eigenvectors and eigenvalues of SP, plus the determined modularity membership
+
+#$ -l mem_total=94G
+#$ -N commDetection
+module load connectomewb/1.2.3
+
+subj=$1
+
+# copy data
+cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/concatenated_rfMRI/rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii \
+    /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii
+
+# transform to csv
+wb_command -cifti-convert -to-text ${subj}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii \
+                                    temp_${subj}_timeSeries.csv
+
+# get only the cortical vertices
+awk 'NR <= 59412 { print }' temp_${subj}_timeSeries.csv >> ${subj}_timeSeries.csv
+
+# remove original and temp time series, and move time series to the appropriate folder
+rm -f ${subj}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii
+rm -f temp_${subj}_timeSeries.csv
+mv -f ${subj}_timeSeries.csv tseries
+
+# run the R script that will produce the final counts
+Rscript community_detection.R $subj
+
+

### 2019-04-04 Manuscript.Rmd
working on TBDs (switching to medians, etc)

@@
 # In case I want to visualize stuff in the brain
-labelCoords_vertex <- read.csv2('labelCoords_vertex.csv')[,2:6]
+labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[, 2:6]
 labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))
@@
 
-Figure 2 shows a representative partitioning of the search space for a single participant (100307).
+Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented on Supplemental Figure 1).
 The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods).
@@
 # Median size of the extra (>2) communities estimated by modularity
-modularityCounts <- lapply(Summaries, function(data) {sort(count(data$Membership)$freq, decreasing = T)})
-modularityCounts_two <- sapply(modularityCounts, function(x) {mean(x[seq(2)], na.rm = T)})
-modularityCounts_extra <- sapply(modularityCounts, function(x) {mean(x[3:4], na.rm = T)})
+modularityCounts <- lapply(Summaries, function(data) {sort(plyr::count(as.character(data$Membership))$freq, decreasing = T)})
+modularityCounts_two <- sapply(modularityCounts, function(x) {sum(x[seq(2)], na.rm = T)})
+modularityCounts_extra <- sapply(modularityCounts, function(x) {sum(x[3:4], na.rm = T)})
 
@@
 This comparison showed that both clustering methods were in high agreement across subjects (mean ARI = `r round(mean(RI_all_within$Index), digits = 2)`, SD = `r round(sd(RI_all_within$Index), digits = 2)`).
-Modularity showed a tendency to produce additional communities (median = `r median(nModularity)`, max = `r max(nModularity)`).
-However, these communities encompassed a **(TBD: small number of vertices (mean = `r mean(modularityCounts_extra, na.rm = T)`, IQR = `r IQR(modularityCounts_extra, na.rm = T)`) compared to the principal two (mean = `r mean(modularityCounts_two, na.rm = T)`, IQR = `r IQR(modularityCounts_two, na.rm = T)`)**, suggesting that the overall network is composed of two main communities.
+Modularity showed a tendency to produce additional communities (median = `r median(nModularity)`, range = `r range(nModularity)`).
+However, these communities encompassed a small number of vertices (median = `r median(modularityCounts_extra)`, IQR = `r quantile(modularityCounts_extra, 0.25)` - `r quantile(modularityCounts_extra, 0.75)`) compared to the principal two (median = `r median(modularityCounts_two)`, IQR = `r quantile(modularityCounts_two, 0.25)` - `r quantile(modularityCounts_two, 0.75)`, suggesting that the overall network is composed of two main communities.
 In addition, the estimation of the optimal number of cuts based on the rank of the first non-zero eigenvalue (see "Partition evaluation" for details) showed that `r prcntDissection` percent of the individual networks were best partitioned into two communities.
@@
 
-### *Pattern stability over time*
+### *Pattern variability over time*
 
@@
 Specifically, we estimated the proportion of DMN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
-The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with **higher absolute Fiedler vector values** were more persistent in their relationship with their corresponding community over time.
+The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
 We refer to this proportion of affiliations over time as the stability of a given node.
@@
 We calculated an index of relative specificity by computing the ratio of each individual’s across-day (within-participant) ARI to the mean of all between-participant ARI values involving that individual.
-**The index is expected to take on a value near 1 if partitionings are well aligned across individuals and/or are subject to a common level of measurement noise.
+The index is expected to take on a value near 1 if partitionings are well aligned across individuals and/or are subject to a common level of measurement noise.
 It is expected to exceed 1 insofar as functional network organization is reliable and individual-specific.
-This index is intended to factor out the potential effects of measurement noise, as they are asumed to be constant for each region (TBD, not sure if needed).**
+This index is intended to factor out the potential effects of measurement noise, as they are asumed to be constant for each region.
 
 Figure 6 shows these ARI ratios for PCC and mPFC for all individuals As expected, we found that while both regions showed evidence for specificity (i.e.
-ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PFC), digits = 2)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PCC), digits = 2)`) when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`) **(TBD: test against 1.
+ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; IQR = `r quantile(Halves_RIRatios_PFC, 0.25)` - `r quantile(Halves_RIRatios_PFC, 0.75)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; IQR = `r quantile(Halves_RIRatios_PCC, 0.25)` - `r quantile(Halves_RIRatios_PCC, 0.75)`) when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`) **(TBD: test against 1.
 I think it might be worth doing it for PCC's sake, as mPFC's numbers + figure already convey its idiosyncrasy very well.
@@
 We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations.
-We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC **(TBD: limiting this to 7m as a seed.
+We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC limiting this to 7m as a seed.
 I think it makes sense, especially since we're saying that PCC (1) is also subdivided to some extent, and (2) also shifts across individuals to some extent.
 Alternatively, you wouldn't use 7m as a seed unless you just wanted to find DMN.
-Full PCC is what a traditional analysis might have done.)**.
+Full PCC is what a traditional analysis might have done.
 We compared the map of correlation values in mPFC to the map of unbinarized Fiedler vector values.
@@
 We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
-In their work, Braga and Buckner selected individual vertices along the dorsolateral prefrontal cortex (DLPFC) that produced two anticorrelated networks.
-Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to find seed vertices in DLPFC that can reproduce them.
-The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 9.
+In their work, Braga and Buckner selected individual vertices along areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two anticorrelated networks [@Braga2017; @Braga2019].
+Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to reproduce our prtitionings by selecting seeds in one these diagnostic areas.
+We confirmed seed placement based on the pattern observed in TPJ and PHC.
+The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 8.
 
 Visual inspection of these networks shows a remarkable similarity between our DMN and non-DMN communities and the previously reported sub-networks A and B.
-Our search space does not comprise a number of diagnostic areas used in identifying netowrk A, such as the temporo-parietal junction and parahippocampal area [@Braga2019].
-Lack of signal from these areas could drive the small discrepancies in the topography between our work and theirs.
+Since our search space did not contain areas TPJ and PHC, lack of signal from these areas could drive the small discrepancies in the topography between our work and theirs (particularly for network A).
 Nevertheless, these qualitative similarities are important, as they collectively suggest there may exist a true functional partitioning of canonical DMN regions into two distinct communities.
@@
 | Hemisphere      |             mPFC             |              PCC            |
-| :---------- | :--------------------: | --------------------: |
-| Left        | `r searchSpace$L.mPFC` | `r searchSpace$L.PCC` |
-| Right       | `r searchSpace$R.mPFC` | `r searchSpace$R.PCC` |
+| :-------------- | :--------------------------- | :-------------------------- |
+| Left            | `r sort(searchSpace$L.mPFC)` | `r sort(searchSpace$L.PCC)` |
+| --------------- | ---------------------------- | --------------------------- |
+| Right           | `r sort(searchSpace$R.mPFC)` | `r sort(searchSpace$R.PCC)` |
+|                 |                              |                             |
 

### 2019-04-05 community_detection.R
fixes/cleaning to comm detection script, and revisions to manuscript

@@ -5,49 +5,65 @@ write(paste("Analyzing data for subject", SubjID), stdout())
 library(igraph)
 library(data.table)
 library(parallel)
+library(tidyverse)
 
-# Normalization approach suggested in network textbook (equation 7.10)
-fisherTanh <- function(Data = padjMatrix){
+## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
+# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
+# Normalization approach suggested in network textbook (equation 7.20)
+# This transformation is approximately normal with mean 0 and sd = sqrt(1 / (n - 3))
+fisherTanh <- function(Data = padjMatrix, preThresh = NA){
   
   transformed <- list()
   
-  # tanh
-  Data[Data == 1] <- 1 * 0.999
-  transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
-  
-  # p-vals
-  if (is.matrix(Data)) {
-    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
-    n <- dim(Data)[1]
-  } else if (is.vector(Data)) {
-    z.vec <- transformed$tanhZ
-    n <- length(Data)
-  }
-  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)
-  
-  # adjust pvals
-  transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")
-  
-  if (is.matrix(Data)) {
-    # get pvals and their adjustment into a symetric matrix form
-    # regular
-    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
-    tempMat[upper.tri(tempMat)] <- transformed$pvals
-    tempMat[lower.tri(tempMat)] <- transformed$pvals
-    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
-    transformed$pvals <- tempMat
+  if (is.numeric(preThresh)) {
+    Data[Data == 1] <- 0.999
+    Data[Data < preThresh] <- 0
+    transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
+  } else {
+    # tanh
+    Data[Data == 1] <- 0.999
+    transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
     
-    # adjusted
[…]

### 2019-04-05 graphAnalysis_solo.R

@@ -198,43 +198,53 @@ partoverCorrMat <- function(ROI = 'R_7m_ROI', lbels = verts[[1]]){
 
 ## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
 # This takes either a matrix of correlation values (vectors too, but manually compute pvals)
-# Normalization approach suggested in network textbook (equation 7.10)
-fisherTanh <- function(Data = padjMatrix){
+# Normalization approach suggested in network textbook (equation 7.20)
+# This transformation is approximately normal with mean 0 and sd = sqrt(1 / (n - 3))
+fisherTanh <- function(Data = padjMatrix, preThresh = NA){
   
   transformed <- list()
   
-  # tanh
-  Data[Data == 1] <- 1 * 0.999
-  transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
-  
-  # p-vals
-  if (is.matrix(Data)) {
-    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
-    n <- dim(Data)[1]
-  } else if (is.vector(Data)) {
-    z.vec <- transformed$tanhZ
-    n <- length(Data)
-  }
-  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)
-  
-  # adjust pvals
-  transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")
-  
-  if (is.matrix(Data)) {
-    # get pvals and their adjustment into a symetric matrix form
-    # regular
-    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
-    tempMat[upper.tri(tempMat)] <- transformed$pvals
-    tempMat[lower.tri(tempMat)] <- transformed$pvals
-    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
-    transformed$pvals <- tempMat
+  if (is.numeric(preThresh)) {
+    Data[Data == 1] <- 0.999
+    Data[Data < preThresh] <- 0
+    transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
+  } else {
+    # tanh
+    Data[Data == 1] <- 0.999
+    transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
     
-    # adjusted
-    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
[…]

### 2019-04-05 Manuscript.Rmd
fixes/cleaning to comm detection script, and revisions to manuscript

@@
 # This transformation is approximately normal with mean 0 and sd = sqrt(1 / (n - 3))
-fisherTanh <- function(Data = padjMatrix){
+fisherTanh <- function(Data = padjMatrix, preThresh = NA){
 
@@
 
+  if (is.numeric(preThresh)) {
+    Data[Data == 1] <- 0.999
+    Data[Data < preThresh] <- 0
+    transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
+  } else {
     # tanh
+    Data[Data == 1] <- 0.999
     transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
@@
     }
-  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n - 3)), lower.tail = F) # no lower tail, but absolute Zs = two tailed
+    transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)
 
@@
       transformed$adjustPvals <- tempMat
+
+      # retain only the significant adjusted pval Z scores
+      transformed$tanhZ[transformed$adjustPvals > 0.05] <- 0
+    }
   }
@@
 # Extras dictates whether the community object + correlation matrix should also be extracted
-communityDetection <- function(Data = parcelBins$First, ROIS = "None", Type = "vertex", thresh = F, extras = F) {
+communityDetection <- function(Data = parcelBins$First, ROIS = "None", Type = "vertex", extras = F) {
 
@@
     transfMat <- fisherTanh(Data = corrMat)
-    if (thresh == T) {
-      transfMat$tanhZ[transfMat$adjustPvals > 0.05] <- 0
-    }
+
     corrMat <- transfMat$tanhZ
@@
       transfMat <- fisherTanh(Data = corrMat)
-
-      # Determine if edges should be thresholded or not
-      if (thresh == T) {
-        transfMat$tanhZ[transfMat$adjustPvals > 0.05] <- 0
-      }
 
@@
 To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series).
-Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DMN or non-DMN more than 95% of the time.
+Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DMN or non-DMN more than 99% of the time.
 
@@
 
-``` {r Stability per subject: Overall, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Variability per subject: Overall, echo=FALSE, message = FALSE, cache = TRUE}
 # Load files
@@
 SVals <- lapply(temp, read.csv2)
+
+# concatenate all proportion of DMN affiliations per node to produce (1) a histogram for fig 4C, and (2) % of node affiliated with either community > 99% over time
+allPropDMN <- sapply(Summaries, "[[", "slidePropDMN")
 
@@
 
-## PLAYING WITH AR AND MA PROCESSES
-# tempSC <- do.call(rbind, SC)
-# tempSC <- SC_PFC
-# tempSC$SubjID <- as.factor(tempSC$SubjID)
-# test <- numeric()
-# intercepts <- numeric()
-# coefficients <- numeric()
-# 
-# for (i in seq(100)) {
-#   temp <- arima(SC[[i]]$Index, c(1,0,0), method = "ML")
-#   test <- c(test, temp$residuals)
-#   intercepts[i] <- temp$coef[2]
-#   coefficients[i] <- temp$coef[1] 
-# }
-# 
-# tempSC$Res <- test
-# 
-# ggplot(data = tempSC, aes(Window, Res, group = SubjID, color = SubjID)) +
-#   geom_line(show.legend = F, alpha = 0.5) +
-#   theme_classic()
-# 
-# ggplot(data = tempSC, aes(Res, group = SubjID, color = SubjID)) +
-#   geom_density(alpha = 0.5, show.legend = F) +
-#   theme_classic()
-# 
-# 
-# test <- aggregate(SC_PCC$Index, by = list(SC_PFC$SubjID), arima, order = c(10,0,0), method = "ML")
-# intercepts <- numeric()
-# coefficients <- numeric()
-# for(i in seq(100)) {
-#   intercepts[i] <- test$x[[i]]['intercept']
-#   coefficients[i] <- test$x[[i]]['ar1']
-# }
-# 
-# plot(intercepts)
-
-# AND WITH MORE SIMILARITY MATRICES
-# THE POINT HERE IS THAT I TOOK THE ARI SIMILARITY MATRIX OF ALL THE SLIDING WINDOWS PER SUBJECT AND AVERAGED ACROSS SUBJECTS
-# THIS PRODUCES A MATRIX WHERE YOU CAN TELL THE AUTOCORRELATED NATURE OF THE DATA IF UNCLUSTERED, BUT OTHERWISE THERE ARE MARKED DAY CLUSTERS
-# simMatrices <- list()
-# nrun <- 1
-# for (subj in SVals) {
-#   nWins <- ncol(subj)
-#   if (nWins != 37) {
-#     print("Fewer than 37 windows...")
-#   } else {
-#     tempMat <- matrix(NA, nWins, nWins)
-#     for (i in seq(nWins)) {
-#       for(j in seq(nWins)) {
-#         tempMat[i,j] <- arandi(subj[,i], subj[,j], adjust = T)
-#       }
-#     }
-#     simMatrices[[nrun]] <- tempMat
-#     nrun <- nrun + 1
-#   }
-# }
-# 
-# meanMatrices <- Reduce("+", simMatrices) / length(simMatrices)
-# corrplot(meanMatrices, method = "color", is.corr = F, cl.lim = c(0,1))
 ```
@@
 
-``` {r Stability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Variability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
 ## Check stability for PCC and mPFC separately
@@
   for (Win in seq(nWins)) {
-    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][,Win], adjust = T)
-    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][,Win], adjust = T)
+    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][, Win], adjust = T)
+    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][, Win], adjust = T)
   }
@@
 
-**This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
-These results suggest that some nodes were considerably variable in time, despite overall stability in the community arrangement.**
-
-There is precedent in thhe literature for the idea that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
+This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+However, only `r round(mean(allPropDMN < 0.01 | allPropDMN > 0.99), digits = 4) * 100` percent of the nodes across participants belonged to either community over 99% of the time.
+These results suggest that even though there is considerable stability in these partitionings, there is variability left to account for.
+
+There is precedent in the literature for the idea that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
 Therefore, we asked whether the magnitude of these eigenvector values was associated with the stability of nodes in time.
@@
 # Get a FV threshold for each subject based on mean vertex stability
-# Run the function safely, because some noisy subjects have no relationship between stability and FV
 # Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
@@
 
-# Store thre FV thresholds for all subject 
+# Store the FV thresholds for all subject 
 threshDF <- data_frame(SubjID = substring(subjList, 1, 6),
@@
 
-These analyses show that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DMN and non-DMN vertices.
+These analyses suggest that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DMN and non-DMN vertices.
 We therefore thresholded each subject's Fiedler vector to produce these refined maps.
-We estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 95%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
+We estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
 Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
@@
 With these thresholded partitions, we recomputed the overall similarity of their functional organization across participants.
-Compared to before, there was even **less overall agreement** of the full maps among individuals (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+Compared to before, there was even less overall agreement of the full maps among individuals (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
 The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
@@
 We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
-Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding across subjects (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unaffected (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r tsnrCohen_PCC[1]`).
+In terms of tSNR variability within each region, mPFC had overall greater standard deviation both before and after the threshold (mPFC: pre-threshold mean SD = 33.96, post-threshold mean SD = 30.15; PCC: pre-threshold mean SD = 15.28, post-threshold mean SD = 14.59).
+However, paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding across subjects (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unaffected (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r tsnrCohen_PCC[1]`).
 In fact, tSNR after thresholding was significantly higher for mPFC (permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
-**(TBD: in terms of tSNR variability (sd) within region, it is true  that mPFC > PCC, both before and after the threshold (mPFC: pre mean sd = 33.96, post mean sd = 30.15; PCC: pre mean sd = 15.28, post mean sd = 14.59))**
 
@@
 
-# Stats
+## Stats
+# one-sample signed rank per region
+Halves_PCC_ratioTest <- wilcox.test(Halves_RIRatios_PCC, mu = 1, alternative = "greater")
+Halves_PFC_ratioTest <- wilcox.test(Halves_RIRatios_PFC, mu = 1, alternative = "greater")
+
+# between regions
 Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T, statType = median)
@@
 # Save unthresholded subjects for comparing and plotting against correlation maps
-# this comment is temporary, just to force the cache to update
-Foo <- "Fighters"
 unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_unthresh[bestindx], "[", i = !posteriorIndx, j =)
@@
 
-Figure 6 shows these ARI ratios for PCC and mPFC for all individuals As expected, we found that while both regions showed evidence for specificity (i.e.
-ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; IQR = `r quantile(Halves_RIRatios_PFC, 0.25)` - `r quantile(Halves_RIRatios_PFC, 0.75)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; IQR = `r quantile(Halves_RIRatios_PCC, 0.25)` - `r quantile(Halves_RIRatios_PCC, 0.75)`) when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`) **(TBD: test against 1.
-I think it might be worth doing it for PCC's sake, as mPFC's numbers + figure already convey its idiosyncrasy very well.
-If we do it here, we'll do it for the run-specific analysis too)**.
+Figure 6 shows these ARI ratios for PCC and mPFC for all individuals.
+A signed-rank test showed evidence for specificity (i.e.
+ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; IQR = `r quantile(Halves_RIRatios_PFC, 0.25)` - `r quantile(Halves_RIRatios_PFC, 0.75)`; V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; IQR = `r quantile(Halves_RIRatios_PCC, 0.25)` - `r quantile(Halves_RIRatios_PCC, 0.75)`; V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`).
+Moreover, the ratios for mPFC  were significantly higher than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
 These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns.
@@
 Run-specific SP results could still capture a subject's unique organizational pattern to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, this time using the mean across-run (within-participant) ARI in the denominator of the ratio (Figure 6).
+We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, this time using the mean across-run (within-participant) ARI in the denominator of the ratio (Figure 6, right).
 
@@
 
+** TODO: median, IQR, and one sample test.
 Ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, SD = `r round(sd(Sess_RIRatios_PFC), digits = 2)`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, SD = `r round(sd(Sess_RIRatios_PCC), digits = 2)`).
-This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
+This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.**
 
@@
 ```{r Meta-analysis ROIs (Fig.
-1), out.width="50%", fig.align = "center", fig.cap= "A: Proportion of times each ROI was reported in each literature.
+1), out.width = "50%", fig.align = "center", fig.cap= "A: Proportion of times each ROI was reported in each literature.
 B: common and unique brain regions associated with DMN and subjective value.
@@
 ```{r Template partition (Fig.
-2), out.width="50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307).
+2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307).
 Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
@@
 # SC_FVvPDMN_plot
+#
+# # histogram on 4 C
+# hist(allPropDMN)
 
@@
 
-```{r BandB comparison (Figure 16), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga and Buckner's (2017) criterion, and those produced by spectral partitioning.
-Networks A and B were produced by carefully selecting a DLPFC seed (pointed by the green arrows).
-In each case, our DMN and non-DMN networks map remarkably well to their proposed functional organization."}
+```{r BandB comparison (Figure 16), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga and Buckner's (2019) criterion, and those produced by spectral partitioning.
+Networks A and B were produced by selecting seeds in diagnostic TPJ, DLPFC and PHC.
+In each case, our DMN and non-DMN networks map well to their proposed functional organization, albeit with some discrepancies on network A/non-DMN."}
 

### 2019-04-05 community_detection.R
accidentally removed relevant code from community_detection script. Reinstated

@@ -5,7 +5,6 @@ write(paste("Analyzing data for subject", SubjID), stdout())
 library(igraph)
 library(data.table)
 library(parallel)
-library(tidyverse)
 
 ## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
 # This takes either a matrix of correlation values (vectors too, but manually compute pvals)
@@ -148,12 +147,13 @@ labelCoords_vertex <- read.table('labelCoords_vertex.csv', sep = ",", header = T
 # load data
 write("Loading data", stdout())
 Data <- fread(paste("./tseries/", SubjID, "_timeSeries.csv", sep = ""), header = F)
-
+Data <- data.matrix(Data)
 # append the ROI label to each vertex
 dimnames(Data) <- list(labelCoords_vertex$Label, seq(ncol(Data)))
 
 # select ROIs
-indx <- sapply(yeoLbls, function(lbl) {grep(lbl, rownames(Data))}) %>% reduce(c)
+indx <- sapply(yeoLbls, function(lbl) {grep(lbl, rownames(Data))}) 
+indx <- do.call(c, indx)
 
 # reduce time series to only search space
 nVerts <- length(indx)

### 2019-04-05 community_detection.R
oops

@@ -162,7 +162,7 @@ tseries <- Data[indx, ]
 # analyze
 write("Correlating data", stdout())
 corrMat <- cor(t(tseries))
-transfMat <- fisherTanh(Data = corrMat, thresh = corrThresh)
+transfMat <- fisherTanh(Data = corrMat, preThresh = corrThresh)
 corrMat <- transfMat$tanhZ
 
 diag(corrMat) <- 0 # avoid self-loops when creating the graph

### 2019-04-05 Manuscript.Rmd
Final touches on Joe's comments, and rounding up numbers. Now onto the discussion!

@@
 temp <- list.files()
-subjList <- sapply(temp, substring, first=1, last=6)
+subjList <- sapply(temp, substring, first = 1, last = 6)
 Summaries <- lapply(temp, read.csv)
@@
 In terms of tSNR variability within each region, mPFC had overall greater standard deviation both before and after the threshold (mPFC: pre-threshold mean SD = 33.96, post-threshold mean SD = 30.15; PCC: pre-threshold mean SD = 15.28, post-threshold mean SD = 14.59).
-However, paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding across subjects (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unaffected (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r tsnrCohen_PCC[1]`).
+However, paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding across subjects (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unaffected (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
 In fact, tSNR after thresholding was significantly higher for mPFC (permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
@@
 A signed-rank test showed evidence for specificity (i.e.
-ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; IQR = `r quantile(Halves_RIRatios_PFC, 0.25)` - `r quantile(Halves_RIRatios_PFC, 0.75)`; V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; IQR = `r quantile(Halves_RIRatios_PCC, 0.25)` - `r quantile(Halves_RIRatios_PCC, 0.75)`; V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`).
+ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC, 0.75), digits = 2)`, V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC, 0.75), digits = 2)`, V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`).
 Moreover, the ratios for mPFC  were significantly higher than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
@@
 
-# Stats
+## Stats
+# one-sample signed rank per region
+Sess_PCC_ratioTest <- wilcox.test(Sess_RIRatios_PCC, mu = 1, alternative = "greater")
+Sess_PFC_ratioTest <- wilcox.test(Sess_RIRatios_PFC, mu = 1, alternative = "greater")
+
+# between
 Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T, statType = median)
@@
 
-** TODO: median, IQR, and one sample test.
-Ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`), but both were mostly above 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, SD = `r round(sd(Sess_RIRatios_PFC), digits = 2)`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, SD = `r round(sd(Sess_RIRatios_PCC), digits = 2)`).
-This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.**
+As before, a signed rank test showed that both regions were significantly above 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), but ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
+This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
 

### 2019-04-05 Manuscript.Rmd
fig captions up to date

@@
 To evaluate the third possibility, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
-If the variability we observed were truly due to having captured an individual's unique organization, day to day ARI values should be consistently higher within- than between-individuals.
+If the variability we observed were truly due to having captured an individual's unique organization, day to day ARI values should be consistently higher within- than between-individuals (an example comparison for two subjects is provided on Supplemental Figure 2).
 Figure 6 shows pairwise comparisons among ten example subjects for PCC and mPFC separately (left).
@@
 Grey lines display each subject's association, while the black line shows the fit from a mixed-effects logistic regression.
-Dashed red lines indicate the mean FV value at which maps were thresholded.", echo=FALSE, message = FALSE}
+Dashed red lines indicate the mean FV value at which maps were thresholded.
+The histogram counts the mean number of vertices that were affiliated at each proportion.", echo=FALSE, message = FALSE}
 # code to generate plots

### 2019-04-07 community_detection.R
added a kmeans script, and made community_detection more flexible

@@ -61,8 +61,19 @@ fisherTanh <- function(Data = padjMatrix, preThresh = NA){
   
 }
 
+# To store files ready to be converted to CIFTI
+HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){
+  
+  nVertices <- 59412
+  tempVec <- rep(padding, nVertices)
+  temp <- grep(MOI, colnames(Data))
+  tempVec[Data$Vertex] <- Data[[temp]]
+  write.table(file = paste(SubjID,"_",MOI,'_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")
+  
+}
+
 # if a minimum corr value is desired (otherwise set NA for p-value based thresholding)
-corrThresh <- 0.2
+corrThresh <- NA
 
 # ROIs
 yeoLbls <- c("L_25_ROI",
@@ -139,15 +150,41 @@ yeoLbls <- c("L_25_ROI",
              "L_23c_ROI",
              "R_23c_ROI",
              "R_PreS_ROI",
-             "R_H_ROI")   
+             "R_H_ROI",
+             "L_STSdp_ROI",
+             "L_STSvp_ROI",
+             "L_STSva_ROI",
+             "L_TE1m_ROI",
+             "L_TE1a_ROI",
+             "L_TPOJ1_ROI",
+             "L_8Av_ROI",
+             "L_8C_ROI",
+             "L_PHA2_ROI",
+             "L_44_ROI",
+             "L_PSL_ROI",
+             "R_STV_ROI",
+             "R_TPOJ1_ROI",
+             "R_TE1m_ROI",
+             "R_STSdp_ROI",
+             "R_STSda_ROI",
+             "R_8Av_ROI",
+             "R_8C_ROI",
+             "R_PCV_ROI",
+             "R_PHA1_ROI",
+             "R_p47r_ROI")   
 
 # load labels and ensure they are numeric
 labelCoords_vertex <- read.table('labelCoords_vertex.csv', sep = ",", header = T)
+
+# get ROI indices
+indx <- sapply(yeoLbls, function(lbl) {grep(lbl, labelCoords_vertex$Label)}) 
+indx <- do.call(c, indx)
 
 # load data
 write("Loading data", stdout())
 Data <- fread(paste("./tseries/", SubjID, "_timeSeries.csv", sep = ""), header = F)
 Data <- data.matrix(Data)
+
 # append the ROI label to each vertex
[…]

### 2019-04-07 kmeans.R
added a kmeans script, and made community_detection more flexible

@@ -1,0 +1,165 @@
+#!/usr/bin/env Rscript
+SubjID <- 101006
+nClusts <- 3
+thresh <- T
+
+library(data.table)
+
+# To store files ready to be converted to CIFTI
+HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0, n = 12){
+  
+  nVertices <- 59412
+  tempVec <- rep(padding, nVertices)
+  temp <- grep(MOI, colnames(Data))
+  tempVec[Data$Vertex] <- Data[[temp]]
+  write.table(file = paste(SubjID,'_Kmeans_', n, 'clusters_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")
+  
+}
+
+# load data
+setwd('./tseries')
+temp <- list.files(pattern = paste(SubjID, "_Session*", sep=""))
+timeSeries_sess <- lapply(temp, fread, header=F)
+timeSeries_sess <- lapply(timeSeries_sess, data.matrix)
+
+tseries <- do.call(cbind, timeSeries_sess)
+
+setwd('../BB_comparison/')
+
+if (thresh) {
+  # ROIs
+  yeoLbls <- c("L_25_ROI",
+               "L_OFC_ROI",
+               "L_10v_ROI",
+               "R_25_ROI",
+               "R_OFC_ROI",
+               "R_10v_ROI",
+               "L_s32_ROI",
+               "L_RSC_ROI",
+               "R_RSC_ROI",
+               "R_23d_ROI",
+               "R_d23ab_ROI",
+               "R_31a_ROI",
+               "R_31pv_ROI",
+               "R_31pd_ROI",
+               "R_7m_ROI",
+               "R_v23ab_ROI",
+               "R_p24_ROI",
+               "R_d32_ROI",
+               "R_9m_ROI",
+               "R_p32_ROI",
+               "R_a24_ROI",
+               "R_10r_ROI",
+               "R_10d_ROI",
+               "L_23d_ROI",
+               "L_d23ab_RO",
+               "L_31a_ROI",
+               "L_31pv_ROI",
+               "L_31pd_ROI",
+               "L_7m_ROI",
+               "L_v23ab_ROI",
+               "L_p24_ROI",
+               "L_d32_ROI",
+               "L_9m_ROI",
+               "L_p32_ROI",
+               "L_a24_ROI",
+               "L_10r_ROI",
+               "L_10d_ROI",
[…]

### 2019-04-07 graphAnalysis.R
added a kmeans script, and made community_detection more flexible

@@ -1,0 +1,1541 @@
+#!/usr/bin/env Rscript
+SubjID <- commandArgs(trailingOnly=TRUE)
+write(paste("Analyzing data for subject", SubjID), stdout())
+
+### Run a graph theoretic fMRI analysis
+
+###------- Libraries and functions ---------------
+write('Loading functions and libraries...', stdout())
+
+library(igraph)
+#library(tidyverse)
+library(ggnetwork)
+library(ggplot2)
+library(gridExtra)
+library(data.table)
+library(plyr)
+library(mcclust)
+library(lme4)
+library(parallel)
+#library(lmerTest)
+
+## log-log degree distribution
+logDegreeDist <- function(Graph = padjMat) {
+  
+  tempD <- degree(Graph)
+  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
+  d <- (0:(max(tempD)-1))
+  ind <- (tempDD!=0)
+  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
+       xlab = "Log-Degree", ylab = "Log-Intensity",  
+       main = "Log-Log Degree Distribution")
+  
+}
+
+
+## Create correlation matrix between vertices of 2 ROIs
+# Requires labeled time series matrix
+vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
+  
+  # extract the time series from the ROIs
+  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
+  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
+  nVerts_1 <- length(indexing_1)
+  nVerts_2 <- length(indexing_2)
+  ROI_1_tseries <- timeSeries[indexing_1, ]
+  ROI_2_tseries <- timeSeries[indexing_2, ]
+  
+  # Create empty matrix
+  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)
+  
+  # 
+  for (vertex_1 in seq(nVerts_1)){
+    
+    # temp series 1
+    tempOne <- ROI_1_tseries[vertex_1, ]
+    
+    for(vertex_2 in seq(nVerts_2)){
+      
+      # temp series 2
+      tempTwo <- ROI_2_tseries[vertex_2, ]
+      
+      # store the Pearson correlation in the corr matrix
[…]

### 2019-04-07 community_detection.R
forgot to properly specify eigenvector/values to be written to csv

@@ -212,7 +212,7 @@ tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirect
 
 # run K-means as a clustering control (no seeding, this is just proving a point)
 write("Running K-Means", stdout())
-km <- kmeans(tseries, 2, iter.max = 100)$cluster
+km <- kmeans(tseries, 3, iter.max = 100)$cluster
 
 
 # Run a fastgreedy modularity community detection on ROIs
@@ -224,12 +224,14 @@ tempCommunity <- fastgreedy.community(tempGraph)
 write("Running SP", stdout())
 tempLap <- laplacian_matrix(tempGraph, normalized=T)
 tempEigen <- eigen(tempLap)
+eigenVals <- tempEigen$values
+eigenVecs <- tempEigen$vectors
 
 # store all outputs in this data frame, so they can be written afterwards in HCP format  
 df <- data.frame(Vertex = indx,
-                 eigenVal = eigenVals$V1,
+                 eigenVal = eigenVals,
                  FV = eigenVecs[ , ncol(eigenVecs) - 1],
-                 modularity = modularity$V1,
+                 #modularity = modularity$V1,
                  kmeans = km)
 
 # write to text files ready to be transformed to CIFTIs

### 2019-04-15 Manuscript.Rmd
Addressed most of Sean's comments on Intro, methods, and Results

@@
 title: 'Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex'
-author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
+author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
 output:
@@
     keep_tex: true
+    highlight: haddock
   word_document: 
-    reference_docx: Style_reference_draft.docx
+    reference_docx: APA_style.docx #Style_reference_draft.docx 
   html_document: default
@@
 
+2.  Graduate Program for Neuroscience, Boston University, Boston, USA
+
 Corresponding author:
@@
 These regions are also implicated in a set of functions associated with the default-mode network (DMN).
-DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Fox2005; @Yeo2011].
-
-  Coordinate-based meta-analyses of the fMRI literature have demonstrated that valuation and DMN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017].
+DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Greicius2003; @Fox2005; @Yeo2011].
+
+  Coordinate-based meta-analyses of the fMRI literature suggest that valuation and DMN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017].
 The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DMN.
@@
 One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DMN effects.
-The potential existence of common nodes has primpted theorizing about posible cognitive-level overlap between valuation and DMN-related processes.
+The potential existence of common nodes has prompted theories positing overlap between valuation and DMN-related cognitive processes.
 For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Northoff2012; @Clithero2014; @Acikalin2017; @Reddan2018].
 
-  However, to draw firm conclusions about functional overlap will require a better understanding of individual-level heterogeneity in topographic patterns of brain activity.
-A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Woo2014; @Michalka2015; @Wang2015], potentially exaggerating the degree of overlap across domains.
+  However, concluding that colocalization at the group level equates to overlap in cognitive function requires a better understanding of individual-level heterogeneity in topographic patterns of brain activity.
+A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Woo2014; @Michalka2015; @Wang2015; @Tobyne2018], potentially exaggerating the degree of overlap across domains.
 This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a].
@@
 In the context of network analysis, community detection algorithms have been successfully used to subdivide brain networks into multiple distinct communities [@Garcia2017].
-Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016].
+Such communities represent clusters of network nodes that share more connections with each other than with the rest of the network [@Fortunato2016].
 In attempting to refine the DMN topography at the individual level, we focus on dividing mPFC and PCC into communities encapsulating what belongs and does not belong to DMN.
@@
 positive or negative number).
-SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018], and was recently shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
-This method can therefore capture a refined group of brain regions that more cohesively share activation patterns during rest.
+SP has recently been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was recently shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
+This method can therefore capture a refined group of brain regions that more cohesively share spontaneously covarying temporal activation patterns during rest.
 
@@
 A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level.
-We then derived an rsFC network of all the surface vertices within the search space for each of `r nSubj` individual resting-state fMRI data sets from the Human Connectome Project (HCP)[@VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel).
+We then derived an rsFC network of all the surface vertices within the search space for each of `r nSubj` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel).
 Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community.
 The resulting communities varied topographically across subjects, while also appearing to follow common organizational principles.
-A combination of sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC.
+Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC.
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
-Lastly, we provide evidence that the resulting communities resembled an organizational scheme recently observed in a handful of subjects [@Braga2017].
+Lastly, we provide evidence that the resulting automatically defined communities resembled an organizational scheme recently observed in a series of low N studies [@Braga2017; @Braga2019].
 Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
@@
 [-@Yeo2011].
-First, we selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial wall.
-Next, we overlayed those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
+First, we selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial surface in HCP's 32,000 surface space (fs_LR_32k).
+Next, we overlaid those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
 This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1).
-The search space was naturally divided into two spatially discontiguous clusters that covered PCC and mPFC, facilitating the study of each general region separately.
+The search space was naturally divided into two spatially discontinuous clusters that covered PCC and mPFC, facilitating the study of each general region separately.
 
@@
 For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009].
-The indicator map for each study was then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/).
+The indicator map for each study was then projected to a standard cortical mesh (fsaverage, 160,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/).
+**TODO: The Glasser et al.
+(2016) parcellation was resampled to fsaverage to pair spheres to parcels from our search space**.
 Any sphere sections that overlapped with the cortex (no lower limit restrictions) were mapped to the corresponding parcel, and we tallied how many studies had positive indicator values in each parcel.
@@
 
-With these lists, we tested for parcels that were significantly more strongly associated with one domain than the other.
+With these lists, we tested for parcels that were significantly more strongly associated with one domain than the other with a chi-squared test.
 We permuted the label of every study (i.e.
-DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains.
+DMN or valuation) 5000 times while preserving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains.
 This gave us a null distribution of 5000 maximum chi-squared values.
@@
 ```
-Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
+
+Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (N = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
 Each subject's data was acquired over two days at Washington University in St.
 Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany).
-Four resting state runs (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised up to 1200 time points(14 min 33 s) for a total of up to 4800 time points (median = `r median(corrCounts$nTR)`, minimum = `r min(corrCounts$nTR)`).
+Four resting state runs (repetition time = 0.720 s, echo time = 33.1 ms, flip angle = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised up to 1200 time points (14 min 33 s) for a total of up to 4800 time points (median = `r median(corrCounts$nTR)`, minimum = `r min(corrCounts$nTR)`).
 Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other.
@@
 subjects with four rsfMRI sessions).
-In addition, only datasets with either low motion levels (under 1.5 mm) or under 0.5 mm mean framewise displacement (FD) were used.
+In addition, only datasets with low motion levels (under 1.5 mm) and less than 5% of points over 0.5 mm framewise displacement (FD) were used.
 See [@VanEssen2012] for more details about the data acquisition protocol.
 
-Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, temporal denoising based on independent components (FIX, [@Griffanti2014; @Salimi-Khorshidi2014]), high-pass filtering (0.0005 Hz threshold), and MNI152-based normalization.
+Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, high-pass filtering (0.0005 Hz threshold), MNI152-based normalization, surface reconstruction, and mapping of functional data to the surface (details can be found on Glasset et al., 2013).
+In addition, data underwent temporal denoising based on independent components [FIX; @Griffanti2014; @Salimi-Khorshidi2014].
 Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017].
-Steps included linear interpolation across timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising and high-motion censoring by deletion, as well as mean greyordinate signal regression [@Burgess2016].
-Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses.
+Steps included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising via grayordinate signal regression [@Burgess2016] and censoring of high-motion timepoints by deletion.
 Finally, data acquired on the same day (i.e.
 left-right and right-left phase encoding session) were temporally demeaned.
-Each subject's brain was comprised of 32k standard HCP greyordinates per hemisphere (combined in a CIFTI file).
+Each subject's brain was comprised of 32k standard grayordinates per hemisphere (combined in a CIFTI file).
 We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.
@@
 
-All network analyses were performed using the igraph package [@G.2006] in R 3.4.1 [@RTeam2018].
+All network analyses were performed using the igraph package [@G.2006; https://igraph.org/r/] in R [v.
+3.4.1; @RTeam2018; https://www.r-project.org/].
 To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices.
 This produced a weighted network for each subject, in which the nodes were surface vertices and the edges were the correlations among them.
-Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify strong correlations.
-The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values).
+Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify significant connections.
+The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were set to 0 (all other edges retained their respective z-values).
 The proportion of remaining edges (i.e.
@@
 Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
-Values of 1 of this transformed distribution were returned to 0 in order to avoid the inclusion of these edges in the network analyses.
+Values of 1 of this transformed distribution were reset to 0 in order to avoid the inclusion of these edges in the network analyses.
 We generated and analyzed network weight matrices at four levels: (1) for each run separately (1200 TRs each); (2) for the concatenated time series for the two runs on each day (2400 TRs total); (3) for each subject's full dataset (4800 TRs total); and (4) on each step of a sliding window analysis (see Partition Evaluation for more details).
@@
 Communities (i.e.
-clusters) were identified using the SP algorithm [@Belkin2003; @Chung1999; @Fiedler1975].
+clusters) were identified using the SP algorithm [@Fiedler1975; @Chung1999; @Belkin2003].
 First, each network was represented as an $n$ x $n$ network weight matrix $W$ as described above (where $n$ equals the number of vertices in the search space, 4,801).
-This matrix was then transformed into its normalized Laplacian form
+This matrix was then transformed into its symmetric normalized Laplacian form
 
@@
 
-Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its transformed correlation values with every other vertex), and $W$ is the network weight matrix.
+Where $I$ is an identity matrix of size $n$, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
+the sum of its Fisher transformed correlation values with every other vertex), and $W$ is the Fisher transformed network weight matrix.
 This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal.
 The transformation ensures that every row sums to zero.
-We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
+We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
 This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975].
@@
 Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community as that which contained the DMN-specific PCC parcel identified in our meta-analysis.
-The high density of these networks ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].
-
-In order to evaluate the convergent validity of the resulting partitionings across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al.
+The high density of the graphs ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].
+
+In order to evaluate the validity of the resulting partitionings across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al.
 [-@Clauset2004].
@@
 Unlike SP, modularity can fractionate a network into more than two communities.
-We assumed that if the partitionings from the bounded and unbounded community detection methods showed high levels of agreement, we could gain confidence in that we were indeed fractioning the search space into an adequate number of communities.
-We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by SP to be non-zero.
-This eigenvalue serves as an estimator of the optimal number of communities in a network [@Chung1999], such that a rank of two in our partitions justifies limiting the number of communities to two.
+Agreement between the partitions provided by the bounded and unbounded community detection methods would indicate confidence in the partitions.
 
@@
 
-In order to evaluate the stability and topographical heterogeneity of the communities within and across individuals, we chose the adjusted rand index (ARI) as a reference metric of agreement between two partitionings [@Hubert1985], which was calculated using the "mcclust" package in R [@Arno2012].
+We used the adjusted Rand index (ARI) to evaluate the stability and topographical heterogeneity of the communities within and across individuals [@Hubert1985], which was calculated using the "mcclust" package in R [@Arno2012].
 The base of the ARI is computed by the formula
@@
 
-Where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number grouped together (separately) in one partition, but separately (together) in the other.
+where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number of nodes grouped together (separately) in one partition, but separately (together) in the other.
 Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $(n\times (n - 1))/2$).
@@
 Alignment between the two algorithms would therefore give us confidence in the validity of the resulting partitionings.
-Next, we compared the partitionings derived from each individual's full time series across subjects, and report the mean pairwise ARI for the group.
+Next, we compared the partitionings derived from each individual's full time series across subjects, and calculated the mean pairwise ARI for the group.
 We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects.
@@
 
-To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the partition derived from the whole subject's data.
+To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partition against the partition derived from the whole subject's data.
 A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017].
@@
 
-We then estimated the level of agreement between network partitions estimated using data from individual days (with 2 days per participant).
+We then estimated the level of agreement between network partitions estimated using data across individual scan days (with 2 days per participant).
 If the functional organization estimated by SP is indeed individual-specific, we should see higher agreement within individual (test/re-test across days) than across individuals.
@@
 Unique areas were identified by first permuting the domain labels across studies (DMN or SV) to create a null distribution for the maximum chi-squared statistic in the search space (see Methods for details).
-The null distribution was used to identify regions that were reported significantly more often reported in one literature or the other.
+The null distribution was used to identify regions that were reported significantly more often in one literature or the other.
 
@@
 There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.005; Right: observed $\chi^2$ = 12.83, *p* = 0.005); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum.
-No toher parcels were preferentially implicated in valuation relative to DMN.
+No other parcels were preferentially implicated in valuation relative to DMN.
 We therefore selected area 7m as an interpretable, bilateral reference point for labeling DMN and non-DMN communities in the analyses that follow.
@@
 modularityCounts_extra <- sapply(modularityCounts, function(x) {sum(x[3:4], na.rm = T)})
-
-# eigenvalue-based diagnosis of optimal n of communities
-prcntDissection <- lapply(Summaries, function(data) {which(data$EigenVal < 0.00001)}) # how many consecutive 0s?
-prcntDissection <- mean((sapply(prcntDissection, length) + 1) == 2) * nSubj # % of subjects who only had 1 zero (thus optimal cuts = 2)
 
@@
 However, these communities encompassed a small number of vertices (median = `r median(modularityCounts_extra)`, IQR = `r quantile(modularityCounts_extra, 0.25)` - `r quantile(modularityCounts_extra, 0.75)`) compared to the principal two (median = `r median(modularityCounts_two)`, IQR = `r quantile(modularityCounts_two, 0.25)` - `r quantile(modularityCounts_two, 0.75)`, suggesting that the overall network is composed of two main communities.
-In addition, the estimation of the optimal number of cuts based on the rank of the first non-zero eigenvalue (see "Partition evaluation" for details) showed that `r prcntDissection` percent of the individual networks were best partitioned into two communities.
 
 Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
-Qualitative inspection of the brain community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects.
+Qualitative inspection of the community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects.
 To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3).
@@
 
-In order to estimate the degree of stability of these partitions in time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min), comparing the partitioning derived from each window with the partitioning computed using the entire time series (Figure 4).
+In order to estimate the stability of these partitions over time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min); comparing the partitioning derived from each windowed time series with the partitioning computed using the entire time series (Figure 4).
 
@@
 
-This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* = `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
 However, only `r round(mean(allPropDMN < 0.01 | allPropDMN > 0.99), digits = 4) * 100` percent of the nodes across participants belonged to either community over 99% of the time.
 These results suggest that even though there is considerable stability in these partitionings, there is variability left to account for.
+**TBD from Sean: I think this point deserves some additional analysis, or discussion.
+My bet is that this comes down to signal noise  and its interaction with the SP algorithm, but it would be very helpful to show this somehow.
+Stability is key for the impact of this paper and this paragraph, as it is currently written, suggests to me that the vertex-level stability it not as stable as I might want it to be**
 
 There is precedent in the literature for the idea that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
-Therefore, we asked whether the magnitude of these eigenvector values was associated with the stability of nodes in time.
+Therefore, we tested whether the magnitude of the eigenvector values was associated with the stability of nodes in time.
 Specifically, we estimated the proportion of DMN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
@@
 
-These analyses suggest that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DMN and non-DMN vertices.
+These analyses suggest that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DMN and non-DMN vertices on an individual subject basis.
 We therefore thresholded each subject's Fiedler vector to produce these refined maps.
-We estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
+For each individual, we estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
 Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
@@
 We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations.
-We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC limiting this to 7m as a seed.
-I think it makes sense, especially since we're saying that PCC (1) is also subdivided to some extent, and (2) also shifts across individuals to some extent.
-Alternatively, you wouldn't use 7m as a seed unless you just wanted to find DMN.
-Full PCC is what a traditional analysis might have done.
+We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC.
 We compared the map of correlation values in mPFC to the map of unbinarized Fiedler vector values.
@@
 We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
-In their work, Braga and Buckner selected individual vertices along areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two anticorrelated networks [@Braga2017; @Braga2019].
+In their original work, Braga and Buckner manually selected individual vertices along areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two anticorrelated networks [@Braga2017; @Braga2019].
 Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to reproduce our prtitionings by selecting seeds in one these diagnostic areas.
@@
 Since our search space did not contain areas TPJ and PHC, lack of signal from these areas could drive the small discrepancies in the topography between our work and theirs (particularly for network A).
-Nevertheless, these qualitative similarities are important, as they collectively suggest there may exist a true functional partitioning of canonical DMN regions into two distinct communities.
+Nevertheless, these qualitative similarities are important, as they collectively suggest that canonical DMN regions consist of two distinct communities.
 Results from the present investigation suggest that the topographic organization of the communities is variable across a large sample of participants, especially in mPFC, and that the SP algorithm is a useful and reliable tool for identifying the two communities in individuals.

### 2019-04-15 batch_makeIM.sh

@@ -328,10 +328,6 @@ while IFS=$'\t' read -r -a label ; do
 done < $HOME/fMRI/Glasser_labels_rh.csv
 
 
-## To do ##
-# - Turn some things into functions on separate files (set function path as "". /path/to/functions" at the beginning of the script, including the period)
-# - Might be good to cat echos like (echo ; echo "Skip..." ; echo) to avoid extra lines
-# - mris_ca_train might be good to combine each study's resulting annotation file
 
 #                                         ######----------- Notes -----------######
 #

### 2019-04-15 Manuscript.Rmd
line numbers, fixed n of subjects reported, and other tweaks

@@
     - \usepackage{setspace}\doublespacing
+    - \usepackage[left]{lineno}
+    - \linenumbers
 ---
@@
 ``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
-# this is used to get the number of subjects and proportion maps for the group (for visualization only)
-setwd('./For_HCP')
-temp <- list.files(pattern = '*Binary*')
-FB <- lapply(temp, read.table)
-Summed <- do.call(cbind, lapply(FB, "[[", 'V1')) - 1
-FB_Means <- rowMeans(Summed)
-nSubj <- length(temp)
-rm(temp)
+# this is used to get the number of subjects 
+setwd('./Summary/')
+nSubj <- length(dir())
 ```
@@
 Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany).
-Four resting state runs (repetition time = 0.720 s, echo time = 33.1 ms, flip angle = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised up to 1200 time points (14 min 33 s) for a total of up to 4800 time points (median = `r median(corrCounts$nTR)`, minimum = `r min(corrCounts$nTR)`).
+Four resting state runs (repetition time = 0.720 s, echo time = 33.1 ms, flip angle = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised 1200 time points (14 min 24 s) for a total of 4800 time points.
 Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other.
@@
 left-right and right-left phase encoding session) were temporally demeaned.
+The post-processed time series had a median of `r median(corrCounts$nTR)` time points (minimum = `r min(corrCounts$nTR)`) across participants.
 Each subject's brain was comprised of 32k standard grayordinates per hemisphere (combined in a CIFTI file).

### 2019-04-18 graphAnalysis.R
cleaned up graphAnalysis so it shows the relevant analyses

@@ -17,183 +17,6 @@ library(plyr)
 library(mcclust)
 library(lme4)
 library(parallel)
-#library(lmerTest)
-
-## log-log degree distribution
-logDegreeDist <- function(Graph = padjMat) {
-  
-  tempD <- degree(Graph)
-  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
-  d <- (0:(max(tempD)-1))
-  ind <- (tempDD!=0)
-  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
-       xlab = "Log-Degree", ylab = "Log-Intensity",  
-       main = "Log-Log Degree Distribution")
-  
-}
-
-
-## Create correlation matrix between vertices of 2 ROIs
-# Requires labeled time series matrix
-vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
-  
-  # extract the time series from the ROIs
-  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
-  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
-  nVerts_1 <- length(indexing_1)
-  nVerts_2 <- length(indexing_2)
-  ROI_1_tseries <- timeSeries[indexing_1, ]
-  ROI_2_tseries <- timeSeries[indexing_2, ]
-  
-  # Create empty matrix
-  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)
-  
-  # 
-  for (vertex_1 in seq(nVerts_1)){
-    
-    # temp series 1
-    tempOne <- ROI_1_tseries[vertex_1, ]
-    
-    for(vertex_2 in seq(nVerts_2)){
-      
-      # temp series 2
-      tempTwo <- ROI_2_tseries[vertex_2, ]
-      
-      # store the Pearson correlation in the corr matrix
-      corrMat[vertex_1, vertex_2] <- cor(tempOne, tempTwo, method = "pearson") 
-      
-    }
-  }
-  
-  # name the dimensions of the matrix according to the surface vertex index
-  rownames(corrMat) <- indexing_1
-  colnames(corrMat) <- indexing_2
-  
-  # plot (optional?)  
-  # unclustered heatmap
-  heatmap(corrMat,
-          Rowv = NA,
-          Colv = NA,
-          scale = "row",
-          col = pallette(1000))
-  
-  # clustered heatmap
-  heatmap(corrMat,
-          scale = "row",
[…]

### 2019-04-18 graphAnalysis_solo.R

@@ -1,1541 +1,0 @@
-#!/usr/bin/env Rscript
-SubjID <- commandArgs(trailingOnly=TRUE)
-write(paste("Analyzing data for subject", SubjID), stdout())
-
-### Run a graph theoretic fMRI analysis
-
-###------- Libraries and functions ---------------
-write('Loading functions and libraries...', stdout())
-
-library(igraph)
-#library(tidyverse)
-library(ggnetwork)
-library(ggplot2)
-library(gridExtra)
-library(data.table)
-library(plyr)
-library(mcclust)
-library(lme4)
-library(parallel)
-#library(lmerTest)
-
-## log-log degree distribution
-logDegreeDist <- function(Graph = padjMat) {
-  
-  tempD <- degree(Graph)
-  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
-  d <- (0:(max(tempD)-1))
-  ind <- (tempDD!=0)
-  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
-       xlab = "Log-Degree", ylab = "Log-Intensity",  
-       main = "Log-Log Degree Distribution")
-  
-}
-
-
-## Create correlation matrix between vertices of 2 ROIs
-# Requires labeled time series matrix
-vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
-  
-  # extract the time series from the ROIs
-  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
-  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
-  nVerts_1 <- length(indexing_1)
-  nVerts_2 <- length(indexing_2)
-  ROI_1_tseries <- timeSeries[indexing_1, ]
-  ROI_2_tseries <- timeSeries[indexing_2, ]
-  
-  # Create empty matrix
-  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)
-  
-  # 
-  for (vertex_1 in seq(nVerts_1)){
-    
-    # temp series 1
-    tempOne <- ROI_1_tseries[vertex_1, ]
-    
-    for(vertex_2 in seq(nVerts_2)){
-      
-      # temp series 2
-      tempTwo <- ROI_2_tseries[vertex_2, ]
-      
-      # store the Pearson correlation in the corr matrix
[…]

### 2019-04-18 Manuscript.Rmd
cleaned up graphAnalysis so it shows the relevant analyses

@@
     group_by(region) %>% 
-    dplyr::summarise(mean_tsnr = mean(varCoeff)) %>%
+    dplyr::summarise(mean_tsnr = mean(tSNR)) %>%
     ungroup()

### 2019-04-18 Manuscript.Rmd
renamed variables, and deleted unnecessary ones from data, manuscript, and graphAnalysis script

@@
 nVertices <- nrow(Summaries[[1]]) # in case I need the number of vertices included per brain
+
 ```
@@
 
-### Testing grounds
-# this part compares the distribution of Fiedler values for DMN and nonDMN
-# note: remove filter(y > 0) for 'full brain'
-# First plot compares the median FV between communities across subjects
-allSummaries <- do.call(rbind, Summaries)
-allSummaries$SubjID <- rep(subjList, each = nVertices) 
-ecdfPCC <- allSummaries %>%
-          mutate(FV_abs = abs(FiedlerVec),
-                 Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
-          filter(y < 0) %>%
-          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
-          stat_ecdf(alpha = 0.3) +
-          #scale_color_manual(values = c("Yellow", "Red")) +
-          xlim(0,0.05) +
-          geom_vline(xintercept = 0.009, lty = 2) +
-          labs(title = "Per-subject ECDF of Fiedler values: PCC") +
-          theme_classic()
-
-ecdfPFC <- allSummaries %>%
-          mutate(FV_abs = abs(FiedlerVec),
-                 Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
-          filter(y > 0) %>%
-          ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
-          #scale_color_manual(values = c("Yellow", "Red")) +
-          stat_ecdf(alpha = 0.3) +
-          xlim(0,0.05) +
-          labs(title = "Per-subject ECDF of Fiedler values: PFC") +
-          geom_vline(xintercept = 0.009, lty = 2) +
-          theme_classic()
-
-ecdfALL <- allSummaries %>%
-  mutate(FV_abs = abs(FiedlerVec),
-         Community = ifelse(FiedlerBinary == 0, "nonDMN", "DMN")) %>%
-  ggplot(aes(FV_abs, group = interaction(SubjID, Community), color = Community)) +
-  #scale_color_manual(values = c("Yellow", "Red")) +
-  stat_ecdf(alpha = 0.5) +
-  xlim(0,0.05) +
-  labs(title = "Per-subject ECDF of Fiedler values") +
-  geom_vline(xintercept = 0.009, lty = 2) +
-  theme_classic()
-
 ```
@@
 allPropDMN <- sapply(Summaries, "[[", "slidePropDMN")
+
+# put all summaries together for model fit
+allSummaries <- do.call(rbind, Summaries)
+allSummaries$SubjID <- rep(subjList, each = nVertices)
 
@@
 
-Foo <- "fighters"
 ```

### 2019-04-18 graphAnalysis.R
renamed variables, and deleted unnecessary ones from data, manuscript, and graphAnalysis script

@@ -2,7 +2,7 @@
 SubjID <- commandArgs(trailingOnly=TRUE)
 write(paste("Analyzing data for subject", SubjID), stdout())
 
-### Run a graph theoretic fMRI analysis
+### Run a graph theoretic fMRI analysis on the pre-processed time series of an individual
 
 ###------- Libraries and functions ---------------
 write('Loading functions and libraries...', stdout())
@@ -19,11 +19,11 @@ library(lme4)
 library(parallel)
 
 
-## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
-# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
-# Normalization approach suggested in network textbook (equation 7.20)
-# This transformation is approximately normal with mean 0 and sd = sqrt(1 / (n - 3))
+# tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
 fisherTanh <- function(Data = padjMatrix, preThresh = NA){
+  # This takes either a matrix of correlation values (vectors too, but manually compute pvals)
+  # Normalization approach suggested in network textbook (equation 7.20)
+  # This transformation is approximately normal with mean 0 and sd = sqrt(1 / (n - 3))
   
   transformed <- list()
   
@@ -44,7 +44,7 @@ fisherTanh <- function(Data = padjMatrix, preThresh = NA){
       z.vec <- transformed$tanhZ
       n <- length(Data)
     }
-    transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)
+    transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n - 3)), lower.tail = F)
     
     # adjust pvals
     transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")
@@ -65,9 +65,10 @@ fisherTanh <- function(Data = padjMatrix, preThresh = NA){
       dimnames(tempMat) <- list(rownames(Data), rownames(Data))
       transformed$adjustPvals <- tempMat
       
-      # retain only the significant adjusted pval Z scores
-      transformed$tanhZ[transformed$adjustPvals > 0.05] <- 0
     }
+    
+    # retain only the significant adjusted pval Z scores
+    transformed$tanhZ[transformed$adjustPvals > 0.05] <- 0
   }
   
   return(transformed)
[…]

### 2019-04-24 Manuscript.Rmd
new revisions, including switching from DMN to DN, abstract, and intro

@@
 ---
-title: 'Individual heterogeneity in functional topography of the default-mode network in medial prefrontal cortex'
+title: 'Individual heterogeneity in the functional network topography of the medial prefrontal cortex'
 author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
@@
 
-```{r setup, include=FALSE}
+```{r setup, include = FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
@@
 
-```{r Libraries and functions, include = FALSE, fig.align="center", fig.width=6, fig.height=4, echo=FALSE}
+```{r Libraries and functions, include = FALSE, echo = FALSE}
 
@@
 # produce one permutation instance of the meta-analysis (so it can be fed to mclapply for quicker results)
-metaPerm <- function(list1 = studyList_sv, list2 = studyList_dmn, labels = Yeo_labels, perm = 1) {
+metaPerm <- function(list1 = studyList_sv, list2 = studyList_DN, labels = Yeo_labels, perm = 1) {
 
@@
   # combine study lists
-  allStudies <- c(studyList_sv, studyList_dmn)
+  allStudies <- c(studyList_sv, studyList_DN)
 
@@
   tmpSV <- randPerm[seq(length(list1))]
-  tmpDMN <- randPerm[-seq(length(list1))]
+  tmpDN <- randPerm[-seq(length(list1))]
 
@@
                       SV = sapply(labels, function(roi) {length(grep(roi, tmpSV))}),
-                      DMN = sapply(labels, function(roi) {length(grep(roi, tmpDMN))}))
+                      DN = sapply(labels, function(roi) {length(grep(roi, tmpDN))}))
 
@@
     apply(tmpDF[, 2:3], 1, function(data) {
-      prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
+      prop.test(data, c(length(tmpSV), length(tmpDN)))$statistic
     }
@@
 # I wanted to also get the index in case I want to extract specific rows from parcel/vertex coord dframes
-getCoords <- function(Labels = DMN_labels, Coords = labelCoords_parcel, TimeSeries = FALSE){
+getCoords <- function(Labels = DN_labels, Coords = labelCoords_parcel, TimeSeries = FALSE){
 
@@
 
-# Ensure that all spectral communities associated with 7m (i.e. DMN) have the same label value of 1 
+# Ensure that all spectral communities associated with 7m (i.e. DN) have the same label value of 1 
 evenSpectral <- function(Data = slideCommunities[[1]][[7]]) {
@@
 # Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
-HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){
+HCPOut <- function(Data = DNval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){
 
@@
 # Perform pairwise comparisons of clustering outcomes on all subjects
-comparePartitions <- function(Data = dmnval7mCommunities, MOI = "FiedlerBinary", Index = "VI", nSubjects = nSubj, subjNames = subjList) {
+comparePartitions <- function(Data = DNval7mCommunities, MOI = "FiedlerBinary", Index = "VI", nSubjects = nSubj, subjNames = subjList) {
   # This function will compare the community partitions from all subjects and create a 'comparison matrix' for every pairwise combination of subjects
@@
 # This function will select a two-tailed fiedler vector threshold with respect to the stability of the vertex
-# The threshold will be based on proportion DMN given by thresholdRange
+# The threshold will be based on proportion DN given by thresholdRange
 threshFV <- function(Data, thresholdRange = c(0.01, 0.99), nthresh = 50) {
@@
   # get the 2 values with highest reports (this should be stable upper/lower proportions)
-  stableExtremes <- sort(table(Data$slidePropDMN), decreasing = T)[seq(2)]
+  stableExtremes <- sort(table(Data$slidePropDN), decreasing = T)[seq(2)]
   stableExtremes <- sort(as.numeric(names(stableExtremes)))
@@
 
-  # Iterate over the possible FV until DMN affiliations go below 1%
+  # Iterate over the possible FV until DN affiliations go below 1%
   count <- 1
@@
 
-    # get the mean proportion of DMN from remaining vertices based on putative threshold
-    meanProp <- Data %>% filter(FiedlerVec <= thresh[count]) %>% summarize(mean(slidePropDMN))
+    # get the mean proportion of DN from remaining vertices based on putative threshold
+    meanProp <- Data %>% filter(FiedlerVec <= thresh[count]) %>% summarize(mean(slidePropDN))
 
@@
 
-  # Iterate over the possible FV until DMN affiliations go over 99%
+  # Iterate over the possible FV until DN affiliations go over 99%
   count <- 1
@@
 
-    # get the mean proportion of DMN from remaining vertices based on putative threshold
-    meanProp <- Data %>% filter(FiedlerVec > thresh[count]) %>% summarize(mean(slidePropDMN))
+    # get the mean proportion of DN from remaining vertices based on putative threshold
+    meanProp <- Data %>% filter(FiedlerVec > thresh[count]) %>% summarize(mean(slidePropDN))
 
@@
 
-``` {r For HCP data, fig.align="center", echo=FALSE, message = FALSE}
-# this is used to get the number of subjects 
-setwd('./Summary/')
-nSubj <- length(dir())
-```
-
 1.  Department of Psychological and Brain Sciences, Boston University, Boston, USA
@@
 
-  There is extensive topographic overlap between cortical regions associated with the default-mode network (DMN) and regions that exhibit effects of subjective value during decision making.
-The two sets of functional effects involve common regions of medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC).
-At the same time, differences between the two sets of activation patterns are not apparent at the aggregated meta-analytic level, and further individual-level functional subdivisions might be obscured by group averaging.
-Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DMN effects.
-We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to divide mPFC/PCC into distinct cortical communities in individual participants (n = 100 from the Human Connectome Project).
-We labeled the communities "DMN" and "non-DMN" on the basis of their overlap with the meta-analytically identified PCC region.
-The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable over time and across test-retest days using moderate amounts of fMRI data (30 min per day).
-The topography of the identified subdivisions differed across individuals, and the degree of inter-individual variability was greater in mPFC than in PCC.
-Our results will aid future task-based fMRI studies in identifying functionally specific cortical subdivisions, and suggest it would be premature to infer that different task manipulations call upon shared cognitive processes solely because they evoke overlapping activation in mPFC at the group or meta-analytic level.
-
-**Keywords:** brain networks; DMN; individual differences
+  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are implicated in multiple cognitive functions, including subjective valuation processes and processes linked to the default network (DN).
+Our ability to interpret these seemingly co-localized effects is constrained by a limited understanding of the individual-level heterogeneity in mPFC/PCC functional organization.
+Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DN effects relative to valuation.
+We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to partition mPFC and PCC into "DN" and "non-DN" subdivisions in individual participants (n = 100 from the Human Connectome Project).
+The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable across test/retest sessions and varied markedly across individuals, especially in mPFC.
+Our results point toward a new generation of strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions.
+
+**Keywords:** brain networks; DN; individual differences
 
@@
   Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018].
-One such function is subjective valuation during economic decision making [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
-Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued.
-These regions are also implicated in a set of functions associated with the default-mode network (DMN).
-DMN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Greicius2003; @Fox2005; @Yeo2011].
-
-  Coordinate-based meta-analyses of the fMRI literature suggest that valuation and DMN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017].
-The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DMN.
-Within PCC and adjacent precuneus, a more posterior subregion appears DMN-specific, whereas a more anterior subregion is implicated in both effects.
-One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DMN effects.
-The potential existence of common nodes has prompted theories positing overlap between valuation and DMN-related cognitive processes.
-For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Northoff2012; @Clithero2014; @Acikalin2017; @Reddan2018].
-
-  However, concluding that colocalization at the group level equates to overlap in cognitive function requires a better understanding of individual-level heterogeneity in topographic patterns of brain activity.
-A key limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Woo2014; @Michalka2015; @Wang2015; @Tobyne2018], potentially exaggerating the degree of overlap across domains.
-This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a].
+One such function is subjective valuation during economic decision making.
+Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
+These regions are also implicated in a set of functions associated with the default-mode network (DN).
+DN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Greicius2003; @Fox2005; @Yeo2011].
+
+  Coordinate-based meta-analyses of the fMRI literature show that valuation and DN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017].
+The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DN.
+Within PCC and adjacent precuneus, a more posterior subregion appears DN-specific, whereas a more anterior subregion is implicated in both effects.
+One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DN effects.
+The potential existence of common brain nodes has prompted theories positing psychological overlap between valuation and DN-related processes.
+For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Acikalin2017; @Clithero2014; @Northoff2012; @Reddan2018].
+
+  However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity.
+A recognized limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], potentially exaggerating the degree of overlap across domains.
+This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013a].
 An alternative approach is to focus on analyses at the individual-participant level.
-Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Laumann2015; @Gordon2017; @Gratton2018b; @Tobyne2018].
+Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018].
 Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
-Recent work has uncovered fine-grained subdivisions within the DMN through tailored analyses of seed-based functional connectivity [@Braga2017; @Braga2019].
-It is therefore possible that the diffuse overlap of DMN and valuation effects can be attributed to a lack of spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
-An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DMN effects within mPFC and PCC.
+Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019].
+It is therefore possible that the diffuse overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
+An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC.
 
   A useful way to characterize individual-specific brain organization is to examine patterns of resting-state functional connectivity (rsFC; i.e.
-time-series correlations between pairs of locations in the brain).
-Connectome-based analyses of rsFC have been fruitful in characterizing individualized functional topologies that correspond well to task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017; @Smith2009].
-A popular way to analyze these connectomes is to rely on graph theoretic methods, which are properly equiped to understand brain network dynamics [@Bassett2018a].
-In the context of network analysis, community detection algorithms have been successfully used to subdivide brain networks into multiple distinct communities [@Garcia2017].
-Such communities represent clusters of network nodes that share more connections with each other than with the rest of the network [@Fortunato2016].
-In attempting to refine the DMN topography at the individual level, we focus on dividing mPFC and PCC into communities encapsulating what belongs and does not belong to DMN.
-Spectral partitioning (SP) is an efficient community detection algorithm that deterministically forces such bisections [@Fiedler1975; @Belkin2003].
-For a network composed of pairwise correlations among its nodes, SP partitions the network by binarizing the eigenvector linked to the second-to-lowest eigenvalue of the adjusted (Laplacian) correlation matrix according to its sign (i.e.
-positive or negative number).
-SP has recently been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was recently shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
-This method can therefore capture a refined group of brain regions that more cohesively share spontaneously covarying temporal activation patterns during rest.
-
-  In this study, we aimed to subdivide regions commonly attributed to both DMN and subjective valuation into individual-specific DMN and non-DMN communities, quantifying the degree of topographical heterogeneity present in this network within and across individuals.
+BOLD time-series correlations between pairs of locations in the brain).
+Connectome-based analyses of rsFC have been fruitful in characterizing individualized functional topologies that correspond well to task-induced activity [@Gordon2017; @Laumann2015; @Smith2009; @Tobyne2017].
+A functional connectome can be represented in the form of a network, and graph theoretic methods can be applied to analyze the network's structure [@Bassett2017; @Rubinov2010].
+In the context of network analysis, community detection algorithms subdivide brain networks into sets of nodes that share more connections with each other than with the rest of the network [@Fortunato2016; @Garcia2017].
+Here we use the technique of spectral partitioning (SP), an efficient community detection algorithm that deterministically subdivides a network into two communities [@Belkin2003; @Chung1999; @Fiedler1975].
+SP has been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
+We use SP here to identify subsets of nodes within mPFC and PCC that share spontaneously covarying temporal activation patterns during rest.
+
+  In this study, we aimed to subdivide regions commonly attributed to both DN and subjective valuation into individual-specific DN and non-DN communities, and to quantify the degree of topographic heterogeneity present in this network within and across individuals.
 We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks.
-First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DMN and limbic networks along the medial cortical wall [@Yeo2011].
-A cortical surface-based meta-analysis of DMN and SV literatures identified a parcel in PCC that was DMN-specific at the aggregate level.
-We then derived an rsFC network of all the surface vertices within the search space for each of `r nSubj` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DMN and non-DMN communities (defined according to the degree of coverage of the PCC parcel).
-Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographical extent of each community.
-The resulting communities varied topographically across subjects, while also appearing to follow common organizational principles.
+First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks along the medial cortical wall [@Yeo2011].
+A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level.
+We then derived an rsFC network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
+Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographic extent of each community.
+The resulting communities varied topographically across individuals, while also appearing to follow common organizational principles.
 Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC.
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
-Lastly, we provide evidence that the resulting automatically defined communities resembled an organizational scheme recently observed in a series of low N studies [@Braga2017; @Braga2019].
+Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities aligns with a recently proposed scheme for the organization of DN subdivisions.
+[@Braga2017; @Braga2019].
 Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
@@
 [-@Yeo2011].
-First, we selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial surface in HCP's 32,000 surface space (fs_LR_32k).
+First, we selected vertices on the cortical surface that were contained by the DN and limbic networks along the medial surface in HCP's 32,000 surface space (fs_LR_32k).
 Next, we overlaid those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
@@
 
-We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DMN effects.
+We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DN effects.
 For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects for current or prospective rewards [@Bartra2013].
-For DMN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009].
+For DN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009].
 These coordinates represent the areas that exceeded the statistical significance threshold in each original study.
@@
 We permuted the label of every study (i.e.
-DMN or valuation) 5000 times while preserving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains.
+DN or valuation) 5000 times while preserving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains.
 This gave us a null distribution of 5000 maximum chi-squared values.
@@
 
-Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (N = `r nSubj`, randomly sampled from the total pool of 469 available subjects).
+Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (N = `r length(dir(path = './Summary'))`, randomly sampled from the total pool of 469 available subjects).
 Each subject's data was acquired over two days at Washington University in St.
@@
 In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
-Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community as that which contained the DMN-specific PCC parcel identified in our meta-analysis.
+Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the DN-specific PCC parcel identified in our meta-analysis.
 The high density of the graphs ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].
@@
 We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows.
-To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series).
-Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DMN or non-DMN more than 99% of the time.
+To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series).
+Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DN or non-DN more than 99% of the time.
 
@@
 We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity.
-First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average activity across all vertices in PCC for each day separately.
+First, we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average activity across all vertices in PCC for each day separately.
 We compared these seed-based maps with the Fiedler vectors produced by SP by examining three sets of spatial correlations across vertices between days: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps.
@@
 ``` {r Meta-analysis permutation, echo=FALSE, message = FALSE, cache = TRUE}
-# Glasser parcels contained in Yeo's 17-net DMN and limbic networks on the medial cortical wall
+# Glasser parcels contained in Yeo's 17-net DN and limbic networks on the medial cortical wall
 Yeo_labels <- c("L_25_ROI",
@@
 
-setwd('../DMN/')
+setwd('../DN/')
 templist <- dir()
-studyList_dmn <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())
+studyList_DN <- lapply(templist, readr::read_csv, col_names = F, col_types = cols())
 
@@
 nRegions_sv <- do.call(rbind, studyList_sv) %>% count
-nRegions_dmn <- do.call(rbind, studyList_dmn) %>% count
-nRegions_all <- left_join(nRegions_sv, nRegions_dmn, by = "X1")
+nRegions_DN <- do.call(rbind, studyList_DN) %>% count
+nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")
 
@@
                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
-                      DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
+                      DN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_DN))}),
                       propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
-                      propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
+                      propDN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_DN))}) / length(studyList_DN))
 
@@
   tmpDF$Chi_squared <- apply(tmpDF[, 2:3], 1, function(data) {
-    round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
+    round(prop.test(data, c(length(studyList_sv), length(studyList_DN)))$statistic, digits = 2)
     })
@@
 # results!
-# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DMN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.005)
-# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DMN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p = 0.02, R: p < 0.0001)
-# v23ab right (proportion sv = 0.16; proportion DMN = 0.36, chi = 11.51, p = 0.01)
-# v23ab left (proportion sv = 0.16; proportion DMN = 0.32, chi = 8.25, p = 0.06)
+# 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.005)
+# 7m bilateral (prportion sv = L: 0.17, R: 0.15; proportion DN = L: 0.36, R: 0.40, Chi = L: 10.07, R: 18.89, L: p = 0.02, R: p < 0.0001)
+# v23ab right (proportion sv = 0.16; proportion DN = 0.36, chi = 11.51, p = 0.01)
+# v23ab left (proportion sv = 0.16; proportion DN = 0.32, chi = 8.25, p = 0.06)
 # null 95th-q chi <- 8.87 (varies; this was done ith 100 but resembles the 5k one)
@@
 
-We performed a coordinate-based meta-analysis to identify subregions of mPFC and PCC that were preferentially associated with the DMN or SV literatures.
-Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to discrete parcels from a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
-The `r length(Yeo_labels)` parcels considered were limited to the medial portion of the default mode and limbic networks defined by the Yeo et al.'s [-@Yeo2011] 17-network parcellation.
-Unique areas were identified by first permuting the domain labels across studies (DMN or SV) to create a null distribution for the maximum chi-squared statistic in the search space (see Methods for details).
+We performed a coordinate-based meta-analysis to identify subregions of mPFC and PCC that were preferentially associated with the DN or SV literatures.
+Volumetric coordinates from a set of DN and SV studies were projected onto a cortical surface, and mapped to discrete parcels from a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
+The `r length(Yeo_labels)` parcels considered were limited to the medial portion of the default and limbic networks defined by the Yeo et al.'s [-@Yeo2011] 17-network parcellation.
+Unique areas were identified by first permuting the domain labels across studies (DN or SV) to create a null distribution for the maximum chi-squared statistic in the search space (see Methods for details).
 The null distribution was used to identify regions that were reported significantly more often in one literature or the other.
@@
 The 95th percentile of the permuted chi-squared distribution was 8.87.
-Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DMN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.029; Right: observed $\chi^2$ = 18.89, *p* < 0.001).
+Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.029; Right: observed $\chi^2$ = 18.89, *p* < 0.001).
 The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.011; Left: observed $\chi^2$ = 8.25, *p* = 0.067).
 There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.005; Right: observed $\chi^2$ = 12.83, *p* = 0.005); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum.
-No other parcels were preferentially implicated in valuation relative to DMN.
-We therefore selected area 7m as an interpretable, bilateral reference point for labeling DMN and non-DMN communities in the analyses that follow.
-We note that area 7m has been found to not partake in DMN in previous work [@AndrewsHanna2010].
-However, we adhere to the nomenclature established by [@Glasser2016], whose area 7m is positioned considerably more ventrally and is well contained within canonical DMN.
+No other parcels were preferentially implicated in valuation relative to DN.
+We therefore selected area 7m as an interpretable, bilateral reference point for labeling DN and non-DN communities in the analyses that follow.
+We note that area 7m has been found to not partake in DN in previous work [@AndrewsHanna2010].
+However, we adhere to the nomenclature established by [@Glasser2016], whose area 7m is positioned considerably more ventrally and is well contained within canonical DN.
 
@@
 
-With our mPFC/PCC search space, we estimated each individual's DMN coverage using their full time series (approximately 4800 total TRs from four scanning sessions over two days).
+With our mPFC/PCC search space, we estimated each individual's DN coverage using their full time series (approximately 4800 total TRs from four scanning sessions over two days).
 Each subject's network (n = `r nSubj`) was constructed by calculating pairwise correlations among the time series for all the surface vertices in the search space (`r nVertices` total vertices).
-We applied the SP community detection algorithm to thresholded transformations of these networks to identify cohesive functional communities corresponding to DMN and non-DMN areas.
+We applied the SP community detection algorithm to thresholded transformations of these networks to identify cohesive functional communities corresponding to DN and non-DN areas.
 
@@
 Since this is a data-driven approach, there is no a priori labeling for the two communities.
-We thus defined the DMN community as the one containing the one DMN-specific PCC parcel from the meta-analysis (7m).
-In qualitative terms, the resulting patterns contained substantial DMN coverage in posterior PCC (as dictated by our labeling strategy), with non-DMN vertices in anterior PCC.
-The mPFC region tended to include DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them.
-This non-DMN section extended posteriorly into pregenual cinglate cortex (area a24).
+We thus defined the DN community as the one containing the one DN-specific PCC parcel from the meta-analysis (7m).
+In qualitative terms, the resulting patterns contained substantial DN coverage in posterior PCC (as dictated by our labeling strategy), with non-DN vertices in anterior PCC.
+The mPFC region tended to include DN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DN pocket between them.
+This non-DN section extended posteriorly into pregenual cinglate cortex (area a24).
 
@@
 
-# concatenate all proportion of DMN affiliations per node to produce (1) a histogram for fig 4C, and (2) % of node affiliated with either community > 99% over time
-allPropDMN <- sapply(Summaries, "[[", "slidePropDMN")
+# concatenate all proportion of DN affiliations per node to produce (1) a histogram for fig 4C, and (2) % of node affiliated with either community > 99% over time
+allPropDN <- sapply(Summaries, "[[", "slidePropDN")
 
@@
 
-# Do a mixed effects GLM (binomial, quasi unavailable on glmer) to estimate the relationship between Fiedler vec and propDMN
-SC_FVvPDMN_model <- glmer(slidePropDMN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
-SC_FVvPDMN_modelSummary <- summary(SC_FVvPDMN_model)
-allSummaries$FittedVals <- fitted(SC_FVvPDMN_model)
+# Do a mixed effects GLM (binomial, quasi unavailable on glmer) to estimate the relationship between Fiedler vec and propDN
+SC_FVvPDN_model <- glmer(slidePropDN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
+SC_FVvPDN_modelSummary <- summary(SC_FVvPDN_model)
+allSummaries$FittedVals <- fitted(SC_FVvPDN_model)
 
@@
 FiedlerVector <- seq(min(allSummaries$FiedlerVec), max(allSummaries$FiedlerVec), length.out = nVertices)
-formula <- SC_FVvPDMN_modelSummary$coefficients[1,1] + (SC_FVvPDMN_modelSummary$coefficients[2,1] * FiedlerVector)
+formula <- SC_FVvPDN_modelSummary$coefficients[1,1] + (SC_FVvPDN_modelSummary$coefficients[2,1] * FiedlerVector)
 Fitted_Proportion <- exp(formula) / (1 + exp(formula))
-SC_FVvPDMN_fits <- data.frame(FiedlerVector, Fitted_Proportion)
+SC_FVvPDN_fits <- data.frame(FiedlerVector, Fitted_Proportion)
 rm(FiedlerVector, formula, Fitted_Proportion)
@@
 This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
-However, only `r round(mean(allPropDMN < 0.01 | allPropDMN > 0.99), digits = 4) * 100` percent of the nodes across participants belonged to either community over 99% of the time.
+However, only `r round(mean(allPropDN < 0.01 | allPropDN > 0.99), digits = 4) * 100` percent of the nodes across participants belonged to either community over 99% of the time.
 These results suggest that even though there is considerable stability in these partitionings, there is variability left to account for.
@@
 Therefore, we tested whether the magnitude of the eigenvector values was associated with the stability of nodes in time.
-Specifically, we estimated the proportion of DMN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
-The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
+Specifically, we estimated the proportion of DN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
+The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
 We refer to this proportion of affiliations over time as the stability of a given node.
@@
 
-These analyses suggest that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DMN and non-DMN vertices on an individual subject basis.
+These analyses suggest that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DN and non-DN vertices on an individual subject basis.
 We therefore thresholded each subject's Fiedler vector to produce these refined maps.
@@
 The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
-Figure 5 (bottom) shows the spatial average of the thresholded binarized partitions across all participants, denoting the proportion of times a vertex was affiliated with the DMN community.
+Figure 5 (bottom) shows the spatial average of the thresholded binarized partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
 This summary illustrates the common organizational layout of both communities, but also highlights the considerable variability across individuals, especially in mPFC.
@@
 ``` {r Noise Effects: Per-subject Fiedler by R-sqd, fig.align="center", fig.width=3, fig.height=3, fig.cap = "FORMER Figure 13.
-Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DMN time series.", echo=FALSE, message = FALSE, cache = TRUE}
+Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DN time series.", echo=FALSE, message = FALSE, cache = TRUE}
 ## next get the mean tSNR of PCC and mPFC before/after thresholding
@@
 
-We extended the analysis of per-day data by examining whether the organization of the DMN could be extracted using per-run data only.
+We extended the analysis of per-day data by examining whether the organization of the DN could be extracted using per-run data only.
 The duration of each run (approximately 14 mins long) falls below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
-Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DMN organization from only a single run of data.
+Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DN organization from only a single run of data.
 
@@
 temp <- list.files()
-subjList_sess <- sapply(temp, substring, first=1, last=9)
+subjList_sess <- sapply(temp, substring, first = 1, last = 9)
 Summaries_sess <- lapply(temp, read.csv)
@@
 
-The thresholded partitions in our work qualitatively resembled the topographical arrangement of DMN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
+The thresholded partitions in our work qualitatively resembled the topographical arrangement of DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
 We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
@@
 
-Visual inspection of these networks shows a remarkable similarity between our DMN and non-DMN communities and the previously reported sub-networks A and B.
+Visual inspection of these networks shows a remarkable similarity between our DN and non-DN communities and the previously reported sub-networks A and B.
 Since our search space did not contain areas TPJ and PHC, lack of signal from these areas could drive the small discrepancies in the topography between our work and theirs (particularly for network A).
-Nevertheless, these qualitative similarities are important, as they collectively suggest that canonical DMN regions consist of two distinct communities.
+Nevertheless, these qualitative similarities are important, as they collectively suggest that canonical DN regions consist of two distinct communities.
 Results from the present investigation suggest that the topographic organization of the communities is variable across a large sample of participants, especially in mPFC, and that the SP algorithm is a useful and reliable tool for identifying the two communities in individuals.
@@
 A considerable amount of meta-analytic work has been dedicated to pinpointing the spatial embedding of behavioral constructs in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across psychological phenomena [@DelaVega2016; @Kragel2018; @Hiser2018].
-In particular, the effects elicited by the subjective value (SV) of an option and the default mode network (DMN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
+In particular, the effects elicited by the subjective value (SV) of an option and the default network (DN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
 However, recent studies have shown considerable variability of the brain's functional topography across individuals, emphasizing the importance of capturing its organization at the individual subject level, and pointing to limitations in aggregative estimations [@Braga2017; @Gordon2017; @Gratton2018b; @Kong2018; @Laumann2015; @Tobyne2018].
@@
 
-Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to subdivide areas of overlap into DMN and non-DMN in 100 individuals from the Human Connectome Project.
+Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to subdivide areas of overlap into DN and non-DN in 100 individuals from the Human Connectome Project.
 Our results show that the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects.
@@
 Also, to the best of our knowledge we are the first to quantify the organizational heterogeneity of these areas in the human brain.
-- We are also not the first to show functional subdivision of DMN [@Kernbach2018] (but that's using group averages on parcellated data), or this particular individualized pattern of subdivision (braga).
+- We are also not the first to show functional subdivision of DN [@Kernbach2018] (but that's using group averages on parcellated data), or this particular individualized pattern of subdivision (braga).
 Our results are complementary in the sense that we show similar outcomes in 100 subjects.
@@
 - Similarity with B&B: One way in which our results are at odds with those from Braga and Buckner is the functional labeling of these sub-networks.
-Based on our criteria, network B would more closely identify with DMN (per 7m affiliation), while we currently do not have enough evidence to label network A.
+Based on our criteria, network B would more closely identify with DN (per 7m affiliation), while we currently do not have enough evidence to label network A.
 These discrepancies should be addressed with explicit behavioral manipulations in the future.
@@
   - other algorithms (benefit of SP is that it's deterministic, allows for diagnostics, and discourages extremely large/small communities)
-  - bipartition: we focus on that since we tried to capture what belongs to DMN and non-DMN.
+  - bipartition: we focus on that since we tried to capture what belongs to DN and non-DN.
 This intuition can be generalized to other behaviors.
@@
 This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future.
-Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DMN and SV'.
-It is worth noting that the SV-only area from the meta-analysis tends to land in non-DMN, although it ends up in no-ones land when thresholding the maps.
+Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DN and SV'.
+It is worth noting that the SV-only area from the meta-analysis tends to land in non-DN, although it ends up in no-ones land when thresholding the maps.
 
@@
 While this suggests that we should see fluctuations in affiliation, and not stability, Vidaurre's work establishes the dynamics of prevalent function among networks, and not their topologies.
-Our work focuses on the topographical arrangement of the DMN network, which can be active or not while maintaining its form.
+Our work focuses on the topographical arrangement of the DN network, which can be active or not while maintaining its form.
 So, the two works are compatible.
@@
 1), out.width = "50%", fig.align = "center", fig.cap= "A: Proportion of times each ROI was reported in each literature.
-B: common and unique brain regions associated with DMN and subjective value.
-DMN regions defined by Yeo et al.
-(2011) in blue, which encompass areas of considerable overlap between DMN and SV.
+B: common and unique brain regions associated with DN and subjective value.
+DN regions defined by Yeo et al.
+(2011) in blue, which encompass areas of considerable overlap between DN and SV.
 Literature-specific regions (bilateral 7m and right v23 in yellow, and bilateral 25 in red) were identified from a permutation analysis of chi-squared tests comparing these literatures."}
@@
 Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
-The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m, bordered)."}
+The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
+# if you want to rescale the range of values, use scales::rescale(vecot, c(min, max))
 include_graphics("./Images/FB_FV_example.png")
@@
 
-``` {r Stability per subject: Fiedler vector vs prop.
-DMN plot (Fig 5), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each subject, we produced partitions for each 20 minute sliding window (1 min shift, ~84 TRs) throughout their full time series (median number of windows = 37).
-B: Proportion of times each vertex was affiliated with the DMN community across windows (up), and the continuous Fiedler vector map for the current subject using their full time series (down).
+``` {r Variability per subject: Fiedler vector vs prop.
+DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each subject, we produced partitions for each 20 minute sliding window (1 min shift, ~84 TRs) throughout their full time series (median number of windows = 37).
+B: Proportion of times each vertex was affiliated with the DN community across windows (up), and the continuous Fiedler vector map for the current subject using their full time series (down).
 The maps share considerable qualitative similarities in their gradients along the cortical surface.
-C: Relationship between the magnitude of Fiedler vector values and the proportion of DMN affiliations.
+C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations.
 Grey lines display each subject's association, while the black line shows the fit from a mixed-effects logistic regression.
@@
 # 
-# # Fiedler Vector x proportion of times a vertex was affiliated with DMN
-# SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
-#   geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
-#   geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 2) +
+# # Fiedler Vector x proportion of times a vertex was affiliated with DN
+# SC_FVvPDN_plot <- ggplot(data = allSummaries) +
+#   geom_smooth(aes(FiedlerVec, slidePropDN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
+#   geom_line(data = SC_FVvPDN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 2) +
 #   geom_vline(xintercept = c(-0.014, 0.013), linetype = "dashed", color = Cols[2]) +
-#   labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
+#   labs(x = "Fiedler Vector Values", y = "Proportion of DN Affiliations") +
 #   scale_y_continuous(limits = c(0,1)) +
@@
 # 
-# SC_FVvPDMN_plot
+# SC_FVvPDN_plot
 #
 # # histogram on 4 C
-# hist(allPropDMN)
+# hist(allPropDN)
 
@@
 
-```{r Thresholded maps (Fig 7), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
+```{r Thresholded maps (Fig 5), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
 Values that did not meet the threshold were set to zero on the Fiedler vector, and 0.5 on the binarized maps (giving rise to a third community of high-variability vertices).
-B: Spatial mean of the binarized maps across all participants, indicating the proportion of DMN affiliations per vertex in our sample.
-This aggregate map shows the common organizational principle of the DMN and non-DMN communities, while also pinpointing the relatively high level of variability in mPFC."}
+B: Spatial mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample.
+This aggregate map shows the common organizational principle of the DN and non-DN communities, while also pinpointing the relatively high level of variability in mPFC."}
 
@@
 ``` {r Partition comparison: halves and runs (Fig.
-8), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 days of scans each), showing pattern agreement across days and subjects for PCC and mPFC separately.
+6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 days of scans each), showing pattern agreement across days and subjects for PCC and mPFC separately.
 Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncrasies in community arrangement for both PCC and mPFC (ratios > 1, solid line), with higher subject-specificity in the latter.
@@
 ``` {r Correlation vs community detection (Fig.
-14), fig.align="center", fig.cap = "A: Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector for 10 example subjects.
+7), fig.align="center", fig.cap = "A: Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector for 10 example subjects.
 The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.
@@
 
-```{r BandB comparison (Figure 16), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga and Buckner's (2019) criterion, and those produced by spectral partitioning.
+```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga and Buckner's (2019) criterion, and those produced by spectral partitioning.
 Networks A and B were produced by selecting seeds in diagnostic TPJ, DLPFC and PHC.
-In each case, our DMN and non-DMN networks map well to their proposed functional organization, albeit with some discrepancies on network A/non-DMN."}
+In each case, our DN and non-DN networks map well to their proposed functional organization, albeit with some discrepancies on network A/non-DN."}
 

### 2019-04-24 Manuscript.Rmd
halfway through the methods

@@
 [-@Yeo2011].
-First, we selected vertices on the cortical surface that were contained by the DN and limbic networks along the medial surface in HCP's 32,000 surface space (fs_LR_32k).
+First, we selected vertices on the medial cortical surface that were contained by the DN and limbic networks in HCP's 32,000 surface space (fs_LR_32k).
 Next, we overlaid those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
 This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1).
-The search space was naturally divided into two spatially discontinuous clusters that covered PCC and mPFC, facilitating the study of each general region separately.
+The search space was naturally divided into two spatially non-contiguous clusters that covered PCC and mPFC, facilitating the examination of each general region separately.
 
@@
 We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DN effects.
-For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects for current or prospective rewards [@Bartra2013].
-For DN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009].
+For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects in contrasts of high-versus-low-value outcomes or prospects [@Bartra2013].
+For DN, we acquired coordinates from 80 studies that were related to task-deactivation [@Laird2009].
 These coordinates represent the areas that exceeded the statistical significance threshold in each original study.
@@
 The indicator map for each study was then projected to a standard cortical mesh (fsaverage, 160,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/).
-**TODO: The Glasser et al.
-(2016) parcellation was resampled to fsaverage to pair spheres to parcels from our search space**.
-Any sphere sections that overlapped with the cortex (no lower limit restrictions) were mapped to the corresponding parcel, and we tallied how many studies had positive indicator values in each parcel.
+We then resampled the Glasser et al.
+(2016) parcellation to fsaverage, and tallied how many studies had positive indicator values intersecting with each cortical parcel (the details of the resampling procedure are described in https://wiki.humanconnectome.org/display/PublicData/HCP+Users+FAQ#HCPUsersFAQ-9.HowdoImapdatabetweenFreeSurferandHCP, and were implemented using a custom script https://github.com/stobyne/Spherical-Surface-Swapper).
 Two studies from the subjective valuation corpus were removed because they did not contain cortical voxels, leaving a final number of 198 studies.
 
-With these lists, we tested for parcels that were significantly more strongly associated with one domain than the other with a chi-squared test.
-We permuted the label of every study (i.e.
-DN or valuation) 5000 times while preserving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from per-parel chi-squared tests comparing the proportion of studies with activation in that parcel in the two domains.
+To test for parcels that were significantly more strongly associated with one domain than the other, we performed per-parcel chi-squared tests comparing the proportion of studies with activation in that parcel between the two domains.
+We permuted the study domain labels (i.e.
+DN or valuation) 5000 times while preserving the total number of studies in each domain, and on each iteration stored the maximum resulting chi-squared statistic (across all parcels).
 This gave us a null distribution of 5000 maximum chi-squared values.
@@
 
-Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, high-pass filtering (0.0005 Hz threshold), MNI152-based normalization, surface reconstruction, and mapping of functional data to the surface (details can be found on Glasset et al., 2013).
+Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, high-pass filtering (0.0005 Hz threshold), MNI152-based normalization, surface reconstruction, and mapping of functional data to the a standardized cortical surface model (details can be found on Glasser et al., 2013).
 In addition, data underwent temporal denoising based on independent components [FIX; @Griffanti2014; @Salimi-Khorshidi2014].
 Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017].
-Steps included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising via grayordinate signal regression [@Burgess2016] and censoring of high-motion timepoints by deletion.
+Steps included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising via mean grayordinate signal regression [@Burgess2016] and censoring of high-motion timepoints by deletion.
 Finally, data acquired on the same day (i.e.
@@
 
-All network analyses were performed using the igraph package [@G.2006; https://igraph.org/r/] in R [v.
-3.4.1; @RTeam2018; https://www.r-project.org/].
+All network analyses were performed using the igraph package [v.
+1.1.2; @G.2006; https://igraph.org/r/] in R [v.
+3.4.1; https://www.r-project.org/; @RTeam2018].
 To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices.
@@
 The proportion of remaining edges (i.e.
-network density) was high for all individuals (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`), which were mostly composed of positive correlations (positive: mean = `r mPos`, sd = `r sdPos`; negative: mean = `r mNeg`, sd = `r sdNeg`).
-Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
-Values of 1 of this transformed distribution were reset to 0 in order to avoid the inclusion of these edges in the network analyses.
-We generated and analyzed network weight matrices at four levels: (1) for each run separately (1200 TRs each); (2) for the concatenated time series for the two runs on each day (2400 TRs total); (3) for each subject's full dataset (4800 TRs total); and (4) on each step of a sliding window analysis (see Partition Evaluation for more details).
+network density) was high for all individuals (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`), and the retained edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, sd = `r sdPos`).
+Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution within the set of retained edges.
+Non-retained edges were reset to 0 to exclude them from the network analyses.
+We generated and analyzed network weight matrices at four levels: (1) for each subject's full dataset (4800 TRs total); (2) on each step of a sliding window analysis (see Partition Evaluation for more details); (3) for the concatenated time series for the two runs on each day (2400 TRs total); and (4) for each run separately (1200 TRs each).
 

### 2019-04-25 graphAnalysis.R
update bib file and continue fixing graphAnalysis

@@ -85,18 +85,14 @@ getCoords <- function(Labels = DMN_labels, Coords = labelCoords_parcel, TimeSeri
   indx <- numeric()
   
   # If you want to select time series from raw data
-  if (TimeSeries == TRUE) {
-    
+  if (TimeSeries) {
     for (ROI in Labels) {
       indx <- c(indx, grep(ROI, rownames(Coords)))
     }
-    
   } else { # for the summary output of the community detection output
-    
     for (ROI in Labels) {
       indx <- c(indx, grep(ROI, Coords$Label))
     }
-    
   }
   
   results <- list()
@@ -311,13 +307,13 @@ slidingWindow <- function(subjTS = NA, mins = 15, jump = 1) {
   
   # Window sizing (length)
   # Think about incorporating custom TRs
-  TS <- dim(subjTS)[2] # time series for the subject
-  WS <- seq(834 * (mins/10)) # window from the first TR up to 834 (~10 mins) times the desired multiplier
+  TS <- ncol(subjTS) # time series for the subject
+  WS <- seq(834 * (mins / 10)) # window from the first TR up to 834 (~10 mins) times the desired multiplier
   jump <- 84 * jump # 84 ~ 1 min, times the number of mins that the window moves
   nJumps <- floor((TS - length(WS)) / jump) # number of jumps to be performed, based on the selected parameters
   
   ##------- using lapply
-  winData <- mclapply(seq(nJumps), function(x) subjTS[, WS + (jump * (x - 1))])
+  winData <- mclapply(seq(nJumps), function(x) {subjTS[, WS + (jump * (x - 1))]})
   commTS <- mclapply(winData, communityDetection, ROIS = "None", modularity = F, extras = F)
   
   return(commTS)
@@ -339,6 +335,9 @@ slideCompare <- function(subjData = slideCommunities[[1]], template = NA, func =
   # 
   #   comm: The subject data might contain modularity and spectral partitions. Choose which to use.
   
+  # alternative way:
+  tempComparison <- sapply(subjData, function(data) {arandi(data$FiedlerBinary, template$FiedlerBinary, adjust = T)})
+  
   # For storing RIs or VIs
   tempComparison <- numeric()
   
@@ -346,8 +345,8 @@ slideCompare <- function(subjData = slideCommunities[[1]], template = NA, func =
   nJumps <- length(subjData)
   
[…]

### 2019-04-25 Manuscript.Rmd
methods revision ready

@@
 All network analyses were performed using the igraph package [v.
-1.1.2; @G.2006; https://igraph.org/r/] in R [v.
+1.1.2; https://igraph.org/r/; @G.2006] in R [v.
 3.4.1; https://www.r-project.org/; @RTeam2018].
@@
 Communities (i.e.
-clusters) were identified using the SP algorithm [@Fiedler1975; @Chung1999; @Belkin2003].
+clusters) were identified using the SP algorithm [@Belkin2003; @Chung1999; @Fiedler1975; @Higham2007].
 First, each network was represented as an $n$ x $n$ network weight matrix $W$ as described above (where $n$ equals the number of vertices in the search space, 4,801).
@@
 
-Where $I$ is an identity matrix of size $n$, $D$ is a diagonal matrix containing the strength of each vertex (i.e.
-the sum of its Fisher transformed correlation values with every other vertex), and $W$ is the Fisher transformed network weight matrix.
-This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal.
+Where $I$ is an identity matrix of size $n$, and $D$ is a diagonal matrix containing the strength of each vertex (i.e.
+the sum of its edge weights with all other vertices).
+This resulted in a matrix wherein each entry was the negative normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal.
 The transformation ensures that every row sums to zero.
@@
 This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975].
-This method partitions the network into two similarly-sized communities, and guarantees that they share at least one edge [@Chung1999].
+This method partitions the network into two similarly-sized communities.
 In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
@@
 
-In order to evaluate the validity of the resulting partitionings across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al.
+In order to evaluate the validity of the resulting partitionings across community-detection methods, we also estimated network communities using the more traditional approach of modularity maximization [@Garcia2017], based on the algorithm from Clauset et al.
 [-@Clauset2004].
 This method compares the strength of the connection between any two vertices to their probability of being randomly connected to any other vertex in the network.
-The method heuristically iterates through many possible combinations of vertices, and selects the partitioning that maximizes the network's so-called modularity.
+The method heuristically iterates through many possible combinations of vertices, and selects the partitioning that maximizes the within-community edge weights, relative to a random network containing the same number of edges.
 Unlike SP, modularity can fractionate a network into more than two communities.
-Agreement between the partitions provided by the bounded and unbounded community detection methods would indicate confidence in the partitions.
+Agreement between the partitions provided by the bounded and unbounded community detection methods would suggest the results are not distorted by the restriction of SP to binary partitionings..
 
@@
 
-where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number of nodes grouped together (separately) in one partition, but separately (together) in the other.
-Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $(n\times (n - 1))/2$).
-The resulting ratio is adjusted by comparing it to a baseline given by the expectation of a random node assignment across partitions.
+where $a$ is the number of pairs of nodes that were grouped together in both partitionings, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number of nodes grouped together (separately) in one partitioning, but separately (together) in the other.
+Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $n(n - 1)/2$).
+The resulting ratio is adjusted against a baseline given by the expectation assuming independent partitionings.
 The index ranges from 0 to 1, where 0 denotes the value expected by chance.
-This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below 50%).
-In short, the ARI determines the chance-corrected percentage of agreement between any two partitions while being agnostic to the labeling scheme.
+This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below the chance level).
+In short, the ARI determines the chance-corrected agreement between any two partitions while being agnostic to the labeling scheme.
 
 We performed a number of comparisons among partitions.
-First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns.
-Modularity and SP have been previously found to show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018].
-Alignment between the two algorithms would therefore give us confidence in the validity of the resulting partitionings.
-Next, we compared the partitionings derived from each individual's full time series across subjects, and calculated the mean pairwise ARI for the group.
+First, we computed the degree of agreement between SP and modularity per subject.
+SP and Modularity have been previously found to show underfitting and overfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings.
+Next, we compared the subject-level SP partitionings across individuals, and calculated the mean pairwise ARI for the group.
 We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects.
-Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all subsequent analyses on PCC and mPFC separately.
-
-To estimate the degree of stability of these partitions per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partition against the partition derived from the whole subject's data.
+Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a].
+
+To estimate the degree of stability of partitionings per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partitioning against the partitioning derived from the whole subject's data.
 A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017].
@@
 Ratios close to one denoted similar within-participant and across-participant alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-participant than across participants.
-We then extended this idea by computing the overall agreement across individual runs (4 per subject).
+We then extended this idea by computing the agreement across individual runs (4 per subject).
 Similar to the day-based analysis, we assessed whether run-level data showed higher agreement within-subject than between subjects.
@@
 The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018b]).
-We therefore compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).
+We therefore compared the within-subject correlation coefficients produced by each method through a paired permutation analysis.
+For each of the 100 individuals, we computed the difference in inter-day correlations between methods, randomly alternated the sign of these values 5000 times, and computed the mean of these differences on each iteration.
+The empirical difference in means was then evaluated against this permuted distribution.
 
@@
 # Compare correlation with community approach on mPFC
-# tempComm_PFC_halves <- lapply(seq_along(tempComm_PFC_halves), function(x) cbind(tempComm_PFC_halves[[x]], Correlation_halves[[x]]))
-# tempComm <- sapply(seq(1, 20, by = 2), function(x) cor(tempComm_PFC_halves[[x]]$FiedlerVec, tempComm_PFC_halves[[x+1]]$FiedlerVec))
-# tempCor <- sapply(seq(1, 20, by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
-# prepostComp <- data.frame(Community = tempComm, Correlation = tempCor)
-# prepostComp <- melt(prepostComp)
-# colnames(prepostComp) <- c("Approach", "Correlation")
-# prepostComp_test <- permute(tempComm, tempCor, paired = T)
-# 
-# 
-# ## Between halves analysis for correlation and communities (mPFC only)
-# D1 <- tempComm_PFC_halves
-# D2 <- lapply(tempComm_PFC_halves, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
-# Data <- c(D1,D2)
-# allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = length(Data), Index = "Cor", subjNames = c(subjList_halves, subjList_halves))
-#
-
-# Compare correlation with community approach on mPFC
 tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
@@
   - Small search space: working at the vertex-level makes it computationally difficult to produce estimates at the whole-brain level.
+
+- Joe:
+  - something to potentially discuss later in the paper: for this to be maximally useful in the future, it would help if a general threshold can be
+    identified (without having to do the windowed analysis on every subject). Looking at the amount variability in the per-subject thresholds might give us 
+    a sense of whether that's possible.
 

### 2019-04-26 Manuscript.Rmd
up to corr vs comm result revisions

@@
 
-We performed a coordinate-based meta-analysis to identify subregions of mPFC and PCC that were preferentially associated with the DN or SV literatures.
-Volumetric coordinates from a set of DN and SV studies were projected onto a cortical surface, and mapped to discrete parcels from a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
+We performed a coordinate-based meta-analysis to identify cortical surface parcels within mPFC and PCC that were preferentially associated with the DN or valuation literature.
+Volumetric coordinates from 80 studies with task deactivation contrasts and 198 studies with valuation contrasts were projected onto a cortical surface, and mapped to discrete parcels from a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
 The `r length(Yeo_labels)` parcels considered were limited to the medial portion of the default and limbic networks defined by the Yeo et al.'s [-@Yeo2011] 17-network parcellation.
-Unique areas were identified by first permuting the domain labels across studies (DN or SV) to create a null distribution for the maximum chi-squared statistic in the search space (see Methods for details).
+Domain-specificity was tested by first permuting the domain labels across studies (DN or valuation) to create a null distribution for the maximum chi-squared statistic in the search space (see Methods for details).
 The null distribution was used to identify regions that were reported significantly more often in one literature or the other.
 
-Figure 1 shows the proportion of times every parcel was reported in each literature, as well as the significant differences between domains.
+Figure 1 shows the proportion of times each parcel was reported for each domain, as well as the significant differences between domains.
 The 95th percentile of the permuted chi-squared distribution was 8.87.
-Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential affiliation to DN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.029; Right: observed $\chi^2$ = 18.89, *p* < 0.001).
+Based on this threshold, area 7m in PCC/precuneus was the only parcel to show a preferential association with the DN bilaterally (Left: observed $\chi^2$ = 10.07, *p* = 0.029; Right: observed $\chi^2$ = 18.89, *p* < 0.001).
 The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.011; Left: observed $\chi^2$ = 8.25, *p* = 0.067).
@@
 We therefore selected area 7m as an interpretable, bilateral reference point for labeling DN and non-DN communities in the analyses that follow.
-We note that area 7m has been found to not partake in DN in previous work [@AndrewsHanna2010].
-However, we adhere to the nomenclature established by [@Glasser2016], whose area 7m is positioned considerably more ventrally and is well contained within canonical DN.
-
-### *Partition Comparison: Full Datasets*
+We note that the area labeled 7m in the parcellation used here [@Glasser2016] is different from (and located inferiorly on the medial surface to) the non-DN area 7m discussed in previous work [@AndrewsHanna2010].
+
+### *Individual-level DN and non-DN communities*
 
@@
 
-With our mPFC/PCC search space, we estimated each individual's DN coverage using their full time series (approximately 4800 total TRs from four scanning sessions over two days).
-Each subject's network (n = `r nSubj`) was constructed by calculating pairwise correlations among the time series for all the surface vertices in the search space (`r nVertices` total vertices).
-We applied the SP community detection algorithm to thresholded transformations of these networks to identify cohesive functional communities corresponding to DN and non-DN areas.
-
-Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented on Supplemental Figure 1).
+Within the mPFC/PCC search space, we estimated the topography of the DN for each individual.
+Using each individual's full time series (approximately 4800 total TRs from four 14-min scanning runs acquired over two days), we calculated the full vertex-to-vertex correlation matrix for the `r nVertices` surface vertices in the search space.
+We represented each individual's correlation matrix in the form of a network, with cortical surface vertices as nodes and thresholded/transformed correlation values as edge weights.
+We then applied the SP community detection algorithm to partition the network into two cohesive functional communities.
+
+Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented in Supplemental Figure 1).
 The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods).
 Since this is a data-driven approach, there is no a priori labeling for the two communities.
-We thus defined the DN community as the one containing the one DN-specific PCC parcel from the meta-analysis (7m).
+We assigned the DN label to the community that contained the DN-specific PCC parcel from the meta-analysis (7m).
+We oriented each individual's Fiedler vector to make sure positive values corresponded to the DN community, and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN).
 In qualitative terms, the resulting patterns contained substantial DN coverage in posterior PCC (as dictated by our labeling strategy), with non-DN vertices in anterior PCC.
@@
 
-Before evaluating the degree of generazibility of this topographic pattern across individuals, we examined the validity of these partitionings by comparing them to results from an alterntive community detection algorithm, modularity maximization [@Clauset2004].
-Modularity seeks to find the set of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model.
-Since modularity is not bound to a desired number of communities, it was capable of finding more than two in our data set.
-We quantified the cross-method agreement in terms of the Adjusted Rand Index (ARI; see methods), which measures the proportion of node pairs of nodes in a network that were either clustered together or separately in both partitionings, while being agnostic to labeling schemes and controlling for chance clustering.
+Before evaluating the degree of generazibility of this topographic pattern across individuals, we examined the validity of the partitionings by comparing them to results from an alternative community detection algorithm, modularity maximization [@Clauset2004].
+Modularity seeks to find the set of communities that maximizes within-community connection weights relative to a null model.
+Since modularity is not constrained to a predetermined number of communities, it was capable of finding more than two in our data set.
+We quantified the cross-method agreement in terms of the Adjusted Rand Index (ARI; see Methods), which measures the proportion of node pairs in a network that were either clustered together or separately in both partitionings, while being agnostic to labeling schemes and controlling for chance clustering.
+The ARI takes values ranging from 0 to 1, with 0 indicating chance agreement.
 
@@
 Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-# To get the rate of stability per vertex across subjects
-FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
-FV <- do.call(cbind, lapply(Summaries, "[[", "FiedlerVec"))
-FBS <- rowMeans(FB)
-FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]
-
-# Now let's test something: 
-# Traditionally, a vertex-wise test would be carried across subjects.
-# If these traditional analyses miss out on these idiosyncrasies, you should get unsignificant results.
-# So we did a prop.test per vertex, and corrected with FDR to mimic this situation.
-All_proptests <- apply(FB, 1, function(x) {prop.test(sum(x), nSubj)})
-Prop_pvals_corrected <- p.adjust(sapply(All_proptests, "[[", "p.value"), method = "BY")
-Prop_pvals_corrected <- ifelse(Prop_pvals_corrected < 0.05, 1, 0)
-Chisquares <- sapply(All_proptests, "[[", "statistic")
-
-# And a t-test on the FV vals
-All_ttests <- apply(FV, 1, t.test)
-Ttest_pvals_corrected <- p.adjust(sapply(All_ttests, "[[", "p.value"), method = "BY")
-Ttest_pvals_corrected <- ifelse(Ttest_pvals_corrected < 0.05, 1, 0)
-Tstats <- sapply(All_ttests, "[[", "statistic")
-
-```
-
-This comparison showed that both clustering methods were in high agreement across subjects (mean ARI = `r round(mean(RI_all_within$Index), digits = 2)`, SD = `r round(sd(RI_all_within$Index), digits = 2)`).
+mPFCvs0_wilcox <- wilcox.test(testPFC) # is the mPFC agreement above chance?
+mPFCvs0_ES <- DescTools::CohenD(testPFC)
+
+```
+
+The two clustering methods had high agreement (mean ARI = `r round(mean(RI_all_within$Index), digits = 2)`, SD = `r round(sd(RI_all_within$Index), digits = 2)`).
 Modularity showed a tendency to produce additional communities (median = `r median(nModularity)`, range = `r range(nModularity)`).
-However, these communities encompassed a small number of vertices (median = `r median(modularityCounts_extra)`, IQR = `r quantile(modularityCounts_extra, 0.25)` - `r quantile(modularityCounts_extra, 0.75)`) compared to the principal two (median = `r median(modularityCounts_two)`, IQR = `r quantile(modularityCounts_two, 0.25)` - `r quantile(modularityCounts_two, 0.75)`, suggesting that the overall network is composed of two main communities.
-
-Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+However, the additional communities encompassed a small number of vertices (median = `r median(modularityCounts_extra)`, IQR = `r quantile(modularityCounts_extra, 0.25)` - `r quantile(modularityCounts_extra, 0.75)`) compared to the principal two (median = `r median(modularityCounts_two)`, IQR = `r quantile(modularityCounts_two, 0.25)` - `r quantile(modularityCounts_two, 0.75)`), suggesting that a binary partitioning could provide a reasonable approximation of the network's true community structure.
+
+Next, we examined the similarity of partitionings across individuals by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
 Qualitative inspection of the community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects.
 To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3).
-Indeed, this analysis showed that the functional topography of PCC was better maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`)(paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+The functional topography of PCC was better maintained across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), but the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, V = `r mPFCvs0_wilcox$statistic`, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).
 
@@
 allPropDN <- sapply(Summaries, "[[", "slidePropDN")
+
+# proportion of fully stable nodes per individual
+prcntStable <- apply(allPropDN, 2, function(subj) {round(mean(subj %in% c(0, 1)), digits = 2)}) * 100
 
@@
 
-# Overall
-SC_all <- do.call(rbind, SC)
-SC_plot <- ggplot(data = SC_all)
-SC_plot <- SC_plot + geom_line(aes(x = Window, y = Index, group = as.factor(SubjID)), color = "slategray4",alpha = 0.3, show.legend = F) +
-              geom_smooth(aes(x = Window, y = Index), color = Cols[2], fill = Cols[2]) +
-              ylim(0,1) + 
-              theme(text = element_text(size=35)) +
-              labs(y = "ARI") +
-              theme_classic()
-
-# Mean RI across windows per subject
-SC_summary <- aggregate(SC_all$Index, by = list(SC_all$SubjID), FUN = mean)
-SC_summary$SD <- aggregate(SC_all$Index, by = list(SC_all$SubjID), FUN = sd)$x
-colnames(SC_summary) <- list("SubjID", "RI", "SD")
-SC_sd_plot <- ggplot(data = SC_summary, aes(x=SD)) + 
-  geom_density(color = "black", fill = Cols[2]) + 
-  xlim(0,1) +
-  labs(x = "SD") +
-  theme(text = element_text(size=35)) +
-  theme_classic()
-
-```
-
-In order to estimate the stability of these partitions over time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min); comparing the partitioning derived from each windowed time series with the partitioning computed using the entire time series (Figure 4).
+```
+
+We next sought to identify a set of temporally stable core nodes in each community.
+In order to estimate the stability of partitions over time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min).
+We compared the partitioning derived from each window with the partitioning computed using the entire time series (Figure 4).
 
@@
 
-This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
-However, only `r round(mean(allPropDN < 0.01 | allPropDN > 0.99), digits = 4) * 100` percent of the nodes across participants belonged to either community over 99% of the time.
-These results suggest that even though there is considerable stability in these partitionings, there is variability left to account for.
-**TBD from Sean: I think this point deserves some additional analysis, or discussion.
-My bet is that this comes down to signal noise  and its interaction with the SP algorithm, but it would be very helpful to show this somehow.
-Stability is key for the impact of this paper and this paragraph, as it is currently written, suggests to me that the vertex-level stability it not as stable as I might want it to be**
-
+The mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+A subset of nodes showed exceptionally high stability, in that they were assigned to the same community in every time window.
+The percentage of stable nodes ranged from 0 to `r max(prcntStable)`% across individuals (median = `r median(prcntStable)`%, IQR = `r quantile(prcntStable, 0.25)`% - `r quantile(prcntStable, 0.75)`%).
+
+We next tested whether the continuous-valued Fiedler vector (before binarization into discrete communities) carried information about the stability of individual nodes.
 There is precedent in the literature for the idea that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
@@
 Specifically, we estimated the proportion of DN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
-The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
-We refer to this proportion of affiliations over time as the stability of a given node.
+The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), signifying that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
 
@@
 
-rm(tempList)
-
-```
-
-These analyses suggest that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DN and non-DN vertices on an individual subject basis.
-We therefore thresholded each subject's Fiedler vector to produce these refined maps.
-For each individual, we estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
-Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
-Sub-threshold vertices were set to zero in Fiedler vector maps and 0.5 in the binarized maps so that they would not bias the calculation of averages.
-Figure 5 shows the thresholded partitioning for the same individual shown in Figure 2.
-The maps used in all subsequent analyses were thresholded by this individualized criterion.
-
-### *Partition Comparison: Thresholded Full Datasets*
-``` {r Partition comparison: all thresholded, echo=FALSE, message = FALSE, cache = TRUE}
 # Apply threshold to Summaries
 # IMPORTANT: THIS PROCESS OVERWRITES THE VARIABLES FROM THE FIRST COMPARISON SECTION
-# THIS IS DONE FOR STORAGE-SAKE, BUT IT MIGHT BE WORTH GIVING THESE TEIR OWN NAME
+# THIS IS DONE FOR STORAGE-SAKE
 if (threshMaps) {
@@
 # percent of stable nodes per subject
-prcntStable <- sapply(Summaries, function(data) {mean(data$FiedlerBinary != 0.5)})
-
+# this can be different from prcntStable because fully stable vertices can technically have low FV values
+# the match between FV and Stability is strong, but not perfect
+prcntSurvived <- sapply(Summaries, function(data) {mean(data$FiedlerBinary != 0.5)})
+
+rm(tempList)
+
+```
+
+These analyses suggest that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DN and non-DN vertices on an individual subject basis.
+We therefore thresholded each subject's Fiedler vector to produce these refined maps.
+For each individual, we estimated the threshold by selecting the smallest absolute Fiedler vector value that yielded an average stability of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
+Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
+The median proportion of retained vertices per individual was `r round(median(prcntSurvived), digits = 2)` (IQR = `r round(quantile(prcntSurvived, 0.25), digits = 2)` - `r round(quantile(prcntSurvived, 0.75), digits = 2)`).
+Sub-threshold vertices were set to zero in Fiedler vector maps and 0.5 in the binarized maps (so that they would not bias the calculation of averages).
+Figure 5 shows the thresholded partitioning for the same individual shown in Figure 2.
+The maps used in all subsequent analyses were thresholded by this individualized criterion.
+
+``` {r Partition comparison: all thresholded, echo=FALSE, message = FALSE, cache = TRUE}
+## Compare partitionings
 # Across subjects
@@
 
-# Now let's test something: 
-# Traditionally, a vertex-wise test would be carried across subjects.
-# If these traditional analyses miss out on these idiosyncrasies, you should get unsignificant results.
-# So we did a prop.test per vertex, and corrected with FDR to mimic this situation.
-All_proptests <- apply(FB, 1, function(x) {prop.test(sum(x), nSubj)})
-Prop_pvals_corrected <- p.adjust(sapply(All_proptests, "[[", "p.value"), method = "BY")
-Prop_pvals_corrected <- ifelse(Prop_pvals_corrected < 0.05, 1, 0)
-Chisquares <- sapply(All_proptests, "[[", "statistic")
-
-# And a t-test on the FV vals
-All_ttests <- apply(FV, 1, t.test)
-Ttest_pvals_corrected <- p.adjust(sapply(All_ttests, "[[", "p.value"), method = "BY")
-Ttest_pvals_corrected <- ifelse(Ttest_pvals_corrected < 0.05, 1, 0)
-Tstats <- sapply(All_ttests, "[[", "statistic")
-
-```
-
-The average proportion of stable vertices per subject was `r round(mean(prcntStable[prcntStable < 1]), digits = 2)` (SD = `r round(sd(prcntStable[prcntStable < 1]), digits = 2)`).
+```
+
 With these thresholded partitions, we recomputed the overall similarity of their functional organization across participants.
-Compared to before, there was even less overall agreement of the full maps among individuals (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+Compared to before, there was lower topographic agreement across individuals (mean ARI = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
 The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
-Figure 5 (bottom) shows the spatial average of the thresholded binarized partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
+Figure 5 (bottom) shows the spatial average of the thresholded partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
 This summary illustrates the common organizational layout of both communities, but also highlights the considerable variability across individuals, especially in mPFC.
@@
 We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
-In terms of tSNR variability within each region, mPFC had overall greater standard deviation both before and after the threshold (mPFC: pre-threshold mean SD = 33.96, post-threshold mean SD = 30.15; PCC: pre-threshold mean SD = 15.28, post-threshold mean SD = 14.59).
-However, paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding across subjects (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unaffected (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
-In fact, tSNR after thresholding was significantly higher for mPFC (permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
-
-### *Partition Comparison: Day 1 vs Day 2*
-
-The relatively high variability seen in the aggregate map could reflect at least three factors: (1) measurement noise, (2) dynamic variation in mPFC network organization, and (3) stable patterns of functional organization that differ across individuals.
+In terms of tSNR variability across vertices within each region, mPFC had overall greater standard deviation both before and after the threshold (mPFC: pre-threshold mean SD = 33.96, post-threshold mean SD = 30.15; PCC: pre-threshold mean SD = 15.28, post-threshold mean SD = 14.59).
+However, paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
+tSNR after thresholding was significantly higher for mPFC (permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
+
+### *Test/re-test reliability across days*
+
+The relatively high inter-individual variability seen in the aggregate map could reflect at least three factors: (1) measurement noise, (2) dynamic variation in mPFC network organization, and (3) stable patterns of functional organization that differ across individuals.
 To evaluate the third possibility, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
-If the variability we observed were truly due to having captured an individual's unique organization, day to day ARI values should be consistently higher within- than between-individuals (an example comparison for two subjects is provided on Supplemental Figure 2).
+Insofar as the observed variability reflects individual-specific brain organization, day to day ARI values should be consistently higher within-individual than between individuals (an example comparison for two individuals is provided in Supplemental Figure 2).
 Figure 6 shows pairwise comparisons among ten example subjects for PCC and mPFC separately (left).
@@
 It is expected to exceed 1 insofar as functional network organization is reliable and individual-specific.
-This index is intended to factor out the potential effects of measurement noise, as they are asumed to be constant for each region.
-
-Figure 6 shows these ARI ratios for PCC and mPFC for all individuals.
+This index is intended to factor out the potential contributions of measurement noise or dynamic instability, which would introduce variability both across individuals and across days.
+
+Figure 6 shows ARI ratios for PCC and mPFC.
 A signed-rank test showed evidence for specificity (i.e.
 ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC, 0.75), digits = 2)`, V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC, 0.75), digits = 2)`, V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`).
-Moreover, the ratios for mPFC  were significantly higher than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
+Moreover, the ratios for mPFC  were significantly greater than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
 These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns.
 
-### *Partition Comparison: Run based*
+### *Test/re-test reliability across runs*
 
@@
 
-Run-specific SP results could still capture a subject's unique organizational pattern to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, this time using the mean across-run (within-participant) ARI in the denominator of the ratio (Figure 6, right).
+Run-specific SP results could still capture a subject's unique organizational pattern to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+We again computed each subject's ARI ratio in order to quantify the specificity of the partitions, this time using the mean of 6 across-run (within-participant) ARI values in the numerator of the ratio (Figure 6, right).
 
@@
 
-As before, a signed rank test showed that both regions were significantly above 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), but ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
+As before, a signed rank test showed that both regions had ARI ratios significantly greater than 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), and ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
 This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
@@
 
-The computational demands of our approach escalate quickly as the number of vertices increases.
-We thus explored the possible advantage of community detection relative to a simple seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
+We next explored the possible advantage of community detection relative to a simple seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
 We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations.
@@
 A considerable amount of meta-analytic work has been dedicated to pinpointing the spatial embedding of behavioral constructs in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across psychological phenomena [@DelaVega2016; @Kragel2018; @Hiser2018].
-In particular, the effects elicited by the subjective value (SV) of an option and the default network (DN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
+In particular, the effects elicited by the subjective value of an option and the default network (DN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
 However, recent studies have shown considerable variability of the brain's functional topography across individuals, emphasizing the importance of capturing its organization at the individual subject level, and pointing to limitations in aggregative estimations [@Braga2017; @Gordon2017; @Gratton2018b; @Kong2018; @Laumann2015; @Tobyne2018].
@@
 - Joe:
-  - something to potentially discuss later in the paper: for this to be maximally useful in the future, it would help if a general threshold can be
-    identified (without having to do the windowed analysis on every subject). Looking at the amount variability in the per-subject thresholds might give us 
-    a sense of whether that's possible.
+  - something to potentially discuss later in the paper: for this to be maximally useful in the future, it would help if a general threshold can be identified (without having to do the windowed analysis on every subject).
+Looking at the amount variability in the per-subject thresholds might give us a sense of whether that's possible.
 

### 2019-04-30 Manuscript.Rmd
done with Joe's revisions, including forcing APA reference style

@@
 bibliography: mPFC_paper.bib
+csl: apa.csl
 header-includes:
@@
 First, we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average activity across all vertices in PCC for each day separately.
-We compared these seed-based maps with the Fiedler vectors produced by SP by examining three sets of spatial correlations across vertices between days: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps.
+We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP across days in three ways: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps.
+Because the values in the maps were continuous-valued (and not categorical labels, which would be amenable to ARI), we quantified the similarity between maps in terms of the spatial Spearman correlation across vertices.
 These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
+For 3 subjects, the maps produced with one of the days' datasets insufficiently covered area 7m, and so the community labeling was reversed (for one additional subject, both daily maps were reverted).
+ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topography was highly similar.
+We thus visually inspected these subjects (n = 7) and reverted the labeling when it was clear that the topologies aligned across days.
+
 The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018b]).
@@
 To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3).
-The functional topography of PCC was better maintained across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), but the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, V = `r mPFCvs0_wilcox$statistic`, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).
+The functional topography of PCC was better maintained across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), but the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).
 
@@
 
-We next explored the possible advantage of community detection relative to a simple seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
+We next explored the possible advantage of community detection relative to a typical seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
 We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations.
 We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC.
-We compared the map of correlation values in mPFC to the map of unbinarized Fiedler vector values.
-We performed pairwise spatial Spearman correlations among maps computed for each day and method from all subjects.
-For `r nrow(unCorrParticipants %>% filter(Corrs < 0))` subjects, the maps produced with one of the days' datasets insufficiently covered area 7m, and so the community labeling was reversed (for one additional subject, both daily maps were reverted).
-ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topography was highly similar.
-We thus visually inspected these subjects (n = 7) and reverted the labeling when it was clear that the topologies aligned across days.
+We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations.
+Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals.
 Figure 7 (left) shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.
@@
 Day 1 community detection versus Day 2 seed-based correlation).
-While both approaches were reliable, community detection displayed a significantly higher ARI across days than a simple correlation (paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", prepostComp_permTest$Pval))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
-Agreement across methods was fair, signifying that the two approaches identified similar topographic features but also systematic differences.
+While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", prepostComp_permTest$Pval))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
+Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences.
 These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies.
 
-### *Similarities with other work*
+### *mPFC community structure resembles a proposed DN sub-network organization*
 
@@
 We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
-In their original work, Braga and Buckner manually selected individual vertices along areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two anticorrelated networks [@Braga2017; @Braga2019].
-Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to reproduce our prtitionings by selecting seeds in one these diagnostic areas.
-We confirmed seed placement based on the pattern observed in TPJ and PHC.
-The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed to their spectral partitioning counterparts on figure 8.
-
-Visual inspection of these networks shows a remarkable similarity between our DN and non-DN communities and the previously reported sub-networks A and B.
-Since our search space did not contain areas TPJ and PHC, lack of signal from these areas could drive the small discrepancies in the topography between our work and theirs (particularly for network A).
-Nevertheless, these qualitative similarities are important, as they collectively suggest that canonical DN regions consist of two distinct communities.
-Results from the present investigation suggest that the topographic organization of the communities is variable across a large sample of participants, especially in mPFC, and that the SP algorithm is a useful and reliable tool for identifying the two communities in individuals.
+In their original work, Braga and Buckner manually selected individual vertices in areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two spatially anticorrelated networks [@Braga2017; @Braga2019].
+Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to reproduce our partitionings by selecting seeds in these diagnostic areas.
+We confirmed seed placement based on functional connectivity patterns observed in TPJ and PHC.
+The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed with the corresponding community detection results in Figure 8.
+
+Visual inspection of these networks shows a remarkable similarity between our DN community and the previously reported sub-network A.
+However, the non-DN community filled areas not covered by either DN-A or DN-B.
+A potential explanation is that SP fractionated the search space into communities that are maximally distant in function, whereas the sub-networks proposed by Braga and Buckner are still considered to be part of DN.
+Subthreshold vertices in the SP partitionings partially overlap with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A (the DN community) and other networks.
+
+Understanding the interaction of these three networks requires future study.
+Nevertheless, these qualitative similarities are important, as they collectively suggest that canonical DN regions consist of at least two distinct communities.
+Results from the present investigation suggest that the topographic organization of the communities is variable across a large sample of participants, especially in mPFC, and that the SP algorithm is a useful and reliable tool for identifying these communities in individuals.
 
@@
 
+  - It matters whether distinct cognitive functions overlap in the brain.
+Apparent overlap has motivated theoretical proposals about ways in which seemingly dissimilar cognitive domains might recruit a shared set of core cognitive processes.
+
+  - The interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals.
+Group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
+Individual-level effects wash out in group averages (Michalka), apparent overlap in functional activation can vanish with increases in spatial precision (Woo), and resting-state networks have reliable individual-specific characteristics (Muller, Braga).
+
+  - We don't yet really understand how much individual-level heterogeneity there is in the functional topography of mPFC.
+We need to (1) develop an efficient/robust method to capture individual-level topography, and (2) quantify the degree of heterogeneity in a large group of individuals.
+
+  - The method we propose is spectral partitioning.
+Restricting our analyses to a general mPFC/PCC search space makes it appropriate to use a technique that identifies a vertex-wise, binary partitioning.
+This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis.
+SP has advantages (deterministic, simple diagnostics).
+Comparisons with modularity maximization suggested the binary partitioning was appropriate.
+
+  - The community structure identified by SP was reliable across test/re-test and was heterogeneous across individuals. The heterogeneity was especially large in mPFC.
+
+  - There are various potential sources of the heterogeneity.
+Could be gross anatomy (varying sulcal patterns; Mackey).
+Could also be shifts in function relative to anatomy (Haxby hyperalignment).
+Could be connectivity (Passingham, Mars, Tobyne).
+A good goal for future work would be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture (Glasser), or structural connectivity/white matter microstructure (Saygin & Kanwisher).
+
+   - SP is data-driven and the communities don't come with labels.
+We applied labels based on the meta-analysis.
+We were able to apply group-level labels on the basis of the topography in PCC, where functional organization was more consistent across individuals.
+Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.
+
+  - Our results are complementary with previous studies that described individual-specific brain organization using a different data aspect ratio (fewer individuals and more data per individual; Gordon, Braga, Poldrack).
+We've been able to quantify the variability in a large sample, and our method does not require massively multi-session data acquisition.
+
+  - We found SP results could be made more stable by thresholding the underlying Fiedler vector.
+We used temporal stability to apply a custom threshold per subject, but there might be ways to use a generalized threshold in the future.
+
+  - SP outperformed seed-based correlation. This makes sense, since it makes use of more information (n(n-1)/2 pairwise correlations, rather than n correlations with the seed).
+
+  - Our work is complementary with Braga & Buckner. They identified subdivisions, whereas we've identified variable topography for the DN as a whole.
+
+  - Limitations. Our approach is (by design) more anatomically focal. A binary partitioning is undoubtedly only an approximation of the ground truth. Etc.
+
+  - Future directions.
+This could be used to identify individualized units of analysis (ROIs) for task activation studies.
+This might be useful in clinical studies, or in studies aiming to dissociate different forms of valuation, or to reach a stronger conclusion as to whether valuation and DMN processes are topographically segregable or colocalized.
+
+<!--
 - Summarize the results
@@
 
-- Limitations
-  - community detection ground truth
-  - other algorithms (benefit of SP is that it's deterministic, allows for diagnostics, and discourages extremely large/small communities)
-  - bipartition: we focus on that since we tried to capture what belongs to DN and non-DN.
-This intuition can be generalized to other behaviors.
-SP can be expanded to extract additional communities in combination with k-means and the identification of the first non-zero eigenvalue in the low-high rank.
-  - Small search space: working at the vertex-level makes it computationally difficult to produce estimates at the whole-brain level.
-
-- Joe:
-  - something to potentially discuss later in the paper: for this to be maximally useful in the future, it would help if a general threshold can be identified (without having to do the windowed analysis on every subject).
-Looking at the amount variability in the per-subject thresholds might give us a sense of whether that's possible.
-
-<!--
-
 For clinical implications, see Hiser & Koenigs 2018.
@@
 
-We would like to thank Dan Sussman for initial guidance on community detection and evaluation methods.
+We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Dan Sussman for initial guidance on community detection and evaluation methods.
 This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI awards N00014-16-1-2832 and N00014-17-1-2304).
@@
 ```{r Meta-analysis ROIs (Fig.
-1), out.width = "50%", fig.align = "center", fig.cap= "A: Proportion of times each ROI was reported in each literature.
-B: common and unique brain regions associated with DN and subjective value.
-DN regions defined by Yeo et al.
-(2011) in blue, which encompass areas of considerable overlap between DN and SV.
-Literature-specific regions (bilateral 7m and right v23 in yellow, and bilateral 25 in red) were identified from a permutation analysis of chi-squared tests comparing these literatures."}
+1), out.width = "50%", fig.align = "center", fig.cap= "Meta-analysis results.
+A: Proportion of times each ROI was reported in the valuation and DN literatures.
+B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details)."}
 # Change to inflated eventually
@@
 
-```{r Template partition (Fig.
+```{r Representative partitioning (Fig.
 2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307).
@@
 
-``` {r Partition comparison: all 2 (Fig.
+``` {r Partitioning comparison: all (Fig.
 3), fig.align="center", out.width = "50%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
-PCC is better aligned across individuals than mPFC.", echo=FALSE, message = FALSE}
+Functional topographic patterns were better aligned across individuals in PCC than mPFC.", echo=FALSE, message = FALSE}
 # code to produce the plot
@@
 ``` {r Variability per subject: Fiedler vector vs prop.
-DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each subject, we produced partitions for each 20 minute sliding window (1 min shift, ~84 TRs) throughout their full time series (median number of windows = 37).
-B: Proportion of times each vertex was affiliated with the DN community across windows (up), and the continuous Fiedler vector map for the current subject using their full time series (down).
+DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each individual, we produced partitions for each 20 minute sliding window (1 min shift, i.e.
+~84 TRs).
+B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (bottom).
 The maps share considerable qualitative similarities in their gradients along the cortical surface.
@@
 Dashed red lines indicate the mean FV value at which maps were thresholded.
-The histogram counts the mean number of vertices that were affiliated at each proportion.", echo=FALSE, message = FALSE}
+The histogram displays the frequency distribution of y-axis values.", echo=FALSE, message = FALSE}
 # code to generate plots
@@
 ```{r Thresholded maps (Fig 5), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
-Values that did not meet the threshold were set to zero on the Fiedler vector, and 0.5 on the binarized maps (giving rise to a third community of high-variability vertices).
-B: Spatial mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample.
-This aggregate map shows the common organizational principle of the DN and non-DN communities, while also pinpointing the relatively high level of variability in mPFC."}
+Subthreshold values effectively formed a third community of high-variability vertices.
+B: mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample.
+This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the relatively high level of variability in mPFC."}
 
@@
 ``` {r Partition comparison: halves and runs (Fig.
-6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 days of scans each), showing pattern agreement across days and subjects for PCC and mPFC separately.
-Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncrasies in community arrangement for both PCC and mPFC (ratios > 1, solid line), with higher subject-specificity in the latter.
-Right: within-to-between subject mean ARI ratios for each subject again show higher idiosyncratic organization for mPFC.", echo=FALSE, message = FALSE}
+6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 scanning days each), showing pattern agreement across days and subjects for PCC and mPFC separately.
+Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncrasies in community arrangement for both PCC and mPFC (ratios > 1, solid line), with higher subject-specificity in mPFC.
+Right: within-to-between subject mean ARI ratios for run-specific partitionings again show higher subject-specific organization for mPFC.", echo=FALSE, message = FALSE}
 ### code for plots in this fig
@@
 ``` {r Correlation vs community detection (Fig.
-7), fig.align="center", fig.cap = "A: Correlation matrix comparing the inter-day spatial stability of maps derived from seed-based functional connectivity (PCC-based) and the Fiedler vector for 10 example subjects.
+7), fig.align="center", fig.cap = "A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects.
 The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.
-There is high agreement within method (diagonal quadrants), but both methods suggest similar partitions (off-diagonal quadrants).
-B: Day 1 vs Day 2 correlation coefficients for every method, as well as between methods.
-Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo = FALSE, message = FALSE}
+The upper-right and lower-left quadrants show across-method agreement.
+B: Day 1 vs Day 2 correlation coefficients for each method, as well as between methods.
+Community detection through spectral partitioning provided more stable estimates, even though both methods showed good level of agreement.", echo = FALSE, message = FALSE}
 # code to produce the plots

### 2019-05-01 Manuscript.Rmd
new version of similarities with other work

@@
 In the context of network analysis, community detection algorithms subdivide brain networks into sets of nodes that share more connections with each other than with the rest of the network [@Fortunato2016; @Garcia2017].
-Here we use the technique of spectral partitioning (SP), an efficient community detection algorithm that deterministically subdivides a network into two communities [@Belkin2003; @Chung1999; @Fiedler1975].
+Here we use the technique of spectral partitioning (SP), an efficient community detection algorithm that deterministically subdivides a network into two communities [@Belkin2003; @chung1997; @Fiedler1975].
 SP has been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
@@
 Communities (i.e.
-clusters) were identified using the SP algorithm [@Belkin2003; @Chung1999; @Fiedler1975; @Higham2007].
+clusters) were identified using the SP algorithm [@Belkin2003; @chung1997; @Fiedler1975; @Higham2007].
 First, each network was represented as an $n$ x $n$ network weight matrix $W$ as described above (where $n$ equals the number of vertices in the search space, 4,801).
@@
 Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to reproduce our partitionings by selecting seeds in these diagnostic areas.
-We confirmed seed placement based on functional connectivity patterns observed in TPJ and PHC.
-The whole-brain seed-based functional connectivity maps for these subjects are juxtaposed with the corresponding community detection results in Figure 8.
+For functional connectomes from two individuals (100307 and 101006), we selected seeds for networks A and B in TPJ (seed indices), and confirmed their placement based on functional connectivity patterns observed in TPJ, PCC, DLPFC, and PHC.
+The whole-brain seed-based functional connectivity maps for two individuals are juxtaposed with the corresponding community detection results in Figure 8.
 
 Visual inspection of these networks shows a remarkable similarity between our DN community and the previously reported sub-network A.
-However, the non-DN community filled areas not covered by either DN-A or DN-B.
-A potential explanation is that SP fractionated the search space into communities that are maximally distant in function, whereas the sub-networks proposed by Braga and Buckner are still considered to be part of DN.
-Subthreshold vertices in the SP partitionings partially overlap with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A (the DN community) and other networks.
-
-Understanding the interaction of these three networks requires future study.
-Nevertheless, these qualitative similarities are important, as they collectively suggest that canonical DN regions consist of at least two distinct communities.
-Results from the present investigation suggest that the topographic organization of the communities is variable across a large sample of participants, especially in mPFC, and that the SP algorithm is a useful and reliable tool for identifying these communities in individuals.
+However, the non-DN community filled areas not covered by either DN-A or DN-B, further evidencing its disentanglement from DN processes.
+Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A and other networks.
+
+Understanding the interaction of these three networks will require future examination.
+Nevertheless, these qualitative similarities are important, as they collectively suggest that: (1) canonical DN regions can be topographically fractionated into DN and non-DN; (2) the DN community can be further partitioned into two sub-networks; (3) the SP algorithm is a useful and reliable tool for identifying this refined topography; and (4) the topographic organization of the communities is variable across a large sample of participants, especially in mPFC.
 
@@
 
-```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga and Buckner's (2019) criterion, and those produced by spectral partitioning.
-Networks A and B were produced by selecting seeds in diagnostic TPJ, DLPFC and PHC.
-In each case, our DN and non-DN networks map well to their proposed functional organization, albeit with some discrepancies on network A/non-DN."}
+```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B from Braga et al.
+(2019) and SP communities for two individuals.
+Upper: networks A and B produced by selecting seeds in TPJ, with our search space delineated by black borders.
+Bottom: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A.
+The non-DN community covers sections of cortex not associated with either DN sub-network."}
 
@@
 
-\newpage
+\pagebreak
 

### 2019-05-01 Manuscript.Rmd
working on discussion

@@
 In particular, the effects elicited by the subjective value of an option and the default network (DN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
-However, recent studies have shown considerable variability of the brain's functional topography across individuals, emphasizing the importance of capturing its organization at the individual subject level, and pointing to limitations in aggregative estimations [@Braga2017; @Gordon2017; @Gratton2018b; @Kong2018; @Laumann2015; @Tobyne2018].
-Therefore, determining the distinct functional mapping of psychological processes (and the potential extent of their overlap) first requires: 1) understanding and quantifying the degree of heterogeneity in the intrinsic functional organization of this area in a large group of individuals; and 2) a method to reliably and precisely capture it in isolated subjects.
-
-Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to subdivide areas of overlap into DN and non-DN in 100 individuals from the Human Connectome Project.
+This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these seemingly dissimilar cognitive domains might recruit a shared set of core cognitive processes [@Northoff2012].
+
+However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals.
+Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013a], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014].
+These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
+
+So far, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive.
+Therefore, affirming the extent of overlap among psychological processes in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.
+
+Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to reliably subdivide canonical DN and limibic networks [@Yeo2011] on the medial cortex into DN and non-DN in 100 individuals from the Human Connectome Project.
+Restricting our analyses to this general mPFC/PCC search space makes it appropriate to use a technique that identifies a vertex-wise, binary partitioning.
+This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis.
+SP has advantages (deterministic, simple diagnostics).
+Comparisons with modularity maximization suggested the binary partitioning was appropriate.
+
 Our results show that the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects.
@@
 Outline:
-
-  - It matters whether distinct cognitive functions overlap in the brain.
-Apparent overlap has motivated theoretical proposals about ways in which seemingly dissimilar cognitive domains might recruit a shared set of core cognitive processes.
-
-  - The interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals.
-Group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
-Individual-level effects wash out in group averages (Michalka), apparent overlap in functional activation can vanish with increases in spatial precision (Woo), and resting-state networks have reliable individual-specific characteristics (Muller, Braga).
-
-  - We don't yet really understand how much individual-level heterogeneity there is in the functional topography of mPFC.
-We need to (1) develop an efficient/robust method to capture individual-level topography, and (2) quantify the degree of heterogeneity in a large group of individuals.
-
-  - The method we propose is spectral partitioning.
-Restricting our analyses to a general mPFC/PCC search space makes it appropriate to use a technique that identifies a vertex-wise, binary partitioning.
-This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis.
-SP has advantages (deterministic, simple diagnostics).
-Comparisons with modularity maximization suggested the binary partitioning was appropriate.
 

### 2019-05-02 Manuscript.Rmd
more discussion work

@@
 These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
-
-So far, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive.
+However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far.
 Therefore, affirming the extent of overlap among psychological processes in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.
 
-Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to reliably subdivide canonical DN and limibic networks [@Yeo2011] on the medial cortex into DN and non-DN in 100 individuals from the Human Connectome Project.
-Restricting our analyses to this general mPFC/PCC search space makes it appropriate to use a technique that identifies a vertex-wise, binary partitioning.
+Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to reliably subdivide brain regions that show overlap of DN and valuation effects into DN and non-DN in 100 individuals.
+Restricting our analyses to this general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning.
 This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis.
-SP has advantages (deterministic, simple diagnostics).
+Unlike some popular clustering algorithms, SP has the advantage of determinisitcally partitioning networks.
 Comparisons with modularity maximization suggested the binary partitioning was appropriate.
 
-Our results show that the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects.
-These sub-networks were stable over time and across test-retest days using moderate amounts of fMRI data (up to 30 min per day), and resembled an organizational scheme recently observed in a handful of subjects [@Braga2017].
+The community structure identified by SP was idiosyncratic across individuals, and stable across test/re-test evaluations within-individuals.
 We also show that spectral partitioning is capable of identifying these sub-networks in isolated individuals better than more direct seed-based functional connectivity approaches.

### 2019-05-02 Manuscript.Rmd
only 4 discussion pts left

@@
 However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals.
-Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013a], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014].
+Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014].
 These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
 However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far.
-Therefore, affirming the extent of overlap among psychological processes in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.
-
-Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to reliably subdivide brain regions that show overlap of DN and valuation effects into DN and non-DN in 100 individuals.
-Restricting our analyses to this general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning.
+Therefore, affirming that among DN and valuation share neural substrates in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.
+
+Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Tian2018].
+For 100 individuals, we reliably subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities.
+Restricting our analyses to a general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning that was sensitive to the complex topography of the brain.
 This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis.
-Unlike some popular clustering algorithms, SP has the advantage of determinisitcally partitioning networks.
-Comparisons with modularity maximization suggested the binary partitioning was appropriate.
-
-The community structure identified by SP was idiosyncratic across individuals, and stable across test/re-test evaluations within-individuals.
-We also show that spectral partitioning is capable of identifying these sub-networks in isolated individuals better than more direct seed-based functional connectivity approaches.
+Partitioning an individual's brain network through SP has a number of advantages, such as identifying communities deterministically, constraining comunities to contain a similar number of vertices (i.e.
+preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and diagnosing the connectedness and separability of a network through examination of its resulting eigenvalues (**TODO: show this in text**) [@chung1997; @Tian2018].
+Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities, suggested the binary partitioning was appropriate.
+
+We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC.
+However, the precise spatial organization of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individuals.
+This idiosyncrasy in functional topography was particularly pronounced in mPFC, and was present with various amounts of data.
+
+The degree of individual-specifitcity observed in this work can arise from a variety of sources.
+For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to systematically vary across individuals [@Mackey2014].
+Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
+A good goal for future work would be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Saygin2016].
+
+Network-partitioning methods such as SP are data-driven, and therefore provide no labeling information about the resulting communities.
+We circumvented this issue by identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially affiliated to the DN literature in the meta-analysis.
+We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals.
+Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.
+
+Our results are complementary with previous studies that described individual-specific brain organization using a different data aspect ratio [fewer individuals and more data per individual; Gordon, Braga, Poldrack].
+While inter-individual differences in functional topography have been described in these studies, here we were able to quantify the variability in a large sample.
+and our method does not require massively multi-session data acquisition.
 
 Outline:
-
-  - The community structure identified by SP was reliable across test/re-test and was heterogeneous across individuals. The heterogeneity was especially large in mPFC.
-
-  - There are various potential sources of the heterogeneity.
-Could be gross anatomy (varying sulcal patterns; Mackey).
-Could also be shifts in function relative to anatomy (Haxby hyperalignment).
-Could be connectivity (Passingham, Mars, Tobyne).
-A good goal for future work would be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture (Glasser), or structural connectivity/white matter microstructure (Saygin & Kanwisher).
-
-   - SP is data-driven and the communities don't come with labels.
-We applied labels based on the meta-analysis.
-We were able to apply group-level labels on the basis of the topography in PCC, where functional organization was more consistent across individuals.
-Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.
-
-  - Our results are complementary with previous studies that described individual-specific brain organization using a different data aspect ratio (fewer individuals and more data per individual; Gordon, Braga, Poldrack).
-We've been able to quantify the variability in a large sample, and our method does not require massively multi-session data acquisition.
 
@@
 Upper: networks A and B produced by selecting seeds in TPJ, with our search space delineated by black borders.
+Correlation values are thresholded at 0.2.
 Bottom: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A.

### 2019-05-03 Manuscript.Rmd
new citations + new discussion paragraph

@@
 A recognized limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], potentially exaggerating the degree of overlap across domains.
-This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013a].
+This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013].
 An alternative approach is to focus on analyses at the individual-participant level.
@@
 However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals.
-Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014].
+Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Mueller2013], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014].
 These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
@@
 
-Our results are complementary with previous studies that described individual-specific brain organization using a different data aspect ratio [fewer individuals and more data per individual; Gordon, Braga, Poldrack].
-While inter-individual differences in functional topography have been described in these studies, here we were able to quantify the variability in a large sample.
-and our method does not require massively multi-session data acquisition.
+Our results are complementary with previous studies that described individual-specific brain organization.
+On one hand, topographical heterogeneity has been qulitatively highlighted using a different data aspect ratio [few individuals and more data per individual; @Gordon2017, @Braga2017, @Braga2019].
+In terms of stability, previous work has relied on parcellations and group priors to show that an individual's functional connectivity pattern is consistent in time [@Gratton2018; @Kong2018], thus being relatively insensitive to an individual's complex topography.
+Here we were able to quantify the variability and stability of fine-scale functional topography in a large sample with moderately low amounts of data (down to a single 15 minute scan).
 
@@
 
-And write a portion on the lack of subcortical reward-related regions (i.e.
-striatum).
-Say something like 'incorporating the ventral striatum did not refine these partitions through either method.
-This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future.
-Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DN and SV'.
-It is worth noting that the SV-only area from the meta-analysis tends to land in non-DN, although it ends up in no-ones land when thresholding the maps.
-
-It might also be worth mentioning that previous work has established the shift in network types during rest through hidden Markov models (Vidaurre et al., 2016?).
-While this suggests that we should see fluctuations in affiliation, and not stability, Vidaurre's work establishes the dynamics of prevalent function among networks, and not their topologies.
-Our work focuses on the topographical arrangement of the DN network, which can be active or not while maintaining its form.
-So, the two works are compatible.
-Note, I played a bit with AR and MA processes per subject to try to understand the autocorrelation in the sliding window.
-First, both acf/pacf and arima (order = n,0,n) R functions suggested that the data was better fit by AR.
-Moreover, ARs from 1 to 10 had neglegible differences, so I stuck with 1 results for simplicity.
-As expected the data is significantly autocorrelated, and when I checked plotted the residuals they were mostly within the 0.15 bound (normally distributed).
-Coefficients ranged from 0.6 to 1.
-So, there is clear rythmicity in the agreement between each window and the overall pattern.
-However, the intercepts from the ARn processes gave more or less the same estimates as the mean rand index over all the windows.
-This is mostly expected, as we saw that the standard deviation of the rand index was low across participants.
-I am currently interpreting this as a signal that there is clear periodicity that is otherwise harmless for our results: in the end, the agreement remains stable throughout the 4800 TRs.
-
-In terms of noise, there are a handful of things to keep in mind.
-First is that yes, mPFC is noisier overall, but that did not preclude the relatively high levels of agreement across days and sessions per subject, even though ARI heavily penalizes discrepancies (less than linearly).
-Second, low $R^2$ values were found all throughout the z-axis, meaning that variance explained is not strictly determined by the cardinal position of the vertex (and while the correlation was significant due to the sheer number of items, the coefficient was relatively low).
-Right now this might be ok as a way to bypass noise comments, but it would also be interesting to take advantage of the Fiedler vector here.
-Since it's linearly related to $R^2$ per subject, perhaps finding a way to threshold these values would provide cleaner and even more consistent maps.
-
-So what's the advantage of this work over previous ones?
-Gratton, Gordon, and Kong have already found some degree of subject stability and intersubject variability.
-Ours complements these findings by looking at the vertex level, not just mean parcel activity (this made sense for them, as they were looking at the whole brain).
-Also, most of these analyses rely on a small set of oversampled subjects (i.e.
-MSC).
-Here we extend this to 100, giving credit to individualize examinations even without oversampling.
+And write a portion on the lack of subcortical reward-related regions (i.e. striatum).
 

### 2019-05-03 Manuscript.Rmd
two discussion points left, plus reinstatement of eigenvalue connectedness info

@@
 Unlike SP, modularity can fractionate a network into more than two communities.
-Agreement between the partitions provided by the bounded and unbounded community detection methods would suggest the results are not distorted by the restriction of SP to binary partitionings..
+Agreement between the partitions provided by the bounded and unbounded community detection methods would suggest the results are not distorted by the restriction of SP to binary partitionings.
+
+<!--
+We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by SP to be non-zero.
+This eigenvalue serves as an estimator of the optimal number of communities in a network (Chung 1999), such that a rank of two in our partitions justifies limiting the number of communities to two.
+-->
 
@@
 
+# # eigenvalue-based diagnosis of optimal n of communities
+# prcntDissection <- lapply(Summaries, function(data) {which(data$EigenVal < 0.00001)}) # how many consecutive 0s?
+# prcntDissection <- mean((sapply(prcntDissection, length) + 1) == 2) * nSubj # % of subjects who only had 1 zero (thus optimal cuts = 2)
+
 ## Across subjects
@@
 However, the additional communities encompassed a small number of vertices (median = `r median(modularityCounts_extra)`, IQR = `r quantile(modularityCounts_extra, 0.25)` - `r quantile(modularityCounts_extra, 0.75)`) compared to the principal two (median = `r median(modularityCounts_two)`, IQR = `r quantile(modularityCounts_two, 0.25)` - `r quantile(modularityCounts_two, 0.75)`), suggesting that a binary partitioning could provide a reasonable approximation of the network's true community structure.
+<!--  In addition, the estimation of the optimal number of cuts based on the rank of the first non-zero eigenvalue (see "Partition evaluation" for details) showed that 100 percent of the individual networks were best partitioned into two communities.
+-->
 
@@
 
-Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Tian2018].
+Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Toker2019].
 For 100 individuals, we reliably subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities.
@@
 Partitioning an individual's brain network through SP has a number of advantages, such as identifying communities deterministically, constraining comunities to contain a similar number of vertices (i.e.
-preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and diagnosing the connectedness and separability of a network through examination of its resulting eigenvalues (**TODO: show this in text**) [@chung1997; @Tian2018].
+preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and diagnosing the connectedness and separability of a network through examination of its resulting eigenvalues (**TODO: show this in text**) [@chung1997; @Higham2007].
 Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities, suggested the binary partitioning was appropriate.
@@
 This idiosyncrasy in functional topography was particularly pronounced in mPFC, and was present with various amounts of data.
-
-The degree of individual-specifitcity observed in this work can arise from a variety of sources.
+This degree of individual-specifitcity can arise from a variety of sources.
 For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to systematically vary across individuals [@Mackey2014].
@@
 Here we were able to quantify the variability and stability of fine-scale functional topography in a large sample with moderately low amounts of data (down to a single 15 minute scan).
+The motivation to sub-divide DN also stems from recent work by Kernbach et al.
+[-@Kernbach2018], where they identified specialized communication of parcels within DN with the rest of the brain in a large pool of individuals.
+
+We found SP results could be made more stable by thresholding the underlying Fiedler vector.
+We generated custom thresholds for each individual by interrogating the relationship between Fiedler vector values and the degree of persistent community affiliation of vertices over time.
+The magnitude of these eigenvector values has been recently used to characterize the continuous connectivity profile of the insula with the rest of the brain, challenging the notion of discrete parcellations of this region [@Tian2018].
+We anticipate that these values will be helpful to future neuroscientific studies in providing gradual information not afforded by other clustering algorithms.
 
 Outline:
-
-  - We found SP results could be made more stable by thresholding the underlying Fiedler vector.
-We used temporal stability to apply a custom threshold per subject, but there might be ways to use a generalized threshold in the future.
 
@@
 <!--
-- Summarize the results
-- Ours are not the first to show variability across individuals, but previous studies have focused on a relatively small number of subjects and often rely on qualitative assessment of these differences.
-They also use parcellations for networks, whereas we focused on individual vertices to gain spatial finesse.
-Also, to the best of our knowledge we are the first to quantify the organizational heterogeneity of these areas in the human brain.
 - We are also not the first to show functional subdivision of DN [@Kernbach2018] (but that's using group averages on parcellated data), or this particular individualized pattern of subdivision (braga).

### 2019-05-03 Manuscript.Rmd
discussion draft done

@@
 
-<!--
-We also diagnosed our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by SP to be non-zero.
-This eigenvalue serves as an estimator of the optimal number of communities in a network (Chung 1999), such that a rank of two in our partitions justifies limiting the number of communities to two.
--->
-
 ### *Partition Evaluation*
@@
 We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects.
-Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a].
+Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013].
 
@@
 
-# # eigenvalue-based diagnosis of optimal n of communities
-# prcntDissection <- lapply(Summaries, function(data) {which(data$EigenVal < 0.00001)}) # how many consecutive 0s?
-# prcntDissection <- mean((sapply(prcntDissection, length) + 1) == 2) * nSubj # % of subjects who only had 1 zero (thus optimal cuts = 2)
-
 ## Across subjects
@@
 However, the additional communities encompassed a small number of vertices (median = `r median(modularityCounts_extra)`, IQR = `r quantile(modularityCounts_extra, 0.25)` - `r quantile(modularityCounts_extra, 0.75)`) compared to the principal two (median = `r median(modularityCounts_two)`, IQR = `r quantile(modularityCounts_two, 0.25)` - `r quantile(modularityCounts_two, 0.75)`), suggesting that a binary partitioning could provide a reasonable approximation of the network's true community structure.
-<!--  In addition, the estimation of the optimal number of cuts based on the rank of the first non-zero eigenvalue (see "Partition evaluation" for details) showed that 100 percent of the individual networks were best partitioned into two communities.
--->
 
@@
 In their original work, Braga and Buckner manually selected individual vertices in areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two spatially anticorrelated networks [@Braga2017; @Braga2019].
-Therefore, we hypothesized that if the communities we identified on the medial wall matched their proposed networks, we should be able to reproduce our partitionings by selecting seeds in these diagnostic areas.
-For functional connectomes from two individuals (100307 and 101006), we selected seeds for networks A and B in TPJ (seed indices), and confirmed their placement based on functional connectivity patterns observed in TPJ, PCC, DLPFC, and PHC.
+Therefore, we hypothesized that if the SP communities corresponded their proposed networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas.
+For functional connectomes from two individuals (100307 and 101006), we selected seeds for networks A and B in TPJ, and confirmed their placement based on functional connectivity patterns observed in TPJ, PCC, DLPFC, and PHC (correlation coefficients thesholded at 0.2), as stipulated by Braga et al.
+[-@Braga2019].
 The whole-brain seed-based functional connectivity maps for two individuals are juxtaposed with the corresponding community detection results in Figure 8.
-
 Visual inspection of these networks shows a remarkable similarity between our DN community and the previously reported sub-network A.
 However, the non-DN community filled areas not covered by either DN-A or DN-B, further evidencing its disentanglement from DN processes.
-Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A and other networks.
-
-Understanding the interaction of these three networks will require future examination.
-Nevertheless, these qualitative similarities are important, as they collectively suggest that: (1) canonical DN regions can be topographically fractionated into DN and non-DN; (2) the DN community can be further partitioned into two sub-networks; (3) the SP algorithm is a useful and reliable tool for identifying this refined topography; and (4) the topographic organization of the communities is variable across a large sample of participants, especially in mPFC.
 
@@
 This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis.
-Partitioning an individual's brain network through SP has a number of advantages, such as identifying communities deterministically, constraining comunities to contain a similar number of vertices (i.e.
-preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and diagnosing the connectedness and separability of a network through examination of its resulting eigenvalues (**TODO: show this in text**) [@chung1997; @Higham2007].
-Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities, suggested the binary partitioning was appropriate.
+Partitioning an individual's brain network through SP has a number of advantages, including identifying communities deterministically, constraining comunities to contain a similar number of vertices (i.e.
+preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and diagnosing the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
+Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], suggested the binary partitioning was appropriate.
 
@@
 On one hand, topographical heterogeneity has been qulitatively highlighted using a different data aspect ratio [few individuals and more data per individual; @Gordon2017, @Braga2017, @Braga2019].
-In terms of stability, previous work has relied on parcellations and group priors to show that an individual's functional connectivity pattern is consistent in time [@Gratton2018; @Kong2018], thus being relatively insensitive to an individual's complex topography.
+In terms of stability, previous work has relied on parcellations and group priors to show that an individual's functional connectivity pattern is consistent in time [@Gratton2018b; @Kong2018], thus being relatively insensitive to an individual's complex topography.
 Here we were able to quantify the variability and stability of fine-scale functional topography in a large sample with moderately low amounts of data (down to a single 15 minute scan).
@@
 
-We found SP results could be made more stable by thresholding the underlying Fiedler vector.
-We generated custom thresholds for each individual by interrogating the relationship between Fiedler vector values and the degree of persistent community affiliation of vertices over time.
+In addition to its general diagnostics, SP provides analytical advantages specific to neuroscience.
+We found that SP outperformed a traditional seed-based correlation approach in capturing idiosyncratic functional topography.
+By relying on all sources of functional covariation among cortical vertices (rather than individual correlations with the seed), community detection methods in general, and SP in particular, are capable of further filtering nodes with weak sub-network affiliation.
+In addition, we found SP results could be made more stable by thresholding the underlying Fiedler vector by using temporal stability to apply a custom threshold per individual.
 The magnitude of these eigenvector values has been recently used to characterize the continuous connectivity profile of the insula with the rest of the brain, challenging the notion of discrete parcellations of this region [@Tian2018].
-We anticipate that these values will be helpful to future neuroscientific studies in providing gradual information not afforded by other clustering algorithms.
-
-Outline:
-
-  - SP outperformed seed-based correlation. This makes sense, since it makes use of more information (n(n-1)/2 pairwise correlations, rather than n correlations with the seed).
-
-  - Our work is complementary with Braga & Buckner. They identified subdivisions, whereas we've identified variable topography for the DN as a whole.
-
-  - Limitations. Our approach is (by design) more anatomically focal. A binary partitioning is undoubtedly only an approximation of the ground truth. Etc.
-
-  - Future directions.
-This could be used to identify individualized units of analysis (ROIs) for task activation studies.
-This might be useful in clinical studies, or in studies aiming to dissociate different forms of valuation, or to reach a stronger conclusion as to whether valuation and DMN processes are topographically segregable or colocalized.
-
-<!--
-- We are also not the first to show functional subdivision of DN [@Kernbach2018] (but that's using group averages on parcellated data), or this particular individualized pattern of subdivision (braga).
-Our results are complementary in the sense that we show similar outcomes in 100 subjects.
-The major discrepancy is that we assign meaning to the communities based on their coverage of regions identified through a meta-analysis.
-- Stability within subject has also been shown before. This work was done using either parcellations and oversampling though. [@Laumann2015; @Gordon2017; @Braga2017; @Gratton2018b; @Kong2018]
-- Talk about SP as a way to identify an individual's partition: deterministic, with simple diagnostics, and requires less data requirements.
-- Similarity with B&B: One way in which our results are at odds with those from Braga and Buckner is the functional labeling of these sub-networks.
-Based on our criteria, network B would more closely identify with DN (per 7m affiliation), while we currently do not have enough evidence to label network A.
-These discrepancies should be addressed with explicit behavioral manipulations in the future.
-Also our search space is limited compared to theirs, thus making the patterns only partially similar.
-- The main gap is mapping behavior to functional organization, but we will do that with behavioral manipulations of subjective value in the future.
-Instead, we focus on understanding the importance of individualized mapping in these areas first, as a baseline.
-- Clinical implications: individualized targets, and more accurate estimation of impacts based on assessment of individual patients.
-Similarly, our approach focuses on individual estimations without group priors, so it's well fit to address the problem of low n in clinical research.
-Also, SP can produce these effects with moderate amounts of data.
-Previous results suggest impractical amounts.
-
-For clinical implications, see Hiser & Koenigs 2018.
-In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC.
-It would be more interesting to identify the repercussions of damage in mPFC per individual.
-They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment.
-The refinement of the technique is thus coupled to being able to identify personalized functional topologies.
-They list a number of results related to mPFC functional connectivity too.
-In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse.
-(note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas' latest)
-
-It will also be good to note that there is concurrent debate on the ground truth of community detection.
-In other fields, identifying a community structure is not necessarily associated with the true organization of the network.
-What happens is that you might find a tangential grouping that gives you information different from your original goal [@Clauset2004].
-In our case, however, averaging everyone's partitions produces organizational maps that resemble those from previous work (e.g.
-Margulies).
-
-Talk about how there are other community detection algorithms, and that modularity and SP over and underfit, respectively.
-However, SP eigenmaps have been found to provide relevant functional information.
-In addition, both modularity and SP rely on connectivity strength, and thus is amenable to the correlative nature of functional connectivity.
-
-And write a portion on the lack of subcortical reward-related regions (i.e. striatum).
-
-Make sure to emphasize that the high overlap between sliding windows makes it more likely that differences are due to noise in the signal, and not strong variability.
-Like, you wouldn't expect the actual network distribution to shift that much after shifting the time series by 1 minute.
--->
+The combination of discrete classification and gradual information provided by SP points to flexible information benefits not regularly afforded by other clustering algorithms.
+
+The community organization of PCC and mPFC shares significant similarities with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; -@Braga2019].
+The topography of our thresholded DN community closely matched network A, while non-DN captured zones uncovered by either DN network.
+Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A and other networks.
+Our findings therefore complement the initial identification of sub-DN networks by quantifying the systematic variability of its underlying topography in a larger group of people Understanding the interaction of networks A (DN), B, and non-DN should be subject of future examinations.
+Nevertheless, these qualitative similarities are important, as they collectively suggest that: (1) canonical DN regions can be topographically fractionated into DN and non-DN; (2) the DN community can be further partitioned into two sub-networks; (3) the SP algorithm is a useful and reliable tool for identifying this refined topography in a data-driven way; and (4) the topographic organization of the communities is variable across a large sample of participants, especially in mPFC.
+
+The work presented here faces a number of challenges.
+A prominent limitation is that our approach is (by design) anatomically focal.
+However, similar spectral methods have been successfully recruited in larger cortical zones.
+For example, Margulies et al.
+[-@Margulies2016] used a combination of gradient maps to characterize the spatial embedding of unimodal and heteromodal regions of cortex.
+Here we show that a variant of such methods, in combination with prior information on the brain space of interest, is capable of producing refined functional topography in individuals.
+A similar limitation corresponds to forcing a bipartition of this region.
+While we provide evidence that binarizing this region is adequate, questions remain regarding the potential dynamics that might obscure additional networks (e.g.
+the correspondence of subthreshold DN vertices to network B, as mentioned above).
+In addition, structural connections from these networks to the rest of the brain might produce more nuanced information about sub-specialization of these communities [@Kernbach2018].
+
+Our findings pose interesting avenues for future work.
+The ability to capture an individual's functional topography without the need of group priors has direct implications for clinical research and diagnosis, where acquiring large sample and data sizes are challenging.
+Studies interested in characterizing the repercussions of mental illness on neural function could benefit from answering this question in individual patients.
+This is especially true for disorders such as schizophrenia and depression that significantly affect mPFC [@Hiser2018].
+mPFC has also recently become a common target for deep brain stimulation (or TMS) as a depression treatment [CITATION FROM HISER AND KOENIGS], but signal quality issues make imaging this area challenging [CITATION].
+Being able to produce stable personalized targets in mPFC has the potential to boost our ability to implement and evaluate the effectiveness of these methods.
+Finally, the main motivating factor for this study was to assess whether cortical regions subserving DN and valuation are indeed overlapping in mPFC and PCC.
+While our current results suggest a re-examination of this question at the individual level, we do not estimate the location of valuation relative to DN.
+A natural next step is to examine whether SP can be similarly used to capture the idiosyncratic cortical topography of valuation.
+This could allow us not only to more strongly conclude whether DN and valuation are neurally segregable, but also aid in studies aiming to dissociate different forms of valuation.
 

### 2019-05-03 Manuscript.Rmd
cleaning up the code, and testing an option to force figure order

@@
     - \linenumbers
+    - \usepackage{float}
 ---
@@
 ```{r setup, include = FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
-```
-
-```{r Libraries and functions, include = FALSE, echo = FALSE}
-
-Cols <- c("aquamarine4", "#D9541A", rgb(190,190,190,100, maxColorValue = 255))
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.pos = 'H')
+```
+
+```{r Libraries, functions, and setups, include = FALSE, echo = FALSE}
+
+# color scheme
+Cols <- c("aquamarine4", "#D9541A", rgb(190, 190, 190, 100, maxColorValue = 255))
 
@@
 threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
-permuting <- FALSE # show permutation progress?
+permuting <- FALSE # show meta-analysis permutation progress? (SLOW)
 
@@
 library(tidyverse)
-library(igraph)
+library(igraph) # DELETE?
 library(pander)
-library(ggnetwork)
+library(ggnetwork) # DELETE?
 library(ggplot2)
-library(gridExtra)
+library(gridExtra) # DELETE?
 library(data.table) 
-library(plyr)
+library(plyr) # DELETE?
 library(mcclust) 
@@
 
-# produce one permutation instance of the meta-analysis (so it can be fed to mclapply for quicker results)
+## produce one permutation instance of the meta-analysis (so it can be fed to mclapply for quicker results)
 metaPerm <- function(list1 = studyList_sv, list2 = studyList_DN, labels = Yeo_labels, perm = 1) {
@@
 
-}
-
-## log-log degree distribution
-logDegreeDist <- function(Graph = padjMat) {
-
-  tempD <- degree(Graph)
-  tempDD <- degree.distribution(Graph) # frequency of occurrencies of certain degrees
-  d <- (0:(max(tempD)-1))
-  ind <- (tempDD!=0)
-  plot(d[ind], tempDD[ind], log = "xy", col = "blue", 
-       xlab = "Log-Degree", ylab = "Log-Intensity",  
-       main = "Log-Log Degree Distribution")
-
-}
-
-## Create correlation matrix between vertices of 2 ROIs
-# Requires labeled time series matrix
-vertexCorrMat <- function(ROI_1 = 'R_7m_ROI', ROI_2 = 'L_7m_ROI'){
-
-  # extract the time series from the ROIs
-  indexing_1 <- which(rownames(timeSeries)==as.character(ROI_1))
-  indexing_2 <- which(rownames(timeSeries)==as.character(ROI_2))
-  nVerts_1 <- length(indexing_1)
-  nVerts_2 <- length(indexing_2)
-  ROI_1_tseries <- timeSeries[indexing_1, ]
-  ROI_2_tseries <- timeSeries[indexing_2, ]
-
-  # Create empty matrix
-  corrMat <- matrix(data = 0, nrow = nVerts_1, ncol = nVerts_2)
-
-  # 
-  for (vertex_1 in seq(nVerts_1)){
-
-    # temp series 1
-    tempOne <- ROI_1_tseries[vertex_1, ]
-
-    for(vertex_2 in seq(nVerts_2)){
-
-      # temp series 2
-      tempTwo <- ROI_2_tseries[vertex_2, ]
-
-      # store the Pearson correlation in the corr matrix
-      corrMat[vertex_1, vertex_2] <- cor(tempOne, tempTwo, method = "pearson")
-
-    }
-  }
-
-  # name the dimensions of the matrix according to the surface vertex index
-  rownames(corrMat) <- indexing_1
-  colnames(corrMat) <- indexing_2
-
-  # plot (optional?)  
-  # unclustered heatmap
-  heatmap(corrMat,
-          Rowv = NA,
-          Colv = NA,
-          scale = "row",
-          col = pallette(1000))
-
-  # clustered heatmap
-  heatmap(corrMat,
-          scale = "row",
-          col = pallette(1000))
-
-  # print min-max corr vals
-  print(range(corrMat))
-
-  return(corrMat)
-
-}
-
-## Correlation matrix between an ROI and the Glasser parcels
-parcelCorrMat <- function(ROI = 'R_7m_ROI', lbels = lookup$V1){
-
-  # extract the time series from the ROIs
-  indexing <- which(rownames(timeSeries)==as.character(ROI))
-  nVerts <- length(indexing)
-  ROI_tseries <- timeSeries[indexing, ]
-
-  # create empty matrix to store values
-  corrMat <- matrix(data = 0, nrow = nVerts, ncol = 360)
-
-  # Loop through every combination of label and 7m vertex
-  for (Parcel in lbels){
-
-    # Get an ROI index to retrieve timeseries and store correlation vals
-    indxROI <- which(lbels==as.character(Parcel))
-
-    for(vertex in seq(nVerts)){
-
-      # temp series
-      tempROI <- as.numeric(ptSeries[indxROI, ])
-      tempVertex <- ROI_tseries[vertex, ]
-
-      # store the Pearson correlation in the corr matrix
-      corrMat[vertex, indxROI] <- cor(tempROI, tempVertex, method = "pearson")
-
-    }
-  }
-
-  # name the columns according to labels
-  colnames(corrMat) <- lbels
-  rownames(corrMat) <- indexing
-
-  # plot (optional?)  
-  # unclustered heatmap
-  heatmap(corrMat,
-          Rowv = NA,
-          Colv = NA,
-          scale = "none",
-          col = pallette(1000))
-
-  # clustered heatmap
-  heatmap(corrMat,
-          scale = "none",
-          col = pallette(1000))
-
-  # print min-max corr vals
-  print(range(corrMat))
-
-  return(corrMat)
-
-}
-
-## Correlation matrix between an Parcel and every other grayordinate
-# THIS CAN BE OPTIMIZED WITH A BETTER USE OF COR()
-partoverCorrMat <- function(ROI = 'R_7m_ROI', lbels = verts[[1]]){
-
-  # extract the time series from the ROI
-  indexing <- which(rownames(ptSeries)==as.character(ROI))
-  ROI_tseries <- as.numeric(ptSeries[indexing, ])
-
-  # get the remaining number of vertices
-  nVerts <- length(lbels)
-
-  # Create data frame to store values
-  parcelIndx <- which(labelCoords_parcel$Label==ROI)
-  corrVec <- data.frame(Seed = rep(ROI, nVerts),
-                        Labels = lbels,
-                        xstart = rep(labelCoords_parcel$x[parcelIndx], nVerts), # 7.33324 for R_7m
-                        ystart = rep(labelCoords_parcel$y[parcelIndx], nVerts), # -63.142
-                        zstart = rep(labelCoords_parcel$z[parcelIndx], nVerts)) # 42.5578
-
-  for(vertex in seq(nVerts)){
-
-    # temp series
-    tempVertex <- timeSeries[vertex, ]
-
-    # store the Pearson correlation in the corr matrix
-    #corrVec$Correlation[vertex] <- cor(ROI_tseries, tempVertex, method = "pearson")
-
-    # Another option, so that FDR can be applied
-    tempCor <- cor.test(ROI_tseries, tempVertex, method = "pearson")
-    corrVec$Correlation[vertex] <- tempCor$estimate
-    corrVec$pval[vertex] <- tempCor$p.value
-
-  }
-
-  # Turn ROI vertices into 0s
-  indexing <- which(corrVec$Labels==as.character(ROI))
-  corrVec$Correlation[indexing] <- 0
-
-  # Create a column with p-vals corrected for multiple comparisons
-  corrVec$adjPval <- p.adjust(corrVec$pval, "BY")
-
-  # normalize correlation vals for analysis (see below)
-  tempTanh <- fisherTanh(Data = corrVec$Correlation)
-  corrVec$tanhZ <- tempTanh$tanhZ
-  corrVec$tanhPvals <- tempTanh$pvals
-  corrVec$tanhPAdjusted <- tempTanh$adjustPvals
-
-  return(corrVec)
-
-}
-
-## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
-# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
-# Normalization approach suggested in network textbook (equation 7.20)
-# This transformation is approximately normal with mean 0 and sd = sqrt(1 / (n - 3))
-fisherTanh <- function(Data = padjMatrix, preThresh = NA){
-
-  transformed <- list()
-
-  if (is.numeric(preThresh)) {
-    Data[Data == 1] <- 0.999
-    Data[Data < preThresh] <- 0
-    transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
-  } else {
-    # tanh
-    Data[Data == 1] <- 0.999
-    transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
-
-    # p-vals
-    if (is.matrix(Data)) {
-      z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
-      n <- dim(Data)[1]
-    } else if (is.vector(Data)) {
-      z.vec <- transformed$tanhZ
-      n <- length(Data)
-    }
-    transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)
-
-    # adjust pvals
-    transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")
-
-    if (is.matrix(Data)) {
-      # get pvals and their adjustment into a symetric matrix form
-      # regular
-      tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
-      tempMat[upper.tri(tempMat)] <- transformed$pvals
-      tempMat[lower.tri(tempMat)] <- transformed$pvals
-      dimnames(tempMat) <- list(rownames(Data), rownames(Data))
-      transformed$pvals <- tempMat
-
-      # adjusted
-      tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
-      tempMat[upper.tri(tempMat)] <- transformed$adjustPvals
-      tempMat[lower.tri(tempMat)] <- transformed$adjustPvals
-      dimnames(tempMat) <- list(rownames(Data), rownames(Data))
-      transformed$adjustPvals <- tempMat
-
-      # retain only the significant adjusted pval Z scores
-      transformed$tanhZ[transformed$adjustPvals > 0.05] <- 0
-    }
-  }
-
-  return(transformed)
-
-}
-
-## Extract the centroid-most vertex from each parcel
-parcelCentroid <- function(ROI = 'R_7m_ROI', all_coordinates = labelCoords_vertex){
-
-  # The coordinate file must contain a Label column
-
-  # Get the ROI-specific vertices
-  indx <- grep(ROI, all_coordinates$Label)
-
-  # Grab the coordinates
-  tempCoords <- all_coordinates[indx, c("x","y","z")]
-  rownames(tempCoords) <- indx
-
-  # Compute the distance among all vertices, and turn into a matrix
-  tempDist <- dist(tempCoords, diag = T)
-  tempDist <- as.matrix(tempDist)
-
-  # Compute the sum of distances for each vertex, and get the minimum
-  sumDists <- colSums(tempDist)
-  minDist <- which(sumDists == min(sumDists))
-  minDist <- indx[minDist]
-
-  return(minDist)
-
-}
-
-## This function takes the output from partoverCorrMat() and adds/removes the characteristics we decided on.
-prepROItoVer <- function(Data = R_7m_allCorr, Coordinates = labelCoords_vertex){
-
-  # Add vertex coordinates
-  tempDframe <- cbind(Data, Coordinates[,1:3])
-
-  # Remove rows with non-significant adjusted pvalues
-  indx <- tempDframe$adjPval < 0.05
-  tempDframe <- tempDframe[indx, ]
-
-  # Characterize correlation direction and round up vals for plotting
-  tempDframe$Relation <- ifelse(tempDframe$Correlation < 0, "Negative", "Positive")
-  tempDframe$Correlation <- round(tempDframe$Correlation, digits = 2)
-
-  # Add a column to differentiate between left/right hemispheres
-  tempDframe$Hemisphere <- substring(tempDframe$Labels,1,1)
-
-  return(tempDframe)
-
-}
-
-## Plot correlation from ROI to rest of vertices
-plotROItoVertex <- function(Data = R_7m_allCorr, ROI = 'R_7m_ROI', ColRange = Cols, View = "Axial", Legends = TRUE){
-
-  ROIindx <- grep(ROI, Data$Labels)
-  ROIvertices <- Data[ROIindx,c("x","y","z")] # grab ROI-specific vertices to black out
-  labelCoord <- ROIvertices[1,] # just to place the label
-
-  if (View == "Axial") {
-    ggplot() +
-      geom_point(data = Data, aes(x=x, y=y, alpha=.5, color = Correlation), show.legend = Legends) +
-      geom_point(data = labelCoords_vertex, aes(x=x, y=y), alpha=0.01) +
-      geom_nodes(data = ROIvertices, aes(x=x, y=y)) +
-      geom_nodelabel_repel(aes(x=labelCoord$x, y=labelCoord$y, label = sub("_ROI","",ROI))) +
-      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
-      theme_blank()
-  } else if (View == "Sagittal") {
-    ggplot() +
-      geom_point(data = Data, aes(x=y, y=z, alpha=.5, color = Correlation), show.legend = Legends) +
-      geom_point(data = labelCoords_vertex, aes(x=y, y=z), alpha=0.01) +
-      geom_nodes(data = ROIvertices, aes(x=y, y=z)) +
-      geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
-      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
-      theme_blank()
-  } else if (View == "Coronal") {
-    ggplot() +
-      geom_point(data = Data, aes(x=x, y=z, alpha=.5, color = Correlation), show.legend = Legends) +
-      geom_point(data = labelCoords_vertex, aes(x=x, y=z),  alpha=0.01) +
-      geom_nodes(data = ROIvertices, aes(x=x, y=z), alpha=.5) +
-      geom_nodelabel_repel(aes(x=labelCoord$x, y=labelCoord$z, label = sub("_ROI","",ROI))) +
-      scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
-      theme_blank()
-  } else if (View == "Medial Right") {
-    if (substring(ROI,1,1) == "R") {
-      oneHemi <- Data[grep("R", Data$Hemisphere), ]
-      oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
-      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
-      medialHemi$y <- medialHemi$y * -1
-      ROIvertices$y <- ROIvertices$y * -1
-      labelCoord$y <- labelCoord$y * -1
-      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
-      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
-      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
-      medialHemi_all$y <- medialHemi_all$y * -1
-      ggplot() +
-        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
-        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
-        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
-        geom_nodes(data = ROIvertices, aes(x=y, y=z), alpha=.5) +
-        geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
-        theme_blank()
-    } else {
-      oneHemi <- Data[grep("R", Data$Hemisphere), ]
-      oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
-      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
-      medialHemi$y <- medialHemi$y * -1
-      ROIvertices$y <- ROIvertices$y * -1
-      labelCoord$y <- labelCoord$y * -1
-      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
-      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
-      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
-      medialHemi_all$y <- medialHemi_all$y * -1
-      ggplot() +
-        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
-        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
-        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
-        theme_blank()
-    }
-  } else if (View == "Medial Left") {
-    if (substring(ROI,1,1) == "L") {
-      oneHemi <- Data[grep("L", Data$Hemisphere), ]
-      oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
-      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
-      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
-      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
-      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
-      ggplot() +
-        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
-        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
-        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
-        geom_nodes(data = ROIvertices, aes(x=y, y=z), alpha=.5) +
-        geom_nodelabel_repel(aes(x=labelCoord$y, y=labelCoord$z, label = sub("_ROI","",ROI))) +
-        theme_blank()
-    } else {
-      oneHemi <- Data[grep("L", Data$Hemisphere), ]
-      oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
-      medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
-      oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
-      oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
-      medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
-      ggplot() +
-        geom_point(data = medialHemi, aes(x=y, y=z, alpha=.1, color = Correlation), show.legend = Legends) +
-        #geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=0.07) +
-        scale_color_gradient2(low = ColRange[1], mid = "white", high = ColRange[2], limits = c(-1,1)) +
-        theme_blank()
-    }
-  }
-
-}
-
-## Run a fastgreedy modularity community detection on ROIs
-# This function relies on having the timeSeries data uploaded, and labelCoords_vertex 
-# Extras dictates whether the community object + correlation matrix should also be extracted
-communityDetection <- function(Data = parcelBins$First, ROIS = "None", Type = "vertex", extras = F) {
-
-  print(paste('Computing modularity based on', Type))
-
-  if (ROIS == "None"){
-
-    # This will just do SP for now, for sliding window
-    print("Previously concatenated data")
-
-    corrMat <- cor(t(Data))
-    corrMatrix <- corrMat
-    transfMat <- fisherTanh(Data = corrMat)
-
-    corrMat <- transfMat$tanhZ
-
-    diag(transfMat$tanhZ) <- 0    
-    diag(corrMat) <- 0
-
-    corrMat <- exp(corrMat)
-    corrMat[corrMat==1] <- 0
-    transfMat$tanhZ <- corrMat
-
-    tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
-    tempLap <- laplacian_matrix(tempGraph, normalized=T)
-    tempEigen <- eigen(tempLap)
-    f.vec <- length(tempEigen$values) - 1
-    tempEigen$binarized <-  as.factor(ifelse(tempEigen$vectors[,f.vec] > 0, 1, 0)) # binarized Fiedler Vector
-
-    summary <- data.frame(Label = colnames(corrMat),
-                          Hemisphere = substring(colnames(corrMat),1,1),
-                          EigenVal = tempEigen$values,
-                          FiedlerVec = tempEigen$vectors[, (length(tempEigen$values) - 1)],
-                          FiedlerBinary = tempEigen$binarized)
-
-    ## Get the final components
-    if (extras == T) {
-      modularityResults <- list(CorrMatrix = corrMatrix,
-                                TransfMatrix = transfMat,
-                                Summary = summary)
-    } else {
-      modularityResults <- list(Summary = summary)
-    }
-
-  } else {
-
-    if (Type == "vertex") {
-      # To store the vertex indices corresponding to the ROIs
-      indx <- numeric()
-
-      # had to place dashes on each side because grep grabbed strings containing the names (i.e. 47m, a24pr)
-      for (ROI in ROIS) {
-        indx <- c(indx, grep(ROI, rownames(Data)))  
-      }
-
-      nVerts <- length(indx)
-      ROI_tseries <- Data[indx, ]
-
-      # This used to be done with the for loop, but it was too slow. cor() speeds up the process by a lot
-      corrMat <- cor(t(ROI_tseries))
-
-      # name the dimensions of the matrix according to the surface vertex index
-      rownames(corrMat) <- indx
-
-      # for storing later
-      corrMatrix <- corrMat
-
-      # transform to Fisher's (think of thresholding)
-      transfMat <- fisherTanh(Data = corrMat)
-
-      # Store Fisher transformed vals for graphing
-      corrMat <- transfMat$tanhZ
-
-      # diagonals of 1 could be interpreted as self-loops
-      diag(transfMat$tanhZ) <- 0    
-      diag(corrMat) <- 0
-
-      # Exponentiate to preserve distribution while ensuring positive weights
-      # I'm keeping corrMat and transfMat$tanhZ separate in case I want to uncorrect transfMat in the future
-      corrMat <- exp(corrMat)
-      corrMat[corrMat == 1] <- 0
-      transfMat$tanhZ <- corrMat
-
-      # community detection
-      # I initially used the absolute value of the correlation, but the exp preserves the distribution 
-      # Next, try using the fisher transform
-
-      tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
-      tempCommunity <- fastgreedy.community(tempGraph)
-
-      # community object
-      #modularityResults$community <- tempCommunity
-
-      # correlation matrix with transformed values
-      #modularityResults$corrMat <- corrMatrix
-
-      # get coordinate info from selected regions (useful for ggplot)
-      summary <- data.frame(Vertex = indx,
-                            Label = tempCommunity$names,
-                            Membership = tempCommunity$membership,
-                            Modularity = tempCommunity$modularity,
-                            x = labelCoords_vertex[indx, "x"],
-                            y = labelCoords_vertex[indx, "y"],
-                            z = labelCoords_vertex[indx, "z"],
-                            Hemisphere = substring(tempCommunity$names,1,1))
-
-    } else if (Type == "parcels") {
-
-      # This used to be done with the for loop, but it was too slow. cor() speeds up the process by a lot
-      corrMat <- cor(t(Data))
-
-      # for storing later
-      corrMatrix <- corrMat
-
-      # transform to Fisher's (think of thresholding)
-      transfMat <- fisherTanh(Data = corrMat)
-
-      # Store Fisher transformed vals for graphing
-      corrMat <- transfMat$tanhZ
-
-      # diagonals of 1 could be interpreted as self-loops
-      diag(transfMat$tanhZ) <- 0
-      diag(corrMat) <- 0
-
-      # Exponentiate to preserve distribution while ensuring positive weights
-      # I'm keeping corrMat and transfMat$tanhZ separate in case I want to uncorrect transfMat in the future
-      corrMat <- exp(corrMat)
-      corrMat[corrMat==1] <- 0
-      transfMat$tanhZ <- corrMat
-
-      # community detection
-      # I initially used the absolute value of the correlation, but the exp preserves the distribution 
-      # Next, try thresholding it by the adjusted p-vals
-      tempGraph <- graph_from_adjacency_matrix(corrMat, weighted = T, mode = "undirected")
-      tempCommunity <- fastgreedy.community(tempGraph)
-
-      # community object
-      #modularityResults$community <- tempCommunity
-
-      # correlation matrix with transformed values
-      #modularityResults$corrMat <- corrMatrix
-
-      # get coordinate info from selected regions (useful for ggplot)
-      summary <- data.frame(Label = tempCommunity$names,
-                            Membership = tempCommunity$membership,
-                            Modularity = tempCommunity$modularity,
-                            x = labelCoords_parcel[ ,"x"],
-                            y = labelCoords_parcel[ ,"y"],
-                            z = labelCoords_parcel[ ,"z"],
-                            Hemisphere = substring(tempCommunity$names,1,1))
-
-    }
-
-    ## Get the final components
-    modularityResults <- list(Community = tempCommunity,
-                              CorrMatrix = corrMatrix,
-                              TransfMatrix = transfMat,
-                              Summary = summary)
-
-  }
-
-  return(modularityResults)
-
-}
-
-## plot the communities from communityDetection
-plotCommunities <- function(Data = modularityResults, Hemi = "R", type = "Membership", Legends = T, bground=0.1, Cols = c("aquamarine4", "#D9541A")) {
-  # This takes the output from the communityDetection function and plots them on the medial wall (since we're interested in medial now)
-  # type is the name of the column to plot
-  if (Hemi == "R") {
-    # "Medial Right"
-    oneHemi <- Data[grep("R", Data$Hemisphere), ] # from the ROIs
-    oneHemi$Medial <- ifelse(oneHemi$x < 20, "Medial", "Other")
-    medialHemi <- oneHemi[grep("Medial", oneHemi$Medial), ]
-    medialHemi$y <- medialHemi$y * -1
-    oneHemi_all <- labelCoords_vertex[grep("R",labelCoords_vertex$Hemisphere), ] # whole surface
-    oneHemi_all$Medial <- ifelse(oneHemi_all$x < 20, "Medial", "Other")
-    medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
-    medialHemi_all$y <- medialHemi_all$y * -1
-    ggplot() + 
-      geom_point(data = medialHemi, aes_string(x="y", y="z", color = type), show.legend=Legends) +
-      geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=bground) +
-      scale_color_gradient(low = Cols[1], high = Cols[2]) +
-      theme_blank() 
-  } else if (Hemi == "L") {
-    # "Medial Left"
-    oneHemi <- Data[grep("L", Data$Hemisphere), ]
-    oneHemi$Medial <- ifelse(oneHemi$x > -20, "Medial", "Other")
-    medialHemi <- oneHemi[which(oneHemi$Medial=="Medial"), ]
-    oneHemi_all <- labelCoords_vertex[grep("L",labelCoords_vertex$Hemisphere), ] # whole surface
-    oneHemi_all$Medial <- ifelse(oneHemi_all$x > -20, "Medial", "Other")
-    medialHemi_all <- oneHemi_all[grep("Medial", oneHemi_all$Medial), ]
-    ggplot() + 
-      geom_point(data = medialHemi, aes_string(x="y", y="z", color = type), show.legend=Legends) +
-      geom_point(data = medialHemi_all, aes(x=y, y=z), alpha=bground) +
-      scale_color_gradient(low = Cols[1], high = Cols[2]) +
-      theme_blank() 
-  }
 }
@@
 
-# eigen value community detection
-eigenVals <- function(Data = binnedCommunities_p$First) {
-
-  # This will produce a vector of values, ready to be plotted
-  tempGraph <- graph_from_adjacency_matrix(Data$TransfMatrix$tanhZ, mode = "undirected", weighted = T)
-  tempGraph <- laplacian_matrix(tempGraph, normalized=T)
-  tempGraph <- eigen(tempGraph)
-  f.vec <- length(tempGraph$values) - 1
-  tempGraph$binarized <-  as.factor(ifelse(tempGraph$vectors[,f.vec] > 0, 1, 0)) # binarized Fiedler Vector
-
-  return(tempGraph)
-
-}
-
-# Attempt at setting up data for confusion matrices and Jaccard index calculations
-confusionMatrix <- function(partition1 = parcelCommunities[[1]]$Membership, partition2 = parcelCommunities[[1]]$FiedlerBinary) {
-
-  # Divide partitions to evaluate
-  # Usually 2 will be fiedler
-
-  # Check if any partition has 0s (since I binarize the Fiedler vector)
-  if (0 %in% partition1) {
-
-    partition1[grep(0, partition1)] <- 1
-    partition1[grep(1, partition1)] <- 2
-
-  }
-
-  if (0 %in% partition2) {
-
-    partition2[grep(1, partition2)] <- 2   
-    partition2[grep(0, partition2)] <- 1
-
-  }
-
-  # Community sizes
-  commSizes1 <- table(partition1)
-  commSizes2 <- table(partition2)
-
-  # Number of communities per partition
-  nComms1 <- length(commSizes1)
-  nComms2 <- length(commSizes2)
-
-  # Number of vertices
-  n <- length(partition1)
-
-  # Putting together elements of the confusion matrix
-  confMatrix <- matrix(nrow = nComms1,
-                       ncol = nComms2)
-
-  for (i in as.numeric(case.names(commSizes1))) {
-
-    # Vertices belonging to community qX of partition X
-    tempComm1 <- partition1 == i
-
-    for (j in as.numeric(case.names(commSizes2))) {
-
-      # Vertices belonging to community qY of partition Y
-      tempComm2 <- partition2 == j
-
-      # Populate matrix
-      confMatrix[i,j] <- sum(tempComm1 & tempComm2)
-
-    }
-  }
-
-  if (sum(confMatrix) != n) {warning('Sum of the confusion matrix is not equal to number of vertices')}
-
-  return(confMatrix)
-
-}
-
-# Permutation for 2 groups
+## Permutation for 2 groups
 permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){
@@
 
-# Non-parametric Bootstrap for a single group
+## Non-parametric Bootstrap for a single group
 bootstrap <- function(group = 1, statType = mean, B = 5000){
@@
   return(bootStats)
-
-}
-
-# number of times a node changes affiliation in a time series
-flexibility <- function(Data = cbind(1:10, 6:15)) {
-  # Calculation of flexibility based on Garcia et al., 2018  
-  # This function takes in a data frame or matrix in which columns are the community affiliation 
-  # It needs at least 2 colums, although it's pointless for that
-
-  # How many jumps can there be?
-  nJumps <- dim(Data)[2] - 1
-
-  # Matrix to store jumps
-  jumpCount <- matrix(nrow = dim(Data)[1], ncol = nJumps)
-
-  # For each transition, get the which nodes changed affiliation
-  for (jump in seq(nJumps)) {
-
-    jumpCount[, jump] <- Data[, jump] != Data[, jump + 1]
-
-  }
-
-  # How many times did every node jump?
-  totalJumps <- rowSums(jumpCount)
-
-  # Calculate the flexibility per node
-  flexibility <- totalJumps / nJumps
-
-  return(flexibility)
-
-}
-
-# Sliding window
-slidingWindow <- function(subjTS = ROI_timeSeries[[1]], mins = 15, jump = 1, Spectral = T, Modularity = F, ROIs = c("_7m_", vmPFC_labels)) {
-  # This is a fairly specific function. It takes the time series from a participant and preps/runs community detection at each specified time window. 
-  # Returns the summaries for each window (based on communityDetection function)
-  # The selection of a window size is based on the fact that a TR = 0.720s and an hour is 5000 TRs (HCP-based)
-  # Since each subject has a different amount of time points, and all are slightly under 1 hr, I chose to round down the number of window moves to avoid unevenness
-  # 
-  # Parameter definitions:
-  #   
-  #   subjTS: Subject time series. Note: if you want to look at more than vmpfc and 7m, add a parameter for the labels that can be passed to the community detection function
-  # 
-  #   mins: Size of the window that will slide through the data.
-  #   
-  #   jump: Steps (in mins) advanced per slide
-  #   
-  #   Spectral: Whether to compute spectral partitioning as well. Takes significantly longer, but might be more useful for bisections
-  #
-  # Right now this takes ~27 mins per subject to run. Think of ways to improve that.
-
-  # Adapted so it works with the output from getCoords
-  # One wouldn't really apply a full-brain analysis of this sort anyways, too computationally intensive
-  indx <- subjTS$Index
-  subjTS <- subjTS$Coords
-
-  # Window sizing (length)
-  # Think about incorporating custom TRs
-  TS <- dim(subjTS)[2] # time series for the subject
-  WS <- seq(834 * (mins/10)) # window from the first TR up to 834 (~10 mins) times the desired multiplier
-  jump <- 84 * jump # 84 ~ 1 min, times the number of mins that the window moves
-  nJumps <- floor((TS - length(WS)) / jump) # number of jumps to be performed, based on the selected parameters
-
-  ##------- using lapply
-  winData <- mclapply(seq(nJumps), function(x) subjTS[,WS+(jump*(x-1))])
-  commTS <- mclapply(winData, communityDetection, ROIS = "None", Type = "vertex", thresh = T, extras = F)
-  return(commTS)
-
-}
-
-# compare sliding window data to overall communities
-slideCompare <- function(subjData = slideCommunities[[1]], template = vmpfc7mCommunities[[1]], func = "RI", comm = "Spectral") {
-  # This function compares the community partition from each window slide to the one derived from the whole data set
-  # 
-  # Parameter definitions:
-  #   
-  #   subjData: A participant's output from slideCommunities
-  #   
-  #   template: The partition from the whole time series
-  # 
-  #   func: Which function to use for comparing ("RI" for adjusted RI, "VI" for variation of information)
-  # 
-  #   comm: The subject data might contain modularity and spectral partitions. Choose which to use.
-
-  # For storing RIs or VIs
-  tempComparison <- numeric()
-
-  # How many jumps does the original data contain?
-  nJumps <- length(subjData)
-
-  # This loop is technically backwards. I should technically divide by function, then partition method, and then run the window comparisons
-  # It's still really fast, so I won't worry.
-  for (Win in seq(nJumps)) {
-    if (comm == "Modularity") {
-      if (func == "RI") {
-        tempComparison[Win] <- arandi(subjData[[Win]]$Membership, template$Membership, adjust = T)
-      } else if (func == "VI") {
-        tempComparison[Win] <- vi.dist(subjData[[Win]]$Membership, template$Membership)
-      }
-    } else if (comm == "Spectral") {
-      if (func == "RI") {
-        tempComparison[Win] <- arandi(subjData[[Win]]$FiedlerBinary, template$FiedlerBinary, adjust = T)
-      } else if (func == "VI") {
-        tempComparison[Win] <- vi.dist(subjData[[Win]]$FiedlerBinary, template$FiedlerBinary)
-      }
-    }
-  }
-
-  return(tempComparison)
-
-}
-
-# Ensure that all spectral communities associated with 7m (i.e. DN) have the same label value of 1 
-evenSpectral <- function(Data = slideCommunities[[1]][[7]]) {
-
-  # Get only the values for 7m
-  shortData <- Data[grep("_7m_", Data$Label), ]
-
-  # Get 7m's most probable affiliation
-  affil <- mean(as.numeric(shortData$FiedlerBinary)-1)
-
-  # If it is close to 1, then invert the labeling. 
-  # Note: This has no effect on RI or VI, since they are insensitive to actual labeling
-  # This is for visualization purposes only
-  if (affil < 0.5) {
-
-    UD <- as.numeric(Data$FiedlerBinary) - 1
-    Data$FiedlerBinary <- as.factor((UD - 1)^2)
-    Data$FiedlerVec <- Data$FiedlerVec * -1
-
-  }
-
-  return(Data)
 
@@
         for (subj2 in seq(nSubjects)) {
-          indexMatrix[subj,subj2] <- vi.dist(allVecs[, subj], allVecs[, subj2])
+          indexMatrix[subj, subj2] <- vi.dist(allVecs[, subj], allVecs[, subj2])
         }
@@
         for (subj2 in seq(nSubjects)) {
-          indexMatrix[subj,subj2] <- arandi(allVecs[, subj], allVecs[, subj2], adjust = T)
+          indexMatrix[subj, subj2] <- arandi(allVecs[, subj], allVecs[, subj2], adjust = T)
         }
@@
         for (subj2 in seq(nSubjects)) {
-          indexMatrix[subj,subj2] <- cor(allVecs[, subj], allVecs[, subj2], method = "spearman")
+          indexMatrix[subj, subj2] <- cor(allVecs[, subj], allVecs[, subj2], method = "spearman")
         }
@@
 
-``` {r Meta-analysis permutation, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Meta-analysis permutation, echo = FALSE, message = FALSE, cache = TRUE}
 # Glasser parcels contained in Yeo's 17-net DN and limbic networks on the medial cortical wall
@@
 }
-# results!
+
+## results!
 # 25 bilateral (prportion sv = L: 0.42, R: 0.39; proportion DN = L: 0.18, R: 0.16, Chi = L: 12.91, R: 12.83, both p = 0.005)
@@
 
-``` {r Partition comparison: all 2, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: all 2, echo = FALSE, message = FALSE, cache = TRUE}
 ## Community number evaluation (across and within methods)
@@
 
-``` {r Variability per subject: Overall, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Variability per subject: Overall, echo = FALSE, message = FALSE, cache = TRUE}
 # Load files
@@
 
-``` {r Variability per subject: PCC vs mPFC, fig.align="center", fig.width=10, fig.height=4, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Variability per subject: PCC vs mPFC, echo = FALSE, message = FALSE, cache = TRUE}
 ## Check stability for PCC and mPFC separately
@@
 
-``` {r Threshold values}
+``` {r Threshold values, echo = FALSE, message = FALSE}
 # Get a FV threshold for each subject based on mean vertex stability
@@
 
-``` {r Partition comparison: all thresholded, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: all thresholded, echo = FALSE, message = FALSE, cache = TRUE}
 ## Compare partitionings
@@
 
-``` {r Noise Effects: Per-subject Fiedler by R-sqd, fig.align="center", fig.width=3, fig.height=3, fig.cap = "FORMER Figure 13.
-Fiedler vector values are linearly related to the total variance explained by each vertex with respect to the mean DN time series.", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r tSNR evaluation, echo = FALSE, message = FALSE, cache = TRUE}
 ## next get the mean tSNR of PCC and mPFC before/after thresholding
@@
 
-``` {r Partition comparison: halves, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: halves, echo = FALSE, message = FALSE, cache = TRUE}
 # Load data
@@
     Summaries_halves[[count]] <- Summaries_halves[[count]] %>%
-            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
+            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i, 2]) & FiedlerVec < as.numeric(threshDF[i, 3]), 0, FiedlerVec)) %>%
             mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
@@
 
-# # Now recompute so that all network analyses are performed on thresholded data
-# # Select subsection of subjects for plotting the similarity matrices
-# Summaries_halves_plot <- Summaries_halves[selectSubj]
-# subjList_halves_plot <- subjList_halves[selectSubj]
-
-# # Compare all halves with RI (plot only)
-# RI_all_between_halves_plot <- comparePartitions(Data = Summaries_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-# 
-# # Compare PCC and PFC among all subjects (plot only)
-# tempComm_PCC_halves_plot <- lapply(Summaries_halves_plot, "[", i = posteriorIndx, j =)
-# tempComm_PFC_halves_plot <- lapply(Summaries_halves_plot, "[", i = !posteriorIndx, j =)
-# RI_PFC_halves_plot <- comparePartitions(Data = tempComm_PFC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-# RI_PCC_halves_plot <- comparePartitions(Data = tempComm_PCC_halves_plot, Index = "RI", nSubjects = length(Summaries_halves_plot), subjNames = subjList_halves_plot)
-```
-
-``` {r Partition comparison: halves ratios, echo=FALSE, message = FALSE, cache = TRUE}
+```
+
+``` {r Partition comparison: halves ratios, echo = FALSE, message = FALSE, cache = TRUE}
 ## Now compare all possible pairs of subjects (for actual reporting)
@@
 
-``` {r Partition comparison: session similarity matrices, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: session similarity matrices, echo = FALSE, message = FALSE, cache = TRUE}
 # Load data
@@
 
-``` {r Partition comparison: session compare all, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: session compare all, echo = FALSE, message = FALSE, cache = TRUE}
 # Now run comparisons among all subjects (for actual reporting)
@@
 
-``` {r Partition comparison: session ratios, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Partition comparison: session ratios, echo = FALSE, message = FALSE, cache = TRUE}
 ## Brain storming:
@@
 Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A and other networks.
-Our findings therefore complement the initial identification of sub-DN networks by quantifying the systematic variability of its underlying topography in a larger group of people Understanding the interaction of networks A (DN), B, and non-DN should be subject of future examinations.
+Our findings therefore complement the initial identification of sub-DN networks by quantifying the systematic variability of its underlying topography in a larger group of people.
+Understanding the interaction of networks A (DN), B, and non-DN should be subject of future examinations.
 Nevertheless, these qualitative similarities are important, as they collectively suggest that: (1) canonical DN regions can be topographically fractionated into DN and non-DN; (2) the DN community can be further partitioned into two sub-networks; (3) the SP algorithm is a useful and reliable tool for identifying this refined topography in a data-driven way; and (4) the topographic organization of the communities is variable across a large sample of participants, especially in mPFC.
@@
 A similar limitation corresponds to forcing a bipartition of this region.
-While we provide evidence that binarizing this region is adequate, questions remain regarding the potential dynamics that might obscure additional networks (e.g.
+While we provide evidence that binarizing our search space is adequate, questions remain regarding the potential dynamics that might obscure additional networks (e.g.
 the correspondence of subthreshold DN vertices to network B, as mentioned above).
@@
 This is especially true for disorders such as schizophrenia and depression that significantly affect mPFC [@Hiser2018].
-mPFC has also recently become a common target for deep brain stimulation (or TMS) as a depression treatment [CITATION FROM HISER AND KOENIGS], but signal quality issues make imaging this area challenging [CITATION].
+mPFC has also recently become a common target for deep brain stimulation (or TMS) as a depression treatment [@Merkl2013], but signal quality issues make imaging this area challenging [CITATION].
 Being able to produce stable personalized targets in mPFC has the potential to boost our ability to implement and evaluate the effectiveness of these methods.
@@
 
-We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Dan Sussman for initial guidance on community detection and evaluation methods.
+We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Daniel Sussman for initial guidance on community detection and evaluation methods.
 This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI awards N00014-16-1-2832 and N00014-17-1-2304).
 Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
+
+\newpage
 
@@
 ```
-
-\pagebreak
+\bigskip
+
+\newpage
 

### 2019-05-17 cross_correlate.R
cleaning up repo for others to see

@@ -1,99 +1,0 @@
-#!/usr/bin/env Rscript
-
-# cross correlate the mean activity of a subject's two networks
-
-# libraries & functions
-suppressMessages(library(data.table))
-suppressMessages(library(tidyverse))
-
-# simple function to get the mean time series of a community 
-mean.activity <- function(data = NA, mask = NA) {
-  
-  #if (is.na(data)) {stop("You need to input some data")}
-  #if (is.na(mask)) {print("No mask provided, will get the overall mean of all vertices")}
-  
-  temp <- data[mask, ]
-  temp <- colMeans(temp)
-  
-  return(temp)
-  
-}
-
-# Non-parametric Bootstrap for a single group
-bootstrap <- function(group = 1, statType = mean, B = 5000){
-  
-  # prep param
-  bootStats <- rep(0,B)
-  
-  # iterate
-  for(b in 1:B){
-    
-    # wait group
-    x <- sample(group,length(group),replace=T)  
-    bootStats[b] <- statType(x,na.rm = T)
-    
-  }
-  
-  return(bootStats)
-  
-}
-
-
-# assign a subject
-SubjID <- commandArgs(trailingOnly=TRUE)
-write(paste("Cross-correlating communities for subject", SubjID), stdout())
-
-# load session data
-setwd('./time_series')
-temp <- list.files(pattern = paste(SubjID, "_Session*", sep=""))
-timeSeries_sess <- lapply(temp, fread, header=F)
-timeSeries_sess <- lapply(timeSeries_sess, data.matrix)
-
-# load the resulting mapping and produce indices for both nets (thresholded at the group mean of |0.01|)
-map <- read_csv(paste("../For_HCP/", SubjID, "_FiedlerVec_dataforCifti.txt", sep=""), col_names = F, col_types = cols())[[1]]
-map[map == -1] <- 0
-comm1 <- which(map < -0.01) # non DMN
-comm2 <- which(map > 0.01) # DMN
-
-# get the mean of the communities per session
-mComm1 <- lapply(timeSeries_sess, mean.activity, mask = comm1)
-mComm2 <- lapply(timeSeries_sess, mean.activity, mask = comm2)
-
-# figure out how to regress out the autocorrelated data to avoid inflated estimates (residuals from ARX?)
-
-# cross-correlate and save into a tibble to plot
[…]

### 2019-05-17 ccf_eval.R
cleaning up repo for others to see

@@ -1,69 +1,0 @@
-# produce histograms for the peaks of each ccf across subjects
-
-# libraries & functions
-suppressMessages(library(tidyverse))
-
-# load data
-setwd('./cross_correlate/')
-temp <- list.files(pattern = ".csv")
-timeSeries_sess <- lapply(temp, read.csv, header = F)
-nSubj <- length(timeSeries_sess)
-
-# save the lag positions and trim mDFs
-lag <- timeSeries_sess[[1]]$V1
-timeSeries_sess <- lapply(timeSeries_sess, "[", i = , j = 2:ncol(timeSeries_sess[[1]]))
-
-
-## mean correlation per peak
-## this is a very rough estimate, because it disregards the variance within subject
-# average within subject and then between subjects + SE
-mCorr_subj <- do.call(rbind, lapply(timeSeries_sess, rowMeans))
-mCorr_all <- tibble(Lag = lag,
-                    meanCorrelation = colMeans(mCorr_subj),
-                    SE = apply(mCorr_subj, 2, sd) / sqrt(nSubj)) %>%
-             mutate(lower = meanCorrelation - SE,
-                    upper = meanCorrelation + SE)
-
-# plot
-(p <- ggplot(aes(Lag, meanCorrelation), data = mCorr_all) +
-        geom_line(color = "grey50") +
-        geom_point(size = 1.5, color = "grey50") +
-        geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2) +
-        geom_hline(yintercept = 0, linetype = "dashed", color = "#D9541A") +
-        geom_vline(xintercept = 0, linetype = "dashed", color = "#D9541A") +
-        theme_classic())
-
-
-## peak counts
-# get the absolute peak per subject
-peaksAbs <- lapply(timeSeries_sess, function(data) {
-    as.numeric(apply(data, 2, function(x) {which(abs(x) == max(abs(x)))}))
-  }) %>% 
-  lapply(function(x) {lag[x]}) %>%
-  do.call(cbind, .) 
-  
-
-# get the positive peak per subject
-peaksPos <- lapply(timeSeries_sess, function(data) {
-    as.numeric(apply(data, 2, function(x) {which(x == max(x))}))
-  }) %>% 
-  lapply(function(x) {lag[x]}) %>%
-  do.call(cbind, .) 
-
[…]

### 2019-05-17 community_detection.R

@@ -1,5 +1,5 @@
 #!/usr/bin/env Rscript
-SubjID <- commandArgs(trailingOnly=TRUE)
+SubjID <- commandArgs(trailingOnly = TRUE)
 write(paste("Analyzing data for subject", SubjID), stdout())
 
 library(igraph)
@@ -72,11 +72,12 @@ HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID =
   
 }
 
-# if a minimum corr value is desired (otherwise set NA for p-value based thresholding)
+# if a minimum corr value is desired prior to clustering (otherwise set NA for p-value based thresholding)
 corrThresh <- NA
 
-# ROIs
-yeoLbls <- c("L_25_ROI",
+
+# ROIs used on the paper
+ROI <- c("L_25_ROI",
              "L_OFC_ROI",
              "L_10v_ROI",
              "R_25_ROI",
@@ -115,72 +116,16 @@ yeoLbls <- c("L_25_ROI",
              "L_10d_ROI",
              "R_s32_ROI",
              "R_9a_ROI",
-             "L_PCV_ROI",
-             "L_POS1_ROI", # from this one on, it's Lauren D's extended space
-             "L_PreS_ROI",
-             "L_H_ROI",
-             "L_POS2_ROI",
-             "L_7Pm_ROI",
-             "L_PGs_ROI",
-             "L_PGi_ROI",
-             "L_TPOJ2_ROI",
-             "L_TPOJ3_ROI",
-             "L_PGp_ROI",
-             "L_TE2a_ROI",
-             "L_MST_ROI",
-             "L_MT_ROI",
-             "L_9-46d_ROI",
-             "L_8Ad_ROI",
-             "L_46_ROI",
-             "R_PGp_ROI",
-             "R_PGs_ROI",
-             "R_PGi_ROI",
-             "R_TPOJ3_ROI",
-             "R_TPOJ2_ROI",
-             "R_MST_ROI",
-             "R_MT_ROI",
-             "R_TE2a_ROI",
-             "R_TE1a_ROI",
-             "R_9-46d_ROI",
-             "R_46_ROI",
-             "R_8Ad_ROI",
-             "R_POS1_ROI",
-             "R_POS2_ROI",
-             "R_7Pm_ROI",
-             "L_23c_ROI",
-             "R_23c_ROI",
-             "R_PreS_ROI",
-             "R_H_ROI",
-             "L_STSdp_ROI",
-             "L_STSvp_ROI",
[…]

### 2019-05-17 ciftitoText.sh
modified meta-analysis script and added data for it (test)

@@ -1,34 +1,0 @@
-#!bin/bash/
-
-# This will produce text files for each subject's CIFTI within a directory
-# First input to the function should be the general filename to follow (e.g. .MyelinMap_BC.32k_fs_LR.dscalar.nii)
-# Second should be the suffix of the generated file (e.g. myelin)
-dataName=$1
-dataType=$2
-
-# echo *${dataName}
-# echo $dataType
-
-# Turn each file into a text file
-for dataFile in *${dataName} ; do
-
-  fname=$(echo $dataFile | cut -f 1 -d '.')
-
-  echo $fname >> ${dataType}_subjList.txt
-
-  wb_command -cifti-convert -to-text $dataFile ${fname}_${dataType}.txt
-
-done
-
-# And combine
-# Note: this creates a tab-separated file.
-
-# Increase the upper limit of open files if necessary (for paste)
-nFiles=$(ls -l | wc -l)
-Limit=2
-if [ "$nFiles" -gt 500 ] ; then
-  ulimit -Hn 500 # The hard limit
-  ulimit -Sn 500 # The soft limit
-fi
-
-paste *_${dataType}.txt >> ${dataType}All.txt

### 2019-05-17 prepSubj.sh

@@ -1,37 +1,0 @@
-#!bin/bash/
-
-subj=$1
-
-echo "Preparing data for subject ${subj}"
-
-# Copy data
-cp /projectnb/connectomedb/Q6/${subj}/MNINonLinear/fsaverage_LR32k/${subj}.corrThickness.32k_fs_LR.dscalar.nii /restricted/projectnb/cd-lab/Claudio/Community/
-cp /projectnb/connectomedb/Q6/${subj}/MNINonLinear/fsaverage_LR32k/${subj}.curvature.32k_fs_LR.dscalar.nii /restricted/projectnb/cd-lab/Claudio/Community/
-cp /projectnb/connectomedb/Q6/${subj}/MNINonLinear/fsaverage_LR32k/${subj}.MyelinMap_BC.32k_fs_LR.dscalar.nii /restricted/projectnb/cd-lab/Claudio/Community/
-
-cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/concatenated_rfMRI/rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii
-cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/rfMRI_REST1_LR/rfMRI_REST1_LR_Atlas_hp2000_clean.int.bpf.residMGSR.censor.demean.dtseries.nii /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST1_LR.dtseries.nii
-cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/rfMRI_REST1_RL/rfMRI_REST1_RL_Atlas_hp2000_clean.int.bpf.residMGSR.censor.demean.dtseries.nii /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST1_RL.dtseries.nii
-cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/rfMRI_REST2_LR/rfMRI_REST2_LR_Atlas_hp2000_clean.int.bpf.residMGSR.censor.demean.dtseries.nii /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST2_LR.dtseries.nii
[…]

### 2019-05-17 view.sh

@@ -1,4 +1,0 @@
-#!/bin/bash
-
-freeview -f $SUBJECTS_DIR/fsaverage/surf/lh.inflated:annot=lh.HCP_MMP1p0.annot:overlay=DECvsDMN_lh_overlay.gii:overlay=DECvsNEG_lh_overlay.gii:overlay=DECvsPOS_lh_overlay.gii:overlay=DMNvsNEG_lh_overlay.gii:overlay=DMNvsPOS_lh_overlay.gii:overlay=NEGvsPOS_lh_overlay.gii \
-            $SUBJECTS_DIR/fsaverage/surf/rh.inflated:annot=rh.HCP_MMP1p0.annot:overlay=DECvsDMN_rh_overlay.gii:overlay=DECvsNEG_rh_overlay.gii:overlay=DECvsPOS_rh_overlay.gii:overlay=DMNvsNEG_rh_overlay.gii:overlay=DMNvsPOS_rh_overlay.gii:overlay=NEGvsPOS_rh_overlay.gii

### 2019-05-17 createCiftifromVector.sh
modified meta-analysis script and added data for it (test)

@@ -1,9 +1,0 @@
-#!bin/bash/
-
-for dataFile in *dataforCifti.txt ; do
-
-  fname=$(echo $dataFile | cut -f 1,2 -d '_')
-
-  wb_command -cifti-convert -from-text ${dataFile} 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii ${fname}.dscalar.nii
-
-done

### 2019-05-17 readTxt.py

@@ -1,49 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-
-import os
-import sys
-
-# get the file name from bash input
-if os.environ.get('filename') == None:
-    print "No outside input from bash"
-    filename = raw_input("Enter file name (without .txt): ")
-else:
-    print "Input from bash"
-    filename = os.environ['filename']
-fname = filename + ".txt"
-
-# make target directory
-if not os.path.exists(filename):
-    os.makedirs(filename)
-
-# open files to read & write
-textFile = open(fname,'rU')
-textArray = textFile.readlines()
-totalRows = len(textArray)
-
-# change dir to store output
-os.chdir(filename)
-
-studyNumber = 1
-
-for i in range(totalRows):
-    if ('//' in textArray[i]) or (textArray[i] == '\n'):
-        # if you want to include all of the coordinates into one file:
-        # just use continue and open (coordFile, 'w') outside of the loop
-        if ('Subjects=' not in textArray[i]) and ('Reference=' not in textArray[i]) and (textArray[i] != '\n'):
-            splitting = textArray[i].split(' ')[1]
-            fileName = 'coords_%s_%s.txt' % (studyNumber,splitting[:-1])
-            studyNumber += 1
-            coordFile = open(fileName,'w')
-        else:
-            continue
-    else:
-
-        print textArray[i]
-        num = round(textArray[i])
-        print num
-        coordFile.write(textArray[i])
-
-coordFile.close
-textFile.close

### 2019-05-17 HCP_labelConn.sh
modified meta-analysis script and added data for it (test)

@@ -1,60 +1,0 @@
-#!bin/bash/
-
-# This is based on Sean's suggestions (see his NeuroImage paper, 2017)
-# First, grab an MGSR dtseries.nii data file from an HCP subject (from SCC). This file contains the residuals from regressing the mean greyordinate value from the series.
-# Second, get the mean of the timeseries for a given parcel using 'Q1-Q6_RelatedParcellation210.CorticalAreas_dil_Colors.32k_fs_LR.dlabel.nii' from Glasser's paper
-# Note: using -cifti-convert -to-text on the resulting file will generate a csv with the mean time series (column) for each parcel (row, N=360).
-#       This can be used to sed-vertex correlations, once the vertex index for columns have been sorted out
-# Third, correlate the parcellated ptseries file. This will create a 360x360 pconn file.
-# Fourth, convert the pconn file to text (as in the note) to get the 360x360 correlation matrix as a csv
-# The advantage here is that the RS are well preprocessed, allowing us to bypass the merging of the 4 RS scans.
-
-dataName=$1
-
-# Parcellate
-for dataFile in *${dataName} ; do
-
-  filename=$(echo $dataFile | cut -f 1 -d '_')
-
-  echo "Working on ${filename}"
-
-  # wb_command -cifti-parcellate ${filename}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii \
-  #                               Q1-Q6_RelatedParcellation210.CorticalAreas_dil_Colors.32k_fs_LR.dlabel.nii \
-  #                               COLUMN ${filename}.ptseries.nii -method MEAN
-
-  echo "Parcellating time series"
-  wb_command -cifti-parcellate ${dataFile} \
-                                Q1-Q6_RelatedParcellation210.CorticalAreas_dil_Colors.32k_fs_LR.dlabel.nii \
-                                COLUMN ${filename}.ptseries.nii -method MEAN
-
-  # Get each parcel's mean timeseries
-  wb_command -cifti-convert -to-text ${filename}.ptseries.nii ${filename}_ptSeries.txt
-
-  # Get the overall time series
-  echo "Storing the whole time series"
-  wb_command -cifti-convert -to-text ${dataFile} ${filename}_timeSeries.csv
-
-done
-
-# series=$(expr $series + 1)
-
-# done
-
-
-# z-score
-
-# average across participants
-
-
-##------ Notes (before 2/19/18)
-
[…]

### 2019-05-17 chiPerVertex.sh

@@ -1,57 +1,0 @@
-#!/bin/bash
-
-# This script takes the summary of the permutation analysis, and assigns the corresponding (signed) chi squared value that came from the comparison between conditions.
-
-# loop through all summary files
-for comparison in *summary.csv ; do
-
-    fname=$(echo $comparison | cut -d '_' -f 1)
-    touch ${fname}_lh_overlay.csv
-    touch ${fname}_rh_overlay.csv
-
-    echo "Working on ${fname} lh..."
-
-    # Go through each label from Glasser and insert its chi2 value on the respective vertex
-    # Change the label system if needed (i.e. DMN-space analysis).
-    while IFS=$'\t' read -r -a label ; do
-
-        if [ -z "$label" ] ; then
-            #echo "Cell is empty"
-            echo 0 >> ${fname}_lh_overlay.csv
-            #echo 0 >> check.csv
-        elif [[ $(grep "$label" ${fname}_summary.csv) != "" ]] ; then
-            #echo "$label in summary"
-            temp=$(grep $label ${fname}_summary.csv)
-            count=(${temp//,/ })
-            echo ${count[1]} >> ${fname}_lh_overlay.csv
-        else
-            #echo "Label not in summary"
-            echo 0 >> ${fname}_lh_overlay.csv
-            #echo 0 >> check.csv
-        fi
-
-    done < Glasser_labels_lh.csv
-
-    echo "Working on ${fname} rh..."
-
-    while IFS=$'\t' read -r -a label ; do
-
-        if [ -z "$label" ] ; then
-            #echo "Cell is empty"
-            echo 0 >> ${dirName}_rh_overlay.csv
-            #echo 0 >> check.csv
-        elif [[ $(grep "$label" ${fname}_summary.csv) != "" ]] ; then
-            #echo "$label in summary"
-            temp=$(grep $label ${fname}_summary.csv)
-            count=(${temp//,/ })
-            echo ${count[1]} >> ${fname}_rh_overlay.csv
-            #echo ${count[0]} >> check.csv
-        else
-            #echo "Label not in summary"
-            echo 0 >> ${fname}_rh_overlay.csv
-            #echo 0 >> check.csv
-        fi
-
-    done < Glasser_labels_rh.csv
-
-  done

### 2019-05-17 kmeans.R

@@ -1,165 +1,0 @@
-#!/usr/bin/env Rscript
-SubjID <- 101006
-nClusts <- 3
-thresh <- T
-
-library(data.table)
-
-# To store files ready to be converted to CIFTI
-HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0, n = 12){
-  
-  nVertices <- 59412
-  tempVec <- rep(padding, nVertices)
-  temp <- grep(MOI, colnames(Data))
-  tempVec[Data$Vertex] <- Data[[temp]]
-  write.table(file = paste(SubjID,'_Kmeans_', n, 'clusters_dataforCifti.txt', sep=""), tempVec, row.names = F, col.names = F, dec = ".")
-  
-}
-
-# load data
-setwd('./tseries')
-temp <- list.files(pattern = paste(SubjID, "_Session*", sep=""))
-timeSeries_sess <- lapply(temp, fread, header=F)
-timeSeries_sess <- lapply(timeSeries_sess, data.matrix)
-
-tseries <- do.call(cbind, timeSeries_sess)
-
-setwd('../BB_comparison/')
-
-if (thresh) {
-  # ROIs
-  yeoLbls <- c("L_25_ROI",
-               "L_OFC_ROI",
-               "L_10v_ROI",
-               "R_25_ROI",
-               "R_OFC_ROI",
-               "R_10v_ROI",
-               "L_s32_ROI",
-               "L_RSC_ROI",
-               "R_RSC_ROI",
-               "R_23d_ROI",
-               "R_d23ab_ROI",
-               "R_31a_ROI",
-               "R_31pv_ROI",
-               "R_31pd_ROI",
-               "R_7m_ROI",
-               "R_v23ab_ROI",
-               "R_p24_ROI",
-               "R_d32_ROI",
-               "R_9m_ROI",
-               "R_p32_ROI",
-               "R_a24_ROI",
-               "R_10r_ROI",
-               "R_10d_ROI",
-               "L_23d_ROI",
-               "L_d23ab_RO",
-               "L_31a_ROI",
-               "L_31pv_ROI",
-               "L_31pd_ROI",
-               "L_7m_ROI",
-               "L_v23ab_ROI",
-               "L_p24_ROI",
-               "L_d32_ROI",
-               "L_9m_ROI",
-               "L_p32_ROI",
-               "L_a24_ROI",
-               "L_10r_ROI",
-               "L_10d_ROI",
[…]

### 2019-05-17 labelResample.sh

@@ -1,36 +1,0 @@
-#!/bin/bash
-
-# 1. To transform the label data from Glasser et al. (2016) into fsaverage space:
-# a. download the following dataset: http://brainvis.wustl.edu/workbench/standard_mesh_atlases.zip
-#    steps from: https://wiki.humanconnectome.org/download/attachments/63078513/Resampling-FreeSurfer-HCP.pdf?version=1&modificationDate=1471988055831&api=v2
-#    you also need to grab the Glasser label files
-
-# b. separate the .dlabel.nii file into .gii for both hemispheres:
-wb_command -cifti-separate Q1-Q6_RelatedParcellation210.CorticalAreas_dil_Final_Final_Areas_Group_Colors.32k_fs_LR.dlabel.nii COLUMN  \
-                           -label CORTEX_LEFT Glasser_pre_labels_lh.label.gii  \
-                           -label CORTEX_RIGHT Glasser_pre_labels_rh.label.gii  \
-
-# c. resample the labels into fsaverage space (twice, one for each hemisphere):
-wb_command -label-resample Glasser_pre_labels_lh.label.gii  \
-                           $HOME/Documents/HBM/Glasser_et_al_2016_HCP_MMP1.0_RVVG/standard_mesh_atlases/resample_fsaverage/fs_LR-deformed_to-fsaverage.L.sphere.32k_fs_LR.surf.gii  \
-                           $HOME/Documents/HBM/Glasser_et_al_2016_HCP_MMP1.0_RVVG/standard_mesh_atlases/resample_fsaverage/fsaverage6_std_sphere.L.41k_fsavg_L.surf.gii \
-                           ADAP_BARY_AREA \
-                           Glasser_post_labels_lh.label.gii  \
-                           -area-metrics  \
-                           $HOME/Documents/HBM/Glasser_et_al_2016_HCP_MMP1.0_RVVG/standard_mesh_atlases/resample_fsaverage/fs_LR.L.midthickness_va_avg.32k_fs_LR.shape.gii  \
-                           $HOME/Documents/HBM/Glasser_et_al_2016_HCP_MMP1.0_RVVG/standard_mesh_atlases/resample_fsaverage/fsaverage6.L.midthickness_va_avg.41k_fsavg_L.shape.gii
[…]

### 2019-05-17 runGraph.sh

@@ -1,33 +1,0 @@
-#!/bin/bash -l
-
-# load modules within SCC
-module load R/3.4.3
-module list
-
-SubjID=$1
-
-# Setups
-#$ -l mem_total=48G
-#$ -pe omp 16
-#$ -j y
-
-# Prep subject
-sh prepSubj.sh $SubjID
-
-# Run the R script that calculates community detection for a set of participants
-Rscript graphAnalysis_solo.R $SubjID
-
-# Clean up
-rm -f ${SubjID}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii
-rm -f ${SubjID}_rfMRI_REST1_LR.dtseries.nii
-rm -f ${SubjID}_rfMRI_REST1_RL.dtseries.nii
-rm -f ${SubjID}_rfMRI_REST2_LR.dtseries.nii
-rm -f ${SubjID}_rfMRI_REST2_RL.dtseries.nii
-rm -f ${SubjID}.ptseries.nii
-rm -f ${SubjID}.corrThickness.32k_fs_LR.dscalar.nii
-rm -f ${SubjID}.curvature.32k_fs_LR.dscalar.nii
-rm -f ${SubjID}.MyelinMap_BC.32k_fs_LR.dscalar.nii
-
-mv ${SubjID}_myelin.txt ./MyelinMaps
-mv ${SubjID}_curvature.txt ./Curvature
-mv ${SubjID}_thickness.txt ./Thickness

### 2019-05-17 spreadCoords.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+
+# use this to transform the initial file with the DMN/SV corpus into .txt per study
+import os
+import sys
+
+# get the file name from bash input
+if os.environ.get('filename') == None:
+    print "No outside input from bash"
+    filename = raw_input("Enter file name (without .txt): ")
+else:
+    print "Input from bash"
+    filename = os.environ['filename']
+fname = filename + ".txt"
+
+# make target directory
+if not os.path.exists(filename):
+    os.makedirs(filename)
+
+# open files to read & write
+textFile = open(fname,'rU')
+textArray = textFile.readlines()
+totalRows = len(textArray)
+
+# change dir to store output
+os.chdir(filename)
+
+studyNumber = 1
+
+for i in range(totalRows):
+    if ('//' in textArray[i]) or (textArray[i] == '\n'):
+        # if you want to include all of the coordinates into one file:
+        # just use continue and open (coordFile, 'w') outside of the loop
+        if ('Subjects=' not in textArray[i]) and ('Reference=' not in textArray[i]) and (textArray[i] != '\n'):
+            splitting = textArray[i].split(' ')[1]
+            fileName = 'coords_%s_%s.txt' % (studyNumber,splitting[:-1])
+            studyNumber += 1
+            coordFile = open(fileName,'w')
+        else:
+            continue
+    else:
+
+        print textArray[i]
+        num = round(textArray[i])
+        print num
+        coordFile.write(textArray[i])
+
+coordFile.close
+textFile.close

### 2019-05-17 BB_makenets.sh
modified meta-analysis script and added data for it (test)

@@ -1,24 +1,0 @@
-#!/bin/bash -l
-
-# grab a seed from a dconn.nii file, produce its dense scalar form, then transform to txt
-# using cifti math produces unreadable dscalars (it assumes they are dconns), which is why I add txt transforms
-
-subj=$1
-rowA=$2 # row index for net A
-rowB=$3 # row index for net B
-
-# get seed for both nets
-wb_command -cifti-math 'x' ${subj}_A.dscalar.nii -var x ${subj}_corr.dconn.nii -select 1 $rowA
-wb_command -cifti-math 'x' ${subj}_B.dscalar.nii -var x ${subj}_corr.dconn.nii -select 1 $rowB
-
-# combine
-wb_command -cifti-math 'B - A' ${subj}_temp.dscalar.nii -var A ${subj}_A.dscalar.nii -var B ${subj}_B.dscalar.nii 
-
-# to text
-wb_command -cifti-convert -to-text ${subj}_temp.dscalar.nii ${subj}_combined.txt
-
-# from text
-wb_command -cifti-convert -from-text ${subj}_combined.txt sample.dscalar.nii ${subj}_combined.dscalar.nii
-
-rm -f ${subj}_temp.dscalar.nii
-rm -f ${subj}_combined.txt

### 2019-05-17 batch_makeIM.sh

@@ -1,402 +1,0 @@
-#!/bin/bash -l
-
-# I know that using a Python sub-script for such an easy task was dumb, but it
-# was the fastest and most comfortable option at the time.
-# IMPORTANT: Make sure you run vertexLabel.m on the HCP annotation file (FreeSurfer only) before running this script. Step 5 depends on the output.
-
-# load modules within SCC
-module load afni/2017.01.29.1818_openmp
-module load fsl
-module load freesurfer/6.0
-module load connectomewb/1.2.3
-module list
-
-# job name
-#$ -N I_POS
-
-echo "TRANSFORMING METANALYSIS COORDINATES INTO CORTICAL PARCELS (Glasser et al., 2016)"
-
-# file name will become a directory
-# echo "Enter file name (without .txt): "
-# read filename
-filename="I_POS"
-export filename
-echo $filename
-
-
-# create dirs, including those to make FreeSurfer commands compatible
-# important for step 7 and annot2label transformation
-mkdir -p $PWD/$filename/results
-mkdir -p $PWD/Glasser/surf
-mkdir -p $PWD/Glasser/label/lh
-mkdir -p $PWD/Glasser/label/rh
-
-if [ ! -f ./Glasser/label/lh.HCP_MMP1p0.annot ] ; then
-    cp *.HCP_MMP1p0.annot ./Glasser/label # make sure to do it for both hemis, I'm using Sean's HCP annotation file
-    cp $SUBJECTS_DIR/fsaverage/surf/*h.white ./Glasser/surf/
-fi
-if [ "$(ls -A ./Glasser/label/lh)" ] ; then
-    echo
-    echo "HCP labels exist..."
-    echo
-else
-    echo
-    echo "Creating HCP label files from HCP annot..."
-    echo
-     # --border <fname>.gii creates a single overlay of binary borders
-    mri_annotation2label --subject Glasser --hemi lh --sd $PWD --annotation HCP_MMP1p0 --outdir ./Glasser/label/lh
-    mri_annotation2label --subject Glasser --hemi rh --sd $PWD --annotation HCP_MMP1p0 --outdir ./Glasser/label/rh
-fi
-
-# create study-specific text files in python
-#python readTxt.py
-
-# copy MNI template to new dir and cd to it to create spheres
-if [ ! -f ./$filename/MNI152_T1_1mm_brain.nii.gz  ] ; then
[…]

### 2019-05-17 createAtlas.sh

@@ -1,28 +1,0 @@
-#!/bin/bash -l
-
-# this function will take a set of labels (from Glasser, .csv) and create an atlas that contains only those ROIs
-# no statistics are computed, it's just a visualization mask
-
-dirName=BBC
-
-#function createAtlas () {
-echo "#!ascii label, from condition ${dirName}" >> ${dirName}_lh_atlas.label
-echo "#!ascii label, from ondition ${dirName}" >> ${dirName}_rh_atlas.label
-totalLeft=0
-totalRight=0
-while IFS=$'\t' read -r -a label ; do
-  	if [[ $label == L* ]] ; then
-			totalLines=$(expr 2 + $(awk 'NR == 2 {print $1}' $HOME/fMRI/Glasser/label/lh/lh.${label}.label))
-    			totalLeft=$(expr $totalLines + $totalLeft)
-    			sed -n 3,${totalLines}p $HOME/fMRI/Glasser/label/lh/lh.${label}.label >> ${dirName}_lh_atlas.label
-    	else
-    			totalLines=$(expr 2 + $(awk 'NR == 2 {print $1}' $HOME/fMRI/Glasser/label/rh/rh.${label}.label))
-    			totalRight=$(expr $totalLines + $totalRight)
-    			sed -n 3,${totalLines}p $HOME/fMRI/Glasser/label/rh/rh.${label}.label >> ${dirName}_rh_atlas.label
-    	fi
-done < ${dirName}_threshLabels.csv
-sed -i "2i "$totalLeft"" ${dirName}_lh_atlas.label
-sed -i "2i "$totalRight"" ${dirName}_rh_atlas.label
-#}
-
-view $dirName

### 2019-05-17 metacoordsVol2Surf.sh

@@ -1,0 +1,316 @@
+#!/bin/bash -l
+
+# This script will take volumetric coordinates from either DN or SV literatures and project them to fsaverage
+# USE: `sh metacoordsVol2Surf.sh metacoordsDN` (or metacoordsPOS for subjective value)
+# IMPORTANT: THIS PROCESS TAKES TIME, ESPECIALLY WHEN PRODUCING SPHERES.
+
+echo "TRANSFORMING METANALYSIS COORDINATES INTO CORTICAL PARCELS (Glasser et al., 2016)"
+
+# file name will become a directory
+# read filename
+filename=$1 
+echo $filename
+
+
+# create dirs, including those to make FreeSurfer commands compatible
+# important for step 7 and annot2label transformation
+mkdir -p $PWD/$filename/results
+mkdir -p $PWD/Glasser/surf
+mkdir -p $PWD/Glasser/label/lh
+mkdir -p $PWD/Glasser/label/rh
+
+if [ ! -f ./Glasser/label/lh.HCP_MMP1p0.annot ] ; then
+    cp ./Basic_files/*.HCP_MMP1p0.annot ./Glasser/label # make sure to do it for both hemis, I'm using Sean's HCP annotation file
+    cp $SUBJECTS_DIR/fsaverage/surf/*h.white ./Glasser/surf/
+fi
+if [ "$(ls -A ./Glasser/label/lh)" ] ; then
+    echo
+    echo "HCP labels exist..."
+    echo
+else
+    echo
+    echo "Creating HCP label files from HCP annot..."
+    echo
+     # --border <fname>.gii creates a single overlay of binary borders
+    mri_annotation2label --subject Glasser --hemi lh --sd $PWD --annotation HCP_MMP1p0 --outdir ./Glasser/label/lh
+    mri_annotation2label --subject Glasser --hemi rh --sd $PWD --annotation HCP_MMP1p0 --outdir ./Glasser/label/rh
+fi
+
+# copy MNI template to new dir and cd to it to create spheres
+if [ ! -f ./$filename/MNI152_T1_1mm_brain.nii.gz  ] ; then
+    cp ./Basic_files/MNI152_T1_1mm_brain.nii.gz ./$filename
+    cd ./$filename
+else
+    cd ./$filename
+fi
+
+# parameters
+sphereSze=10 ; # size of the sphere to be projected to the cortical surface
[…]

### 2019-05-17 vector2Cifti.sh

@@ -1,0 +1,12 @@
+#!bin/bash/
+
+# this will take ALL the outputs from HCPOut (from communityDetection.R) and turn them into CIFTIs
+# these can then be viewed on wb_command with a 60k surface model from the HCP
+
+for dataFile in *dataforCifti.txt ; do
+
+  fname=$(echo $dataFile | cut -f 1,2 -d '_')
+
+  wb_command -cifti-convert -from-text ${dataFile} ./Basic_files/testSubj.dscalar.nii ${fname}.dscalar.nii
+
+done

### 2019-05-17 countCors.R
modified meta-analysis script and added data for it (test)

@@ -1,104 +1,0 @@
-# simple script to count the number of pos/neg correlations that go into SP
-# this can be used to compute densities later on
-
-library(data.table)
-
-# fisher r to z transformation, plus p-value adjustment with FDR
-fisherTanh <- function(Data = padjMatrix){
-  
-  transformed <- list()
-  
-  # tanh
-  transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
-  
-  # p-vals
-  if (is.matrix(Data)) {
-    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
-    n <- dim(Data)[1]
-  } else if (is.vector(Data)) {
-    z.vec <- transformed$tanhZ
-    n <- length(Data)
-  }
-  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n - 3)), lower.tail = F) # no lower tail, but absolute Zs = two tailed
-  
-  # adjust pvals
-  transformed$adjustPvals <- p.adjust(transformed$pvals, "BH")
-  
-  if (is.matrix(Data)) {
-    # get pvals and their adjustment into a symetric matrix form
-    # regular
-    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
-    tempMat[upper.tri(tempMat)] <- transformed$pvals
-    tempMat[lower.tri(tempMat)] <- transformed$pvals
-    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
-    transformed$pvals <- tempMat
-    
-    # adjusted
-    tempMat <- matrix(0, dim(Data)[1], dim(Data)[2])
-    tempMat[upper.tri(tempMat)] <- transformed$adjustPvals
-    tempMat[lower.tri(tempMat)] <- transformed$adjustPvals
-    dimnames(tempMat) <- list(rownames(Data), rownames(Data))
-    transformed$adjustPvals <- tempMat
-  }
-  
-  return(transformed)
-  
-}
-
-# get filenames
-files <- dir(pattern = "_timeSeries.csv")
-subjList <- sapply(files, substring, first = 1, last = 6)
-
-# get sample summary file to get vertex indices
-vertexIndex <- read.csv('./Analyzed/Summary/100307_finalSummary.csv')
-vertexIndex <- vertexIndex$Vertex
-
-# vectors to store correlations and other stuff Joe asked for later on
-nTR <- as.numeric()
-neg <- as.numeric()
[…]

### 2019-05-17 Manuscript.Rmd
added meta-analysis results file so that they work with manuscript.rmd

@@
 # Use table(unlist(list)) to get the counts in that case
-setwd('./POS')
+setwd('./metaresultsPOS')
 templist <- dir()
@@
 
-setwd('../DN/')
+setwd('../metaresultsDN/')
 templist <- dir()

### 2019-05-17 spreadCoords.py
added meta-analysis results file so that they work with manuscript.rmd

@@ -1,50 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-
-# use this to transform the initial file with the DMN/SV corpus into .txt per study
-import os
-import sys
-
-# get the file name from bash input
-if os.environ.get('filename') == None:
-    print "No outside input from bash"
-    filename = raw_input("Enter file name (without .txt): ")
-else:
-    print "Input from bash"
-    filename = os.environ['filename']
-fname = filename + ".txt"
-
-# make target directory
-if not os.path.exists(filename):
-    os.makedirs(filename)
-
-# open files to read & write
-textFile = open(fname,'rU')
-textArray = textFile.readlines()
-totalRows = len(textArray)
-
-# change dir to store output
-os.chdir(filename)
-
-studyNumber = 1
-
-for i in range(totalRows):
-    if ('//' in textArray[i]) or (textArray[i] == '\n'):
-        # if you want to include all of the coordinates into one file:
-        # just use continue and open (coordFile, 'w') outside of the loop
-        if ('Subjects=' not in textArray[i]) and ('Reference=' not in textArray[i]) and (textArray[i] != '\n'):
-            splitting = textArray[i].split(' ')[1]
-            fileName = 'coords_%s_%s.txt' % (studyNumber,splitting[:-1])
-            studyNumber += 1
-            coordFile = open(fileName,'w')
-        else:
-            continue
-    else:
-
-        print textArray[i]
-        num = round(textArray[i])
-        print num
-        coordFile.write(textArray[i])
-
-coordFile.close
-textFile.close

### 2019-05-20 graphAnalysis.R
apa knitr style and fixed graphAnalysis. Ready to go.

@@ -77,7 +77,7 @@ fisherTanh <- function(Data = padjMatrix, preThresh = NA){
 
 
 # get ROI coords & index
-getCoords <- function(Labels = DMN_labels, Coords = labelCoords_parcel, TimeSeries = FALSE){
+getCoords <- function(Labels, Coords, TimeSeries = FALSE){
   # The point here is to reduce the summary dframes from community detection to show only ROIs
   # Should work for extracting any label-indexed dframe though
   # I wanted to also get the index in case I want to extract specific rows from parcel/vertex coord dframes
@@ -105,7 +105,7 @@ getCoords <- function(Labels = DMN_labels, Coords = labelCoords_parcel, TimeSeri
 
 
 # Run community detection on ROIs
-communityDetection <- function(Data = NA, ROIS = "None", modularity = T, extras = T) {
+communityDetection <- function(Data = NA, ROIS = "None", modularity = T, extras = T, indx = NA) {
   # This function relies on having the timeSeries data uploaded, and labelCoords_vertex as the row names for ROI selection
   # Extras dictates whether the community object + correlation matrix should also be extracted
   #
@@ -118,6 +118,8 @@ communityDetection <- function(Data = NA, ROIS = "None", modularity = T, extras 
   #   modularity: TRUE if you would like to also run the fastgreedy modularity community detection
   #
   #   extras: if you want to return the original and transformed correlation matrices  
+  #
+  #   indx: if the ROI data has already been selected, input the vertex index (given by getCoords) or any index you would like for a matrix axis
 
   if (ROIS != "None") {
     # To store the vertex indices corresponding to the ROIs
@@ -131,7 +133,7 @@ communityDetection <- function(Data = NA, ROIS = "None", modularity = T, extras 
     # reduce time series to only include ROIs
     nVerts <- length(indx)
     Data <- Data[indx, ]
-  }
+  } 
   
   # This used to be done with the for loop, but it was too slow. cor() speeds up the process by a lot
   corrMat <- cor(t(Data))
@@ -185,11 +187,11 @@ communityDetection <- function(Data = NA, ROIS = "None", modularity = T, extras 
   } else {
     # put summary together
     summary <- data.frame(Vertex = indx,
[…]

### 2019-05-21 Manuscript.Rmd
working on (hopefully) Joe and Sean's last comments in parallel. Up to network defs.

@@
 ---
-title: 'Individual heterogeneity in the functional network topography of the medial prefrontal cortex'
+title: 'Individual heterogeneity in the functional network topography of medial prefrontal cortex'
 author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
@@
     - \usepackage{float}
+
+# reset counter for supplemental figures/tables (PDF ONLY)
+\newcommand{\beginsupplement}{
+  \setcounter{table}{0}  
+  \renewcommand{\thetable}{S\arabic{table}} 
+  \setcounter{figure}{0} 
+  \renewcommand{\thefigure}{S\arabic{figure}}
+}
 ---
@@
 Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
-These regions are also implicated in a set of functions associated with the default-mode network (DN).
+Both mPFC and PCC are also among the regions implicated in a set of functions associated with the default network (DN).
 DN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Greicius2003; @Fox2005; @Yeo2011].
@@
 Within PCC and adjacent precuneus, a more posterior subregion appears DN-specific, whereas a more anterior subregion is implicated in both effects.
-One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within the distributed brain systems that subserve valuation and DN effects.
-The potential existence of common brain nodes has prompted theories positing psychological overlap between valuation and DN-related processes.
+One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within partially overlapping distributed brain systems that subserve valuation and DN effects.
+This colocalization has prompted theories that the psychological constructs of valuation and DN-related processes share common features.
 For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Acikalin2017; @Clithero2014; @Northoff2012; @Reddan2018].
@@
   However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity.
-A recognized limitation of group averaging and meta-analysis is that individual-specific functional subdivisions can be blurred and overlooked [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], potentially exaggerating the degree of overlap across domains.
-This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013].
+A recognized limitation of group averaging and meta-analysis is that the functional topography of the individual can be misaligned and blurred [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains.
+This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013].
 An alternative approach is to focus on analyses at the individual-participant level.
@@
 Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019].
-It is therefore possible that the diffuse overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
-An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC.
-
-  A useful way to characterize individual-specific brain organization is to examine patterns of resting-state functional connectivity (rsFC; i.e.
-BOLD time-series correlations between pairs of locations in the brain).
-Connectome-based analyses of rsFC have been fruitful in characterizing individualized functional topologies that correspond well to task-induced activity [@Gordon2017; @Laumann2015; @Smith2009; @Tobyne2017].
+It is therefore possible that the previously reported overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
+An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC in a large sample of individuals.
+
+  A useful way to characterize individual-specific brain organization is to examine patterns of resting-state functional connectivity.
+Connectome-based analyses of resting-state functional connectivity have been fruitful in identifying individualized functional subregions that correspond well to task-induced activity patterns [@Gordon2017; @Laumann2015; @Smith2009; @Tobyne2018].
 A functional connectome can be represented in the form of a network, and graph theoretic methods can be applied to analyze the network's structure [@Bassett2017; @Rubinov2010].
@@
 SP has been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
-We use SP here to identify subsets of nodes within mPFC and PCC that share spontaneously covarying temporal activation patterns during rest.
-
-  In this study, we aimed to subdivide regions commonly attributed to both DN and subjective valuation into individual-specific DN and non-DN communities, and to quantify the degree of topographic heterogeneity present in this network within and across individuals.
-We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks.
-First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks along the medial cortical wall [@Yeo2011].
+We use SP here to identify subsets of nodes within mPFC and PCC that share spontaneously covarying temporal activation patterns.
+
+  In this study, we aimed to subdivide mPFC and PCC into individual-specific DN and non-DN communities, and to quantify the degree of topographic heterogeneity in the resulting community structure over time and across individuals.
+We did this by capitalizing on the respective strengths of meta-analysis and subject-specific analyses of brain networks.
+First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks on the medial cortical wall [@Yeo2011].
 A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level.
-We then derived an rsFC network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
+We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
 Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographic extent of each community.
 The resulting communities varied topographically across individuals, while also appearing to follow common organizational principles.
-Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that this idiosyncrasy was higher in mPFC.
+Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that individual-level idiosyncrasy was greater in mPFC.
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
-Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities aligns with a recently proposed scheme for the organization of DN subdivisions.
+Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities aligns with and complements a recently proposed scheme for identifying subdivisions within the DN.
 [@Braga2017; @Braga2019].
 Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
+**REVISIT JOE'S COMMENTS ON THE B&B PART OF THE INTRO**
 
@@
 [-@Yeo2011].
-First, we selected vertices on the medial cortical surface that were contained by the DN and limbic networks in HCP's 32,000 surface space (fs_LR_32k).
-Next, we overlaid those networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
+First, we selected vertices on the medial cortical surface that were contained by the DN and limbic networks in HCP's 32,000 vertex surface space (fs_LR_32k).
+Next, we overlaid those networks on a parcellated atlas of the human cortical surface [360 regions; @Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
 This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1).
-The search space was naturally divided into two spatially non-contiguous clusters that covered PCC and mPFC, facilitating the examination of each general region separately.
+The search space in each hemisphere was naturally divided into two spatially non-contiguous clusters that covered PCC and mPFC, facilitating the examination of each region separately.
 
@@
 We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DN effects.
-For subjective valuation, we gathered peak brain coordinates of activity from 200 studies that were associated with positive effects in contrasts of high-versus-low-value outcomes or prospects [@Bartra2013].
+For subjective valuation, we gathered peak activation coordinates from 200 studies that were associated with positive effects in contrasts of higher-value minus lower-value outcomes or prospects [@Bartra2013].
 For DN, we acquired coordinates from 80 studies that were related to task-deactivation [@Laird2009].
-These coordinates represent the areas that exceeded the statistical significance threshold in each original study.
-For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009].
-The indicator map for each study was then projected to a standard cortical mesh (fsaverage, 160,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/).
+The coordinates represent the areas that exceeded the statistical significance threshold in each original study.
+For each study, we created an indicator map in standard volumetric space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009].
+The indicator map for each study was then projected to a standard cortical mesh (fsaverage, 160,000 vertices, projfrac-max from 0 to 1 by 0.25, registered using mni152.register.dat) using FreeSurfer's mri_vol2surf [@Fischl1999; @Dale1999] (http://surfer.nmr.mgh.harvard.edu/).
 We then resampled the Glasser et al.
-(2016) parcellation to fsaverage, and tallied how many studies had positive indicator values intersecting with each cortical parcel (the details of the resampling procedure are described in https://wiki.humanconnectome.org/display/PublicData/HCP+Users+FAQ#HCPUsersFAQ-9.HowdoImapdatabetweenFreeSurferandHCP, and were implemented using a custom script https://github.com/stobyne/Spherical-Surface-Swapper).
-Two studies from the subjective valuation corpus were removed because they did not contain cortical voxels, leaving a final number of 198 studies.
+(2016) parcellation to fsaverage, and tallied how many studies had positive indicator values intersecting with each cortical parcel (the details of the resampling procedure are described in https://wiki.humanconnectome.org/display/PublicData/HCP+Users+FAQ#HCPUsersFAQ-9.HowdoImapdatabetweenFreeSurferandHCP, and were implemented using a custom script available at https://github.com/stobyne/Spherical-Surface-Swapper).
+Two studies from the subjective valuation corpus were removed because they did not contain activation peaks that overlapped with cortex, leaving a final number of 198 studies.
 
 To test for parcels that were significantly more strongly associated with one domain than the other, we performed per-parcel chi-squared tests comparing the proportion of studies with activation in that parcel between the two domains.
-We permuted the study domain labels (i.e.
-DN or valuation) 5000 times while preserving the total number of studies in each domain, and on each iteration stored the maximum resulting chi-squared statistic (across all parcels).
+We permuted the study domain labels (DN or valuation) 5000 times while preserving the total number of studies in each domain, and on each iteration stored the maximum resulting chi-squared statistic (across all parcels).
 This gave us a null distribution of 5000 maximum chi-squared values.
@@
 
-### *fMRI Data*
+### *resting-state fMRI Data*
 
@@
 Only subjects with both left-right and right-left phase encoding were included (i.e.
-subjects with four rsfMRI sessions).
+subjects with four resting-state fMRI sessions).
 In addition, only datasets with low motion levels (under 1.5 mm) and less than 5% of points over 0.5 mm framewise displacement (FD) were used.
@@
 
-Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, high-pass filtering (0.0005 Hz threshold), MNI152-based normalization, surface reconstruction, and mapping of functional data to the a standardized cortical surface model (details can be found on Glasser et al., 2013).
-In addition, data underwent temporal denoising based on independent components [FIX; @Griffanti2014; @Salimi-Khorshidi2014].
+Data initially underwent the HCP minimal preprocessing pipeline [@Glasser2013], which included gradient nonlinearity correction, motion correction, EPI distortion correction, high-pass filtering (0.0005 Hz threshold), MNI152-based normalization, surface reconstruction, and mapping of functional data to a standardized cortical surface model (details can be found in Glasser et al., 2013).
+In addition, data underwent temporal denoising based on independent components [FMRIB's ICA-based X-noiseifier, FIX; @Griffanti2014; @Salimi-Khorshidi2014].
 Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017].
-Steps included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising via mean grayordinate signal regression [@Burgess2016] and censoring of high-motion timepoints by deletion.
-Finally, data acquired on the same day (i.e.
-left-right and right-left phase encoding session) were temporally demeaned.
+Steps (in order) included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising via mean grayordinate signal regression [@Burgess2016].
+After filtering and denoising, high-motion time points were censored by deletion and each run was temporally de-meaned.
 The post-processed time series had a median of `r median(corrCounts$nTR)` time points (minimum = `r min(corrCounts$nTR)`) across participants.
@@
 
-### *Seed-based rsFC versus Community Detection*
+### *Seed-based Resting-state Functional Connectivity versus Community Detection*
 
@@
 # Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we're manually reverting it after visual inspection
-revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1", "156637_H1")
+revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1")
 for (subj in revertSubjs) {
@@
 # But the Corr vs FV analysis below is badly affected
-# For now I'm just selecting the individuals that have negatively correlated FVectors
-# It might be worth visually inspecting each to see if a simple heuristic works (i.e. if corr < -0.5, then FV * -1 & 1 - FB)
-# Although this doesn't adress which half is the culprit
 unCorrParticipants <- data.frame(SubjID = subjList,
-                                 Corrs = sapply(seq(1, nSubj *2, by = 2), function(x) {cor(Summaries_halves_unthresh[[x]]$FiedlerVec, Summaries_halves_unthresh[[x+1]]$FiedlerVec)})) %>%
+                                 Corrs = sapply(seq(1, nSubj * 2, by = 2), function(x) {cor(Summaries_halves_unthresh[[x]]$FiedlerVec, Summaries_halves_unthresh[[x+1]]$FiedlerVec)})) %>%
   filter(Corrs < 0)
@@
 best <- tmp %>% top_n(10, wt = DailyARI) 
-bestindx <- substr(subjList_halves,1,6) %in% best$SubjID
+bestindx <- substr(subjList_halves, 1, 6) %in% best$SubjID
 
@@
 
+\beginsupplement
+
 ``` {r Subdivide search space into hemi-region for table, echo = FALSE, message = FALSE} 

### 2019-05-21 Manuscript.Rmd
Done with the methods

@@
 Non-retained edges were reset to 0 to exclude them from the network analyses.
-We generated and analyzed network weight matrices at four levels: (1) for each subject's full dataset (4800 TRs total); (2) on each step of a sliding window analysis (see Partition Evaluation for more details); (3) for the concatenated time series for the two runs on each day (2400 TRs total); and (4) for each run separately (1200 TRs each).
+We generated and analyzed network weight matrices at four levels: (1) for each subject's full concatenated dataset (up to 4800 TRs); (2) on each step of a sliding window analysis (see Partition Evaluation for more details); (3) for the concatenated time series for the two runs on each day (up to 2400 TRs); and (4) for each run separately (up to 1200 TRs).
 
@@
 The transformation ensures that every row sums to zero.
-We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two.
-This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values and is binarized by sign [@Fiedler1975].
-This method partitions the network into two similarly-sized communities.
+We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue (traditionally called the 'Fiedler vector') to divide the network into two.
+The Fiedler vector provides a set of positive and negative values and is binarized by sign to partition the network into two similarly-sized communities [@Fiedler1975].
 In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
 Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the DN-specific PCC parcel identified in our meta-analysis.
-The high density of the graphs ensured that spectral partitioning did not face the issues associated with its use in sparse networks [@Fortunato2016].
+The high density of the graphs ensured that SP did not face the issues associated with its use in sparse networks [@Fortunato2016].
 
@@
 [-@Clauset2004].
-This method compares the strength of the connection between any two vertices to their probability of being randomly connected to any other vertex in the network.
-The method heuristically iterates through many possible combinations of vertices, and selects the partitioning that maximizes the within-community edge weights, relative to a random network containing the same number of edges.
+The method heuristically iterates through many possible combinations of vertices, and selects the partitioning that maximizes the within-community edge weights, relative to a random network containing the same number of edges and communities.
 Unlike SP, modularity can fractionate a network into more than two communities.
@@
 We used the adjusted Rand index (ARI) to evaluate the stability and topographical heterogeneity of the communities within and across individuals [@Hubert1985], which was calculated using the "mcclust" package in R [@Arno2012].
+The ARI is a metric that quantifies the similarity between two alternative clusterings of the same data.
 The base of the ARI is computed by the formula
@@
 Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $n(n - 1)/2$).
-The resulting ratio is adjusted against a baseline given by the expectation assuming independent partitionings.
-The index ranges from 0 to 1, where 0 denotes the value expected by chance.
-This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below the chance level).
-In short, the ARI determines the chance-corrected agreement between any two partitions while being agnostic to the labeling scheme.
+The resulting ratio is adjusted against a baseline given by the expectation assuming independent partitionings to yield an index that ranges from 0 to 1, where 0 denotes the value expected by chance.
+This means that even though differences are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below the chance level).
+In short, the ARI quantifies the chance-corrected agreement between any two partitions while being agnostic to the labeling scheme.
 
@@
 First, we computed the degree of agreement between SP and modularity per subject.
-SP and Modularity have been previously found to show underfitting and overfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings.
+SP and Modularity have been previously found to show underfitting and overfitting tendencies, respectively, in their community detection performance in a diverse set of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings.
 Next, we compared the subject-level SP partitionings across individuals, and calculated the mean pairwise ARI for the group.
 We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects.
-Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013].
-
-To estimate the degree of stability of partitionings per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partitioning against the partitioning derived from the whole subject's data.
-A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017].
+
+To estimate the degree of variability of partitionings per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partitioning against the partitioning derived from the subject's whole data set.
+A 20-min window has previously been found adequate for identifying stable community features in brain networks [@Gordon2017].
 We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows.
@@
 We tested this idea by computing the ratio of the mean ARI within and between individuals.
-Ratios close to one denoted similar within-participant and across-participant alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-participant than across participants.
+Ratios close to one would denote similar within-participant and across-participant alignment, whereas ratios considerably higher than one would suggest that partitions were more similar within-participant than across participants.
 We then extended this idea by computing the agreement across individual runs (4 per subject).
@@
 
-We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity.
-First, we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average activity across all vertices in PCC for each day separately.
-We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP across days in three ways: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps.
+We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach based on seed-based functional connectivity.
+For each day (2 per individual), we we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in PCC.
+The sign of the Fiedler vector was reoriented so the DN community was marked by positive values in every subject.
+We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP by calculating three sets of across-day similarity values for each individual: 1) between the two seed-based maps; 2) between the two SP-based maps; and 3) between seed- and SP-based maps.
 Because the values in the maps were continuous-valued (and not categorical labels, which would be amenable to ARI), we quantified the similarity between maps in terms of the spatial Spearman correlation across vertices.
 These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-For 3 subjects, the maps produced with one of the days' datasets insufficiently covered area 7m, and so the community labeling was reversed (for one additional subject, both daily maps were reverted).
-ARI is robust to these labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects, even though the topography was highly similar.
-We thus visually inspected these subjects (n = 7) and reverted the labeling when it was clear that the topologies aligned across days.
+For 7 subjects, the community maps produced with one of the days' data sets insufficiently covered area 7m (i.e.
+less than 50% coverage), and so the sign of the Fiedler vector did not match the community assignment specified above.
+ARI is robust to such labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects across days, even though the topography was highly similar.
+We thus visually inspected these subjects and reverted the labeling when it was clear that the topography aligned across days.
 

### 2019-05-22 Manuscript.Rmd
done up to the results

@@
   word_document: 
-    reference_docx: APA_style.docx #Style_reference_draft.docx 
-  html_document: default
+    reference_docx: Style_reference_draft.docx 
 bibliography: mPFC_paper.bib
@@
     - \usepackage{float}
-
-# reset counter for supplemental figures/tables (PDF ONLY)
-\newcommand{\beginsupplement}{
+    - \newcommand{\beginsupplement}{
         \setcounter{table}{0}  
@@
       }
+
 ---
@@
 For each day (2 per individual), we we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in PCC.
-The sign of the Fiedler vector was reoriented so the DN community was marked by positive values in every subject.
+The sign of the Fiedler vector was oriented so the DN community was marked by positive values in every subject.
 We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP by calculating three sets of across-day similarity values for each individual: 1) between the two seed-based maps; 2) between the two SP-based maps; and 3) between seed- and SP-based maps.
@@
 Volumetric coordinates from 80 studies with task deactivation contrasts and 198 studies with valuation contrasts were projected onto a cortical surface, and mapped to discrete parcels from a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
-The `r length(Yeo_labels)` parcels considered were limited to the medial portion of the default and limbic networks defined by the Yeo et al.'s [-@Yeo2011] 17-network parcellation.
+The `r length(Yeo_labels)` parcels considered were limited to the medial portion of the default and limbic networks defined by the Yeo et al.
+[-@Yeo2011] 17-network parcellation.
 Domain-specificity was tested by first permuting the domain labels across studies (DN or valuation) to create a null distribution for the maximum chi-squared statistic in the search space (see Methods for details).
@@
 The adjacent area v23 exhibited a similar effect, albeit only unilaterally (Right: observed $\chi^2$ = 11.51, *p* = 0.011; Left: observed $\chi^2$ = 8.25, *p* = 0.067).
-There appeared to be a bilateral preference toward valuation effects in area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.005; Right: observed $\chi^2$ = 12.83, *p* = 0.005); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum.
+There appeared to be a bilateral preference toward valuation effects in mPFC area 25 (Left: observed $\chi^2$ = 12.91, *p* = 0.005; Right: observed $\chi^2$ = 12.83, *p* = 0.005); however, closer inspection suggested this effect was driven by subcortical foci centered in adjacent ventral striatum.
 No other parcels were preferentially implicated in valuation relative to DN.
@@
 We assigned the DN label to the community that contained the DN-specific PCC parcel from the meta-analysis (7m).
-We oriented each individual's Fiedler vector to make sure positive values corresponded to the DN community, and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN).
+We oriented each individual's Fiedler vector so positive values corresponded to the DN community, and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN).
 In qualitative terms, the resulting patterns contained substantial DN coverage in posterior PCC (as dictated by our labeling strategy), with non-DN vertices in anterior PCC.
@@
 We quantified the cross-method agreement in terms of the Adjusted Rand Index (ARI; see Methods), which measures the proportion of node pairs in a network that were either clustered together or separately in both partitionings, while being agnostic to labeling schemes and controlling for chance clustering.
-The ARI takes values ranging from 0 to 1, with 0 indicating chance agreement.
+The ARI normally takes values ranging from 0 to 1, with 0 indicating chance agreement (but can take negative values if the similarity falls below chance).
 
@@
 Modularity showed a tendency to produce additional communities (median = `r median(nModularity)`, range = `r range(nModularity)`).
-However, the additional communities encompassed a small number of vertices (median = `r median(modularityCounts_extra)`, IQR = `r quantile(modularityCounts_extra, 0.25)` - `r quantile(modularityCounts_extra, 0.75)`) compared to the principal two (median = `r median(modularityCounts_two)`, IQR = `r quantile(modularityCounts_two, 0.25)` - `r quantile(modularityCounts_two, 0.75)`), suggesting that a binary partitioning could provide a reasonable approximation of the network's true community structure.
-
-Next, we examined the similarity of partitionings across individuals by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
-Qualitative inspection of the community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects.
-To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3).
-The functional topography of PCC was better maintained across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), but the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).
+However, the additional communities encompassed a small number of vertices (median = `r median(modularityCounts_extra)`, IQR = `r quantile(modularityCounts_extra, 0.25)` - `r quantile(modularityCounts_extra, 0.75)`) compared to the principal two (median = `r median(modularityCounts_two)`, IQR = `r quantile(modularityCounts_two, 0.25)` - `r quantile(modularityCounts_two, 0.75)`), suggesting that a binary partitioning provided a reasonable approximation of the network's true community structure.
+
+Next, we examined the similarity of SP-based partitionings across individuals by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+Qualitative inspection of the community organization showed good alignment for PCC, whereas the pattern in mPFC was consistent but shifted topographically across subjects.
+To quantify this heterogeneity in mPFC, we calculated the between-subject ARI for each region separately (Figure 3).
+The functional topography of PCC was better aligned across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), but the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).
 
@@
 
-These analyses suggest that there is potential value in thresholding the Fiedler vector as a means to identify idiosyncratic and reliable DN and non-DN vertices on an individual subject basis.
+These analyses suggest that there is potential value in thresholding the Fiedler vector as a means to identify reliable DN and non-DN vertices on an individual subject basis.
 We therefore thresholded each subject's Fiedler vector to produce these refined maps.
-For each individual, we estimated the threshold by selecting the smallest absolute Fiedler vector value that yielded an average stability of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
+For each individual, we estimated the threshold by selecting the smallest absolute Fiedler vector value that yielded an average stability across suprathreshold nodes of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
 Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
@@
 The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
-Figure 5 (bottom) shows the spatial average of the thresholded partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
+Figure 5B shows the spatial average of the thresholded partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
 This summary illustrates the common organizational layout of both communities, but also highlights the considerable variability across individuals, especially in mPFC.
@@
 
-To test the possibility that the higher inter-subject variability in mPFC was driven merely by lower signal quality in the retained vertices, we quantified the mean temporal signal to noise ratio (tSNR) for each region, both before and after thresholding.
+To test the possibility that the higher inter-subject variability in mPFC was driven merely by lower signal quality in the retained vertices, we quantified the temporal signal to noise ratio (tSNR) for each region, both before and after thresholding.
 We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
-In terms of tSNR variability across vertices within each region, mPFC had overall greater standard deviation both before and after the threshold (mPFC: pre-threshold mean SD = 33.96, post-threshold mean SD = 30.15; PCC: pre-threshold mean SD = 15.28, post-threshold mean SD = 14.59).
-However, paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
-tSNR after thresholding was significantly higher for mPFC (permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
+In terms of tSNR variability across vertices within each region, mPFC had overall greater  spatial standard deviation both before and after the threshold (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59).
+However, tSNR after thresholding was significantly higher for mPFC than PCC (permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
+Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
+In short, mPFC had higher overall tSNR, albeit with freater variability across nodes, and the thresholding step was helpful for focusing the analysis on vertices with high signal quality.
+**revise**
 
@@
 The relatively high inter-individual variability seen in the aggregate map could reflect at least three factors: (1) measurement noise, (2) dynamic variation in mPFC network organization, and (3) stable patterns of functional organization that differ across individuals.
-To evaluate the third possibility, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
+To arbritrate among these possibilities, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
 Insofar as the observed variability reflects individual-specific brain organization, day to day ARI values should be consistently higher within-individual than between individuals (an example comparison for two individuals is provided in Supplemental Figure 2).
@@
 We extended the analysis of per-day data by examining whether the organization of the DN could be extracted using per-run data only.
-The duration of each run (approximately 14 mins long) falls below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
+The duration of each run (approximately 14 min) falls below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
 Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DN organization from only a single run of data.
@@
 Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals.
-Figure 7 (left) shows that these pairwise comparisons resemble those from the day-to-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.
-
-Figure 7 (right) shows the test/re-test reliability across days for patterns dervied using community detection, seed-based correlation, and across methods (e.g.
+Figure 7A shows that these pairwise comparisons resemble those from the across-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.
+
+Figure 7B shows the test/re-test reliability across days for patterns derived using community detection, seed-based correlation, and across methods (e.g.
 Day 1 community detection versus Day 2 seed-based correlation).
@@
 Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences.
-These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies.
+These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies, while also conveying the advantage of being data-driven, unbiased and observer agnostic.
 
@@
 The thresholded partitions in our work qualitatively resembled the topographical arrangement of DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
-We explored this similarity by reproducing their seed-based connectivity approach in three of our subjects.
-In their original work, Braga and Buckner manually selected individual vertices in areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two spatially anticorrelated networks [@Braga2017; @Braga2019].
+We explored this similarity by reproducing their seed-based connectivity approach in two of our subjects.
+In their original work, Braga and Buckner [-@Braga2017] manually selected individual vertices in areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two spatially anticorrelated networks [@Braga2017; @Braga2019].
 Therefore, we hypothesized that if the SP communities corresponded their proposed networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas.
@@
 Visual inspection of these networks shows a remarkable similarity between our DN community and the previously reported sub-network A.
-However, the non-DN community filled areas not covered by either DN-A or DN-B, further evidencing its disentanglement from DN processes.
+However, the non-DN community filled areas not covered by either DN-A or DN-B.
+This result supports the idea that the two approaches serve complementary purposes.
+Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach partitions DN from non-DN cortex.
 
@@
 In particular, the effects elicited by the subjective value of an option and the default network (DN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
-This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these seemingly dissimilar cognitive domains might recruit a shared set of core cognitive processes [@Northoff2012].
+This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these seemingly dissimilar cognitive domains might recruit a shared set of core cognitive processes [@Acikalin2017; @Northoff2012].
 

### 2019-05-22 Manuscript.Rmd
remove unnnecessary YAML metadata

@@
   pdf_document: 
-    keep_tex: true
+    keep_tex: false
     highlight: haddock
-  word_document: 
-    reference_docx: Style_reference_draft.docx 
 bibliography: mPFC_paper.bib

### 2019-05-23 Manuscript.Rmd
updated figures, and imported the fig files to the repo

@@
 A: Proportion of times each ROI was reported in the valuation and DN literatures.
-B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details)."}
+B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details).
+Areas in blue represent the remaining search space."}
 # Change to inflated eventually
-include_graphics("./Images/ROIS4.png")
+include_graphics("./Images/ROIS.png")
 ```
@@
 ``` {r Variability per subject: Fiedler vector vs prop.
-DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each individual, we produced partitions for each 20 minute sliding window (1 min shift, i.e.
-~84 TRs).
+DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs).
 B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (bottom).
@@
 Dashed red lines indicate the mean FV value at which maps were thresholded.
-The histogram displays the frequency distribution of y-axis values.", echo=FALSE, message = FALSE}
+The histogram displays the mean frequency distribution of y-axis values.", echo=FALSE, message = FALSE}
 # code to generate plots
@@
 6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 scanning days each), showing pattern agreement across days and subjects for PCC and mPFC separately.
+The block-diagonal structure is indicative of test-retest reliability across days within an individual.
 Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncrasies in community arrangement for both PCC and mPFC (ratios > 1, solid line), with higher subject-specificity in mPFC.
@@
 7), fig.align="center", fig.cap = "A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects.
-The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector.
+The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector, with two single-day-based maps per individual.
 The upper-right and lower-left quadrants show across-method agreement.
 B: Day 1 vs Day 2 correlation coefficients for each method, as well as between methods.
-Community detection through spectral partitioning provided more stable estimates, even though both methods showed good level of agreement.", echo = FALSE, message = FALSE}
+Community detection through spectral partitioning provided more stable estimates, even though both methods showed good levels of agreement.", echo = FALSE, message = FALSE}
 # code to produce the plots
@@
 (2019) and SP communities for two individuals.
-Upper: networks A and B produced by selecting seeds in TPJ, with our search space delineated by black borders.
+Panel A: networks A and B produced by selecting seeds in TPJ, with our search space delineated by black borders.
 Correlation values are thresholded at 0.2.
-Bottom: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A.
+Panel B: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A.
 The non-DN community covers sections of cortex not associated with either DN sub-network."}

### 2019-05-23 Manuscript.Rmd
halfway through the discussion

@@
   pdf_document: 
-    keep_tex: false
+    keep_tex: true
     highlight: haddock
@@
 
-Corresponding author:
+Corresponding author: Claudio Toro-Serey (ctoro@bu.edu)
 
@@
 
+All code used in this study is openly available at [https://github.com/ctoroserey/mPFC_partitioning](https://github.com/ctoroserey/mPFC_partitioning)
+
 ### *Search space*
@@
 We generated and analyzed network weight matrices at four levels: (1) for each subject's full concatenated dataset (up to 4800 TRs); (2) on each step of a sliding window analysis (see Partition Evaluation for more details); (3) for the concatenated time series for the two runs on each day (up to 2400 TRs); and (4) for each run separately (up to 1200 TRs).
-
+
 ### *Community Detection*
@@
 
-A considerable amount of meta-analytic work has been dedicated to pinpointing the spatial embedding of behavioral constructs in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across psychological phenomena [@DelaVega2016; @Kragel2018; @Hiser2018].
-In particular, the effects elicited by the subjective value of an option and the default network (DN) have been suggested to be inseparable in this area, an overlap that partially extends to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
-This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these seemingly dissimilar cognitive domains might recruit a shared set of core cognitive processes [@Acikalin2017; @Northoff2012].
+A considerable amount of meta-analytic work has been dedicated to characterizing the brain activity patterns associated with psychological processes in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across domains [@DelaVega2016; @Kragel2018; @Hiser2018].
+In particular, activation patterns associated with subjective valuation and with the default network (DN) have been suggested to be inseparable in this area, with overlap also partially extending to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
+This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these superficially dissimilar cognitive domains might recruit a shared set of core cognitive processes [@Acikalin2017; @Northoff2012].
 
@@
 These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
-However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far.
-Therefore, affirming that among DN and valuation share neural substrates in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.
+However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far [@Braga2017; @Braga2019; Gordon2017].
+To affirm that DN and valuation share neural substrates in this area requires a method to reliably and precisely capture the functional topography of mPFC in isolated individuals, as well as a quantitative estimate of the degree of topographic heterogeneity across a large group of individuals.
 
 Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Toker2019].
-For 100 individuals, we reliably subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities.
+For 100 individuals, we subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities.
 Restricting our analyses to a general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning that was sensitive to the complex topography of the brain.
-This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis.
-Partitioning an individual's brain network through SP has a number of advantages, including identifying communities deterministically, constraining comunities to contain a similar number of vertices (i.e.
-preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and diagnosing the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
+This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use parcels that are several orders of magnitude larger than vertices as the units of analysis.
+Partitioning an individual's brain network through SP has a number of advantages, including identifying communities deterministically, constraining communities to contain a similar number of vertices (i.e.
+preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
 Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], suggested the binary partitioning was appropriate.
@@
 We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC.
-However, the precise spatial organization of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individuals.
-This idiosyncrasy in functional topography was particularly pronounced in mPFC, and was present with various amounts of data.
-This degree of individual-specifitcity can arise from a variety of sources.
-For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to systematically vary across individuals [@Mackey2014].
+The precise spatial positioning of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individual.
+The idiosyncrasy in functional topography was particularly pronounced in mPFC, and was identified in both run-based and day-based analyses.
+Individual-specificity could theoretically arise from a variety of sources.
+For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; Lopez2019].
 Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
-A good goal for future work would be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Saygin2016].
+An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [Osher2016; @Saygin2011; @Saygin2016].
 
 Network-partitioning methods such as SP are data-driven, and therefore provide no labeling information about the resulting communities.
-We circumvented this issue by identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially affiliated to the DN literature in the meta-analysis.
+We circumvented this issue by independently identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially associated with the DN relative to subjective valuation in our meta-analysis.
 We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals.

### 2019-05-24 Manuscript.Rmd
revisions ready, csl disambiguation fixed, all references in bib file

@@
 library(tidyverse)
-library(igraph) # DELETE?
-library(pander)
-library(ggnetwork) # DELETE?
 library(ggplot2)
-library(gridExtra) # DELETE?
 library(data.table) 
-library(plyr) # DELETE?
 library(mcclust) 
@@
 Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
-**REVISIT JOE'S COMMENTS ON THE B&B PART OF THE INTRO**
 
@@
 We generated and analyzed network weight matrices at four levels: (1) for each subject's full concatenated dataset (up to 4800 TRs); (2) on each step of a sliding window analysis (see Partition Evaluation for more details); (3) for the concatenated time series for the two runs on each day (up to 2400 TRs); and (4) for each run separately (up to 1200 TRs).
-
+
 ### *Community Detection*
@@
 Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
-In short, mPFC had higher overall tSNR, albeit with freater variability across nodes, and the thresholding step was helpful for focusing the analysis on vertices with high signal quality.
-**revise**
+In short, mPFC had higher overall tSNR, albeit with greater variability across nodes.
+Applying the thresholding step allowed us to focus the analysis on vertices with high signal quality.
 
@@
 These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
-However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far [@Braga2017; @Braga2019; Gordon2017].
+However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far [@Braga2017; @Braga2019; @Gordon2017].
 To affirm that DN and valuation share neural substrates in this area requires a method to reliably and precisely capture the functional topography of mPFC in isolated individuals, as well as a quantitative estimate of the degree of topographic heterogeneity across a large group of individuals.
@@
 
-Our results are complementary with previous studies that described individual-specific brain organization.
-On one hand, topographical heterogeneity has been qulitatively highlighted using a different data aspect ratio [few individuals and more data per individual; @Gordon2017, @Braga2017, @Braga2019].
-In terms of stability, previous work has relied on parcellations and group priors to show that an individual's functional connectivity pattern is consistent in time [@Gratton2018b; @Kong2018], thus being relatively insensitive to an individual's complex topography.
-Here we were able to quantify the variability and stability of fine-scale functional topography in a large sample with moderately low amounts of data (down to a single 15 minute scan).
+Our results extend previous work that described individual-specific brain organization.
+Several recent investigations have identified topographic heterogeneity using a different data aspect ratio than we used here [a small number of individuals and a large number of scanning sessions per individual; @Braga2017; @Braga2019; @Gordon2017].
+Previous work has also shown that functional correlations among pre-defined cortical parcels are highly stable within an individual [@Gratton2018b; @Kong2018].
+Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan).
 The motivation to sub-divide DN also stems from recent work by Kernbach et al.
-[-@Kernbach2018], where they identified specialized communication of parcels within DN with the rest of the brain in a large pool of individuals.
-
-In addition to its general diagnostics, SP provides analytical advantages specific to neuroscience.
+[-@Kernbach2018], which identified specialized communication of parcels within DN with the rest of the brain in a large pool of individuals.
+
+In addition to the technical advantages noted above, the SP algorithm offers analytical advantages specific to neuroscience.
 We found that SP outperformed a traditional seed-based correlation approach in capturing idiosyncratic functional topography.
-By relying on all sources of functional covariation among cortical vertices (rather than individual correlations with the seed), community detection methods in general, and SP in particular, are capable of further filtering nodes with weak sub-network affiliation.
-In addition, we found SP results could be made more stable by thresholding the underlying Fiedler vector by using temporal stability to apply a custom threshold per individual.
+Community detection methods such as SP are stabilized by relying on  all pairwise correlations among cortical vertices (rather than correlations with an individual seed).
+In addition, we found we could increase the temporal stability of SP results by thresholding the underlying Fiedler vector.
 The magnitude of these eigenvector values has been recently used to characterize the continuous connectivity profile of the insula with the rest of the brain, challenging the notion of discrete parcellations of this region [@Tian2018].
-The combination of discrete classification and gradual information provided by SP points to flexible information benefits not regularly afforded by other clustering algorithms.
-
-The community organization of PCC and mPFC shares significant similarities with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; -@Braga2019].
-The topography of our thresholded DN community closely matched network A, while non-DN captured zones uncovered by either DN network.
+The combination of discrete classification and graded information yielded by SP provides additional flexibility and richness relative to some other clustering algorithms.
+
+The community organization of PCC and mPFC shares significant similarities with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019].
+The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network.
 Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A and other networks.
-Our findings therefore complement the initial identification of sub-DN networks by quantifying the systematic variability of its underlying topography in a larger group of people.
-Understanding the interaction of networks A (DN), B, and non-DN should be subject of future examinations.
-Nevertheless, these qualitative similarities are important, as they collectively suggest that: (1) canonical DN regions can be topographically fractionated into DN and non-DN; (2) the DN community can be further partitioned into two sub-networks; (3) the SP algorithm is a useful and reliable tool for identifying this refined topography in a data-driven way; and (4) the topographic organization of the communities is variable across a large sample of participants, especially in mPFC.
-
-The work presented here faces a number of challenges.
-A prominent limitation is that our approach is (by design) anatomically focal.
-However, similar spectral methods have been successfully recruited in larger cortical zones.
-For example, Margulies et al.
-[-@Margulies2016] used a combination of gradient maps to characterize the spatial embedding of unimodal and heteromodal regions of cortex.
-Here we show that a variant of such methods, in combination with prior information on the brain space of interest, is capable of producing refined functional topography in individuals.
-A similar limitation corresponds to forcing a bipartition of this region.
-While we provide evidence that binarizing our search space is adequate, questions remain regarding the potential dynamics that might obscure additional networks (e.g.
-the correspondence of subthreshold DN vertices to network B, as mentioned above).
-In addition, structural connections from these networks to the rest of the brain might produce more nuanced information about sub-specialization of these communities [@Kernbach2018].
-
-Our findings pose interesting avenues for future work.
-The ability to capture an individual's functional topography without the need of group priors has direct implications for clinical research and diagnosis, where acquiring large sample and data sizes are challenging.
-Studies interested in characterizing the repercussions of mental illness on neural function could benefit from answering this question in individual patients.
-This is especially true for disorders such as schizophrenia and depression that significantly affect mPFC [@Hiser2018].
-mPFC has also recently become a common target for deep brain stimulation (or TMS) as a depression treatment [@Merkl2013], but signal quality issues make imaging this area challenging [CITATION].
-Being able to produce stable personalized targets in mPFC has the potential to boost our ability to implement and evaluate the effectiveness of these methods.
-Finally, the main motivating factor for this study was to assess whether cortical regions subserving DN and valuation are indeed overlapping in mPFC and PCC.
-While our current results suggest a re-examination of this question at the individual level, we do not estimate the location of valuation relative to DN.
-A natural next step is to examine whether SP can be similarly used to capture the idiosyncratic cortical topography of valuation.
-This could allow us not only to more strongly conclude whether DN and valuation are neurally segregable, but also aid in studies aiming to dissociate different forms of valuation.
+Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of its underlying topography in a larger group of people.
+Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research.
+These two sets of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
+
+Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying this refined topography in a data-driven way.
+The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help us better characterize the heterogenous influences on neural function reported in disorders that significantly target mPFC, such as depression and schizophrenia [@Hiser2018].
+Furthermore, it encourages interrogating where task-related activity for various domains is situated relative to an individual's mPFC organization.
+Our work is motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation and episodic memory functions [@Euston2012], self-referential thought and theory of mind [Mitchell2005], and multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010], among others.
+Delineating the precise neural mapping of these phenomena will allow us to better theorize about what common features compose their psycholological architecture.
 
@@
 
-## ARI for days
+# ## ARI for days
 # ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) +
@@
 #   theme_classic(base_size = 14)
-
-## ARI for session
+# 
+# ## ARI for session
 # ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) +

### 2019-05-24 Manuscript.Rmd
forgot the @ in two citations. oops

@@
 A recognized limitation of group averaging and meta-analysis is that the functional topography of the individual can be misaligned and blurred [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains.
-This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013].
+This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013].
 An alternative approach is to focus on analyses at the individual-participant level.
@@
 Furthermore, it encourages interrogating where task-related activity for various domains is situated relative to an individual's mPFC organization.
-Our work is motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation and episodic memory functions [@Euston2012], self-referential thought and theory of mind [Mitchell2005], and multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010], among others.
+Our work is motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation and episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], and multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010], among others.
 Delineating the precise neural mapping of these phenomena will allow us to better theorize about what common features compose their psycholological architecture.

### 2019-05-24 Manuscript.Rmd
and more small mistakes

@@
 Individual-specificity could theoretically arise from a variety of sources.
-For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; Lopez2019].
+For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; @Lopez2019].
 Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
-An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [Osher2016; @Saygin2011; @Saygin2016].
+An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
 

### 2019-05-25 Manuscript.Rmd
cleaned up comments throughout the manuscript, hoping to improve readability

@@
   pdf_document: 
-    keep_tex: true
+    keep_tex: false
     highlight: haddock
@@
 labelCoords_vertex <- read.csv2('labelCoords_vertex.csv', sep = ",")[, 2:6]
-labelCoords_vertex <- transform(labelCoords_vertex, x = as.numeric(as.character(x)), y = as.numeric(as.character(y)), z = as.numeric(as.character(z)))
+labelCoords_vertex <- transform(labelCoords_vertex, 
+                                x = as.numeric(as.character(x)), 
+                                y = as.numeric(as.character(y)), 
+                                z = as.numeric(as.character(z)))
 
@@
 threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
-permuting <- FALSE # show meta-analysis permutation progress? (SLOW)
+permute <- FALSE # show meta-analysis permutation progress? (SLOW)
 
@@
 
-## produce one permutation instance of the meta-analysis (so it can be fed to mclapply for quicker results)
+## produce one permutation instance of the meta-analysis (so it can be fed to mclapply for faster results)
 metaPerm <- function(list1 = studyList_sv, list2 = studyList_DN, labels = Yeo_labels, perm = 1) {
@@
 # Once this is created, go to the terminal and input something like this
-# wb_command -cifti-convert -from-text dataforCifti.txt 100307.MyelinMap_BC.32k_fs_LR.dscalar.nii testCifti.dscalar.nii
-# Where the myelin file here is just a templace. It can be any dscalar.nii with the right surface size
+# wb_command -cifti-convert -from-text dataforCifti.txt testSubj.dscalar.nii testCifti.dscalar.nii
+# testSubj can be found under the `Basic_files` in the repo
 HCPOut <- function(Data = DNval7mCommunities[[1]], MOI = "Membership", SubjID = "100307", padding = 0){
@@
 
-# Permutation analysis
-# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
-# Load the coordinates as studies in a list, because for the contrast the studies are permuted
-# Use table(unlist(list)) to get the counts in that case
+## Permutation analysis
+# load parcels reported per study for each corpus
 setwd('./metaresultsPOS')
@@
 # optional because it can take a long time to run
-if (permuting) {
+if (permute) {
 
@@
 ``` {r Load Summary Data}
-# Load data
+# Load data, create a subject list, get the total n, and the number of vertices
 setwd('./Summary/')
@@
 nSubj <- length(Summaries)
-nVertices <- nrow(Summaries[[1]]) # in case I need the number of vertices included per brain
+nVertices <- nrow(Summaries[[1]])
 
@@
 ## Community number evaluation (across and within methods)
-# ARI between methods
+# ARI between methods (membership = modularity assignment)
 RI_all_within <- comparePartitions(Data = Summaries, Index = "RI", MOI = c("FiedlerBinary", "Membership"), nSubjects = nSubj, subjNames = subjList)
@@
 # Number of communities per subject for modularity
-nModularity <- sapply(Summaries, function(data) {max(data$Membership)}) # n of estimated communities by modularity
+nModularity <- sapply(Summaries, function(data) {max(data$Membership)})
 
@@
 
-## Across subjects
+# ARI among individuals
 # Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
@@
 
+# and now ARI among individuals per region (PCC or mPFC)
 posteriorIndx <- Summaries[[1]]$y < 0
@@
 
-# Let's compare stuff
+# Let's sttistically compare stuff
 testPCC <- RI_PCC[lower.tri(RI_PCC)]
@@
 Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
-Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) 
 mPFCvs0_wilcox <- wilcox.test(testPFC) # is the mPFC agreement above chance?
-mPFCvs0_ES <- DescTools::CohenD(testPFC)
+mPFCvs0_ES <- cohenD(testPFC)
 
@@
 # Load files
+# these include the community assignment per window, as well as the agreement per window vs total partitioning
 setwd('./Sliding_window/')
@@
 ``` {r Variability per subject: PCC vs mPFC, echo = FALSE, message = FALSE, cache = TRUE}
-## Check stability for PCC and mPFC separately
-# Get the sliding values for PCC and PFC separately
+## Check variability for PCC and mPFC separately
 tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
@@
 
+# compare the PCC and mPFC partitionings with those produced per window
 for (subj in seq(nSubj)) {
@@
 
+# and get descriptives for all individuals
 SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
@@
 
+# ARI among subjects for each region separately
 posteriorIndx <- Summaries[[1]]$y < 0
@@
 
-# Let's compare stuff
+# Let's statistically compare stuff
 testPCC <- RI_PCC[lower.tri(RI_PCC)]
@@
 Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
-Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-# To get the rate of stability per vertex across subjects
+Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC)
+
+# To get the rate of stability per vertex across subjects (used for plotting)
 FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
@@
 # Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
-# Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we're manually reverting it after visual inspection
+# Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we manually reverted it after visual inspection
 revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1")
@@
 
-# # Select 10 subjects from the sample to plot
-# selectSubj <- seq(40)
-# subjList_sess_plot <- subjList_sess[selectSubj]
-# Summaries_sess_plot <- Summaries_sess[selectSubj]
-# 
-# 
-# # Across subjects (just for plotting)
-# RI_all_between_sess_plot <- comparePartitions(Data = Summaries_sess_plot, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-# tempComm_PCC_sess <- lapply(Summaries_sess_plot, "[", i = posteriorIndx, j =)
-# tempComm_PFC_sess <- lapply(Summaries_sess_plot, "[", i = !posteriorIndx, j =)
-# RI_PFC_sess_plot <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
-# RI_PCC_sess_plot <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess_plot), subjNames = subjList_sess_plot)
 ```
@@
 ``` {r Partition comparison: session ratios, echo = FALSE, message = FALSE, cache = TRUE}
-## Brain storming:
-## Within-subject comparisons would be more interesting? Like, comparing the mean RI within-between per subject
-## Perhaps a more interresting idea would be to generate an index of variance within/between subject
-## These are just attempts at that are not perfect:
-
-# 1) Ratio of mean within subject sessions over between subject ones (per-subject)
+# Ratio of mean within subject sessions over between subject ones (per-subject)
 # Overall
@@
 D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
-Data <- c(D1,D2)
+Data <- c(D1, D2)
 subjList_halves_plot <- rep(best$SubjID, each = 2)
@@
 # Compare correlation with community approach on mPFC
+# correlations among methods
 tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
@@
 tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
+
+# put together in a data frame
 prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
@@
 colnames(prepostComp) <- c("Approach", "Correlation")
+
+# paired permutations and effect sizes for within-subj perm vs corr
 prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
@@
 Areas in blue represent the remaining search space."}
-# Change to inflated eventually
+# brain images were produced using the HCP wb_view. 
+# see the function HCPOut for details on how they were transferred from R to CIFTI
 include_graphics("./Images/ROIS.png")
@@
 The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
-# if you want to rescale the range of values, use scales::rescale(vecot, c(min, max))
 include_graphics("./Images/FB_FV_example.png")
@@
 ```
+
 \bigskip

### 2019-05-25 communityDetection.R
directory restructuring, and deletion of unnecessary files

@@ -1,4 +1,7 @@
 #!/usr/bin/env Rscript
+
+# IMPORTANT: THIS FUNCTION ASSUMES THAT THE TIME SERIES FOR THE SUBJECT ARE HOUSE
+# IN THE SAME DIRECTORY AS A CSV FILE, CALLED '<SUBJID>_timeSeries.csv``
 SubjID <- commandArgs(trailingOnly = TRUE)
 write(paste("Analyzing data for subject", SubjID), stdout())
 
@@ -127,7 +130,7 @@ indx <- do.call(c, indx)
 
 ## load and prep data
 write("Loading data", stdout())
-Data <- fread(paste("./tseries/", SubjID, "_timeSeries.csv", sep = ""), header = F)
+Data <- fread(paste(SubjID, "_timeSeries.csv", sep = ""), header = F)
 Data <- data.matrix(Data)
 
 # append the ROI label to each vertex

### 2019-05-25 Manuscript.Rmd
directory restructuring, and deletion of unnecessary files

@@
 # load parcels reported per study for each corpus
-setwd('./metaresultsPOS')
+setwd('./meta_coords/metaresultsPOS')
 templist <- dir()

### 2019-05-25 Manuscript.Rmd
more file updates

--- 2019-05-25 Manuscript.Rmd
@@
 # load parcels reported per study for each corpus
-setwd('./metaresultsPOS')
+setwd('./Meta_coords/metaresultsPOS')
 templist <- dir()

### 2019-05-25 metacoordsVol2Surf.sh
more file updates

@@ -6,9 +6,9 @@
 
 echo "TRANSFORMING METANALYSIS COORDINATES INTO CORTICAL PARCELS (Glasser et al., 2016)"
 
+# this should be a SV or DN directory, here: metacoordsDN or metacoordsSV
 # file name will become a directory
-# read filename
-filename=$1 
+filename="meta_coords/${1}" 
 echo $filename
 
 
@@ -238,7 +238,7 @@ while IFS=$',' read -r -a label ; do
 	else
 		echo 0 >> ${dirName}_summary.csv # if parcel was not reported in the literature
   	fi
-done < $HOME/fMRI/Glasser_labels.csv
+done < $HOME/Basic_files/Glasser_labels.csv
 ############
 
 # create a label file to visualize which areas were reported in the literature
@@ -292,7 +292,7 @@ while IFS=$'\t' read -r -a label ; do
         echo 0 >> ${dirName}_lh_overlay.csv
         #echo 0 >> check.csv
     fi
-done < $HOME/fMRI/Glasser_labels_lh.csv
+done < $HOME/Basic_files/Glasser_labels_lh.csv
 
 while IFS=$'\t' read -r -a label ; do
     if [ -z "$label" ] ; then

### 2019-05-25 metacoordsVol2Surf.sh
little typo

@@ -8,7 +8,7 @@ echo "TRANSFORMING METANALYSIS COORDINATES INTO CORTICAL PARCELS (Glasser et al.
 
 # this should be a SV or DN directory, here: metacoordsDN or metacoordsSV
 # file name will become a directory
-filename="meta_coords/${1}" 
+filename="Meta_coords/${1}" 
 echo $filename
 
 

### 2019-05-26 Manuscript.Rmd
halfway through the last revision

@@
 
-  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018].
+  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large and diverse set of cognitive functions [@Hiser2018; @Kragel2018].
 One such function is subjective valuation during economic decision making.
@@
 One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within partially overlapping distributed brain systems that subserve valuation and DN effects.
-This colocalization has prompted theories that the psychological constructs of valuation and DN-related processes share common features.
+This colocalization has prompted theories that valuation and DN-related processes share common elements at the psychological level.
 For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Acikalin2017; @Clithero2014; @Northoff2012; @Reddan2018].
@@
   However, strong conclusions about functional colocalization require consideration of individual-level heterogeneity in topographic patterns of brain activity.
-A recognized limitation of group averaging and meta-analysis is that the functional topography of the individual can be misaligned and blurred [@Fedorenko2012; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains.
+A recognized limitation of group averaging and meta-analysis is that the functional topography of individual brains can be misaligned and blurred [@Fedorenko2012; @Guntupalli2018a; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains.
 This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013].
 An alternative approach is to focus on analyses at the individual-participant level.
-Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018].
-Subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
+Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018], and subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
 Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019].
@@
 Here we use the technique of spectral partitioning (SP), an efficient community detection algorithm that deterministically subdivides a network into two communities [@Belkin2003; @chung1997; @Fiedler1975].
-SP has been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI (rsfMRI) data [@Tian2018], and was shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
+SP has previously been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI data [@Tian2018], and was shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
 We use SP here to identify subsets of nodes within mPFC and PCC that share spontaneously covarying temporal activation patterns.
@@
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
-Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities aligns with and complements a recently proposed scheme for identifying subdivisions within the DN.
-[@Braga2017; @Braga2019].
+Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019].
 Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
@@
 This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1).
-The search space in each hemisphere was naturally divided into two spatially non-contiguous clusters that covered PCC and mPFC, facilitating the examination of each region separately.
+The search space in each hemisphere was naturally divided into two spatially non-contiguous clusters in PCC and mPFC, facilitating the examination of each region separately.
 
@@
 For DN, we acquired coordinates from 80 studies that were related to task-deactivation [@Laird2009].
-The coordinates represent the areas that exceeded the statistical significance threshold in each original study.
+The coordinates represent areas that exceeded the statistical significance threshold in each original study.
 For each study, we created an indicator map in standard volumetric space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere [@Wager2009].
@@
 To test for parcels that were significantly more strongly associated with one domain than the other, we performed per-parcel chi-squared tests comparing the proportion of studies with activation in that parcel between the two domains.
-We permuted the study domain labels (DN or valuation) 5000 times while preserving the total number of studies in each domain, and on each iteration stored the maximum resulting chi-squared statistic (across all parcels).
+We permuted the study domain labels (DN or valuation) 5000 times while preserving the total number of studies in each domain, and on each iteration stored the maximum resulting chi-squared statistic across all parcels.
 This gave us a null distribution of 5000 maximum chi-squared values.
@@
 
-### *resting-state fMRI Data*
+### *Resting-state fMRI Data*
 
@@
 Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other.
-Only subjects with both left-right and right-left phase encoding were included (i.e.
+Only subjects with both left-right and right-left phase encoding for each day were included (i.e.
 subjects with four resting-state fMRI sessions).
@@
 Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017].
-Steps (in order) included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising via mean grayordinate signal regression [@Burgess2016].
-After filtering and denoising, high-motion time points were censored by deletion and each run was temporally de-meaned.
-The post-processed time series had a median of `r median(corrCounts$nTR)` time points (minimum = `r min(corrCounts$nTR)`) across participants.
+Steps (in order) included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), and temporal denoising via mean grayordinate signal regression [@Burgess2016].
+After filtering and denoising, the interpolated high-motion time points were censored by deletion and each run was temporally de-meaned.
+The processed time series had a median of `r median(corrCounts$nTR)` time points (minimum = `r min(corrCounts$nTR)`) across participants.
 Each subject's brain was comprised of 32k standard grayordinates per hemisphere (combined in a CIFTI file).
@@
 First, each network was represented as an $n$ x $n$ network weight matrix $W$ as described above (where $n$ equals the number of vertices in the search space, 4,801).
-This matrix was then transformed into its symmetric normalized Laplacian form
+The matrix was then transformed into its symmetric normalized Laplacian form
 
@@
 We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue (traditionally called the 'Fiedler vector') to divide the network into two.
-The Fiedler vector provides a set of positive and negative values and is binarized by sign to partition the network into two similarly-sized communities [@Fiedler1975].
+The Fiedler vector consists of a set of positive and negative values and is binarized by sign to partition the network into two similarly-sized communities [@Fiedler1975].
 In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
@@
 
-We used the adjusted Rand index (ARI) to evaluate the stability and topographical heterogeneity of the communities within and across individuals [@Hubert1985], which was calculated using the "mcclust" package in R [@Arno2012].
+We used the Adjusted Rand index (ARI) to evaluate the stability and topographical heterogeneity of the communities within and across individuals [@Hubert1985], which was calculated using the "mcclust" package in R [@Arno2012].
 The ARI is a metric that quantifies the similarity between two alternative clusterings of the same data.
@@
 The resulting ratio is adjusted against a baseline given by the expectation assuming independent partitionings to yield an index that ranges from 0 to 1, where 0 denotes the value expected by chance.
-This means that even though differences are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below the chance level).
+This means that even though differences are heavily penalized, positive ARI values compare favorably against chance clustering (and the index can take negative values if the ratio given by the formula above falls below the chance level).
 In short, the ARI quantifies the chance-corrected agreement between any two partitions while being agnostic to the labeling scheme.
@@
 We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach based on seed-based functional connectivity.
-For each day (2 per individual), we we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in PCC.
-The sign of the Fiedler vector was oriented so the DN community was marked by positive values in every subject.
-We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP by calculating three sets of across-day similarity values for each individual: 1) between the two seed-based maps; 2) between the two SP-based maps; and 3) between seed- and SP-based maps.
+Independently for each day (2 per individual), we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in PCC.
+We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP, with the sign of the Fiedler vector oriented so the DN community was marked by positive values in every subject.
+We calculated three sets of across-day similarity values for each individual: 1) between the two seed-based maps; 2) between the two SP-based maps; and 3) between seed- and SP-based maps.
 Because the values in the maps were continuous-valued (and not categorical labels, which would be amenable to ARI), we quantified the similarity between maps in terms of the spatial Spearman correlation across vertices.
 These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-For 7 subjects, the community maps produced with one of the days' data sets insufficiently covered area 7m (i.e.
-less than 50% coverage), and so the sign of the Fiedler vector did not match the community assignment specified above.
-ARI is robust to such labeling issues, but this produced strong negative correlations of the Fiedler vector for these subjects across days, even though the topography was highly similar.
-We thus visually inspected these subjects and reverted the labeling when it was clear that the topography aligned across days.
+For 7 subjects, the community maps produced with one of the days' data sets insufficiently covered area 7m, and so our community labeling scheme for the Fiedler vector produced a sign mismatch across days.
+ARI is robust to such labeling issues, but the inconsistency produced strong negative correlations of the Fiedler vector across days for these individuals.
+Visual inspection showed that the community layout was well aligned across days, and so we matched the labeling of their partitionings based on the day that sufficiently covered area 7m.
 
 The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018b]).
-We therefore compared the within-subject correlation coefficients produced by each method through a paired permutation analysis.
-For each of the 100 individuals, we computed the difference in inter-day correlations between methods, randomly alternated the sign of these values 5000 times, and computed the mean of these differences on each iteration.
+We therefore compared the within-subject spatial correlation coefficients produced by each method through a paired permutation analysis.
+For each of the 100 individuals, we computed the difference in inter-day correlations between methods, randomized the sign of these values 5000 times, and computed the mean of these differences on each iteration.
 The empirical difference in means was then evaluated against this permuted distribution.
@@
 
-Next, we examined the similarity of SP-based partitionings across individuals by computing the ARI between every pair of subjects, and found that there was moderate above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+Next, we examined the similarity of SP-based partitionings across individuals by computing the ARI between every pair of subjects, and found modestly above-chance agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
 Qualitative inspection of the community organization showed good alignment for PCC, whereas the pattern in mPFC was consistent but shifted topographically across subjects.
 To quantify this heterogeneity in mPFC, we calculated the between-subject ARI for each region separately (Figure 3).
-The functional topography of PCC was better aligned across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), but the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).
+The functional topography of PCC was better aligned across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), although the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).
 
@@
 There is precedent in the literature for the idea that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
-Therefore, we tested whether the magnitude of the eigenvector values was associated with the stability of nodes in time.
+Therefore, we tested whether the magnitude of the eigenvector values was associated with the stability of nodes over time.
 Specifically, we estimated the proportion of DN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
-The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), signifying that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
+The model identified a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), signifying that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
 
@@
 Sub-threshold vertices were set to zero in Fiedler vector maps and 0.5 in the binarized maps (so that they would not bias the calculation of averages).
-Figure 5 shows the thresholded partitioning for the same individual shown in Figure 2.
+Figure 5A shows the thresholded partitioning for the same individual shown in Figure 2.
 The maps used in all subsequent analyses were thresholded by this individualized criterion.
@@
 
-With these thresholded partitions, we recomputed the overall similarity of their functional organization across participants.
+With these thresholded partitions, we recomputed the overall similarity across participants.
 Compared to before, there was lower topographic agreement across individuals (mean ARI = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
-The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
-Figure 5B shows the spatial average of the thresholded partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
-This summary illustrates the common organizational layout of both communities, but also highlights the considerable variability across individuals, especially in mPFC.
+The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+Figure 5B shows the average of the thresholded partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
+This summary illustrates the common organizational layout of both communities, but also highlights the considerable variability across individuals.
 

### 2019-05-26 Manuscript.Rmd
done up to results of last revisions

@@
 These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-For 7 subjects, the community maps produced with one of the days' data sets insufficiently covered area 7m, and so our community labeling scheme for the Fiedler vector produced a sign mismatch across days.
+For 7 subjects, the communities produced with one of the days' data sets had split coverage of area 7m, and so our community labeling scheme for the Fiedler vector produced a sign mismatch across days.
 ARI is robust to such labeling issues, but the inconsistency produced strong negative correlations of the Fiedler vector across days for these individuals.
@@
 We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
-In terms of tSNR variability across vertices within each region, mPFC had overall greater  spatial standard deviation both before and after the threshold (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59).
-However, tSNR after thresholding was significantly higher for mPFC than PCC (permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
-Paired permutation analyses (5000 iterations) showed that the mean tSNR in mPFC significantly increased after thresholding (Pre: mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (Pre: mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; Post: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
+In terms of tSNR variability across vertices within each region, mPFC had overall greater spatial standard deviation both before and after thresholding (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59).
+However, tSNR after thresholding was significantly higher for mPFC than PCC (mPFC: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; PCC: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
+This reflected a significant increase in mean tSNR in mPFC as a result of the thresholding step (pre-threshold mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (pre-threshold mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
 In short, mPFC had higher overall tSNR, albeit with greater variability across nodes.
@@
 To arbritrate among these possibilities, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
-Insofar as the observed variability reflects individual-specific brain organization, day to day ARI values should be consistently higher within-individual than between individuals (an example comparison for two individuals is provided in Supplemental Figure 2).
+Insofar as the observed variability reflects individual-specific brain organization, across-day ARI values should be consistently higher within-individual than between individuals (an example comparison for two individuals is provided in Supplemental Figure 2).
 Figure 6 shows pairwise comparisons among ten example subjects for PCC and mPFC separately (left).
@@
 The duration of each run (approximately 14 min) falls below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
-Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DN organization from only a single run of data.
+Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DN organization from a single run of data.
 
@@
 
-Run-specific SP results could still capture a subject's unique organizational pattern to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+Run-specific SP results still captured unique organizational patterns to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
 We again computed each subject's ARI ratio in order to quantify the specificity of the partitions, this time using the mean of 6 across-run (within-participant) ARI values in the numerator of the ratio (Figure 6, right).
@@
 
-We next explored the possible advantage of community detection relative to a typical seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
+We next explored the possible advantage of community detection relative to a more conventional seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
 We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations.
 We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC.
-We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations.
+We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations across vertices.
 Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals.
@@
 Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences.
-These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies, while also conveying the advantage of being data-driven, unbiased and observer agnostic.
-
-### *mPFC community structure resembles a proposed DN sub-network organization*
-
-The thresholded partitions in our work qualitatively resembled the topographical arrangement of DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
-We explored this similarity by reproducing their seed-based connectivity approach in two of our subjects.
+These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies, in addition to their other advantages of being data-driven, unbiased and observer agnostic.
+
+### *Alignment of mPFC community structure with a proposed DN sub-network organization*
+
+The thresholded partitions we identified had conceptual and topographic similarities to DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
+We explored the relationship between the two sets of sub-regions by reproducing their seed-based connectivity approach in two of our subjects.
 In their original work, Braga and Buckner [-@Braga2017] manually selected individual vertices in areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two spatially anticorrelated networks [@Braga2017; @Braga2019].
-Therefore, we hypothesized that if the SP communities corresponded their proposed networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas.
-For functional connectomes from two individuals (100307 and 101006), we selected seeds for networks A and B in TPJ, and confirmed their placement based on functional connectivity patterns observed in TPJ, PCC, DLPFC, and PHC (correlation coefficients thesholded at 0.2), as stipulated by Braga et al.
+We hypothesized that if the SP communities corresponded to one or both of the previously proposed sub-networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas.
+For whole-brain functional connectomes from two individuals (100307 and 101006), we selected seeds for networks A and B in TPJ, and confirmed their placement based on functional connectivity patterns observed in TPJ, PCC, DLPFC, and PHC (correlation coefficients thesholded at 0.2), as stipulated by Braga et al.
 [-@Braga2019].
 The whole-brain seed-based functional connectivity maps for two individuals are juxtaposed with the corresponding community detection results in Figure 8.
-Visual inspection of these networks shows a remarkable similarity between our DN community and the previously reported sub-network A.
+Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A.
 However, the non-DN community filled areas not covered by either DN-A or DN-B.
 This result supports the idea that the two approaches serve complementary purposes.
-Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach partitions DN from non-DN cortex.
+Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
 

### 2019-05-26 Manuscript.Rmd
main corpus 100% ready! now onto refs

@@
 In particular, activation patterns associated with subjective valuation and with the default network (DN) have been suggested to be inseparable in this area, with overlap also partially extending to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
-This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these superficially dissimilar cognitive domains might recruit a shared set of core cognitive processes [@Acikalin2017; @Northoff2012].
+This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these superficially dissimilar domains might involve a shared set of core cognitive processes [@Acikalin2017; @Clithero2014; @Northoff2012].
 
@@
 Partitioning an individual's brain network through SP has a number of advantages, including identifying communities deterministically, constraining communities to contain a similar number of vertices (i.e.
-preventing the allocation of most vertices to a single community), providing continuous values to determine the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
+preventing the allocation of most vertices to a single community), providing continuous values that relate to the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
 Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], suggested the binary partitioning was appropriate.
@@
 In addition, we found we could increase the temporal stability of SP results by thresholding the underlying Fiedler vector.
-The magnitude of these eigenvector values has been recently used to characterize the continuous connectivity profile of the insula with the rest of the brain, challenging the notion of discrete parcellations of this region [@Tian2018].
+The magnitude of Fiedler vector values has been recently used to characterize the continuous connectivity profile of the insula with the rest of the brain, challenging the notion of discrete parcellations in that region [@Tian2018].
 The combination of discrete classification and graded information yielded by SP provides additional flexibility and richness relative to some other clustering algorithms.
 
-The community organization of PCC and mPFC shares significant similarities with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019].
+The community organization of PCC and mPFC was congruent with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019].
 The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network.
-Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this network could act as a dynamic intermediary between DN-A and other networks.
-Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of its underlying topography in a larger group of people.
+Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks.
+Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people.
 Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research.
@@
 
-Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying this refined topography in a data-driven way.
-The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help us better characterize the heterogenous influences on neural function reported in disorders that significantly target mPFC, such as depression and schizophrenia [@Hiser2018].
-Furthermore, it encourages interrogating where task-related activity for various domains is situated relative to an individual's mPFC organization.
-Our work is motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation and episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], and multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010], among others.
-Delineating the precise neural mapping of these phenomena will allow us to better theorize about what common features compose their psycholological architecture.
+Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying individualized topography in a data-driven way.
+The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help characterize heterogenous changes in mPFC activity in disorders such as depression and schizophrenia [@Hiser2018].
+It will be beneficial for future task-based fMRI experiments to be able to characterize where task-evoked activity is situated relative to an individual's overall mPFC organization.
+Our work was originally motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation versus episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], and potential topographic distinctions among multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010].
+An individualized frame of reference will enhance the ability of future studies to gauge similarities and differences among brain activity patterns associated with diverse psychological domains.
 
@@
 This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI awards N00014-16-1-2832 and N00014-17-1-2304).
-Data were provided [in part] by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
+Data were provided by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
 
@@
 B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details).
-Areas in blue represent the remaining search space."}
+Areas in blue represent the remainder of the search space."}
 # brain images were produced using the HCP wb_view. 
@@
 Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
-The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
+The bottom brain shows the binarized Fiedler vector, with red areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
 include_graphics("./Images/FB_FV_example.png")
@@
 DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs).
-B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (bottom).
+B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (lower).
 The maps share considerable qualitative similarities in their gradients along the cortical surface.
 C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations.
-Grey lines display each subject's association, while the black line shows the fit from a mixed-effects logistic regression.
+Grey lines display data for each subject, and the black line shows the fit from a mixed-effects logistic regression.
 Dashed red lines indicate the mean FV value at which maps were thresholded.
@@
 Subthreshold values effectively formed a third community of high-variability vertices.
-B: mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample.
-This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the relatively high level of variability in mPFC."}
+B: Mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample.
+This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the high level of variability in mPFC."}
 
@@
 The block-diagonal structure is indicative of test-retest reliability across days within an individual.
-Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncrasies in community arrangement for both PCC and mPFC (ratios > 1, solid line), with higher subject-specificity in mPFC.
-Right: within-to-between subject mean ARI ratios for run-specific partitionings again show higher subject-specific organization for mPFC.", echo=FALSE, message = FALSE}
+Middle: ratio of within-subject ARI to between-subject mean ARI for all individuals across days suggests idiosyncratic community arrangement for both PCC and mPFC (ratios > 1, solid line), with greater subject-specificity in mPFC.
+Right: within-to-between subject mean ARI ratios for run-specific partitionings again show greater subject-specific organization for mPFC.", echo=FALSE, message = FALSE}
 ### code for plots in this fig
@@
 The upper-right and lower-left quadrants show across-method agreement.
-B: Day 1 vs Day 2 correlation coefficients for each method, as well as between methods.
+B: Day 1 vs Day 2 within-subject correlation coefficients for each method, as well as between methods.
 Community detection through spectral partitioning provided more stable estimates, even though both methods showed good levels of agreement.", echo = FALSE, message = FALSE}
@@
 (2019) and SP communities for two individuals.
-Panel A: networks A and B produced by selecting seeds in TPJ, with our search space delineated by black borders.
+Panel A: Whole-brain networks A and B produced by selecting seeds in TPJ, with our community detection search space delineated by black borders.
 Correlation values are thresholded at 0.2.
@@
 
-```{r Extra examples (supplemental fig 1), out.width = "50%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings, with their binarized forms.
+```{r Extra examples (supplemental fig 1), out.width = "50%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings, showing both Fiedler vector values (left) and binarized communities (right).
 A common organizational principle is visible, even though it shifts topographically across individuals."}
@@
 
-```{r ARI Comparison (supplemental fig 2), out.width = "50%", fig.align = "center", fig.cap = "Example of a day-to-day comparison using ARI for two subjects (100307 and 100408).
-This reflects how qualitatively similar, individual-specific partitionings can have relatively low values, and how partitionings across individuals are much closer to chance (i.e.
-0)"}
+```{r ARI Comparison (supplemental fig 2), out.width = "50%", fig.align = "center", fig.cap = "Example of an across-day comparison using ARI for two subjects (100307 and 100408).
+This reflects how qualitatively similar, within-subject partitionings can have relatively small ARI values (here 0.24-0.25), and how partitionings across individuals are much closer to the chance level of zero."}
 include_graphics("./Images/ARI_comparison.png")

### 2019-05-26 Manuscript.Rmd
done! ready for preprinting.

@@
 threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
-permute <- FALSE # show meta-analysis permutation progress? (SLOW)
+Permute <- FALSE # show meta-analysis permutation progress? (SLOW)
 
@@
 # optional because it can take a long time to run
-if (permute) {
+if (Permute) {
 
@@
 Day 1 community detection versus Day 2 seed-based correlation).
-While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", prepostComp_permTest$Pval))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
+While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", round(prepostComp_permTest$Pval, digits = 3)))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
 Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences.

### 2019-05-26 Manuscript.Rmd
working on instructions and uploading data to osf

@@
 # raw counts for each area per literature
-nRegions_sv <- do.call(rbind, studyList_sv) %>% count
-nRegions_DN <- do.call(rbind, studyList_DN) %>% count
+nRegions_sv <- do.call(rbind, studyList_sv) %>% count(X1)
+nRegions_DN <- do.call(rbind, studyList_DN) %>% count(X1)
 nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")

### 2019-05-26 USEFORDATAPREPINFO.sh
working on instructions and uploading data to osf

@@ -1,31 +1,0 @@
-#!/bin/bash -l
-
-# this script will copy a subject's dense time series, turn it into a csv, and run community detection on it
-# its output is just the eigenvectors and eigenvalues of SP, plus the determined modularity membership
-
-#$ -l mem_total=94G
-#$ -N commDetection
-module load connectomewb/1.2.3
-
-subj=$1
-
-# copy data
-cp /projectnb/connectomedb/Q6_postprocessing/${subj}/MNINonLinear/Results/concatenated_rfMRI/rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii \
-    /restricted/projectnb/cd-lab/Claudio/Community/${subj}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii
-
-# transform to csv
-wb_command -cifti-convert -to-text ${subj}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii \
-                                    temp_${subj}_timeSeries.csv
-
-# get only the cortical vertices
-awk 'NR <= 59412 { print }' temp_${subj}_timeSeries.csv >> ${subj}_timeSeries.csv
-
-# remove original and temp time series, and move time series to the appropriate folder
-rm -f ${subj}_rfMRI_REST1+2_LR+RL.residMGSR.dtseries.nii
-rm -f temp_${subj}_timeSeries.csv
-mv -f ${subj}_timeSeries.csv tseries
-
-# run the R script that will produce the final counts
-Rscript community_detection.R $subj
-
-

### 2019-06-18 Manuscript.Rmd
added small changes post-eLife comments

--- 2019-05-26 Manuscript.Rmd
@@
 An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC in a large sample of individuals.
+This initial evaluation of variability during rest will provide grounds for individualized topographical estimation of behavioral effects (such as valuation) in the future.
 
@@
 SP has previously been used to characterize the posterior-anterior functional gradient of the insula using resting-state fMRI data [@Tian2018], and was shown to robustly and reliably separate both simulated and actual primate ECoG networks [@Toker2019].
-We use SP here to identify subsets of nodes within mPFC and PCC that share spontaneously covarying temporal activation patterns.
+We use SP here to identify subsets of nodes within mPFC and PCC that share spontaneously covarying temporal activation patterns during rest.
 
@@
 We did this by capitalizing on the respective strengths of meta-analysis and subject-specific analyses of brain networks.
+We used a data-driven procedure to identify two communities that each spanned both mPFC and PCC in each individual participant.
+We found that the resulting communities had a consistent topographic layout within PCC (according to a label-agnostic similarity metric), whereas their layout in mPFC was individual-specific and stable across test/re-test.
+We took advantage of the more consistent configuration within PCC to assign meta-analysis-derived labels to the two communities.
+Because our data-driven method established correspondence between PCC subregions and mPFC subregions, the labels defined in PCC could then be indexed into the more heterogeneous community structure of mPFC in each individual.
+
+  The outline of our paper is as follows.
 First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks on the medial cortical wall [@Yeo2011].
@@
 # raw counts for each area per literature
-nRegions_sv <- do.call(rbind, studyList_sv) %>% count
-nRegions_DN <- do.call(rbind, studyList_DN) %>% count
+nRegions_sv <- do.call(rbind, studyList_sv) %>% count #(X1)
+nRegions_DN <- do.call(rbind, studyList_DN) %>% count #(X1)
 nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")
@@
 These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns.
+We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner.
+The greater inter-individual consistency in PCC was therefore not merely an artifact of having used a PCC subregion as the basis for label assignment.
 
@@
 B: Mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample.
+Note that 7m-based community label reorientation was used to align the partitionings across individuals in a way that was independent from the community analysis itself.
 This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the high level of variability in mPFC."}

### 2019-06-18 Manuscript.Rmd
final revisions

@@
 An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC in a large sample of individuals.
-This initial evaluation of variability during rest will provide grounds for individualized topographical estimation of behavioral effects (such as valuation) in the future.
+This evaluation of variability during rest will provide a frame of reference for individualized topographical estimation of behavioral effects (such as valuation) in the future.
 
@@
 We did this by capitalizing on the respective strengths of meta-analysis and subject-specific analyses of brain networks.
-We used a data-driven procedure to identify two communities that each spanned both mPFC and PCC in each individual participant.
-We found that the resulting communities had a consistent topographic layout within PCC (according to a label-agnostic similarity metric), whereas their layout in mPFC was individual-specific and stable across test/re-test.
+We used a data-driven network-analysis procedure to identify two communities that each spanned both mPFC and PCC in each individual participant.
+We found that the resulting communities had a stereotyped topographic layout within PCC (according to a label-agnostic similarity metric), whereas their layout in mPFC was variable across individuals but stable across test/re-test.
 We took advantage of the more consistent configuration within PCC to assign meta-analysis-derived labels to the two communities.
@@
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
-Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019].
+Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019].
 Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
@@
 mPFCvs0_wilcox <- wilcox.test(testPFC) # is the mPFC agreement above chance?
-mPFCvs0_ES <- cohenD(testPFC)
+mPFCvs0_ES <- DescTools::CohenD(testPFC)
 
@@
 
-```{r Thresholded maps (Fig 5), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom).
+```{r Thresholded maps (Fig 5), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector map for subject 100307 (top), and its binarized form (bottom).
 Subthreshold values effectively formed a third community of high-variability vertices.
 B: Mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample.
-Note that 7m-based community label reorientation was used to align the partitionings across individuals in a way that was independent from the community analysis itself.
+Colors represent PCC-based labels ("DN" versus "non-DN"), which were applied in a subsequent step following the data-driven community-detection analysis and which were necessarily well-aligned in PCC.
 This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the high level of variability in mPFC."}
@@
 6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 scanning days each), showing pattern agreement across days and subjects for PCC and mPFC separately.
+Color scale represents the ARI, which quantifies topographic similarity irrespective of how the communities are labeled.
 The block-diagonal structure is indicative of test-retest reliability across days within an individual.

### 2019-06-18 Manuscript.Rmd
adapting for J Neuro

@@
 title: 'Individual heterogeneity in the functional network topography of medial prefrontal cortex'
+subtitle: 'Heterogeneity in the functional topography of mPFC'
 author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
@@
 
-## Methods
+## Materials and Methods
+
+### *Code Accessibility*
 

### 2019-06-21 Manuscript.Rmd
added the reference and an abbreviated title

--- 2019-06-18 Manuscript.Rmd
@@
 title: 'Individual heterogeneity in the functional network topography of medial prefrontal cortex'
+subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
 author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
@@
 We assigned the DN label to the community that contained the DN-specific PCC parcel from the meta-analysis (7m).
-We oriented each individual's Fiedler vector so positive values corresponded to the DN community, and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN).
+We oriented each individual's Fiedler vector so positive values corresponded to the DN community [@Nenning2017], and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN).
 In qualitative terms, the resulting patterns contained substantial DN coverage in posterior PCC (as dictated by our labeling strategy), with non-DN vertices in anterior PCC.
@@
 For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; @Lopez2019].
-Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
+Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
 An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
@@
 B: Mean of the binarized maps across all participants, indicating the proportion of DN affiliations per vertex in our sample.
-Colors represent PCC-based labels ("DN" versus "non-DN"), which were applied in a subsequent step following the data-driven community-detection analysis and which were necessarily well-aligned in PCC.
+Colors represent PCC-based labels ('DN' versus 'non-DN'), which were applied in a subsequent step following the data-driven community-detection analysis and which were necessarily well-aligned in PCC.
 This aggregate map shows the common organizational principle of the DN and non-DN communities, while also showing the high level of variability in mPFC."}

### 2019-06-21 Manuscript.Rmd
sig. statement

@@
 
-Corresponding author: Claudio Toro-Serey (ctoro@bu.edu)
+Corresponding authors: Claudio Toro-Serey (ctoro@bu.edu) & Joseph T. McGuire (jtmcg@bu.edu)
 
@@
 **Keywords:** brain networks; DN; individual differences
+
+## Significance Statement
+
+  Much attention has been given to evaluating the apparent neural overlap of various psychological domains in medial prefrontal (mPFC) and posterior cingulate cortices, but recent descriptive analyses of individualized human functional topography suggest a breaking point from group-averaging to examine this issue.
+Here we show that canonical default network in these regions can be subdivided at the individual level using spectral partitioning, and quantify the heterogeneity of this functional topography across many individuals for the first time.
+We find that the intrinsic organization of mPFC is particularly variable across individuals, but consistent within individuals over time.
+This work extends the notion that affirming the neural overlap of distinct behaviors in this area should be done at the individual level.
 

### 2019-06-24 Manuscript.Rmd
j neuro version

--- 2019-06-21 Manuscript.Rmd
@@
 
-**Keywords:** brain networks; DN; individual differences
+## Significance Statement
+
+  Multiple psychological functions engage topographically overlapping regions of human medial prefrontal cortex (mPFC), and the reason for the apparent overlap is not yet well understood.
+Here we present evidence that our understanding of the functional organization of mPFC can be advanced by accounting for individual-level topographic variability.
+We report results from a data-driven, network-based approach to subdividing mPFC and posterior cingulate cortex jointly into two distinct communities on the basis of non-task functional neuroimaging data.
+One of the identified communities corresponded to the brain's canonical default network.
+The community structure of mPFC was stable across test/re-test but exhibited high variability across individuals.
+The approach we introduce will help characterize the functional role of mPFC across diverse psychological domains.
 
@@
 The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network.
-Subthreshold vertices from the DN community overlaped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks.
+Subthreshold vertices from the DN community overlapped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks.
 Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people.
@@
 We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Daniel Sussman for initial guidance on community detection and evaluation methods.
-This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI awards N00014-16-1-2832 and N00014-17-1-2304).
+This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI award N00014-16-1-2832 and DURIP award N00014-17-1-2304).
 Data were provided by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.

### 2019-06-26 communityDetection.R
modularity membership was wrongly indexed in the short comm detection script

@@ -176,7 +176,7 @@ eigenVecs <- tempEigen$vectors
 df <- data.frame(Vertex = indx,
                  eigenVal = eigenVals,
                  FV = eigenVecs[ , ncol(eigenVecs) - 1],
-                 modularity = modularity$V1)
+                 modularity = tempCommunity$membership)
 
 # write to text files ready to be transformed to CIFTIs
 # these can be turned into CIFTI files using wb_command:

### 2019-07-01 Manuscript.Rmd
clarification on B&B thanks to Lauren

@@
 Corresponding authors: Claudio Toro-Serey (ctoro@bu.edu) & Joseph T. McGuire (jtmcg@bu.edu)
+
+Keywords: functional connectivity, default network, individual differences, network neuroscience, medial prefrontal cortex
 
@@
 We explored the relationship between the two sets of sub-regions by reproducing their seed-based connectivity approach in two of our subjects.
-In their original work, Braga and Buckner [-@Braga2017] manually selected individual vertices in areas including the dorsolateral prefrontal cortex (DLPFC), temporo-parietal junction (TPJ), and parahippocampal cortex (PHC) that produced two spatially anticorrelated networks [@Braga2017; @Braga2019].
+In their work, Braga and Buckner [-@Braga2017; @Braga2019] manually selected individual vertices in dorsolateral prefrontal cortex (DLPFC) that produced two spatially anticorrelated, interdigitated networks with distinctive patterns in the temporo-parietal junction (TPJ), inferior parietal lobule (IPL), parahippocampal cortex, mPFC, and PCC.
 We hypothesized that if the SP communities corresponded to one or both of the previously proposed sub-networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas.
-For whole-brain functional connectomes from two individuals (100307 and 101006), we selected seeds for networks A and B in TPJ, and confirmed their placement based on functional connectivity patterns observed in TPJ, PCC, DLPFC, and PHC (correlation coefficients thesholded at 0.2), as stipulated by Braga et al.
-[-@Braga2019].
-The whole-brain seed-based functional connectivity maps for two individuals are juxtaposed with the corresponding community detection results in Figure 8.
+For whole-brain functional connectomes from two individuals (100307 and 101006), we evaluated seeds in each diagnostic region that reproduced networks A and B (correlation coefficients thesholded at 0.2), and confirmed their placement based on functional connectivity patterns observed in the remaining areas.
+In both individuals, seeds in posterior IPL and TPJ most clearly identified networks A and B, respectively.
+
+The whole-brain seed-based functional connectivity maps for the two individuals are juxtaposed with the corresponding community detection results in Figure 8.
 Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A.
 However, the non-DN community filled areas not covered by either DN-A or DN-B.
-This result supports the idea that the two approaches serve complementary purposes.
+It is worth noting that a few distinguishing features are missing due to below-threshold correlation values (e.g.
+network B in right PCC of 100307).
+Even so, this result supports the idea that the two approaches serve complementary purposes.
 Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
@@
 
-```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B from Braga et al.
-(2019) and SP communities for two individuals.
+```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (recreated based on descriptions from Braga et al.
+(2019)) and SP communities for two individuals.
 Panel A: Whole-brain networks A and B produced by selecting seeds in TPJ, with our community detection search space delineated by black borders.

### 2019-07-01 Manuscript.Rmd
B&B edits ready. NeuroImage version

@@
 
+\bigskip
+
 Corresponding authors: Claudio Toro-Serey (ctoro@bu.edu) & Joseph T. McGuire (jtmcg@bu.edu)
+
+\bigskip
 
@@
 In both individuals, seeds in posterior IPL and TPJ most clearly identified networks A and B, respectively.
-
 The whole-brain seed-based functional connectivity maps for the two individuals are juxtaposed with the corresponding community detection results in Figure 8.
+It is worth noting that a few distinguishing features are missing due to below-threshold correlation values (e.g.
+network B in right PCC of 100307).
+
 Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A.
 However, the non-DN community filled areas not covered by either DN-A or DN-B.
-It is worth noting that a few distinguishing features are missing due to below-threshold correlation values (e.g.
-network B in right PCC of 100307).
-Even so, this result supports the idea that the two approaches serve complementary purposes.
+This result supports the idea that the two approaches serve complementary purposes.
 Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
@@
 
-```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (recreated based on descriptions from Braga et al.
+```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (estimated based on descriptions from Braga et al.
 (2019)) and SP communities for two individuals.

### 2019-07-03 communityDetection.R
added a check to ensure only cortical data are used for SP within comm detection

@@ -133,6 +133,9 @@ write("Loading data", stdout())
 Data <- fread(paste(SubjID, "_timeSeries.csv", sep = ""), header = F)
 Data <- data.matrix(Data)
 
+# make sure that there is only cortical info
+if (nrow(Data) > 59412) { Data <- Data[seq(59412), ] }
+
 # append the ROI label to each vertex
 dimnames(Data) <- list(labelCoords_vertex$Label, seq(ncol(Data)))
 

### 2019-08-19 Manuscript.Rmd
rearranging figure location
added ARI simulation example and fixed a tiny bug in thresholding communities in example script

@@
 
+```{r Meta-analysis ROIs (Fig.
+1), out.width = "50%", fig.align = "center", fig.cap= "Meta-analysis results.
+A: Proportion of times each ROI was reported in the valuation and DN literatures.
+B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details).
+Areas in blue represent the remainder of the search space."}
+# brain images were produced using the HCP wb_view. 
+# see the function HCPOut for details on how they were transferred from R to CIFTI
+include_graphics("./Images/ROIS.png")
+```
+
 ### *Individual-level DN and non-DN communities*
@@
 
+```{r Representative partitioning (Fig.
+2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307).
+Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
+The bottom brain shows the binarized Fiedler vector, with red areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
+include_graphics("./Images/FB_FV_example.png")
+```
+
 Before evaluating the degree of generazibility of this topographic pattern across individuals, we examined the validity of the partitionings by comparing them to results from an alternative community detection algorithm, modularity maximization [@Clauset2004].
@@
 The functional topography of PCC was better aligned across individuals (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`; paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`), although the mean ARI in mPFC still exceeded the chance value of zero (Wilcoxon signed rank test, *p* `r ifelse(mPFCvs0_wilcox$p.value == 0, "< 0.001", paste("=", mPFCvs0_wilcox$p.value))`; Cohen's D = `r round(mPFCvs0_ES, digits = 2)`).
-
-### *Pattern variability over time*
-
-``` {r Variability per subject: Overall, echo = FALSE, message = FALSE, cache = TRUE}
-# Load files
-# these include the community assignment per window, as well as the agreement per window vs total partitioning
-setwd('./Sliding_window/')
-temp <- list.files(pattern = '*Comparisons.csv')
-SC <- lapply(temp, read.csv2)
-temp <- list.files(pattern = '*Values.csv')
-SVals <- lapply(temp, read.csv2)
-
-# concatenate all proportion of DN affiliations per node to produce (1) a histogram for fig 4C, and (2) % of node affiliated with either community > 99% over time
-allPropDN <- sapply(Summaries, "[[", "slidePropDN")
-
-# proportion of fully stable nodes per individual
-prcntStable <- apply(allPropDN, 2, function(subj) {round(mean(subj %in% c(0, 1)), digits = 2)}) * 100
-
-# put all summaries together for model fit
-allSummaries <- do.call(rbind, Summaries)
-allSummaries$SubjID <- rep(subjList, each = nVertices)
-
-# Do a mixed effects GLM (binomial, quasi unavailable on glmer) to estimate the relationship between Fiedler vec and propDN
-SC_FVvPDN_model <- glmer(slidePropDN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
-SC_FVvPDN_modelSummary <- summary(SC_FVvPDN_model)
-allSummaries$FittedVals <- fitted(SC_FVvPDN_model)
-
-# Create a smaller dataframe just to plot the fit
-# Otherwise, plotting the thousands fitted can place an unnecessary burden on the document
-# (at some point, knitting to pdf wouldn't show the logistic plot because of this)
-FiedlerVector <- seq(min(allSummaries$FiedlerVec), max(allSummaries$FiedlerVec), length.out = nVertices)
-formula <- SC_FVvPDN_modelSummary$coefficients[1,1] + (SC_FVvPDN_modelSummary$coefficients[2,1] * FiedlerVector)
-Fitted_Proportion <- exp(formula) / (1 + exp(formula))
-SC_FVvPDN_fits <- data.frame(FiedlerVector, Fitted_Proportion)
-rm(FiedlerVector, formula, Fitted_Proportion)
-
-```
-
-We next sought to identify a set of temporally stable core nodes in each community.
-In order to estimate the stability of partitions over time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min).
-We compared the partitioning derived from each window with the partitioning computed using the entire time series (Figure 4).
-
-``` {r Variability per subject: PCC vs mPFC, echo = FALSE, message = FALSE, cache = TRUE}
-## Check variability for PCC and mPFC separately
-tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
-tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)
-
-SC_PCC <- data.frame()
-SC_PFC <- data.frame()
-
-# compare the PCC and mPFC partitionings with those produced per window
-for (subj in seq(nSubj)) {
-  tempPCC <- numeric()
-  tempPFC <- numeric()
-  nWins <- ncol(tempSW_PCC[[subj]])
-  for (Win in seq(nWins)) {
-    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][, Win], adjust = T)
-    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][, Win], adjust = T)
-  }
-  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
-                      Window = seq(nWins),
-                      Index = tempPCC)
-  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
-                      Window = seq(nWins),
-                      Index = tempPFC)
-  SC_PCC <- rbind(SC_PCC, dfPCC)
-  SC_PFC <- rbind(SC_PFC, dfPFC)
-}
-
-# and get descriptives for all individuals
-SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
-SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
-SC_PCC_summary$Region <- rep("PCC", nSubj)
-SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
-SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
-SC_PFC_summary$Region <- rep("mPFC", nSubj)
-SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
-colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
-rm(SC_PCC_summary, SC_PFC_summary)
-
-# Compare mean ARI of sliding windows between regions
-SW_PCCvPFC_permuteTest <- permute(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"], paired = T)
-SW_PCCvPFC_ES <- cohenD(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"])
-
-```
-
-The mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
-A subset of nodes showed exceptionally high stability, in that they were assigned to the same community in every time window.
-The percentage of stable nodes ranged from 0 to `r max(prcntStable)`% across individuals (median = `r median(prcntStable)`%, IQR = `r quantile(prcntStable, 0.25)`% - `r quantile(prcntStable, 0.75)`%).
-
-We next tested whether the continuous-valued Fiedler vector (before binarization into discrete communities) carried information about the stability of individual nodes.
-There is precedent in the literature for the idea that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
-Therefore, we tested whether the magnitude of the eigenvector values was associated with the stability of nodes over time.
-Specifically, we estimated the proportion of DN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
-The model identified a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), signifying that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
-
-``` {r Threshold values, echo = FALSE, message = FALSE}
-# Get a FV threshold for each subject based on mean vertex stability
-# Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
-TFV <- safely(threshFV)
-tempList <- lapply(Summaries, TFV)
-
-# Store the FV thresholds for all subject 
-threshDF <- data_frame(SubjID = substring(subjList, 1, 6),
-                       Lower = NA,
-                       Upper = NA)
-for (i in seq_along(tempList)) {
-  if (is.null(tempList[[i]]$result)) {
-    # if there wass no clear threshold (i.e. noisy participants), then leave it as 0
-    threshDF[i, 2:3] <- c(0, 0)
-  } else {
-    threshDF[i, 2] <- as.numeric(tempList[[i]]$result[1])
-    threshDF[i, 3] <- as.numeric(tempList[[i]]$result[2])
-  }
-}
-
-# get descriptives
-threshDescriptives <- threshDF %>% 
-                        filter(Lower < 0, Upper > 0) %>% 
-                        summarize(mL = mean(Lower), 
-                                  sdL = sd(Lower), 
-                                  mU = mean(Upper), 
-                                  sdU = sd(Upper)) %>% 
-                        round(., digits = 4)
-
-# number of subjects without stable vertices
-nUnstable <- threshDF %>% 
-                filter(Lower == 0, Upper == 0) %>% 
-                nrow
-
-# Apply threshold to Summaries
-# IMPORTANT: THIS PROCESS OVERWRITES THE VARIABLES FROM THE FIRST COMPARISON SECTION
-# THIS IS DONE FOR STORAGE-SAKE
-if (threshMaps) {
-  for (i in seq(nSubj)) {
-  Summaries[[i]] <- Summaries[[i]] %>%
-    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i, 2]) & FiedlerVec < as.numeric(threshDF[i, 3]), 0, FiedlerVec)) %>%
-    mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
-  }
-}
-
-# percent of stable nodes per subject
-# this can be different from prcntStable because fully stable vertices can technically have low FV values
-# the match between FV and Stability is strong, but not perfect
-prcntSurvived <- sapply(Summaries, function(data) {mean(data$FiedlerBinary != 0.5)})
-
-rm(tempList)
-
-```
-
-These analyses suggest that there is potential value in thresholding the Fiedler vector as a means to identify reliable DN and non-DN vertices on an individual subject basis.
-We therefore thresholded each subject's Fiedler vector to produce these refined maps.
-For each individual, we estimated the threshold by selecting the smallest absolute Fiedler vector value that yielded an average stability across suprathreshold nodes of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
-Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
-The median proportion of retained vertices per individual was `r round(median(prcntSurvived), digits = 2)` (IQR = `r round(quantile(prcntSurvived, 0.25), digits = 2)` - `r round(quantile(prcntSurvived, 0.75), digits = 2)`).
-Sub-threshold vertices were set to zero in Fiedler vector maps and 0.5 in the binarized maps (so that they would not bias the calculation of averages).
-Figure 5A shows the thresholded partitioning for the same individual shown in Figure 2.
-The maps used in all subsequent analyses were thresholded by this individualized criterion.
-
-``` {r Partition comparison: all thresholded, echo = FALSE, message = FALSE, cache = TRUE}
-## Compare partitionings
-# Across subjects
-# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
-RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
-RI_all_between_lowtri <- RI_all_between[lower.tri(RI_all_between)]
-
-# ARI among subjects for each region separately
-posteriorIndx <- Summaries[[1]]$y < 0
-tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
-tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
-RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
-RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
-
-# Let's statistically compare stuff
-testPCC <- RI_PCC[lower.tri(RI_PCC)]
-testPFC <- RI_PFC[lower.tri(RI_PFC)]
-Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
-Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC)
-
-# To get the rate of stability per vertex across subjects (used for plotting)
-FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
-FV <- do.call(cbind, lapply(Summaries, "[[", "FiedlerVec"))
-FBS <- rowMeans(FB)
-FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]
-
-```
-
-With these thresholded partitions, we recomputed the overall similarity across participants.
-Compared to before, there was lower topographic agreement across individuals (mean ARI = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
-The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
-Figure 5B shows the average of the thresholded partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
-This summary illustrates the common organizational layout of both communities, but also highlights the considerable variability across individuals.
-
-``` {r tSNR evaluation, echo = FALSE, message = FALSE, cache = TRUE}
-## next get the mean tSNR of PCC and mPFC before/after thresholding
-# the first piece of code gets each subject's mean tSNR per region, and reduces to a single matrix
-# the second one is similar, but filtering out vertices that didn't meet the threshold
-# the third one applies summary stats to each list to create a summary table
-snr_means <- list()
-
-snr_means$pre_thresh <- lapply(Summaries, function(data) {
-  data %>% 
-    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
-    group_by(region) %>% 
-    dplyr::summarise(mean_tsnr = mean(tSNR)) %>%
-    ungroup()
-}) %>% reduce(left_join, by = "region")
-
-snr_means$post_thresh <- lapply(Summaries, function(data) {
-  data %>% 
-    filter(FiedlerBinary != 0.5) %>%
-    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
-    group_by(region) %>% 
-    dplyr::summarise(mean_tsnr = mean(tSNR)) %>%
-    ungroup()
-}) %>% reduce(left_join, by = "region")
-
-# and compute summary stats on each 
-snr_means$overall <- sapply(snr_means, function(x) {
-  c(rowMeans(x[, -1]), apply(x[, -1], 1, sd))
-})
-rownames(snr_means$overall) <- c("mPFC_mean", "PCC_mean", "mPFC_SD", "PCC_SD")
-
-# permutation pre vs post
-tsnrPermute_mPFC <- permute(as.numeric(snr_means$pre_thresh[1, -1]), as.numeric(snr_means$post_thresh[1, -1]), paired = T)
-tsnrPermute_PCC <- permute(as.numeric(snr_means$pre_thresh[2, -1]), as.numeric(snr_means$post_thresh[2, -1]), paired = T)
-tsnrPermute_Post <- permute(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]))
-
-# effect size pre vs post
-tsnrCohen_mPFC <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$pre_thresh[1, -1]))
-tsnrCohen_PCC <- CohenD(as.numeric(snr_means$post_thresh[2, -1]), as.numeric(snr_means$pre_thresh[2, -1]))
-tsnrCohen_Post <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]))
-```
-
-To test the possibility that the higher inter-subject variability in mPFC was driven merely by lower signal quality in the retained vertices, we quantified the temporal signal to noise ratio (tSNR) for each region, both before and after thresholding.
-We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
-In terms of tSNR variability across vertices within each region, mPFC had overall greater spatial standard deviation both before and after thresholding (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59).
-However, tSNR after thresholding was significantly higher for mPFC than PCC (mPFC: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; PCC: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
-This reflected a significant increase in mean tSNR in mPFC as a result of the thresholding step (pre-threshold mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (pre-threshold mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
-In short, mPFC had higher overall tSNR, albeit with greater variability across nodes.
-Applying the thresholding step allowed us to focus the analysis on vertices with high signal quality.
-
-### *Test/re-test reliability across days*
-
-The relatively high inter-individual variability seen in the aggregate map could reflect at least three factors: (1) measurement noise, (2) dynamic variation in mPFC network organization, and (3) stable patterns of functional organization that differ across individuals.
-To arbritrate among these possibilities, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
-Insofar as the observed variability reflects individual-specific brain organization, across-day ARI values should be consistently higher within-individual than between individuals (an example comparison for two individuals is provided in Supplemental Figure 2).
-Figure 6 shows pairwise comparisons among ten example subjects for PCC and mPFC separately (left).
-
-``` {r Partition comparison: halves, echo = FALSE, message = FALSE, cache = TRUE}
-# Load data
-setwd('./Summary_halves/')
-temp <- list.files(pattern = "*_finalSummary.csv")
-subjList_halves <- sapply(temp, substring, first=1, last=9)
-Summaries_halves <- lapply(temp, read.csv)
-
-# Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
-# Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we manually reverted it after visual inspection
-revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1")
-for (subj in revertSubjs) {
-  indx <- grep(subj, subjList_halves)
-  Summaries_halves[[indx]] <- transform(Summaries_halves[[indx]], FiedlerVec = FiedlerVec * -1)
-}
-Summaries_halves_unthresh <- Summaries_halves
-
-# Some participants have strongly uncorrelated maps because 7m isn't fully covered on one of the days
-# ARI doesn't mind this, so the results are fine
-# But the Corr vs FV analysis below is badly affected
-unCorrParticipants <- data.frame(SubjID = subjList,
-                                 Corrs = sapply(seq(1, nSubj * 2, by = 2), function(x) {cor(Summaries_halves_unthresh[[x]]$FiedlerVec, Summaries_halves_unthresh[[x+1]]$FiedlerVec)})) %>%
-  filter(Corrs < 0)
-
-# Load the correlation-based maps from each day for analysis in a subsequent section
-temp <- list.files(pattern = "*_corHalves.csv")
-Correlation_halves <- lapply(temp, read.csv, header = F)
-
-# Apply threshold to Summaries
-if (threshMaps) {
-  # create a vector of repeated indices, so each threshold is applied to each subject twice
-  threshindex <- rep(seq(nSubj), each = 2)
-  count <- 1
-  for (i in threshindex) {
-    Summaries_halves[[count]] <- Summaries_halves[[count]] %>%
-            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i, 2]) & FiedlerVec < as.numeric(threshDF[i, 3]), 0, FiedlerVec)) %>%
-            mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
-    count <- count + 1
-  }
-}
-
-```
-
-``` {r Partition comparison: halves ratios, echo = FALSE, message = FALSE, cache = TRUE}
-## Now compare all possible pairs of subjects (for actual reporting)
-# Compare all halves with RI
-RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-
-# Compare PCC and PFC among all subjects
-tempComm_PCC_halves <- lapply(Summaries_halves, "[", i = posteriorIndx, j =)
-tempComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
-RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
-
-## Let's compare stuff (not accounting for complex interdependencies in the observations)
-## Overall differences in mean RI between PCC and mPFC
-lowPCC_halves <- RI_PCC_halves[lower.tri(RI_PCC_halves)]
-lowPFC_halves <- RI_PFC_halves[lower.tri(RI_PFC_halves)]
-Halves_PCCvPFC_perm <- permute(lowPCC_halves, lowPFC_halves, statType = mean, paired = T)
-Halves_PCCvPFC_ES <- cohenD(lowPCC_halves, lowPFC_halves) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
-# create a selection matrix containing all within-subject session comparisons
-template <- diagBlocks(ncol(RI_all_between_halves), 2) 
-lowTemplate <- template[lower.tri(template)]
-
-# Overall
-# First list element is the within subject values, second is the between subject values
-lowRIHalves <- RI_all_between_halves[lower.tri(RI_all_between_halves)]
-Halves_overallComparison <- list(lowRIHalves[lowTemplate],
-                                lowRIHalves[!lowTemplate])
-Halves_overallComparison[[3]] <- permute(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
-Halves_overallComparison[[4]] <- cohenD(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
-
-# PCC 
-Halves_PCCComparison <- list(lowPCC_halves[lowTemplate],
-                           lowPCC_halves[!lowTemplate])
-Halves_PCCComparison[[3]] <- permute(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
-Halves_PCCComparison[[4]] <- cohenD(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
-
-# mPFC
-Halves_PFCComparison <- list(lowPFC_halves[lowTemplate],
-                           lowPFC_halves[!lowTemplate])
-Halves_PFCComparison[[3]] <- permute(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
-Halves_PFCComparison[[4]] <- cohenD(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
-
-## Ratio of mean within subject sessions over between subject ones (per-subject)
-# Overall
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_all_between_halves[lower.tri(RI_all_between_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_halves), by = 2), function(x) RI_all_between_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_overall <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# PCC
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_PCC_halves[lower.tri(RI_PCC_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_halves), by = 2), function(x) RI_PCC_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_PCC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# PFC
-# Split the within-subject session RI values per subject
-withinSubjVals <- RI_PFC_halves[lower.tri(RI_PFC_halves)][lowTemplate]
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_halves), by = 2), function(x) RI_PFC_halves[-(x:(x+1)), x:(x+1)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Halves_RIRatios_PFC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
-
-# Summarize for plotting
-Halves_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
-                                      RI = c(Halves_RIRatios_PCC, Halves_RIRatios_PFC))
-
-## Stats
-# one-sample signed rank per region
-Halves_PCC_ratioTest <- wilcox.test(Halves_RIRatios_PCC, mu = 1, alternative = "greater")
-Halves_PFC_ratioTest <- wilcox.test(Halves_RIRatios_PFC, mu = 1, alternative = "greater")
-
-# between regions
-Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T, statType = median)
-Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
-
-# Select a submatrix with the best-performing subjects to show on the matrix figures
-# These will be also displayed on the session matrix
-# This way I don't have to recompute stuff
-tmp <- data_frame(SubjID = subjList,
-                  DailyARI = Halves_PFCComparison[[1]])
-best <- tmp %>% top_n(10, wt = DailyARI) 
-bestindx <- substr(subjList_halves, 1, 6) %in% best$SubjID
-
-RI_all_between_halves_plot <- RI_all_between_halves[bestindx, bestindx]
-RI_PFC_halves_plot <- RI_PFC_halves[bestindx, bestindx]
-RI_PCC_halves_plot <- RI_PCC_halves[bestindx, bestindx]
-
-# Get the same subsection of participants for the correlation plots
-Correlation_halves_plot <- Correlation_halves[bestindx]
-
-# Save unthresholded subjects for comparing and plotting against correlation maps
-unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_unthresh[bestindx], "[", i = !posteriorIndx, j =)
-unthreshComm_PFC_halves <- lapply(Summaries_halves_unthresh, "[", i = !posteriorIndx, j =)
-```
-
-Once again we found low alignment across individuals for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) and mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed comparatively high levels of within-individual agreement (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
-We calculated an index of relative specificity by computing the ratio of each individual’s across-day (within-participant) ARI to the mean of all between-participant ARI values involving that individual.
-The index is expected to take on a value near 1 if partitionings are well aligned across individuals and/or are subject to a common level of measurement noise.
-It is expected to exceed 1 insofar as functional network organization is reliable and individual-specific.
-This index is intended to factor out the potential contributions of measurement noise or dynamic instability, which would introduce variability both across individuals and across days.
-
-Figure 6 shows ARI ratios for PCC and mPFC.
-A signed-rank test showed evidence for specificity (i.e.
-ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC, 0.75), digits = 2)`, V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC, 0.75), digits = 2)`, V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`).
-Moreover, the ratios for mPFC were significantly greater than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
-These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns.
-We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner.
-The greater inter-individual consistency in PCC was therefore not merely an artifact of having used a PCC subregion as the basis for label assignment.
-
-### *Test/re-test reliability across runs*
-
-We extended the analysis of per-day data by examining whether the organization of the DN could be extracted using per-run data only.
-The duration of each run (approximately 14 min) falls below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
-Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DN organization from a single run of data.
-
-``` {r Partition comparison: session similarity matrices, echo = FALSE, message = FALSE, cache = TRUE}
-# Load data
-setwd('./Summary_sess/')
-temp <- list.files()
-subjList_sess <- sapply(temp, substring, first = 1, last = 9)
-Summaries_sess <- lapply(temp, read.csv)
-
-# Apply threshold to Summaries
-if (threshMaps) {
-  # create a vector of repeated indices, so each threshold is applied to each subject twice
-  threshindex <- rep(seq(nSubj), each = 4)
-  count <- 1
-  for (i in threshindex) {
-    Summaries_sess[[count]] <- Summaries_sess[[count]] %>%
-            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
-            mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
-    count <- count + 1
-  }
-}
-
-```
-
-``` {r Partition comparison: session compare all, echo = FALSE, message = FALSE, cache = TRUE}
-# Now run comparisons among all subjects (for actual reporting)
-RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
-tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
-RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
-
-## Let's compare stuff (not accounting for complex interdependencies in the observations)
-## Overall differences in mean RI between PCC and mPFC
-lowPCC_sess <- RI_PCC_sess[lower.tri(RI_PCC_sess)]
-lowPFC_sess <- RI_PFC_sess[lower.tri(RI_PFC_sess)]
-Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T)
-Sess_PCCvPFC_ES <- cohenD(lowPCC_sess, lowPFC_sess) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
-
-## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
-
-# create a selection matrix containing all within-subject session comparisons
-template <- diagBlocks(ncol(RI_all_between_sess), 4) 
-lowTemplate <- template[lower.tri(template)]
-
-# Overall
-# First list element is the within subject values, second is the between subject values
-lowRISess <- RI_all_between_sess[lower.tri(RI_all_between_sess)]
-Sess_overallComparison <- list(lowRISess[lowTemplate],
-                               lowRISess[!lowTemplate])
-Sess_overallComparison[[3]] <- permute(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
-Sess_overallComparison[[4]] <- cohenD(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
-
-# PCC 
-Sess_PCCComparison <- list(lowPCC_sess[lowTemplate],
-                           lowPCC_sess[!lowTemplate])
-Sess_PCCComparison[[3]] <- permute(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
-Sess_PCCComparison[[4]] <- cohenD(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
-
-# mPFC
-Sess_PFCComparison <- list(lowPFC_sess[lowTemplate],
-                           lowPFC_sess[!lowTemplate])
-Sess_PFCComparison[[3]] <- permute(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
-Sess_PFCComparison[[4]] <- cohenD(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
-
-# Select the best performing for plotting, from daily performance
-bestindx <- substr(subjList_sess,1,6) %in% best$SubjID
-RI_all_between_sess_plot <- RI_all_between_sess[bestindx, bestindx]
-RI_PFC_sess_plot <- RI_PFC_sess[bestindx, bestindx]
-RI_PCC_sess_plot <- RI_PCC_sess[bestindx, bestindx]
-```
-
-Run-specific SP results still captured unique organizational patterns to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-We again computed each subject's ARI ratio in order to quantify the specificity of the partitions, this time using the mean of 6 across-run (within-participant) ARI values in the numerator of the ratio (Figure 6, right).
-
-``` {r Partition comparison: session ratios, echo = FALSE, message = FALSE, cache = TRUE}
-# Ratio of mean within subject sessions over between subject ones (per-subject)
-# Overall
-# Split the within-subject session RI values per subject
-temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
-withinSubjVals <- split(Sess_overallComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_sess), by = 4), function(x) RI_all_between_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# PCC
-temp <- ceiling(seq_along(Sess_PCCComparison[[1]])/6)
-withinSubjVals <- split(Sess_PCCComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_sess), by = 4), function(x) RI_PCC_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# PFC
-temp <- ceiling(seq_along(Sess_PFCComparison[[1]])/6)
-withinSubjVals <- split(Sess_PFCComparison[[1]], temp)
-
-# Now grab the columns from the similarity matrix for a subject
-betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_sess), by = 4), function(x) RI_PFC_sess[-(x:(x+3)), x:(x+3)])
-
-# And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
-
-# Summarize for plotting
-Sess_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
-                                    RI = c(Sess_RIRatios_PCC, Sess_RIRatios_PFC))
-
-## Stats
-# one-sample signed rank per region
-Sess_PCC_ratioTest <- wilcox.test(Sess_RIRatios_PCC, mu = 1, alternative = "greater")
-Sess_PFC_ratioTest <- wilcox.test(Sess_RIRatios_PFC, mu = 1, alternative = "greater")
-
-# between
-Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T, statType = median)
-Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
-```
-
-As before, a signed rank test showed that both regions had ARI ratios significantly greater than 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), and ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
-This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
-
-### *Correlation vs community detection in mPFC*
-
-``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
-## Between halves analysis for correlation and communities (mPFC only)
-# Spearman to avoid issues with the differences in value ranges
-unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
-D1 <- unthreshComm_PFC_halves_plot
-D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
-Data <- c(D1, D2)
-subjList_halves_plot <- rep(best$SubjID, each = 2)
-allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
-
-```
-
-``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
-# Compare correlation with community approach on mPFC
-# correlations among methods
-tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
-tempCor <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
-tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
-
-# put together in a data frame
-prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
-prepostComp <- melt(prepostComp)
-colnames(prepostComp) <- c("Approach", "Correlation")
-
-# paired permutations and effect sizes for within-subj perm vs corr
-prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
-prepostComp_ES <- cohenD(tempComm, tempCor)
-```
-
-We next explored the possible advantage of community detection relative to a more conventional seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
-We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations.
-We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC.
-We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations across vertices.
-Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals.
-Figure 7A shows that these pairwise comparisons resemble those from the across-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.
-
-Figure 7B shows the test/re-test reliability across days for patterns derived using community detection, seed-based correlation, and across methods (e.g.
-Day 1 community detection versus Day 2 seed-based correlation).
-While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", round(prepostComp_permTest$Pval, digits = 3)))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
-Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences.
-These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies, in addition to their other advantages of being data-driven, unbiased and observer agnostic.
-
-### *Alignment of mPFC community structure with a proposed DN sub-network organization*
-
-The thresholded partitions we identified had conceptual and topographic similarities to DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
-We explored the relationship between the two sets of sub-regions by reproducing their seed-based connectivity approach in two of our subjects.
-In their work, Braga and Buckner [-@Braga2017; @Braga2019] manually selected individual vertices in dorsolateral prefrontal cortex (DLPFC) that produced two spatially anticorrelated, interdigitated networks with distinctive patterns in the temporo-parietal junction (TPJ), inferior parietal lobule (IPL), parahippocampal cortex, mPFC, and PCC.
-We hypothesized that if the SP communities corresponded to one or both of the previously proposed sub-networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas.
-For whole-brain functional connectomes from two individuals (100307 and 101006), we evaluated seeds in each diagnostic region that reproduced networks A and B (correlation coefficients thesholded at 0.2), and confirmed their placement based on functional connectivity patterns observed in the remaining areas.
-In both individuals, seeds in posterior IPL and TPJ most clearly identified networks A and B, respectively.
-The whole-brain seed-based functional connectivity maps for the two individuals are juxtaposed with the corresponding community detection results in Figure 8.
-It is worth noting that a few distinguishing features are missing due to below-threshold correlation values (e.g.
-network B in right PCC of 100307).
-
-Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A.
-However, the non-DN community filled areas not covered by either DN-A or DN-B.
-This result supports the idea that the two approaches serve complementary purposes.
-Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
-
-## Discussion
-
-A considerable amount of meta-analytic work has been dedicated to characterizing the brain activity patterns associated with psychological processes in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across domains [@DelaVega2016; @Kragel2018; @Hiser2018].
-In particular, activation patterns associated with subjective valuation and with the default network (DN) have been suggested to be inseparable in this area, with overlap also partially extending to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
-This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these superficially dissimilar domains might involve a shared set of core cognitive processes [@Acikalin2017; @Clithero2014; @Northoff2012].
-
-However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals.
-Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Mueller2013], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014].
-These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
-However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far [@Braga2017; @Braga2019; @Gordon2017].
-To affirm that DN and valuation share neural substrates in this area requires a method to reliably and precisely capture the functional topography of mPFC in isolated individuals, as well as a quantitative estimate of the degree of topographic heterogeneity across a large group of individuals.
-
-Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Toker2019].
-For 100 individuals, we subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities.
-Restricting our analyses to a general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning that was sensitive to the complex topography of the brain.
-This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use parcels that are several orders of magnitude larger than vertices as the units of analysis.
-Partitioning an individual's brain network through SP has a number of advantages, including identifying communities deterministically, constraining communities to contain a similar number of vertices (i.e.
-preventing the allocation of most vertices to a single community), providing continuous values that relate to the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
-Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], suggested the binary partitioning was appropriate.
-
-We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC.
-The precise spatial positioning of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individual.
-The idiosyncrasy in functional topography was particularly pronounced in mPFC, and was identified in both run-based and day-based analyses.
-Individual-specificity could theoretically arise from a variety of sources.
-For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; @Lopez2019].
-Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
-An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
-
-Network-partitioning methods such as SP are data-driven, and therefore provide no labeling information about the resulting communities.
-We circumvented this issue by independently identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially associated with the DN relative to subjective valuation in our meta-analysis.
-We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals.
-Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.
-
-Our results extend previous work that described individual-specific brain organization.
-Several recent investigations have identified topographic heterogeneity using a different data aspect ratio than we used here [a small number of individuals and a large number of scanning sessions per individual; @Braga2017; @Braga2019; @Gordon2017].
-Previous work has also shown that functional correlations among pre-defined cortical parcels are highly stable within an individual [@Gratton2018b; @Kong2018].
-Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan).
-The motivation to sub-divide DN also stems from recent work by Kernbach et al.
-[-@Kernbach2018], which identified specialized communication of parcels within DN with the rest of the brain in a large pool of individuals.
-
-In addition to the technical advantages noted above, the SP algorithm offers analytical advantages specific to neuroscience.
-We found that SP outperformed a traditional seed-based correlation approach in capturing idiosyncratic functional topography.
-Community detection methods such as SP are stabilized by relying on  all pairwise correlations among cortical vertices (rather than correlations with an individual seed).
-In addition, we found we could increase the temporal stability of SP results by thresholding the underlying Fiedler vector.
-The magnitude of Fiedler vector values has been recently used to characterize the continuous connectivity profile of the insula with the rest of the brain, challenging the notion of discrete parcellations in that region [@Tian2018].
-The combination of discrete classification and graded information yielded by SP provides additional flexibility and richness relative to some other clustering algorithms.
-
-The community organization of PCC and mPFC was congruent with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019].
-The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network.
-Subthreshold vertices from the DN community overlapped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks.
-Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people.
-Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research.
-These two sets of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
-
-Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying individualized topography in a data-driven way.
-The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help characterize heterogenous changes in mPFC activity in disorders such as depression and schizophrenia [@Hiser2018].
-It will be beneficial for future task-based fMRI experiments to be able to characterize where task-evoked activity is situated relative to an individual's overall mPFC organization.
-Our work was originally motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation versus episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], and potential topographic distinctions among multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010].
-An individualized frame of reference will enhance the ability of future studies to gauge similarities and differences among brain activity patterns associated with diverse psychological domains.
-
-\newpage
-## Acknowledgements
-
-We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Daniel Sussman for initial guidance on community detection and evaluation methods.
-This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI award N00014-16-1-2832 and DURIP award N00014-17-1-2304).
-Data were provided by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
-
-\newpage
-
-## Figures
-
-```{r Meta-analysis ROIs (Fig.
-1), out.width = "50%", fig.align = "center", fig.cap= "Meta-analysis results.
-A: Proportion of times each ROI was reported in the valuation and DN literatures.
-B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details).
-Areas in blue represent the remainder of the search space."}
-# brain images were produced using the HCP wb_view. 
-# see the function HCPOut for details on how they were transferred from R to CIFTI
-include_graphics("./Images/ROIS.png")
-```
-
-\bigskip
-
-```{r Representative partitioning (Fig.
-2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307).
-Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
-The bottom brain shows the binarized Fiedler vector, with red areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
-include_graphics("./Images/FB_FV_example.png")
-```
-
-\bigskip
 
@@
 
-\bigskip
+### *Pattern variability over time*
+
+``` {r Variability per subject: Overall, echo = FALSE, message = FALSE, cache = TRUE}
+# Load files
+# these include the community assignment per window, as well as the agreement per window vs total partitioning
+setwd('./Sliding_window/')
+temp <- list.files(pattern = '*Comparisons.csv')
+SC <- lapply(temp, read.csv2)
+temp <- list.files(pattern = '*Values.csv')
+SVals <- lapply(temp, read.csv2)
+
+# concatenate all proportion of DN affiliations per node to produce (1) a histogram for fig 4C, and (2) % of node affiliated with either community > 99% over time
+allPropDN <- sapply(Summaries, "[[", "slidePropDN")
+
+# proportion of fully stable nodes per individual
+prcntStable <- apply(allPropDN, 2, function(subj) {round(mean(subj %in% c(0, 1)), digits = 2)}) * 100
+
+# put all summaries together for model fit
+allSummaries <- do.call(rbind, Summaries)
+allSummaries$SubjID <- rep(subjList, each = nVertices)
+
+# Do a mixed effects GLM (binomial, quasi unavailable on glmer) to estimate the relationship between Fiedler vec and propDN
+SC_FVvPDN_model <- glmer(slidePropDN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
+SC_FVvPDN_modelSummary <- summary(SC_FVvPDN_model)
+allSummaries$FittedVals <- fitted(SC_FVvPDN_model)
+
+# Create a smaller dataframe just to plot the fit
+# Otherwise, plotting the thousands fitted can place an unnecessary burden on the document
+# (at some point, knitting to pdf wouldn't show the logistic plot because of this)
+FiedlerVector <- seq(min(allSummaries$FiedlerVec), max(allSummaries$FiedlerVec), length.out = nVertices)
+formula <- SC_FVvPDN_modelSummary$coefficients[1,1] + (SC_FVvPDN_modelSummary$coefficients[2,1] * FiedlerVector)
+Fitted_Proportion <- exp(formula) / (1 + exp(formula))
+SC_FVvPDN_fits <- data.frame(FiedlerVector, Fitted_Proportion)
+rm(FiedlerVector, formula, Fitted_Proportion)
+
+```
+
+We next sought to identify a set of temporally stable core nodes in each community.
+In order to estimate the stability of partitions over time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min).
+We compared the partitioning derived from each window with the partitioning computed using the entire time series (Figure 4).
 
@@
 
-\bigskip
+``` {r Variability per subject: PCC vs mPFC, echo = FALSE, message = FALSE, cache = TRUE}
+## Check variability for PCC and mPFC separately
+tempSW_PCC <- lapply(SVals, "[", i = posteriorIndx, j =)
+tempSW_PFC <- lapply(SVals, "[", i = !posteriorIndx, j =)
+
+SC_PCC <- data.frame()
+SC_PFC <- data.frame()
+
+# compare the PCC and mPFC partitionings with those produced per window
+for (subj in seq(nSubj)) {
+  tempPCC <- numeric()
+  tempPFC <- numeric()
+  nWins <- ncol(tempSW_PCC[[subj]])
+  for (Win in seq(nWins)) {
+    tempPCC[Win] <- arandi(tempComm_PCC[[subj]]$FiedlerBinary, tempSW_PCC[[subj]][, Win], adjust = T)
+    tempPFC[Win] <- arandi(tempComm_PFC[[subj]]$FiedlerBinary, tempSW_PFC[[subj]][, Win], adjust = T)
+  }
+  dfPCC <- data.frame(SubjID = rep(subjList[subj], nWins),
+                      Window = seq(nWins),
+                      Index = tempPCC)
+  dfPFC <- data.frame(SubjID = rep(subjList[subj], nWins),
+                      Window = seq(nWins),
+                      Index = tempPFC)
+  SC_PCC <- rbind(SC_PCC, dfPCC)
+  SC_PFC <- rbind(SC_PFC, dfPFC)
+}
+
+# and get descriptives for all individuals
+SC_PCC_summary <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = mean)
+SC_PCC_summary$SD <- aggregate(SC_PCC$Index, by = list(SC_PCC$SubjID), FUN = sd)$x
+SC_PCC_summary$Region <- rep("PCC", nSubj)
+SC_PFC_summary <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = mean)
+SC_PFC_summary$SD <- aggregate(SC_PFC$Index, by = list(SC_PFC$SubjID), FUN = sd)$x
+SC_PFC_summary$Region <- rep("mPFC", nSubj)
+SC_PCCPFC_summary <- rbind(SC_PFC_summary, SC_PCC_summary)
+colnames(SC_PCCPFC_summary) <- list("SubjID", "Index", "SD", "Region")
+rm(SC_PCC_summary, SC_PFC_summary)
+
+# Compare mean ARI of sliding windows between regions
+SW_PCCvPFC_permuteTest <- permute(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"], paired = T)
+SW_PCCvPFC_ES <- cohenD(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "PCC"], SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region == "mPFC"])
+
+```
+
+The mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+A subset of nodes showed exceptionally high stability, in that they were assigned to the same community in every time window.
+The percentage of stable nodes ranged from 0 to `r max(prcntStable)`% across individuals (median = `r median(prcntStable)`%, IQR = `r quantile(prcntStable, 0.25)`% - `r quantile(prcntStable, 0.75)`%).
+
+We next tested whether the continuous-valued Fiedler vector (before binarization into discrete communities) carried information about the stability of individual nodes.
+There is precedent in the literature for the idea that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Gkantsidis2003; @Tian2018].
+Therefore, we tested whether the magnitude of the eigenvector values was associated with the stability of nodes over time.
+Specifically, we estimated the proportion of DN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
+The model identified a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), signifying that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
+
+``` {r Threshold values, echo = FALSE, message = FALSE}
+# Get a FV threshold for each subject based on mean vertex stability
+# Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
+TFV <- safely(threshFV)
+tempList <- lapply(Summaries, TFV)
+
+# Store the FV thresholds for all subject 
+threshDF <- data_frame(SubjID = substring(subjList, 1, 6),
+                       Lower = NA,
+                       Upper = NA)
+for (i in seq_along(tempList)) {
+  if (is.null(tempList[[i]]$result)) {
+    # if there wass no clear threshold (i.e. noisy participants), then leave it as 0
+    threshDF[i, 2:3] <- c(0, 0)
+  } else {
+    threshDF[i, 2] <- as.numeric(tempList[[i]]$result[1])
+    threshDF[i, 3] <- as.numeric(tempList[[i]]$result[2])
+  }
+}
+
+# get descriptives
+threshDescriptives <- threshDF %>% 
+                        filter(Lower < 0, Upper > 0) %>% 
+                        summarize(mL = mean(Lower), 
+                                  sdL = sd(Lower), 
+                                  mU = mean(Upper), 
+                                  sdU = sd(Upper)) %>% 
+                        round(., digits = 4)
+
+# number of subjects without stable vertices
+nUnstable <- threshDF %>% 
+                filter(Lower == 0, Upper == 0) %>% 
+                nrow
+
+# Apply threshold to Summaries
+# IMPORTANT: THIS PROCESS OVERWRITES THE VARIABLES FROM THE FIRST COMPARISON SECTION
+# THIS IS DONE FOR STORAGE-SAKE
+if (threshMaps) {
+  for (i in seq(nSubj)) {
+  Summaries[[i]] <- Summaries[[i]] %>%
+    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i, 2]) & FiedlerVec < as.numeric(threshDF[i, 3]), 0, FiedlerVec)) %>%
+    mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
+  }
+}
+
+# percent of stable nodes per subject
+# this can be different from prcntStable because fully stable vertices can technically have low FV values
+# the match between FV and Stability is strong, but not perfect
+prcntSurvived <- sapply(Summaries, function(data) {mean(data$FiedlerBinary != 0.5)})
+
+rm(tempList)
+
+```
+
+These analyses suggest that there is potential value in thresholding the Fiedler vector as a means to identify reliable DN and non-DN vertices on an individual subject basis.
+We therefore thresholded each subject's Fiedler vector to produce these refined maps.
+For each individual, we estimated the threshold by selecting the smallest absolute Fiedler vector value that yielded an average stability across suprathreshold nodes of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
+Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
+The median proportion of retained vertices per individual was `r round(median(prcntSurvived), digits = 2)` (IQR = `r round(quantile(prcntSurvived, 0.25), digits = 2)` - `r round(quantile(prcntSurvived, 0.75), digits = 2)`).
+Sub-threshold vertices were set to zero in Fiedler vector maps and 0.5 in the binarized maps (so that they would not bias the calculation of averages).
+Figure 5A shows the thresholded partitioning for the same individual shown in Figure 2.
+The maps used in all subsequent analyses were thresholded by this individualized criterion.
 
@@
 
-\bigskip
+``` {r Partition comparison: all thresholded, echo = FALSE, message = FALSE, cache = TRUE}
+## Compare partitionings
+# Across subjects
+# Note: the upper and lower triangles can totally be combined before plotting, instead of adding one corrplot over another. Might work on that eventually.
+RI_all_between <- comparePartitions(Data = Summaries, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+RI_all_between_lowtri <- RI_all_between[lower.tri(RI_all_between)]
+
+# ARI among subjects for each region separately
+posteriorIndx <- Summaries[[1]]$y < 0
+tempComm_PCC <- lapply(Summaries, "[", i = posteriorIndx, j =)
+tempComm_PFC <- lapply(Summaries, "[", i = !posteriorIndx, j =)
+RI_PFC <- comparePartitions(Data = tempComm_PFC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+RI_PCC <- comparePartitions(Data = tempComm_PCC, Index = "RI", nSubjects = length(Summaries), subjNames = subjList)
+
+# Let's statistically compare stuff
+testPCC <- RI_PCC[lower.tri(RI_PCC)]
+testPFC <- RI_PFC[lower.tri(RI_PFC)]
+Overall_PCCvsPFC_permTest <- permute(testPCC, testPFC, statType = mean, paired = T)
+Overall_PCCvsPFC_ES <- cohenD(testPCC, testPFC)
+
+# To get the rate of stability per vertex across subjects (used for plotting)
+FB <- do.call(cbind, lapply(Summaries, "[[", "FiedlerBinary"))
+FV <- do.call(cbind, lapply(Summaries, "[[", "FiedlerVec"))
+FBS <- rowMeans(FB)
+FBS[FBS < 0.5] <- 1 - FBS[FBS < 0.5]
+
+```
+
+With these thresholded partitions, we recomputed the overall similarity across participants.
+Compared to before, there was lower topographic agreement across individuals (mean ARI = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`).
+The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between areas was preserved (paired permutation, *p* `r ifelse(Overall_PCCvsPFC_permTest$Pval == 0, "< 0.001", paste("=", Overall_PCCvsPFC_permTest$Pval))`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).
+Figure 5B shows the average of the thresholded partitions across all participants, denoting the proportion of times a vertex was affiliated with the DN community.
+This summary illustrates the common organizational layout of both communities, but also highlights the considerable variability across individuals.
+
+``` {r tSNR evaluation, echo = FALSE, message = FALSE, cache = TRUE}
+## next get the mean tSNR of PCC and mPFC before/after thresholding
+# the first piece of code gets each subject's mean tSNR per region, and reduces to a single matrix
+# the second one is similar, but filtering out vertices that didn't meet the threshold
+# the third one applies summary stats to each list to create a summary table
+snr_means <- list()
+
+snr_means$pre_thresh <- lapply(Summaries, function(data) {
+  data %>% 
+    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
+    group_by(region) %>% 
+    dplyr::summarise(mean_tsnr = mean(tSNR)) %>%
+    ungroup()
+}) %>% reduce(left_join, by = "region")
+
+snr_means$post_thresh <- lapply(Summaries, function(data) {
+  data %>% 
+    filter(FiedlerBinary != 0.5) %>%
+    mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
+    group_by(region) %>% 
+    dplyr::summarise(mean_tsnr = mean(tSNR)) %>%
+    ungroup()
+}) %>% reduce(left_join, by = "region")
+
+# and compute summary stats on each 
+snr_means$overall <- sapply(snr_means, function(x) {
+  c(rowMeans(x[, -1]), apply(x[, -1], 1, sd))
+})
+rownames(snr_means$overall) <- c("mPFC_mean", "PCC_mean", "mPFC_SD", "PCC_SD")
+
+# permutation pre vs post
+tsnrPermute_mPFC <- permute(as.numeric(snr_means$pre_thresh[1, -1]), as.numeric(snr_means$post_thresh[1, -1]), paired = T)
+tsnrPermute_PCC <- permute(as.numeric(snr_means$pre_thresh[2, -1]), as.numeric(snr_means$post_thresh[2, -1]), paired = T)
+tsnrPermute_Post <- permute(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]))
+
+# effect size pre vs post
+tsnrCohen_mPFC <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$pre_thresh[1, -1]))
+tsnrCohen_PCC <- CohenD(as.numeric(snr_means$post_thresh[2, -1]), as.numeric(snr_means$pre_thresh[2, -1]))
+tsnrCohen_Post <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]))
+```
+
+To test the possibility that the higher inter-subject variability in mPFC was driven merely by lower signal quality in the retained vertices, we quantified the temporal signal to noise ratio (tSNR) for each region, both before and after thresholding.
+We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
+In terms of tSNR variability across vertices within each region, mPFC had overall greater spatial standard deviation both before and after thresholding (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59).
+However, tSNR after thresholding was significantly higher for mPFC than PCC (mPFC: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; PCC: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
+This reflected a significant increase in mean tSNR in mPFC as a result of the thresholding step (pre-threshold mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (pre-threshold mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
+In short, mPFC had higher overall tSNR, albeit with greater variability across nodes.
+Applying the thresholding step allowed us to focus the analysis on vertices with high signal quality.
+
+### *Test/re-test reliability across days*
+
+The relatively high inter-individual variability seen in the aggregate map could reflect at least three factors: (1) measurement noise, (2) dynamic variation in mPFC network organization, and (3) stable patterns of functional organization that differ across individuals.
+To arbritrate among these possibilities, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
+Insofar as the observed variability reflects individual-specific brain organization, across-day ARI values should be consistently higher within-individual than between individuals (an example comparison for two individuals is provided in Supplemental Figure 2).
+Figure 6 shows pairwise comparisons among ten example subjects for PCC and mPFC separately (left).
 
@@
 
-\bigskip
+``` {r Partition comparison: halves, echo = FALSE, message = FALSE, cache = TRUE}
+# Load data
+setwd('./Summary_halves/')
+temp <- list.files(pattern = "*_finalSummary.csv")
+subjList_halves <- sapply(temp, substring, first=1, last=9)
+Summaries_halves <- lapply(temp, read.csv)
+
+# Before thresholding, capture within/between daily comparisons for FV vs correlation analysis (only for daily)
+# Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we manually reverted it after visual inspection
+revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1")
+for (subj in revertSubjs) {
+  indx <- grep(subj, subjList_halves)
+  Summaries_halves[[indx]] <- transform(Summaries_halves[[indx]], FiedlerVec = FiedlerVec * -1)
+}
+Summaries_halves_unthresh <- Summaries_halves
+
+# Some participants have strongly uncorrelated maps because 7m isn't fully covered on one of the days
+# ARI doesn't mind this, so the results are fine
+# But the Corr vs FV analysis below is badly affected
+unCorrParticipants <- data.frame(SubjID = subjList,
+                                 Corrs = sapply(seq(1, nSubj * 2, by = 2), function(x) {cor(Summaries_halves_unthresh[[x]]$FiedlerVec, Summaries_halves_unthresh[[x+1]]$FiedlerVec)})) %>%
+  filter(Corrs < 0)
+
+# Load the correlation-based maps from each day for analysis in a subsequent section
+temp <- list.files(pattern = "*_corHalves.csv")
+Correlation_halves <- lapply(temp, read.csv, header = F)
+
+# Apply threshold to Summaries
+if (threshMaps) {
+  # create a vector of repeated indices, so each threshold is applied to each subject twice
+  threshindex <- rep(seq(nSubj), each = 2)
+  count <- 1
+  for (i in threshindex) {
+    Summaries_halves[[count]] <- Summaries_halves[[count]] %>%
+            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i, 2]) & FiedlerVec < as.numeric(threshDF[i, 3]), 0, FiedlerVec)) %>%
+            mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
+    count <- count + 1
+  }
+}
+
+```
+
+``` {r Partition comparison: halves ratios, echo = FALSE, message = FALSE, cache = TRUE}
+## Now compare all possible pairs of subjects (for actual reporting)
+# Compare all halves with RI
+RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+
+# Compare PCC and PFC among all subjects
+tempComm_PCC_halves <- lapply(Summaries_halves, "[", i = posteriorIndx, j =)
+tempComm_PFC_halves <- lapply(Summaries_halves, "[", i = !posteriorIndx, j =)
+RI_PFC_halves <- comparePartitions(Data = tempComm_PFC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+RI_PCC_halves <- comparePartitions(Data = tempComm_PCC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
+
+## Let's compare stuff (not accounting for complex interdependencies in the observations)
+## Overall differences in mean RI between PCC and mPFC
+lowPCC_halves <- RI_PCC_halves[lower.tri(RI_PCC_halves)]
+lowPFC_halves <- RI_PFC_halves[lower.tri(RI_PFC_halves)]
+Halves_PCCvPFC_perm <- permute(lowPCC_halves, lowPFC_halves, statType = mean, paired = T)
+Halves_PCCvPFC_ES <- cohenD(lowPCC_halves, lowPFC_halves) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
+# create a selection matrix containing all within-subject session comparisons
+template <- diagBlocks(ncol(RI_all_between_halves), 2) 
+lowTemplate <- template[lower.tri(template)]
+
+# Overall
+# First list element is the within subject values, second is the between subject values
+lowRIHalves <- RI_all_between_halves[lower.tri(RI_all_between_halves)]
+Halves_overallComparison <- list(lowRIHalves[lowTemplate],
+                                lowRIHalves[!lowTemplate])
+Halves_overallComparison[[3]] <- permute(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
+Halves_overallComparison[[4]] <- cohenD(Halves_overallComparison[[1]], Halves_overallComparison[[2]])
+
+# PCC 
+Halves_PCCComparison <- list(lowPCC_halves[lowTemplate],
+                           lowPCC_halves[!lowTemplate])
+Halves_PCCComparison[[3]] <- permute(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
+Halves_PCCComparison[[4]] <- cohenD(Halves_PCCComparison[[1]], Halves_PCCComparison[[2]])
+
+# mPFC
+Halves_PFCComparison <- list(lowPFC_halves[lowTemplate],
+                           lowPFC_halves[!lowTemplate])
+Halves_PFCComparison[[3]] <- permute(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
+Halves_PFCComparison[[4]] <- cohenD(Halves_PFCComparison[[1]], Halves_PFCComparison[[2]])
+
+## Ratio of mean within subject sessions over between subject ones (per-subject)
+# Overall
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_all_between_halves[lower.tri(RI_all_between_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_halves), by = 2), function(x) RI_all_between_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_overall <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# PCC
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_PCC_halves[lower.tri(RI_PCC_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_halves), by = 2), function(x) RI_PCC_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_PCC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# PFC
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_PFC_halves[lower.tri(RI_PFC_halves)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_halves), by = 2), function(x) RI_PFC_halves[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_PFC <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# Summarize for plotting
+Halves_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
+                                      RI = c(Halves_RIRatios_PCC, Halves_RIRatios_PFC))
+
+## Stats
+# one-sample signed rank per region
+Halves_PCC_ratioTest <- wilcox.test(Halves_RIRatios_PCC, mu = 1, alternative = "greater")
+Halves_PFC_ratioTest <- wilcox.test(Halves_RIRatios_PFC, mu = 1, alternative = "greater")
+
+# between regions
+Halves_mPFCvPCC_permTest <- permute(Halves_RIRatios_PFC, Halves_RIRatios_PCC, paired = T, statType = median)
+Halves_mPFCvPCC_ES <- cohenD(Halves_RIRatios_PFC, Halves_RIRatios_PCC)
+
+# Select a submatrix with the best-performing subjects to show on the matrix figures
+# These will be also displayed on the session matrix
+# This way I don't have to recompute stuff
+tmp <- data_frame(SubjID = subjList,
+                  DailyARI = Halves_PFCComparison[[1]])
+best <- tmp %>% top_n(10, wt = DailyARI) 
+bestindx <- substr(subjList_halves, 1, 6) %in% best$SubjID
+
+RI_all_between_halves_plot <- RI_all_between_halves[bestindx, bestindx]
+RI_PFC_halves_plot <- RI_PFC_halves[bestindx, bestindx]
+RI_PCC_halves_plot <- RI_PCC_halves[bestindx, bestindx]
+
+# Get the same subsection of participants for the correlation plots
+Correlation_halves_plot <- Correlation_halves[bestindx]
+
+# Save unthresholded subjects for comparing and plotting against correlation maps
+unthreshComm_PFC_halves_plot <- lapply(Summaries_halves_unthresh[bestindx], "[", i = !posteriorIndx, j =)
+unthreshComm_PFC_halves <- lapply(Summaries_halves_unthresh, "[", i = !posteriorIndx, j =)
+```
+
+Once again we found low alignment across individuals for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) and mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed comparatively high levels of within-individual agreement (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`).
+We calculated an index of relative specificity by computing the ratio of each individual’s across-day (within-participant) ARI to the mean of all between-participant ARI values involving that individual.
+The index is expected to take on a value near 1 if partitionings are well aligned across individuals and/or are subject to a common level of measurement noise.
+It is expected to exceed 1 insofar as functional network organization is reliable and individual-specific.
+This index is intended to factor out the potential contributions of measurement noise or dynamic instability, which would introduce variability both across individuals and across days.
+
+Figure 6 shows ARI ratios for PCC and mPFC.
+A signed-rank test showed evidence for specificity (i.e.
+ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC, 0.75), digits = 2)`, V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC, 0.75), digits = 2)`, V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`).
+Moreover, the ratios for mPFC were significantly greater than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
+These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns.
+We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner.
+The greater inter-individual consistency in PCC was therefore not merely an artifact of having used a PCC subregion as the basis for label assignment.
+
+### *Test/re-test reliability across runs*
+
+We extended the analysis of per-day data by examining whether the organization of the DN could be extracted using per-run data only.
+The duration of each run (approximately 14 min) falls below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
+Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DN organization from a single run of data.
+
+``` {r Partition comparison: session similarity matrices, echo = FALSE, message = FALSE, cache = TRUE}
+# Load data
+setwd('./Summary_sess/')
+temp <- list.files()
+subjList_sess <- sapply(temp, substring, first = 1, last = 9)
+Summaries_sess <- lapply(temp, read.csv)
+
+# Apply threshold to Summaries
+if (threshMaps) {
+  # create a vector of repeated indices, so each threshold is applied to each subject twice
+  threshindex <- rep(seq(nSubj), each = 4)
+  count <- 1
+  for (i in threshindex) {
+    Summaries_sess[[count]] <- Summaries_sess[[count]] %>%
+            mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
+            mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
+    count <- count + 1
+  }
+}
+
+```
+
+``` {r Partition comparison: session compare all, echo = FALSE, message = FALSE, cache = TRUE}
+# Now run comparisons among all subjects (for actual reporting)
+RI_all_between_sess <- comparePartitions(Data = Summaries_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+tempComm_PCC_sess <- lapply(Summaries_sess, "[", i = posteriorIndx, j =)
+tempComm_PFC_sess <- lapply(Summaries_sess, "[", i = !posteriorIndx, j =)
+RI_PFC_sess <- comparePartitions(Data = tempComm_PFC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+RI_PCC_sess <- comparePartitions(Data = tempComm_PCC_sess, Index = "RI", nSubjects = length(Summaries_sess), subjNames = subjList_sess)
+
+## Let's compare stuff (not accounting for complex interdependencies in the observations)
+## Overall differences in mean RI between PCC and mPFC
+lowPCC_sess <- RI_PCC_sess[lower.tri(RI_PCC_sess)]
+lowPFC_sess <- RI_PFC_sess[lower.tri(RI_PFC_sess)]
+Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T)
+Sess_PCCvPFC_ES <- cohenD(lowPCC_sess, lowPFC_sess) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
+
+## Differences in RI values for sessions within vs between subjects (all subjects pooled together)
+
+# create a selection matrix containing all within-subject session comparisons
+template <- diagBlocks(ncol(RI_all_between_sess), 4) 
+lowTemplate <- template[lower.tri(template)]
+
+# Overall
+# First list element is the within subject values, second is the between subject values
+lowRISess <- RI_all_between_sess[lower.tri(RI_all_between_sess)]
+Sess_overallComparison <- list(lowRISess[lowTemplate],
+                               lowRISess[!lowTemplate])
+Sess_overallComparison[[3]] <- permute(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
+Sess_overallComparison[[4]] <- cohenD(Sess_overallComparison[[1]], Sess_overallComparison[[2]])
+
+# PCC 
+Sess_PCCComparison <- list(lowPCC_sess[lowTemplate],
+                           lowPCC_sess[!lowTemplate])
+Sess_PCCComparison[[3]] <- permute(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
+Sess_PCCComparison[[4]] <- cohenD(Sess_PCCComparison[[1]], Sess_PCCComparison[[2]])
+
+# mPFC
+Sess_PFCComparison <- list(lowPFC_sess[lowTemplate],
+                           lowPFC_sess[!lowTemplate])
+Sess_PFCComparison[[3]] <- permute(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
+Sess_PFCComparison[[4]] <- cohenD(Sess_PFCComparison[[1]], Sess_PFCComparison[[2]])
+
+# Select the best performing for plotting, from daily performance
+bestindx <- substr(subjList_sess,1,6) %in% best$SubjID
+RI_all_between_sess_plot <- RI_all_between_sess[bestindx, bestindx]
+RI_PFC_sess_plot <- RI_PFC_sess[bestindx, bestindx]
+RI_PCC_sess_plot <- RI_PCC_sess[bestindx, bestindx]
+```
+
+Run-specific SP results still captured unique organizational patterns to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+We again computed each subject's ARI ratio in order to quantify the specificity of the partitions, this time using the mean of 6 across-run (within-participant) ARI values in the numerator of the ratio (Figure 6, right).
+
+``` {r Partition comparison: session ratios, echo = FALSE, message = FALSE, cache = TRUE}
+# Ratio of mean within subject sessions over between subject ones (per-subject)
+# Overall
+# Split the within-subject session RI values per subject
+temp <- ceiling(seq_along(Sess_overallComparison[[1]])/6)
+withinSubjVals <- split(Sess_overallComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_all_between_sess), by = 4), function(x) RI_all_between_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# PCC
+temp <- ceiling(seq_along(Sess_PCCComparison[[1]])/6)
+withinSubjVals <- split(Sess_PCCComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_sess), by = 4), function(x) RI_PCC_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# PFC
+temp <- ceiling(seq_along(Sess_PFCComparison[[1]])/6)
+withinSubjVals <- split(Sess_PFCComparison[[1]], temp)
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_sess), by = 4), function(x) RI_PFC_sess[-(x:(x+3)), x:(x+3)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+
+# Summarize for plotting
+Sess_RIRatios_summary <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
+                                    RI = c(Sess_RIRatios_PCC, Sess_RIRatios_PFC))
+
+## Stats
+# one-sample signed rank per region
+Sess_PCC_ratioTest <- wilcox.test(Sess_RIRatios_PCC, mu = 1, alternative = "greater")
+Sess_PFC_ratioTest <- wilcox.test(Sess_RIRatios_PFC, mu = 1, alternative = "greater")
+
+# between
+Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T, statType = median)
+Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)
+```
+
+As before, a signed rank test showed that both regions had ARI ratios significantly greater than 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), and ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
+This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
+
+### *Correlation vs community detection in mPFC*
+
+``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+## Between halves analysis for correlation and communities (mPFC only)
+# Spearman to avoid issues with the differences in value ranges
+unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
+D1 <- unthreshComm_PFC_halves_plot
+D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
+Data <- c(D1, D2)
+subjList_halves_plot <- rep(best$SubjID, each = 2)
+allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
+
+```
+
+``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+# Compare correlation with community approach on mPFC
+# correlations among methods
+tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
+tempCor <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
+tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
+
+# put together in a data frame
+prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
+prepostComp <- melt(prepostComp)
+colnames(prepostComp) <- c("Approach", "Correlation")
+
+# paired permutations and effect sizes for within-subj perm vs corr
+prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
+prepostComp_ES <- cohenD(tempComm, tempCor)
+```
+
+We next explored the possible advantage of community detection relative to a more conventional seed-based functional connectivity analysis for estimating the individual-specific functional topography of mPFC.
+We examined whether maps generated with SP were more similar per participant across days than those computed from seed-based correlations.
+We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC.
+We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations across vertices.
+Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals.
+Figure 7A shows that these pairwise comparisons resemble those from the across-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.
 
@@
 
-\bigskip
+Figure 7B shows the test/re-test reliability across days for patterns derived using community detection, seed-based correlation, and across methods (e.g.
+Day 1 community detection versus Day 2 seed-based correlation).
+While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", round(prepostComp_permTest$Pval, digits = 3)))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
+Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences.
+These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies, in addition to their other advantages of being data-driven, unbiased and observer agnostic.
+
+### *Alignment of mPFC community structure with a proposed DN sub-network organization*
+
+The thresholded partitions we identified had conceptual and topographic similarities to DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
+We explored the relationship between the two sets of sub-regions by reproducing their seed-based connectivity approach in two of our subjects.
+In their work, Braga and Buckner [-@Braga2017; @Braga2019] manually selected individual vertices in dorsolateral prefrontal cortex (DLPFC) that produced two spatially anticorrelated, interdigitated networks with distinctive patterns in the temporo-parietal junction (TPJ), inferior parietal lobule (IPL), parahippocampal cortex, mPFC, and PCC.
+We hypothesized that if the SP communities corresponded to one or both of the previously proposed sub-networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas.
+For whole-brain functional connectomes from two individuals (100307 and 101006), we evaluated seeds in each diagnostic region that reproduced networks A and B (correlation coefficients thesholded at 0.2), and confirmed their placement based on functional connectivity patterns observed in the remaining areas.
+In both individuals, seeds in posterior IPL and TPJ most clearly identified networks A and B, respectively.
+The whole-brain seed-based functional connectivity maps for the two individuals are juxtaposed with the corresponding community detection results in Figure 8.
+It is worth noting that a few distinguishing features are missing due to below-threshold correlation values (e.g.
+network B in right PCC of 100307).
+
+Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A.
+However, the non-DN community filled areas not covered by either DN-A or DN-B.
+This result supports the idea that the two approaches serve complementary purposes.
+Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
 
@@
 ```
+
+## Discussion
+
+A considerable amount of meta-analytic work has been dedicated to characterizing the brain activity patterns associated with psychological processes in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across domains [@DelaVega2016; @Kragel2018; @Hiser2018].
+In particular, activation patterns associated with subjective valuation and with the default network (DN) have been suggested to be inseparable in this area, with overlap also partially extending to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
+This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these superficially dissimilar domains might involve a shared set of core cognitive processes [@Acikalin2017; @Clithero2014; @Northoff2012].
+
+However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals.
+Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Mueller2013], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014].
+These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
+However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far [@Braga2017; @Braga2019; @Gordon2017].
+To affirm that DN and valuation share neural substrates in this area requires a method to reliably and precisely capture the functional topography of mPFC in isolated individuals, as well as a quantitative estimate of the degree of topographic heterogeneity across a large group of individuals.
+
+Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Toker2019].
+For 100 individuals, we subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities.
+Restricting our analyses to a general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning that was sensitive to the complex topography of the brain.
+This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use parcels that are several orders of magnitude larger than vertices as the units of analysis.
+Partitioning an individual's brain network through SP has a number of advantages, including identifying communities deterministically, constraining communities to contain a similar number of vertices (i.e.
+preventing the allocation of most vertices to a single community), providing continuous values that relate to the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
+Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], suggested the binary partitioning was appropriate.
+
+We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC.
+The precise spatial positioning of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individual.
+The idiosyncrasy in functional topography was particularly pronounced in mPFC, and was identified in both run-based and day-based analyses.
+Individual-specificity could theoretically arise from a variety of sources.
+For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; @Lopez2019].
+Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
+An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
+
+Network-partitioning methods such as SP are data-driven, and therefore provide no labeling information about the resulting communities.
+We circumvented this issue by independently identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially associated with the DN relative to subjective valuation in our meta-analysis.
+We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals.
+Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.
+
+Our results extend previous work that described individual-specific brain organization.
+Several recent investigations have identified topographic heterogeneity using a different data aspect ratio than we used here [a small number of individuals and a large number of scanning sessions per individual; @Braga2017; @Braga2019; @Gordon2017].
+Previous work has also shown that functional correlations among pre-defined cortical parcels are highly stable within an individual [@Gratton2018b; @Kong2018].
+Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan).
+The motivation to sub-divide DN also stems from recent work by Kernbach et al.
+[-@Kernbach2018], which identified specialized communication of parcels within DN with the rest of the brain in a large pool of individuals.
+
+In addition to the technical advantages noted above, the SP algorithm offers analytical advantages specific to neuroscience.
+We found that SP outperformed a traditional seed-based correlation approach in capturing idiosyncratic functional topography.
+Community detection methods such as SP are stabilized by relying on  all pairwise correlations among cortical vertices (rather than correlations with an individual seed).
+In addition, we found we could increase the temporal stability of SP results by thresholding the underlying Fiedler vector.
+The magnitude of Fiedler vector values has been recently used to characterize the continuous connectivity profile of the insula with the rest of the brain, challenging the notion of discrete parcellations in that region [@Tian2018].
+The combination of discrete classification and graded information yielded by SP provides additional flexibility and richness relative to some other clustering algorithms.
+
+The community organization of PCC and mPFC was congruent with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019].
+The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network.
+Subthreshold vertices from the DN community overlapped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks.
+Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people.
+Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research.
+These two sets of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
+
+Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying individualized topography in a data-driven way.
+The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help characterize heterogenous changes in mPFC activity in disorders such as depression and schizophrenia [@Hiser2018].
+It will be beneficial for future task-based fMRI experiments to be able to characterize where task-evoked activity is situated relative to an individual's overall mPFC organization.
+Our work was originally motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation versus episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], and potential topographic distinctions among multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010].
+An individualized frame of reference will enhance the ability of future studies to gauge similarities and differences among brain activity patterns associated with diverse psychological domains.
+
+\newpage
+## Acknowledgements
+
+We thank Lauren DiNicola, Daniel Reznik, Xavier Guell, and David Somers for helpful discussions, and Daniel Sussman for initial guidance on community detection and evaluation methods.
+This work was supported by grants from the National Science Foundation (BCS-1755757 and BCS-1625552) and the Office of Naval Research (MURI award N00014-16-1-2832 and DURIP award N00014-17-1-2304).
+Data were provided by the Human Connectome Project, WU-Minn Consortium (Principal Investigators: David Van Essen and Kamil Ugurbil; 1U54MH091657) funded by the 16 NIH Institutes and Centers that support the NIH Blueprint for Neuroscience Research; and by the McDonnell Center for Systems Neuroscience at Washington University.
+
+\newpage
 
@@
 include_graphics("./Images/ARI_comparison.png")
+
+# # the second plot (simulation), showing decay of similarity as differences increase
+# library(mcclust)
+# library(reshape2)
+# 
+# # Produce a random vector with 100 binary classifications
+# n <- 4801
+# v1 <- rbinom(n = n, size = 1, prob = 0.5)
+# 
+# # Data frame to store evaluations
+# evals <- data.frame(Diffs = seq(n),
+#                     ARI = rep(0,n),
+#                     RI = rep(0,n),
+#                     EQ = rep(0,n))
+# 
+# # Check the degree of agreement per metric for each incremental switch in affiliation
+# for (i in seq(n)) {
+#   
+#   # Switch affiliation up to the ith node
+#   ifelse(i < n, v2temp <- c((1 - v1[seq(i)]), v1[(i+1):n]), v2temp <- v1)
+#   
+#   # Evaluate
+#   evals$ARI[i] <- arandi(v1,v2temp)
+#   evals$RI[i] <- arandi(v1,v2temp, adjust = F)
+#   evals$EQ[i] <- mean(v1 == v2temp)
+#   
+# }
+# 
+# # Make the data.frame long instead of wide for ggplot
+# evals <- melt(evals[seq(n-1),], id.vars = "Diffs")
+# 
+# # And plot
+# ggplot(data = evals, aes(Diffs, value, group = variable, color = variable)) + 
+#   geom_line(size = 1.5) +
+#   labs(x = "Number of Class Differences", y = "Similarity Value") +
+#   scale_color_discrete(name = "Method") +
+#   scale_x_continuous(breaks = c(seq(0, 4000, by = 1000), 4801)) +
+#   theme(legend.position = c(0.9, 0.32),
+#         legend.key=element_blank(),
+#         panel.grid.major = element_blank(), 
+#         panel.grid.minor = element_blank(), 
+#         panel.background = element_blank(), 
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 22))
 ```

### 2019-08-19 communityDetection.R
added ARI simulation example and fixed a tiny bug in thresholding communities in example script

@@ -19,7 +19,7 @@ fisherTanh <- function(Data = padjMatrix, preThresh = NA){
   
   if (is.numeric(preThresh)) {
     Data[Data == 1] <- 0.999
-    Data[Data < preThresh] <- 0
+    Data[abs(Data) < preThresh] <- 0
     transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
   } else {
     # tanh

### 2019-08-20 graphAnalysis.R
don't threshold correlation matrices anymore

@@ -29,7 +29,7 @@ fisherTanh <- function(Data = padjMatrix, preThresh = NA){
   
   if (is.numeric(preThresh)) {
     Data[Data == 1] <- 0.999
-    Data[Data < preThresh] <- 0
+    Data[abs(Data) < preThresh] <- 0
     transformed$tanhZ <- 0.5 * log((1 + Data) / (1 - Data))
   } else {
     # tanh
@@ -105,7 +105,7 @@ getCoords <- function(Labels, Coords, TimeSeries = FALSE){
 
 
 # Run community detection on ROIs
-communityDetection <- function(Data = NA, ROIS = "None", modularity = T, extras = T, indx = NA) {
+communityDetection <- function(Data = NA, ROIS = "None", modularity = T, extras = T, indx = NA, thresh = corThresh) {
   # This function relies on having the timeSeries data uploaded, and labelCoords_vertex as the row names for ROI selection
   # Extras dictates whether the community object + correlation matrix should also be extracted
   #
@@ -145,7 +145,7 @@ communityDetection <- function(Data = NA, ROIS = "None", modularity = T, extras 
   corrMatrix <- corrMat
   
   # transform to Fisher's (think of thresholding)
-  transfMat <- fisherTanh(Data = corrMat)
+  transfMat <- fisherTanh(Data = corrMat, preThresh = thresh)
   
   # Store Fisher transformed vals for graphing
   corrMat <- transfMat$tanhZ
@@ -471,8 +471,9 @@ comparePartitions <- function(Data = NA, MOI = "FiedlerBinary", Index = "VI", nS
 ###------- Setups ---------------
 write('Setting up variables for future computations...', stdout())
 
-## Choose what to analyze
+## general setups
 Sliding <- T
+corThresh <- 0
 
 # colors to differentiate other things
 #Cols <- c("aquamarine4","#D9541A",rgb(190,190,190,100, maxColorValue = 255)) # left, right, interhemisphere

### 2019-08-20 communityDetection.R
don't threshold correlation matrices anymore

@@ -76,7 +76,7 @@ HCPOut <- function(Data = dmnval7mCommunities[[1]], MOI = "Membership", SubjID =
 }
 
 # if a minimum corr value is desired prior to clustering (otherwise set NA for p-value based thresholding)
-corrThresh <- NA
+corrThresh <- 0
 
 
 # ROIs used on the paper

### 2019-08-26 Manuscript.Rmd
added tSNR wording and map

@@
 We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
+A map of the mean tSNR across individuals can be found on Supplemental Figure 3.
 In terms of tSNR variability across vertices within each region, mPFC had overall greater spatial standard deviation both before and after thresholding (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59).
@@
 
+\bigskip
+
+```{r Extra examples (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Signal quality prior to FV thresholding.
+Left: Surface map displaying the vertex-wise mean tSNR across individuals.
+Right: Mean tSNR for mPFC and PCC across individuals."}
+# To get the box plot:
+#   
+# allSnr <- list()
+# 
+# for (i in seq_along(Summaries)) {
+#   
+#   allSnr[[i]] <- Summaries[[i]] %>% 
+#                   mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
+#                   group_by(region) %>%
+#                   summarise(mtSNR = mean(tSNR))
+#                 
+# }
+# 
+# allSnr <- do.call(rbind, allSnr)
+# 
+# ggplot(data = allSnr, aes(region, mtSNR, fill = region)) + 
+#   geom_boxplot(show.legend = F) +
+#   scale_fill_manual(values = Cols[seq(2)]) +
+#   labs(x = "", y = "mean tSNR") +
+#   theme(legend.position = c(0.9, 0.32),
+#         legend.key=element_blank(),
+#         panel.grid.major = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.background = element_blank(),
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 22))
+
+include_graphics("./Images/tSNR.png")
+```
+
 \newpage

### 2019-08-27 Manuscript.Rmd
added a missing ROI to the example analysis script

@@
 # raw counts for each area per literature
-nRegions_sv <- do.call(rbind, studyList_sv) %>% count #(X1)
-nRegions_DN <- do.call(rbind, studyList_DN) %>% count #(X1)
+nRegions_sv <- do.call(rbind, studyList_sv) %>% count(X1)
+nRegions_DN <- do.call(rbind, studyList_DN) %>% count(X1)
 nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")
@@
 
-```{r Extra examples (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Signal quality prior to FV thresholding.
+```{r tSNR (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Signal quality prior to FV thresholding.
 Left: Surface map displaying the vertex-wise mean tSNR across individuals.
@@
 
+```{r extra B&B checks with silhouette (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga & Buckner (2017)."}
+# # produce the silhouette plot
+# setwd('Silhouette')
+# 
+# # load data and get the overall plus mean (+SE) silhouette scores per cluster x subject
+# files <- list.files()
+# data <- lapply(files, read_csv) %>% reduce(full_join)
+# data2 <- data %>% 
+#   group_by(Clusters) %>%
+#   summarise(mSil = mean(Silhouette),
+#             seSil = sd(Silhouette) / sqrt(length(Silhouette)))
+# 
+# # plot
+# ggplot() +
+#   geom_line(data = data, aes(Clusters, Silhouette, group = SubjID), show.legend = F, alpha = 0.09, size = 1.5) +
+#   geom_point(data = data2, aes(Clusters, mSil), show.legend = F, size = 2) +
+#   geom_errorbar(data = data2, aes(Clusters, ymin = mSil - seSil, ymax = mSil + seSil), width = 0.1, size = 1) +
+#   labs(x = "Number of Clusters", y = "Silhouette Score") +
+#   theme(legend.key = element_blank(),
+#         panel.grid.major = element_blank(), 
+#         panel.grid.minor = element_blank(), 
+#         panel.background = element_blank(), 
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 22))
+
+```
+
 \newpage

### 2019-08-27 graphAnalysis.R

@@ -556,7 +556,8 @@ mPFC_labels <- c("_a24_",
                "_s32_",
                "_p24_",
                "_10d_",
-               "_25_")
+               "_25_",
+               "R_9a_ROI")
 
 # Little test to ensure that the ROIs match before running the whole thing
 if (FALSE %in% (mPFC_labels %in% c(mPFC_labels, "Blah"))) {

### 2019-08-27 Manuscript.Rmd
small updates to remove nas during permutations

@@
 ## Permutation for 2 groups
-permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){
+permute <- function(group1, group2, statType = mean, nPerms = 5000, paired = FALSE, na.rm = FALSE){
+
+  # remove NAs? in case of paired, remove the same measure in both groups 
+  # (not for independent samples, for which NAs are removed by default)
+  if (na.rm & paired) {
+    g1 <- which(is.na(group1))
+    g2 <- which(is.na(group2))
+    nas <- c(g1, g2)
+
+    if (length(nas) > 0) {
+      group1 <- group1[-nas]
+      group2 <- group2[-nas]
+    }
+  }
 
@@
   if (paired == FALSE) {
-
     for (i in 1:nPerms){
@@
       # stats
-      tempDiffs <- statType(tempOne,na.rm=T) - statType(tempTwo,na.rm=T)
+      tempDiffs <- statType(tempOne, na.rm = T) - statType(tempTwo, na.rm = T)
       summaryPerm$jointDist[i] <- tempDiffs # statType(tempDiffs, na.rm = T) 
-
-    }
-
+    }  
   } else {
-
     for (i in 1:nPerms){
-
       # shift labels in a pairwise fashion
@@
       summaryPerm$jointDist[i] <- tempDiffs
-
-    }
-
+    }
   }
@@
   # get the observed difference
-  diffs <- statType(group1,na.rm=T) - statType(group2,na.rm=T)
+  diffs <- statType(group1, na.rm=T) - statType(group2, na.rm=T)
   observedAbs <- abs(diffs) # maybe leave it as means here
@@
 # Load data, create a subject list, get the total n, and the number of vertices
-setwd('./Summary/')
+setwd('Summary/')
 temp <- list.files()
@@
     group_by(region) %>% 
-    dplyr::summarise(mean_tsnr = mean(tSNR)) %>%
+    dplyr::summarise(mean_tsnr = mean(tSNR, na.rm = T)) %>%
     ungroup()
@@
 snr_means$overall <- sapply(snr_means, function(x) {
-  c(rowMeans(x[, -1]), apply(x[, -1], 1, sd))
+  c(rowMeans(x[, -1], na.rm = T), apply(x[, -1], 1, sd, na.rm = T))
 })
@@
 # permutation pre vs post
-tsnrPermute_mPFC <- permute(as.numeric(snr_means$pre_thresh[1, -1]), as.numeric(snr_means$post_thresh[1, -1]), paired = T)
-tsnrPermute_PCC <- permute(as.numeric(snr_means$pre_thresh[2, -1]), as.numeric(snr_means$post_thresh[2, -1]), paired = T)
-tsnrPermute_Post <- permute(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]))
+tsnrPermute_mPFC <- permute(as.numeric(snr_means$pre_thresh[1, -1]), as.numeric(snr_means$post_thresh[1, -1]), paired = T, na.rm = T)
+tsnrPermute_PCC <- permute(as.numeric(snr_means$pre_thresh[2, -1]), as.numeric(snr_means$post_thresh[2, -1]), paired = T, na.rm = T)
+tsnrPermute_Post <- permute(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]), na.rm = T)
 
@@
 lowPFC_sess <- RI_PFC_sess[lower.tri(RI_PFC_sess)]
-Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T)
+Sess_PCCvPFC_perm <- permute(lowPCC_sess, lowPFC_sess, statType = mean, paired = T, na.rm = T)
 Sess_PCCvPFC_ES <- cohenD(lowPCC_sess, lowPFC_sess) # caveat: maybe not ideal for bounded values, like RI. BUT VI yields similar results.
@@
 # between
-Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T, statType = median)
+Sess_mPFCvPCC_permTest <- permute(Sess_RIRatios_PFC, Sess_RIRatios_PCC, paired = T, statType = median, na.rm = T)
 Sess_mPFCvPCC_ES <- cohenD(Sess_RIRatios_PFC, Sess_RIRatios_PCC)

### 2019-08-30 Manuscript.Rmd
adding sulcal morphology analyses and silhouette description

@@
 ---
-title: 'Individual heterogeneity in the functional network topography of medial prefrontal cortex'
-subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
+title: Individual heterogeneity in the functional network topography of medial prefrontal
+  cortex
 author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
+csl: apa.csl
 output:
+  word_document: default
   pdf_document:
-    keep_tex: false
     highlight: haddock
-bibliography: mPFC_paper.bib
-csl: apa.csl
+    keep_tex: no
 header-includes:
@@
 - \usepackage{float}
-    - \newcommand{\beginsupplement}{ 
-        \setcounter{table}{0}  
-        \renewcommand{\thetable}{S\arabic{table}} 
-        \setcounter{figure}{0} 
-        \renewcommand{\thefigure}{S\arabic{figure}}
-      }
-
+- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
+  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
+subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
+bibliography: mPFC_paper.bib
 ---
@@
 # And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+Sess_RIRatios_overall <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]], na.rm = T) / mean(betweenSubjVals[[i]], na.rm = T)})
 
@@
 # And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+Sess_RIRatios_PCC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]], na.rm = T) / mean(betweenSubjVals[[i]], na.rm = T)})
 
@@
 # And get a vector of the meanWithin / meanBetween ratio per subject
-Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]]) / mean(betweenSubjVals[[i]])})
+Sess_RIRatios_PFC <- sapply(seq(nSubj), function(i) {mean(withinSubjVals[[i]], na.rm = T) / mean(betweenSubjVals[[i]], na.rm = T)})
 
@@
 
-As before, a signed rank test showed that both regions had ARI ratios significantly greater than 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), and ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
+As before, a signed rank test showed that both regions had ARI ratios significantly greater than 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25, na.rm = T), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75, na.rm = T), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC, na.rm = T), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25, na.rm = T), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75, na.rm = T), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), and ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
 This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
@@
 
+### *Relationship between functional organization and sulcal morphology*
+
+``` {r sulcal comparison, echo=FALSE, message = FALSE, cache = TRUE}
+# load curvature data and retain only the relevant subjects
+setwd('Curvature')
+files <- list.files(pattern = "curvature")
+curvList <- substr(files, 1, 6)
+files <- files[curvList %in% subjList]
+
+# update Summaries dfs
+curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries[[1]]$Vertex]})
+for (i in seq(nSubj)) {
+  Summaries[[i]]$Curvature <- curvData[[i]]
+}
+
+# select vmPFC like Lopez-Persem
+
+```
+
 ### *Alignment of mPFC community structure with a proposed DN sub-network organization*
@@
 
-```{r extra B&B checks with silhouette (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga & Buckner (2017)."}
+```{r extra B&B checks with silhouette (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga & Buckner (2017).
+*ADD KMEANS DEETS HERE*.
+B: K-means based silhouette scores were computed per individual to determine the appropriate number of clusters within the search space.
+Scores decreased as the number of clusters increased, suggesting that a bisection was the best solution.
+Paired permutations comparing mean scores across individuals indicated that the difference between two (mean = 0.042, SE = 0.001) and three (mean = 0.032, SE = 0.0009) cluster solutions was significant (*p* < 0.0001, Cohen's D = 0.96)"}
 # # produce the silhouette plot
@@
 #   geom_line(data = data, aes(Clusters, Silhouette, group = SubjID), show.legend = F, alpha = 0.09, size = 1.5) +
+#   #geom_line(data = data2, aes(Clusters, mSil), show.legend = F, size = 1.2) +
+#   geom_errorbar(data = data2, aes(Clusters, ymin = mSil - seSil, ymax = mSil + seSil), width = 0.1, size = 1) +
 #   geom_point(data = data2, aes(Clusters, mSil), show.legend = F, size = 2) +
-#   geom_errorbar(data = data2, aes(Clusters, ymin = mSil - seSil, ymax = mSil + seSil), width = 0.1, size = 1) +
 #   labs(x = "Number of Clusters", y = "Silhouette Score") +
@@
 #         text = element_text(size = 22))
-
+# 
+# # paired permutation comparing the median silhouete score between 2 and 3 clusters
+# t <- data %>% 
+#   filter(Clusters == 2:3) %>% 
+#   spread(Clusters, Silhouette)
+# silhPerm <- permute(t$`2`, t$`3`, paired = T, statType = mean)
+# silhES <- cohenD(t$`2`, t$`3`)
+
+include_graphics("./Images/kmeansVSsp.png")
 ```

### 2019-08-30 Manuscript.Rmd
working sulcal relationship. needs polishing though

@@
 
-# update Summaries dfs
+# select vmPFC like Lopez-Persem
+# select bilateral parcels that cover the mask seen in fig. 4B in Lopez-Persem et al. 2019
+# the parcels surrounding sulci ROS-S and SU-ROS are: a24, p32, s32, 10r
+persemROI <- c("_25_", "_s32_", "_a24_", "_10v_", "_10r_", "_p32_")
+primarySulci <- c("L_a24_ROI", "R_a24_ROI", "L_s32_ROI", "R_s32_ROI", "L_p32_ROI", "R_p32_ROI", "L_10r_ROI", "R_10r_ROI")
+
+# update Summaries dfs, and reduce to vmPFC only
 curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries[[1]]$Vertex]})
@@
   Summaries[[i]]$Curvature <- curvData[[i]]
-}
-
-# select vmPFC like Lopez-Persem
-
+  Summaries[[i]]$SubjID <- subjList[[i]]
+}
+
+curvVmpfc <- lapply(Summaries, getCoords, Labels = persemROI)
+curvVmpfc <- lapply(curvVmpfc, "[[", "Coords")
+
+# compute per-subject correlations between Fiedler Vector and curvature
+curvCors <- sapply(curvVmpfc, function(subj) {cor(subj$Curvature, subj$FiedlerVec)})
+
+# mimic the binning and averaging they did
+do.call(rbind, curvVmpfc) %>%
+  mutate(Curvature = round(Curvature, digits = 1)) %>%
+  filter(Curvature > -0.3,
+         FiedlerVec > 0.01) %>%
+  group_by(SubjID, Curvature) %>%
+  summarise(mFV = mean(FiedlerVec)) %>%
+  group_by(Curvature) %>%
+  summarise(meanFV = mean(mFV),
+            seFV = sd(mFV, na.rm = T) / sqrt(100)) %>%
+  ggplot(aes(Curvature, meanFV)) +
+    geom_point(show.legend = F, size = 1.5) +
+    geom_errorbar(aes(Curvature, ymin = meanFV - seFV, ymax = meanFV + seFV), width = 0.01, size = 1) +
+    theme_classic()
 ```

### 2019-09-03 Manuscript.Rmd
structure vs function analyses ready

--- 2019-08-30 Manuscript.Rmd
@@
 
-# update Summaries dfs
+# select vmPFC like Lopez-Persem
+# select bilateral parcels that cover the mask seen in fig. 4B in Lopez-Persem et al. 2019
+# the parcels surrounding sulci ROS-S and SU-ROS are: a24, p32, s32, 10r
+persemROI <- c("_25_", "_s32_", "_a24_", "_10v_", "_10r_", "_p32_", "_OFC_")
+primarySulci <- c("L_a24_ROI", "R_a24_ROI", "L_s32_ROI", "R_s32_ROI", "L_p32_ROI", "R_p32_ROI", "L_10r_ROI", "R_10r_ROI")
+
+indx <- getCoords(Labels = persemROI, Coords = Summaries[[1]])$Index
+vmpfc <- rep(0, nVertices)
+vmpfc[indx] <- 1
+
+# update Summaries dfs, and reduce to vmPFC only
 curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries[[1]]$Vertex]})
@@
   Summaries[[i]]$Curvature <- curvData[[i]]
-}
-
-# select vmPFC like Lopez-Persem
+  Summaries[[i]]$SubjID <- subjList[[i]]
+  Summaries[[i]]$vmpfc <- vmpfc
+  Summaries[[i]] <- Summaries[[i]] %>% mutate(region = case_when(
+    y < 0 ~ "PCC",
+    vmpfc == 1 ~ "vmPFC",
+    TRUE ~ "dmPFC"
+  ),
+  sulcus = ifelse(Curvature < 0, 1, 0))
+}
+
+# # mimic the binning and averaging L-P did on vmPFC
+# # this will plot a similar figure for a similar mask, plus a more dorsal mPFC one and PCC
+# do.call(rbind, Summaries) %>%
+#   mutate(Curvature = round(Curvature, digits = 1)) %>%
+#   filter(Curvature > -0.5,
+#          FiedlerVec > 0) %>% 
+#   group_by(SubjID, region, Curvature) %>%
+#   summarise(mFV = mean(FiedlerVec)) %>%
+#   group_by(region, Curvature) %>%
+#   summarise(meanFV = mean(mFV),
+#             seFV = sd(mFV, na.rm = T) / sqrt(100)) %>%
+#   ggplot(aes(Curvature, meanFV, color = region)) +
+#     geom_line(size = 1.5) +
+#     labs(y = "Mean Fiedler Vector Value", color = "Region") +
+#     geom_errorbar(aes(Curvature, ymin = meanFV - seFV, ymax = meanFV + seFV), width = 0.05, size = 1.5) +
+#     scale_x_continuous(breaks = c(-0.4, -0.2, 0, 0.2, 0.4, 0.6, 0.8)) +
+#     geom_point(size = 3) +
+#     scale_color_manual(values = c("firebrick", "dodgerblue4", "gold2")) +
+#     geom_vline(xintercept = 0, linetype = "dashed") +
+#     theme(#legend.position = c(0.9, 0.32),
+#           legend.key=element_blank(),
+#           panel.grid.major = element_blank(),
+#           panel.grid.minor = element_blank(),
+#           panel.background = element_blank(),
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 22))
+
+# MIXED EFFECTS LOGISTIC ESTIMATING SULCUS FROM FV AND REGION, WORKS BUT CHANGE REFERENCE
+t <- do.call(rbind, Summaries) %>%
+  mutate(Curvature = round(Curvature, digits = 1),
+         region = factor(region, levels = list("vmPFC", "residual_mPFC", "PCC"))) #%>%
+  #filter(abs(FiedlerVec) > 0.01)
+
+glmodel2 <- glmer(FiedlerBinary ~ Curvature * region + (1 | SubjID), data = t, family = "binomial")
 

### 2019-09-03 Manuscript.Rmd
further cleaning of the structural code

--- 2019-08-30 Manuscript.Rmd
@@
   Summaries[[i]]$Curvature <- curvData[[i]]
-}
-
-# select vmPFC like Lopez-Persem
+  Summaries[[i]]$SubjID <- subjList[[i]]
+  Summaries[[i]]$vmpfc <- vmpfc
+  Summaries[[i]] <- Summaries[[i]] %>% mutate(region = case_when(
+    y < 0 ~ "PCC",
+    vmpfc == 1 ~ "vmPFC",
+    TRUE ~ "dmPFC"
+  ),
+  sulcus = ifelse(Curvature < 0, 1, 0))
+}
+
+# # mimic the binning and averaging L-P did on vmPFC
+# # this will plot a similar figure for a similar mask, plus a more dorsal mPFC one and PCC
+# do.call(rbind, Summaries) %>%
+#   mutate(Curvature = round(Curvature, digits = 1)) %>%
+#   filter(Curvature > -0.5) %>%
+#   group_by(SubjID, region, FiedlerBinary, Curvature) %>%
+#   summarise(mFV = mean(FiedlerVec)) %>%
+#   group_by(region, FiedlerBinary, Curvature) %>%
+#   summarise(meanFV = mean(mFV),
+#             seFV = sd(mFV, na.rm = T) / sqrt(100)) %>%
+#   ggplot(aes(Curvature, meanFV, color = region, linetype = as.character(FiedlerBinary))) +
+#     geom_line(size = 1.2, show.legend = F) +
+#     labs(y = "Mean Fiedler Vector Value", color = "Region") +
+#     geom_errorbar(aes(Curvature, ymin = meanFV - seFV, ymax = meanFV + seFV), width = 0.08, size = 1.2, linetype = "solid", show.legend = F) +
+#     scale_x_continuous(breaks = c(-0.4, 0, 0.4, 0.8)) +
+#     geom_point(size = 2) +
+#     scale_color_manual(values = c("firebrick", "dodgerblue4", "gold2")) +
+#     geom_vline(xintercept = 0, linetype = "dashed") +
+#     geom_hline(yintercept = 0, linetype = "dashed") +
+#     theme(#legend.position = c(0.9, 0.32),
+#           legend.key=element_blank(),
+#           panel.grid.major = element_blank(),
+#           panel.grid.minor = element_blank(),
+#           panel.background = element_blank(),
+#           axis.line = element_line(colour = "black"),
+#           text = element_text(size = 22))
+
+# MIXED EFFECTS LOGISTIC ESTIMATING SULCUS FROM FV AND REGION, WORKS BUT CHANGE REFERENCE
+sulcData <- do.call(rbind, Summaries) %>%
+  mutate(Curvature = round(Curvature, digits = 1),
+         region = factor(region, levels = list("vmPFC", "dmPFC", "PCC"))) #%>%
+  #filter(abs(FiedlerVec) > 0.01)
+
+sulcGLM <- list()
+sulcGLM$vmpfc <- glmer(FiedlerBinary ~ Curvature * region + (1 | SubjID), data = sulcData, family = "binomial")
+sulcData$region <- factor(sulcData$region, levels = list("dmPFC", "vmPFC", "PCC"))
+sulcGLM$dmpfc <- glmer(FiedlerBinary ~ Curvature * region + (1 | SubjID), data = sulcData, family = "binomial")
+
+# right now it looks like vmpfc FV is negatively related to curvature, but the opposite is true for dmPFC
+lapply(sulcGLM, summary)
 

### 2019-09-04 Manuscript.Rmd
intro reframe

@@
 
-  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large and diverse set of cognitive functions [@Hiser2018; @Kragel2018].
-One such function is subjective valuation during economic decision making.
-Both mPFC and PCC (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
-Both mPFC and PCC are also among the regions implicated in a set of functions associated with the default network (DN).
-DN effects include a decrease in BOLD activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Mckiernan2003; @Laird2009], as well as a distinctive pattern of inter-region correlations in resting-state fMRI data [@Greicius2003; @Fox2005; @Yeo2011].
-
-  Coordinate-based meta-analyses of the fMRI literature show that valuation and DN effects occur in overlapping and largely indistinguishable regions of ventral mPFC [@Acikalin2017].
-The two sets of effects diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DN.
+  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large and diverse set of cognitive processes [@Hiser2018; @Kragel2018], and are among the regions implicated in a set of functions associated with the default network (DN) [@Buckner2008].
+In humans, areas in the DN are chiefly characterized by an increase in BOLD activity in the absence of externally oriented tasks [@Buckner2008], which is mirrored by a decrease in activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Laird2009; @Mckiernan2003].
+Since activity in the DN is related to the availability to engage in introspective thought, its distincitve topographical pattern is often captured by inter-region correlations in resting-state fMRI data [@Buckner2008; @Fox2005; @Greicius2003; @Yeo2011].
+
+  In addition to their role in undirected mentation, mPFC and PCC participate in subjective valuation during economic decision making.
+Both regions (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
+While many cognitive functions can be at least partially separated in mPFC [@DelaVega2016; @Hiser2018; @Kragel2018], coordinate-based meta-analyses of the fMRI literature show that valuation indistinguishably overlaps with the DN in ventral mPFC [@Acikalin2017].
+However, subjective valuation and introspective cognition diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DN.
 Within PCC and adjacent precuneus, a more posterior subregion appears DN-specific, whereas a more anterior subregion is implicated in both effects.
-One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within partially overlapping distributed brain systems that subserve valuation and DN effects.
-This colocalization has prompted theories that valuation and DN-related processes share common elements at the psychological level.
+One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within partially overlapping distributed brain systems that subserve valuation and DN-related cognition.
+This colocalization has prompted theories that these processes share common elements at the psychological level.
 For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Acikalin2017; @Clithero2014; @Northoff2012; @Reddan2018].
@@
 Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019].
-It is therefore possible that the previously reported overlap of DN and valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
-An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of DN effects within mPFC and PCC in a large sample of individuals.
-This evaluation of variability during rest will provide a frame of reference for individualized topographical estimation of behavioral effects (such as valuation) in the future.
+It is therefore possible that the previously reported overlap of the DN with valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
+An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of the DN within mPFC and PCC in a large sample of individuals.
+This evaluation of variability during rest will provide a frame of reference for individualized topographical estimation of behavioral effects (such as valuation) in the future, and could provide insights on the extent to which certain task-positive effects attributed to DN regions truly belong to this network [@Spreng2012].
 
@@
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
+We found that the DN community was likely to be located within principal sulci in ventral mPFC and PCC.
 Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019].
-Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
+Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, provides a new framework and tool set for future investigations of overlap across cognitive domains, and motivates future re-examination of seemingly inseparable cognitive processes (such as valuation and introspective thought) in these areas.
 
@@
 
-We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DN effects.
+We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DN-related processes.
 For subjective valuation, we gathered peak activation coordinates from 200 studies that were associated with positive effects in contrasts of higher-value minus lower-value outcomes or prospects [@Bartra2013].
-For DN, we acquired coordinates from 80 studies that were related to task-deactivation [@Laird2009].
+For DN, we acquired coordinates from 80 studies that were related to task-deactivation (i.e.
+findings where externally directed tasks reduced BOLD compared to a baseline) [@Laird2009].
 The coordinates represent areas that exceeded the statistical significance threshold in each original study.
@@
 unthreshComm_PFC_halves <- lapply(Summaries_halves_unthresh, "[", i = !posteriorIndx, j =)
+
+## RI ratio analysis for Modularity
+# bottom line: the ratios are notably smaller but still above one, and the diffs between mPFC and PCC remain
+RI_PFC_halves_Modularity <- comparePartitions(Data = tempComm_PFC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves, MOI = "Membership")
+RI_PCC_halves_Modularity <- comparePartitions(Data = tempComm_PCC_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves, MOI = "Membership")
+
+# PCC
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_PCC_halves_Modularity[lower.tri(RI_PCC_halves_Modularity)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PCC_halves_Modularity), by = 2), function(x) RI_PCC_halves_Modularity[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_PCC_Modularity <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# PFC
+# Split the within-subject session RI values per subject
+withinSubjVals <- RI_PFC_halves_Modularity[lower.tri(RI_PFC_halves_Modularity)][lowTemplate]
+
+# Now grab the columns from the similarity matrix for a subject
+betweenSubjVals <- lapply(seq(1, ncol(RI_PFC_halves_Modularity), by = 2), function(x) RI_PFC_halves_Modularity[-(x:(x+1)), x:(x+1)])
+
+# And get a vector of the meanWithin / meanBetween ratio per subject
+Halves_RIRatios_PFC_Modularity <- sapply(seq(nSubj), function(i) {withinSubjVals[[i]] / mean(betweenSubjVals[[i]])})
+
+# Summarize for plotting
+Halves_RIRatios_summary_Modularity <- data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)),
+                                      RI = c(Halves_RIRatios_PCC_Modularity, Halves_RIRatios_PFC_Modularity))
+
+# stats between regions
+Halves_mPFCvPCC__Modularity_permTest <- permute(Halves_RIRatios_PFC_Modularity, Halves_RIRatios_PCC_Modularity, paired = T, statType = median)
+Halves_mPFCvPCC_Modularity_ES <- cohenD(Halves_RIRatios_PFC_Modularity, Halves_RIRatios_PCC_Modularity)
+
 ```
@@
 # right now it looks like vmpfc FV is negatively related to curvature, but the opposite is true for dmPFC
-lapply(sulcGLM, summary)
+#lapply(sulcGLM, summary)
+
+# correlation retake
+# problem: PCC is positively correlated?
+t <- do.call(rbind, Summaries) %>%
+      mutate(Curvature = round(Curvature, digits = 1)) %>%
+      filter(Curvature > -0.5) %>%
+      group_by(SubjID, Hemisphere, region, Curvature) %>%
+      summarise(mFV = median(FiedlerVec)) %>%
+      group_by(SubjID, Hemisphere, region) %>%
+      dplyr::summarize(cor(Curvature, mFV, method = "spearman")) %>%
+      rename(Correlation = `cor(Curvature, mFV, method = "spearman")`)
+
+t %>% group_by(Hemisphere, region) %>% 
+  summarise(mCor = mean(Correlation, na.rm =T), 
+            seCor = sd(Correlation, na.rm = T) / sqrt(100)) %>%
+  ggplot(aes(region, mCor, color = Hemisphere)) +
+    geom_line() +
+  geom_point(size = 2) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  geom_errorbar(aes(region, ymin = mCor - seCor, ymax = mCor + seCor), width = 0.08, size = 1.2, linetype = "solid", show.legend = F) +
+  theme_classic()
+
+t %>% ggplot(aes(Correlation, color = Hemisphere)) +
+        geom_density(fill = "grey", alpha = 0.1) +
+        facet_wrap(vars(region), ncol = 1) +
+        theme_classic()
 

### 2019-09-05 Manuscript.Rmd
done with most intro and methods

@@
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
-We found that the DN community was likely to be located within principal sulci in ventral mPFC and PCC.
+*We found that the DN community was likely to be located within principal sulci in ventral mPFC and PCC*.
 Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019].
@@
 [-@Yeo2011].
+Even though this map misses sections of retrosplenial cortext that are typically involved in canonical DN [@Buckner2008], it provided a good coverage of regions in PCC and mPFC where valuation and DN overlap [@Acikalin2017].
 First, we selected vertices on the medial cortical surface that were contained by the DN and limbic networks in HCP's 32,000 vertex surface space (fs_LR_32k).
-Next, we overlaid those networks on a parcellated atlas of the human cortical surface [360 regions; @Glasser2016], and retained a set of parcels that covered approximately the same brain regions.
+Next, we overlaid those networks on a parcellated atlas of the human cortical surface [360 regions; @Glasser2016], and retained a set of parcels that covered approximately the same brain regions (at least 15% overlap, visually inspected).
 This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1).
@@
 corrCounts <- corrCounts %>%
-  mutate(prcntNS = NonSignificant / Total,
-         prcntPos = SignificantPos / (Total - NonSignificant),
-         prcntNeg = SignificantNeg / (Total - NonSignificant),
-         density = 1 - prcntNS)
-
-# density descriptives
-mdAll <- mean(corrCounts$density)
-sddAll <- sd(corrCounts$density)
+  mutate(prcntPos = Positive / Total,
+         prcntNeg = Negative / Total)
 
@@
 To establish each subject's network, we selected all the vertices contained within the mPFC/PCC search space (n = 4,801 per subject; mPFC = 2854, PCC = 1947) and computed the Pearson correlation of the time series for every pair of vertices.
+All correlation values were transformed using Fisher's r to z.
 This produced a weighted network for each subject, in which the nodes were surface vertices and the edges were the correlations among them.
-Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify significant connections.
-The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were set to 0 (all other edges retained their respective z-values).
-The proportion of remaining edges (i.e.
-network density) was high for all individuals (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`), and the retained edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, sd = `r sdPos`).
-Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution within the set of retained edges.
-Non-retained edges were reset to 0 to exclude them from the network analyses.
+Edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, sd = `r sdPos`).
+We chose not to threshold this network, as SP is well equipped to operate on complete (i.e.
+fully-connected) graphs [@chung1997].
+However, our results are unchanged even if we cut all non-significant correlations from the weight matrices.
+Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
+Ensuring that all edges were positive facilitated the construction of the graph Laplacian (see below), which requires all off-diagonal elements to have the same sign by design.
 We generated and analyzed network weight matrices at four levels: (1) for each subject's full concatenated dataset (up to 4800 TRs); (2) on each step of a sliding window analysis (see Partition Evaluation for more details); (3) for the concatenated time series for the two runs on each day (up to 2400 TRs); and (4) for each run separately (up to 1200 TRs).
@@
 Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the DN-specific PCC parcel identified in our meta-analysis.
-The high density of the graphs ensured that SP did not face the issues associated with its use in sparse networks [@Fortunato2016].
+The completeness of the graphs ensured that SP did not face the issues associated with its use in sparse networks [@Fortunato2016].
 
@@
 Next, we compared the subject-level SP partitionings across individuals, and calculated the mean pairwise ARI for the group.
-We then performed the same evaluation for PCC and mPFC separately, and examined whether there were mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects.
+We then performed the same evaluation for PCC and mPFC separately, and examined whether there were differences in overall agreement within these regions by performing a paired permutation analysis.
+We randomized the sign of the difference in pairwise ARI across individuals between mPFC and PCC 5000 times, and computed the mean of these differences across all comparisons on each iteration.
+The empirical difference in mean pairwise ARI between regions was then evaluated against this permuted distribution.
 
 To estimate the degree of variability of partitionings per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partitioning against the partitioning derived from the subject's whole data set.
-A 20-min window has previously been found adequate for identifying stable community features in brain networks [@Gordon2017].
+A 20-min window has previously been found to approximate an individual's asymptote for the stability of community features in brain networks [@Gordon2017].
 We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows.
 To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full time series).
-Based on this relationship, we identified a threshold Fiedler vector value for each subject, such that above-threshold vertices were persistently associated with either DN or non-DN more than 99% of the time.
+Based on this significant relationship, we identified a threshold Fiedler vector value for each subject, such that empirical above-threshold vertices were persistently associated with either DN or non-DN more than 99% of the time.
 
@@
 We evaluated the performance of the SP algorithm in comparison to a simpler partitioning approach based on seed-based functional connectivity.
-Independently for each day (2 per individual), we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in PCC.
+Independently for each day (2 per individual), we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in the PCC search space.
+We used the whole region to echo the approach often taken in seed-based connectivity analyses that do not rely on ROIs derived from independent analyses.
 We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP, with the sign of the Fiedler vector oriented so the DN community was marked by positive values in every subject.
@@
 
-The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Gratton2018b]).
+The two methods were expected to produce somewhat similar results, but the one displaying greater within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see Kong et al.
+[-@Kong2018] and Gratton et al.
+[-@Gratton2018b]).
 We therefore compared the within-subject spatial correlation coefficients produced by each method through a paired permutation analysis.
@@
 The empirical difference in means was then evaluated against this permuted distribution.
+
+\bigskip
+
+### *Associations with sulcal morphology*
+
+We examined whether the location of the DN and non-DN communities was guided by sulcal morphology.
 
@@
 A: Proportion of times each ROI was reported in the valuation and DN literatures.
-B: Regions identified in permutation-based chi-squared tests contrasting the two literatures (see text for details).
+B: Regions identified in permutation-based chi-squared tests contrasting the two literatures.
+Area 25 (in red) was disregarded because of the possible confound with projections from spheres located in ventral striatum (see text for details).
 Areas in blue represent the remainder of the search space."}
@@
 
-Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented in Supplemental Figure 1).
-The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods).
+Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented in the first two columns of Supplemental Figure 1).
+The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's normalized Laplacian matrix, see Methods).
 Since this is a data-driven approach, there is no a priori labeling for the two communities.
@@
 The ARI normally takes values ranging from 0 to 1, with 0 indicating chance agreement (but can take negative values if the similarity falls below chance).
+Supplemental Figure 2 contains examples of ARI values in real and simulated contexts.
 
@@
 
+Recent work has suggested that the location of the DN in individuals is bounded by the organization of sulcal morphology in vmPFC [@Lopez2019].
+
 ### *Alignment of mPFC community structure with a proposed DN sub-network organization*
@@
 
-```{r Extra examples (supplemental fig 1), out.width = "50%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings, showing both Fiedler vector values (left) and binarized communities (right).
+```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings, showing both Fiedler vector values (left) and binarized communities (right).
 A common organizational principle is visible, even though it shifts topographically across individuals."}
@@
 
-```{r ARI Comparison (supplemental fig 2), out.width = "50%", fig.align = "center", fig.cap = "Example of an across-day comparison using ARI for two subjects (100307 and 100408).
-This reflects how qualitatively similar, within-subject partitionings can have relatively small ARI values (here 0.24-0.25), and how partitionings across individuals are much closer to the chance level of zero."}
+```{r ARI Comparison (supplemental fig 2), out.width = "100%", fig.align = "center", fig.cap = "A: Example of an across-day comparison using ARI for two subjects (100307 and 100408).
+This reflects how qualitatively similar, within-subject partitionings can have relatively small ARI values (here 0.24-0.25), and how partitionings across individuals are much closer to the chance level of zero.
+B: Simulated comparison between two binary partitionings.
+The allegiance of each node is progressively switched, and the agreement between the new vector and the original one is computed on each change.
+The x-axis shows the number of nodes switched.
+Comparing the increasingly dissimilar maps by computing the proportion of equal cluster labelings (EQ) shows the expected linear decrease in similarity.
+The unadjusted form of the ARI (RI) displays an exponentially decaying similarity, and increases after reaching 50% as a result of node pairs once again being grouped in the same/different clusters (making the index label-agnostic).
+The ARI decays more dramatically as a function of increasing dissimilarity, reaching 0 at chance levels.
+Low ARI values can therefore still occur when there is notable agreement between partitionings."}
+
 include_graphics("./Images/ARI_comparison.png")

### 2019-09-05 Manuscript.Rmd
intro tweaks

@@
 In humans, areas in the DN are chiefly characterized by an increase in BOLD activity in the absence of externally oriented tasks [@Buckner2008], which is mirrored by a decrease in activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Laird2009; @Mckiernan2003].
+The latter effect has fueled the idea of the DN as a "task-negative" network, although certain self-referential tasks can prompt its activation [@Spreng2012].
 Since activity in the DN is related to the availability to engage in introspective thought, its distincitve topographical pattern is often captured by inter-region correlations in resting-state fMRI data [@Buckner2008; @Fox2005; @Greicius2003; @Yeo2011].
@@
 A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level.
-We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
+*We focused on the contrast between DN and valuation areas because of their notable overlap in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017].* We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
 Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographic extent of each community.

### 2019-09-05 Manuscript.Rmd
structural methods written up

--- 2019-09-05 Manuscript.Rmd
@@
 A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level.
+We focused on the contrast between DN and valuation areas because of their notable overlap in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017].
 We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
@@
 
-We examined whether the location of the DN and non-DN communities was guided by sulcal morphology.
+Next we asked whether the location of the DN and non-DN communities was guided by sulcal morphology.
+Based on previous reports of individual alignment of DN within sulci in ventral mPFC [@Lopez2019], we sub-divided our search space into three regions: vmPFC, which matched their ROI (areas 25, s32, a24, 10v, 10r, p32, and OFC); superior mPFC (sup-mPFC), encompassing the remaining dorsal areas in our mPFC space; and all of the PCC search space.
+We used each subject's curvature maps from the HCP (transformed to fs_LR 32k space), in which cortical depth is quantified by negative numbers for sulci and positive numbers for gyri.
+For each individual, we computed the correlation (Spearman) between curvature and the unthresholded Fiedler Vector values in each region and hemisphere separately (6 correlations per individual).
+Positive correlations meant that the DN was more likely to be contained in sulci, with non-DN housed in gyri.
+Finally, we collected all individual correlations for each combination of hemisphere and region, and performed a one-sample t-test on each set to determine whether correlations were significantly different than 0 in our group (6 tests total).
 
@@
 
-``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Correlation vs community detection: compute, fig.align = "center", echo = FALSE, message = FALSE, cache = TRUE}
 ## Between halves analysis for correlation and communities (mPFC only)
@@
 
-``` {r Correlation vs community detection: comparison, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
+``` {r Correlation vs community detection: comparison, fig.align = "center", echo = FALSE, message = FALSE, cache = TRUE}
 # Compare correlation with community approach on mPFC
@@
 ``` {r Correlation vs community detection (Fig.
-7), fig.align="center", fig.cap = "A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects.
+7), fig.align = "center", fig.cap = "A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects.
 The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector, with two single-day-based maps per individual.
@@
 
-``` {r sulcal comparison, echo=FALSE, message = FALSE, cache = TRUE}
+``` {r sulcal comparison, echo = FALSE, message = FALSE, cache = TRUE}
+# reload summaries, as this is done on unthresholded data
+# Load data, create a subject list, get the total n, and the number of vertices
+setwd('Summary/')
+temp <- list.files()
+subjList <- sapply(temp, substring, first = 1, last = 6)
+Summaries_curv <- lapply(temp, read.csv)
+
 # load curvature data and retain only the relevant subjects
-setwd('Curvature')
+setwd('../Curvature')
 files <- list.files(pattern = "curvature")
@@
 persemROI <- c("_25_", "_s32_", "_a24_", "_10v_", "_10r_", "_p32_", "_OFC_")
-primarySulci <- c("L_a24_ROI", "R_a24_ROI", "L_s32_ROI", "R_s32_ROI", "L_p32_ROI", "R_p32_ROI", "L_10r_ROI", "R_10r_ROI")
-
-indx <- getCoords(Labels = persemROI, Coords = Summaries[[1]])$Index
+
+indx <- getCoords(Labels = persemROI, Coords = Summaries_curv[[1]])$Index
 vmpfc <- rep(0, nVertices)
@@
 # update Summaries dfs, and reduce to vmPFC only
-curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries[[1]]$Vertex]})
+curvData <- lapply(files, function(file) {read.table(file, header = F)$V1[Summaries_curv[[1]]$Vertex]})
 for (i in seq(nSubj)) {
-  Summaries[[i]]$Curvature <- curvData[[i]]
-  Summaries[[i]]$SubjID <- subjList[[i]]
-  Summaries[[i]]$vmpfc <- vmpfc
-  Summaries[[i]] <- Summaries[[i]] %>% mutate(region = case_when(
+  Summaries_curv[[i]]$Curvature <- curvData[[i]]
+  Summaries_curv[[i]]$SubjID <- subjList[[i]]
+  Summaries_curv[[i]]$vmpfc <- vmpfc
+  Summaries_curv[[i]] <- Summaries_curv[[i]] %>% mutate(region = case_when(
     y < 0 ~ "PCC",
     vmpfc == 1 ~ "vmPFC",
-    TRUE ~ "dmPFC"
+    TRUE ~ "sup-mPFC"
   ),
@@
 
-# # mimic the binning and averaging L-P did on vmPFC
-# # this will plot a similar figure for a similar mask, plus a more dorsal mPFC one and PCC
-# do.call(rbind, Summaries) %>%
+# correlation 
+# binned correlations
+curvCors <- do.call(rbind, Summaries_curv) %>%
   # mutate(Curvature = round(Curvature, digits = 1)) %>%
-#   filter(Curvature > -0.5) %>%
-#   group_by(SubjID, region, FiedlerBinary, Curvature) %>%
-#   summarise(mFV = mean(FiedlerVec)) %>%
-#   group_by(region, FiedlerBinary, Curvature) %>%
-#   summarise(meanFV = mean(mFV),
-#             seFV = sd(mFV, na.rm = T) / sqrt(100)) %>%
-#   ggplot(aes(Curvature, meanFV, color = region, linetype = as.character(FiedlerBinary))) +
-#     geom_line(size = 1.2, show.legend = F) +
-#     labs(y = "Mean Fiedler Vector Value", color = "Region") +
-#     geom_errorbar(aes(Curvature, ymin = meanFV - seFV, ymax = meanFV + seFV), width = 0.08, size = 1.2, linetype = "solid", show.legend = F) +
-#     scale_x_continuous(breaks = c(-0.4, 0, 0.4, 0.8)) +
-#     geom_point(size = 2) +
-#     scale_color_manual(values = c("firebrick", "dodgerblue4", "gold2")) +
-#     geom_vline(xintercept = 0, linetype = "dashed") +
-#     geom_hline(yintercept = 0, linetype = "dashed") +
-#     theme(#legend.position = c(0.9, 0.32),
+  # group_by(SubjID, Hemisphere, region, Curvature) %>%
+  # summarise(mFV = median(FiedlerVec, na.rm = T)) %>%
+  group_by(SubjID, Hemisphere, region) %>%
+  dplyr::summarize(cor(Curvature, FiedlerVec, method = "spearman")) %>%
+  rename(Correlation = `cor(Curvature, FiedlerVec, method = "spearman")`)
+
+# stats: one sample t's per hemisphere/region
+curvCors %>% group_by(region, Hemisphere) %>% 
+  summarise(TStat = t.test(Correlation)$statistic,
+            p = t.test(Correlation)$p.val,
+            Sig = p < 0.05,
+            ES = DescTools::CohenD(Correlation))
+
+# stats: paired t on PCC between hemispheres
+t <- curvCors %>% 
+  filter(region == "PCC") %>% 
+  spread(Hemisphere, Correlation)
+
+curvPCC_t <- t.test(t$L, t$R, paired = T)
+curvPCC_ES <- DescTools::CohenD(t$L, t$R)
+
+```
+
+```{r Association with sulci (Fig.
+8), fig.align = "center", fig.cap = "A: Correspondence between SP communities and sulcal morphology in two example individuals.
+Zoomed-in boxes show areas in PCC and ventral mPFC where the DN community appears to be guided by sulcal organization.
+This relationship is less defined in superior mPFC.
+The superior rostral sulcus houses the DN community, in agreement with findings by Lopez-Persem et al.
+(2019).
+B: We quantified this relationship by correlating cortical curvature with the unthresholded Fiedler values.
+We divided the search space into three areas (left): ventral mPFC (yellow), superior mPFC (sup-mPFC, red), and PCC (blue).
+Correlations on each combination of region and hemisphere per individual showed that DN (signaled by positive FV values) tends to be represented in vmPFC sulci, but is likely located in gyri within sup-dmPFC.
+PCC has an inversed relationship across hemispheres, with DN landing more often in left hemisphere sulci."}
+# # box plot
+# curvCors %>%  ggplot(aes(Hemisphere, Correlation, fill = region)) +
+#   geom_hline(yintercept = 0, linetype = "dashed", size = 1.2) +
+#   geom_boxplot(show.legend = F, size = 1.5) +
+#   geom_jitter(width=0.1, alpha = 0.3, show.legend = F) +
+#   scale_fill_manual(values = c("dodgerblue4", "firebrick", "gold2")) +
+#   labs(y = "Correlation") +
+#   guides(color = F) +
+#   facet_wrap(vars(region), ncol = 3) +
+#   theme(legend.position = c(0.85, 0.7),
 #         legend.key=element_blank(),
@@
 
-# MIXED EFFECTS LOGISTIC ESTIMATING SULCUS FROM FV AND REGION, WORKS BUT CHANGE REFERENCE
-sulcData <- do.call(rbind, Summaries) %>%
-  mutate(Curvature = round(Curvature, digits = 1),
-         region = factor(region, levels = list("vmPFC", "dmPFC", "PCC"))) #%>%
-  #filter(abs(FiedlerVec) > 0.01)
-
-sulcGLM <- list()
-sulcGLM$vmpfc <- glmer(FiedlerBinary ~ Curvature * region + (1 | SubjID), data = sulcData, family = "binomial")
-sulcData$region <- factor(sulcData$region, levels = list("dmPFC", "vmPFC", "PCC"))
-sulcGLM$dmpfc <- glmer(FiedlerBinary ~ Curvature * region + (1 | SubjID), data = sulcData, family = "binomial")
-
-# right now it looks like vmpfc FV is negatively related to curvature, but the opposite is true for dmPFC
-#lapply(sulcGLM, summary)
-
-# correlation retake
-# problem: PCC is positively correlated?
-t <- do.call(rbind, Summaries) %>%
-      mutate(Curvature = round(Curvature, digits = 1)) %>%
-      filter(Curvature > -0.5) %>%
-      group_by(SubjID, Hemisphere, region, Curvature) %>%
-      summarise(mFV = median(FiedlerVec)) %>%
-      group_by(SubjID, Hemisphere, region) %>%
-      dplyr::summarize(cor(Curvature, mFV, method = "spearman")) %>%
-      rename(Correlation = `cor(Curvature, mFV, method = "spearman")`)
-
-t %>% group_by(Hemisphere, region) %>% 
-  summarise(mCor = mean(Correlation, na.rm =T), 
-            seCor = sd(Correlation, na.rm = T) / sqrt(100)) %>%
-  ggplot(aes(region, mCor, color = Hemisphere)) +
-    geom_line() +
-  geom_point(size = 2) +
-  geom_hline(yintercept = 0, linetype = "dashed") +
-  geom_errorbar(aes(region, ymin = mCor - seCor, ymax = mCor + seCor), width = 0.08, size = 1.2, linetype = "solid", show.legend = F) +
-  theme_classic()
-
-t %>% ggplot(aes(Correlation, color = Hemisphere)) +
-        geom_density(fill = "grey", alpha = 0.1) +
-        facet_wrap(vars(region), ncol = 1) +
-        theme_classic()
-
+include_graphics("./Images/sulciVSfv.png")
 ```
@@
 In both individuals, seeds in posterior IPL and TPJ most clearly identified networks A and B, respectively.
-The whole-brain seed-based functional connectivity maps for the two individuals are juxtaposed with the corresponding community detection results in Figure 8.
+The whole-brain seed-based functional connectivity maps for the two individuals are juxtaposed with the corresponding community detection results in Figure 9.
 It is worth noting that a few distinguishing features are missing due to below-threshold correlation values (e.g.
@@
 
-```{r BandB comparison (Figure 8), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (estimated based on descriptions from Braga et al.
+```{r BandB comparison (Figure 9), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (estimated based on descriptions from Braga et al.
 (2019)) and SP communities for two individuals.

### 2019-09-05 Manuscript.Rmd
more morphology and clarifying sliding window analysis

@@
 We used each subject's curvature maps from the HCP (transformed to fs_LR 32k space), in which cortical depth is quantified by negative numbers for sulci and positive numbers for gyri.
-For each individual, we computed the correlation (Spearman) between curvature and the unthresholded Fiedler Vector values in each region and hemisphere separately (6 correlations per individual).
+For each individual, we computed the correlation (Spearman) between curvature and the unthresholded Fiedler vector values in each region and hemisphere separately (6 correlations per individual).
 Positive correlations meant that the DN was more likely to be contained in sulci, with non-DN housed in gyri.
@@
 
-We next sought to identify a set of temporally stable core nodes in each community.
-In order to estimate the stability of partitions over time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min).
+We next sought to estimate the variability of individual partitionings over time.
+We did so by performing a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min).
 We compared the partitioning derived from each window with the partitioning computed using the entire time series (Figure 4).
+The significant level of sequential overlap was meant to promote highly similar partitionings among nearby windows, so that we could identify nodes that were highly variable where discrepancies occurred.
+This also allowed us to determine whether these variable nodes followed a specific spatial structure.
 
@@
 # # Fiedler Vector x proportion of times a vertex was affiliated with DN
-# SC_FVvPDN_plot <- ggplot(data = allSummaries) +
+# (SC_FVvPDN_plot <- ggplot(data = allSummaries) +
 #   geom_smooth(aes(FiedlerVec, slidePropDN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
@@
 #   scale_y_continuous(limits = c(0,1)) +
-#   theme_classic()
-# 
-# SC_FVvPDN_plot
+#   theme_classic())
+# 
 #
@@
 Specifically, we estimated the proportion of DN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
-The model identified a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), signifying that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
+We stress that the stability expected from our highly overlapping windows added relevance to the observed variability.
+The model identified a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2, 2], digits = 2)`, *p* < 0.001), signifying that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
 
@@
 We therefore thresholded each subject's Fiedler vector to produce these refined maps.
-For each individual, we estimated the threshold by selecting the smallest absolute Fiedler vector value that yielded an average stability across suprathreshold nodes of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
+For each individual, we estimated the threshold by selecting the empirical smallest absolute Fiedler vector value that yielded an average stability across suprathreshold nodes of 99%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately.
 Individuals without such stable nodes (n = `r nUnstable`) were not thresholded, and were included in the subsequent analyses in unthresholded form.
@@
 
-Recent work has suggested that the location of the DN in individuals is bounded by the organization of sulcal morphology in vmPFC [@Lopez2019].
+Next, we asked if the idiosyncratic organization of the DN was reflected by patterns of sulcal morphology.
+A variety of studies have provided evidence that suclal and gyral organization can inform the location of functional effects (*PAPERS*).
+Among these, recent work has suggested that the location of the DN in individuals lies mostly within sulci in vmPFC [@Lopez2019].
+We sought to replicate this relationship using the SP communities, as well as interrogating whether it persisted in PCC and more dorsal mPFC regions.
+
+Here you'll want to mention a number of things:
+
+- in vmpfc ROS-S contains DN, just like L-P
+- hemispheric differences in PCC
+- the papers given by rev 3
 

### 2019-09-06 Manuscript.Rmd
apa citation tweaks

@@
 ### *Correlation vs community detection in mPFC*
-
+
 ``` {r Correlation vs community detection: compute, fig.align = "center", echo = FALSE, message = FALSE, cache = TRUE}
@@
 curvCors %>% group_by(region, Hemisphere) %>% 
-  summarise(TStat = t.test(Correlation)$statistic,
+  summarise(medianCor = median(Correlation),
+            seCor = sd(Correlation) / sqrt(nSubj),
+            TStat = t.test(Correlation)$statistic,
             p = t.test(Correlation)$p.val,

### 2019-09-06 Manuscript.Rmd
supplemental fig wording

@@
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
-*We found that the DN community was likely to be located within principal sulci in ventral mPFC and PCC*.
+We found that the DN community was likely to be located within principal sulci in ventral mPFC and left PCC, but in gyri within superior mPFC and right PCC.
 Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019].
@@
 # stats between regions
-Halves_mPFCvPCC__Modularity_permTest <- permute(Halves_RIRatios_PFC_Modularity, Halves_RIRatios_PCC_Modularity, paired = T, statType = median)
+Halves_mPFCvPCC_Modularity_permTest <- permute(Halves_RIRatios_PFC_Modularity, Halves_RIRatios_PCC_Modularity, paired = T, statType = median)
 Halves_mPFCvPCC_Modularity_ES <- cohenD(Halves_RIRatios_PFC_Modularity, Halves_RIRatios_PCC_Modularity)
@@
 Moreover, the ratios for mPFC were significantly greater than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
-These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns.
+These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found on Supplemental Figure 4).
+This pattern of results is unchanged when computed using modularity to detect these communities, even though the ratios were closer to 1 (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
 We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner.
@@
 
-```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings, showing both Fiedler vector values (left) and binarized communities (right).
-A common organizational principle is visible, even though it shifts topographically across individuals."}
+```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings.
+The first two columns show both Fiedler vector values  and binarized communities, respectively.
+A common organizational principle is visible, even though it shifts topographically across individuals.
+The organization is also evident when using Modularity (third column), even though some isolated vertices were sometimes placed in a small third community (see subject 100408).
+The fourth column shows Fiedler vector maps after adding adding retrosplenial cortex (a common component of canonincal DN affected by task-deactivation).
+The addition of this area to the search space does not alter the original results, and the region is adequately covered by the DN community."}
 include_graphics("./Images/extra_examples.png")
@@
 
-```{r extra B&B checks with silhouette (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga & Buckner (2017).
+```{r day- and run-wise brain comparisons (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Visual examples of idiosyncratic organization across days and runs.
+Left: Thresholded partitionings captured with SP are highly similar across days within individuals, but are topographically distinct across individuals.
+The organization estimated for each dat is also mostly indistinct from that captured using the full time series (Supplemental Figure 1).
+Right: Thresholded partitionings estimated using the first scanning session from day 1, and the last scanning session from day 2.
+As expected, the considerable reduction in the amount of data used decreased the reliability of the community localization across single scanning sessions, which were in some cases irrecoverable (e.g.
+subjects 100408 and 687163).
+Even so, the general location of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data.
+This shows that even with notably noisier estimates and lower within-individual ARI values produced by working with less data, it is possible to gain information about the general location of DN and non-DN in individuals."}
+include_graphics("./Images/days_runs_examples.png")
+```
+
+```{r extra B&B checks with silhouette (supplemental fig 5), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga & Buckner (2017).
 *ADD KMEANS DEETS HERE*.

### 2019-09-06 Manuscript.Rmd
done with structural associations

@@
 output:
-  word_document: default
+  word_document: #default
+    reference_docx: Style_reference_draft.docx
   pdf_document:
@@
 In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
-Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the DN-specific PCC parcel identified in our meta-analysis.
+Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the DN-specific PCC parcel identified in our meta-analysis (i.e.
+over 50% coverage).
 The completeness of the graphs ensured that SP did not face the issues associated with its use in sparse networks [@Fortunato2016].
@@
 For each individual, we computed the correlation (Spearman) between curvature and the unthresholded Fiedler vector values in each region and hemisphere separately (6 correlations per individual).
-Positive correlations meant that the DN was more likely to be contained in sulci, with non-DN housed in gyri.
+Since the DN is indicated by positive FV values, positive correlations meant that the DN was more likely to be contained in sulci, with non-DN housed in gyri.
 Finally, we collected all individual correlations for each combination of hemisphere and region, and performed a one-sample t-test on each set to determine whether correlations were significantly different than 0 in our group (6 tests total).
@@
 
-```{r Thresholded maps (Fig 5), out.width = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector map for subject 100307 (top), and its binarized form (bottom).
+```{r Thresholded maps (Fig 5), out.height = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector map for subject 100307 (top), and its binarized form (bottom).
 Subthreshold values effectively formed a third community of high-variability vertices.
@@
 # effect size pre vs post
-tsnrCohen_mPFC <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$pre_thresh[1, -1]))
-tsnrCohen_PCC <- CohenD(as.numeric(snr_means$post_thresh[2, -1]), as.numeric(snr_means$pre_thresh[2, -1]))
-tsnrCohen_Post <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]))
+tsnrCohen_mPFC <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$pre_thresh[1, -1]), na.rm = T)
+tsnrCohen_PCC <- CohenD(as.numeric(snr_means$post_thresh[2, -1]), as.numeric(snr_means$pre_thresh[2, -1]), na.rm = T)
+tsnrCohen_Post <- CohenD(as.numeric(snr_means$post_thresh[1, -1]), as.numeric(snr_means$post_thresh[2, -1]), na.rm = T)
 ```
@@
 These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found on Supplemental Figure 4).
-This pattern of results is unchanged when computed using modularity to detect these communities, even though the ratios were closer to 1 (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
+This pattern of results was unchanged when computed using modularity to detect these communities, even though the ratios were closer to 1 (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
 We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner.
@@
 We extended the analysis of per-day data by examining whether the organization of the DN could be extracted using per-run data only.
-The duration of each run (approximately 14 min) falls below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
-Nonetheless, high ARI ratios would indicate that the SP algorithm can reliably estimate individual-specific patterns of DN organization from a single run of data.
+The duration of each run (approximately 14 min) falls well below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
+Nonetheless, high ARI ratios could indicate that the SP algorithm can still estimate individual-specific patterns of DN organization from a single run of data.
 
@@
 
-Run-specific SP results still captured unique organizational patterns to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+Run-specific SP results captured unique organizational patterns to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+Supplemental Figure 4 shows that even though the community estimates were indeed less reliable within-individuals than those captured using daily data (and sometimes even failed to produce meaningful partitionings), the layout of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data.
 We again computed each subject's ARI ratio in order to quantify the specificity of the partitions, this time using the mean of 6 across-run (within-participant) ARI values in the numerator of the ratio (Figure 6, right).
@@
 As before, a signed rank test showed that both regions had ARI ratios significantly greater than 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25, na.rm = T), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75, na.rm = T), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC, na.rm = T), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25, na.rm = T), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75, na.rm = T), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), and ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
-This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
+This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data, albeit coarsely.
 
 ### *Correlation vs community detection in mPFC*
-
+
 ``` {r Correlation vs community detection: compute, fig.align = "center", echo = FALSE, message = FALSE, cache = TRUE}
@@
 We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC.
+The use of the whole PCC region (instead of just 7m) was meant to echo the way seed-based connectivity is often employed in the absence of prior analytic ROI selection.
 We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations across vertices.
@@
 # stats: one sample t's per hemisphere/region
-curvCors %>% group_by(region, Hemisphere) %>% 
-  summarise(medianCor = median(Correlation),
+curvStats <- curvCors %>% 
+                group_by(region, Hemisphere) %>% 
+                summarise(meanCor = mean(Correlation),
                           seCor = sd(Correlation) / sqrt(nSubj),
-            TStat = t.test(Correlation)$statistic,
-            p = t.test(Correlation)$p.val,
+                          TStat = round(t.test(Correlation)$statistic, digits = 2),
+                          p = round(t.test(Correlation)$p.val, digits = 4),
                           Sig = p < 0.05,
@@
 
+Next, we asked if the idiosyncratic organization of the DN was reflected by patterns of sulcal morphology.
+A variety of studies have provided evidence that suclal and gyral organization inform the location of functional effects [@Amiez2013; @Amiez2014; @Zlatkina2016].
+Among these, recent work has suggested that the location of the DN in individuals lies mostly within sulci in vmPFC [@Lopez2019].
+We sought to reproduce this relationship using the SP communities, as well as interrogating whether it persisted in PCC and more dorsal mPFC regions.
+
+Figure 8A shows a qualitative comparison between the thresholded DN and non-DN communities and curvature maps for two individuals.
+In agreement with findings from Lopez-Persem et al.
+[@Lopez2019], we found that the DN community was likely to be found within the superior rostral sulcus in vmPFC.
+The non-DN community covered both gyri and sulci in this area.
+A similar trend was present in PCC (especially in the left hemisphere), where the DN community traced sulcal layouts and non-DN was more likely to appear in gyri.
+This relationship was not as clear in sup-mPFC, where both DN and non-DN could be mapped onto both gyri and sulci.
+
+We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the one used by Lopez-Persem et al.
+[-@Lopez2019], a superior mPFC zone (sup-mPFC) that contained the remaining dorsal mPFC regions, and PCC (Figure 8B, left).
+For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere.
+Negative correlations in this context imply that the DN was likely found in sulci and non-DN in gyri.
+Results can be found on Figure 8B.
+We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
+Correlations between FV and curvature were positive and significantly different than zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC.
+Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
+The difference across hemispheres was significant (paired t-test: t = `r curvPCC_t$statistic`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`).
+These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al.
+[-@Lopez2019], and suggest that the association between function and structure is heterogenous within canonical DN.
+
 ```{r Association with sulci (Fig.
@@
 Zoomed-in boxes show areas in PCC and ventral mPFC where the DN community appears to be guided by sulcal organization.
-This relationship is less defined in superior mPFC.
+This relationship is less defined in superior mPcFC.
 The superior rostral sulcus houses the DN community, in agreement with findings by Lopez-Persem et al.
 (2019).
-B: We quantified this relationship by correlating cortical curvature with the unthresholded Fiedler values.
+B: Correlations between cortical curvature and the unthresholded Fiedler values.
 We divided the search space into three areas (left): ventral mPFC (yellow), superior mPFC (sup-mPFC, red), and PCC (blue).
-Correlations on each combination of region and hemisphere per individual showed that DN (signaled by positive FV values) tends to be represented in vmPFC sulci, but is likely located in gyri within sup-dmPFC.
-PCC has an inversed relationship across hemispheres, with DN landing more often in left hemisphere sulci."}
+Boxplots on the right show the distribution of correlation values across individuals for each combination of region and hemisphere, indicating that DN (signaled by positive FV values) tended to be represented in vmPFC sulci, but was likely located in gyri within sup-dmPFC.
+PCC had an inversed relationship across hemispheres, with DN landing more often in left hemisphere sulci."}
 # # box plot
@@
 
-Next, we asked if the idiosyncratic organization of the DN was reflected by patterns of sulcal morphology.
-A variety of studies have provided evidence that suclal and gyral organization can inform the location of functional effects (*PAPERS*).
-Among these, recent work has suggested that the location of the DN in individuals lies mostly within sulci in vmPFC [@Lopez2019].
-We sought to replicate this relationship using the SP communities, as well as interrogating whether it persisted in PCC and more dorsal mPFC regions.
-
-Here you'll want to mention a number of things:
-
-- in vmpfc ROS-S contains DN, just like L-P
-- hemispheric differences in PCC
-- the papers given by rev 3
-
 ### *Alignment of mPFC community structure with a proposed DN sub-network organization*
@@
 
+\bigskip
+
 ```{r day- and run-wise brain comparisons (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Visual examples of idiosyncratic organization across days and runs.
@@
 
-```{r extra B&B checks with silhouette (supplemental fig 5), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga & Buckner (2017).
+\bigskip
+
+```{r extra B&B checks with silhouette (supplemental fig 5), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga et al.
+(2019).
 *ADD KMEANS DEETS HERE*.

### 2019-09-06 Manuscript.Rmd
results ready, onto discussion revisions now

@@
 ```{r Meta-analysis ROIs (Fig.
-1), out.width = "50%", fig.align = "center", fig.cap= "Meta-analysis results.
+1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1.
+Meta-analysis results.
 A: Proportion of times each ROI was reported in the valuation and DN literatures.
@@
 ```{r Representative partitioning (Fig.
-2), out.width = "50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307).
+2), out.width = "50%", fig.align = "center", fig.cap = "Figure 2.
+Brain partition for an example subject (100307).
 Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities.
@@
 ``` {r Partitioning comparison: all (Fig.
-3), fig.align="center", out.width = "50%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
+3), fig.align="center", out.width = "50%", fig.cap = "Figure 3.
+Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately.
 Functional topographic patterns were better aligned across individuals in PCC than mPFC.", echo=FALSE, message = FALSE}
@@
 ``` {r Variability per subject: Fiedler vector vs prop.
-DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs).
+DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 4.
+A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs).
 B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (lower).
@@
 
-```{r Thresholded maps (Fig 5), out.height = "50%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector map for subject 100307 (top), and its binarized form (bottom).
+```{r Thresholded maps (Fig 5), out.height = "50%", fig.align = "center", fig.cap= "Figure 5.
+A: Thresholded Fiedler vector map for subject 100307 (top), and its binarized form (bottom).
 Subthreshold values effectively formed a third community of high-variability vertices.
@@
 ``` {r Partition comparison: halves and runs (Fig.
-6), fig.align="center", out.width = "100%", fig.cap = "Left: Similarity matrix for 10 example participants (2 scanning days each), showing pattern agreement across days and subjects for PCC and mPFC separately.
+6), fig.align="center", out.width = "100%", fig.cap = "Figure 6.
+Left: Similarity matrix for 10 example participants (2 scanning days each), showing pattern agreement across days and subjects for PCC and mPFC separately.
 Color scale represents the ARI, which quantifies topographic similarity irrespective of how the communities are labeled.
@@
 ``` {r Correlation vs community detection (Fig.
-7), fig.align = "center", fig.cap = "A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects.
+7), fig.align = "center", fig.cap = "Figure 7.
+A: Correlation matrix comparing the across-day spatial stability of mPFC maps derived from seed-based functional connectivity (using a PCC seed) and the Fiedler vector for 10 example subjects.
 The top-left quadrant represents seed-based FC maps, and the bottom-right the Fiedler vector, with two single-day-based maps per individual.
@@
 
-We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the one used by Lopez-Persem et al.
-[-@Lopez2019], a superior mPFC zone (sup-mPFC) that contained the remaining dorsal mPFC regions, and PCC (Figure 8B, left).
-For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere.
-Negative correlations in this context imply that the DN was likely found in sulci and non-DN in gyri.
-Results can be found on Figure 8B.
-We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
-Correlations between FV and curvature were positive and significantly different than zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC.
-Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
-The difference across hemispheres was significant (paired t-test: t = `r curvPCC_t$statistic`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`).
-These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al.
-[-@Lopez2019], and suggest that the association between function and structure is heterogenous within canonical DN.
-
 ```{r Association with sulci (Fig.
-8), fig.align = "center", fig.cap = "A: Correspondence between SP communities and sulcal morphology in two example individuals.
+8), fig.align = "center", fig.cap = "Figure 8.
+A: Correspondence between SP communities and sulcal morphology in two example individuals.
 Zoomed-in boxes show areas in PCC and ventral mPFC where the DN community appears to be guided by sulcal organization.
@@
 
+We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the one used by Lopez-Persem et al.
+[-@Lopez2019], a superior mPFC zone (sup-mPFC) that contained the remaining dorsal mPFC regions, and PCC (Figure 8B, left).
+For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere.
+Negative correlations in this context imply that the DN was likely found in sulci and non-DN in gyri.
+Results can be found on Figure 8B.
+We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
+Correlations between FV and curvature were positive and significantly different than zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC.
+Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
+The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`).
+These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al.
+[-@Lopez2019], and suggest that the association between function and structure is heterogenous within canonical DN.
+
 ### *Alignment of mPFC community structure with a proposed DN sub-network organization*
@@
 However, the non-DN community filled areas not covered by either DN-A or DN-B.
-This result supports the idea that the two approaches serve complementary purposes.
+Since this three-network configuration is at odds with the two-network solution suggested in our previous analyses (i.e.
+comparison with modularity), we ran additional evaluations to confirm its existence.
+First, we reproduced the whole-brain k-means clustering analysis (n of clusters = 12, 100 iterations) performed by Braga et al.
+[-@Braga2019] in our two subjects using their full time series (Supplemental Figure 5A).
+In addition to identifying DN networks A and B through this approach (in line with their findings), we found a third cluster that aligned well with the non-DN community.
+To understand why we could not find this organization before, we performed a silhouette analysis to determine the ideal number of clusters in our search space (Supplemental Figure 5B).
+For every individual, we ran k-means clusterings with a specified number of clusters ranging from 2 to 5, and computed a silhouette score for each solution (higher silhouette scores indicate a better fit).
+Scores decreased as the number of clusters increased for all individuals, suggesting that a bisection was indeed the best solution.
+Paired permutations comparing mean scores across individuals indicated that the difference between two (mean = 0.042, SE = 0.001) and three (mean = 0.032, SE = 0.0009) cluster solutions was significant (*p* < 0.0001, Cohen's D = 0.96).
+Visualization of a two-cluster k-means revealed a close match with partitionings estimated through modularity, and are comparable to those produced by SP prior to thresholding (Supplemental Figure 5A, bottom rows).
+These analyses suggest that SP isolated DN-A and the non-DN community as the dominant opposite signals within our search space, but that DN-B is observable once we take advantage of the continuous information contained in the Fiedler vector.
+
+These results supports the idea that the two approaches serve complementary purposes.
 Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
-
-```{r BandB comparison (Figure 9), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between DN sub-networks A and B (estimated based on descriptions from Braga et al.
+Furthermore, they show that our approach can identify the three networks in a way that is less computationally demanding than full-brain clustering, outperforming other clustering methods that lack the continuous information provided by SP.
+
+```{r BandB comparison (Figure 9), out.width = "100%", fig.align = "center", fig.cap= "Figure 9.
+Qualitative comparison between DN sub-networks A and B (estimated based on descriptions from Braga et al.
 (2019)) and SP communities for two individuals.
@@
 Panel B: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A.
-The non-DN community covers sections of cortex not associated with either DN sub-network."}
+The non-DN community covers sections of cortex not associated with either SP sub-network."}
 
@@
 
-```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Additional examples of individualized partitionings.
+```{r Extra examples (supplemental fig 1), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 1.
+Additional examples of individualized partitionings.
 The first two columns show both Fiedler vector values  and binarized communities, respectively.
@@
 
-```{r ARI Comparison (supplemental fig 2), out.width = "100%", fig.align = "center", fig.cap = "A: Example of an across-day comparison using ARI for two subjects (100307 and 100408).
+```{r ARI Comparison (supplemental fig 2), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 2.
+A: Example of an across-day comparison using ARI for two subjects (100307 and 100408).
 This reflects how qualitatively similar, within-subject partitionings can have relatively small ARI values (here 0.24-0.25), and how partitionings across individuals are much closer to the chance level of zero.
@@
 
-```{r tSNR (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Signal quality prior to FV thresholding.
+```{r tSNR (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 3.
+Signal quality prior to FV thresholding.
 Left: Surface map displaying the vertex-wise mean tSNR across individuals.
@@
 
-```{r day- and run-wise brain comparisons (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Visual examples of idiosyncratic organization across days and runs.
+```{r day- and run-wise brain comparisons (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 4.
+Visual examples of idiosyncratic organization across days and runs.
 Left: Thresholded partitionings captured with SP are highly similar across days within individuals, but are topographically distinct across individuals.
@@
 
-```{r extra B&B checks with silhouette (supplemental fig 5), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga et al.
+```{r extra B&B checks with silhouette (supplemental fig 5), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 5.
+Additional checks to confirm the match between our findings with Braga et al.
 (2019).
-*ADD KMEANS DEETS HERE*.
-B: K-means based silhouette scores were computed per individual to determine the appropriate number of clusters within the search space.
-Scores decreased as the number of clusters increased, suggesting that a bisection was the best solution.
-Paired permutations comparing mean scores across individuals indicated that the difference between two (mean = 0.042, SE = 0.001) and three (mean = 0.032, SE = 0.0009) cluster solutions was significant (*p* < 0.0001, Cohen's D = 0.96)"}
+A: DN sub-networks A and B identified through whole-brain k-means clustering are congruent with the existence of a third sub-network, which matches the non-DN SP community (top rows).
+Limiting k-means to two clusters within the search space aligns with results from modularity (bottom two rows).
+B: K-means based silhouette scores were computed per individual to determine the appropriate number of clusters within the search space (the higher the score, the better).
+This showed that two networks were the ideal solution."}
 # # produce the silhouette plot

### 2019-09-06 Manuscript.Rmd
final revisions before sending to Joe/Sean

@@
 output:
-  word_document: #default
-    reference_docx: Style_reference_draft.docx
   pdf_document:
@@
     keep_tex: no
+  word_document: #default
+    reference_docx: Style_reference_draft.docx
 header-includes:
@@
 
-## Significance Statement
-
-  Multiple psychological functions engage topographically overlapping regions of human medial prefrontal cortex (mPFC), and the reason for the apparent overlap is not yet well understood.
-Here we present evidence that our understanding of the functional organization of mPFC can be advanced by accounting for individual-level topographic variability.
-We report results from a data-driven, network-based approach to subdividing mPFC and posterior cingulate cortex jointly into two distinct communities on the basis of non-task functional neuroimaging data.
-One of the identified communities corresponded to the brain's canonical default network.
-The community structure of mPFC was stable across test/re-test but exhibited high variability across individuals.
-The approach we introduce will help characterize the functional role of mPFC across diverse psychological domains.
-
-\newpage
-
 ## Introduction
@@
 A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level.
-We focused on the contrast between DN and valuation areas because of their notable overlap in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017].
 We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
@@
 This non-DN section extended posteriorly into pregenual cinglate cortex (area a24).
+We note that the addition of restrosplenial cortex (an area commonly regarded as part of canonical DN) to the search space did not change these results, and that the area was adequately covered by the DN community (Supplemental Figure 1).
 
@@
 Moreover, the ratios for mPFC were significantly greater than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
+This pattern was mostly unchanged when computed using modularity to detect these communities, showing that the results persist even without a forced binarization (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
 These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found on Supplemental Figure 4).
-This pattern of results was unchanged when computed using modularity to detect these communities, even though the ratios were closer to 1 (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
 We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner.
@@
 Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
-The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`).
+The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2)`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`).
 These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al.
@@
 In addition to identifying DN networks A and B through this approach (in line with their findings), we found a third cluster that aligned well with the non-DN community.
-To understand why we could not find this organization before, we performed a silhouette analysis to determine the ideal number of clusters in our search space (Supplemental Figure 5B).
+To understand why we could not find the three discrete clusters before, we performed a silhouette analysis to determine the ideal number of clusters in our search space (Supplemental Figure 5B).
 For every individual, we ran k-means clusterings with a specified number of clusters ranging from 2 to 5, and computed a silhouette score for each solution (higher silhouette scores indicate a better fit).
@@
 Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
-Furthermore, they show that our approach can identify the three networks in a way that is less computationally demanding than full-brain clustering, outperforming other clustering methods that lack the continuous information provided by SP.
+Furthermore, they show that our approach can identify the three networks in PCC and mPFC in a way that is less computationally demanding than full-brain clustering, outperforming other clustering methods that lack the type of continuous information provided by SP.
 
@@
 preventing the allocation of most vertices to a single community), providing continuous values that relate to the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
-Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], suggested the binary partitioning was appropriate.
+Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], plus a silhouette analysis, suggested the binary partitioning was appropriate.
 
@@
 Individual-specificity could theoretically arise from a variety of sources.
-For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; @Lopez2019].
-Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
-An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
+For example, Individual variability could be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
+Alternatively, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014].
+Our findings support this idea, echoing previous findings that DN is contained within sulci (in particular the superior rostral sulcus) in vmPFC [@Lopez2019].
+This relationship was heterogeneous throughout the rest of the search space, as more dorsal mPFC regions were likely located in gyri, whereas PCC had hemispheric differences in this association.
+An important goal for future work will be to assess whether the network layout in these regions can also be predicted on the basis of other aspects of brain structure, such as myeloarchitecture [@Glasser2016] or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
 
@@
 We circumvented this issue by independently identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially associated with the DN relative to subjective valuation in our meta-analysis.
+Our focus on this contrast was approapriate because of the notable topographical overlap between these processes in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017].
 We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals.
@@
 Previous work has also shown that functional correlations among pre-defined cortical parcels are highly stable within an individual [@Gratton2018b; @Kong2018].
-Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan).
+Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan, although estimates become considerably more unreliable).
 The motivation to sub-divide DN also stems from recent work by Kernbach et al.
@@
 The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network.
-Subthreshold vertices from the DN community overlapped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks.
+Subthreshold vertices from the SP communities in turn overlapped with DN-B vertices.
 Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people.
 Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research.
-These two sets of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
+SP is related to methods that have gained traction recently for distinguishing functional cortical gradients [@Margulies2016; @Huntenburg2018].
+Dedicated work could determine whether DN-A and DN-B form part of a gradual information processing sequence, or if their functions can be discretized.
+Regardless, this set of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
 
@@
 It will be beneficial for future task-based fMRI experiments to be able to characterize where task-evoked activity is situated relative to an individual's overall mPFC organization.
-Our work was originally motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation versus episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], and potential topographic distinctions among multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010].
+Our work was originally motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation versus episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], which have been grouped under the DN umbrella based on group averages [@Spreng2012], and potential topographic distinctions among multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010].
 An individualized frame of reference will enhance the ability of future studies to gauge similarities and differences among brain activity patterns associated with diverse psychological domains.

### 2019-09-06 Manuscript.Rmd
there's always one last tweak

@@
 
-Run-specific SP results captured unique organizational patterns to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
+Run-specific SP results captured unique organizational patterns to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]], na.rm = T), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]], na.rm = T), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
 Supplemental Figure 4 shows that even though the community estimates were indeed less reliable within-individuals than those captured using daily data (and sometimes even failed to produce meaningful partitionings), the layout of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data.
@@
 We circumvented this issue by independently identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially associated with the DN relative to subjective valuation in our meta-analysis.
-Our focus on this contrast was approapriate because of the notable topographical overlap between these processes in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017].
+Our focus on this contrast was appropriate because of the notable topographical overlap between these processes in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017].
 We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals.

### 2019-09-09 Manuscript.Rmd
formatting tweaks

@@
 
-Keywords: functional connectivity, default network, individual differences, network neuroscience, medial prefrontal cortex
+## Highights:
+
+- Medial Default Network overlaps topographically with task effects such as valuation.
+
+- Qualitative work suggests overlap could be due to variability across individuals.
+
+- We used Spectral Partitioning to find and compare Default Network across individuals.
+
+- Topographical organization was highly idiosyncratic, especially in frontal regions.
+
+- Variability suggests that apparent overlap should be re-examined in individuals.
 
@@
 We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to partition mPFC and PCC into "DN" and "non-DN" subdivisions in individual participants (n = 100 from the Human Connectome Project).
-The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable across test/retest sessions and varied markedly across individuals, especially in mPFC.
+The spectral partitioning algorithm identified individual-level cortical subdivisions that were reliable across test/retest datasets and varied markedly across individuals, especially in mPFC.
+Location of the DN was informed by cortical folding, and resembled a recently proposed fractionation of this network.
 Our results point toward a new generation of strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions.
 
-## Introduction
+Keywords: functional connectivity, default network, individual differences, network neuroscience, medial prefrontal cortex
+
+\newpage
+
+## 1. Introduction
 
@@
 
-## Materials and Methods
-
-### *Code Accessibility*
+## 2. Material and Methods
+
+### 2.1. *Code Accessibility*
 
@@
 
-### *Search space*
+### 2.2. *Search space*
 
@@
 
-### *Meta-analysis*
+### 2.3. *Meta-analysis*
 
@@
 
-### *Resting-state fMRI Data*
+### 2.4. *Resting-state fMRI Data*
 
@@
 
-### *Network Definition*
+### 2.5. *Network Definition*
 
@@
 
-### *Community Detection*
+### 2.6. *Community Detection*
 
@@
 
-### *Partition Evaluation*
+### 2.7. *Partition Evaluation*
 
@@
 
-### *Seed-based Resting-state Functional Connectivity versus Community Detection*
+### 2.8. *Seed-based Resting-state Functional Connectivity versus Community Detection*
 
@@
 
-### *Associations with sulcal morphology*
+### 2.9. *Associations with sulcal morphology*
 
@@
 
-## Results
-
-### *Meta-analysis*
+## 3. Results
+
+### 3.1. *Meta-analysis*
 
@@
 
-### *Individual-level DN and non-DN communities*
+### 3.2. *Individual-level DN and non-DN communities*
 
@@
 
-### *Pattern variability over time*
+### 3.3. *Pattern variability over time*
 
@@
 
-### *Test/re-test reliability across days*
+### 3.4. *Test/re-test reliability across days*
 
@@
 
-### *Test/re-test reliability across runs*
+### 3.5. *Test/re-test reliability across runs*
 
@@
 
-### *Correlation vs community detection in mPFC*
+### 3.6. *Correlation vs community detection in mPFC*
 
@@
 
-### *Relationship between functional organization and sulcal morphology*
+### 3.7. *Relationship between functional organization and sulcal morphology*
 
@@
 Among these, recent work has suggested that the location of the DN in individuals lies mostly within sulci in vmPFC [@Lopez2019].
-We sought to reproduce this relationship using the SP communities, as well as interrogating whether it persisted in PCC and more dorsal mPFC regions.
+We sought to reproduce this relationship using the SP communities, and interrogated whether it persisted in PCC and more dorsal mPFC regions.
 
@@
 We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
-Correlations between FV and curvature were positive and significantly different than zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC.
+Correlations between FV and curvature were positive and significantly different from zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC.
 Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
@@
 
-### *Alignment of mPFC community structure with a proposed DN sub-network organization*
+### 3.8. *Alignment of mPFC community structure with a proposed DN sub-network organization*
 
@@
 
-## Discussion
+## 4. Discussion
 
@@
 Alternatively, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014].
-Our findings support this idea, echoing previous findings that DN is contained within sulci (in particular the superior rostral sulcus) in vmPFC [@Lopez2019].
-This relationship was heterogeneous throughout the rest of the search space, as more dorsal mPFC regions were likely located in gyri, whereas PCC had hemispheric differences in this association.
+Our results support this idea, echoing previous findings that DN is contained within sulci (in particular the superior rostral sulcus) in vmPFC [@Lopez2019].
+This relationship was heterogeneous throughout the rest of the search space.
+DN was likely located in gyri in more dorsal mPFC regions, whereas this association differed across hemispheres in PCC.
 An important goal for future work will be to assess whether the network layout in these regions can also be predicted on the basis of other aspects of brain structure, such as myeloarchitecture [@Glasser2016] or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
@@
 Regardless, this set of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
+
+### 4.1. *Conclusion*
 

### 2019-09-10 Manuscript.Rmd
small formatting updates

@@
 output:
+  word_document: #default
+    reference_docx: Style_reference_draft.docx
   pdf_document:
@@
     keep_tex: no
-  word_document: #default
-    reference_docx: Style_reference_draft.docx
 header-includes:
@@
   \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
-subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
+#subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
 bibliography: mPFC_paper.bib
@@
 
-## Highights:
+## Highlights:
 
@@
 
-\bigskip
+\newpage
 

### 2019-09-10 Manuscript.Rmd
Figure renaming

@@
 # see the function HCPOut for details on how they were transferred from R to CIFTI
-include_graphics("./Images/ROIS.png")
+include_graphics("./Images/FIG1.png")
 ```
@@
 The bottom brain shows the binarized Fiedler vector, with red areas denoting the DN community (as indicated by coverage of area 7m, bordered)."}
-include_graphics("./Images/FB_FV_example.png")
+include_graphics("./Images/FIG2.png")
 ```
@@
 
-include_graphics("./Images/similarity_all.png")
+include_graphics("./Images/FIG3.png")
 
@@
 
-include_graphics("./Images/SW_props.png")
+include_graphics("./Images/FIG4.png")
 
@@
 
-include_graphics("./Images/thresholded.png")
+include_graphics("./Images/FIG5.png")
 
@@
 
-include_graphics("./Images/ratios.png")
+include_graphics("./Images/FIG6.png")
 
@@
 
-include_graphics("./Images/commvscorr.png")
+include_graphics("./Images/FIG7.png")
 
@@
 
-include_graphics("./Images/sulciVSfv.png")
+include_graphics("./Images/FIG8.png")
 ```
@@
 # Change to inflated eventually
-include_graphics("./Images/braga_comparison.png")
+include_graphics("./Images/FIG9.png")
 
@@
 The addition of this area to the search space does not alter the original results, and the region is adequately covered by the DN community."}
-include_graphics("./Images/extra_examples.png")
+include_graphics("./Images/SFIG1.png")
 ```
@@
 
-include_graphics("./Images/ARI_comparison.png")
+include_graphics("./Images/SFIG2.png")
 
@@
 
-include_graphics("./Images/tSNR.png")
+include_graphics("./Images/SFIG3.png")
 ```
@@
 This shows that even with notably noisier estimates and lower within-individual ARI values produced by working with less data, it is possible to gain information about the general location of DN and non-DN in individuals."}
-include_graphics("./Images/days_runs_examples.png")
+include_graphics("./Images/SFIG4.png")
 ```
@@
 
-include_graphics("./Images/kmeansVSsp.png")
+include_graphics("./Images/SFIG5.png")
 ```

### 2019-09-12 Manuscript.Rmd
Sean second revisions for NI, up to a quarter of the methods

@@
   cortex
-author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
+author: "Claudio Toro-Serey^1^, Sean M. Tobyne^1,2^, & Joseph T. McGuire^1^"
 csl: apa.csl
@@
 
-- Qualitative work suggests overlap could be due to variability across individuals.
-
-- We used Spectral Partitioning to find and compare Default Network across individuals.
-
-- Topographical organization was highly idiosyncratic, especially in frontal regions.
-
-- Variability suggests that apparent overlap should be re-examined in individuals.
+- Overlap at the group level could be due to variability across individuals.
+
+- Individual subject level Default Networks were identified with Spectral Partitioning.
+
+- Topographical organization is highly idiosyncratic, especially in frontal regions.
+
+- Group-level overlap may be spurious and should be examined at the individual level.
 
@@
 Location of the DN was informed by cortical folding, and resembled a recently proposed fractionation of this network.
-Our results point toward a new generation of strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions.
-
-Keywords: functional connectivity, default network, individual differences, network neuroscience, medial prefrontal cortex
+Our results point toward a new generation of strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions, especially at the individual level.
+
+Keywords: functional connectivity, default network, individual differences, network neuroscience, medial prefrontal cortex, spectral partitioning
 
@@
 An alternative approach is to focus on analyses at the individual-participant level.
-Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Tobyne2018], and subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
+Individual-level analyses of fMRI data have identified idiosyncratic, reliable, and valid patterns of functional organization that would be blurred in aggregative estimates [@Gordon2017; @Gratton2018b; @Laumann2015; @Michalka2015; @Tobyne2018], and subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018].
 Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019].
@@
 
-### 2.1. *Code Accessibility*
-
-All code used in this study is openly available at [https://github.com/ctoroserey/mPFC_partitioning](https://github.com/ctoroserey/mPFC_partitioning)
+### 2.1. *Data and Code Accessibility Statement*
+
+All code used in this study is openly available at [https://github.com/ctoroserey/mPFC_partitioning](https://github.com/ctoroserey/mPFC_partitioning).
+Resting-state fMRI data was acquired from the Human Connectome Project [@VanEssen2012].
 
@@
 [-@Yeo2011].
-Even though this map misses sections of retrosplenial cortext that are typically involved in canonical DN [@Buckner2008], it provided a good coverage of regions in PCC and mPFC where valuation and DN overlap [@Acikalin2017].
+This map did not include sections of retrosplenial cortext that are typically included in canonical DN [@Buckner2008], however it did provide coverage of regions in PCC and mPFC where valuation and DN overlap [@Acikalin2017].
 First, we selected vertices on the medial cortical surface that were contained by the DN and limbic networks in HCP's 32,000 vertex surface space (fs_LR_32k).
@@
 subjects with four resting-state fMRI sessions).
-In addition, only datasets with low motion levels (under 1.5 mm) and less than 5% of points over 0.5 mm framewise displacement (FD) were used.
+In addition, only datasets with low motion levels (under 1.5 mm) and less than 5% of points over 0.5 mm framewise displacement [FD; @Power2014] were used.
 See [@VanEssen2012] for more details about the data acquisition protocol.
@@
 Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017].
-Steps (in order) included linear interpolation across high motion timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), and temporal denoising via mean grayordinate signal regression [@Burgess2016].
+Steps (in order) included linear interpolation across high motion timepoints with over 0.5 mm of FD, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), and temporal denoising via mean grayordinate signal regression [@Burgess2016].
+Interpolation of high motion time points is performed to avoid temporal smoothing of noisy signal from head motion into the filtered signal during the bandpass procedure.
 After filtering and denoising, the interpolated high-motion time points were censored by deletion and each run was temporally de-meaned.
@@
 In agreement with findings from Lopez-Persem et al.
-[@Lopez2019], we found that the DN community was likely to be found within the superior rostral sulcus in vmPFC.
+[-@Lopez2019], we found that the DN community was likely to be found within the superior rostral sulcus in vmPFC.
 The non-DN community covered both gyri and sulci in this area.
@@
 However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far [@Braga2017; @Braga2019; @Gordon2017].
-To affirm that DN and valuation share neural substrates in this area requires a method to reliably and precisely capture the functional topography of mPFC in isolated individuals, as well as a quantitative estimate of the degree of topographic heterogeneity across a large group of individuals.
+To affirm that DN, valuation, and other functions share neural substrates in this area requires a method to reliably and precisely capture the functional topography of mPFC in isolated individuals, as well as a quantitative estimate of the degree of topographic heterogeneity across a large group of individuals.
 

### 2019-09-12 Manuscript.Rmd
Sean revisions up to results, completed

@@
 All correlation values were transformed using Fisher's r to z.
-This produced a weighted network for each subject, in which the nodes were surface vertices and the edges were the correlations among them.
+This produced a weighted network for each subject, in which the nodes were surface vertices and the edge weights were the correlations among them.
 Edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, sd = `r sdPos`).
@@
 fully-connected) graphs [@chung1997].
-However, our results are unchanged even if we cut all non-significant correlations from the weight matrices.
+However, our results are unchanged even if we cut all non-significant correlations from the weight matrices (uncorrected).
 Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
@@
 Unlike SP, modularity can fractionate a network into more than two communities.
-Agreement between the partitions provided by the bounded and unbounded community detection methods would suggest the results are not distorted by the restriction of SP to binary partitionings.
+Agreement between the partitions provided by the bounded (SP) and unbounded (modularity) community detection methods would suggest the results are not distorted by the restriction of SP to binary partitionings.
 
@@
 First, we computed the degree of agreement between SP and modularity per subject.
-SP and Modularity have been previously found to show underfitting and overfitting tendencies, respectively, in their community detection performance in a diverse set of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings.
+SP and Modularity have been previously found to show a tendency for underfitting and overfitting, respectively, in their community detection performance in a diverse set of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings.
 Next, we compared the subject-level SP partitionings across individuals, and calculated the mean pairwise ARI for the group.
@@
 To estimate the degree of variability of partitionings per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partitioning against the partitioning derived from the subject's whole data set.
-A 20-min window has previously been found to approximate an individual's asymptote for the stability of community features in brain networks [@Gordon2017].
+A 20-min window has previously been found to approximate asymptotic stability of community features in brain networks as time series are lengthened [@Gordon2017].
 We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows.
@@
 We used each subject's curvature maps from the HCP (transformed to fs_LR 32k space), in which cortical depth is quantified by negative numbers for sulci and positive numbers for gyri.
-For each individual, we computed the correlation (Spearman) between curvature and the unthresholded Fiedler vector values in each region and hemisphere separately (6 correlations per individual).
+For each individual, we computed the Spearman correlation between curvature and the unthresholded Fiedler vector values in each region and hemisphere separately (6 correlations per individual).
 Since the DN is indicated by positive FV values, positive correlations meant that the DN was more likely to be contained in sulci, with non-DN housed in gyri.
@@
 We compared the partitioning derived from each window with the partitioning computed using the entire time series (Figure 4).
-The significant level of sequential overlap was meant to promote highly similar partitionings among nearby windows, so that we could identify nodes that were highly variable where discrepancies occurred.
-This also allowed us to determine whether these variable nodes followed a specific spatial structure.
+The significant level of sequential overlap was meant to promote highly similar partitionings among nearby windows, so that we could identify nodes that were highly variable where discrepancies occurred (i.e.
+highly variable nodes that changed their partition membership with minor perturbations to the windowed data).
+*This also allowed us to determine whether these variable nodes followed a specific spatial structure.*
 
@@
 Specifically, we estimated the proportion of DN affiliations per node as a function of Fiedler vector values, using a logistic mixed effects model (Figure 4).
-We stress that the stability expected from our highly overlapping windows added relevance to the observed variability.
 The model identified a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDN_modelSummary$coefficients[2, 2], digits = 2)`, *p* < 0.001), signifying that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community over time.
@@
 The relatively high inter-individual variability seen in the aggregate map could reflect at least three factors: (1) measurement noise, (2) dynamic variation in mPFC network organization, and (3) stable patterns of functional organization that differ across individuals.
-To arbritrate among these possibilities, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
+To arbitrate among these possibilities, we examined the test/re-test reliability of mPFC/PCC community structure across separate days of testing.
 Insofar as the observed variability reflects individual-specific brain organization, across-day ARI values should be consistently higher within-individual than between individuals (an example comparison for two individuals is provided in Supplemental Figure 2).

### 2019-09-13 Manuscript.Rmd
one last tweak
some subject maps got flipped again across days, now that data is unthresholded
I visually inspected the cross-day match and reflipped the necessary maps (some of which overlapped with the original flip list)

@@
 These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-For 7 subjects, the communities produced with one of the days' data sets had split coverage of area 7m, and so our community labeling scheme for the Fiedler vector produced a sign mismatch across days.
+For 8 subjects, the communities produced with one of the days' data sets had split coverage of area 7m, and so our community labeling scheme for the Fiedler vector produced a sign mismatch across days.
 ARI is robust to such labeling issues, but the inconsistency produced strong negative correlations of the Fiedler vector across days for these individuals.
@@
 highly variable nodes that changed their partition membership with minor perturbations to the windowed data).
-*This also allowed us to determine whether these variable nodes followed a specific spatial structure.*
 
@@
 temp <- list.files(pattern = "*_finalSummary.csv")
-subjList_halves <- sapply(temp, substring, first=1, last=9)
+subjList_halves <- sapply(temp, substring, first = 1, last = 9)
 Summaries_halves <- lapply(temp, read.csv)
@@
 # Some subjects didn't have the correct labeling scheme in one of their days (see corr vs FV below), so we manually reverted it after visual inspection
-revertSubjs <- c("144226_H2", "165840_H1", "192843_H1", "303624_H1", "687163_H1", "108525_H2", "156637_H1")
+revertSubjs <- c("102816_H2", "144226_H2", "192843_H1", "211720_H1", "303624_H1", "386250_H1", "687163_H1", "108525_H2")
 for (subj in revertSubjs) {
@@
 ## Now compare all possible pairs of subjects (for actual reporting)
-# Compare all halves with RI
+# Compare all halves with ARI
 RI_all_between_halves <- comparePartitions(Data = Summaries_halves, Index = "RI", nSubjects = length(Summaries_halves), subjNames = subjList_halves)
@@
 
-# paired permutations and effect sizes for within-subj perm vs corr
-prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
+# paired permutations and effect sizes for within-subj perm vs corr (8 subjs reversed)
+prepostComp_permTest <- permute(tempComm, tempCor, statType = median, paired = T)
 prepostComp_ES <- cohenD(tempComm, tempCor)
@@
 # # Day 1 vs Day 2 Spatial Correlation Comparison
-# prepostComp_plot <- ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
-#   geom_boxplot(show.legend = F) +
+# ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
+#   geom_boxplot(show.legend = F, size = 1.5) +
 #   labs(x = "", y = "Correlation Coefficient") +
-#   ylim(0,1) +
-#   theme(text = element_text(size=35)) +
-#   theme_classic()
-# prepostComp_plot
+#   ylim(NA,1) +
+#   geom_hline(yintercept = 0, linetype = "dashed", size = 1.2) +
+#   theme(legend.position = c(0.85, 0.7),
+#         legend.key=element_blank(),
+#         panel.grid.major = element_blank(),
+#         panel.grid.minor = element_blank(),
+#         panel.background = element_blank(),
+#         axis.line = element_line(colour = "black"),
+#         text = element_text(size = 22))
 
@@
 Day 1 community detection versus Day 2 seed-based correlation).
-While both approaches were reliable, community detection displayed a significantly higher mean correlation coefficient across days than seed-based correlation (Community: mean = `r round(mean(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: mean = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", round(prepostComp_permTest$Pval, digits = 3)))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
-Agreement across methods was fair (mean = `r round(mean(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences.
+While both approaches were reliable, community detection displayed a significantly higher median correlation coefficient across days than seed-based correlation (Community: median = `r round(median(tempComm), digits = 2)`, SD = `r round(sd(tempComm), digits = 2)`; Seed-based: median = `r round(mean(tempCor), digits = 2)`, SD = `r round(sd(tempCor), digits = 2)`; paired permutation *p* `r ifelse(prepostComp_permTest$Pval < 0.001, "< 0.001", paste("=", round(prepostComp_permTest$Pval, digits = 3)))`; Cohen's D = `r round(prepostComp_ES, digits = 2)`).
+Agreement across methods was fair (median = `r round(median(tempBoth), digits = 2)`, SD = `r round(sd(tempBoth), digits = 2)`), signifying that the two approaches identified similar topographic features but also had systematic differences.
 These findings suggest that graph-theoretic community detection algorithms are advantageous for detecting stable functional topologies, in addition to their other advantages of being data-driven, unbiased and observer agnostic.

### 2019-09-13 Manuscript.Rmd
intro rehashed

@@
 ---
-title: Individual heterogeneity in the functional network topography of medial prefrontal
+title: Spectral partitioning identifies individual heterogeneity in the functional network topography of ventral and anterior medial prefrontal
   cortex
@@
 
-1.  Department of Psychological and Brain Sciences, Boston University, Boston, USA
+1.  Department of Psychological and Brain Sciences and Center for Systems Neuroscience, Boston University, Boston, USA
 
@@
 
-  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are implicated in multiple cognitive functions, including subjective valuation processes and processes linked to the default network (DN).
-Our ability to interpret these seemingly co-localized effects is constrained by a limited understanding of the individual-level heterogeneity in mPFC/PCC functional organization.
-Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DN effects relative to valuation.
+  Regions of human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are part of the default network (DN), and additionally are implicated in diverse cognitive functions ranging from autobiographical memory to subjective valuation.
+Our ability to interpret the apparent co-localization of these effects is constrained by a limited understanding of the individual-level heterogeneity in mPFC/PCC functional organization.
+Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was more strongly associated with the DN than with valuation effects.
 We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to partition mPFC and PCC into "DN" and "non-DN" subdivisions in individual participants (n = 100 from the Human Connectome Project).
 The spectral partitioning algorithm identified individual-level cortical subdivisions that were reliable across test/retest datasets and varied markedly across individuals, especially in mPFC.
-Location of the DN was informed by cortical folding, and resembled a recently proposed fractionation of this network.
 Our results point toward a new generation of strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions, especially at the individual level.
@@
 
-  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large and diverse set of cognitive processes [@Hiser2018; @Kragel2018], and are among the regions implicated in a set of functions associated with the default network (DN) [@Buckner2008].
-In humans, areas in the DN are chiefly characterized by an increase in BOLD activity in the absence of externally oriented tasks [@Buckner2008], which is mirrored by a decrease in activity during cognitively demanding tasks compared with less-demanding task conditions or periods of rest [@Laird2009; @Mckiernan2003].
-The latter effect has fueled the idea of the DN as a "task-negative" network, although certain self-referential tasks can prompt its activation [@Spreng2012].
-Since activity in the DN is related to the availability to engage in introspective thought, its distincitve topographical pattern is often captured by inter-region correlations in resting-state fMRI data [@Buckner2008; @Fox2005; @Greicius2003; @Yeo2011].
-
-  In addition to their role in undirected mentation, mPFC and PCC participate in subjective valuation during economic decision making.
-Both regions (together with ventral striatum) consistently show greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011].
-While many cognitive functions can be at least partially separated in mPFC [@DelaVega2016; @Hiser2018; @Kragel2018], coordinate-based meta-analyses of the fMRI literature show that valuation indistinguishably overlaps with the DN in ventral mPFC [@Acikalin2017].
-However, subjective valuation and introspective cognition diverge in other brain areas; a region of the striatum is preferentially associated with valuation, whereas bilateral temporoparietal junction is linked with the DN.
-Within PCC and adjacent precuneus, a more posterior subregion appears DN-specific, whereas a more anterior subregion is implicated in both effects.
-One possible interpretation of these findings is that mPFC and anterior PCC operate as common nodes within partially overlapping distributed brain systems that subserve valuation and DN-related cognition.
-This colocalization has prompted theories that these processes share common elements at the psychological level.
-For example, the two sets of processes might share elements of self-referential cognition, episodic memory, mental simulation, or monitoring and regulation of internal states [@Acikalin2017; @Clithero2014; @Northoff2012; @Reddan2018].
+  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a diverse set of cognitive processes [@Hiser2018; @Kragel2018], and contain subregions that are part of the brain's default network [DN; @Buckner2008].
+DN regions are characterized by a decrease in BOLD activity during externally oriented tasks  that require attention or cognitive control, in comparison with less-demanding task conditions or periods of rest [@Buckner2008; @Laird2009; @Mckiernan2003].
+The DN can also be identified on the basis of a distinctive pattern of inter-region correlations in resting-state fMRI data [@Buckner2008; @Fox2005; @Greicius2003; @Yeo2011].
+
+*Many different cognitive task manipulations evoke patterns of brain activity that overlap with DN regions in ventral/anterior mPFC and in PCC.
+Examples include manipulations of self-referential thinking *(Gusnard et al., 2001;* [@Mitchell2005], memory *(Schacter et al., 2007;*[@Euston2012], affective regulation *(Schiller et al., 2008;*[@Reddan2018], and subjective valuation [@Bartra2013; @Clithero2014; @Kable2007; @Levy2011).
+Some of these task-related effects are thought to reflect processes integral to the functional role of the DN, such as internally oriented cognition, scene construction, and self-projection [@Hassabis2007].
+For other task-related effects, such as subjective valuation (i.e., greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued), the degree of overlap with DN regions is only partial and the reason for the overlap is less obvious [@Acikalin2017].
+Insofar as the DN shares a subset of nodes in common with the distributed brain system that supports valuation and other functions, this has potential to inform our theoretical understanding of the cognitive operations involved in those functions [@Northoff2012].
+As a result, there is widespread interest in understanding the degree to which DN regions overlap topographically with task-related effects [@Dinicola2019; @Spreng2012].*
 
@@
 A recognized limitation of group averaging and meta-analysis is that the functional topography of individual brains can be misaligned and blurred [@Fedorenko2012; @Guntupalli2018a; @Michalka2015; @Tobyne2018; @Wang2015; @Woo2014], exaggerating the apparent overlap across domains.
-This concern is especially pronounced in mPFC, which is subject to considerable idiosyncratic cortical folding [@Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013].
+This concern is especially pronounced in ventral mPFC, which is subject to considerable idiosyncratic cortical folding [@Lopez2019; @Mackey2014; @Zilles2013] and inter-subject functional variability [@Mueller2013].
 An alternative approach is to focus on analyses at the individual-participant level.
@@
 Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019].
-It is therefore possible that the previously reported overlap of the DN with valuation effects can be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
-An important first step, and the goal of the present paper, is to quantify the degree of topographic heterogeneity of the DN within mPFC and PCC in a large sample of individuals.
-This evaluation of variability during rest will provide a frame of reference for individualized topographical estimation of behavioral effects (such as valuation) in the future, and could provide insights on the extent to which certain task-positive effects attributed to DN regions truly belong to this network [@Spreng2012].
+It is therefore possible that the previously reported overlap of the DN with task-related effects could, in some cases, be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
+An important first step, and the goal of the present paper, is to quantify the degree of variability in the topography of the DN within mPFC and PCC across a large sample of individuals.
+The methods we propose for individual-level identification of DN regions have potential to benefit future investigations of the overlap between DN regions and task-related activity.
 
@@
   The outline of our paper is as follows.
-First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks on the medial cortical wall [@Yeo2011].
+First, we defined a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks on the medial cortical wall [@Yeo2011].
 A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level.
+Valuation was selected as a domain in which task-related activity patterns overlap extensively with DN regions on the medial surface, despite being segregable elsewhere [@Acikalin2017].
 We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
@@
 The resulting communities varied topographically across individuals, while also appearing to follow common organizational principles.
-Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that individual-level idiosyncrasy was greater in mPFC.
+Test-retest analyses showed that these partitionings were similar across scanning days within (but not between) individuals, and that individual-level idiosyncrasy was greater in mPFC.
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
@@
 Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019].
-Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, provides a new framework and tool set for future investigations of overlap across cognitive domains, and motivates future re-examination of seemingly inseparable cognitive processes (such as valuation and introspective thought) in these areas.
+Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, provides a new framework and tool set for future investigations of overlap across cognitive domains.
 

### 2019-09-13 Manuscript.Rmd
JTM revisions, up to results

@@
 [-@Yeo2011].
-This map did not include sections of retrosplenial cortext that are typically included in canonical DN [@Buckner2008], however it did provide coverage of regions in PCC and mPFC where valuation and DN overlap [@Acikalin2017].
 First, we selected vertices on the medial cortical surface that were contained by the DN and limbic networks in HCP's 32,000 vertex surface space (fs_LR_32k).
-Next, we overlaid those networks on a parcellated atlas of the human cortical surface [360 regions; @Glasser2016], and retained a set of parcels that covered approximately the same brain regions (at least 15% overlap, visually inspected).
+Next, we overlaid those networks on a parcellated atlas of the human cortical surface [360 regions; @Glasser2016], and retained a set of parcels that covered approximately the same brain regions (visually inspected, retaining parcels that appeared to have at least 15% overlap).
 This resulted in a search space that consisted of 40 parcels across hemispheres (Supplementary Table 1).
@@
 
-We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with valuation or DN-related processes.
-For subjective valuation, we gathered peak activation coordinates from 200 studies that were associated with positive effects in contrasts of higher-value minus lower-value outcomes or prospects [@Bartra2013].
-For DN, we acquired coordinates from 80 studies that were related to task-deactivation (i.e.
-findings where externally directed tasks reduced BOLD compared to a baseline) [@Laird2009].
+We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels within the search space were preferentially associated with subjective valuation or with decreased activity during externally oriented tasks, which served to operationalize the DN.
+For subjective valuation, we gathered peak activation coordinates from 200 studies that reported positive effects in contrasts of higher-value minus lower-value outcomes or prospects [@Bartra2013].
+For the DN, we acquired coordinates from 80 studies that reported reductions in BOLD during externally directed tasks compared to a baseline [@Laird2009].
 The coordinates represent areas that exceeded the statistical significance threshold in each original study.
@@
 Our fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (N = `r length(dir(path = './Summary'))`, randomly sampled from the total pool of 469 available subjects).
+The Washington University Institutional Review Board approved all experimental procedures, and all subjects provided written informed consent in accordance with the guidelines set by the institution.
 Each subject's data was acquired over two days at Washington University in St.
@@
 Edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, sd = `r sdPos`).
-We chose not to threshold this network, as SP is well equipped to operate on complete (i.e.
-fully-connected) graphs [@chung1997].
-However, our results are unchanged even if we cut all non-significant correlations from the weight matrices (uncorrected).
-Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution.
+We chose not to threshold the network, as the SP algorithm is well equipped to operate on complete (i.e.
+fully-connected) weighted graphs [@chung1997].
+However, our results are unchanged if we cut all non-significant correlations from the weight matrices (uncorrected).
+Next, we took the exponential of the z-transformed correlations so that all weights became positive while maintaining their ordinal ranks.
 Ensuring that all edges were positive facilitated the construction of the graph Laplacian (see below), which requires all off-diagonal elements to have the same sign by design.
@@
 In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
-Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the DN-specific PCC parcel identified in our meta-analysis (i.e.
-over 50% coverage).
+Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DN" community as that which contained the majority of the vertices in the DN-specific PCC parcel identified in our meta-analysis (area 7m).
 The completeness of the graphs ensured that SP did not face the issues associated with its use in sparse networks [@Fortunato2016].
@@
 
-where $a$ is the number of pairs of nodes that were grouped together in both partitionings, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number of nodes grouped together (separately) in one partitioning, but separately (together) in the other.
+where $a$ is the number of pairs of nodes that were grouped together in both partitionings, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number of pairs grouped together (separately) in one partitioning, but separately (together) in the other.
 Therefore, the ARI estimates the fraction of all possible node pairs that had the same status (connected or not) in both partitionings (with the denominator equal to $n(n - 1)/2$).
@@
 We then performed the same evaluation for PCC and mPFC separately, and examined whether there were differences in overall agreement within these regions by performing a paired permutation analysis.
-We randomized the sign of the difference in pairwise ARI across individuals between mPFC and PCC 5000 times, and computed the mean of these differences across all comparisons on each iteration.
+For each individual and region we got the mean ARI with all 99 other individuals, then took the difference between regions to get an ARI difference per subject.
+On each of 5000 permutations each subject’s ARI difference was independently sign-flipped and the mean difference across subjects was added to a null distribution.
 The empirical difference in mean pairwise ARI between regions was then evaluated against this permuted distribution.
 
-To estimate the degree of variability of partitionings per individual we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partitioning against the partitioning derived from the subject's whole data set.
-A 20-min window has previously been found to approximate asymptotic stability of community features in brain networks as time series are lengthened [@Gordon2017].
+To identify vertices whose community assignment was more stable or more variable, we performed a sliding window analysis (20 min windows, 1 min increments, median number of windows per subject = 37, range = 35 - 37), comparing each window's resulting partitioning against the partitioning derived from the subject's whole data set.
+A 20-min window has previously been found to yield relatively stable and unbiased estimates of individual-level brain network characteristics [@Gordon2017].
 We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows.
@@
 Independently for each day (2 per individual), we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in the PCC search space.
-We used the whole region to echo the approach often taken in seed-based connectivity analyses that do not rely on ROIs derived from independent analyses.
+We used the whole PCC region because it is traditionally thought to be part of the DN [@Buckner2008], it is a common area for researchers to place seeds for vertex- and volume-based connectivity analyses [@Fox2005], and it was often dominated by the DN community.
 We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP, with the sign of the Fiedler vector oriented so the DN community was marked by positive values in every subject.
@@
 
-Next we asked whether the location of the DN and non-DN communities was guided by sulcal morphology.
-Based on previous reports of individual alignment of DN within sulci in ventral mPFC [@Lopez2019], we sub-divided our search space into three regions: vmPFC, which matched their ROI (areas 25, s32, a24, 10v, 10r, p32, and OFC); superior mPFC (sup-mPFC), encompassing the remaining dorsal areas in our mPFC space; and all of the PCC search space.
+Next we asked whether the location of the DN and non-DN communities was systematically related to sulcal morphology.
+Based on a previous report of individual alignment of DN within sulci in ventral mPFC [vmPFC; @Lopez2019], we subdivided our search space into three regions: vmPFC, which matched the ROI used by Lopez-Persem and colleagues (2019; areas 25, s32, a24, 10v, 10r, p32, and OFC); superior mPFC (sup-mPFC), encompassing the remaining dorsal areas in our mPFC space; and all of the PCC search space.
 We used each subject's curvature maps from the HCP (transformed to fs_LR 32k space), in which cortical depth is quantified by negative numbers for sulci and positive numbers for gyri.
 For each individual, we computed the Spearman correlation between curvature and the unthresholded Fiedler vector values in each region and hemisphere separately (6 correlations per individual).
-Since the DN is indicated by positive FV values, positive correlations meant that the DN was more likely to be contained in sulci, with non-DN housed in gyri.
-Finally, we collected all individual correlations for each combination of hemisphere and region, and performed a one-sample t-test on each set to determine whether correlations were significantly different than 0 in our group (6 tests total).
+Since the DN was indicated by positive FV values, negative correlations meant that the DN was more likely to be contained in sulci, with non-DN located in gyri.
+Finally, we collected all individual correlations for each combination of hemisphere and region, and performed a one-sample t-test on each set to determine whether correlations were significantly different from 0 in our group (6 tests total).
 

### 2019-09-14 Manuscript.Rmd
results ready

@@
   cortex
-author: "Claudio Toro-Serey^1^, Sean M. Tobyne^1,2^, & Joseph T. McGuire^1^"
+author: "Claudio Toro-Serey^1,2^, Sean M. Tobyne^1,3^, & Joseph T. McGuire^1,2^"
 csl: apa.csl
@@
 
-1.  Department of Psychological and Brain Sciences and Center for Systems Neuroscience, Boston University, Boston, USA
-
-2.  Graduate Program for Neuroscience, Boston University, Boston, USA
+1.  Department of Psychological and Brain Sciences, Boston University, Boston, USA
+
+2.  Center for Systems Neuroscience, Boston University, Boston, USA
+
+3.  Graduate Program for Neuroscience, Boston University, Boston, USA
 
@@
 
-*Many different cognitive task manipulations evoke patterns of brain activity that overlap with DN regions in ventral/anterior mPFC and in PCC.
-Examples include manipulations of self-referential thinking *(Gusnard et al., 2001;* [@Mitchell2005], memory *(Schacter et al., 2007;*[@Euston2012], affective regulation *(Schiller et al., 2008;*[@Reddan2018], and subjective valuation [@Bartra2013; @Clithero2014; @Kable2007; @Levy2011).
+Many different cognitive task manipulations evoke patterns of brain activity that overlap with DN regions in ventral/anterior mPFC and in PCC.
+Examples include manipulations of self-referential thinking [@Gusnard2001; @Mitchell2005], memory [@Euston2012; @Schacter2007], affective regulation [@Reddan2018; @Schiller2008], and subjective valuation [@Bartra2013; @Clithero2014; @Kable2007; @Levy2011).
 Some of these task-related effects are thought to reflect processes integral to the functional role of the DN, such as internally oriented cognition, scene construction, and self-projection [@Hassabis2007].
@@
 Insofar as the DN shares a subset of nodes in common with the distributed brain system that supports valuation and other functions, this has potential to inform our theoretical understanding of the cognitive operations involved in those functions [@Northoff2012].
-As a result, there is widespread interest in understanding the degree to which DN regions overlap topographically with task-related effects [@Dinicola2019; @Spreng2012].*
+As a result, there is widespread interest in understanding the degree to which DN regions overlap topographically with task-related effects [@Dinicola2019; @Spreng2012].
 
@@
 This produced a weighted network for each subject, in which the nodes were surface vertices and the edge weights were the correlations among them.
-Edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, sd = `r sdPos`).
+Edges mostly consisted of positive correlations (mean proportion positive = `r mPos`, SD = `r sdPos`).
 We chose not to threshold the network, as the SP algorithm is well equipped to operate on complete (i.e.
@@
 
-We performed a coordinate-based meta-analysis to identify cortical surface parcels within mPFC and PCC that were preferentially associated with the DN or valuation literature.
+We performed a coordinate-based meta-analysis to identify cortical surface parcels within mPFC and PCC that were preferentially associated with the DN or with subjective valuation.
 Volumetric coordinates from 80 studies with task deactivation contrasts and 198 studies with valuation contrasts were projected onto a cortical surface, and mapped to discrete parcels from a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study.
@@
 Since this is a data-driven approach, there is no a priori labeling for the two communities.
-We assigned the DN label to the community that contained the DN-specific PCC parcel from the meta-analysis (7m).
+We assigned the DN label to the community that contained the majority of the DN-specific PCC parcel from the meta-analysis (7m).
 We oriented each individual's Fiedler vector so positive values corresponded to the DN community [@Nenning2017], and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN).
@@
 This non-DN section extended posteriorly into pregenual cinglate cortex (area a24).
-We note that the addition of restrosplenial cortex (an area commonly regarded as part of canonical DN) to the search space did not change these results, and that the area was adequately covered by the DN community (Supplemental Figure 1).
+We note that the addition of restrosplenial cortex (an area commonly regarded as part of canonical DN) to the search space did not change these results; as expected, that the area tended to be largely assigned to the DN community (Supplemental Figure 1).
 
@@
 
-Before evaluating the degree of generazibility of this topographic pattern across individuals, we examined the validity of the partitionings by comparing them to results from an alternative community detection algorithm, modularity maximization [@Clauset2004].
+Before evaluating the degree of generalizibility of this topographic pattern across individuals, we examined the validity of the partitionings by comparing them to results from an alternative community detection algorithm, modularity maximization [@Clauset2004].
 Modularity seeks to find the set of communities that maximizes within-community connection weights relative to a null model.
@@
 
-We next sought to estimate the variability of individual partitionings over time.
+We next sought to estimate whether individual vertices had a stable or unstable community affiliation over time.
 We did so by performing a sliding window analysis on each subject's full time series (20 min windows shifting by 1 min).
 We compared the partitioning derived from each window with the partitioning computed using the entire time series (Figure 4).
-The significant level of sequential overlap was meant to promote highly similar partitionings among nearby windows, so that we could identify nodes that were highly variable where discrepancies occurred (i.e.
-highly variable nodes that changed their partition membership with minor perturbations to the windowed data).
+Our focus here was not on the overall level of agreement (which is expected to be high given the use of overlapping data), but on differences in stability across nodes.
+The sliding window analysis provided a means to identify nodes that were highly variable, and allowed us to determine whether these variable nodes followed a specific spatial structure.
 
@@
 
-The mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation, *p* `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
+The mean ARI along each subject's time series was significantly higher for PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) than mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; paired permutation, *p* `r ifelse(SW_PCCvPFC_permuteTest$Pval < 0.001, "< 0.001", paste("=", SW_PCCvPFC_permuteTest$Pval))`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`).
 A subset of nodes showed exceptionally high stability, in that they were assigned to the same community in every time window.
@@
 We calculated tSNR using time series that were not demeaned, but were otherwise equivalent to the data originally used.
-A map of the mean tSNR across individuals can be found on Supplemental Figure 3.
+A map of the mean tSNR across individuals can be found in Supplemental Figure 3.
 In terms of tSNR variability across vertices within each region, mPFC had overall greater spatial standard deviation both before and after thresholding (mPFC: pre-threshold mean spatial SD = 33.96, post-threshold mean spatial SD = 30.15; PCC: pre-threshold mean spatial SD = 15.28, post-threshold mean spatial SD = 14.59).
-However, tSNR after thresholding was significantly higher for mPFC than PCC (mPFC: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; PCC: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
+However, mean tSNR after thresholding was significantly higher for mPFC than PCC (mPFC: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; PCC: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
 This reflected a significant increase in mean tSNR in mPFC as a result of the thresholding step (pre-threshold mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (pre-threshold mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
@@
 ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC, 0.75), digits = 2)`, V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC, 0.75), digits = 2)`, V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`).
-Moreover, the ratios for mPFC were significantly greater than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
-This pattern was mostly unchanged when computed using modularity to detect these communities, showing that the results persist even without a forced binarization (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
-These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found on Supplemental Figure 4).
+Moreover, the ratios for mPFC were significantly greater than those for PCC when compared in a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
+This pattern was mostly unchanged when computed using modularity maximization to detect the communities, showing that the results persist even without a forced binarization (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
+These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found in Supplemental Figure 4).
 We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner.
@@
 The duration of each run (approximately 14 min) falls well below a previously suggested stability threshold for fMRI-based modularity estimations [@Gordon2017].
-Nonetheless, high ARI ratios could indicate that the SP algorithm can still estimate individual-specific patterns of DN organization from a single run of data.
+Nonetheless, high ARI ratios could indicate that the SP algorithm can still obtain information about individual-specific patterns of DN organization from a single run of data.
 
@@
 Run-specific SP results captured unique organizational patterns to some degree, even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]], na.rm = T), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]], na.rm = T), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`).
-Supplemental Figure 4 shows that even though the community estimates were indeed less reliable within-individuals than those captured using daily data (and sometimes even failed to produce meaningful partitionings), the layout of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data.
+Supplemental Figure 4 shows that even though the community estimates were indeed less reliable within-individuals than those captured using per-day data (and sometimes even failed to produce meaningful partitionings), the layout of DN and non-DN was still observable in many cases, and was comparable to the organization seen using larger amounts of data.
 We again computed each subject's ARI ratio in order to quantify the specificity of the partitions, this time using the mean of 6 across-run (within-participant) ARI values in the numerator of the ratio (Figure 6, right).
@@
 As before, a signed rank test showed that both regions had ARI ratios significantly greater than 1 (mPFC: median = `r round(median(Sess_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PFC, 0.25, na.rm = T), digits = 2)` - `r round(quantile(Sess_RIRatios_PFC, 0.75, na.rm = T), digits = 2)`, V = `r Sess_PFC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PFC_ratioTest$p.value))`; PCC: median = `r round(median(Sess_RIRatios_PCC, na.rm = T), digits = 2)`, IQR = `r round(quantile(Sess_RIRatios_PCC, 0.25, na.rm = T), digits = 2)` - `r round(quantile(Sess_RIRatios_PCC, 0.75, na.rm = T), digits = 2)`, V = `r Sess_PCC_ratioTest$statistic`, *p* `r ifelse(Sess_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Sess_PCC_ratioTest$p.value))`), and ratios for mPFC were higher than those of PCC (permutation *p* = `r ifelse(Sess_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Sess_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Sess_mPFCvPCC_ES, digits = 2)`).
-This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data, albeit coarsely.
+This result further confirms that the intrinsic functional organization of mPFC is uniquely arranged per individual, and provides evidence that information about such patterns can be extracted from relatively small amounts of data.
 
@@
 We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC.
-The use of the whole PCC region (instead of just 7m) was meant to echo the way seed-based connectivity is often employed in the absence of prior analytic ROI selection.
+The use of the whole PCC region (instead of just 7m) was meant to echo the way seed-based connectivity is often employed, relying on the group-average location of canonical DN regions.
 We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations across vertices.
 Pairwise spatial correlations were calculated among maps computed for each day and method from all individuals.
-Figure 7A shows that these pairwise comparisons resemble those from the across-day comparisons above, and suggests good alignment between methods, but particularly high agreement within subject and method.
+Figure 7A shows that these pairwise comparisons resembled those from the across-day comparisons above, and suggested good alignment between methods, but particularly high agreement within subject and method.
 
@@
                           TStat = round(t.test(Correlation)$statistic, digits = 2),
-                          p = round(t.test(Correlation)$p.val, digits = 4),
+                          p_unc = t.test(Correlation)$p.val,
                           Sig = p < 0.05,
                           ES = DescTools::CohenD(Correlation))
+
+# FDR correction
+curvStats$p <- round(p.adjust(curvStats$p_unc, method = "BY"), digits = 3)
 
@@
 
-Next, we asked if the idiosyncratic organization of the DN was reflected by patterns of sulcal morphology.
-A variety of studies have provided evidence that suclal and gyral organization inform the location of functional effects [@Amiez2013; @Amiez2014; @Zlatkina2016].
-Among these, recent work has suggested that the location of the DN in individuals lies mostly within sulci in vmPFC [@Lopez2019].
-We sought to reproduce this relationship using the SP communities, and interrogated whether it persisted in PCC and more dorsal mPFC regions.
+Next, we asked if the idiosyncratic organization of the DN was corresponded to patterns of sulcal morphology.
+Several previous studies have provided evidence that sulcal and gyral organization informs the location of functional effects [@Amiez2013; @Amiez2014; @Zlatkina2016].
+Recent work has suggested that DN regions in individuals lie mostly within sulci in vmPFC [@Lopez2019].
+We sought to reproduce this relationship using the SP communities, and interrogated whether it persisted in PCC and more superior mPFC regions.
 
 Figure 8A shows a qualitative comparison between the thresholded DN and non-DN communities and curvature maps for two individuals.
-In agreement with findings from Lopez-Persem et al.
-[-@Lopez2019], we found that the DN community was likely to be found within the superior rostral sulcus in vmPFC.
-The non-DN community covered both gyri and sulci in this area.
-A similar trend was present in PCC (especially in the left hemisphere), where the DN community traced sulcal layouts and non-DN was more likely to appear in gyri.
-This relationship was not as clear in sup-mPFC, where both DN and non-DN could be mapped onto both gyri and sulci.
+In agreement with findings from Lopez-Persem and colleagues [-@Lopez2019], the DN community appeared to overlap with the superior rostral sulcus in vmPFC in these individuals, whereas the non-DN community included both gyri and sulci.
+A similar trend was observable in left PCC, where the DN community traced sulcal layouts and non-DN was more likely to appear in gyri.
 
@@
 Zoomed-in boxes show areas in PCC and ventral mPFC where the DN community appears to be guided by sulcal organization.
-This relationship is less defined in superior mPcFC.
-The superior rostral sulcus houses the DN community, in agreement with findings by Lopez-Persem et al.
+This relationship is less defined in superior mPFC.
+The superior rostral sulcus aligned with the DN community, in agreement with findings by Lopez-Persem et al.
 (2019).
@@
 We divided the search space into three areas (left): ventral mPFC (yellow), superior mPFC (sup-mPFC, red), and PCC (blue).
-Boxplots on the right show the distribution of correlation values across individuals for each combination of region and hemisphere, indicating that DN (signaled by positive FV values) tended to be represented in vmPFC sulci, but was likely located in gyri within sup-dmPFC.
-PCC had an inversed relationship across hemispheres, with DN landing more often in left hemisphere sulci."}
+Boxplots on the right show the distribution of correlation values across individuals for each combination of region and hemisphere, indicating that DN (defined by positive FV values) tended to be represented in vmPFC sulci, but was likely located in gyri within sup-dmPFC.
+PCC showed evidence of an opposite association across hemispheres."}
 # # box plot
@@
 
-We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the one used by Lopez-Persem et al.
-[-@Lopez2019], a superior mPFC zone (sup-mPFC) that contained the remaining dorsal mPFC regions, and PCC (Figure 8B, left).
+We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the region tested by Lopez-Persem et al.
+[-@Lopez2019], a superior mPFC area (sup-mPFC) that contained the remaining mPFC regions, and PCC (Figure 8B, left).
 For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere.
-Negative correlations in this context imply that the DN was likely found in sulci and non-DN in gyri.
-Results can be found on Figure 8B.
-We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
-Correlations between FV and curvature were positive and significantly different from zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC.
-Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
+Negative correlations in this context imply that the DN was found in sulci and non-DN in gyri.
+Results are shown in Figure 8B.
+Correlations tended to be slightly negative in vmPFC, both on the left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`); the distribution was only significantly different from zero in the right hemisphere, and weakly so (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`, FDR corrected; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
+Correlations between FV and curvature were positive and significantly different from zero in sup-mPFC, both on the left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`).
+Correlations in PCC were negative and significantly different from zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
 The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2)`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`).
-These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al.
-[-@Lopez2019], and suggest that the association between function and structure is heterogenous within canonical DN.
+These results provide preliminary indictations that the association between function and structure is heterogenous across subregions of the canonical DN.
 
@@
 
-Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A.
+Visual inspection of these networks showed high similarity between our DN community and the previously reported sub-network A.
 However, the non-DN community filled areas not covered by either DN-A or DN-B.
@@
 comparison with modularity), we ran additional evaluations to confirm its existence.
-First, we reproduced the whole-brain k-means clustering analysis (n of clusters = 12, 100 iterations) performed by Braga et al.
-[-@Braga2019] in our two subjects using their full time series (Supplemental Figure 5A).
-In addition to identifying DN networks A and B through this approach (in line with their findings), we found a third cluster that aligned well with the non-DN community.
-To understand why we could not find the three discrete clusters before, we performed a silhouette analysis to determine the ideal number of clusters in our search space (Supplemental Figure 5B).
-For every individual, we ran k-means clusterings with a specified number of clusters ranging from 2 to 5, and computed a silhouette score for each solution (higher silhouette scores indicate a better fit).
-Scores decreased as the number of clusters increased for all individuals, suggesting that a bisection was indeed the best solution.
-Paired permutations comparing mean scores across individuals indicated that the difference between two (mean = 0.042, SE = 0.001) and three (mean = 0.032, SE = 0.0009) cluster solutions was significant (*p* < 0.0001, Cohen's D = 0.96).
+First, we reproduced the whole-brain k-means clustering analysis (12 clusters, 100 iterations) performed by Braga et al.
+[-@Braga2019] using the full time series for two subjects (Supplemental Figure 5A).
+In addition to identifying DN networks A and B through this approach (in line with previous findings), we found a third cluster that aligned well with the non-DN community.
+To understand why modularity maximization did not identify the same three discrete clusters within the search space, we performed a silhouette analysis to determine the ideal number of clusters in our search space (Supplemental Figure 5B).
+For all 100 individuals, we ran k-means clusterings restricted to the mPFC/PCC search space with a specified number of clusters ranging from 2 to 5, and computed a silhouette score for each solution (higher silhouette scores indicate a better fit).
+Scores decreased as the number of clusters increased beyond 2 for all individuals, suggesting that a bisection was indeed the best solution.
+Paired permutations comparing silhouette scores across individuals indicated that the difference between two (mean = 0.042, SE = 0.001) and three (mean = 0.032, SE = 0.0009) cluster solutions was significant (*p* < 0.0001, Cohen's D = 0.96).
 Visualization of a two-cluster k-means revealed a close match with partitionings estimated through modularity, and are comparable to those produced by SP prior to thresholding (Supplemental Figure 5A, bottom rows).
@@
 
-These results supports the idea that the two approaches serve complementary purposes.
+These results support the idea that the two approaches serve complementary purposes.
 Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
-Furthermore, they show that our approach can identify the three networks in PCC and mPFC in a way that is less computationally demanding than full-brain clustering, outperforming other clustering methods that lack the type of continuous information provided by SP.
+Furthermore, they show that our approach, through its continuous-valued information, provides a way to estimate the location of the three networks in PCC and mPFC in a way that is less computationally demanding than full-brain clustering.
 

### 2019-09-14 Manuscript.Rmd
discussion ready

@@
 
-  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a diverse set of cognitive processes [@Hiser2018; @Kragel2018], and contain subregions that are part of the brain's default network [DN; @Buckner2008].
+  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a diverse set of cognitive processes [@Hiser2018; @Kragel2018], and contain subregions that are part of the brain's default network [DN; @Buckner2008; @Buckner2019].
 DN regions are characterized by a decrease in BOLD activity during externally oriented tasks  that require attention or cognitive control, in comparison with less-demanding task conditions or periods of rest [@Buckner2008; @Laird2009; @Mckiernan2003].
@@
 Many different cognitive task manipulations evoke patterns of brain activity that overlap with DN regions in ventral/anterior mPFC and in PCC.
-Examples include manipulations of self-referential thinking [@Gusnard2001; @Mitchell2005], memory [@Euston2012; @Schacter2007], affective regulation [@Reddan2018; @Schiller2008], and subjective valuation [@Bartra2013; @Clithero2014; @Kable2007; @Levy2011).
+Examples include manipulations of self-referential thinking [@Gusnard2001; @Mitchell2005], memory [@Euston2012; @Schacter2007], affective regulation [@Reddan2018; @Schiller2008], and subjective valuation [@Bartra2013; @Clithero2014; @Kable2007; @Levy2011].
 Some of these task-related effects are thought to reflect processes integral to the functional role of the DN, such as internally oriented cognition, scene construction, and self-projection [@Hassabis2007].
@@
 Insofar as the DN shares a subset of nodes in common with the distributed brain system that supports valuation and other functions, this has potential to inform our theoretical understanding of the cognitive operations involved in those functions [@Northoff2012].
-As a result, there is widespread interest in understanding the degree to which DN regions overlap topographically with task-related effects [@Dinicola2019; @Spreng2012].
+As a result, there is widespread interest in understanding the degree to which DN regions overlap topographically with task-related effects [@Buckner2019; @Dinicola2019; @Spreng2012].
 
@@
 A considerable amount of meta-analytic work has been dedicated to characterizing the brain activity patterns associated with psychological processes in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across domains [@DelaVega2016; @Kragel2018; @Hiser2018].
-In particular, activation patterns associated with subjective valuation and with the default network (DN) have been suggested to be inseparable in this area, with overlap also partially extending to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
-This apparent neural overlap has important implications, as it has motivated theoretical proposals about ways in which these superficially dissimilar domains might involve a shared set of core cognitive processes [@Acikalin2017; @Clithero2014; @Northoff2012].
+For example, activation patterns associated with subjective valuation and with the default network (DN) have been suggested to be indistinguishable in mPFC, with overlap also partially extending to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
+This apparent overlap of task-related effects with DN regions has important implications, as it has motivated theoretical proposals about ways in which these superficially dissimilar domains might involve a shared set of core cognitive processes [@Acikalin2017; @Clithero2014; @Northoff2012].
 
@@
 These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.
-However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far [@Braga2017; @Braga2019; @Gordon2017].
-To affirm that DN, valuation, and other functions share neural substrates in this area requires a method to reliably and precisely capture the functional topography of mPFC in isolated individuals, as well as a quantitative estimate of the degree of topographic heterogeneity across a large group of individuals.
+To date, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive [@Braga2017; @Braga2019; @Gordon2017].
+A strong test of the overlap between task-related effects and DN regions would require a method to reliably and precisely capture the functional topography of mPFC in isolated individuals, as well as a quantitative estimate of the degree of topographic heterogeneity across a large group of individuals.
 
 Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Toker2019].
-For 100 individuals, we subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities.
+For each of 100 individuals, we subdivided canonical DN regions into DN and non-DN communities.
 Restricting our analyses to a general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning that was sensitive to the complex topography of the brain.
@@
 preventing the allocation of most vertices to a single community), providing continuous values that relate to the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007].
-Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], plus a silhouette analysis, suggested the binary partitioning was appropriate.
-
-We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC.
+Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], as well as a silhouette analysis, suggested the binary partitioning was appropriate.
+
+We found a generalizable pattern across individual partitionings, in which the DN community covered ventral and anterior/superior mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC.
 The precise spatial positioning of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individual.
@@
 Individual-specificity could theoretically arise from a variety of sources.
-For example, Individual variability could be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
+For example, individual variability could be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], and could relate to the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
 Alternatively, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014].
-Our results support this idea, echoing previous findings that DN is contained within sulci (in particular the superior rostral sulcus) in vmPFC [@Lopez2019].
-This relationship was heterogeneous throughout the rest of the search space.
-DN was likely located in gyri in more dorsal mPFC regions, whereas this association differed across hemispheres in PCC.
-An important goal for future work will be to assess whether the network layout in these regions can also be predicted on the basis of other aspects of brain structure, such as myeloarchitecture [@Glasser2016] or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
+Our results offer some support for this idea, echoing previous findings that DN is contained within sulci (in particular the superior rostral sulcus) in vmPFC [@Lopez2019].
+Structure/function associations were heterogeneous in other regions; DN tended to be located in gyri in more superior mPFC regions, whereas the association differed across hemispheres in PCC.
+Future studies should further characterize this heterogeneous relationship.
+Another important goal for future work will be to assess whether the network layout in these regions can also be predicted on the basis of other aspects of brain structure, such as myeloarchitecture [@Glasser2016] or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].
 
@@
 We circumvented this issue by independently identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially associated with the DN relative to subjective valuation in our meta-analysis.
-Our focus on this contrast was appropriate because of the notable topographical overlap between these processes in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017].
 We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals.
@@
 Previous work has also shown that functional correlations among pre-defined cortical parcels are highly stable within an individual [@Gratton2018b; @Kong2018].
-Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan, although estimates become considerably more unreliable).
-The motivation to sub-divide DN also stems from recent work by Kernbach et al.
+Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan, although estimates based on more data were more reliable).
+The motivation to subdivide DN also stems from recent work by Kernbach et al.
 [-@Kernbach2018], which identified specialized communication of parcels within DN with the rest of the brain in a large pool of individuals.
@@
 Community detection methods such as SP are stabilized by relying on  all pairwise correlations among cortical vertices (rather than correlations with an individual seed).
-In addition, we found we could increase the temporal stability of SP results by thresholding the underlying Fiedler vector.
+In addition, we found we could threshold the underlying Fiedler vector on the basis of the temporal stability of SP results.
 The magnitude of Fiedler vector values has been recently used to characterize the continuous connectivity profile of the insula with the rest of the brain, challenging the notion of discrete parcellations in that region [@Tian2018].
@@
 Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people.
-Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research.
+Understanding the interaction of networks DN-A, DN-B, and non-DN is an important goal for future research.
 SP is related to methods that have gained traction recently for distinguishing functional cortical gradients [@Margulies2016; @Huntenburg2018].
-Dedicated work could determine whether DN-A and DN-B form part of a gradual information processing sequence, or if their functions can be discretized.
-Regardless, this set of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
+A valuable goal for future work would be to asses whether DN-A and DN-B form part of a gradual information processing sequence, or if their functions can be discretized.
+Regardless, this set of results collectively suggested that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
 
@@
 Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying individualized topography in a data-driven way.
-The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help characterize heterogenous changes in mPFC activity in disorders such as depression and schizophrenia [@Hiser2018].
+The ability to capture an individual's functional topography without the need for group priors is clinically relevant, as it could help characterize heterogenous changes in mPFC activity in disorders such as depression and schizophrenia [@Hiser2018].
 It will be beneficial for future task-based fMRI experiments to be able to characterize where task-evoked activity is situated relative to an individual's overall mPFC organization.
-Our work was originally motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation versus episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], which have been grouped under the DN umbrella based on group averages [@Spreng2012], and potential topographic distinctions among multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010].
+Our work is relevant to interpreting the overlap of DN regions with task-related brain activity in numerous cognitive domains, including valuation [@Acikalin2017; @Shenhav2019], memory [@Euston2012], and self-referential thought [@Mitchell2005].
 An individualized frame of reference will enhance the ability of future studies to gauge similarities and differences among brain activity patterns associated with diverse psychological domains.

### 2019-09-14 Manuscript.Rmd
discussion and supplemental revisions done

@@
 The organization is also evident when using Modularity (third column), even though some isolated vertices were sometimes placed in a small third community (see subject 100408).
-The fourth column shows Fiedler vector maps after adding adding retrosplenial cortex (a common component of canonincal DN affected by task-deactivation).
-The addition of this area to the search space does not alter the original results, and the region is adequately covered by the DN community."}
+The fourth column shows Fiedler vector maps after adding retrosplenial cortex (a common component of canonincal DN affected by task-deactivation).
+The addition of this area to the search space does not alter the original results, and the retrosplenial region tends to be included in the DN community."}
 include_graphics("./Images/SFIG1.png")
@@
 The ARI decays more dramatically as a function of increasing dissimilarity, reaching 0 at chance levels.
-Low ARI values can therefore still occur when there is notable agreement between partitionings."}
+Low ARI values can therefore still occur when there is systematic agreement between partitionings."}
 
@@
 ```{r tSNR (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 3.
-Signal quality prior to FV thresholding.
+BOLD signal quality in the mPFC and PCC search space.
 Left: Surface map displaying the vertex-wise mean tSNR across individuals.
@@
 Visual examples of idiosyncratic organization across days and runs.
-Left: Thresholded partitionings captured with SP are highly similar across days within individuals, but are topographically distinct across individuals.
-The organization estimated for each dat is also mostly indistinct from that captured using the full time series (Supplemental Figure 1).
-Right: Thresholded partitionings estimated using the first scanning session from day 1, and the last scanning session from day 2.
-As expected, the considerable reduction in the amount of data used decreased the reliability of the community localization across single scanning sessions, which were in some cases irrecoverable (e.g.
+Left: Thresholded partitionings captured with SP were highly similar across days within individuals, but were topographically distinct across individuals.
+The organization estimated for each day was generally similar to that captured using the full time series (Supplemental Figure 1).
+Right: Thresholded partitionings estimated using the first scanning run from day 1, and the last scanning run from day 2.
+As expected, the considerable reduction in the amount of data used decreased the reliability of the community localization across single scanning runs, which were in some cases irrecoverable (e.g.
 subjects 100408 and 687163).
-Even so, the general location of DN and non-DN is still observable in many cases, and is comparable to the organization seen using larger amounts of data.
-This shows that even with notably noisier estimates and lower within-individual ARI values produced by working with less data, it is possible to gain information about the general location of DN and non-DN in individuals."}
+Even so, the general location of DN and non-DN was still observable in many cases, and is comparable to the organization seen using larger amounts of data.
+This shows that even with notably noisier estimates and lower within-individual ARI values from working with less data, it was possible to gain information about the general location of DN and non-DN in individuals."}
 include_graphics("./Images/SFIG4.png")
@@
 ```{r extra B&B checks with silhouette (supplemental fig 5), out.width = "100%", fig.align = "center", fig.cap = "Supplemental Figure 5.
-Additional checks to confirm the match between our findings with Braga et al.
+Additional checks to confirm the match between our findings and Braga et al.
 (2019).
-A: DN sub-networks A and B identified through whole-brain k-means clustering are congruent with the existence of a third sub-network, which matches the non-DN SP community (top rows).
-Limiting k-means to two clusters within the search space aligns with results from modularity (bottom two rows).
+A: DN sub-networks A and B identified through whole-brain k-means clustering were congruent with the existence of a third sub-network, which matched the non-DN SP community (top rows).
+Limiting k-means to two clusters within the search space aligned with results from modularity (bottom two rows).
 B: K-means based silhouette scores were computed per individual to determine the appropriate number of clusters within the search space (the higher the score, the better).
-This showed that two networks were the ideal solution."}
+This showed that two networks produced the preferred solution."}
 # # produce the silhouette plot

### 2019-09-14 Manuscript.Rmd
tiny hiccup error

@@
                           p_unc = t.test(Correlation)$p.val,
-                          Sig = p < 0.05,
+                          #Sig = p < 0.05,
                           ES = DescTools::CohenD(Correlation))

### 2019-09-14 Manuscript.Rmd
yet more tweaks

--- 2019-09-14 Manuscript.Rmd
@@
                           TStat = round(t.test(Correlation)$statistic, digits = 2),
-                          p_unc = t.test(Correlation)$p.val,
+                          p = round(t.test(Correlation)$p.val, digits = 3),
                           Sig = p < 0.05,
                           ES = DescTools::CohenD(Correlation))
-
-# FDR correction
-curvStats$p <- round(p.adjust(curvStats$p_unc, method = "BY"), digits = 3)
 
@@
 Results are shown in Figure 8B.
-Correlations tended to be slightly negative in vmPFC, both on the left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`); the distribution was only significantly different from zero in the right hemisphere, and weakly so (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`, FDR corrected; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
+Correlations tended to be slightly negative in vmPFC, both on the left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`); the distribution was only significantly different from zero in the right hemisphere, and weakly so (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
 Correlations between FV and curvature were positive and significantly different from zero in sup-mPFC, both on the left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`).
@@
 The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2)`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`).
-These results provide preliminary indictations that the association between function and structure is heterogenous across subregions of the canonical DN.
+These results provide preliminary indicatations that the association between function and structure is heterogenous across subregions of the canonical DN.
 

### 2019-09-16 Manuscript.Rmd
final JTM revision

@@
 
-- Medial Default Network overlaps topographically with task effects such as valuation.
-
-- Overlap at the group level could be due to variability across individuals.
-
-- Individual subject level Default Networks were identified with Spectral Partitioning.
-
-- Topographical organization is highly idiosyncratic, especially in frontal regions.
-
-- Group-level overlap may be spurious and should be examined at the individual level.
+- The topography of Default Network cortical regions varies across individuals.
+
+- A community detection algorithm, spectral partitioning, was applied to rs-fMRI data.
+
+- The algorithm identified individualized Default Network regions in mPFC and PCC.
+
+- Default Network topography varied across individuals in mPFC, moreso than in PCC.
+
+- Overlap of task effects with DN regions should be assessed at the individual level.
 
@@
   Regions of human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are part of the default network (DN), and additionally are implicated in diverse cognitive functions ranging from autobiographical memory to subjective valuation.
-Our ability to interpret the apparent co-localization of these effects is constrained by a limited understanding of the individual-level heterogeneity in mPFC/PCC functional organization.
+Our ability to interpret the apparent co-localization of task-related effects with DN-regions is constrained by a limited understanding of the individual-level heterogeneity in mPFC/PCC functional organization.
 Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was more strongly associated with the DN than with valuation effects.
 We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to partition mPFC and PCC into "DN" and "non-DN" subdivisions in individual participants (n = 100 from the Human Connectome Project).
-The spectral partitioning algorithm identified individual-level cortical subdivisions that were reliable across test/retest datasets and varied markedly across individuals, especially in mPFC.
-Our results point toward a new generation of strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions, especially at the individual level.
-
-Keywords: functional connectivity, default network, individual differences, network neuroscience, medial prefrontal cortex, spectral partitioning
+The spectral partitioning algorithm identified individual-level cortical subdivisions that varied markedly across individuals, especially in mPFC, and were reliable across test/retest datasets.
+Our results point toward new strategies for assessing whether distinct cognitive functions engage common or distinct mPFC subregions at the individual level.
+
+Keywords: functional connectivity, default network, network neuroscience, medial prefrontal cortex, spectral partitioning
 
@@
 
-Many different cognitive task manipulations evoke patterns of brain activity that overlap with DN regions in ventral/anterior mPFC and in PCC.
+Many different cognitive task manipulations evoke patterns of brain activity that overlap with DN regions in ventral and anterior mPFC and in PCC.
 Examples include manipulations of self-referential thinking [@Gusnard2001; @Mitchell2005], memory [@Euston2012; @Schacter2007], affective regulation [@Reddan2018; @Schiller2008], and subjective valuation [@Bartra2013; @Clithero2014; @Kable2007; @Levy2011].
-Some of these task-related effects are thought to reflect processes integral to the functional role of the DN, such as internally oriented cognition, scene construction, and self-projection [@Hassabis2007].
+Some of these task-related effects are thought to reflect processes integral to the functional role of the DN, such as internally oriented cognition, scene construction, and self-projection [@Buckner2007; @Hassabis2007].
 For other task-related effects, such as subjective valuation (i.e., greater BOLD activity in response to more highly valued choice prospects and outcomes, relative to prospects and outcomes that are less highly valued), the degree of overlap with DN regions is only partial and the reason for the overlap is less obvious [@Acikalin2017].
-Insofar as the DN shares a subset of nodes in common with the distributed brain system that supports valuation and other functions, this has potential to inform our theoretical understanding of the cognitive operations involved in those functions [@Northoff2012].
+Insofar as the DN shares a subset of nodes in common with the distributed brain systems that support valuation and other functions, this has potential to inform our theoretical understanding of the cognitive operations involved in those functions [@Northoff2012].
 As a result, there is widespread interest in understanding the degree to which DN regions overlap topographically with task-related effects [@Buckner2019; @Dinicola2019; @Spreng2012].
@@
 Recent work has uncovered fine-grained subdivisions within the DN using both data-driven clustering and individually customized seed-based connectivity analysis [@Braga2017; @Braga2019].
-It is therefore possible that the previously reported overlap of the DN with task-related effects could, in some cases, be attributed to low effective spatial resolution, and that the organization of mPFC and PCC would be better understood at the individual level.
-An important first step, and the goal of the present paper, is to quantify the degree of variability in the topography of the DN within mPFC and PCC across a large sample of individuals.
-The methods we propose for individual-level identification of DN regions have potential to benefit future investigations of the overlap between DN regions and task-related activity.
+It is therefore possible that the apparent overlap of the DN with task-related effects might, in some cases, be attributable to low effective spatial resolution, and that the organization of mPFC and PCC might be better understood at the individual level.
+An important first step in investigating this possibility, and the goal of the present paper, is to quantify the degree of variability in the topography of the DN within mPFC and PCC across a large sample of individuals.
 
@@
 A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level.
-Valuation was selected as a domain in which task-related activity patterns overlap extensively with DN regions on the medial surface, despite being segregable elsewhere [@Acikalin2017].
+Valuation was selected as an example of a cognitive domain in which group-average activity patterns overlap extensively with DN regions on the medial surface, despite being segregable elsewhere [@Acikalin2017].
 We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC).
@@
 Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity.
-We found that the DN community was likely to be located within principal sulci in ventral mPFC and left PCC, but in gyri within superior mPFC and right PCC.
+We observed a trend for the DN community to be located within principal sulci in ventral mPFC and left PCC, but in gyri within superior mPFC and right PCC.
 Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019].
-Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, provides a new framework and tool set for future investigations of overlap across cognitive domains.
+Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, and provides a new framework and tool set for future investigations of overlap across cognitive domains.
 
@@
 All code used in this study is openly available at [https://github.com/ctoroserey/mPFC_partitioning](https://github.com/ctoroserey/mPFC_partitioning).
-Resting-state fMRI data was acquired from the Human Connectome Project [@VanEssen2012].
+Resting-state fMRI data were obtained from the Human Connectome Project [@VanEssen2012].
 
@@
 Steps (in order) included linear interpolation across high motion timepoints with over 0.5 mm of FD, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), and temporal denoising via mean grayordinate signal regression [@Burgess2016].
-Interpolation of high motion time points is performed to avoid temporal smoothing of noisy signal from head motion into the filtered signal during the bandpass procedure.
+Interpolation of high motion time points was performed to avoid temporal smoothing of noisy signal from head motion into the filtered signal during the bandpass procedure.
 After filtering and denoising, the interpolated high-motion time points were censored by deletion and each run was temporally de-meaned.
@@
 fully-connected) weighted graphs [@chung1997].
-However, our results are unchanged if we cut all non-significant correlations from the weight matrices (uncorrected).
+However, our results were unchanged if we retained only significant correlations (*p* < 0.05, uncorrected) in the weight matrices.
 Next, we took the exponential of the z-transformed correlations so that all weights became positive while maintaining their ordinal ranks.
 Ensuring that all edges were positive facilitated the construction of the graph Laplacian (see below), which requires all off-diagonal elements to have the same sign by design.
-We generated and analyzed network weight matrices at four levels: (1) for each subject's full concatenated dataset (up to 4800 TRs); (2) on each step of a sliding window analysis (see Partition Evaluation for more details); (3) for the concatenated time series for the two runs on each day (up to 2400 TRs); and (4) for each run separately (up to 1200 TRs).
+We generated and analyzed network weight matrices at four levels: (1) for each subject's full concatenated dataset (up to 4800 TRs); (2) on each step of a sliding window analysis (see Section 2.7 for more details); (3) for the concatenated time series for the two runs on each day (up to 2400 TRs); and (4) for each run separately (up to 1200 TRs).
 
@@
 
-Where $I$ is an identity matrix of size $n$, and $D$ is a diagonal matrix containing the strength of each vertex (i.e.
+where $I$ is an identity matrix of size $n$, and $D$ is a diagonal matrix containing the strength of each vertex (i.e.
 the sum of its edge weights with all other vertices).
@@
 We then computed the eigenvalues and eigenvectors of the symmetric normalized Laplacian matrix, and used the eigenvector associated with the second-to-lowest eigenvalue (traditionally called the 'Fiedler vector') to divide the network into two.
-The Fiedler vector consists of a set of positive and negative values and is binarized by sign to partition the network into two similarly-sized communities [@Fiedler1975].
+The Fiedler vector consists of a set of positive and negative values and is binarized by sign to partition the network into two similar-sized communities [@Fiedler1975].
 In this way, SP avoids producing communities that are too small to be physiologically meaningful (for example, small sets of vertices that are spuriously correlated due to measurement noise).
@@
 We performed a number of comparisons among partitions.
-First, we computed the degree of agreement between SP and modularity per subject.
-SP and Modularity have been previously found to show a tendency for underfitting and overfitting, respectively, in their community detection performance in a diverse set of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings.
+First, we computed the degree of agreement between SP and modularity maximization per subject.
+SP and modularity maximization have been previously found to show a tendency toward underfitting and overfitting, respectively, in their community detection performance in a diverse set of network types [@Ghasemian2018], so alignment between the two algorithms would increase our confidence in the validity of the resulting partitionings.
 Next, we compared the subject-level SP partitionings across individuals, and calculated the mean pairwise ARI for the group.
 We then performed the same evaluation for PCC and mPFC separately, and examined whether there were differences in overall agreement within these regions by performing a paired permutation analysis.
-For each individual and region we got the mean ARI with all 99 other individuals, then took the difference between regions to get an ARI difference per subject.
-On each of 5000 permutations each subject’s ARI difference was independently sign-flipped and the mean difference across subjects was added to a null distribution.
-The empirical difference in mean pairwise ARI between regions was then evaluated against this permuted distribution.
+For each individual and region we took the mean ARI with all 99 other individuals, then took the difference between regions to get an ARI difference per subject.
+On each of 5000 permutations each subject’s ARI difference was independently sign-flipped and the group mean difference was added to a null distribution.
+The unpermuted group mean difference was then evaluated against this permuted distribution.
 
@@
 Independently for each day (2 per individual), we estimated each subject's DN partition in mPFC based on its vertex-wise functional correlations (Pearson) with the spatially averaged activity across all vertices in the PCC search space.
-We used the whole PCC region because it is traditionally thought to be part of the DN [@Buckner2008], it is a common area for researchers to place seeds for vertex- and volume-based connectivity analyses [@Fox2005], and it was often dominated by the DN community.
+We used the whole PCC region because it is traditionally thought to be a prominent node of the DN [@Buckner2008], and is a common area for researchers to place seeds for vertex- and volume-based connectivity analyses [e.g.
+@Fox2005].
 We compared these seed-based maps with the unthresholded Fiedler vectors produced by SP, with the sign of the Fiedler vector oriented so the DN community was marked by positive values in every subject.
@@
 These spatial correlations were meant to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them.
-For 8 subjects, the communities produced with one of the days' data sets had split coverage of area 7m, and so our community labeling scheme for the Fiedler vector produced a sign mismatch across days.
+For 8 subjects, the communities produced with one of the days' data sets had split coverage of area 7m, and our community labeling scheme for the Fiedler vector produced a sign mismatch across days.
 ARI is robust to such labeling issues, but the inconsistency produced strong negative correlations of the Fiedler vector across days for these individuals.
@@
 B: Regions identified in permutation-based chi-squared tests contrasting the two literatures.
-Area 25 (in red) was disregarded because of the possible confound with projections from spheres located in ventral striatum (see text for details).
+Area 25 (in red) initially appeared to be associated with valuation, but was not interpreted because the effect was found to reflect carryover from subcortical foci centered in ventral striatum (see text for details).
 Areas in blue represent the remainder of the search space."}
@@
 Using each individual's full time series (approximately 4800 total TRs from four 14-min scanning runs acquired over two days), we calculated the full vertex-to-vertex correlation matrix for the `r nVertices` surface vertices in the search space.
-We represented each individual's correlation matrix in the form of a network, with cortical surface vertices as nodes and thresholded/transformed correlation values as edge weights.
+We represented each individual's correlation matrix in the form of a network, with cortical surface vertices as nodes and transformed correlation values as edge weights.
 We then applied the SP community detection algorithm to partition the network into two cohesive functional communities.
@@
 The mPFC region tended to include DN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DN pocket between them.
-This non-DN section extended posteriorly into pregenual cinglate cortex (area a24).
-We note that the addition of restrosplenial cortex (an area commonly regarded as part of canonical DN) to the search space did not change these results; as expected, that the area tended to be largely assigned to the DN community (Supplemental Figure 1).
+This non-DN section extended posteriorly into pregenual cingulate cortex (area a24).
+We note that the addition of restrosplenial cortex (an area commonly regarded as part of canonical DN) to the search space did not change these results; as expected, that area tended to be largely assigned to the DN community (Supplemental Figure 1).
 
@@
 ``` {r Variability per subject: Fiedler vector vs prop.
-DN plot (Fig 4), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 4.
+DN plot (Fig 4), fig.align = "center", fig.width = 3, fig.height = 3, fig.cap = "Figure 4.
 A: For each individual, we produced partitions for each 20 minute sliding window (84 TRs).
-B: Proportion of times each vertex was affiliated with the DN community across windows (upper), and the continuous Fiedler vector map for the current subject using their full time series (lower).
-The maps share considerable qualitative similarities in their gradients along the cortical surface.
+B: Proportion of times each vertex was affiliated with the DN community across windows in one example subject (upper), and the continuous Fiedler vector map for the same subject using their full time series (lower).
 C: Relationship between the magnitude of Fiedler vector values and the proportion of DN affiliations.
@@
 However, mean tSNR after thresholding was significantly higher for mPFC than PCC (mPFC: mean = `r round(snr_means$overall[1, 2], digits = 2)`, SD = `r round(snr_means$overall[3, 2], digits = 2)`; PCC: mean = `r round(snr_means$overall[2, 2], digits = 2)`, SD = `r round(snr_means$overall[4, 2], digits = 2)`; permutation p-value `r ifelse(tsnrPermute_Post$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_Post$Pval))`, Cohen's D = `r round(tsnrCohen_Post[1], digits = 2)`).
-This reflected a significant increase in mean tSNR in mPFC as a result of the thresholding step (pre-threshold mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC was unchanged (pre-threshold mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
+This reflected a significant increase in mean tSNR in mPFC as a result of the thresholding step (pre-threshold mean = `r round(snr_means$overall[1, 1], digits = 2)`, SD = `r round(snr_means$overall[3, 1], digits = 2)`; paired permutation p-value `r ifelse(tsnrPermute_mPFC$Pval < 0.001, "< 0.001", paste("=", tsnrPermute_mPFC$Pval))`, Cohen's D = `r round(tsnrCohen_mPFC[1], digits = 2)`), whereas the mean signal quality in PCC increased only slightly (pre-threshold mean = `r round(snr_means$overall[2, 1], digits = 2)`, SD = `r round(snr_means$overall[4, 1], digits = 2)`; paired permutation p-value = `r tsnrPermute_PCC$Pval`, Cohen's D = `r round(tsnrCohen_PCC[1], digits = 2)`).
 In short, mPFC had higher overall tSNR, albeit with greater variability across nodes.
-Applying the thresholding step allowed us to focus the analysis on vertices with high signal quality.
+Applying the thresholding step focused the analysis on vertices with high signal quality.
 
@@
 Moreover, the ratios for mPFC were significantly greater than those for PCC when compared in a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`).
-This pattern was mostly unchanged when computed using modularity maximization to detect the communities, showing that the results persist even without a forced binarization (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
-These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found in Supplemental Figure 4).
+This pattern was mostly unchanged when computed using modularity maximization to detect the communities, showing that the results persisted even without a forced binarization (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`).
+These test/retest results suggest that the topographic variability seen in mPFC arose at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found in Supplemental Figure 4).
 We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner.
@@
 We generated a seed time-series by averaging all vertices in the PCC region of our search space, and calculated its correlation with the activity of each vertex in mPFC.
-The use of the whole PCC region (instead of just 7m) was meant to echo the way seed-based connectivity is often employed, relying on the group-average location of canonical DN regions.
+The use of the whole PCC region (instead of just 7m) was meant to represent a typical approach to seed-based connectivity that relies on the group-average location of canonical DN regions.
 We compared the map of correlation values in mPFC to the map of unthresholded Fiedler vector values using Spearman correlations across vertices.
@@
 
-Next, we asked if the idiosyncratic organization of the DN was corresponded to patterns of sulcal morphology.
+Next, we asked if the idiosyncratic organization of the DN corresponded to patterns of sulcal morphology.
 Several previous studies have provided evidence that sulcal and gyral organization informs the location of functional effects [@Amiez2013; @Amiez2014; @Zlatkina2016].
@@
 A: Correspondence between SP communities and sulcal morphology in two example individuals.
-Zoomed-in boxes show areas in PCC and ventral mPFC where the DN community appears to be guided by sulcal organization.
-This relationship is less defined in superior mPFC.
+Zoomed-in boxes show areas in PCC and ventral mPFC where the DN community appears to follow sulci.
 The superior rostral sulcus aligned with the DN community, in agreement with findings by Lopez-Persem et al.
@@
 B: Correlations between cortical curvature and the unthresholded Fiedler values.
-We divided the search space into three areas (left): ventral mPFC (yellow), superior mPFC (sup-mPFC, red), and PCC (blue).
-Boxplots on the right show the distribution of correlation values across individuals for each combination of region and hemisphere, indicating that DN (defined by positive FV values) tended to be represented in vmPFC sulci, but was likely located in gyri within sup-dmPFC.
+We divided the search space into three areas (left): vmPFC (yellow), superior mPFC (sup-mPFC, red), and PCC (blue).
+Boxplots on the right show the distribution of correlation values across individuals for each combination of region and hemisphere, indicating that the DN (defined by positive FV values) was associated with sulci in vmPFC, but with gyri within sup-dmPFC.
 PCC showed evidence of an opposite association across hemispheres."}
@@
 Results are shown in Figure 8B.
-Correlations tended to be slightly negative in vmPFC, both on the left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`); the distribution was only significantly different from zero in the right hemisphere, and weakly so (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
+Correlations tended to be slightly negative in vmPFC, both on the left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`); the distribution was only significantly different from zero in the right hemisphere, and weakly so (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`, uncorrected; Cohen's D = `r round(curvStats$ES[6], digits = 2)`).
 Correlations between FV and curvature were positive and significantly different from zero in sup-mPFC, both on the left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`).
-Correlations in PCC were negative and significantly different from zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
+Correlations in PCC were negative and significantly different from zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly greater than zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`).
 The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2)`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`).
-These results provide preliminary indicatations that the association between function and structure is heterogenous across subregions of the canonical DN.
+These results provide preliminary indications that the association between function and structure is heterogenous across subregions of the canonical DN.
 
@@
 The thresholded partitions we identified had conceptual and topographic similarities to DN sub-networks A and B proposed by Braga and Buckner [-@Braga2017].
-We explored the relationship between the two sets of sub-regions by reproducing their seed-based connectivity approach in two of our subjects.
-In their work, Braga and Buckner [-@Braga2017; @Braga2019] manually selected individual vertices in dorsolateral prefrontal cortex (DLPFC) that produced two spatially anticorrelated, interdigitated networks with distinctive patterns in the temporo-parietal junction (TPJ), inferior parietal lobule (IPL), parahippocampal cortex, mPFC, and PCC.
+We explored the relationship between the two sets of sub-regions by reproducing the previously described seed-based connectivity approach in two of our subjects.
+In previous work, Braga and Buckner [-@Braga2017; @Braga2019] manually selected individual vertices in dorsolateral prefrontal cortex (DLPFC) that produced two spatially anticorrelated, interdigitated networks with distinctive patterns in the temporo-parietal junction (TPJ), inferior parietal lobule (IPL), parahippocampal cortex, mPFC, and PCC.
 We hypothesized that if the SP communities corresponded to one or both of the previously proposed sub-networks, our partitionings should match networks A and B generated by seed-based functional connectivity in these diagnostic areas.
-For whole-brain functional connectomes from two individuals (100307 and 101006), we evaluated seeds in each diagnostic region that reproduced networks A and B (correlation coefficients thesholded at 0.2), and confirmed their placement based on functional connectivity patterns observed in the remaining areas.
+For whole-brain functional connectomes from two individuals (100307 and 101006), we evaluated seeds in each diagnostic region that reproduced networks A and B (correlation coefficients thresholded at 0.2), and confirmed their placement based on functional connectivity patterns observed in the remaining areas.
 In both individuals, seeds in posterior IPL and TPJ most clearly identified networks A and B, respectively.
@@
 Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex.
-Furthermore, they show that our approach, through its continuous-valued information, provides a way to estimate the location of the three networks in PCC and mPFC in a way that is less computationally demanding than full-brain clustering.
+Furthermore, the results show that the continuous-valued output of our approach provides a method for estimating the location of the three networks in PCC and mPFC that is less computationally demanding than full-brain clustering.
 
@@
 Panel B: thresholded communities (indicated by borders) show strong resemblance between the DN community and network A.
-The non-DN community covers sections of cortex not associated with either SP sub-network."}
+The non-DN community covers sections of cortex not associated with either DN sub-network."}
 
@@
 A considerable amount of meta-analytic work has been dedicated to characterizing the brain activity patterns associated with psychological processes in medial prefrontal cortex (mPFC), revealing both dissociable and overlapping activation across domains [@DelaVega2016; @Kragel2018; @Hiser2018].
-For example, activation patterns associated with subjective valuation and with the default network (DN) have been suggested to be indistinguishable in mPFC, with overlap also partially extending to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
+For example, topographic patterns associated with subjective valuation and with the default network (DN) have been suggested to be indistinguishable in mPFC, with overlap also partially extending to posterior cingulate cortex (PCC) [@Acikalin2017; @Bartra2013; @Clithero2014; @Laird2009].
 This apparent overlap of task-related effects with DN regions has important implications, as it has motivated theoretical proposals about ways in which these superficially dissimilar domains might involve a shared set of core cognitive processes [@Acikalin2017; @Clithero2014; @Northoff2012].
@@
 Individual-specificity could theoretically arise from a variety of sources.
-For example, individual variability could be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], and could relate to the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
+For example, individual variability could be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or could relate to the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018].
 Alternatively, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014].
@@
 SP is related to methods that have gained traction recently for distinguishing functional cortical gradients [@Margulies2016; @Huntenburg2018].
-A valuable goal for future work would be to asses whether DN-A and DN-B form part of a gradual information processing sequence, or if their functions can be discretized.
-Regardless, this set of results collectively suggested that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
+A valuable goal for future work would be to assess whether DN-A and DN-B form part of a gradual information processing sequence, or if their functions can be discretized.
+Regardless, this set of results collectively suggests that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.
 
@@
 Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying individualized topography in a data-driven way.
-The ability to capture an individual's functional topography without the need for group priors is clinically relevant, as it could help characterize heterogenous changes in mPFC activity in disorders such as depression and schizophrenia [@Hiser2018].
+The ability to capture an individual's functional topography without the need for group priors is clinically relevant, as it could help target the assessment of mPFC activity changes in disorders such as depression and schizophrenia [@Hiser2018].
 It will be beneficial for future task-based fMRI experiments to be able to characterize where task-evoked activity is situated relative to an individual's overall mPFC organization.
@@
 The organization is also evident when using Modularity (third column), even though some isolated vertices were sometimes placed in a small third community (see subject 100408).
-The fourth column shows Fiedler vector maps after adding retrosplenial cortex (a common component of canonincal DN affected by task-deactivation).
+The fourth column shows Fiedler vector maps after adding retrosplenial cortex (a common component of canonical DN affected by task-deactivation).
 The addition of this area to the search space does not alter the original results, and the retrosplenial region tends to be included in the DN community."}
@@
 Comparing the increasingly dissimilar maps by computing the proportion of equal cluster labelings (EQ) shows the expected linear decrease in similarity.
-The unadjusted form of the ARI (RI) displays an exponentially decaying similarity, and increases after reaching 50% as a result of node pairs once again being grouped in the same/different clusters (making the index label-agnostic).
-The ARI decays more dramatically as a function of increasing dissimilarity, reaching 0 at chance levels.
+The unadjusted form of the ARI (RI) displays a nonlinearly decaying similarity, and increases after reaching 50% as a result of node pairs once again being grouped in the same/different clusters (making the index label-agnostic).
+The ARI decays more steeply as a function of increasing dissimilarity, reaching 0 at chance levels.
 Low ARI values can therefore still occur when there is systematic agreement between partitionings."}
